### 2022-07-19 src/tex/ms.tex
[showyourwork] first commit

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@bruce-edelman}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
    Phasellus eu tellus sit amet tortor gravida placerat. 
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
    Praesent eget sem vel leo ultrices bibendum. 
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
    Curabitur auctor semper nulla donec varius orci eget risus. 
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
Phasellus eu tellus sit amet tortor gravida placerat. 
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
Praesent eget sem vel leo ultrices bibendum. 
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
Curabitur auctor semper nulla donec varius orci eget risus. 
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

\end{document}

### 2022-07-19 src/tex/ms.tex
first commit

@@
-% Define document class
-\documentclass[twocolumn]{aastex631}
-\usepackage{showyourwork}
+\documentclass[twocolumn, linenumber]{aastex63}
 
-% Begin!
+\newcommand{\msun}{\ensuremath{{\rm M}_\odot}}
+\newcommand{\result}[1]{\textcolor{red}{#1}}
+\newcommand{\bruce}[1]{\textcolor{blue}{BE: #1}}
+\newcommand{\NewChange}[1]{\textcolor{green}{#1}}
+
+\graphicspath{{./}{figures/}}
+
+\usepackage[perpage]{footmisc}
+\usepackage{colortbl}
+\usepackage{lineno}
+\usepackage{amsmath}
+\usepackage{appendix}
+\definecolor{Gray}{gray}{0.9}
+\linenumbers
+
 \begin{document}
 
-% Title
-\title{An open source scientific article}
+\title{Covering Your Basis: Model-Agnostic Inference of LIGO-Virgos Binary Black Hole Spin Distribution}
 
-% Author list
-\author{@bruce-edelman}
+\author{Bruce Edelman}
+\email{bedelman@uoregon.edu}
+\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
 
-% Abstract with filler text
+\author{Lexi Vives}
+\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
+
+\author{Ben Farr}
+\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
+
 \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-    Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-    Phasellus eu tellus sit amet tortor gravida placerat. 
-    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-    Praesent eget sem vel leo ultrices bibendum. 
-    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-    Curabitur auctor semper nulla donec varius orci eget risus. 
-    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-    Duis eget orci sit amet orci dignissim rutrum.
+We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical mass distribution of binary black holes using GWTC-3.
 \end{abstract}
 
-% Main body with filler text
-\section{Introduction}
-\label{sec:intro}
+\section{Introduction} \label{sec:intro}
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. 
-Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis. 
-Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna. 
-Donec vehicula augue eu neque, morbi tristique senectus et netus et. 
-Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum. 
-Phasellus eu tellus sit amet tortor gravida placerat. 
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. 
-Praesent eget sem vel leo ultrices bibendum. 
-Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac. 
-Curabitur auctor semper nulla donec varius orci eget risus. 
-Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam. 
-Duis eget orci sit amet orci dignissim rutrum.
+Now that gravitational wave observations of compact binary coalescence is a regular occurrence, producing catalogs of nearly 100 such detections, we now have access to a complete understanding of the population of compact binaries.
+In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration, the catalog size is expected to increase by a factor of 5.
+The extensive physics governing the formation and evolution of compact objects that end up merging is imprinted on the properties of the population of CBCs, allowing us to learn about these not well understood ideas through looking at the distribution of observed GWs.
+In particular the mass distribution of binary black holes has been shown to be very useful in measuring cosmological parameters, constraining modified gravitational wave propagation, constraining a running Planck mass, looking of evidence of ultralight bosons through superradiance, putting constraints on uncertain nuclear reaction rates important for stellar evolution, and even looking for primordial black holes.
+Through a better understanding of the mass, spin, and redshift distribution of compact binaries we can extend this be a useful tool in all the different physical applications mentioned above.
+In this paper we highlight how the use of basis-splines can be a useful model-agnostic modeling approach to the astrophysical distributions of compact binaries.
+We show that with a particular choice of basis, we can efficiently model the spin and/or mass distribution of compact binaries in GWTC-3 with spline regression in hierarchical Bayesian inference.
+We show our results are similar to those produced with the more simpler and motivated parametric models, while being capable of finding more subtle features should they appear in future catalogs.
+This method can be extended to higher-dimensional basis-splines to model correlations between different distributions which will be necessary to confidently disentangle differently competing formation channels should they exist.
 
-Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi. 
-Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae. 
-Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna. 
-Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante. 
-Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient. 
-Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis. 
-Pellentesque cursus luctus mauris \citep{Luger2021}.
+\section{Methods} \label{sec:methods}
+\subsection{Constructing A Basis} \label{sec:basis_splines}
 
-\bibliography{bib}
+A common non-parametric method in statistical applications is the use of B-Splines or basis splines.
+A spline function of order $k$, is a piece-wise polynomial of order $k-1$ polynomials stitched together from defined ``knot'' locations across the domain.
+They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights.
+B-Splines of order $k$ are a set of order $k-1$ polynomials that form a complete basis for any spline function of order $k$.
+Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for every possible spline function with knots, $\mathbf{t}$.
+One can construct the B-Splines for a given knot vector using the Cox-de Boor recursion formula -- for knots $t_0$, $t_1$,...,$t_{i+k}$ the basis components are given by:
+\begin{equation}
+    B_{i,1}(x | \mathbf{t}) = 
+    \begin{cases}
+        1, & \text{if } t_i \leq x < t_{i+1} \\
+        0, & \text{otherwise}
+    \end{cases}
+\end{equation}
+\begin{equation}
+    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x)B_{i,k}(x) + \big[1-\omega_{i+1,k}(x)\big]B_{i+1,k}(x)
+\end{equation}
+\noindent Where $\omega_{i,k}$ above is defined as:
+\begin{equation}
+    \omega_{i,k}(x | \mathbf{t}) =
+    \begin{cases}
+        \frac{x-t_i}{t_{i+k}-t_i}, & t_{i+k} \neq t_i \\
+        0, & \text{otherwise}
+    \end{cases}
+\end{equation}
+
+A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function.
+Namely, $M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$.
+The M-Spline basis only differs from B-Splines by a normalization factor, namely:
+\begin{equation}\label{eq:MB_SplineRelation}
+    M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
+\end{equation}
+\noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper.
+
+Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1.
+Notice that when we introduced knots and in equation \ref{eq:MB_SplineRelation}, you can see there needs to be knots up to $t_{i+k}$ while $i$ indexes the desired degrees of freedom in your basis.
+This means in practice one must define $n+k$ knots.
+However, you have control in the boundary conditions by how many of the $n+k$ knots you place at the lower and upper bounds.
+By placing $k$ knots at each boundary (leaving $n-k$ interior knots), the first and last basis components are maximized at the boundaries.
+Alternatively one may want to a-priori enforce vanishing boundary conditions, for example, if they knew for a fact that the function they are modeling has $p(x_\mathrm{bound}) = 0$.
+This can be done by placing $k-1$ knots at the boundaries you wish the spline to vanish at.
+See figure for an example of a cubic M-Spline (k=3) basis with 10 degrees of freedom with $k=3$ knots at each boundary (left) versus enforcing vanishing boundary conditions by having $k-1=2$ knots at each boundary (right).
+
+\subsection{Parameterized Perturbations} \label{sec:perturbation_model}
+\subsection{Generic Mass Model} \label{sec:nonparametric_model}
+\section{Results} \label{sec:results}
+\subsection{Mass Spectrum Inference with GWTC-3} \label{sec:GWTC3_inferece}
+\section{Conclusions}\label{sec:conclusion}
+\section{Acknowledgements}\label{sec:acknowledments}
+This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
+This work benefited from access to the University of Oregon high performance computer, Talapas.
+This material is based upon work supported in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility fully funded by the National Science Foundation.
+\software{
+\textsc{Astropy}~\citep{2018AJ....156..123A},
+\textsc{NumPy}~\citep{harris2020array},
+\textsc{Matplotlib}~\citep{Hunter:2007},
+\textsc{bilby}~\citep{Ashton_2019},
+\textsc{GWPopulation}~\citep{Talbot_2019}
+}
+\bibliography{references}{}
+\bibliographystyle{aasjournal}
+
+\appendix
+\section{Hierarchical Bayesian Inference} \label{sec:hierarchical_inference}
+
+% This appendix goes over in detail the hierarchical bayeisan inference framework
+We use hierarchical Bayesian inference to simultaneously infer the population distributions of the primary masses ($m_1$), mass ratios ($q$) and the redshifts ($z$) of observed BBHs.
+For a set of hyper-parameters, $\Lambda$, and local ($z=0$) merger rate density (units of mergers per co-moving volume per time), $\mathcal{R}_0$, we write the overall number density of BBH mergers in the universe as:
+
+\begin{equation} \label{number_density}
+     \frac{dN(m_1, q, z | \mathcal{R}_0, \Lambda)}{dm_1dqdz} = \frac{dV_c}{dz}\bigg(\frac{T_\mathrm{obs}}{1+z}\bigg) \frac{d\mathcal{R}(m_1, q, z | \mathcal{R}_0, \Lambda)}{dm_1dq} = \mathcal{R}_0 p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)
+\end{equation}
+
+\noindent
+Above, $dV_c$ is the co-moving volume element \citep{hogg_cosmo} and $T_\mathrm{obs}$, the observing time period that produced the catalog with the related factor of $1+z$ converting this detector-frame time to source-frame.
+We assume a LambdaCDM cosmology using the cosmological parameters from \citet{Planck2015}.
+The redshift evolution of the merger rate follows $p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$.
+Integrating equation \ref{number_density} across all masses, and up to some redshift, $z_m$, returns the total number of BBH mergers in the universe out to that redshift.
+Let $\{d_i\}$ represent a set of data from $N_\mathrm{obs}$ observed gravitational waves associated with BBH mergers.
+We model the merger rate as an inhomogenous point process and when imposing a log-uniform prior on the merger rate, we can marginalize over the merger rate to get the posterior distribution of our hyper-parameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.
+
+\begin{equation} \label{posterior}
+    p\left(\Lambda | \{d_i\} \right) \propto \frac{p(\Lambda)}{\xi(\Lambda)^{N_\mathrm{obs}}} \prod_{i=1}^{N_\mathrm{obs}} \Bigg[ \int \mathcal{L}\left(d_i | m_1^i, q^i, z^i \right) p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda) dm_1 dq dz \Bigg],
+\end{equation}
+
+\noindent
+where, $\mathcal{L}(d_i|m_1, q, z)$, is the single-event likelihood function from each events original analysis, and $\xi(\Lambda)$ is the detection efficiency given a population distribution described by $\Lambda$.
+The procedure for calculating $\xi(\Lambda)$ is described in more detail below.
+The LVC reports out posterior samples for each observed event, with which we can use importance sampling to estimate the integrals above in equation \ref{posterior}.
+We replace the integrals with ensemble averages over $K_i$ posterior samples associated with each event in the catalog:
+
+\begin{equation}
+ p\left(\Lambda | \{d_i\}\right) \propto p(\Lambda) \prod_{i=1}^{N_\mathrm{obs}} \bigg[ \frac{1}{K_i} \sum_{j=1}^{K_i} \frac{p(m_1^{i,j}|\Lambda)p(q^{i,j}|\Lambda)p(z^{i,j}|\Lambda)}{\pi(m_1^{i,j}, q^{i,j}, z^{i,j})} \bigg]
+\end{equation}
+
+\noindent 
+Here $j$ indexes the $K_i$ posterior samples from each event and $\pi(m_1, q, z)$ is the default prior used by parameter estimations that produced the posterior samples for each event.
+In the analyses of GWTC-2 the default prior used is uniform in detector frame masses and Euclidean volume.
+The corresponding prior evaluated in source frame masses and redshift is $\pi(m_1, q, z) \propto m_1(1+z)^2 D_L^2(z) \frac{dD_L}{dz}$, where $D_L$ is the luminosity distance.
+
+To carefully incorporate selection effects to our model we need to quantify the detection efficiency, $\xi(\Lambda)$, of the search pipelines that were used to create GWTC-2, at a given population distribution described by $\Lambda$.
+
+\begin{equation} \label{det_eff}
+     \xi(\Lambda) = \int dm_1 dq dz P_\mathrm{det}(m_1, q, z)p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)
+\end{equation}
+
+\noindent The above integral is not tractable since there is no analytic prescription for $P_\mathrm{det}(m_1,q,z)$, the detection probability of an individual event.
+To estimate this integral we use a software injection campaign where GWs from a fixed, broad population of sources are simulated, put into real detector data, and then run through the same search pipelines that were used to produce the catalog we are analyzing \footnote{For O3a we used the injection sets used by \citet{o3a_pop}, which can be found at https://dcc.ligo.org/LIGO-P2000217/public.
+For O1/O2 we used the mock injection sets used by \citet{o1o2_pop} which can be found at https://dcc.ligo.org/LIGO-P2000434/public}.
+With these search results in hand, we use importance sampling to evaluate the integral in equation \ref{det_eff}:
+
+\begin{equation} \label{xi}
+     \xi(\Lambda) = \frac{1}{N_\mathrm{inj}} \sum_{i=1}^{N_\mathrm{found}} \frac{p(m_1^i | \Lambda) p(q^i | m_1, \Lambda) p(z^i | \Lambda)}{p_\mathrm{inj}(m_1^i, q^i, z^i)}
+\end{equation}
+
+\noindent
+Where the sum indexes only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, and $p_\mathrm{inj}(m_1, q, z)$ is the reference distribution from which the injections were drawn.
+Additionally, we follow the procedure outlined in \citet{Farr_2019} to marginalize the uncertainty in our estimate of $\xi(\Lambda)$ due to a finite number of simulated events.
+We make the assumption that repeated sampling of $\xi(\Lambda)$ will follow a normal distribution with $\xi(\Lambda) \sim \mathcal{N}(\mu(\Lambda), \sigma(\Lambda))$, where the mean, $\mu$, is the estimate from equation \ref{xi}, while the variance, $\sigma^2$, is defined as:
+
+\begin{equation}
+    \sigma^2(\Lambda) \equiv \frac{\mu^2(\Lambda)}{N_\mathrm{eff}} \simeq \frac{1}{N^2_\mathrm{inj}} \sum_{i=1}^{N_\mathrm{found}} \bigg[\frac{p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)}{p_\mathrm{inj}(m_1, q, z)}\bigg]^2 - \frac{\mu^2(\Lambda)}{N_\mathrm{inj}}
+\end{equation}
+
+\noindent
+Above we define $N_\mathrm{eff}$ as the effective number of independent draws contributing to the importance sampled estimate, in which we verify to be sufficiently high after re-weighting the injections to a given population (i.e.
+$N_\mathrm{eff} > 4N_\mathrm{obs}$).
+We write the hyper-posterior marginalized over the merger rate and uncertainty in estimation of $\xi(\Lambda)$, neglecting terms of $\mathcal{O}(N_\mathrm{eff}^{-2})$ or greater \citep{Farr_2019}, as:
+
+\begin{equation}\label{importance-posterior}
+    \log p\left(\Lambda | \{d_i\}\right) \propto \sum_{i=1}^{N_\mathrm{obs}} \log \bigg[ \frac{1}{K_i} \sum_{j=1}^{K_i} \frac{p(m_1^{i,j}|\Lambda)p(q^{i,j}|\Lambda)p(z^{i,j}|\Lambda)}{\pi(m_1^{i,j}, q^{i,j}, z^{i,j})} \bigg] -  \\
+    N_\mathrm{obs} \log \mu + \frac{3N_\mathrm{obs} + N_\mathrm{obs}^2}{2N_\mathrm{eff}} + \mathcal{O}(N_\mathrm{eff}^{-2}).
+\end{equation}
+
+\noindent
+We explicitly enumerate each of the models used in this work for $p(m_1|\Lambda)$, $p(q|m_1, \Lambda)$, and $p(z|\Lambda)$ along with their respective hyper-parameters and prior distributions in Table \ref{tab:model_params}.
+To calculate marginal likelihoods and draw samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the \textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}.
+
+\section{Validation Studies} \label{sec:validation}
 

### 2022-07-19 src/scripts/mpl_utils.py
add mpl_utils for consistent plot fmts

@@ -1,0 +1,365 @@
+from warnings import warn
+from cycler import cycler
+import numpy as np
+import matplotlib as mpl
+mpl.use("Agg")
+import matplotlib.pyplot as plt
+
+# set random seed for reproducibility
+np.random.seed(0)
+
+# Standardized figure widths in inches.
+# These are based on the output of `\the\textwidth` and `\the\columnwidth` in
+# the LaTeX document.  If we change our LaTeX template, we should double-check
+# that they do not change.
+# NOTE: If LaTeX displays a number in `pt` units, divide by 72 to get inches.
+widths = {
+    'textwidth' : 7.0,
+    'columnwidth' : 3.0,
+}
+
+
+def limit_ax_oom(
+        ax, n_oom: int, x_or_y: str,
+        measure_from: str="upper", base: float=10.0,
+    ) -> None:
+    r"""
+    Takes a :class:`matplotlib.axes._subplots.AxesSubplot` object, and limits
+    its limits to ``n_oom`` orders of magnitude (in the logarithmic base set by
+    the ``base`` parameter, ``10.0`` by default) from either the upper or lower
+    data limit (set with ``measure_from`` argument, "upper" by default).  Either
+    operates on x- or y-axis, set by passing "x" or "y" for ``x_or_y`` argument.
+
+    If the data limits are already within the specified orders of magnitude, no
+    changes will be made.
+    """
+    import math
+    import numpy
+
+    # Validate inputs.
+    if x_or_y not in {"x", "y"}:
+        raise KeyError("Invalid choice for 'x_or_y', must be either 'x' or 'y'")
+    if measure_from not in {"upper", "lower"}:
+        raise KeyError(
+            "Invalid choice for 'measure_from', must be either 'upper' or "
+            "'lower'"
+        )
+
+    # Get data limits along specified axis.
+    if x_or_y == "x":
+        data_lo, data_hi = ax.dataLim.x0, ax.dataLim.x1
+    else:
+        data_lo, data_hi = ax.dataLim.y0, ax.dataLim.y1
+
+    # Convert data limits to log-scale, rounding to the next integer.
[…]

### 2022-07-19 src/tex/ms.tex
remove figs to check build
enforce line breaks in tex text

@@
 
+\usepackage{showyourwork}
 \usepackage[perpage]{footmisc}
@@
 \begin{abstract}
-We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical mass distribution of binary black holes using GWTC-3.
+We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical mass distribution of 
+binary black holes using GWTC-3.
 \end{abstract}
@@
 
-Now that gravitational wave observations of compact binary coalescence is a regular occurrence, producing catalogs of nearly 100 such detections, we now have access to a complete understanding of the population of compact binaries.
-In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration, the catalog size is expected to increase by a factor of 5.
-The extensive physics governing the formation and evolution of compact objects that end up merging is imprinted on the properties of the population of CBCs, allowing us to learn about these not well understood ideas through looking at the distribution of observed GWs.
-In particular the mass distribution of binary black holes has been shown to be very useful in measuring cosmological parameters, constraining modified gravitational wave propagation, constraining a running Planck mass, looking of evidence of ultralight bosons through superradiance, putting constraints on uncertain nuclear reaction rates important for stellar evolution, and even looking for primordial black holes.
-Through a better understanding of the mass, spin, and redshift distribution of compact binaries we can extend this be a useful tool in all the different physical applications mentioned above.
-In this paper we highlight how the use of basis-splines can be a useful model-agnostic modeling approach to the astrophysical distributions of compact binaries.
-We show that with a particular choice of basis, we can efficiently model the spin and/or mass distribution of compact binaries in GWTC-3 with spline regression in hierarchical Bayesian inference.
-We show our results are similar to those produced with the more simpler and motivated parametric models, while being capable of finding more subtle features should they appear in future catalogs.
-This method can be extended to higher-dimensional basis-splines to model correlations between different distributions which will be necessary to confidently disentangle differently competing formation channels should they exist.
+Now that gravitational wave observations of compact binary coalescence is a regular occurrence, producing catalogs of nearly 
+100 such detections, we now have access to a complete understanding of the population of compact binaries. In the coming fourth 
+observing run of the LIGO-Virgo-KAGRA collaboration, the catalog size is expected to increase by a factor of 5. The extensive 
+physics governing the formation and evolution of compact objects that end up merging is imprinted on the properties of the population 
+of CBCs, allowing us to learn about these not well understood ideas through looking at the distribution of observed GWs. In particular 
+the mass distribution of binary black holes has been shown to be very useful in measuring cosmological parameters, constraining modified 
+gravitational wave propagation, constraining a running Planck mass, looking of evidence of ultralight bosons through superradiance, 
+putting constraints on uncertain nuclear reaction rates important for stellar evolution, and even looking for primordial black holes. 
+Through a better understanding of the mass, spin, and redshift distribution of compact binaries we can extend this be a useful tool 
+in all the different physical applications mentioned above. In this paper we highlight how the use of basis-splines can be a useful 
+model-agnostic modeling approach to the astrophysical distributions of compact binaries. We show that with a particular choice of basis, 
+we can efficiently model the spin and/or mass distribution of compact binaries in GWTC-3 with spline regression in hierarchical 
+Bayesian inference. We show our results are similar to those produced with the more simpler and motivated parametric models, 
+while being capable of finding more subtle features should they appear in future catalogs. This method can be extended to higher-dimensional 
+basis-splines to model correlations between different distributions which will be necessary to confidently disentangle differently 
+competing formation channels should they exist.
 
@@
 
-A common non-parametric method in statistical applications is the use of B-Splines or basis splines.
-A spline function of order $k$, is a piece-wise polynomial of order $k-1$ polynomials stitched together from defined ``knot'' locations across the domain.
+A common non-parametric method in statistical applications is the use of B-Splines or basis splines. A spline function of order $k$, 
+is a piece-wise polynomial of order $k-1$ polynomials stitched together from defined ``knot'' locations across the domain. 
 They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
 B-Splines of order $k$ are a set of order $k-1$ polynomials that form a complete basis for any spline function of order $k$. 
-Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for every possible spline function with knots, $\mathbf{t}$.
-One can construct the B-Splines for a given knot vector using the Cox-de Boor recursion formula -- for knots $t_0$, $t_1$,...,$t_{i+k}$ the basis components are given by:
+Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
+every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines for a given knot vector using the Cox-de Boor 
+recursion formula -- for knots $t_0$, $t_1$,...,$t_{i+k}$ the basis components are given by:
 \begin{equation}
@@
 
-A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function.
-Namely, $M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$.
-The M-Spline basis only differs from B-Splines by a normalization factor, namely:
+A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function. Namely, 
+$M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. The M-Spline basis only differs 
+from B-Splines by a normalization factor, namely:
 \begin{equation}\label{eq:MB_SplineRelation}
@@
 
-Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1.
-Notice that when we introduced knots and in equation \ref{eq:MB_SplineRelation}, you can see there needs to be knots up to $t_{i+k}$ while $i$ indexes the desired degrees of freedom in your basis.
-This means in practice one must define $n+k$ knots.
-However, you have control in the boundary conditions by how many of the $n+k$ knots you place at the lower and upper bounds.
-By placing $k$ knots at each boundary (leaving $n-k$ interior knots), the first and last basis components are maximized at the boundaries.
-Alternatively one may want to a-priori enforce vanishing boundary conditions, for example, if they knew for a fact that the function they are modeling has $p(x_\mathrm{bound}) = 0$.
-This can be done by placing $k-1$ knots at the boundaries you wish the spline to vanish at.
-See figure for an example of a cubic M-Spline (k=3) basis with 10 degrees of freedom with $k=3$ knots at each boundary (left) versus enforcing vanishing boundary conditions by having $k-1=2$ knots at each boundary (right).
+Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. Notice 
+that when we introduced knots and in equation \ref{eq:MB_SplineRelation}, you can see there needs to be knots up to $t_{i+k}$ while $i$ 
+indexes the desired degrees of freedom in your basis. This means in practice one must define $n+k$ knots. However, you have control 
+in the boundary conditions by how many of the $n+k$ knots you place at the lower and upper bounds. By placing $k$ knots at each boundary 
+(leaving $n-k$ interior knots), the first and last basis components are maximized at the boundaries. Alternatively one may want to 
+a-priori enforce vanishing boundary conditions, for example, if they knew for a fact that the function they are modeling has 
+$p(x_\mathrm{bound}) = 0$.  This can be done by placing $k-1$ knots at the boundaries you wish the spline to vanish at. See figure for 
+an example of a cubic M-Spline (k=3) basis with 10 degrees of freedom with $k=3$ knots at each boundary (left) versus enforcing vanishing 
+boundary conditions by having $k-1=2$ knots at each boundary (right).
 
@@
 \section{Acknowledgements}\label{sec:acknowledments}
-This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration.
-This work benefited from access to the University of Oregon high performance computer, Talapas.
-This material is based upon work supported in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility fully funded by the National Science Foundation.
+This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
+(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
+This work benefited from access to the University of Oregon high performance computer, Talapas.  This material is based upon work supported 
+in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
+fully funded by the National Science Foundation.
 \software{
@@
 % This appendix goes over in detail the hierarchical bayeisan inference framework
-We use hierarchical Bayesian inference to simultaneously infer the population distributions of the primary masses ($m_1$), mass ratios ($q$) and the redshifts ($z$) of observed BBHs.
-For a set of hyper-parameters, $\Lambda$, and local ($z=0$) merger rate density (units of mergers per co-moving volume per time), $\mathcal{R}_0$, we write the overall number density of BBH mergers in the universe as:
+We use hierarchical Bayesian inference to simultaneously infer the population distributions of the primary masses ($m_1$), mass ratios 
+($q$) and the redshifts ($z$) of observed BBHs. For a set of hyper-parameters, $\Lambda$, and local ($z=0$) merger rate density (units of 
+mergers per co-moving volume per time), $\mathcal{R}_0$, we write the overall number density of BBH mergers in the universe as:
 
@@
 \noindent
-Above, $dV_c$ is the co-moving volume element \citep{hogg_cosmo} and $T_\mathrm{obs}$, the observing time period that produced the catalog with the related factor of $1+z$ converting this detector-frame time to source-frame.
-We assume a LambdaCDM cosmology using the cosmological parameters from \citet{Planck2015}.
-The redshift evolution of the merger rate follows $p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$.
-Integrating equation \ref{number_density} across all masses, and up to some redshift, $z_m$, returns the total number of BBH mergers in the universe out to that redshift.
-Let $\{d_i\}$ represent a set of data from $N_\mathrm{obs}$ observed gravitational waves associated with BBH mergers.
-We model the merger rate as an inhomogenous point process and when imposing a log-uniform prior on the merger rate, we can marginalize over the merger rate to get the posterior distribution of our hyper-parameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.
+Above, $dV_c$ is the co-moving volume element \citep{hogg_cosmo} and $T_\mathrm{obs}$, the observing time period that produced the 
+catalog with the related factor of $1+z$ converting this detector-frame time to source-frame. We assume a LambdaCDM cosmology using 
+the cosmological parameters from \citet{Planck2015}. The redshift evolution of the merger rate follows 
+$p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$. Integrating equation \ref{number_density} across all masses, 
+and up to some redshift, $z_m$, returns the total number of BBH mergers in the universe out to that redshift. Let $\{d_i\}$ represent a 
+set of data from $N_\mathrm{obs}$ observed gravitational waves associated with BBH mergers. We model the merger rate as an inhomogenous 
+point process and when imposing a log-uniform prior on the merger rate, we can marginalize over the merger rate to get the posterior 
+distribution of our hyper-parameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.
 
@@
 \noindent
-where, $\mathcal{L}(d_i|m_1, q, z)$, is the single-event likelihood function from each events original analysis, and $\xi(\Lambda)$ is the detection efficiency given a population distribution described by $\Lambda$.
-The procedure for calculating $\xi(\Lambda)$ is described in more detail below.
-The LVC reports out posterior samples for each observed event, with which we can use importance sampling to estimate the integrals above in equation \ref{posterior}.
-We replace the integrals with ensemble averages over $K_i$ posterior samples associated with each event in the catalog:
+where, $\mathcal{L}(d_i|m_1, q, z)$, is the single-event likelihood function from each events original analysis, and $\xi(\Lambda)$ 
+is the detection efficiency given a population distribution described by $\Lambda$. The procedure for calculating $\xi(\Lambda)$ is 
+described in more detail below. The LVC reports out posterior samples for each observed event, with which we can use importance sampling 
+to estimate the integrals above in equation \ref{posterior}. We replace the integrals with ensemble averages over $K_i$ posterior samples 
+associated with each event in the catalog:
 
@@
 \noindent 
-Here $j$ indexes the $K_i$ posterior samples from each event and $\pi(m_1, q, z)$ is the default prior used by parameter estimations that produced the posterior samples for each event.
-In the analyses of GWTC-2 the default prior used is uniform in detector frame masses and Euclidean volume.
-The corresponding prior evaluated in source frame masses and redshift is $\pi(m_1, q, z) \propto m_1(1+z)^2 D_L^2(z) \frac{dD_L}{dz}$, where $D_L$ is the luminosity distance.
+Here $j$ indexes the $K_i$ posterior samples from each event and $\pi(m_1, q, z)$ is the default prior used by parameter estimations that 
+produced the posterior samples for each event. In the analyses of GWTC-2 the default prior used is uniform in detector frame masses and 
+Euclidean volume. The corresponding prior evaluated in source frame masses and redshift is 
+$\pi(m_1, q, z) \propto m_1(1+z)^2 D_L^2(z) \frac{dD_L}{dz}$, where $D_L$ is the luminosity distance.
 
-To carefully incorporate selection effects to our model we need to quantify the detection efficiency, $\xi(\Lambda)$, of the search pipelines that were used to create GWTC-2, at a given population distribution described by $\Lambda$.
+To carefully incorporate selection effects to our model we need to quantify the detection efficiency, $\xi(\Lambda)$, of the search 
+pipelines that were used to create GWTC-2, at a given population distribution described by $\Lambda$.
 
@@
 
-\noindent The above integral is not tractable since there is no analytic prescription for $P_\mathrm{det}(m_1,q,z)$, the detection probability of an individual event.
-To estimate this integral we use a software injection campaign where GWs from a fixed, broad population of sources are simulated, put into real detector data, and then run through the same search pipelines that were used to produce the catalog we are analyzing \footnote{For O3a we used the injection sets used by \citet{o3a_pop}, which can be found at https://dcc.ligo.org/LIGO-P2000217/public.
-For O1/O2 we used the mock injection sets used by \citet{o1o2_pop} which can be found at https://dcc.ligo.org/LIGO-P2000434/public}.
-With these search results in hand, we use importance sampling to evaluate the integral in equation \ref{det_eff}:
+\noindent The above integral is not tractable since there is no analytic prescription for $P_\mathrm{det}(m_1,q,z)$, the detection 
+probability of an individual event. To estimate this integral we use a software injection campaign where GWs from a fixed, broad 
+population of sources are simulated, put into real detector data, and then run through the same search pipelines that were used to 
+produce the catalog we are analyzing \footnote{For O3a we used the injection sets used by \citet{o3a_pop}, which can be found at 
+https://dcc.ligo.org/LIGO-P2000217/public. For O1/O2 we used the mock injection sets used by \citet{o1o2_pop} which can be found at 
+https://dcc.ligo.org/LIGO-P2000434/public}. With these search results in hand, we use importance sampling to evaluate the integral 
+in equation \ref{det_eff}:
 
@@
 \noindent
-Where the sum indexes only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, and $p_\mathrm{inj}(m_1, q, z)$ is the reference distribution from which the injections were drawn.
-Additionally, we follow the procedure outlined in \citet{Farr_2019} to marginalize the uncertainty in our estimate of $\xi(\Lambda)$ due to a finite number of simulated events.
-We make the assumption that repeated sampling of $\xi(\Lambda)$ will follow a normal distribution with $\xi(\Lambda) \sim \mathcal{N}(\mu(\Lambda), \sigma(\Lambda))$, where the mean, $\mu$, is the estimate from equation \ref{xi}, while the variance, $\sigma^2$, is defined as:
+Where the sum indexes only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, 
+and $p_\mathrm{inj}(m_1, q, z)$ is the reference distribution from which the injections were drawn. Additionally, we follow the procedure 
+outlined in \citet{Farr_2019} to marginalize the uncertainty in our estimate of $\xi(\Lambda)$ due to a finite number of simulated events. 
+We make the assumption that repeated sampling of $\xi(\Lambda)$ will follow a normal distribution with 
+$\xi(\Lambda) \sim \mathcal{N}(\mu(\Lambda), \sigma(\Lambda))$, where the mean, $\mu$, is the estimate from equation \ref{xi}, 
+while the variance, $\sigma^2$, is defined as:
 
@@
 \noindent
-Above we define $N_\mathrm{eff}$ as the effective number of independent draws contributing to the importance sampled estimate, in which we verify to be sufficiently high after re-weighting the injections to a given population (i.e.
-$N_\mathrm{eff} > 4N_\mathrm{obs}$).
-We write the hyper-posterior marginalized over the merger rate and uncertainty in estimation of $\xi(\Lambda)$, neglecting terms of $\mathcal{O}(N_\mathrm{eff}^{-2})$ or greater \citep{Farr_2019}, as:
+Above we define $N_\mathrm{eff}$ as the effective number of independent draws contributing to the importance sampled estimate, 
+in which we verify to be sufficiently high after re-weighting the injections to a given population (i.e. $N_\mathrm{eff} > 4N_\mathrm{obs}$). 
+We write the hyper-posterior marginalized over the merger rate and uncertainty in estimation of $\xi(\Lambda)$, neglecting terms of 
+$\mathcal{O}(N_\mathrm{eff}^{-2})$ or greater \citep{Farr_2019}, as:
 
@@
 \noindent
-We explicitly enumerate each of the models used in this work for $p(m_1|\Lambda)$, $p(q|m_1, \Lambda)$, and $p(z|\Lambda)$ along with their respective hyper-parameters and prior distributions in Table \ref{tab:model_params}.
-To calculate marginal likelihoods and draw samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the \textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}.
+We explicitly enumerate each of the models used in this work for $p(m_1|\Lambda)$, $p(q|m_1, \Lambda)$, and $p(z|\Lambda)$ along with 
+their respective hyper-parameters and prior distributions in Table \ref{tab:model_params}. To calculate marginal likelihoods and draw 
+samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
+\textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with 
+the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}.
 

### 2022-08-08 src/tex/ms.tex
got some data and figures put in now

@@
 
+\begin{figure*}[ht!]
+    \script{spline_basis_plot.py}
+    \begin{centering}
+        \includegraphics[width=\textwidth]{figures/spline_basis_plot.pdf}
+        \caption{Plot showing proper (left) and improper (right) MSpline bases with 20 degrees of freedom and equal weights for each component. The 
+            difference penalty as described in Section II hinges on the fact that basis coeficients that are close produce smoother or flatter 
+            curves. This means one does not want to use an improper basis (i.e. right) with a difference penalty as the resulting curve is not flat 
+            with each component having equal weights.}
+        \label{fig:spline_basis}
+    \end{centering}
+\end{figure*}
+
 Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. Notice 
@@
 \section{Results} \label{sec:results}
+
+\begin{figure*}[ht!]
+    \script{mass_distribution_plot.py}
+    \begin{centering}
+        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
+        \caption{Plot showing the primary mass (left) and mass ratio (right) distributions inferred with the 
+        \textsc{MSpline} model (black) with 40 knots for $m_1$, and 15 knots for $q$. We show the results for the \textsc{PowerlawPeak} (blue) and 
+        \textsc{PowerlawSpline} (orange) models fromthe LVK's GWTC-3 population analyses. Solid lines show the median of the posterior while the shaded
+        bands show the 90\% credible intervals.}
+        \label{fig:mass_distribution}
+    \end{centering}
+\end{figure*}
+
+\begin{figure*}[ht!]
+    \script{component_spin_distribution_plot.py}
+    \begin{centering}
+        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
+        \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
+        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
+        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
+        \label{fig:component_spin_distribution}
+    \end{centering}
+\end{figure*}
+
 \subsection{Mass Spectrum Inference with GWTC-3} \label{sec:GWTC3_inferece}

### 2022-08-08 src/scripts/component_spin_distribution_plot.py

@@ -1,0 +1,129 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+
+def load_mag_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_m1q_indmag_indtilt_spinmag_ppds.h5')
+    return datadict['a1'], datadict['pa1'], datadict['a2'], datadict['pa2']
+
+def load_tilt_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_m1q_indmag_indtilt_spintilt_ppds.h5')
+    return datadict['ct1'], datadict['pct1'], datadict['ct2'], datadict['pct2']
+
+
+def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
+    xs = np.linspace(0, 1, 1000)
+    
+    _data = dd.io.load(paths.data / fi)
+    lines = dict()
+    for key in _data["lines"].keys():
+        lines[key] = _data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    if a1:
+        med = np.median(lines['a_1'], axis=0)
+        low = np.percentile(lines['a_1'], 5, axis=0)
+        high = np.percentile(lines['a_1'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=3, alpha=0.75, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
+        ax.plot(xs, high, color=col, lw=0.2, alpha=0.4)#, label=lab)
+    else:
+        med = np.median(lines['a_2'], axis=0)
+        low = np.percentile(lines['a_2'], 5, axis=0)
+        high = np.percentile(lines['a_2'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=3, alpha=0.75, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
[…]

### 2022-08-08 src/scripts/mass_distribution_plot.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+
+def load_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_m1q_indmag_indtilt_mass_ppds.h5')
+    return datadict['m1'], datadict['pm1'], datadict['q'], datadict['pqs']
+
+
+def load_o3b_paper_run_masspdf(filename):
+    """
+    Generates a plot of the PPD and X% credible region for the mass distribution,
+    where X=limits[1]-limits[0]
+    """
+    mass_1 = np.linspace(2, 100, 1000)
+    mass_ratio = np.linspace(0.1, 1, 500)
+        
+    # load in the traces. 
+    # Each entry in lines is p(m1 | Lambda_i) or p(q | Lambda_i)
+    # where Lambda_i is a single draw from the hyperposterior
+    # The ppd is a 2D object defined in m1 and q
+    with open(filename, 'r') as _data:
+        _data = dd.io.load(filename)
+        marginals = _data["lines"]
+    for ii in range(len(marginals['mass_1'])):
+        marginals['mass_1'][ii] /= np.trapz(marginals['mass_1'][ii], mass_1)
+        marginals['mass_ratio'][ii] /= np.trapz(marginals['mass_ratio'][ii], mass_ratio)
+    return marginals['mass_1'], marginals['mass_ratio'], mass_1, mass_ratio
+
+
+def plot_o3b_res(ax, fi, m1=False, col='tab:blue', lab='PP'):
+    plpeak_mpdfs, plpeak_qpdfs, plpeak_ms, plpeak_qs = load_o3b_paper_run_masspdf(paths.data / fi)
+    if m1:
+        med = np.median(plpeak_mpdfs, axis=0)
+        low = np.percentile(plpeak_mpdfs, 5, axis=0)
+        high = np.percentile(plpeak_mpdfs, 95, axis=0)
+        ax.plot(plpeak_ms, med, color=col, lw=3, alpha=0.75, label=lab)
+        ax.fill_between(plpeak_ms, low, high, color=col, alpha=0.3)
[…]

### 2022-08-08 src/scripts/mpl_utils.py

@@ -1,365 +1,0 @@
-from warnings import warn
-from cycler import cycler
-import numpy as np
-import matplotlib as mpl
-mpl.use("Agg")
-import matplotlib.pyplot as plt
-
-# set random seed for reproducibility
-np.random.seed(0)
-
-# Standardized figure widths in inches.
-# These are based on the output of `\the\textwidth` and `\the\columnwidth` in
-# the LaTeX document.  If we change our LaTeX template, we should double-check
-# that they do not change.
-# NOTE: If LaTeX displays a number in `pt` units, divide by 72 to get inches.
-widths = {
-    'textwidth' : 7.0,
-    'columnwidth' : 3.0,
-}
-
-
-def limit_ax_oom(
-        ax, n_oom: int, x_or_y: str,
-        measure_from: str="upper", base: float=10.0,
-    ) -> None:
-    r"""
-    Takes a :class:`matplotlib.axes._subplots.AxesSubplot` object, and limits
-    its limits to ``n_oom`` orders of magnitude (in the logarithmic base set by
-    the ``base`` parameter, ``10.0`` by default) from either the upper or lower
-    data limit (set with ``measure_from`` argument, "upper" by default).  Either
-    operates on x- or y-axis, set by passing "x" or "y" for ``x_or_y`` argument.
-
-    If the data limits are already within the specified orders of magnitude, no
-    changes will be made.
-    """
-    import math
-    import numpy
-
-    # Validate inputs.
-    if x_or_y not in {"x", "y"}:
-        raise KeyError("Invalid choice for 'x_or_y', must be either 'x' or 'y'")
-    if measure_from not in {"upper", "lower"}:
-        raise KeyError(
-            "Invalid choice for 'measure_from', must be either 'upper' or "
-            "'lower'"
-        )
-
-    # Get data limits along specified axis.
-    if x_or_y == "x":
-        data_lo, data_hi = ax.dataLim.x0, ax.dataLim.x1
-    else:
-        data_lo, data_hi = ax.dataLim.y0, ax.dataLim.y1
-
-    # Convert data limits to log-scale, rounding to the next integer.
[…]

### 2022-08-08 src/scripts/spline_basis_plot.py

@@ -1,0 +1,112 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+from utils import MSpline
+
+ndof = 20
+k = 3
+xmin = 0
+xmax = 1
+xlab = 'x'
+
+cmap = 'magma'
+figx, figy = 16, 5
+fig, axs = plt.subplots(nrows=1, ncols=2, sharey='all', figsize=(figx,figy))
+
+nadd = k - 1
+interior_knots = np.linspace(xmin, xmax, ndof+k-2*nadd)
+#knots = np.concatenate([np.array([xmin]*nadd), interior_knots, np.array([xmax]*nadd)])
+dx = interior_knots[1]-interior_knots[0]
+knots = np.concatenate([xmin-np.arange(1,k)[::-1]*dx, interior_knots, xmax+dx*np.arange(1,k)])
+
+coef = np.array([1./ndof]*ndof)
+grid = np.linspace(xmin, xmax, 2500)
+basis = MSpline(ndof, k=k, knots=knots)(grid)
+
+color_cycle = iter(plt.cm.get_cmap(cmap)(np.linspace(0.3, .9,ndof)[::-1]))
+total_color = iter(plt.cm.get_cmap(cmap)([0.05]))
+
+
+total = 0
+for ii in range(ndof):
+    basis[ii,0] = 2*basis[ii,1]-basis[ii,2]
+    basis[ii,-1] = 2*basis[ii,-2]-basis[ii,-3]
+    norm = 1.0 / (sum([np.trapz(basis[i, :], grid) * coef[i] for i in range(ndof)]))
+    axs[0].plot(grid, norm * coef[ii] * basis[ii,:], color=next(color_cycle), lw=3)#, label=f'c_{ii}')# = {coef[ii]:0.2f}')
+    total += norm * coef[ii] * basis[ii,:]
+axs[0].plot(grid, total, color=next(total_color), lw=4, label=r'$\sum_{i}^{N_\mathrm{dof}} c_{i} M_{i,k}(x)$')
+maxy = max(total)
+
+dx = knots[k+3] - knots[k+2]
+dy = maxy / (ndof)
+ys = [dy]*len(knots)
+xs = knots.copy()
+for i, x in enumerate(knots):
+    if np.abs(knots[i-1]-x) < 1e-6:
+        ys[i] = ys[i-1] + dy
+    if np.abs(xmin-x) < 1e-6:
[…]

### 2022-08-08 src/scripts/utils.py

@@ -1,0 +1,58 @@
+import pickle
+import paths
+import numpy as np
+
+
+def load_posterior(fi):
+    with open(paths.data / fi, 'rb') as f:
+        posterior_dict = pickle.load(f)
+    return posterior_dict
+
+
+class MSpline(object):
+    def __init__(
+        self, n_df, knots=None, interior_knots=None, xrange=(0, 1), k=4, proper=True
+    ):
+        self.order = k
+        self.N = n_df
+        self.xrange = xrange
+        if knots is None:
+            if interior_knots is None:
+                interior_knots = np.linspace(*xrange, n_df - k + 2)
+            if proper:
+                dx = interior_knots[1] - interior_knots[0]
+                knots = np.append(
+                    np.append(
+                        np.array([xrange[0] - 2 * dx, xrange[0] - dx]), interior_knots
+                    ),
+                    np.array([xrange[1] + dx, xrange[1] + 2 * dx]),
+                )
+            else:
+                knots = np.append(
+                    np.append(np.array([xrange[0]] * (k - 1)), interior_knots),
+                    np.array([xrange[1]] * (k - 1)),
+                )
+        self.knots = knots
+        self.interior_knots = knots
+        assert len(self.knots) == self.N + self.order
+
+    def _basis(self, xs, i, k):
+        if self.knots[i + k] - self.knots[i] < 1e-6:
+            return np.zeros_like(xs)
+        elif k == 1:
+            v = np.zeros_like(xs)
+            v[(xs >= self.knots[i]) & (xs < self.knots[i + 1])] = 1 / (
+                self.knots[i + 1] - self.knots[i]
+            )
+            return v
+        else:
+            v = (xs - self.knots[i]) * self._basis(xs, i, k - 1) + (
+                self.knots[i + k] - xs
+            ) * self._basis(xs, i + 1, k - 1)
+            return (v * k) / ((k - 1) * (self.knots[i + k] - self.knots[i]))
+
+    def basis(self, xs):
+        return [self._basis(xs, i, k=self.order) for i in range(self.N)]
+
+    def __call__(self, xs):
+        return np.concatenate(self.basis(xs)).reshape(self.N, *xs.shape)

### 2022-08-30 src/tex/ms.tex
setup zenodo integration

@@
 
-\author{Lexi Vives}
-\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-
 \author{Ben Farr}
@@
 Now that gravitational wave observations of compact binary coalescence is a regular occurrence, producing catalogs of nearly 
-100 such detections, we now have access to a complete understanding of the population of compact binaries. In the coming fourth 
-observing run of the LIGO-Virgo-KAGRA collaboration, the catalog size is expected to increase by a factor of 5. The extensive 
-physics governing the formation and evolution of compact objects that end up merging is imprinted on the properties of the population 
-of CBCs, allowing us to learn about these not well understood ideas through looking at the distribution of observed GWs. In particular 
-the mass distribution of binary black holes has been shown to be very useful in measuring cosmological parameters, constraining modified 
-gravitational wave propagation, constraining a running Planck mass, looking of evidence of ultralight bosons through superradiance, 
-putting constraints on uncertain nuclear reaction rates important for stellar evolution, and even looking for primordial black holes. 
-Through a better understanding of the mass, spin, and redshift distribution of compact binaries we can extend this be a useful tool 
-in all the different physical applications mentioned above. In this paper we highlight how the use of basis-splines can be a useful 
-model-agnostic modeling approach to the astrophysical distributions of compact binaries. We show that with a particular choice of basis, 
-we can efficiently model the spin and/or mass distribution of compact binaries in GWTC-3 with spline regression in hierarchical 
-Bayesian inference. We show our results are similar to those produced with the more simpler and motivated parametric models, 
-while being capable of finding more subtle features should they appear in future catalogs. This method can be extended to higher-dimensional 
-basis-splines to model correlations between different distributions which will be necessary to confidently disentangle differently 
-competing formation channels should they exist.
+100 such detections, we are beginning to have access to a more complete understanding of the population of compact binaries. 
+In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration, the catalog size is expected to increase by up to a factor of 5. 
+Looking at population properties of compact objects lets us probe the complex physics common to all of our observations that governs the 
+formation and evolution of merging compact objects. The history of these dense objects is imprinted on the properties of the population 
+of CBCs, allowing us to learn about these not well understood ideas through careful evaluation of the enture distribution of observed GWs. 
+The mass distribution of binary black holes has been used to measure cosmological parameters, constrain modified gravitational wave propagation, 
+constrain a non-constant Planck mass, look for evidence of ultralight bosons through superradiance, put constraints on the uncertain nuclear reaction 
+rates important for stellar evolution, look for primordial black holes, to constrain the neutron star equation of state, 
+and to understand the fromation channels/environments of compact binary coalescences (CBCs). Through a better understanding of the mass, spin, 
+and redshift distribution of compact binaries that will come with the increased catalog size, one can probe these dufferent physical phenoma with 
+greater fidelity.
+
+With the latest LIGO-Virgo-KAGRA (LVK) catalog of CBCs (GWTC-3), new understanding of the population has come into light. One of the main findings was that 
+the mass distribution exhibits substructure with peaks rather than being perfectly described by a smooth power law distribution. The evidence for this was 
+found with mutliple different flexible or non-parametric models that aim to be data-oriented with little bias on the function form. While these models are 
+useful for looking for unexpected features in the data, or finding where our simpler models fail, they can be harder to interpret and are not based on specific
+astrophysical motivation. These types of models will become more important as the size of our catalogs increase and we enter a data-dominated regime rather than
+prior/model dominated.
+
+The spin distribution of binary black holes (BBHs) has also been of controversial interest in the literature recently, with different parameteric approaches finding 
+rather different conclusions on the distribution of spins of BBHs which has significant impact on the inferences about relative contribution of dynamically formed
+binaries versus ones formed in the field. This is another use case for flexible data-driven models to alleivate the discrepencies among parametric approaches. 
+In particular there has been little work on flexible model development for the spin distribution of BBHs, which makes sense given the relatively smaller catalog 
+sizes and the large uncertainty in individual black hole spin measurements with GWs.
+
+In this paper we highlight how the use of basis-splines can be a useful model-agnostic modeling approach to the astrophysical distributions of compact 
+binaries. We show that with a particular choice of basis, one can efficiently model the spin, mass and redshift distributions of compact binaries in GWTC-3 with
+hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and illustrate how our results are similar
+to those produced with the more simpler and astrophysically motivated parametric models. This data-drien approach will be capable of finding more subtle features, that 
+may not be expected, should they appear in future catalogs. Additionally this method can be extended to higher-dimensional basis-splines in order to model 
+joint population disributions over multiple surce parameters, which will be important to confidently disentangle different competing formation channels 
+should they exist. In Section II we go over the background of basis splines and model construction. In Section III we present results using our basis spline model 
+on the mass and spin distributions of BBHs in GWTC-3, followed by discussing the results and astrophysical implications in Section IV and concluding in Section V.
 
@@
 }
-\bibliography{references}{}
+\bibliography{bib}{}
 \bibliographystyle{aasjournal}

### 2022-08-30 src/scripts/component_spin_distribution_plot.py

@@ -5,7 +5,6 @@ import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
 
-
 def load_mag_ppd():
     datadict = dd.io.load(paths.data / 'mspline_m1q_indmag_indtilt_spinmag_ppds.h5')
     return datadict['a1'], datadict['pa1'], datadict['a2'], datadict['pa2']

### 2022-08-30 src/scripts/mass_distribution_plot.py

@@ -5,10 +5,9 @@ import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
 
-
 def load_ppd():
     datadict = dd.io.load(paths.data / 'mspline_m1q_indmag_indtilt_mass_ppds.h5')
-    return datadict['m1'], datadict['pm1'], datadict['q'], datadict['pqs']
+    return datadict['m1'], datadict['pm1'], datadict['q'], datadict['pq']
 
 
 def load_o3b_paper_run_masspdf(filename):

### 2022-09-14 src/tex/appendicies.tex
update the git repo

\appendix
\section{Hierarchical Bayesian Inference} \label{sec:hierarchical_inference}

% This appendix goes over in detail the hierarchical bayeisan inference framework
We use hierarchical Bayesian inference to infer the population properties of CBCs. We want to infer the number density of merging CBCs 
in the universe and how this can change with their masses, spins, etc. Often times it is useful to formulate the question in terms of the 
merger rates which is the number of mergers per $Gpc^{3}$ co-moving volume per year. For a set of hyper-parameters, $\Lambda$, $\lambda$, and local ($z=0$) 
merger rate density, $\mathcal{R}_0$, we write the overall number density of BBH mergers in the universe as:

\begin{equation} \label{number_density}
     \frac{dN(\theta, z | \mathcal{R}_0, \Lambda, \lambda)}{d\theta dz} = \frac{dV_c}{dz}\bigg(\frac{T_\mathrm{obs}}{1+z}\bigg) \frac{d\mathcal{R}(\theta, z | \mathcal{R}_0, \Lambda, \lambda)}{d\theta} = \mathcal{R}_0 p(\theta | \Lambda) p(z | \lambda)
\end{equation}

\noindent
Where up above, we denote the co-moving volume element as $dV_c$ \citep{hogg_cosmo}, and $T_\mathrm{obs}$ as the observing time period that produced the 
catalog with the related factor of $1+z$ converting this detector-frame time to source-frame. We assume a LambdaCDM cosmology using 
the cosmological parameters from \citet{Planck2015}. We model the merger rate evolving with redshift following a power law distribution: 
$p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$. When integrating equation \ref{number_density} across all $\theta$
and out to some maximum redshift, $z_\mathrm{max}$, we get the total number of CBCs in the universe out to that redshift. We follow previous notations, \
letting $\{d_i\}$ represent the set of data from $N_\mathrm{obs}$ CBCs observed with gravitational waves. The merger rate is then described as an inhomogenous 
Poisson process and after imposing the usual log-uniform prior on the merger rate, we marginalize out merger rate and arrive at the posterior
distribution of our hyper-parameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.

\begin{equation}
    p\left(\Lambda, \lambda | \{d_i\}\right) \frac{p(\Lambda)p(\lambda)}{\xi(\Lambda,\lambda)^{N_\mathrm{obs}}} \prod_{i=1}^{N_\mathrm{obs}} \bigg[ \frac{1}{K_i} \sum_{j=1}^{K_i} \frac{p(\theta^{i,j}|\Lambda)p(z^{i,j}|\lambda)}{\pi(\theta, z^{i,j})} \bigg]
\end{equation}

\noindent
where, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples. Above, $j$
indexes the $K_i$ posterior samples from each event and $\pi(\theta, z)$ is the default prior used by parameter estimations that 
produced the posterior samples for each event. In the analyses of GWTC-2 the default prior used is uniform in detector frame masses, 
component spins and Euclidean volume. The corresponding prior evaluated in source frame primary mass, mass ratio, component spins 
and redshift is:

\begin{equation}
    \pi(m_1, q, a_1, a_2, \cos{\theta_1}, \cos{\theta_2}, z) \propto \frac{1}{4} m_1 (1+z)^2 D_L^2(z) \frac{dD_L}{dz}
\end{equation}

\noindent where $D_L$ is the luminosity distance. To carefully incorporate selection effects to our model we need to quantify the detection efficiency,
$\xi(\Lambda, \lambda)$, of the search pipelines that were used to create GWTC-3, at a given population distribution described by $\Lambda$ and $\lambda$.

\begin{equation}
     \xi(\Lambda, \lambda) = \int d\theta dz P_\mathrm{det}(\theta, z)p(\theta | \Lambda) p(z | \lambda)
\end{equation}

\noindent
To estimate this integral we use a software injection campaign where gravitational waveforms from a large population of simulated sources. 
These simulated waevforms are put into real detector data, and then this data is evaluated with the same search pipelines that were used to 
produce the catalog we are analyzing. With these search results in hand, we use importance sampling and evaluate the integral 
with the monte carlo sum estimate $\mu$, and its corresponding variance and effective number of samples:

\begin{equation} \label{xi}
     \xi(\Lambda, \lambda) \approx \mu(\Lambda, \lambda) \frac{1}{N_\mathrm{inj}} \sum_{i=1}^{N_\mathrm{found}} \frac{p(\theta^i | \Lambda) p(z^i | \lambda)}{p_\mathrm{inj}(\theta, z^i)}
\end{equation}

\begin{equation}
    \sigma^2(\Lambda, \lambda) \equiv \frac{\mu^2(\Lambda, \lambda)}{N_\mathrm{eff}} \simeq \frac{1}{N^2_\mathrm{inj}} \sum_{i=1}^{N_\mathrm{found}} \bigg[\frac{p(\theta | \Lambda) p(z | \lambda)}{p_\mathrm{inj}(\theta, z)}\bigg]^2 - \frac{\mu^2(\Lambda, \lambda)}{N_\mathrm{inj}}
\end{equation}

\noindent
Where the sums indexes only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, 
and $p_\mathrm{inj}(\theta, z)$ is the reference distribution from which the injections were drawn. Additionally, we follow the procedure 
outlined in \citet{Farr_2019} to marginalize the uncertainty in our estimate of $\xi(\Lambda, \lambda)$, in which we verify that $N_\mathrm{eff}$ is 
sufficiently high after re-weighting the injections to a given population (i.e. $N_\mathrm{eff} > 4N_\mathrm{obs}$). 
The total hyper-posterior marginalized over the merger rate and the uncertainty in the monte carlo integral calculating $\xi(\Lambda, \lambda)$ \citep{Farr_2019}, as:

\begin{equation}\label{importance-posterior}
    \log p\left(\Lambda, \lambda | \{d_i\}\right) \propto \sum_{i=1}^{N_\mathrm{obs}} \log \bigg[ \frac{1}{K_i} \sum_{j=1}^{K_i} \frac{p(\theta^{i,j}|\Lambda)p(z^{i,j}|\lambda)}{\pi(\theta^{i,j}, z^{i,j})} \bigg] -  \\
    N_\mathrm{obs} \log \mu(\Lambda, \lambda) + \frac{3N_\mathrm{obs} + N_\mathrm{obs}^2}{2N_\mathrm{eff}} + \mathcal{O}(N_\mathrm{eff}^{-2}).
\end{equation}

We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
their respective hyper-parameters and prior distributions in the next section. To calculate marginal likelihoods and draw 
samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
\textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with 
the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}. We also make use of the hamiltonian monte carlo algorithms in 
\textsc{numpyro} and use \textsc{jax} to calculate our likelihoods \bruce{FIND citations for these}.

\section{Models and Hyper-Parameters} \label{sec:hypparams}

\section{Validation Studies} \label{sec:validation}

### 2022-09-14 src/tex/intro.tex
update the git repo

--- 2022-08-30 src/tex/ms.tex
@@
-\documentclass[twocolumn, linenumber]{aastex63}
-
-\newcommand{\msun}{\ensuremath{{\rm M}_\odot}}
-\newcommand{\result}[1]{\textcolor{red}{#1}}
-\newcommand{\bruce}[1]{\textcolor{blue}{BE: #1}}
-\newcommand{\NewChange}[1]{\textcolor{green}{#1}}
-
-\graphicspath{{./}{figures/}}
-
-\usepackage{showyourwork}
-\usepackage[perpage]{footmisc}
-\usepackage{colortbl}
-\usepackage{lineno}
-\usepackage{amsmath}
-\usepackage{appendix}
-\definecolor{Gray}{gray}{0.9}
-\linenumbers
-
-\begin{document}
-
-\title{Covering Your Basis: Model-Agnostic Inference of LIGO-Virgos Binary Black Hole Spin Distribution}
-
-\author{Bruce Edelman}
-\email{bedelman@uoregon.edu}
-\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-
-\author{Ben Farr}
-\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-
-\begin{abstract}
-We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical mass distribution of 
-binary black holes using GWTC-3.
-\end{abstract}
-
 \section{Introduction} \label{sec:intro}
 
-Now that gravitational wave observations of compact binary coalescence is a regular occurrence, producing catalogs of nearly 
-100 such detections, we are beginning to have access to a more complete understanding of the population of compact binaries. 
-In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration, the catalog size is expected to increase by up to a factor of 5. 
+Observations of gravitational waves from compact binary coalescences (CBCs) is becoming a regular occurrence, 
+recently producing catalogs of 90 such detections \bruce{cite GWTCs}. This growing catalog size is beginning to enable access to a more complete 
+understanding of the population properties CBCs, which encodes the history of the formation and evolution of these extreme compact objects. 
+In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration \bruce{cite detectors}, the catalog size is expected to increase by up to a factor of 5. 
 Looking at population properties of compact objects lets us probe the complex physics common to all of our observations that governs the 
@@
 on the mass and spin distributions of BBHs in GWTC-3, followed by discussing the results and astrophysical implications in Section IV and concluding in Section V.
-
-\section{Methods} \label{sec:methods}
-\subsection{Constructing A Basis} \label{sec:basis_splines}
-
-A common non-parametric method in statistical applications is the use of B-Splines or basis splines. A spline function of order $k$, 
-is a piece-wise polynomial of order $k-1$ polynomials stitched together from defined ``knot'' locations across the domain. 
-They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
-B-Splines of order $k$ are a set of order $k-1$ polynomials that form a complete basis for any spline function of order $k$. 
-Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
-every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines for a given knot vector using the Cox-de Boor 
-recursion formula -- for knots $t_0$, $t_1$,...,$t_{i+k}$ the basis components are given by:
-\begin{equation}
-    B_{i,1}(x | \mathbf{t}) = 
-    \begin{cases}
-        1, & \text{if } t_i \leq x < t_{i+1} \\
-        0, & \text{otherwise}
-    \end{cases}
-\end{equation}
-\begin{equation}
-    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x)B_{i,k}(x) + \big[1-\omega_{i+1,k}(x)\big]B_{i+1,k}(x)
-\end{equation}
-\noindent Where $\omega_{i,k}$ above is defined as:
-\begin{equation}
-    \omega_{i,k}(x | \mathbf{t}) =
-    \begin{cases}
-        \frac{x-t_i}{t_{i+k}-t_i}, & t_{i+k} \neq t_i \\
-        0, & \text{otherwise}
-    \end{cases}
-\end{equation}
-
-A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function. Namely, 
-$M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. The M-Spline basis only differs 
-from B-Splines by a normalization factor, namely:
-\begin{equation}\label{eq:MB_SplineRelation}
-    M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
-\end{equation}
-\noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper.
-
-\begin{figure*}[ht!]
-    \script{spline_basis_plot.py}
-    \begin{centering}
-        \includegraphics[width=\textwidth]{figures/spline_basis_plot.pdf}
-        \caption{Plot showing proper (left) and improper (right) MSpline bases with 20 degrees of freedom and equal weights for each component. The 
-            difference penalty as described in Section II hinges on the fact that basis coeficients that are close produce smoother or flatter 
-            curves. This means one does not want to use an improper basis (i.e. right) with a difference penalty as the resulting curve is not flat 
-            with each component having equal weights.}
-        \label{fig:spline_basis}
-    \end{centering}
-\end{figure*}
-
-Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. Notice 
-that when we introduced knots and in equation \ref{eq:MB_SplineRelation}, you can see there needs to be knots up to $t_{i+k}$ while $i$ 
-indexes the desired degrees of freedom in your basis. This means in practice one must define $n+k$ knots. However, you have control 
-in the boundary conditions by how many of the $n+k$ knots you place at the lower and upper bounds. By placing $k$ knots at each boundary 
-(leaving $n-k$ interior knots), the first and last basis components are maximized at the boundaries. Alternatively one may want to 
-a-priori enforce vanishing boundary conditions, for example, if they knew for a fact that the function they are modeling has 
-$p(x_\mathrm{bound}) = 0$.  This can be done by placing $k-1$ knots at the boundaries you wish the spline to vanish at. See figure for 
-an example of a cubic M-Spline (k=3) basis with 10 degrees of freedom with $k=3$ knots at each boundary (left) versus enforcing vanishing 
-boundary conditions by having $k-1=2$ knots at each boundary (right).
-
-\subsection{Parameterized Perturbations} \label{sec:perturbation_model}
-\subsection{Generic Mass Model} \label{sec:nonparametric_model}
-\section{Results} \label{sec:results}
-
-\begin{figure*}[ht!]
-    \script{mass_distribution_plot.py}
-    \begin{centering}
-        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
-        \caption{Plot showing the primary mass (left) and mass ratio (right) distributions inferred with the 
-        \textsc{MSpline} model (black) with 40 knots for $m_1$, and 15 knots for $q$. We show the results for the \textsc{PowerlawPeak} (blue) and 
-        \textsc{PowerlawSpline} (orange) models fromthe LVK's GWTC-3 population analyses. Solid lines show the median of the posterior while the shaded
-        bands show the 90\% credible intervals.}
-        \label{fig:mass_distribution}
-    \end{centering}
-\end{figure*}
-
-\begin{figure*}[ht!]
-    \script{component_spin_distribution_plot.py}
-    \begin{centering}
-        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
-        \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
-        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
-        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
-        \label{fig:component_spin_distribution}
-    \end{centering}
-\end{figure*}
-
-\subsection{Mass Spectrum Inference with GWTC-3} \label{sec:GWTC3_inferece}
-\section{Conclusions}\label{sec:conclusion}
-\section{Acknowledgements}\label{sec:acknowledments}
-This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
-(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
-This work benefited from access to the University of Oregon high performance computer, Talapas.  This material is based upon work supported 
-in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
-fully funded by the National Science Foundation.
-\software{
-\textsc{Astropy}~\citep{2018AJ....156..123A},
-\textsc{NumPy}~\citep{harris2020array},
-\textsc{Matplotlib}~\citep{Hunter:2007},
-\textsc{bilby}~\citep{Ashton_2019},
-\textsc{GWPopulation}~\citep{Talbot_2019}
-}
-\bibliography{bib}{}
-\bibliographystyle{aasjournal}
-
-\appendix
-\section{Hierarchical Bayesian Inference} \label{sec:hierarchical_inference}
-
-% This appendix goes over in detail the hierarchical bayeisan inference framework
-We use hierarchical Bayesian inference to simultaneously infer the population distributions of the primary masses ($m_1$), mass ratios 
-($q$) and the redshifts ($z$) of observed BBHs. For a set of hyper-parameters, $\Lambda$, and local ($z=0$) merger rate density (units of 
-mergers per co-moving volume per time), $\mathcal{R}_0$, we write the overall number density of BBH mergers in the universe as:
-
-\begin{equation} \label{number_density}
-     \frac{dN(m_1, q, z | \mathcal{R}_0, \Lambda)}{dm_1dqdz} = \frac{dV_c}{dz}\bigg(\frac{T_\mathrm{obs}}{1+z}\bigg) \frac{d\mathcal{R}(m_1, q, z | \mathcal{R}_0, \Lambda)}{dm_1dq} = \mathcal{R}_0 p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)
-\end{equation}
-
-\noindent
-Above, $dV_c$ is the co-moving volume element \citep{hogg_cosmo} and $T_\mathrm{obs}$, the observing time period that produced the 
-catalog with the related factor of $1+z$ converting this detector-frame time to source-frame. We assume a LambdaCDM cosmology using 
-the cosmological parameters from \citet{Planck2015}. The redshift evolution of the merger rate follows 
-$p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$. Integrating equation \ref{number_density} across all masses, 
-and up to some redshift, $z_m$, returns the total number of BBH mergers in the universe out to that redshift. Let $\{d_i\}$ represent a 
-set of data from $N_\mathrm{obs}$ observed gravitational waves associated with BBH mergers. We model the merger rate as an inhomogenous 
-point process and when imposing a log-uniform prior on the merger rate, we can marginalize over the merger rate to get the posterior 
-distribution of our hyper-parameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.
-
-\begin{equation} \label{posterior}
-    p\left(\Lambda | \{d_i\} \right) \propto \frac{p(\Lambda)}{\xi(\Lambda)^{N_\mathrm{obs}}} \prod_{i=1}^{N_\mathrm{obs}} \Bigg[ \int \mathcal{L}\left(d_i | m_1^i, q^i, z^i \right) p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda) dm_1 dq dz \Bigg],
-\end{equation}
-
-\noindent
-where, $\mathcal{L}(d_i|m_1, q, z)$, is the single-event likelihood function from each events original analysis, and $\xi(\Lambda)$ 
-is the detection efficiency given a population distribution described by $\Lambda$. The procedure for calculating $\xi(\Lambda)$ is 
-described in more detail below. The LVC reports out posterior samples for each observed event, with which we can use importance sampling 
-to estimate the integrals above in equation \ref{posterior}. We replace the integrals with ensemble averages over $K_i$ posterior samples 
-associated with each event in the catalog:
-
-\begin{equation}
- p\left(\Lambda | \{d_i\}\right) \propto p(\Lambda) \prod_{i=1}^{N_\mathrm{obs}} \bigg[ \frac{1}{K_i} \sum_{j=1}^{K_i} \frac{p(m_1^{i,j}|\Lambda)p(q^{i,j}|\Lambda)p(z^{i,j}|\Lambda)}{\pi(m_1^{i,j}, q^{i,j}, z^{i,j})} \bigg]
-\end{equation}
-
-\noindent 
-Here $j$ indexes the $K_i$ posterior samples from each event and $\pi(m_1, q, z)$ is the default prior used by parameter estimations that 
-produced the posterior samples for each event. In the analyses of GWTC-2 the default prior used is uniform in detector frame masses and 
-Euclidean volume. The corresponding prior evaluated in source frame masses and redshift is 
-$\pi(m_1, q, z) \propto m_1(1+z)^2 D_L^2(z) \frac{dD_L}{dz}$, where $D_L$ is the luminosity distance.
-
-To carefully incorporate selection effects to our model we need to quantify the detection efficiency, $\xi(\Lambda)$, of the search 
-pipelines that were used to create GWTC-2, at a given population distribution described by $\Lambda$.
-
-\begin{equation} \label{det_eff}
-     \xi(\Lambda) = \int dm_1 dq dz P_\mathrm{det}(m_1, q, z)p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)
-\end{equation}
-
-\noindent The above integral is not tractable since there is no analytic prescription for $P_\mathrm{det}(m_1,q,z)$, the detection 
-probability of an individual event. To estimate this integral we use a software injection campaign where GWs from a fixed, broad 
-population of sources are simulated, put into real detector data, and then run through the same search pipelines that were used to 
-produce the catalog we are analyzing \footnote{For O3a we used the injection sets used by \citet{o3a_pop}, which can be found at 
-https://dcc.ligo.org/LIGO-P2000217/public. For O1/O2 we used the mock injection sets used by \citet{o1o2_pop} which can be found at 
-https://dcc.ligo.org/LIGO-P2000434/public}. With these search results in hand, we use importance sampling to evaluate the integral 
-in equation \ref{det_eff}:
-
-\begin{equation} \label{xi}
-     \xi(\Lambda) = \frac{1}{N_\mathrm{inj}} \sum_{i=1}^{N_\mathrm{found}} \frac{p(m_1^i | \Lambda) p(q^i | m_1, \Lambda) p(z^i | \Lambda)}{p_\mathrm{inj}(m_1^i, q^i, z^i)}
-\end{equation}
-
-\noindent
-Where the sum indexes only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, 
-and $p_\mathrm{inj}(m_1, q, z)$ is the reference distribution from which the injections were drawn. Additionally, we follow the procedure 
-outlined in \citet{Farr_2019} to marginalize the uncertainty in our estimate of $\xi(\Lambda)$ due to a finite number of simulated events. 
-We make the assumption that repeated sampling of $\xi(\Lambda)$ will follow a normal distribution with 
-$\xi(\Lambda) \sim \mathcal{N}(\mu(\Lambda), \sigma(\Lambda))$, where the mean, $\mu$, is the estimate from equation \ref{xi}, 
-while the variance, $\sigma^2$, is defined as:
-
-\begin{equation}
-    \sigma^2(\Lambda) \equiv \frac{\mu^2(\Lambda)}{N_\mathrm{eff}} \simeq \frac{1}{N^2_\mathrm{inj}} \sum_{i=1}^{N_\mathrm{found}} \bigg[\frac{p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)}{p_\mathrm{inj}(m_1, q, z)}\bigg]^2 - \frac{\mu^2(\Lambda)}{N_\mathrm{inj}}
-\end{equation}
-
-\noindent
-Above we define $N_\mathrm{eff}$ as the effective number of independent draws contributing to the importance sampled estimate, 
-in which we verify to be sufficiently high after re-weighting the injections to a given population (i.e. $N_\mathrm{eff} > 4N_\mathrm{obs}$). 
-We write the hyper-posterior marginalized over the merger rate and uncertainty in estimation of $\xi(\Lambda)$, neglecting terms of 
-$\mathcal{O}(N_\mathrm{eff}^{-2})$ or greater \citep{Farr_2019}, as:
-
-\begin{equation}\label{importance-posterior}
-    \log p\left(\Lambda | \{d_i\}\right) \propto \sum_{i=1}^{N_\mathrm{obs}} \log \bigg[ \frac{1}{K_i} \sum_{j=1}^{K_i} \frac{p(m_1^{i,j}|\Lambda)p(q^{i,j}|\Lambda)p(z^{i,j}|\Lambda)}{\pi(m_1^{i,j}, q^{i,j}, z^{i,j})} \bigg] -  \\
-    N_\mathrm{obs} \log \mu + \frac{3N_\mathrm{obs} + N_\mathrm{obs}^2}{2N_\mathrm{eff}} + \mathcal{O}(N_\mathrm{eff}^{-2}).
-\end{equation}
-
-\noindent
-We explicitly enumerate each of the models used in this work for $p(m_1|\Lambda)$, $p(q|m_1, \Lambda)$, and $p(z|\Lambda)$ along with 
-their respective hyper-parameters and prior distributions in Table \ref{tab:model_params}. To calculate marginal likelihoods and draw 
-samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
-\textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with 
-the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}.
-
-\section{Validation Studies} \label{sec:validation}
-
-\end{document}

### 2022-09-14 src/tex/methods.tex
update the git repo

\section{Methods} \label{sec:methods}

\subsection{Constructing A Basis} \label{sec:basis_splines}

A common non-parametric method in statistical applications is the use of B-Splines or basis splines. A spline function of order $k$, 
is a piece-wise polynomial of order $k-1$ polynomials stitched together from defined ``knot'' locations across the domain. 
They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
B-Splines of order $k$ are a set of order $k-1$ polynomials that form a complete basis for any spline function of order $k$. 
Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines for a given knot vector using the Cox-de Boor 
recursion formula -- for knots $t_0$, $t_1$,...,$t_{i+k}$ the basis components are given by:
\begin{equation}
    B_{i,1}(x | \mathbf{t}) = 
    \begin{cases}
        1, & \text{if } t_i \leq x < t_{i+1} \\
        0, & \text{otherwise}
    \end{cases}
\end{equation}
\begin{equation}
    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x)B_{i,k}(x) + \big[1-\omega_{i+1,k}(x)\big]B_{i+1,k}(x)
\end{equation}
\noindent Where $\omega_{i,k}$ above is defined as:
\begin{equation}
    \omega_{i,k}(x | \mathbf{t}) =
    \begin{cases}
        \frac{x-t_i}{t_{i+k}-t_i}, & t_{i+k} \neq t_i \\
        0, & \text{otherwise}
    \end{cases}
\end{equation}

A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function. Namely, 
$M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. The M-Spline basis only differs 
from B-Splines by a normalization factor, namely:
\begin{equation}\label{eq:MB_SplineRelation}
    M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
\end{equation}
\noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper.

\subsection{Penalized Splines}
A common issue when using splines as a flexible fitting method is their sensitivity to the chosen number of knots, and their locations. 
Adding more knots knots will increase the natural a-priori variance in the spline function, while the space between knots can limit the 
resolution of features in the data the spline is capable of fitting. To ensure your spline based model is flexible enough to find sharp
features in data, one would want to add as many knots as densely as possible, but this comes with the sometimes un-wanted affect of the 
larger variance as mentioned above. To overcome this we resort to the frequentist penalized spline (PSpline) in which one applies a penalty
to the likelihood based on the difference of adjacent knot coeficients. Since the resulting linear combination of spline basis components is 
smoother, or flatter, when the basis coeficients are near each other, this has a natural smoothing affect to the spline function. Since we are 
using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog, by applying 
the stochastic differnece prior described in \bruce{CITE THIS PAPER}, which is equivalent to a Gaussian random walk prior where each succeeding 
coeficient is normally distributed about its neighboring coeficients. Thus our smoothing prior for our bayesian framework is:

\begin{equation}
    \tau_\lambda \sim \mathcal{G}(a, b)
\end{equation}
\begin{equation}
    p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}' \bm{D} \bm{c}}
\end{equation}

The smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a 
very large number of knots such that your domain is densly populated with basis coeficients, the smoothing prior will smooth out regions where 
the data can be described smoothly, and relax when the data has features for the spline function to fit. In practice one would want to add knots 
of order the number of observations or more. One downside of this prior specification is a moderate dependence on choice of the b hyper-parameter for 
Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method in \bruce{CITE BAYESIAN PSPLINES} where we construct 
a mixture model on a wide range of gamma distributions with different b hyper-parameters. Our prior is now defined as:

\begin{equation}
    \bm{p} \sim \mathcal{D}(n)
\end{equation}
\begin{equation}
    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
\end{equation}
\begin{equation}
    p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}' \bm{D} \bm{c}}
\end{equation}

Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve 
across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior

\begin{equation}
    \bm{p} \sim \mathcal{D}(n)
\end{equation}
\begin{equation}
    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
\end{equation}
\begin{equation}
    \lambda_k = \mathcal{G}(\omega, \omega)
\end{equation}
\begin{equation}
    p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}' \bm{D} \bm{\Lambda} \bm{D}' \bm{c}}
\end{equation}

Where above the matrix $\bm{\Lambda}$ is defined as: $\bm{\Lambda} = \mathrm{diag}\big(1,\lambda_0,...\lambda_k\big)$. This enforces a smooth evolution of the smoothing penalty 
across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
the power-law like mass distributions that are commonly used.

\begin{figure*}[ht!]
    \script{spline_basis_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/spline_basis_plot.pdf}
        \caption{Plot showing proper (left) and improper (right) MSpline bases with 20 degrees of freedom and equal weights for each component. The 
            difference penalty as described in Section II hinges on the fact that basis coeficients that are close produce smoother or flatter 
            curves. This means one does not want to use an improper basis (i.e. right) with a difference penalty as the resulting curve is not flat 
            with each component having equal weights.}
        \label{fig:spline_basis}
    \end{centering}
\end{figure*}

Since the smoothing prior is really wanting to pull the coeficients closer to each other to smooth the distribution, 
we must ensure that the spline function is in fact flat or smooth with all equal coeficients. We follow the distinction from \bruce{CITE bayesian psplines} that the difference
penalty or prior is only valid with ``proper'' spline bases. This is where the knots are evenly spaced and are not stacked at the extremal values, 
as is sometimes done. Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. The ``proper''
basis is shown on the left where the resulting (black) curve is flat with equal components, while the ``improper'' basis on the right has the 
components squeezed up against the boundaries where multiple knots are located causing the sharp increases at the bounds even with all 10 coeficients equal.

\subsection{Model Specfication}

We use hierarchical Bayesian inference to simultaneosly infer the mass, spin and redshift distributions of binary black holes (BBHs) using 
the 69 confident BBH detections reported in the recent LVK catalog of observations, GWTC-3. In particular we choose to parameterize the two
masses with the primary (more massive component) mass and the mass ratio defined as $q=\frac{m_2}{m_1}$. We choose to model 4 of the 6 total 
spin degrees of freedom of a binary merger with each component spin magnitude, and the cosine of the tilt angle which is defined as the angle 
between each spin vector and the binaries orbital angular mommentum vector. We additionally will fit a population model on the redshift distribution
of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology defined by the Planck 2015 results, which defines an analytical mapping between each event's inferred
luminosity distance and it's redshift. While we choose to use MSpline distibutions for the masses and spins, we use the canonical \textsc{PowrerlawRedshift}
model describing the evolution of CBC merger rates as a power law in $(1+z)$ with a slope of $\lambda_z$. The corresponsing distribution is Thus
desribed by $p(z|\lambda)\propto \frac{dV_c}{dz} \frac{T_\mathrm{obs}}{1+z} (1+z)^\lambda$. We model the spin magnitude and tilt distibutions to be 
described by independent MSpline distributions for each component.

### 2022-09-14 src/tex/ms.tex
update the git repo

--- 2022-07-19 src/tex/ms.tex
@@
 \usepackage{lineno}
+\usepackage{bm}
 \usepackage{amsmath}
@@
 
-\section{Introduction} \label{sec:intro}
+\input{intro.tex}
+\input{methods.tex}
+\input{results.tex}
+\input{conclusion.tex}
 
-Now that gravitational wave observations of compact binary coalescence is a regular occurrence, producing catalogs of nearly 
-100 such detections, we now have access to a complete understanding of the population of compact binaries. In the coming fourth 
-observing run of the LIGO-Virgo-KAGRA collaboration, the catalog size is expected to increase by a factor of 5. The extensive 
-physics governing the formation and evolution of compact objects that end up merging is imprinted on the properties of the population 
-of CBCs, allowing us to learn about these not well understood ideas through looking at the distribution of observed GWs. In particular 
-the mass distribution of binary black holes has been shown to be very useful in measuring cosmological parameters, constraining modified 
-gravitational wave propagation, constraining a running Planck mass, looking of evidence of ultralight bosons through superradiance, 
-putting constraints on uncertain nuclear reaction rates important for stellar evolution, and even looking for primordial black holes. 
-Through a better understanding of the mass, spin, and redshift distribution of compact binaries we can extend this be a useful tool 
-in all the different physical applications mentioned above. In this paper we highlight how the use of basis-splines can be a useful 
-model-agnostic modeling approach to the astrophysical distributions of compact binaries. We show that with a particular choice of basis, 
-we can efficiently model the spin and/or mass distribution of compact binaries in GWTC-3 with spline regression in hierarchical 
-Bayesian inference. We show our results are similar to those produced with the more simpler and motivated parametric models, 
-while being capable of finding more subtle features should they appear in future catalogs. This method can be extended to higher-dimensional 
-basis-splines to model correlations between different distributions which will be necessary to confidently disentangle differently 
-competing formation channels should they exist.
-
-\section{Methods} \label{sec:methods}
-\subsection{Constructing A Basis} \label{sec:basis_splines}
-
-A common non-parametric method in statistical applications is the use of B-Splines or basis splines. A spline function of order $k$, 
-is a piece-wise polynomial of order $k-1$ polynomials stitched together from defined ``knot'' locations across the domain. 
-They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
-B-Splines of order $k$ are a set of order $k-1$ polynomials that form a complete basis for any spline function of order $k$. 
-Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
-every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines for a given knot vector using the Cox-de Boor 
-recursion formula -- for knots $t_0$, $t_1$,...,$t_{i+k}$ the basis components are given by:
-\begin{equation}
-    B_{i,1}(x | \mathbf{t}) = 
-    \begin{cases}
-        1, & \text{if } t_i \leq x < t_{i+1} \\
-        0, & \text{otherwise}
-    \end{cases}
-\end{equation}
-\begin{equation}
-    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x)B_{i,k}(x) + \big[1-\omega_{i+1,k}(x)\big]B_{i+1,k}(x)
-\end{equation}
-\noindent Where $\omega_{i,k}$ above is defined as:
-\begin{equation}
-    \omega_{i,k}(x | \mathbf{t}) =
-    \begin{cases}
-        \frac{x-t_i}{t_{i+k}-t_i}, & t_{i+k} \neq t_i \\
-        0, & \text{otherwise}
-    \end{cases}
-\end{equation}
-
-A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function. Namely, 
-$M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. The M-Spline basis only differs 
-from B-Splines by a normalization factor, namely:
-\begin{equation}\label{eq:MB_SplineRelation}
-    M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
-\end{equation}
-\noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper.
-
-Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. Notice 
-that when we introduced knots and in equation \ref{eq:MB_SplineRelation}, you can see there needs to be knots up to $t_{i+k}$ while $i$ 
-indexes the desired degrees of freedom in your basis. This means in practice one must define $n+k$ knots. However, you have control 
-in the boundary conditions by how many of the $n+k$ knots you place at the lower and upper bounds. By placing $k$ knots at each boundary 
-(leaving $n-k$ interior knots), the first and last basis components are maximized at the boundaries. Alternatively one may want to 
-a-priori enforce vanishing boundary conditions, for example, if they knew for a fact that the function they are modeling has 
-$p(x_\mathrm{bound}) = 0$.  This can be done by placing $k-1$ knots at the boundaries you wish the spline to vanish at. See figure for 
-an example of a cubic M-Spline (k=3) basis with 10 degrees of freedom with $k=3$ knots at each boundary (left) versus enforcing vanishing 
-boundary conditions by having $k-1=2$ knots at each boundary (right).
-
-\subsection{Parameterized Perturbations} \label{sec:perturbation_model}
-\subsection{Generic Mass Model} \label{sec:nonparametric_model}
-\section{Results} \label{sec:results}
-\subsection{Mass Spectrum Inference with GWTC-3} \label{sec:GWTC3_inferece}
-\section{Conclusions}\label{sec:conclusion}
 \section{Acknowledgements}\label{sec:acknowledments}
@@
 \textsc{bilby}~\citep{Ashton_2019},
-\textsc{GWPopulation}~\citep{Talbot_2019}
+\textsc{GWPopulation}~\citep{Talbot_2019},
+\textsc{jax},
+\textsc{numpyro},
+\textsc{arviz},
+\textsc{seaborn},
+\textsc{corner} \bruce{CITE ALL ABOVE}
 }
-\bibliography{references}{}
+\bibliography{bib}{}
 \bibliographystyle{aasjournal}
 
-\appendix
-\section{Hierarchical Bayesian Inference} \label{sec:hierarchical_inference}
-
-% This appendix goes over in detail the hierarchical bayeisan inference framework
-We use hierarchical Bayesian inference to simultaneously infer the population distributions of the primary masses ($m_1$), mass ratios 
-($q$) and the redshifts ($z$) of observed BBHs. For a set of hyper-parameters, $\Lambda$, and local ($z=0$) merger rate density (units of 
-mergers per co-moving volume per time), $\mathcal{R}_0$, we write the overall number density of BBH mergers in the universe as:
-
-\begin{equation} \label{number_density}
-     \frac{dN(m_1, q, z | \mathcal{R}_0, \Lambda)}{dm_1dqdz} = \frac{dV_c}{dz}\bigg(\frac{T_\mathrm{obs}}{1+z}\bigg) \frac{d\mathcal{R}(m_1, q, z | \mathcal{R}_0, \Lambda)}{dm_1dq} = \mathcal{R}_0 p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)
-\end{equation}
-
-\noindent
-Above, $dV_c$ is the co-moving volume element \citep{hogg_cosmo} and $T_\mathrm{obs}$, the observing time period that produced the 
-catalog with the related factor of $1+z$ converting this detector-frame time to source-frame. We assume a LambdaCDM cosmology using 
-the cosmological parameters from \citet{Planck2015}. The redshift evolution of the merger rate follows 
-$p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$. Integrating equation \ref{number_density} across all masses, 
-and up to some redshift, $z_m$, returns the total number of BBH mergers in the universe out to that redshift. Let $\{d_i\}$ represent a 
-set of data from $N_\mathrm{obs}$ observed gravitational waves associated with BBH mergers. We model the merger rate as an inhomogenous 
-point process and when imposing a log-uniform prior on the merger rate, we can marginalize over the merger rate to get the posterior 
-distribution of our hyper-parameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.
-
-\begin{equation} \label{posterior}
-    p\left(\Lambda | \{d_i\} \right) \propto \frac{p(\Lambda)}{\xi(\Lambda)^{N_\mathrm{obs}}} \prod_{i=1}^{N_\mathrm{obs}} \Bigg[ \int \mathcal{L}\left(d_i | m_1^i, q^i, z^i \right) p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda) dm_1 dq dz \Bigg],
-\end{equation}
-
-\noindent
-where, $\mathcal{L}(d_i|m_1, q, z)$, is the single-event likelihood function from each events original analysis, and $\xi(\Lambda)$ 
-is the detection efficiency given a population distribution described by $\Lambda$. The procedure for calculating $\xi(\Lambda)$ is 
-described in more detail below. The LVC reports out posterior samples for each observed event, with which we can use importance sampling 
-to estimate the integrals above in equation \ref{posterior}. We replace the integrals with ensemble averages over $K_i$ posterior samples 
-associated with each event in the catalog:
-
-\begin{equation}
- p\left(\Lambda | \{d_i\}\right) \propto p(\Lambda) \prod_{i=1}^{N_\mathrm{obs}} \bigg[ \frac{1}{K_i} \sum_{j=1}^{K_i} \frac{p(m_1^{i,j}|\Lambda)p(q^{i,j}|\Lambda)p(z^{i,j}|\Lambda)}{\pi(m_1^{i,j}, q^{i,j}, z^{i,j})} \bigg]
-\end{equation}
-
-\noindent 
-Here $j$ indexes the $K_i$ posterior samples from each event and $\pi(m_1, q, z)$ is the default prior used by parameter estimations that 
-produced the posterior samples for each event. In the analyses of GWTC-2 the default prior used is uniform in detector frame masses and 
-Euclidean volume. The corresponding prior evaluated in source frame masses and redshift is 
-$\pi(m_1, q, z) \propto m_1(1+z)^2 D_L^2(z) \frac{dD_L}{dz}$, where $D_L$ is the luminosity distance.
-
-To carefully incorporate selection effects to our model we need to quantify the detection efficiency, $\xi(\Lambda)$, of the search 
-pipelines that were used to create GWTC-2, at a given population distribution described by $\Lambda$.
-
-\begin{equation} \label{det_eff}
-     \xi(\Lambda) = \int dm_1 dq dz P_\mathrm{det}(m_1, q, z)p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)
-\end{equation}
-
-\noindent The above integral is not tractable since there is no analytic prescription for $P_\mathrm{det}(m_1,q,z)$, the detection 
-probability of an individual event. To estimate this integral we use a software injection campaign where GWs from a fixed, broad 
-population of sources are simulated, put into real detector data, and then run through the same search pipelines that were used to 
-produce the catalog we are analyzing \footnote{For O3a we used the injection sets used by \citet{o3a_pop}, which can be found at 
-https://dcc.ligo.org/LIGO-P2000217/public. For O1/O2 we used the mock injection sets used by \citet{o1o2_pop} which can be found at 
-https://dcc.ligo.org/LIGO-P2000434/public}. With these search results in hand, we use importance sampling to evaluate the integral 
-in equation \ref{det_eff}:
-
-\begin{equation} \label{xi}
-     \xi(\Lambda) = \frac{1}{N_\mathrm{inj}} \sum_{i=1}^{N_\mathrm{found}} \frac{p(m_1^i | \Lambda) p(q^i | m_1, \Lambda) p(z^i | \Lambda)}{p_\mathrm{inj}(m_1^i, q^i, z^i)}
-\end{equation}
-
-\noindent
-Where the sum indexes only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, 
-and $p_\mathrm{inj}(m_1, q, z)$ is the reference distribution from which the injections were drawn. Additionally, we follow the procedure 
-outlined in \citet{Farr_2019} to marginalize the uncertainty in our estimate of $\xi(\Lambda)$ due to a finite number of simulated events. 
-We make the assumption that repeated sampling of $\xi(\Lambda)$ will follow a normal distribution with 
-$\xi(\Lambda) \sim \mathcal{N}(\mu(\Lambda), \sigma(\Lambda))$, where the mean, $\mu$, is the estimate from equation \ref{xi}, 
-while the variance, $\sigma^2$, is defined as:
-
-\begin{equation}
-    \sigma^2(\Lambda) \equiv \frac{\mu^2(\Lambda)}{N_\mathrm{eff}} \simeq \frac{1}{N^2_\mathrm{inj}} \sum_{i=1}^{N_\mathrm{found}} \bigg[\frac{p(m_1 | \Lambda) p(q | m_1, \Lambda) p(z | \Lambda)}{p_\mathrm{inj}(m_1, q, z)}\bigg]^2 - \frac{\mu^2(\Lambda)}{N_\mathrm{inj}}
-\end{equation}
-
-\noindent
-Above we define $N_\mathrm{eff}$ as the effective number of independent draws contributing to the importance sampled estimate, 
-in which we verify to be sufficiently high after re-weighting the injections to a given population (i.e. $N_\mathrm{eff} > 4N_\mathrm{obs}$). 
-We write the hyper-posterior marginalized over the merger rate and uncertainty in estimation of $\xi(\Lambda)$, neglecting terms of 
-$\mathcal{O}(N_\mathrm{eff}^{-2})$ or greater \citep{Farr_2019}, as:
-
-\begin{equation}\label{importance-posterior}
-    \log p\left(\Lambda | \{d_i\}\right) \propto \sum_{i=1}^{N_\mathrm{obs}} \log \bigg[ \frac{1}{K_i} \sum_{j=1}^{K_i} \frac{p(m_1^{i,j}|\Lambda)p(q^{i,j}|\Lambda)p(z^{i,j}|\Lambda)}{\pi(m_1^{i,j}, q^{i,j}, z^{i,j})} \bigg] -  \\
-    N_\mathrm{obs} \log \mu + \frac{3N_\mathrm{obs} + N_\mathrm{obs}^2}{2N_\mathrm{eff}} + \mathcal{O}(N_\mathrm{eff}^{-2}).
-\end{equation}
-
-\noindent
-We explicitly enumerate each of the models used in this work for $p(m_1|\Lambda)$, $p(q|m_1, \Lambda)$, and $p(z|\Lambda)$ along with 
-their respective hyper-parameters and prior distributions in Table \ref{tab:model_params}. To calculate marginal likelihoods and draw 
-samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
-\textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with 
-the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}.
-
-\section{Validation Studies} \label{sec:validation}
+\input{appendicies.tex}
 

### 2022-09-14 src/tex/results.tex
update the git repo

\section{Population Inference of GWTC-3 BBHs} \label{sec:results}

\subsection{Mass Distribution} \label{sec:mass_dist}

We apply our newly constructed models to the BBH analysis that was done in the astrophysical population companion paper to GWTC-3. 
We find consistent features in the mass disribution with what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} 
mass models. In particular our MSpline model finds a peak in merger rate density at both 10 and 35 soloar masses, agreeing with those reported
in \bruce{CITE o3b paper}. We also find a significantly less declining mass distribution that has considerably larger support for higher mass 
mergers when compared to the other power-law based models. Another interesting consequence of this is that we thus infer a much less steeply
evolving merger rate with redshift. It is known that there is a strong correlation between the primary mass power law index, $alpha$, and the 
redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- the inferred rate must drastically increase 
with resdshift to explain the few higher mass events in our catalog, but when one infers a flatter distribution like the MSPline inferred
distribition in plot \ref{fig:mass_distribution}, the higher mass mergers are consistent with the local merger rate denstiy as a function of mass, 
and thus the model does not need to have as steep of power-law in redshift. With this more flexible mass population model, we now 
find that the merger rate is fully consistent with being unifom with co-moving volume, rather than the confidently evolving merger rate 
conclusion from \bruce{cite O3b}.

\begin{figure*}[ht!]
    \script{mass_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
        \caption{Plot showing the primary mass (left) and mass ratio (right) distributions inferred with the 
        \textsc{MSpline} model (black) with 40 knots for $m_1$, and 15 knots for $q$. We show the results for the \textsc{PowerlawPeak} (blue) and 
        \textsc{PowerlawSpline} (orange) models fromthe LVK's GWTC-3 population analyses. Solid lines show the median of the posterior while the shaded
        bands show the 90\% credible intervals.}
        \label{fig:mass_distribution}
    \end{centering}
\end{figure*}

In addition to the primary mass distirbution there is some mild evidence for a mass ratio distibution that is not well described by a power law, 
which is how the mass ratio distribution is commonly modeled. In particular our smoothed MSpline model finds a decrease in the merger rate at $q\sim1$, 
while agreeing well with the power-law on the decline in rate from $q \in [0.4, 0.8]$, and a much larger tail extending to more asymmetric
mass ratios.

\subsection{Spin Distributions} \label{sec:spin_dist}

The spins distribution of merging combact binaries provides a very useful insight into the formation history of the binary. In particular the two main subcategories, 
the isolated and dynamical formation channels, would produce distinct signatures in the spin distribution when looking at a population of observations. Isolated formation
is where the only interactions with the binary are between each other. As the binary evolves and mass transfer happens between the two components, we expect the orientation
of each components spin vector to be preferentially aligned with the orbital angular mommentumof the system. Some misalignment is epected to occur due to the kicks from 
each star exploding in supernovae leaving behind the compact objects. Conversely, the dynamical channel

\begin{figure*}[ht!]
    \script{component_spin_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
        \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
        \label{fig:component_spin_distribution}
    \end{centering}
\end{figure*}

\begin{figure*}
    \script{iid_component_spin_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/iid_component_spin_distribution_plot.pdf}
        \caption{Plot showing the inferred component spin magnitude (left) and spin tilt (right) distributions inferred with the 9-knot \textsc{MSpline} models. 
        Each components spin magnitude and tilt are assumed to be IID. We compare by showing the results for the
        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
        \label{fig:iid_component_spin_distribution}
    \end{centering}
\end{figure*}

### 2022-09-14 src/scripts/component_spin_distribution_plot.py

@@ -104,7 +104,7 @@ for ax, ps, lab in zip([axs[1,0], axs[1,1]], [ct1_pdfs, ct2_pdfs], ['cos_tilt_1'
     med = np.median(ps, axis=0)
     low = np.percentile(ps, 5, axis=0)
     high = np.percentile(ps, 95, axis=0)
-    ax.fill_between(xs, low, high, color='k', alpha=0.3)#, label='90% CI')
+    ax.fill_between(xs, low, high, color='k', alpha=0.2)#, label='90% CI')
     ax.plot(xs, med, color='k', lw=4, alpha=0.9, label='MSpline')
     ax.plot(xs, low, color='k', lw=0.25, alpha=0.3)
     ax.plot(xs, high, color='k', lw=0.25, alpha=0.3)

### 2022-09-14 src/scripts/iid_component_spin_distribution_plot.py

@@ -1,0 +1,125 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+def load_mag_ppd():
+    datadict = dd.io.load(paths.data / 'from_cit/mspline_m1q_iid_spins_expprior_ppds.h5')
+    return datadict['mags'], datadict['dRda']
+
+def load_tilt_ppd():
+    datadict = dd.io.load(paths.data / 'from_cit/mspline_m1q_iid_spins_expprior_ppds.h5')
+    return datadict['cts'], datadict['dRdct']
+
+
+def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
+    xs = np.linspace(0, 1, 1000)
+    
+    _data = dd.io.load(paths.data / fi)
+    lines = dict()
+    for key in _data["lines"].keys():
+        lines[key] = _data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    if a1:
+        med = np.median(lines['a_1'], axis=0)
+        low = np.percentile(lines['a_1'], 5, axis=0)
+        high = np.percentile(lines['a_1'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=3, alpha=0.75, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
+        ax.plot(xs, high, color=col, lw=0.2, alpha=0.4)#, label=lab)
+    else:
+        med = np.median(lines['a_2'], axis=0)
+        low = np.percentile(lines['a_2'], 5, axis=0)
+        high = np.percentile(lines['a_2'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=3, alpha=0.75, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
+        ax.plot(xs, high, color=col, lw=0.2, alpha=0.4)
+    return ax
+
+
[…]

### 2022-09-19 src/tex/methods.tex
slowly filling out draft....

@@
 
-A common non-parametric method in statistical applications is the use of B-Splines or basis splines. A spline function of order $k$, 
-is a piece-wise polynomial of order $k-1$ polynomials stitched together from defined ``knot'' locations across the domain. 
+A common non-parametric method in statistical applications is the use of basis splines. A spline function of order $k$, 
+is a piece-wise polynomial of order $k$ polynomials stitched together from defined ``knot'' locations across the domain. 
 They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
-B-Splines of order $k$ are a set of order $k-1$ polynomials that form a complete basis for any spline function of order $k$. 
+Basis splines of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
 Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
-every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines for a given knot vector using the Cox-de Boor 
-recursion formula -- for knots $t_0$, $t_1$,...,$t_{i+k}$ the basis components are given by:
+every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines basis components for a given knot vector 
+using the Cox-de Boor recursion formula. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:
+
 \begin{equation}
@@
 \end{equation}
+
+\noindent combined with the recursion relation:
+
 \begin{equation}
-    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x)B_{i,k}(x) + \big[1-\omega_{i+1,k}(x)\big]B_{i+1,k}(x)
+    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x | \mathbf{t})B_{i,k}(x | \mathbf{t}) + \\
+                                \big[1-\omega_{i+1,k}(x | \mathbf{t})\big] B_{i+1,k}(x | \mathbf{t})
 \end{equation}
-\noindent Where $\omega_{i,k}$ above is defined as:
+
+\noindent where $\omega_{i,k}$ is defined as:
+
 \begin{equation}
@@
 
+\noindent allowing one to build a basis of $i$ components that spans the vector space of order-$k$ spline functions interpolated 
+from this knot vector. This is known as the ``B-Spline'' basis.
+
 A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function. Namely, 
@@
 from B-Splines by a normalization factor, namely:
+
 \begin{equation}\label{eq:MB_SplineRelation}
@@
 \end{equation}
+
 \noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper.
@@
 the stochastic differnece prior described in \bruce{CITE THIS PAPER}, which is equivalent to a Gaussian random walk prior where each succeeding 
-coeficient is normally distributed about its neighboring coeficients. Thus our smoothing prior for our bayesian framework is:
+coeficient is normally distributed about its neighboring coeficients. Thus the smoothing prior for $n$ degree's of freedom basis with a smoothing 
+difference order of $r$ is defined as:
 
-\begin{equation}
-    \tau_\lambda \sim \mathcal{G}(a, b)
-\end{equation}
-\begin{equation}
-    p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}' \bm{D} \bm{c}}
-\end{equation}
+\begin{eqnarray}
+\tau_\lambda \sim \mathcal{G}(a, b), \\
+p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}}
+\end{eqnarray}
 
-The smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a 
-very large number of knots such that your domain is densly populated with basis coeficients, the smoothing prior will smooth out regions where 
+\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $a$, $b$, shape parameters for the Gamma distribution, such that
+the mean is at 1, with a large vairabce. This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. 
+By adding in a very large number of knots such that your domain is densly populated with basis coeficients, the smoothing prior will smooth out regions where 
 the data can be described smoothly, and relax when the data has features for the spline function to fit. In practice one would want to add knots 
@@
 Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method in \bruce{CITE BAYESIAN PSPLINES} where we construct 
-a mixture model on a wide range of gamma distributions with different b hyper-parameters. Our prior is now defined as:
+a mixture model on a wide range of gamma distributions with different b hyper-parameters. We can now replace the prior on $\tau_\lambda$ with:
 
-\begin{equation}
-    \bm{p} \sim \mathcal{D}(n)
-\end{equation}
-\begin{equation}
+\begin{eqnarray}
+\bm{p} \sim \mathcal{D}(m), \\
 p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
-\end{equation}
-\begin{equation}
-    p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}' \bm{D} \bm{c}}
-\end{equation}
+\end{eqnarray}
 
 Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
-that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve 
-across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior
+that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
+across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
+effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:
 
-\begin{equation}
-    \bm{p} \sim \mathcal{D}(n)
-\end{equation}
-\begin{equation}
-    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
-\end{equation}
-\begin{equation}
-    \lambda_k = \mathcal{G}(\omega, \omega)
-\end{equation}
-\begin{equation}
-    p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}' \bm{D} \bm{\Lambda} \bm{D}' \bm{c}}
-\end{equation}
+\begin{eqnarray}
+\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
+\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
+p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c}}
+\end{eqnarray}
 
-Where above the matrix $\bm{\Lambda}$ is defined as: $\bm{\Lambda} = \mathrm{diag}\big(1,\lambda_0,...\lambda_k\big)$. This enforces a smooth evolution of the smoothing penalty 
+Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
+prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
 across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 

### 2022-09-19 src/tex/ms.tex
slowly filling out draft....

@@
 
-\title{Covering Your Basis: Model-Agnostic Inference of LIGO-Virgos Binary Black Hole Spin Distribution}
+\title{Covering Your Basis: Model-Agnostic Inference of LIGO-Virgos Binary Black Hole Popuation Properties}
 
@@
 
+\author{Zoheyr Doctor}
+\affiliation{Center for Interdisciplinary Exploration and Research in Astrophysics (CIERA), Department of Physics and Astronomy, Northwestern
+University, Evanston, IL 60201, USA}
+
+\author{Jon Hornung}
+\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
+\affiliation{Thurston High School, Springfield, OR 9747, USA}
+
 \begin{abstract}
-We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical mass distribution of 
-binary black holes using GWTC-3.
+We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 
+binary black hole masses and spins using the 69 confident observations in GWTC-3. We find the same features previously recovered 
+with similarly flexible models in the mass distribution, namely the peaks in merger rates at \~10\msun and \~35\msun. 
+We apply our method to investigate whether the spin components are indendendenty distributed with a model agnositc way, where we find that 
+the spin magnitude distribution seems to be quite consistently IID, with XX\% of black hole spins below XX at XX\% credibility. We report 
+slight evidence of tilt distributions that do not peak at $\cos(\theta_i) = 1$ as previous models assumed, and slight evidence that 
+the components are distributed differently, in contrast to the spin magnitude distribution. While we do not find signs of a significant
+zero spinning sub population we do find that the data prefer not to force the support for exactly zero spinning black holes to 0 as 
+the non-singular Beta distribution and \textsc{Default} model assumes. 
 \end{abstract}

### 2022-09-22 src/scripts/deprecated/component_spin_distribution_plot.py
add more plots with more stable looking results

@@ -1,0 +1,148 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+def load_mag_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_60m1_12ind_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['dRda1'], datadict['dRda2'], datadict['mags'], datadict['mags']
+
+def load_tilt_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_60m1_12ind_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['dRdct1'], datadict['dRdct2'], datadict['tilts'], datadict['tilts']
+
+
+def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
+    xs = np.linspace(0, 1, 1000)
+    
+    _data = dd.io.load(paths.data / fi)
+    lines = dict()
+    for key in _data["lines"].keys():
+        lines[key] = _data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    if a1:
+        med = np.median(lines['a_1'], axis=0)
+        low = np.percentile(lines['a_1'], 5, axis=0)
+        high = np.percentile(lines['a_1'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high, color='k', lw=0.1, alpha=0.1)#, label=lab)
+    else:
+        med = np.median(lines['a_2'], axis=0)
+        low = np.percentile(lines['a_2'], 5, axis=0)
+        high = np.percentile(lines['a_2'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
[…]

### 2022-09-22 src/scripts/deprecated/iid_component_spin_distribution_plot.py

@@ -1,0 +1,134 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+def load_mag_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_60m1_12iid_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['mags'], datadict['dRda']
+
+def load_tilt_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_60m1_12iid_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['tilts'], datadict['dRdct']
+
+
+def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
+    xs = np.linspace(0, 1, 1000)
+    
+    _data = dd.io.load(paths.data / fi)
+    lines = dict()
+    for key in _data["lines"].keys():
+        lines[key] = _data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    if a1:
+        med = np.median(lines['a_1'], axis=0)
+        low = np.percentile(lines['a_1'], 5, axis=0)
+        high = np.percentile(lines['a_1'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high, color='k', lw=0.1, alpha=0.1)#, label=lab)
+    else:
+        med = np.median(lines['a_2'], axis=0)
+        low = np.percentile(lines['a_2'], 5, axis=0)
+        high = np.percentile(lines['a_2'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high,color='k', lw=0.1, alpha=0.1)
+    return ax
+
+
[…]

### 2022-09-22 src/tex/appendicies.tex
add more plots with more stable looking results

@@
 We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
-their respective hyper-parameters and prior distributions in the next section. To calculate marginal likelihoods and draw 
+their respective hyper-parameters and prior distributions in the next section. To calculate draw 
 samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
-\textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with 
-the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}. We also make use of the hamiltonian monte carlo algorithms in 
-\textsc{numpyro} and use \textsc{jax} to calculate our likelihoods \bruce{FIND citations for these}.
-
-\section{Models and Hyper-Parameters} \label{sec:hypparams}
+NUTS hamiltonian monte carlo sampler in \textsc{numpyro} and \textsc{jax} to calculate likelihoods \bruce{FIND citations for these}.
 
 \section{Validation Studies} \label{sec:validation}
+
+\section{Penalized Splines and Smoothing}\label{sec:psplines}
+
+A common issue when using splines as a flexible fitting method is their sensitivity to the chosen number of knots, and their locations. 
+Adding more knots knots will increase the natural a-priori variance in the spline function, while the space between knots can limit the 
+resolution of features in the data the spline is capable of fitting. To ensure your spline based model is flexible enough to find sharp
+features in data, one would want to add as many knots as densely as possible, but this comes with the sometimes un-wanted affect of the 
+larger variance as mentioned above. To overcome this we resort to the frequentist penalized spline (PSpline) in which one applies a penalty
+to the likelihood based on the difference of adjacent knot coeficients. Since the resulting linear combination of spline basis components is 
+smoother, or flatter, when the basis coeficients are near each other, this has a natural smoothing affect to the spline function. Since we are 
+using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog, by applying 
+the stochastic differnece prior described in \bruce{CITE THIS PAPER}, which is equivalent to a Gaussian random walk prior where each succeeding 
+coeficient is normally distributed about its neighboring coeficients. Thus the smoothing prior for $n$ degree's of freedom basis with a smoothing 
+difference order of $r$ is defined as:
+
+\begin{eqnarray}
+\tau_\lambda \sim \mathcal{G}(a, b), \\
+p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
+\end{eqnarray}
+
+\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $a$, $b$, shape parameters for the Gamma distribution, such that
+the mean is at 1, with a large vairabce. This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. 
+By adding in a very large number of knots such that your domain is densly populated with basis coeficients, the smoothing prior will smooth out regions where 
+the data can be described smoothly, and relax when the data has features for the spline function to fit. In practice one would want to add knots 
+of order the number of observations or more. One downside of this prior specification is a moderate dependence on choice of the b hyper-parameter for 
+Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method in \bruce{CITE BAYESIAN PSPLINES} where we construct 
+a mixture model on a wide range of gamma distributions with different b hyper-parameters. We can now replace the prior on $\tau_\lambda$ with:
+
+\begin{align}
+    \bm{p} \sim \mathcal{D}(m), \\
+    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
+\end{align}
+
+Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
+that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
+across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
+effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:
+
+\begin{eqnarray}
+\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
+\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
+p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c} \big] e^{-n\bm{c}}
+\end{eqnarray}
+
+Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
+prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
+across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
+the power-law like mass distributions that are commonly used.
+
+Since the smoothing prior is really wanting to pull the coeficients closer to each other to smooth the distribution, 
+we must ensure that the spline function is in fact flat or smooth with all equal coeficients. We follow the distinction from \bruce{CITE bayesian psplines} that the difference
+penalty or prior is only valid with ``proper'' spline bases. This is where the knots are evenly spaced and are not stacked at the extremal values, 
+as is sometimes done. Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. The ``proper''
+basis is shown on the left where the resulting (black) curve is flat with equal components, while the ``improper'' basis on the right has the 
+components squeezed up against the boundaries where multiple knots are located causing the sharp increases at the bounds even with all 10 coeficients equal.
+*\

### 2022-09-22 src/tex/conclusion.tex
add more plots with more stable looking results

\section{Conclusions}\label{sec:conclusion}

\bruce{have subsection in results.tex to discuss the astro interpretation of our results and connect to literature. 
I think main points for conclusion are to sum up conclusions with one last call to literature for most important parts, 
followed by short discussion of the outlook going into O4 and how this method will be especially useful as we rapidly approach
GW's data rich era}

### 2022-09-22 src/tex/methods.tex
add more plots with more stable looking results

@@
-\section{Methods} \label{sec:methods}
-
-\subsection{Constructing A Basis} \label{sec:basis_splines}
+\section{Constructing A Basis} \label{sec:basis_splines}
 
@@
 
-\begin{equation}
-    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x | \mathbf{t})B_{i,k}(x | \mathbf{t}) + \\
-                                \big[1-\omega_{i+1,k}(x | \mathbf{t})\big] B_{i+1,k}(x | \mathbf{t})
-\end{equation}
+\begin{multline*}
+    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x | \mathbf{t})B_{i,k}(x | \mathbf{t})\\
+                                + \big[1-\omega_{i+1,k}(x | \mathbf{t})\big] B_{i+1,k}(x | \mathbf{t})
+\end{multline*}
 
@@
 \end{equation}
+
+\begin{figure}[ht!]
+    \script{spline_basis_plot.py}
+        \includegraphics[width=0.45\textwidth]{figures/spline_basis_plot.pdf}
+        \caption{Plot showing proper MSpline bases with 20 degrees of freedom and equal weights for each component.}
+        \label{fig:spline_basis}
+\end{figure}
 
@@
 
-\subsection{Penalized Splines}
-A common issue when using splines as a flexible fitting method is their sensitivity to the chosen number of knots, and their locations. 
-Adding more knots knots will increase the natural a-priori variance in the spline function, while the space between knots can limit the 
-resolution of features in the data the spline is capable of fitting. To ensure your spline based model is flexible enough to find sharp
-features in data, one would want to add as many knots as densely as possible, but this comes with the sometimes un-wanted affect of the 
-larger variance as mentioned above. To overcome this we resort to the frequentist penalized spline (PSpline) in which one applies a penalty
-to the likelihood based on the difference of adjacent knot coeficients. Since the resulting linear combination of spline basis components is 
-smoother, or flatter, when the basis coeficients are near each other, this has a natural smoothing affect to the spline function. Since we are 
-using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog, by applying 
-the stochastic differnece prior described in \bruce{CITE THIS PAPER}, which is equivalent to a Gaussian random walk prior where each succeeding 
-coeficient is normally distributed about its neighboring coeficients. Thus the smoothing prior for $n$ degree's of freedom basis with a smoothing 
-difference order of $r$ is defined as:
+\section{Model Construction}
 
-\begin{eqnarray}
-\tau_\lambda \sim \mathcal{G}(a, b), \\
-p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}}
-\end{eqnarray}
-
-\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $a$, $b$, shape parameters for the Gamma distribution, such that
-the mean is at 1, with a large vairabce. This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. 
-By adding in a very large number of knots such that your domain is densly populated with basis coeficients, the smoothing prior will smooth out regions where 
-the data can be described smoothly, and relax when the data has features for the spline function to fit. In practice one would want to add knots 
-of order the number of observations or more. One downside of this prior specification is a moderate dependence on choice of the b hyper-parameter for 
-Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method in \bruce{CITE BAYESIAN PSPLINES} where we construct 
-a mixture model on a wide range of gamma distributions with different b hyper-parameters. We can now replace the prior on $\tau_\lambda$ with:
-
-\begin{eqnarray}
-\bm{p} \sim \mathcal{D}(m), \\
-p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
-\end{eqnarray}
-
-Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
-that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
-across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
-effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:
-
-\begin{eqnarray}
-\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
-\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
-p(\bm{c} | \tau_\lambda) \propto \exp{-\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c}}
-\end{eqnarray}
-
-Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
-prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
-across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
-the power-law like mass distributions that are commonly used.
-
-\begin{figure*}[ht!]
-    \script{spline_basis_plot.py}
-    \begin{centering}
-        \includegraphics[width=\textwidth]{figures/spline_basis_plot.pdf}
-        \caption{Plot showing proper (left) and improper (right) MSpline bases with 20 degrees of freedom and equal weights for each component. The 
-            difference penalty as described in Section II hinges on the fact that basis coeficients that are close produce smoother or flatter 
-            curves. This means one does not want to use an improper basis (i.e. right) with a difference penalty as the resulting curve is not flat 
-            with each component having equal weights.}
-        \label{fig:spline_basis}
-    \end{centering}
-\end{figure*}
-
-Since the smoothing prior is really wanting to pull the coeficients closer to each other to smooth the distribution, 
-we must ensure that the spline function is in fact flat or smooth with all equal coeficients. We follow the distinction from \bruce{CITE bayesian psplines} that the difference
-penalty or prior is only valid with ``proper'' spline bases. This is where the knots are evenly spaced and are not stacked at the extremal values, 
-as is sometimes done. Figure shows examples of two different M-Spline bases with 10 degrees of freedom and knots spaced linearly from 0 to 1. The ``proper''
-basis is shown on the left where the resulting (black) curve is flat with equal components, while the ``improper'' basis on the right has the 
-components squeezed up against the boundaries where multiple knots are located causing the sharp increases at the bounds even with all 10 coeficients equal.
-
-\subsection{Model Specfication}
-
+\bruce{placeholder paragraph here to introduce our model constructions.}
 We use hierarchical Bayesian inference to simultaneosly infer the mass, spin and redshift distributions of binary black holes (BBHs) using 

### 2022-09-22 src/tex/ms.tex
add more plots with more stable looking results

@@
 
-\title{Covering Your Basis: Model-Agnostic Inference of LIGO-Virgos Binary Black Hole Popuation Properties}
+\title{Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population}
 
@@
 \section{Acknowledgements}\label{sec:acknowledments}
+We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful and discussions during the preparation this manuscript, 
+along with helpful comments on an early draft by Tom Callister.
 This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
@@
 \textsc{Matplotlib}~\citep{Hunter:2007},
-\textsc{bilby}~\citep{Ashton_2019},
-\textsc{GWPopulation}~\citep{Talbot_2019},
 \textsc{jax},
 \textsc{numpyro},
-\textsc{arviz},
-\textsc{seaborn},
-\textsc{corner} \bruce{CITE ALL ABOVE}
+\bruce{CITE ALL ABOVE}
 }

### 2022-09-22 src/tex/results.tex
add more plots with more stable looking results

@@
-\section{Population Inference of GWTC-3 BBHs} \label{sec:results}
+\section{Binary Black Hole Population Inference with GWTC-3} \label{sec:results}
 
-\subsection{Mass Distribution} \label{sec:mass_dist}
+\bruce{intro paragraph here to describe GWTC3 catalog and the selection we made for our analyses}
+
+\subsection{BBH Mass Distibution} \label{sec:mass_dist}
 
@@
         \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
-        \caption{Plot showing the primary mass (left) and mass ratio (right) distributions inferred with the 
-        \textsc{MSpline} model (black) with 40 knots for $m_1$, and 15 knots for $q$. We show the results for the \textsc{PowerlawPeak} (blue) and 
-        \textsc{PowerlawSpline} (orange) models fromthe LVK's GWTC-3 population analyses. Solid lines show the median of the posterior while the shaded
-        bands show the 90\% credible intervals.}
+        \caption{Plot showing the primary mass distribution inferred with the \textsc{MSpline} model with 40 knots for $m_1$. We show the results for the 
+        \textsc{PowerlawSpline} (blue) model from the LVK's GWTC-3 population analyses.}
         \label{fig:mass_distribution}
@@
 
-\subsection{Spin Distributions} \label{sec:spin_dist}
+\subsection{BBH Component Spin Distributions} \label{sec:spin_dist}
 
@@
 each star exploding in supernovae leaving behind the compact objects. Conversely, the dynamical channel     
+\begin{figure}
+    \script{plot_iid_spinmag.py}
+    \includegraphics[width=0.45\textwidth]{figures/iid_spinmag.pdf}
+    \caption{Caption.}
+    \label{fig:iid_spinmag_dist}
+\end{figure}
 
-\begin{figure*}[ht!]
-    \script{component_spin_distribution_plot.py}
-    \begin{centering}
-        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
-        \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
-        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
-        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
-        \label{fig:component_spin_distribution}
-    \end{centering}
-\end{figure*}
+\begin{figure}
+    \script{plot_iid_spintilt.py}
+    \includegraphics[width=0.45\textwidth]{figures/iid_spintilt.pdf}
+    \caption{Caption.}
+    \label{fig:iid_spintilt_dist}
+\end{figure}
+%\begin{figure*}[ht!]
+%    \script{component_spin_distribution_plot.py}
+%    \begin{centering}
+%%        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
+ %       \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
+%        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
+%        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
+%        \label{fig:component_spin_distribution}
+%    \end{centering}
+%\end{figure*}
 
-\begin{figure*}
-    \script{iid_component_spin_distribution_plot.py}
-    \begin{centering}
-        \includegraphics[width=\textwidth]{figures/iid_component_spin_distribution_plot.pdf}
-        \caption{Plot showing the inferred component spin magnitude (left) and spin tilt (right) distributions inferred with the 9-knot \textsc{MSpline} models. 
-        Each components spin magnitude and tilt are assumed to be IID. We compare by showing the results for the
-        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
-        \label{fig:iid_component_spin_distribution}
-    \end{centering}
-\end{figure*}
+%\begin{figure*}
+%    \script{iid_component_spin_distribution_plot.py}
+%    \begin{centering}
+%        \includegraphics[width=\textwidth]{figures/iid_component_spin_distribution_plot.pdf}
+%        \caption{Plot showing the inferred component spin magnitude (left) and spin tilt (right) distributions inferred with the 9-knot \textsc{MSpline} models. 
+%        Each components spin magnitude and tilt are assumed to be IID. We compare by showing the results for the
+%        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
+%        \label{fig:iid_component_spin_distribution}
+%    \end{centering}
+%\end{figure*}
+
+Comment here are the inferences of iid model vs Default and then iid vs independent test pointing out possible reasons for why spin tilt 
+does not peak at cos theta = 1 i.e. salvo's paper
+
+\subsection{The Effective Spin Dimensions}
+
+Transform comp spin results to effective dims to see how strong changes in mag/tilt dont significantly affect our best constrained/measured
+effective spins
+
+Present results fitting chi eff dist with MSpline I am making a change.
+
+\subsection{Discussion}
+
+\begin{figure}
+    \script{plot_ind_spinmag.py}
+    \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
+    \caption{Caption.}
+    \label{fig:ind_spinmag_dist}
+\end{figure}
+
+\begin{figure}
+    \script{plot_ind_spintilt.py}
+        \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
+        \caption{Caption.}
+        \label{fig:ind_spintilt_dist}
+\end{figure}
+
+\bruce{Here we discuss the astrophysical implications of work -- connect to wider literature}

### 2022-09-22 src/scripts/component_spin_distribution_plot.py

@@ -1,128 +1,0 @@
-#!/usr/bin/env python
-
-import paths
-import numpy as np
-import matplotlib.pyplot as plt
-import deepdish as dd
-
-def load_mag_ppd():
-    datadict = dd.io.load(paths.data / 'mspline_m1q_indmag_indtilt_spinmag_ppds.h5')
-    return datadict['a1'], datadict['pa1'], datadict['a2'], datadict['pa2']
-
-def load_tilt_ppd():
-    datadict = dd.io.load(paths.data / 'mspline_m1q_indmag_indtilt_spintilt_ppds.h5')
-    return datadict['ct1'], datadict['pct1'], datadict['ct2'], datadict['pct2']
-
-
-def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
-    xs = np.linspace(0, 1, 1000)
-    
-    _data = dd.io.load(paths.data / fi)
-    lines = dict()
-    for key in _data["lines"].keys():
-        lines[key] = _data["lines"][key][()]
-        for ii in range(len(lines[key])):
-            lines[key][ii] /= np.trapz(lines[key][ii], xs)
-    if a1:
-        med = np.median(lines['a_1'], axis=0)
-        low = np.percentile(lines['a_1'], 5, axis=0)
-        high = np.percentile(lines['a_1'], 95, axis=0)
-        ax.plot(xs, med, color=col, lw=3, alpha=0.75, label=lab)
-        ax.fill_between(xs, low, high, color=col, alpha=0.3)
-        ax.plot(xs, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
-        ax.plot(xs, high, color=col, lw=0.2, alpha=0.4)#, label=lab)
-    else:
-        med = np.median(lines['a_2'], axis=0)
-        low = np.percentile(lines['a_2'], 5, axis=0)
-        high = np.percentile(lines['a_2'], 95, axis=0)
-        ax.plot(xs, med, color=col, lw=3, alpha=0.75, label=lab)
-        ax.fill_between(xs, low, high, color=col, alpha=0.3)
-        ax.plot(xs, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
-        ax.plot(xs, high, color=col, lw=0.2, alpha=0.4)
[…]

### 2022-09-22 src/scripts/iid_component_spin_distribution_plot.py

@@ -1,125 +1,0 @@
-#!/usr/bin/env python
-
-import paths
-import numpy as np
-import matplotlib.pyplot as plt
-import deepdish as dd
-
-def load_mag_ppd():
-    datadict = dd.io.load(paths.data / 'from_cit/mspline_m1q_iid_spins_expprior_ppds.h5')
-    return datadict['mags'], datadict['dRda']
-
-def load_tilt_ppd():
-    datadict = dd.io.load(paths.data / 'from_cit/mspline_m1q_iid_spins_expprior_ppds.h5')
-    return datadict['cts'], datadict['dRdct']
-
-
-def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
-    xs = np.linspace(0, 1, 1000)
-    
-    _data = dd.io.load(paths.data / fi)
-    lines = dict()
-    for key in _data["lines"].keys():
-        lines[key] = _data["lines"][key][()]
-        for ii in range(len(lines[key])):
-            lines[key][ii] /= np.trapz(lines[key][ii], xs)
-    if a1:
-        med = np.median(lines['a_1'], axis=0)
-        low = np.percentile(lines['a_1'], 5, axis=0)
-        high = np.percentile(lines['a_1'], 95, axis=0)
-        ax.plot(xs, med, color=col, lw=3, alpha=0.75, label=lab)
-        ax.fill_between(xs, low, high, color=col, alpha=0.3)
-        ax.plot(xs, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
-        ax.plot(xs, high, color=col, lw=0.2, alpha=0.4)#, label=lab)
-    else:
-        med = np.median(lines['a_2'], axis=0)
-        low = np.percentile(lines['a_2'], 5, axis=0)
-        high = np.percentile(lines['a_2'], 95, axis=0)
-        ax.plot(xs, med, color=col, lw=3, alpha=0.75, label=lab)
-        ax.fill_between(xs, low, high, color=col, alpha=0.3)
-        ax.plot(xs, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
-        ax.plot(xs, high, color=col, lw=0.2, alpha=0.4)
-    return ax
-
-
[…]

### 2022-09-22 src/scripts/mass_distribution_plot.py

@@ -6,8 +6,8 @@ import matplotlib.pyplot as plt
 import deepdish as dd
 
 def load_ppd():
-    datadict = dd.io.load(paths.data / 'mspline_m1q_indmag_indtilt_mass_ppds.h5')
-    return datadict['m1'], datadict['pm1'], datadict['q'], datadict['pq']
+    datadict = dd.io.load(paths.data / 'mspline_60m1_14iid_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['m1s'], datadict['dRdm1'], datadict['qs'], datadict['dRdq']
 
 
 def load_o3b_paper_run_masspdf(filename):
@@ -37,42 +37,45 @@ def plot_o3b_res(ax, fi, m1=False, col='tab:blue', lab='PP'):
         med = np.median(plpeak_mpdfs, axis=0)
         low = np.percentile(plpeak_mpdfs, 5, axis=0)
         high = np.percentile(plpeak_mpdfs, 95, axis=0)
-        ax.plot(plpeak_ms, med, color=col, lw=3, alpha=0.75, label=lab)
+        ax.plot(plpeak_ms, med, color=col, lw=5, alpha=0.5, label=lab)
         ax.fill_between(plpeak_ms, low, high, color=col, alpha=0.3)
-        ax.plot(plpeak_ms, low, color=col, lw=0.2, alpha=0.4)#, label=lab)
-        ax.plot(plpeak_ms, high, color=col, lw=0.2, alpha=0.4)
+        ax.plot(plpeak_ms, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(plpeak_ms, high, color='k', lw=0.1, alpha=0.1)
     else:
         med = np.median(plpeak_qpdfs, axis=0)
         low = np.percentile(plpeak_qpdfs, 5, axis=0)
         high = np.percentile(plpeak_qpdfs, 95, axis=0)
-        ax.plot(plpeak_qs, med, color=col, lw=3, alpha=0.75, label=lab)
+        ax.plot(plpeak_qs, med, color=col, lw=5, alpha=0.5, label=lab)
         ax.fill_between(plpeak_qs, low, high, color=col, alpha=0.3)
[…]

### 2022-09-22 src/scripts/spline_basis_plot.py

@@ -12,8 +12,8 @@ xmax = 1
 xlab = 'x'
 
 cmap = 'magma'
-figx, figy = 16, 5
-fig, axs = plt.subplots(nrows=1, ncols=2, sharey='all', figsize=(figx,figy))
+figx, figy = 7, 5
+fig, axs = plt.subplots(nrows=1, ncols=1, sharey='all', figsize=(figx,figy))
 
 nadd = k - 1
 interior_knots = np.linspace(xmin, xmax, ndof+k-2*nadd)
@@ -34,13 +34,13 @@ for ii in range(ndof):
     basis[ii,0] = 2*basis[ii,1]-basis[ii,2]
     basis[ii,-1] = 2*basis[ii,-2]-basis[ii,-3]
     norm = 1.0 / (sum([np.trapz(basis[i, :], grid) * coef[i] for i in range(ndof)]))
-    axs[0].plot(grid, norm * coef[ii] * basis[ii,:], color=next(color_cycle), lw=3)#, label=f'c_{ii}')# = {coef[ii]:0.2f}')
+    axs.plot(grid, norm * coef[ii] * basis[ii,:], color=next(color_cycle), lw=4.5)#, label=f'c_{ii}')# = {coef[ii]:0.2f}')
     total += norm * coef[ii] * basis[ii,:]
-axs[0].plot(grid, total, color=next(total_color), lw=4, label=r'$\sum_{i}^{N_\mathrm{dof}} c_{i} M_{i,k}(x)$')
+axs.plot(grid, total, color=next(total_color), lw=6, label=r'$\sum_{i}^{N_\mathrm{dof}} c_{i} M_{i,k}(x)$')
 maxy = max(total)
 
 dx = knots[k+3] - knots[k+2]
-dy = maxy / (ndof)
+dy = 1.5*maxy / (ndof)
 ys = [dy]*len(knots)
 xs = knots.copy()
 for i, x in enumerate(knots):
@@ -50,63 +50,18 @@ for i, x in enumerate(knots):
         xs[i] = knots[i] + 0.1*dx
     if np.abs(xmax-x) < 1e-6:
         xs[i] = knots[i] - 0.1*dx
-axs[0].scatter(xs, ys, s=200, marker='x', color='k', alpha=0.4, label='Knots', lw=2.5, zorder=10)
+axs.scatter(xs, ys, s=250, marker='x', color='k', alpha=0.4, label='Knots', lw=2.5, zorder=10)
 
[…]

### 2022-09-22 src/scripts/plot_iid_spinmag.py
separate plots

@@ -1,0 +1,72 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+def load_mag_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_60m1_14iid_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['mags'], datadict['dRda']
+
+def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
+    xs = np.linspace(0, 1, 1000)
+    
+    _data = dd.io.load(paths.data / fi)
+    lines = dict()
+    for key in _data["lines"].keys():
+        lines[key] = _data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    if a1:
+        med = np.median(lines['a_1'], axis=0)
+        low = np.percentile(lines['a_1'], 5, axis=0)
+        high = np.percentile(lines['a_1'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high, color='k', lw=0.1, alpha=0.1)#, label=lab)
+    else:
+        med = np.median(lines['a_2'], axis=0)
+        low = np.percentile(lines['a_2'], 5, axis=0)
+        high = np.percentile(lines['a_2'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high,color='k', lw=0.1, alpha=0.1)
+    return ax
+
+figx, figy = 7, 5
+fig, axs = plt.subplots(nrows=1, ncols=1, figsize=(figx,figy))
+
+xmin, xmax = 0, 1
+mags, a_pdfs = load_mag_ppd()
+for jj in range(len(a_pdfs)):
[…]

### 2022-09-22 src/scripts/plot_iid_spintilt.py

@@ -1,0 +1,72 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+def load_tilt_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_60m1_14iid_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['tilts'], datadict['dRdct']
+
+def plot_o3b_spintilt(ax, fi,ct1=False, col='tab:blue', lab='PP'):
+    xs = np.linspace(-1, 1, 1000)
+    _data = dd.io.load(paths.data / fi)
+    lines = dict()
+    for key in _data["lines"].keys():
+        lines[key] = _data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    if ct1:
+        med = np.median(lines['cos_tilt_1'], axis=0)
+        low = np.percentile(lines['cos_tilt_1'], 5, axis=0)
+        high = np.percentile(lines['cos_tilt_1'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high, color='k', lw=0.1, alpha=0.1)#, label=lab)
+    else:
+        med = np.median(lines['cos_tilt_2'], axis=0)
+        low = np.percentile(lines['cos_tilt_2'], 5, axis=0)
+        high = np.percentile(lines['cos_tilt_2'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high, color='k', lw=0.1, alpha=0.1)
+    return ax
+
+figx, figy = 7, 5
+fig, axs = plt.subplots(nrows=1, ncols=1, figsize=(figx,figy))
+
+xmin, xmax = -1, 1
[…]

### 2022-09-22 src/scripts/plot_ind_spinmag.py

@@ -1,0 +1,76 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+def load_mag_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_60m1_12ind_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['dRda1'], datadict['dRda2'], datadict['mags'], datadict['mags']
+
+def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
+    xs = np.linspace(0, 1, 1000)
+    
+    _data = dd.io.load(paths.data / fi)
+    lines = dict()
+    for key in _data["lines"].keys():
+        lines[key] = _data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    if a1:
+        med = np.median(lines['a_1'], axis=0)
+        low = np.percentile(lines['a_1'], 5, axis=0)
+        high = np.percentile(lines['a_1'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high, color='k', lw=0.1, alpha=0.1)#, label=lab)
+    else:
+        med = np.median(lines['a_2'], axis=0)
+        low = np.percentile(lines['a_2'], 5, axis=0)
+        high = np.percentile(lines['a_2'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high, color='k', lw=0.1, alpha=0.1)
+    return ax
+
+figx, figy = 7, 5
+fig, ax = plt.subplots(nrows=1, ncols=1, sharey='row', sharex='row', figsize=(figx,figy))
+
+xmin, xmax = 0, 1
[…]

### 2022-09-22 src/scripts/plot_ind_spintilt.py

@@ -1,0 +1,75 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+def load_tilt_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_60m1_12ind_compspins_powerlaw_q_z_ppds.h5')
+    return datadict['dRdct1'], datadict['dRdct2'], datadict['tilts'], datadict['tilts']
+
+def plot_o3b_spintilt(ax, fi,ct1=False, col='tab:blue', lab='PP'):
+    xs = np.linspace(-1, 1, 1000)
+    _data = dd.io.load(paths.data / fi)
+    lines = dict()
+    for key in _data["lines"].keys():
+        lines[key] = _data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    if ct1:
+        med = np.median(lines['cos_tilt_1'], axis=0)
+        low = np.percentile(lines['cos_tilt_1'], 5, axis=0)
+        high = np.percentile(lines['cos_tilt_1'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high,  color='k', lw=0.1, alpha=0.1)#, label=lab)
+    else:
+        med = np.median(lines['cos_tilt_2'], axis=0)
+        low = np.percentile(lines['cos_tilt_2'], 5, axis=0)
+        high = np.percentile(lines['cos_tilt_2'], 95, axis=0)
+        ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
+        ax.fill_between(xs, low, high, color=col, alpha=0.3)
+        ax.plot(xs, low, color='k', lw=0.1, alpha=0.1)#, label=lab)
+        ax.plot(xs, high, color='k', lw=0.1, alpha=0.1)
+    return ax
+
+figx, figy = 7,5
[…]

### 2022-09-24 src/scripts/create_chieff_from_compspin.py
add chi eff plot

@@ -1,0 +1,157 @@
+import numpy as np
+import jax.numpy as jnp
+from scipy.stats import gaussian_kde
+from gwpopulation.cupy_utils import trapz
+from gwpopulation.conversions import convert_to_beta_parameters
+from gwpopulation.models.mass import SinglePeakSmoothedMassDistribution
+from gwpopulation.models.spin import iid_spin_orientation_gaussian_isotropic, iid_spin_magnitude_beta
+from bilby.core.result import read_in_result
+from bilby.hyper.model import Model
+from jax import jit
+from utils import MSplineIndependentSpinTilts, MSplineIndependentSpinMagnitudes, MSplinePrimaryPowerlawRatio
+import deepdish as dd
+from tqdm import trange
+import paths
+import warnings
+warnings.filterwarnings('ignore')
+
+
+def draw_chieff_samples_gwpop(result, magmodel, tiltmodel, massmodel, ndraws=500, nsamples=2000):
+    mags = np.linspace(0,1,2000)
+    a1s, a2s = np.meshgrid(mags, mags)
+    m1s = np.linspace(2,100,200)
+    qs = np.linspace(0.05, 1, 2000)
+    mms, qqs = np.meshgrid(m1s, qs)
+    ctilts = np.linspace(-1,1,2000)
+    ct1s, ct2s = np.meshgrid(ctilts, ctilts)
+    
+    magdata = {'a_1': a1s, 'a_2': a2s}
+    tiltdata = {'cos_tilt_1': ct1s, 'cos_tilt_2': ct2s}
+    massdata = {'mass_1': mms, 'mass_ratio': qqs}
+    
+    samples = {'a_1': np.empty((ndraws, nsamples)), 'a_2': np.empty((ndraws, nsamples)), 'cos_tilt_1': np.empty((ndraws, nsamples)),
+               'cos_tilt_2': np.empty((ndraws, nsamples)), 'mass_1': np.empty((ndraws, nsamples)), 'mass_ratio': np.empty((ndraws, nsamples))}
+    
+    idxs = np.random.choice(len(result.posterior), size=ndraws, replace=False)
+
+    for i in trange(ndraws):
+        samp  = result.posterior.iloc[idxs[i]]
+        if 'mu_chi' in samp:
+            samp, _ = convert_to_beta_parameters(samp)
[…]

### 2022-09-24 src/scripts/plot_chieff.py
add chi eff plot

@@ -2,3 +2,61 @@ import paths
 import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
+
+fig, ax = plt.subplots(1,1,figsize=(7,5))
+ppds = dd.io.load(paths.data / "chi_eff_ppds.h5")
+default = ppds["Default"]
+mspl = ppds["MSplineInd"]
+plt.plot(
+    default["chieffs"],
+    np.median(default["pchieff"], axis=0),
+    lw=2,
+    color="tab:blue",
+    label="Default",
+)
+plt.fill_between(
+    default["chieffs"],
+    *np.percentile(default["pchieff"], (5, 95), axis=0),
+    color="tab:blue",
+    alpha=0.15,
+)
+plt.plot(
+    mspl["chieffs"],
+    np.median(mspl["pchieff"], axis=0),
+    lw=2,
+    color="tab:purple",
+    label="MSpline Ind Spins",
+)
+plt.fill_between(
+    mspl["chieffs"],
+    *np.percentile(mspl["pchieff"], (5, 95), axis=0),
+    color="tab:purple",
+    alpha=0.15,
+)
+handpicked_ppds = dd.io.load(
+    paths.data / "mspline_60m1_handpicked_27chieff_powerlaw_q_z_fitlamb_ppds.h5"
+)
+xs = handpicked_ppds["chieffs"]
+pchiefss = handpicked_ppds["dRdchieff"]
+for i in range(1500):
+    norm = np.trapz(pchiefss[i, :], x=xs)
+    pchiefss[i, :] /= norm
+plt.plot(
+    xs,
+    np.median(pchiefss, axis=0),
+    lw=2,
+    color="tab:red",
+    label="MSpline Chi Effective",
+)
+plt.fill_between(
+    xs, *np.percentile(pchiefss, (5, 95), axis=0), color="tab:red", alpha=0.15
+)
+plt.xlim(-0.75, 0.5)
+plt.ylim(0, 6.5)
+plt.legend(frameon=False, fontsize=14)
+ax.grid(True, which="major", ls=":")
+ax.tick_params(labelsize=14)
+plt.xlabel(r"$\chi_\mathrm{eff}$", fontsize=18)
+plt.ylabel(r"$p(\chi_\mathrm{eff})$", fontsize=18)
+plt.title(f"GWTC-3: Effective Spin Distribution", fontsize=18)
+plt.savefig(paths.figures / "chi_eff.pdf", dpi=300)

### 2022-09-24 src/scripts/utils.py

@@ -1,8 +1,22 @@
 import numpy as np
+import jax.numpy as jnp
 
 
 HARDCODED_CHIEFF_KNOTS = np.array([-1.4, -1.2, -1.0, -0.8, -0.6, -0.5, -0.4, -0.32, -0.25, -0.19, -0.14, -0.1, -0.07, -0.05, -0.025, 
                    0.0, 0.025, 0.05, 0.07, 0.1, 0.14, 0.19, 0.25, 0.32, 0.4, 0.5, 0.6, 0.8, 1.0, 1.2, 1.4])
+
+
+def powerlaw_pdf(xx, alpha, low, high):
+    """
+    $$ p(x) \propto x^{\alpha}\Theta(x-x_\mathrm{min})\Theta(x_\mathrm{max}-x) $$
+    """
+    prob = jnp.power(xx, alpha)
+    norm = jnp.where(
+        jnp.equal(alpha, -1.0),
+        1.0 / jnp.log(high / low),
+        (1.0 + alpha) / (jnp.power(high, 1.0 + alpha) - jnp.power(low, 1.0 + alpha)),
+    )
+    return jnp.where(jnp.greater(xx, high) | jnp.less(xx, low), 0.0, prob * norm)
 
 
 class MSpline(object):
@@ -52,3 +66,339 @@ class MSpline(object):
 
     def __call__(self, xs):
         return np.concatenate(self.basis(xs)).reshape(self.N, *xs.shape)
+
+
+class Base1DMSplineModel(object):
+    def __init__(
+        self,
+        nknots,
+        xx,
+        xx_inj,
+        knots=None,
+        interior_knots=None,
+        xrange=(0, 1),
+        order=3,
+        prefix="c",
+        domain="x",
+        basis=MSpline,
+    ):
+        self.nknots = nknots
+        self.domain = domain
+        self.xmin, self.xmax = xrange
+        self.order = order
+        self.prefix = prefix
+        self.interpolator = basis(
+            nknots,
+            knots=knots,
+            interior_knots=interior_knots,
+            xrange=xrange,
+            k=order + 1,
+        )
+        self.variable_names = [f"{self.prefix}{i}" for i in range(self.nknots)]
+        self.pe_design_matrix = jnp.array(self.interpolator(xx))
+        self.inj_design_matrix = jnp.array(self.interpolator(xx_inj))
+        self.funcs = [self.inj_pdf, self.pe_pdf]
+        self.grid = jnp.linspace(*xrange, 2500)
[…]

### 2022-09-25 src/tex/ms.tex
update with macros etc

@@
 \newcommand{\NewChange}[1]{\textcolor{green}{#1}}
+
+\newcommand{\CIPlusMinus}[1]{{#1[median]^{+#1[error plus]}_{-#1[error minus]}}}
+\newcommand{\CIBoundsBracket}[1]{{[#1[5th percentile], #1[95th percentile]]}}
+\newcommand{\CIBoundsDash}[1]{{#1[5th percentile]\textendash#1[95th percentile]}}
 
@@
 \usepackage{appendix}
+\input{macros}
+
 \definecolor{Gray}{gray}{0.9}
@@
 
+\author{Jaxen Godfrey}
+\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
+
+\author{Alexis Vives}
+\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
+
 \author{Jon Hornung}
@@
 zero spinning sub population we do find that the data prefer not to force the support for exactly zero spinning black holes to 0 as 
-the non-singular Beta distribution and \textsc{Default} model assumes. 
+the non-singular Beta distribution and \textsc{Default} model assumes. \result{$\CIPlusMinus{\macros[MSPlineIIDCompSpins][peakCosTilt]}$}
+\result{$\CIPlusMinus{\macros[MSPlineIndependentCompSpins][peakCosTilt1]}$}, \result{$\CIPlusMinus{\macros[MSPlineIndependentCompSpins][peakCosTilt2]}$}
 \end{abstract}
@@
 \section{Acknowledgements}\label{sec:acknowledments}
-We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful and discussions during the preparation this manuscript, 
+We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful discussions during the preparation this manuscript, 
 along with helpful comments on an early draft by Tom Callister.

### 2022-09-25 src/scripts/create_macros.py

@@ -1,0 +1,46 @@
+#!/usr/bin/env python
+
+import json2latex
+import paths
+import deepdish as dd
+import numpy as np
+
+def load_tilt_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_ppds.h5')
+    return datadict['tilts'], datadict['dRdct']
+
+def load_ind_tilt_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_50m1_16ind_compspins_smoothprior_powerlaw_q_z_ppds.h5')
+    return datadict['tilts'], datadict['dRdct1'], datadict['dRdct2']
+
+def save_param_cred_intervals(param_data):
+    return  {'median': "{:.2f}".format(np.median(param_data)), 
+             'error plus': "{:.2f}".format(np.percentile(param_data, 95)-np.mean(param_data)), 
+             'error minus': "{:.2f}".format(np.median(param_data)-np.percentile(param_data, 5)),
+             '5th percentile': "{:.2f}".format(np.percentile(param_data, 5)), 
+             '95th percentile': "{:.2f}".format(np.percentile(param_data, 95))}
+
+macro_dict = {}
+print("Saving MSpline IID Component Spin macros...")
+xs, ct_pdfs = load_tilt_ppd()
+peak_tilts = []
+for jj in range(len(ct_pdfs)):
+    peak_tilts.append(xs[np.argmax(ct_pdfs[jj,:])])
+peak_tilts = np.array(peak_tilts)
+macro_dict['MSPlineIIDCompSpins'] = {'peakCosTilt': save_param_cred_intervals(peak_tilts)}
+
+print("Saving MSpline Independent Component Spin macros...")
+xs, ct1_pdfs, ct2_pdfs = load_ind_tilt_ppd()
+peak_tilts1 = []
+peak_tilts2 = []
+for jj in range(len(ct1_pdfs)):
+    peak_tilts1.append(xs[np.argmax(ct1_pdfs[jj,:])])
+    peak_tilts2.append(xs[np.argmax(ct2_pdfs[jj,:])])
+peak_tilts1 = np.array(peak_tilts1)
+peak_tilts2 = np.array(peak_tilts2)
+macro_dict['MSPlineIndependentCompSpins'] = {'peakCosTilt1': save_param_cred_intervals(peak_tilts1)}
[…]

### 2022-09-25 src/scripts/plot_iid_spintilt.py

@@ -43,11 +43,11 @@ def plot_o3b_spintilt(ax, fi,ct1=False, col='tab:blue', lab='PP'):
 
 figx, figy = 7, 5
 fig, axs = plt.subplots(nrows=1, ncols=1, figsize=(figx,figy))
-
 xmin, xmax = -1, 1
 xs, ct_pdfs = load_tilt_ppd()
 for jj in range(len(ct_pdfs)):
     ct_pdfs[jj,:] /= np.trapz(ct_pdfs[jj,:], xs)
+
 xmin=-1
 ax = axs
 ax = plot_o3b_spintilt(ax,'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_orientation_data.h5', ct1=True, lab='Default', col='tab:blue')

### 2022-09-25 src/scripts/utils.py

@@ -1,5 +1,16 @@
 import numpy as np
 import jax.numpy as jnp
+import paths
+import json
+
+
+def save_macro(subdict):
+    with open(paths.data / "macros.json", 'r') as f:
+        old_macro = json.load(f)
+    new_macro = old_macro.copy()
+    new_macro.update(subdict)
+    with open(paths.data / "macros.json", 'w') as f:
+        json.dump(new_macro, f)
 
 
 def powerlaw_pdf(xx, alpha, low, high):

### 2022-09-25 src/tex/macros.tex
macro infra (I promise I am not procrastinating)

\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"MSplineIIDCompSpins": \{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "MSplineIndependentCompSpins": \{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}\}}\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\def\macros@out{??}\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@I@out\macros@III\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@I@out\macros@IV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@I@out\macros@V\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@VI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@VII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@III@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@III@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@III@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@III@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@III@out{1.00}\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IV@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IV@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IV@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IV@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IV@out{0.96}\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@V@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@V@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@V@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@V@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@V@out{0.47}\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{0.89}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{1.00}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{0.84}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.99}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.62}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.57}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\makeatother

### 2022-09-25 src/tex/ms.tex
macro infra (I promise I am not procrastinating)

@@
 zero spinning sub population we do find that the data prefer not to force the support for exactly zero spinning black holes to 0 as 
-the non-singular Beta distribution and \textsc{Default} model assumes. \result{$\CIPlusMinus{\macros[MSPlineIIDCompSpins][peakCosTilt]}$}
-\result{$\CIPlusMinus{\macros[MSPlineIndependentCompSpins][peakCosTilt1]}$}, \result{$\CIPlusMinus{\macros[MSPlineIndependentCompSpins][peakCosTilt2]}$}
+the non-singular Beta distribution and \textsc{Default} model assumes. MSpline IID:
+$\cos{\theta}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}
+$\gamma = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}
+$f_{<0} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}
+MSpline Independent:
+$\cos{\theta_1}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$} and $\cos{\theta_2}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}
+$\gamma_1 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and $\gamma_2 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$} 
+$f_{1,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}
 \end{abstract}

### 2022-09-25 src/scripts/create_macros.py

@@ -1,6 +1,7 @@
 #!/usr/bin/env python
 
 import json2latex
+import json
 import paths
 import deepdish as dd
 import numpy as np
@@ -24,23 +25,57 @@ macro_dict = {}
 print("Saving MSpline IID Component Spin macros...")
 xs, ct_pdfs = load_tilt_ppd()
 peak_tilts = []
+gamma_fracs = []
+frac_neg_cts = []
 for jj in range(len(ct_pdfs)):
+    ct_pdfs[jj,:] /= np.trapz(ct_pdfs[jj,:], xs)
     peak_tilts.append(xs[np.argmax(ct_pdfs[jj,:])])
+    gam = ct_pdfs[jj,xs>=0.9] / ct_pdfs[jj, xs<=-0.9]
+    gamma_fracs.append(gam)
+    neg = xs <= 0
+    frac_neg_cts.append(np.trapz(ct_pdfs[jj,neg], x=xs[neg]))
 peak_tilts = np.array(peak_tilts)
-macro_dict['MSPlineIIDCompSpins'] = {'peakCosTilt': save_param_cred_intervals(peak_tilts)}
+gamma_fracs = np.array(gamma_fracs)
+frac_neg_cts = np.array(frac_neg_cts)
+macro_dict['MSplineIIDCompSpins'] = {'peakCosTilt': save_param_cred_intervals(peak_tilts), 
+                                     'log10gammaFrac': save_param_cred_intervals(np.log10(gamma_fracs)), 
+                                     'negFrac': save_param_cred_intervals(frac_neg_cts)}
 
 print("Saving MSpline Independent Component Spin macros...")
 xs, ct1_pdfs, ct2_pdfs = load_ind_tilt_ppd()
 peak_tilts1 = []
 peak_tilts2 = []
+gamma_fracs1 = []
+gamma_fracs2 = []
+frac_neg_cts1 = []
+frac_neg_cts2 = []
 for jj in range(len(ct1_pdfs)):
+    ct1_pdfs[jj,:] /= np.trapz(ct1_pdfs[jj,:], xs)
+    ct2_pdfs[jj,:] /= np.trapz(ct2_pdfs[jj,:], xs)
     peak_tilts1.append(xs[np.argmax(ct1_pdfs[jj,:])])
     peak_tilts2.append(xs[np.argmax(ct2_pdfs[jj,:])])
[…]

### 2022-09-25 src/tex/methods.tex
methods.tex is mostly finished but w/o citations

@@
 
-A common non-parametric method in statistical applications is the use of basis splines. A spline function of order $k$, 
+A common non-parametric method in statistical applications is the use of basis splines \bruce{cite}. A spline function of order $k$, 
 is a piece-wise polynomial of order $k$ polynomials stitched together from defined ``knot'' locations across the domain. 
@@
 every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines basis components for a given knot vector 
-using the Cox-de Boor recursion formula. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:
+using the Cox-de Boor recursion formula \bruce{cite}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:
 
@@
 
+\noindent allowing one to build a basis of $i$ components that spans the vector space of order-$k$ spline functions interpolated 
+from this knot vector. This is known as the ``B-Spline'' basis after it's inventor de Boor \bruce{cite}. The power of basis splines
+comes from the fact that you only have to do a somewhat expensive interpolation once for each set of points you want to evaluate your
+spline functions at. This allows for much quicker evaluation time rather than having to re-do a \bruce{Is this right???} $\mathcal{O}(n^2)$
+operation one can do a simple dot product of 2d matrix and 1d vector which is easily  $\mathcal{O}(n)$. This means it is much more feasible 
+to use large numbers of knots and GPU calculations for expensive markov chain monte carlo (MCMC) based analyses.
+
+A similar basis, the M-Spline basis \bruce{cite}, has desirable properties when looking to model a probability density function, which is the 
+goal of population inference. Namely, $M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. We now have
+a useful basis that can represent all spline functions that are probability density functions given our array of knots. The M-Spline basis differs 
+from B-Splines by the normalization factor:
+
+\begin{equation}\label{eq:MB_SplineRelation}
+M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
+\end{equation}
+
 \begin{figure}[ht!]
@@
 
-\noindent allowing one to build a basis of $i$ components that spans the vector space of order-$k$ spline functions interpolated 
-from this knot vector. This is known as the ``B-Spline'' basis.
-
-A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function. Namely, 
-$M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. The M-Spline basis only differs 
-from B-Splines by a normalization factor, namely:
-
-\begin{equation}\label{eq:MB_SplineRelation}
-M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
-\end{equation}
-
 \noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper. 
+Figure \ref{fig:spline_basis} shows an example of a 3rd order M-Spline basis with 20 degrees of freedom and knots linearly spaced from 0 to 1.
+Another important feature of basis splines is that under appropiate prior conditions, one can alleviate sensitivities to arbitrarily 
+chosen prior specifications that splines commonly struggle with. We look to the use of penalized splines or P-Splines \bruce{cite P-splines}, 
+that adds a smoothing penalty (or prior) based on the difference of basis spline coeficients. This allows one to much more denseley populate
+the domain with knots without the worry of extra variance in the inferred spline functions. We discuss the details of this smoothing prior 
+in Appendix \ref{sec:psplines}.
 
@@
 \bruce{placeholder paragraph here to introduce our model constructions.}
-We use hierarchical Bayesian inference to simultaneosly infer the mass, spin and redshift distributions of binary black holes (BBHs) using 
-the 69 confident BBH detections reported in the recent LVK catalog of observations, GWTC-3. In particular we choose to parameterize the two
-masses with the primary (more massive component) mass and the mass ratio defined as $q=\frac{m_2}{m_1}$. We choose to model 4 of the 6 total 
-spin degrees of freedom of a binary merger with each component spin magnitude, and the cosine of the tilt angle which is defined as the angle 
-between each spin vector and the binaries orbital angular mommentum vector. We additionally will fit a population model on the redshift distribution
-of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology defined by the Planck 2015 results, which defines an analytical mapping between each event's inferred
-luminosity distance and it's redshift. While we choose to use MSpline distibutions for the masses and spins, we use the canonical \textsc{PowrerlawRedshift}
-model describing the evolution of CBC merger rates as a power law in $(1+z)$ with a slope of $\lambda_z$. The corresponsing distribution is Thus
-desribed by $p(z|\lambda)\propto \frac{dV_c}{dz} \frac{T_\mathrm{obs}}{1+z} (1+z)^\lambda$. We model the spin magnitude and tilt distibutions to be 
-described by independent MSpline distributions for each component.
+We use hierarchical Bayesian inference to simultaneosly infer the astrophysical mass, spin and redshift distributions of 
+a binary black holes (BBHs) given a catalog of gravitational wave observations. See Appendix \ref{sec:hierarchical_inference} for a detailed 
+description of the analysis framework. We choose to parameterize the binaries' masses with the primary (defined as the more massive component) mass 
+and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. We choose to model 4 of the 6 total 
+spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
+$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular mommentum vector. 
+We additionally will fit a population model on the redshift or luminosity distance distribution of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology using the 
+parameters from the Planck 2015 results \bruce{cite here}, which defines an analytical mapping between each event's inferred
+luminosity distance and it's redshift. While we choose to use MSpline distibutions for the primary mass and spin distributions, we 
+model the mass ratio distribution with a power law , i.e. $p(q | m_1, m_\mathrm{min}, \beta_q) \propto q^{\beta_q} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$. 
+Where $\Theta$ is the Heaviside step function that ensures $m_2$ is within the range [$m_\mathrm{min}$, $m_1$].
+We model the evolution of the merger rate with redshift with the \textsc{PowrerlawRedshift} \bruce{cite mayas paper} model, which is desribed by 
+$p(z|\lambda_z)\propto \frac{dV_c}{dz} \frac{T_\mathrm{obs}}{1+z} (1+z)^\lambda_z$. We describe our specific prior choices on the hyper-parameters and each model 
+in more detail in Appendix \ref{sec:modelpriors}.

### 2022-09-25 src/tex/appendicies.tex
methods.tex is mostly finished but w/o citations
cleanup more of appendices/methods

--- 2022-09-14 src/tex/appendicies.tex
@@
 We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
-their respective hyper-parameters and prior distributions in the next section. To calculate marginal likelihoods and draw 
+their respective hyper-parameters and prior distributions in the next section. To calculate draw 
 samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
-\textsc{Bilby} \citep{Ashton_2019, bilby_gwtc1} and \textsc{GWPopulation} \citep{Talbot_2019} Bayesian inference software libraries with 
-the \textsc{Dynesty} dynamic nested sampling algorithm \citep{Speagle_2020}. We also make use of the hamiltonian monte carlo algorithms in 
-\textsc{numpyro} and use \textsc{jax} to calculate our likelihoods \bruce{FIND citations for these}.
+NUTS hamiltonian monte carlo sampler in \textsc{numpyro} and \textsc{jax} to calculate likelihoods \bruce{FIND citations for these}.
 
-\section{Models and Hyper-Parameters} \label{sec:hypparams}
+\section{Penalized Splines and Smoothing}\label{sec:psplines}
+
+Spline functions have been shown to be sensitivite to the chosen number of knots, and their locations or spacing. 
+Adding more knots knots increases the a-priori variance in the spline function, while the space between knots can limit the 
+resolution of features in the data the spline is capable of resolving. To ensure your spline based model is flexible enough 
+one would want to add as many knots as densely as possible, but this comes with the inherit larger variance as mentioned above. 
+To overcome this we resort to the frequentist penalized spline (P-Spline) in which one applies a penalty or regularization term 
+to the likelihood based on the difference of adjacent knot coeficients. The linear combination of spline basis components is 
+is flat when the basis coeficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as the differences between adjacent
+knot coeficients get larger, one gets a smoothing of the spline function inferences. Since we are using hierarchical Bayesian inferece as our 
+statistical framework, we formulate this penalized likelihood with its Bayesian analog. The difference penalty is equivalent to applying a stochastic 
+differnece prior among the knots, as described in \bruce{CITE THIS PAPER}. This is also sometimes referred to as a Gaussian random walk prior, since
+each coeficient is normally distributed about its neighboring coeficients. We then use as our smoothing prior, for a spline basis with $n$ degree's of freedom
+, and a difference order of $r$ in our smoothing penalty (see \bruce{cite P-splines paper}) is defined as:
+
+\begin{eqnarray}
+\tau_\lambda \sim \Gamma(a, b), \\
+p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
+\end{eqnarray}
+
+\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $a$, $b$, shape parameters for the Gamma distribution. 
+This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a very large number 
+of knots such that your domain is densly populated with basis coeficients, this allows the freedom for the model to find the smoothing 
+scale that the data prefers. One downside of this prior specification as noted by\ bruce{CITE BAYESIAN PSPLINES}, is a slight dependence on choice 
+of the b hyper-parameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \bruce{CITE BAYESIAN PSPLINES} 
+to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyper-parameters. 
+We now replace the prior on $\tau_\lambda$ with:
+
+\begin{align}
+    \bm{p} \sim \mathcal{D}(m), \\
+    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
+\end{align}
+
+%Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
+%that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
+%across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
+%effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:
+
+%\begin{eqnarray}
+%\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
+%\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
+%p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c} \big] e^{-n\bm{c}}
+%\end{eqnarray}
+
+%Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
+%prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
+%across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
+%the power-law like mass distributions that are commonly used.
+
+Since the smoothing prior is really wanting to pull the coeficients closer to each other to smooth the distribution, 
+we must ensure that the spline function is in fact flat or smooth with all equal coeficients. Often times one would stack knots at the same values 
+at hard parameter boundaries but this removes the feature that with equal weights the spline function is flat. We follow the distinction from \bruce{CITE psplines} 
+that the difference penalty or prior is only valid with ``proper'' spline bases. A proper basis is where all of the knots are evenly spaced, see Figure \ref{fig:spline_basis}.
+
+\section{Model specification} \label{sec:modelpriors}
 

### 2022-09-25 src/scripts/spline_basis_plot.py

@@ -6,7 +6,7 @@ import matplotlib.pyplot as plt
 from utils import MSpline
 
 ndof = 20
-k = 3
+k = 4
 xmin = 0
 xmax = 1
 xlab = 'x'
@@ -57,11 +57,11 @@ max_col = 6
 ncol = max([leg_item // max_col, 3])
 axs.legend(loc='upper center', fancybox=True, shadow=True, ncol=ncol, fontsize=16)
 axs.set_xlim(0,1)
-axs.set_ylim(0, 1.5)
+axs.set_ylim(0, 1.45)
 axs.set_xlabel(xlab, fontsize=18)
 axs.grid(True, which="major", ls=":")
 axs.set_ylabel(f'p({xlab})', fontsize=18)
 axs.tick_params(labelsize=14)
-plt.title(f'MSpline Basis: k={k-1}, n={ndof}, from {xlab}=[{xmin}, {xmax}]', fontsize=16)
+plt.title(f'MSpline Basis: k={k-1}, n={ndof}', fontsize=16)
 fig.tight_layout()
 plt.savefig(paths.figures / 'spline_basis_plot.pdf', dpi=300)

### 2022-09-25 src/tex/appendicies.tex
one last update to appendicies??? before citations of course.

@@
 \begin{eqnarray}
-\tau_\lambda \sim \Gamma(a, b), \\
+\tau_\lambda \propto \Gamma(a, b) \\
 p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
@@
 
-\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $a$, $b$, shape parameters for the Gamma distribution. 
+\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $\Gamma(a,b)$ the Gamma distribution with shape parameters, $a$ and $b$. 
 This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a very large number 
@@
 \begin{align}
-    \bm{p} \sim \mathcal{D}(m), \\
-    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \mathcal{G}(1, b_m)
+    \bm{p} \propto \mathcal{D}(m) \\
+    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_m)
 \end{align}
+
+\noindent Where above $\mathcal{D}(m)$ is a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
+and $b_m$ is an array of $m$ different b shape parameters for the Gamma distribution.
 

### 2022-09-25 src/tex/appendicies.tex
make plots prettier / less cluttery

@@
 \begin{eqnarray}
-\tau_\lambda \propto \Gamma(a, b) \\
+\tau_\lambda \sim \Gamma(a, b) \\
 p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
@@
 \begin{align}
-    \bm{p} \propto \mathcal{D}(m) \\
-    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_m)
+    \bm{p} \sim \mathcal{D}(m) \\
+    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_i)
 \end{align}
@@
 \noindent Where above $\mathcal{D}(m)$ is a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
-and $b_m$ is an array of $m$ different b shape parameters for the Gamma distribution.
+and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.
 

### 2022-09-25 src/scripts/mass_distribution_plot.py

@@ -4,11 +4,27 @@ import paths
 import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
+from utils import plot_mean_and_90CI
+from matplotlib.ticker import ScalarFormatter
+
 
 def load_ppd():
     datadict = dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_ppds.h5')
     return datadict['m1s'], datadict['dRdm1'], datadict['qs'], datadict['dRdq']
 
+
+def load_o3b_paper_run_m1ppd(filename):
+    mass_1 = np.linspace(2, 100, 1000)
+    mass_ratio = np.linspace(0.1, 1, 500)
+    # load in the traces. 
+    # Each entry in lines is p(m1 | Lambda_i) or p(q | Lambda_i)
+    # where Lambda_i is a single draw from the hyperposterior
+    # The ppd is a 2D object defined in m1 and q
+    with open(filename, 'r') as _data:
+        _data = dd.io.load(filename)
+        ppd = _data["ppd"]
+    m1ppd = np.trapz(ppd, x=mass_ratio, axis=0)
+    return mass_1, m1ppd / np.trapz(m1ppd, x=mass_1)
 
 def load_o3b_paper_run_masspdf(filename):
     """
@@ -30,32 +46,17 @@ def load_o3b_paper_run_masspdf(filename):
         marginals['mass_ratio'][ii] /= np.trapz(marginals['mass_ratio'][ii], mass_ratio)
     return marginals['mass_1'], marginals['mass_ratio'], mass_1, mass_ratio
 
+def plot_o3b_m1_ppd(ax, fi, col='tab:blue', lab='PLPeak'):
+    ms, ppd = load_o3b_paper_run_m1ppd(paths.data / fi)
+    ax.plot(ms, ppd, color=col, label=lab, alpha=0.75, lw=4)
+    return ax
 
-def plot_o3b_res(ax, fi, m1=False, col='tab:blue', lab='PP'):
+def plot_o3b_res(ax, fi, m1=True, col='tab:blue', lab='PP', bounds=False):
     plpeak_mpdfs, plpeak_qpdfs, plpeak_ms, plpeak_qs = load_o3b_paper_run_masspdf(paths.data / fi)
     if m1:
[…]

### 2022-09-25 src/scripts/plot_chieff.py

@@ -2,37 +2,14 @@ import paths
 import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
+from utils import plot_mean_and_90CI
 
 fig, ax = plt.subplots(1,1,figsize=(7,5))
 ppds = dd.io.load(paths.data / "chi_eff_ppds.h5")
 default = ppds["Default"]
 mspl = ppds["MSplineInd"]
-plt.plot(
-    default["chieffs"],
-    np.median(default["pchieff"], axis=0),
-    lw=2,
-    color="tab:blue",
-    label="Default",
-)
-plt.fill_between(
-    default["chieffs"],
-    *np.percentile(default["pchieff"], (5, 95), axis=0),
-    color="tab:blue",
-    alpha=0.15,
-)
-plt.plot(
-    mspl["chieffs"],
-    np.median(mspl["pchieff"], axis=0),
-    lw=2,
-    color="tab:purple",
-    label="MSpline Ind Spins",
-)
-plt.fill_between(
-    mspl["chieffs"],
-    *np.percentile(mspl["pchieff"], (5, 95), axis=0),
-    color="tab:purple",
-    alpha=0.15,
-)
+ax = plot_mean_and_90CI(ax, default["chieffs"], default["pchieff"], color='tab:blue', label='Default', bounds=False)
+ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:purple', label='MSpline Ind Spin', bounds=False)
 handpicked_ppds = dd.io.load(
     paths.data / "mspline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5"
 )
@@ -41,16 +18,7 @@ pchiefss = handpicked_ppds["dRdchieff"]
 for i in range(1500):
     norm = np.trapz(pchiefss[i, :], x=xs)
     pchiefss[i, :] /= norm
-plt.plot(
-    xs,
-    np.median(pchiefss, axis=0),
-    lw=2,
-    color="tab:red",
-    label="MSpline Chi Effective",
-)
-plt.fill_between(
-    xs, *np.percentile(pchiefss, (5, 95), axis=0), color="tab:red", alpha=0.15
-)
+ax = plot_mean_and_90CI(ax, xs, pchiefss, color='tab:red', label='MSpline Chi Eff')
 plt.xlim(-0.75, 0.5)
 plt.ylim(0, 6.5)
 plt.legend(frameon=False, fontsize=14)

### 2022-09-25 src/scripts/plot_iid_spinmag.py

@@ -4,14 +4,14 @@ import paths
 import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
+from utils import plot_mean_and_90CI
 
 def load_mag_ppd():
     datadict = dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_ppds.h5')
     return datadict['mags'], datadict['dRda']
 
-def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
+def plot_o3b_spinmag(ax, fi, a1=True, col='tab:blue', lab='PP'):
     xs = np.linspace(0, 1, 1000)
-    
     _data = dd.io.load(paths.data / fi)
     lines = dict()
     for key in _data["lines"].keys():
@@ -19,27 +19,9 @@ def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
         for ii in range(len(lines[key])):
             lines[key][ii] /= np.trapz(lines[key][ii], xs)
     if a1:
-        low = np.percentile(lines['a_1'], 35, axis=0)
-        high = np.percentile(lines['a_1'], 65, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.5, label=lab)
-        ax.plot(xs, low, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        low = np.percentile(lines['a_1'], 5, axis=0)
-        high = np.percentile(lines['a_1'], 95, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.1)
-        ax.plot(xs, low, color='k', lw=0.05, alpha=0.05)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.05, alpha=0.05)#, label=lab)
+        ax = plot_mean_and_90CI(ax, xs, lines['a_1'], color=col, label=lab, bounds=False)
     else:
-        low = np.percentile(lines['a_2'], 35, axis=0)
-        high = np.percentile(lines['a_2'], 65, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.5, label=lab)
[…]

### 2022-09-25 src/scripts/plot_iid_spintilt.py

@@ -4,6 +4,7 @@ import paths
 import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
+from utils import plot_mean_and_90CI
 
 def load_tilt_ppd():
     datadict = dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_ppds.h5')
@@ -18,27 +19,9 @@ def plot_o3b_spintilt(ax, fi,ct1=False, col='tab:blue', lab='PP'):
         for ii in range(len(lines[key])):
             lines[key][ii] /= np.trapz(lines[key][ii], xs)
     if ct1:
-        low = np.percentile(lines['cos_tilt_1'], 35, axis=0)
-        high = np.percentile(lines['cos_tilt_1'], 65, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.5, label=lab)
-        ax.plot(xs, low, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        low = np.percentile(lines['cos_tilt_1'], 5, axis=0)
-        high = np.percentile(lines['cos_tilt_1'], 95, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.1)
-        ax.plot(xs, low, color='k', lw=0.05, alpha=0.05)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.05, alpha=0.05)#, label=lab)
+        ax = plot_mean_and_90CI(ax, xs, lines['cos_tilt_1'], color=col, label=lab, bounds=False)
     else:
-        low = np.percentile(lines['cos_tilt_2'], 35, axis=0)
-        high = np.percentile(lines['cos_tilt_2'], 65, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.5, label=lab)
-        ax.plot(xs, low, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.25, alpha=0.1)
-        low = np.percentile(lines['cos_tilt_2'], 5, axis=0)
-        high = np.percentile(lines['cos_tilt_2'], 95, axis=0)
[…]

### 2022-09-25 src/scripts/plot_ind_spinmag.py

@@ -4,14 +4,16 @@ import paths
 import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
+from utils import plot_mean_and_90CI
+
 
 def load_mag_ppd():
     datadict = dd.io.load(paths.data / 'mspline_50m1_16ind_compspins_smoothprior_powerlaw_q_z_ppds.h5')
     return datadict['dRda1'], datadict['dRda2'], datadict['mags'], datadict['mags']
 
-def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
+
+def plot_o3b_spinmag(ax, fi, a1=True, col='tab:blue', lab='PP'):
     xs = np.linspace(0, 1, 1000)
-    
     _data = dd.io.load(paths.data / fi)
     lines = dict()
     for key in _data["lines"].keys():
@@ -19,27 +21,9 @@ def plot_o3b_spinmag(ax, fi, a1=False, col='tab:blue', lab='PP'):
         for ii in range(len(lines[key])):
             lines[key][ii] /= np.trapz(lines[key][ii], xs)
     if a1:
-        low = np.percentile(lines['a_1'], 35, axis=0)
-        high = np.percentile(lines['a_1'], 65, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.5, label=lab)
-        ax.plot(xs, low, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        low = np.percentile(lines['a_1'], 5, axis=0)
-        high = np.percentile(lines['a_1'], 95, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.1)
-        ax.plot(xs, low, color='k', lw=0.05, alpha=0.05)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.05, alpha=0.05)#, label=lab)
+        ax = plot_mean_and_90CI(ax, xs, lines['a_1'], color=col, label=lab, bounds=False)
     else:
-        low = np.percentile(lines['a_2'], 35, axis=0)
-        high = np.percentile(lines['a_2'], 65, axis=0)
[…]

### 2022-09-25 src/scripts/plot_ind_spintilt.py

@@ -4,10 +4,13 @@ import paths
 import numpy as np
 import matplotlib.pyplot as plt
 import deepdish as dd
+from utils import plot_mean_and_90CI
+
 
 def load_tilt_ppd():
     datadict = dd.io.load(paths.data / 'mspline_50m1_16ind_compspins_smoothprior_powerlaw_q_z_ppds.h5')
     return datadict['dRdct1'], datadict['dRdct2'], datadict['tilts'], datadict['tilts']
+
 
 def plot_o3b_spintilt(ax, fi,ct1=False, col='tab:blue', lab='PP'):
     xs = np.linspace(-1, 1, 1000)
@@ -18,31 +21,9 @@ def plot_o3b_spintilt(ax, fi,ct1=False, col='tab:blue', lab='PP'):
         for ii in range(len(lines[key])):
             lines[key][ii] /= np.trapz(lines[key][ii], xs)
     if ct1:
-        #med = np.median(lines['cos_tilt_1'], axis=0)
-        #ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
-        low = np.percentile(lines['cos_tilt_1'], 35, axis=0)
-        high = np.percentile(lines['cos_tilt_1'], 65, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.5, label=lab)
-        ax.plot(xs, low, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.25, alpha=0.1)#, label=lab)
-        low = np.percentile(lines['cos_tilt_1'], 5, axis=0)
-        high = np.percentile(lines['cos_tilt_1'], 95, axis=0)
-        ax.fill_between(xs, low, high, color=col, alpha=0.1)
-        ax.plot(xs, low, color='k', lw=0.05, alpha=0.05)#, label=lab)
-        ax.plot(xs, high, color='k', lw=0.05, alpha=0.05)#, label=lab)
+        ax = plot_mean_and_90CI(ax, xs, lines['cos_tilt_1'], color=col, label=lab, bounds=False)
     else:
-        #med = np.median(lines['cos_tilt_2'], axis=0)
-        #ax.plot(xs, med, color=col, lw=5, alpha=0.5, label=lab)
[…]

### 2022-09-25 src/scripts/utils.py

@@ -4,6 +4,26 @@ import paths
 import json
 
 
+def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None, tracecolor='k'):
+
+    mean = np.mean(ar, axis=0)
+    ax.plot(xs, mean, color=color, label=label, lw=5, alpha=0.75)
+    
+    if bounds:
+        low = np.percentile(ar, (100-CI)/2., axis=0)
+        high = np.percentile(ar, 100-(100-CI)/2., axis=0)
+        #ax.plot(xs, low, color='k', lw=0.05, alpha=0.05)
+        #ax.plot(xs, high, color='k', lw=0.05, alpha=0.05)
+        ax.fill_between(xs, low, high, color=color, alpha=0.08)
+    
+    if traces is not None:
+        for _ in range(traces):
+            idx = np.random.choice(ar.shape[0])
+            ax.plot(xs, ar[idx], color=tracecolor, lw=0.025, alpha=0.02)  
+    
+    return ax
+
+
 def save_macro(subdict):
     with open(paths.data / "macros.json", 'r') as f:
         old_macro = json.load(f)

### 2022-09-25 src/tex/macros.tex
add more macros

@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"MSplineIIDCompSpins": \{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "MSplineIndependentCompSpins": \{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}\}}\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\def\macros@out{??}\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@I@out\macros@III\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@I@out\macros@IV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@I@out\macros@V\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@VI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@VII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@III@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@III@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@III@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@III@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@III@out{1.00}\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IV@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IV@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IV@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IV@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IV@out{0.96}\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@V@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@V@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@V@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@V@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@V@out{0.47}\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{0.89}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{1.00}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{0.84}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.99}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.62}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.57}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"MSplineIndependentCompSpins": \{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@III\else\def\macros@out{??}\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@I@out\macros@IV\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@I@out\macros@V\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XII\else\def\macros@II@out{??}\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@III@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@III@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@III@out\macros@XV\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@III@out\macros@XVI\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IV@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IV@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IV@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IV@out{0.89}\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@V@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@V@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@V@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@V@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@V@out{1.00}\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{0.84}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{0.99}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{0.62}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.57}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{1.00}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.96}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.47}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XIII@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XIII@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XIII@out\macros@XIX\else\def\macros@XIII@out{??}\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XIV@out\macros@XX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XIV@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XIV@out\macros@XXII\else\def\macros@XIV@out{??}\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XV@out\macros@XXV\else\def\macros@XV@out{??}\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XVI@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XVI@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XVI@out\macros@XXVIII\else\def\macros@XVI@out{??}\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.03}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{0.49}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.05}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.05}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.44}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.07}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.05}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{0.47}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.05}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.12}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.50}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.07}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\makeatother

### 2022-09-25 src/tex/ms.tex
add more macros

@@
 \begin{abstract}
+
+    Default: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$} 
+             $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} 
+             $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$}
+
+    MSplineIID: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelowNeg0p3]}$}
+                $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$} 
+                $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$}
+
+    MSplineIND: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$}
+                $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$} 
+                $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$}
+
+    MSplineChiEff: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelowNeg0p3]}$}
+                   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$} 
+                   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}
+
 We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 

### 2022-09-25 src/scripts/create_macros.py

@@ -4,70 +4,103 @@ import json2latex
 import json
 import paths
 import numpy as np
-from utils import load_iid_tilt_ppd, load_ind_tilt_ppd
+import deepdish as dd
+from utils import load_iid_tilt_ppd, load_ind_tilt_ppd, save_param_cred_intervals
 
-def save_param_cred_intervals(param_data):
-    return  {'median': "{:.2f}".format(np.median(param_data)), 
-             'error plus': "{:.2f}".format(np.percentile(param_data, 95)-np.mean(param_data)), 
-             'error minus': "{:.2f}".format(np.median(param_data)-np.percentile(param_data, 5)),
-             '5th percentile': "{:.2f}".format(np.percentile(param_data, 5)), 
-             '95th percentile': "{:.2f}".format(np.percentile(param_data, 95))}
+def MSplineIIDSpinMacros():
+    print("Saving MSpline IID Component Spin macros...")
+    xs, ct_pdfs = load_iid_tilt_ppd()
+    peak_tilts = []
+    gamma_fracs = []
+    frac_neg_cts = []
+    for jj in range(len(ct_pdfs)):
+        ct_pdfs[jj,:] /= np.trapz(ct_pdfs[jj,:], xs)
+        peak_tilts.append(xs[np.argmax(ct_pdfs[jj,:])])
+        gam = ct_pdfs[jj,xs>=0.9] / ct_pdfs[jj, xs<=-0.9]
+        gamma_fracs.append(gam)
+        neg = xs <= 0
+        frac_neg_cts.append(np.trapz(ct_pdfs[jj,neg], x=xs[neg]))
+    peak_tilts = np.array(peak_tilts)
+    gamma_fracs = np.array(gamma_fracs)
+    frac_neg_cts = np.array(frac_neg_cts)
+    return {'peakCosTilt': save_param_cred_intervals(peak_tilts), 
+            'log10gammaFrac': save_param_cred_intervals(np.log10(gamma_fracs)), 
+            'negFrac': save_param_cred_intervals(frac_neg_cts)}
 
-macro_dict = {}
-print("Saving MSpline IID Component Spin macros...")
-xs, ct_pdfs = load_iid_tilt_ppd()
-peak_tilts = []
-gamma_fracs = []
-frac_neg_cts = []
[…]

### 2022-09-25 src/scripts/utils.py

@@ -5,6 +5,14 @@ import json
 import deepdish as dd
 
 
+def save_param_cred_intervals(param_data):
+    return  {'median': "{:.2f}".format(np.median(param_data)), 
+             'error plus': "{:.2f}".format(np.percentile(param_data, 95)-np.mean(param_data)), 
+             'error minus': "{:.2f}".format(np.median(param_data)-np.percentile(param_data, 5)),
+             '5th percentile': "{:.2f}".format(np.percentile(param_data, 5)), 
+             '95th percentile': "{:.2f}".format(np.percentile(param_data, 95))}
+
+
 def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None, tracecolor='k'):
 
     mean = np.mean(ar, axis=0)

### 2022-09-26 src/tex/appendicies.tex
Re-work intro, add citations etc

@@
 \appendix
+\section{Penalized Splines and Smoothing}\label{sec:psplines}
+
+Spline functions have been shown to be sensitivite to the chosen number of knots, and their locations or spacing. 
+Adding more knots knots increases the a-priori variance in the spline function, while the space between knots can limit the 
+resolution of features in the data the spline is capable of resolving. To ensure your spline based model is flexible enough 
+one would want to add as many knots as densely as possible, but this comes with the inherit larger variance as mentioned above. 
+To overcome this we resort to the frequentist penalized spline (P-Spline) in which one applies a penalty or regularization term 
+to the likelihood based on the difference of adjacent knot coeficients. The linear combination of spline basis components is 
+is flat when the basis coeficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as the differences between adjacent
+knot coeficients get larger, one gets a smoothing of the spline function inferences. Since we are using hierarchical Bayesian inferece as our 
+statistical framework, we formulate this penalized likelihood with its Bayesian analog. The difference penalty is equivalent to applying a stochastic 
+differnece prior among the knots, as described in \bruce{CITE THIS PAPER}. This is also sometimes referred to as a Gaussian random walk prior, since
+each coeficient is normally distributed about its neighboring coeficients. For a spline basis with $n$ degree's of freedom, 
+and a difference penalty of order of $r$ (see \bruce{cite P-splines paper}), our prior is defined as:
+
+\begin{eqnarray}
+\tau_\lambda \sim \Gamma(a, b) \\
+p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D}_{r}^{\mathrm{T}} \bm{D}_r \bm{c}  \big] e^{-n\bm{c}}
+\end{eqnarray}
+
+\noindent Above $\bm{D}_r$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $\Gamma(a,b)$ the Gamma distribution with shape parameters, $a$ and $b$. 
+This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a very large number 
+of knots such that your domain is densly populated with basis coeficients, this allows the freedom for the model to find the smoothing 
+scale that the data prefers. One downside of this prior specification as noted by\ bruce{CITE BAYESIAN PSPLINES}, is a slight dependence on choice 
+of the b hyper-parameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \bruce{CITE BAYESIAN PSPLINES} 
+to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyper-parameters. 
+We now replace the prior on $\tau_\lambda$ with:
+
+\begin{align}
+    \bm{p} \sim \mathcal{D}(m) \\
+    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_i)
+\end{align}
+
+\noindent Where above $\mathcal{D}(m)$ is a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
+and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.
+
+%Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
+%that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
+%across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
+%effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:
+
+%\begin{eqnarray}
+%\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
+%\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
+%p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c} \big] e^{-n\bm{c}}
+%\end{eqnarray}
+
+%Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
+%prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
+%across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
+%the power-law like mass distributions that are commonly used.
+
+This prior is imparting a natural attraction of the coeficients closer to each other in order to smooth the spline function, so one 
+must ensure that the spline function is in fact flat given all equal coeficients. Since one needs to define n+k knots to construct an order-k basis with 
+n degrees of freedom, people often will place knots on top of each other at hard parameter boundaries \bruce{cite msplines / o-splines}. 
+This may seemed motivated, especially if there is no reality in the parameter beyond the boundary, but this violates the above condition. 
+We follow the distinction from \bruce{CITE psplines} that the difference penalty or smooothing prior is only valid with ``proper'' spline bases. 
+A proper basis is where all n+k knots are evenly spaced, see Figure \ref{fig:spline_basis}, as opposed to stacking them at the bounds.
+
 \section{Hierarchical Bayesian Inference} \label{sec:hierarchical_inference}
@@
 the cosmological parameters from \citet{Planck2015}. We model the merger rate evolving with redshift following a power law distribution: 
-$p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$. When integrating equation \ref{number_density} across all $\theta$
+$p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$ \cite{Fishbach_2018redshift}. When integrating equation \ref{number_density} across all $\theta$
 and out to some maximum redshift, $z_\mathrm{max}$, we get the total number of CBCs in the universe out to that redshift. We follow previous notations, \
@@
 indexes the $K_i$ posterior samples from each event and $\pi(\theta, z)$ is the default prior used by parameter estimations that 
-produced the posterior samples for each event. In the analyses of GWTC-2 the default prior used is uniform in detector frame masses, 
-component spins and Euclidean volume. The corresponding prior evaluated in source frame primary mass, mass ratio, component spins 
-and redshift is:
+produced the posterior samples for each event. In the analyses of GWTC-3, either the default prior used was uniform in detector frame masses, 
+component spins and Euclidean volume or the posterior samples were re-weighted to such a prior before using them in our analysis. 
+The corresponding prior evaluated in the parameters we hierarchicaly model, i.e. source frame primary mass, mass ratio, component spins and redshift is:
 
@@
 
-\section{Penalized Splines and Smoothing}\label{sec:psplines}
-
-Spline functions have been shown to be sensitivite to the chosen number of knots, and their locations or spacing. 
-Adding more knots knots increases the a-priori variance in the spline function, while the space between knots can limit the 
-resolution of features in the data the spline is capable of resolving. To ensure your spline based model is flexible enough 
-one would want to add as many knots as densely as possible, but this comes with the inherit larger variance as mentioned above. 
-To overcome this we resort to the frequentist penalized spline (P-Spline) in which one applies a penalty or regularization term 
-to the likelihood based on the difference of adjacent knot coeficients. The linear combination of spline basis components is 
-is flat when the basis coeficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as the differences between adjacent
-knot coeficients get larger, one gets a smoothing of the spline function inferences. Since we are using hierarchical Bayesian inferece as our 
-statistical framework, we formulate this penalized likelihood with its Bayesian analog. The difference penalty is equivalent to applying a stochastic 
-differnece prior among the knots, as described in \bruce{CITE THIS PAPER}. This is also sometimes referred to as a Gaussian random walk prior, since
-each coeficient is normally distributed about its neighboring coeficients. We then use as our smoothing prior, for a spline basis with $n$ degree's of freedom
-, and a difference order of $r$ in our smoothing penalty (see \bruce{cite P-splines paper}) is defined as:
-
-\begin{eqnarray}
-\tau_\lambda \sim \Gamma(a, b) \\
-p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{D_r} \bm{c}  \big] e^{-n\bm{c}}
-\end{eqnarray}
-
-\noindent Above $\bm{D_r}$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $\Gamma(a,b)$ the Gamma distribution with shape parameters, $a$ and $b$. 
-This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a very large number 
-of knots such that your domain is densly populated with basis coeficients, this allows the freedom for the model to find the smoothing 
-scale that the data prefers. One downside of this prior specification as noted by\ bruce{CITE BAYESIAN PSPLINES}, is a slight dependence on choice 
-of the b hyper-parameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \bruce{CITE BAYESIAN PSPLINES} 
-to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyper-parameters. 
-We now replace the prior on $\tau_\lambda$ with:
-
-\begin{align}
-    \bm{p} \sim \mathcal{D}(m) \\
-    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_i)
-\end{align}
-
-\noindent Where above $\mathcal{D}(m)$ is a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
-and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.
-
-%Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
-%that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
-%across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
-%effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:
-
-%\begin{eqnarray}
-%\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
-%\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
-%p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c} \big] e^{-n\bm{c}}
-%\end{eqnarray}
-
-%Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
-%prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
-%across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
-%the power-law like mass distributions that are commonly used.
-
-Since the smoothing prior is really wanting to pull the coeficients closer to each other to smooth the distribution, 
-we must ensure that the spline function is in fact flat or smooth with all equal coeficients. Often times one would stack knots at the same values 
-at hard parameter boundaries but this removes the feature that with equal weights the spline function is flat. We follow the distinction from \bruce{CITE psplines} 
-that the difference penalty or prior is only valid with ``proper'' spline bases. A proper basis is where all of the knots are evenly spaced, see Figure \ref{fig:spline_basis}.
-
 \section{Model specification} \label{sec:modelpriors}
 
-\section{Validation Studies} \label{sec:validation}
+\bruce{Need to fill this section in and put tables with specific hyper-parameter/prior settings made}
+
+%\section{Validation Studies} \label{sec:validation}

### 2022-09-26 src/tex/intro.tex
Re-work intro, add citations etc

@@
 
-Observations of gravitational waves from compact binary coalescences (CBCs) is becoming a regular occurrence, 
-recently producing catalogs of 90 such detections \bruce{cite GWTCs}. This growing catalog size is beginning to enable access to a more complete 
-understanding of the population properties CBCs, which encodes the history of the formation and evolution of these extreme compact objects. 
-In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration \bruce{cite detectors}, the catalog size is expected to increase by up to a factor of 5. 
-Looking at population properties of compact objects lets us probe the complex physics common to all of our observations that governs the 
-formation and evolution of merging compact objects. The history of these dense objects is imprinted on the properties of the population 
-of CBCs, allowing us to learn about these not well understood ideas through careful evaluation of the enture distribution of observed GWs. 
-The mass distribution of binary black holes has been used to measure cosmological parameters, constrain modified gravitational wave propagation, 
-constrain a non-constant Planck mass, look for evidence of ultralight bosons through superradiance, put constraints on the uncertain nuclear reaction 
-rates important for stellar evolution, look for primordial black holes, to constrain the neutron star equation of state, 
-and to understand the fromation channels/environments of compact binary coalescences (CBCs). Through a better understanding of the mass, spin, 
-and redshift distribution of compact binaries that will come with the increased catalog size, one can probe these dufferent physical phenoma with 
-greater fidelity.
+Observations of gravitational waves (GWs) from compact binary coalescences (CBCs) is becoming a regular occurrence, 
+recently producing catalogs of 90 such detection \cite{GWTC1,gwtc2,GWTC3}. With this growing catalog size, we are steadily approaching a more complete  
+understanding of the population properties CBCs, just 7 years after the first observation \cite{o1o2_pop,o3a_pop,o3b_astro_dist}. 
+In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration detectors \cite{aLIGO,aVIRGO, KAGRA}, with the increased sensitivities, 
+there could be a detection as often as every day. This large influx of incoming data will drastically increase what we can learn by combining all observations
+in order to studying the compact object population. The history of these dense objects is imprinted on the properties of the population 
+of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitation radiation emitted. The population distibutions 
+of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB}, 
+constrain modified gravitational wave propagation, constrain a running Planck mass, look for evidence of ultralight bosons through superradiance, 
+constrain stellar nuclear reaction rates \cite{Farmer_2020}, look for primordial black holes \cite{Ng_2021}, and constrain the neutron star equation of state \bruce{Cite all points}. 
+Through a better understanding of the mass, spin, and redshift distributions of compact binaries that will come with the increased catalog size, 
+one can probe a wide range of different physical phenoma with even greater fidelity.
 
-With the latest LIGO-Virgo-KAGRA (LVK) catalog of CBCs (GWTC-3), new understanding of the population has come into light. One of the main findings was that 
-the mass distribution exhibits substructure with peaks rather than being perfectly described by a smooth power law distribution. The evidence for this was 
-found with mutliple different flexible or non-parametric models that aim to be data-oriented with little bias on the function form. While these models are 
-useful for looking for unexpected features in the data, or finding where our simpler models fail, they can be harder to interpret and are not based on specific
-astrophysical motivation. These types of models will become more important as the size of our catalogs increase and we enter a data-dominated regime rather than
-prior/model dominated.
+Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 \citep{Tiwari_2021_b,Edelman_2022ApJ} found signs of structure 
+beyond the reported $m_1\sim35\,\msun$ feature by \citet{Talbot_2019, o3a_pop}. The has evidence for this structure, such as the peak at $m_1\sim10\,\msun$, has only increased
+with GWTC-3 \cite{o3b_astro_dist,Tiwari_2022ApJ}. This substructure was first confidently found with mutliple different flexible or non-parametric models that aim 
+to be data-oriented with little bias on the functional form. Conversely the other canonical approach is to use simple parametric models that aim to describe the data
+in the simplest way, building in astrophyscially motivated priors, followed by sequentially adding complexities only as the data demands it. While in the current environment 
+this simple approach is clearly more powerful, as we go forward into the data-rich catalog era flexible models can be a useful complement.
+Non-parametric or semi-parametric methods are particularly useful at looking for unexpected features in the data, or finding where 
+our simpler parametric models may be missing features in the data. Development and robust teting of these types of methods in the short term will provide
+knock dowm effects later down the line as the size of our catalogs increase and we enter a data-dominated regime rather than prior/model dominated.
 
-The spin distribution of binary black holes (BBHs) has also been of controversial interest in the literature recently, with different parameteric approaches finding 
-rather different conclusions on the distribution of spins of BBHs which has significant impact on the inferences about relative contribution of dynamically formed
-binaries versus ones formed in the field. This is another use case for flexible data-driven models to alleivate the discrepencies among parametric approaches. 
-In particular there has been little work on flexible model development for the spin distribution of BBHs, which makes sense given the relatively smaller catalog 
-sizes and the large uncertainty in individual black hole spin measurements with GWs.
+The spin distributions of binary black holes (BBHs) have particular interest since the two main formation scenarios of BBHs produce 
+distinctly different spin distrubitons \bruce{cite}. Isolated or field formation scenarios predict spins that are preferentially, although some small misalignment can occur 
+depending on the nature of the supernovae kicks as each star collapses to a compact object \bruce{cite}. Dynamical formation scenarios occur in dense environments where 
+many-body interactions between a large number compact objects occur before producing a binary that will merger within a Hubble time. Thus the dynamical channel produces 
+an isotropic spin orientation distribution \bruce{cite}. It has also been of controversial interest in the literature recently, with different parameteric approaches finding 
+different conclusions on the distribution of spins of BBHs. Recent studies have disagreed on the possible existence of a significant zero-spinning subpopulation, along with the 
+presence of significant mis-alignment ($\cos{\theta_i} < 0.0$) \cite{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}.
+A recent study has shown the spin orientation distribution infernce is senitive to modeling choices and
+may not peak at perfectly aligned spins, as is commonly assumed \cite{spinitasyoulike}. 
+Other approaches to building better models for BBH spins again, as with the mass models, focus on iterating through different simple parameteric descriptions with 
+increasing complexities \cite{BuildBetterSpinModels,Callister_NoEvidence,spinitasyoulike}. The spin distributions offer a nice use case for flexible data-driven models, both 
+to help alleivate the current disputes in the literature and because there has been little work on flexible model development for the spin distribution of BBHs thus far.
 
-In this paper we highlight how the use of basis-splines can be a useful model-agnostic modeling approach to the astrophysical distributions of compact 
-binaries. We show that with a particular choice of basis, one can efficiently model the spin, mass and redshift distributions of compact binaries in GWTC-3 with
+In this paper we highlight how the use of basis-splines can be a useful non-parametric modeling approach to the astrophysical distributions of compact 
+binaries. We show that with a particular choice of basis, one can efficiently model the mass and spin distributions of compact binaries in GWTC-3 with
 hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and illustrate how our results are similar
 to those produced with the more simpler and astrophysically motivated parametric models. This data-drien approach will be capable of finding more subtle features, that 
-may not be expected, should they appear in future catalogs. Additionally this method can be extended to higher-dimensional basis-splines in order to model 
-joint population disributions over multiple surce parameters, which will be important to confidently disentangle different competing formation channels 
-should they exist. In Section II we go over the background of basis splines and model construction. In Section III we present results using our basis spline model 
-on the mass and spin distributions of BBHs in GWTC-3, followed by discussing the results and astrophysical implications in Section IV and concluding in Section V.
+may not be expected, should they appear in future catalogs. In Section \ref{sec:basis_splines} we go over the background of basis splines, in Section \ref{sec:results} 
+we present results using our basis spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context and concluding 
+in Section \ref{sec:conclusion}.

### 2022-09-26 src/tex/macros.tex
Re-work intro, add citations etc

--- 2022-09-25 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"MSplineIIDCompSpins": \{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "MSplineIndependentCompSpins": \{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}\}}\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\def\macros@out{??}\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@I@out\macros@III\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@I@out\macros@IV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@I@out\macros@V\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@VI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@VII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@III@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@III@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@III@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@III@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@III@out{1.00}\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IV@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IV@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IV@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IV@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IV@out{0.96}\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@V@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@V@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@V@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@V@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@V@out{0.47}\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{0.89}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{1.00}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{0.84}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.99}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.62}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.57}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"MSplineIndependentCompSpins": \{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@IV\else\def\macros@out{??}\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@I@out\macros@V\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@I@out\macros@IX\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@I@out\macros@X\else\def\macros@I@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XIII\else\def\macros@II@out{??}\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@III@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@III@out\macros@XV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@III@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@III@out\macros@XVII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"PLPeak": \{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@IV@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@IV@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@IV@out\macros@XX\else\def\macros@IV@out{??}\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@V@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@V@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@V@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@V@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@V@out{0.89}\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{1.00}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{0.84}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{0.99}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.62}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.57}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.00}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.96}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{0.47}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XIV@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XIV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XIV@out\macros@XXIII\else\def\macros@XIV@out{??}\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XV@out\macros@XXVI\else\def\macros@XV@out{??}\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XVI@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XVI@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XVI@out\macros@XXIX\else\def\macros@XVI@out{??}\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XVII@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XVII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XVII@out\macros@XXXII\else\def\macros@XVII@out{??}\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XVIII@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XVIII@out\macros@XXXIV\else\def\macros@XVIII@out{??}\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XIX@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XIX@out\macros@XXXVI\else\def\macros@XIX@out{??}\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XX@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XX@out\macros@XXXVIII\else\def\macros@XX@out{??}\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.03}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.49}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.05}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{0.05}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.44}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.07}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.05}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.47}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.05}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.12}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.50}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.07}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{6.32}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{5.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{6.90}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{44.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{38.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{55.46}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{6.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{5.82}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{6.59}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{80.10}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{11.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{12.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{67.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{91.26}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{5.83}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{1.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{1.47}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{4.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{6.81}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{43.20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{10.47}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{38.49}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{54.97}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\makeatother

### 2022-09-26 src/tex/methods.tex
Re-work intro, add citations etc

--- 2022-09-22 src/tex/methods.tex
@@
 
-A common non-parametric method in statistical applications is the use of basis splines. A spline function of order $k$, 
+A common non-parametric method in used in many statistical applications is basis splines. A spline function of order $k$, 
 is a piece-wise polynomial of order $k$ polynomials stitched together from defined ``knot'' locations across the domain. 
@@
 every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines basis components for a given knot vector 
-using the Cox-de Boor recursion formula. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:
+using the Cox-de Boor recursion formula \cite{deBoor78}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:
 
@@
 
+\noindent allowing one to build a basis of $i$ components that spans the vector space of order-$k$ spline functions interpolated 
+from this knot vector. This is known as the ``B-Spline'' basis after it's inventor de Boor \cite{deBoor78}. The power of basis splines
+comes from the fact that you only have to do the, somewhat expensive, interpolation once for each set of points you want to evaluate your
+spline functions at. This allows for much quicker speeds since each evaluation of the spline function becomes a simpler operation that is just
+a dot product of 2d matrix and 1d vector. This straightforward operation is also ideal for optimizations from the use GPU accelerators, 
+enabling expensive markov chain monte carlo (MCMC) based analyses with hundreds of parameters. Basis splines can easily be generalized to 
+their two-dimensional analog, producing tensor product basis splines that, with this computational advantange, allow for high fidelity
+modeling of two-dimensional spline functions.
+
+A similar basis, the M-Spline basis \citep{monotone_regression_splines}, has desirable properties when looking to model a probability density function, 
+which is the goal of population inference. Namely, $M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. We now have
+a useful basis that can represent all spline functions that are probability density functions given our array of knots. The M-Spline basis differs 
+from B-Splines by the normalization factor:
+
+\begin{equation}\label{eq:MB_SplineRelation}
+M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
+\end{equation}
+
 \begin{figure}[ht!]
@@
 
-\noindent allowing one to build a basis of $i$ components that spans the vector space of order-$k$ spline functions interpolated 
-from this knot vector. This is known as the ``B-Spline'' basis.
-
-A similar basis, the M-Spline basis, has desirable properties when looking to model a probability density function. Namely, 
-$M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. The M-Spline basis only differs 
-from B-Splines by a normalization factor, namely:
-
-\begin{equation}\label{eq:MB_SplineRelation}
-M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
-\end{equation}
-
 \noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper. 
-
-\section{Model Construction}
-
-\bruce{placeholder paragraph here to introduce our model constructions.}
-We use hierarchical Bayesian inference to simultaneosly infer the mass, spin and redshift distributions of binary black holes (BBHs) using 
-the 69 confident BBH detections reported in the recent LVK catalog of observations, GWTC-3. In particular we choose to parameterize the two
-masses with the primary (more massive component) mass and the mass ratio defined as $q=\frac{m_2}{m_1}$. We choose to model 4 of the 6 total 
-spin degrees of freedom of a binary merger with each component spin magnitude, and the cosine of the tilt angle which is defined as the angle 
-between each spin vector and the binaries orbital angular mommentum vector. We additionally will fit a population model on the redshift distribution
-of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology defined by the Planck 2015 results, which defines an analytical mapping between each event's inferred
-luminosity distance and it's redshift. While we choose to use MSpline distibutions for the masses and spins, we use the canonical \textsc{PowrerlawRedshift}
-model describing the evolution of CBC merger rates as a power law in $(1+z)$ with a slope of $\lambda_z$. The corresponsing distribution is Thus
-desribed by $p(z|\lambda)\propto \frac{dV_c}{dz} \frac{T_\mathrm{obs}}{1+z} (1+z)^\lambda$. We model the spin magnitude and tilt distibutions to be 
-described by independent MSpline distributions for each component.
+Figure \ref{fig:spline_basis} shows an example of a 3rd order M-Spline basis with 20 degrees of freedom and knots linearly spaced from 0 to 1.
+Another important feature of basis splines is that under appropiate prior conditions, one can alleviate sensitivities to arbitrarily 
+chosen prior specifications that splines commonly struggle with. We look to the use of penalized splines or P-Splines \cite{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
+that adds a smoothing penalty (or prior) based on the difference of basis spline coeficients. This allows one to much more denseley populate
+the domain with knots without the worry of extra variance in the inferred spline functions. We discuss the smoothing prior in more detail 
+in Appendix \ref{sec:psplines}, along with our specific prior and basis choices for each model in Appendix \ref{sec:modelpriors}.

### 2022-09-26 src/tex/results.tex
add chi eff plot
methods.tex is mostly finished but w/o citations
Re-work intro, add citations etc

@@
 
-\bruce{intro paragraph here to describe GWTC3 catalog and the selection we made for our analyses}
+We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneosly infer the astrophysical mass, spin and redshift distributions of 
+a binary black holes (BBHs) given a catalog of gravitational wave observations. We choose to parameterize the binaries' masses with the primary (defined as the more massive component) mass 
+and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. We choose to model 4 of the 6 total 
+spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
+$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular mommentum vector. 
+We additionally will fit a population model on the redshift or luminosity distance distribution of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology using the 
+parameters from the Planck 2015 results \cite{Planck2015}, which defines an analytical mapping between each event's inferred
+luminosity distance and it's redshift. While we choose to use MSpline distibutions to model the primary mass and spin distributions, we 
+model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta_q) \propto q^{\beta_q} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$. 
+Where the $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$].
+We model the evolution of the merger rate with redshift with the \textsc{PowrerlawRedshift} model \cite{Fishbach_2018redshift}, which is desribed by 
+$p(z|\lambda_z)\propto \frac{dV_c}{dz} \frac{T_\mathrm{obs}}{1+z} (1+z)^\lambda_z$. We describe our specific prior choices on the hyper-parameters and each model 
+in more detail in Appendix \ref{sec:modelpriors}. We choose the same cut on the recent GWTC-3 catalog as was done in the LVK's accompanying population analysis, \bruce{cite}.
+Keeping all possible BBH mergers with false alarm rates less than 1 per year, we have 70 oservations. We choose to emit the currently not well understood event, GW190814 \cite{190814disc},
+as it was concluded to be an outlier of the rest of the BBH population in both GWTC-2 and GWTC-3 \cite{o3a_pop}.
+This leaves us with a catlog of 69 BBH mergers observerd oveer a period of about 2 years, from
+which we want to infer the population properties of. We start by looking towards the mass distribution.
 
 \subsection{BBH Mass Distibution} \label{sec:mass_dist}
+
+PLPeak: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_99percentile]}$}
+
+PLSpline: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_99percentile]}$}
+
+MSpline: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_99percentile]}$}
 
@@
 
+\subsubsection{Spin Magnitude}
+
+\subsubsection{Spin Orientation}
+
 The spins distribution of merging combact binaries provides a very useful insight into the formation history of the binary. In particular the two main subcategories, 
@@
 \end{figure}
-%\begin{figure*}[ht!]
-%    \script{component_spin_distribution_plot.py}
-%    \begin{centering}
-%%        \includegraphics[width=\textwidth]{figures/component_spin_distribution_plot.pdf}
- %       \caption{Plot showing the inferred component spin magnitude (top) and spin tilt (bottom) distributions inferred with the 9-knot \textsc{MSpline} models. 
-%        There are two independent \textsc{MSpline} (black) models for each primary/secondary spin magnitude and spin tilt. We compare by showing the results for the
-%        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
-%        \label{fig:component_spin_distribution}
-%    \end{centering}
-%\end{figure*}
-
-%\begin{figure*}
-%    \script{iid_component_spin_distribution_plot.py}
-%    \begin{centering}
-%        \includegraphics[width=\textwidth]{figures/iid_component_spin_distribution_plot.pdf}
-%        \caption{Plot showing the inferred component spin magnitude (left) and spin tilt (right) distributions inferred with the 9-knot \textsc{MSpline} models. 
-%        Each components spin magnitude and tilt are assumed to be IID. We compare by showing the results for the
-%        \textsc{Default} (iid) spin model used with the \textsc{PowerlawPeak} mass model (blue) and the \textsc{PowerlawSpline} mass model (orange).}
-%        \label{fig:iid_component_spin_distribution}
-%    \end{centering}
-%\end{figure*}
 
@@
 
-\subsection{The Effective Spin Dimensions}
+\subsection{The Effective Spin Dimension}
 
@@
 
+\begin{figure}
+    \script{plot_chieff.py}
+    \includegraphics[width=0.45\textwidth]{figures/chi_eff.pdf}
+    \caption{Caption.}
+    \label{fig:chieff_dist}
+\end{figure}
+
 \bruce{Here we discuss the astrophysical implications of work -- connect to wider literature}

### 2022-09-26 src/scripts/create_macros.py

@@ -5,7 +5,49 @@ import json
 import paths
 import numpy as np
 import deepdish as dd
-from utils import load_iid_tilt_ppd, load_ind_tilt_ppd, save_param_cred_intervals
+from scipy.integrate import cumtrapz
+from utils import load_iid_tilt_ppd, load_ind_tilt_ppd, save_param_cred_intervals, load_o3b_paper_run_masspdf, load_mass_ppd
+
+
+def get_m1_m99(pdfs, ms):
+    m99 = []
+    m1 = []
+    for m in pdfs:                                                                                                                                                                        
+        i = len(m)
+        cumulative_prob = cumtrapz(m, ms, initial = 0)
+        init_prob = cumulative_prob[-1]
+        prob = init_prob
+        final_prob = init_prob*0.99                                                                                                                                              
+        while prob > (final_prob):
+            i -= 1
+            prob = cumulative_prob[i]                                                                                                                                                         
+        m99.append(ms[i])
+    m99 = np.array(m99)
+    for m in pdfs:
+        i = 0
+        cumulative_prob = cumtrapz(m, ms, initial = 0)
+        init_prob = cumulative_prob[-1]
+        prob = 0
+        final_prob = init_prob*0.01
+        while prob < (final_prob):
+            i += 1
+            prob = cumulative_prob[i]
+        m1.append(ms[i])
+    m1 = np.array(m1)
+    return m1, m99
+
+
+def MSplineMassMacros():
+    print("Saving Mass Distribution Macros...")
+    ms, m_pdfs, _, _ = load_mass_ppd()
+    m1s, m99s = get_m1_m99(m_pdfs, ms)
+    plpeak_mpdfs, _, plpeak_ms, _ = load_o3b_paper_run_masspdf(paths.data / 'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5')
+    plpeak_m1s, plpeak_m99s = get_m1_m99(plpeak_mpdfs, plpeak_ms)
+    ps_mpdfs, _, ps_ms, _ = load_o3b_paper_run_masspdf(paths.data / 'spline_20n_mass_m_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5')
+    ps_m1s, ps_m99s = get_m1_m99(ps_mpdfs, ps_ms)
[…]

### 2022-09-26 src/scripts/mass_distribution_plot.py

@@ -3,53 +3,9 @@
 import paths
 import numpy as np
 import matplotlib.pyplot as plt
-import deepdish as dd
-from utils import plot_mean_and_90CI
+from utils import plot_mean_and_90CI, load_mass_ppd, load_o3b_paper_run_masspdf
 from matplotlib.ticker import ScalarFormatter
 
-
-def load_ppd():
-    datadict = dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_ppds.h5')
-    return datadict['m1s'], datadict['dRdm1'], datadict['qs'], datadict['dRdq']
-
-
-def load_o3b_paper_run_m1ppd(filename):
-    mass_1 = np.linspace(2, 100, 1000)
-    mass_ratio = np.linspace(0.1, 1, 500)
-    # load in the traces. 
-    # Each entry in lines is p(m1 | Lambda_i) or p(q | Lambda_i)
-    # where Lambda_i is a single draw from the hyperposterior
-    # The ppd is a 2D object defined in m1 and q
-    with open(filename, 'r') as _data:
-        _data = dd.io.load(filename)
-        ppd = _data["ppd"]
-    m1ppd = np.trapz(ppd, x=mass_ratio, axis=0)
-    return mass_1, m1ppd / np.trapz(m1ppd, x=mass_1)
-
-def load_o3b_paper_run_masspdf(filename):
-    """
-    Generates a plot of the PPD and X% credible region for the mass distribution,
-    where X=limits[1]-limits[0]
-    """
-    mass_1 = np.linspace(2, 100, 1000)
-    mass_ratio = np.linspace(0.1, 1, 500)
-        
-    # load in the traces. 
-    # Each entry in lines is p(m1 | Lambda_i) or p(q | Lambda_i)
-    # where Lambda_i is a single draw from the hyperposterior
-    # The ppd is a 2D object defined in m1 and q
-    with open(filename, 'r') as _data:
-        _data = dd.io.load(filename)
-        marginals = _data["lines"]
-    for ii in range(len(marginals['mass_1'])):
-        marginals['mass_1'][ii] /= np.trapz(marginals['mass_1'][ii], mass_1)
[…]

### 2022-09-26 src/scripts/utils.py

@@ -484,3 +484,28 @@ def plot_o3b_spinmag(ax, fi, a1=True, col='tab:blue', lab='PP'):
 def load_ind_mag_ppd():
     datadict = dd.io.load(paths.data / 'mspline_50m1_16ind_compspins_smoothprior_powerlaw_q_z_ppds.h5')
     return datadict['dRda1'], datadict['dRda2'], datadict['mags'], datadict['mags']
+
+
+def load_o3b_paper_run_masspdf(filename):
+    """
+    Generates a plot of the PPD and X% credible region for the mass distribution,
+    where X=limits[1]-limits[0]
+    """
+    mass_1 = np.linspace(2, 100, 1000)
+    mass_ratio = np.linspace(0.1, 1, 500)
+        
+    # load in the traces. 
+    # Each entry in lines is p(m1 | Lambda_i) or p(q | Lambda_i)
+    # where Lambda_i is a single draw from the hyperposterior
+    # The ppd is a 2D object defined in m1 and q
+    with open(filename, 'r') as _data:
+        _data = dd.io.load(filename)
+        marginals = _data["lines"]
+    for ii in range(len(marginals['mass_1'])):
+        marginals['mass_1'][ii] /= np.trapz(marginals['mass_1'][ii], mass_1)
+        marginals['mass_ratio'][ii] /= np.trapz(marginals['mass_ratio'][ii], mass_ratio)
+    return marginals['mass_1'], marginals['mass_ratio'], mass_1, mass_ratio
+
+def load_mass_ppd():
+    datadict = dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_ppds.h5')
+    return datadict['m1s'], datadict['dRdm1'], datadict['qs'], datadict['dRdq']

### 2022-09-26 src/tex/intro.tex
fix words

@@
 In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration detectors \cite{aLIGO,aVIRGO, KAGRA}, with the increased sensitivities, 
-there could be a detection as often as every day. This large influx of incoming data will drastically increase what we can learn by combining all observations
+there could be a detection as often as every day \cite{LVK_prospects}. This large influx of incoming data will drastically increase what we can learn by combining all observations
 in order to studying the compact object population. The history of these dense objects is imprinted on the properties of the population 
@@
 different conclusions on the distribution of spins of BBHs. Recent studies have disagreed on the possible existence of a significant zero-spinning subpopulation, along with the 
-presence of significant mis-alignment ($\cos{\theta_i} < 0.0$) \cite{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}.
-A recent study has shown the spin orientation distribution infernce is senitive to modeling choices and
-may not peak at perfectly aligned spins, as is commonly assumed \cite{spinitasyoulike}. 
+presence of significant mis-alignment ($\cos{\theta_i} < 0.0$) \cite{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}. A recent study 
+has shown the spin orientation distribution infernce is senitive to modeling choices and may not peak at perfectly aligned spins, as is commonly assumed \cite{spinitasyoulike}. 
 Other approaches to building better models for BBH spins again, as with the mass models, focus on iterating through different simple parameteric descriptions with 
@@
 
-In this paper we highlight how the use of basis-splines can be a useful non-parametric modeling approach to the astrophysical distributions of compact 
-binaries. We show that with a particular choice of basis, one can efficiently model the mass and spin distributions of compact binaries in GWTC-3 with
-hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and illustrate how our results are similar
-to those produced with the more simpler and astrophysically motivated parametric models. This data-drien approach will be capable of finding more subtle features, that 
-may not be expected, should they appear in future catalogs. In Section \ref{sec:basis_splines} we go over the background of basis splines, in Section \ref{sec:results} 
-we present results using our basis spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context and concluding 
-in Section \ref{sec:conclusion}.
+Polynomial splines have been applied to success across different areas of gravitational-wave astronomy. They have been used to model the gravitational-wave data noise spectrum, 
+detector calibration uncertainties, coherent gravitational waveform deviations, and modulations to a power law mass distribution \cite{Littenberg_2015,Edwards_2018,B_Farr_etal_2014,Edelman_2021,Edelman_2022ApJ}
+In this paper we highlight how the use of basis-splines can provide a powerful non-parametric modeling approach to the astrophysical distributions of compact 
+binaries. We illustrate how one can efficiently model the mass and spin distributions of compact binaries in GWTC-3 with basis splines to infer population properties using 
+hierarchical Bayesian inference.
+We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower dimensional parametric models.
+This data-drien approach will be capable of finding more subtle features, that may not be expected, should they appear in future catalogs. 
+In Section \ref{sec:basis_splines} we go over the background of basis splines, in Section \ref{sec:results} we present results using our basis 
+spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context and concluding in Section \ref{sec:conclusion}.

### 2022-09-26 src/tex/conclusion.tex
methods.tex is mostly finished but w/o citations
disc section

@@
+\section{Discussion}\label{sec:astrodiscussion}
+
+\bruce{Here we discuss the astrophysical implications of work -- connect to wider literature}
+
 \section{Conclusions}\label{sec:conclusion}
 
-\bruce{have subsection in results.tex to discuss the astro interpretation of our results and connect to literature. 
-I think main points for conclusion are to sum up conclusions with one last call to literature for most important parts, 
+\bruce{main points for conclusion are to sum up conclusions with one last call to literature for most important parts, 
 followed by short discussion of the outlook going into O4 and how this method will be especially useful as we rapidly approach

### 2022-09-26 src/tex/intro.tex
disc section

@@
 In Section \ref{sec:basis_splines} we go over the background of basis splines, in Section \ref{sec:results} we present results using our basis 
-spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context and concluding in Section \ref{sec:conclusion}.
+spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context Section \ref{sec:astrodiscussion} 
+and concluding in Section \ref{sec:conclusion}.

### 2022-09-26 src/tex/results.tex
disc section
more macros and mass results

@@
 \section{Binary Black Hole Population Inference with GWTC-3} \label{sec:results}
-
-We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneosly infer the astrophysical mass, spin and redshift distributions of 
-a binary black holes (BBHs) given a catalog of gravitational wave observations. We choose to parameterize the binaries' masses with the primary (defined as the more massive component) mass 
-and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. We choose to model 4 of the 6 total 
-spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
-$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular mommentum vector. 
-We additionally will fit a population model on the redshift or luminosity distance distribution of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology using the 
-parameters from the Planck 2015 results \cite{Planck2015}, which defines an analytical mapping between each event's inferred
-luminosity distance and it's redshift. While we choose to use MSpline distibutions to model the primary mass and spin distributions, we 
-model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta_q) \propto q^{\beta_q} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$. 
-Where the $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$].
-We model the evolution of the merger rate with redshift with the \textsc{PowrerlawRedshift} model \cite{Fishbach_2018redshift}, which is desribed by 
-$p(z|\lambda_z)\propto \frac{dV_c}{dz} \frac{T_\mathrm{obs}}{1+z} (1+z)^\lambda_z$. We describe our specific prior choices on the hyper-parameters and each model 
-in more detail in Appendix \ref{sec:modelpriors}. We choose the same cut on the recent GWTC-3 catalog as was done in the LVK's accompanying population analysis, \bruce{cite}.
-Keeping all possible BBH mergers with false alarm rates less than 1 per year, we have 70 oservations. We choose to emit the currently not well understood event, GW190814 \cite{190814disc},
-as it was concluded to be an outlier of the rest of the BBH population in both GWTC-2 and GWTC-3 \cite{o3a_pop}.
-This leaves us with a catlog of 69 BBH mergers observerd oveer a period of about 2 years, from
-which we want to infer the population properties of. We start by looking towards the mass distribution.
-
-\subsection{BBH Mass Distibution} \label{sec:mass_dist}
-
-PLPeak: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_99percentile]}$}
-
-PLSpline: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_99percentile]}$}
-
-MSpline: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_99percentile]}$}
-
-We apply our newly constructed models to the BBH analysis that was done in the astrophysical population companion paper to GWTC-3. 
-We find consistent features in the mass disribution with what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} 
-mass models. In particular our MSpline model finds a peak in merger rate density at both 10 and 35 soloar masses, agreeing with those reported
-in \bruce{CITE o3b paper}. We also find a significantly less declining mass distribution that has considerably larger support for higher mass 
-mergers when compared to the other power-law based models. Another interesting consequence of this is that we thus infer a much less steeply
-evolving merger rate with redshift. It is known that there is a strong correlation between the primary mass power law index, $alpha$, and the 
-redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- the inferred rate must drastically increase 
-with resdshift to explain the few higher mass events in our catalog, but when one infers a flatter distribution like the MSPline inferred
-distribition in plot \ref{fig:mass_distribution}, the higher mass mergers are consistent with the local merger rate denstiy as a function of mass, 
-and thus the model does not need to have as steep of power-law in redshift. With this more flexible mass population model, we now 
-find that the merger rate is fully consistent with being unifom with co-moving volume, rather than the confidently evolving merger rate 
-conclusion from \bruce{cite O3b}.
 
@@
 
-In addition to the primary mass distirbution there is some mild evidence for a mass ratio distibution that is not well described by a power law, 
-which is how the mass ratio distribution is commonly modeled. In particular our smoothed MSpline model finds a decrease in the merger rate at $q\sim1$, 
-while agreeing well with the power-law on the decline in rate from $q \in [0.4, 0.8]$, and a much larger tail extending to more asymmetric
-mass ratios.
+We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneosly infer the astrophysical mass, spin and redshift distributions of 
+a binary black holes (BBHs) given a catalog of gravitational wave observations. We parameterize the binaries' masses with the primary (defined as the more massive component) mass 
+and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. We model 4 of the 6 total 
+spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
+$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular mommentum vector. 
+We additionally will fit a population model on the redshift or luminosity distance distribution of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology using the 
+parameters from the Planck 2015 results \cite{Planck2015}, which defines an analytical mapping between each event's inferred
+luminosity distance and it's redshift. While we choose to use MSpline distibutions to model the primary mass and spin distributions, we 
+model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$. 
+Where $\beta$ is the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \cite{Talbot_2019,o1o2_pop,o3a_pop}.
+We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model \cite{Fishbach_2018redshift}, which is desribed by 
+$p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$. We describe our specific prior choices on the hyper-parameters and each model 
+in more detail in Appendix \ref{sec:modelpriors}. We use the same cut on the recent GWTC-3 catalog as was done in the LVK's accompanying population analysis, 
+keeping all 70 possibly BBH mergers with false alarm rates less than 1 per year \cite{GWTC3,o3b_astro_dist}. We choose to emit the currently not well understood event, 
+GW190814 \cite{190814disc}, as it was concluded to be an outlier of the rest of the BBH population in both GWTC-2 and GWTC-3 \cite{o3a_pop,o3b_astro_dist,Essick_2022}. 
+This leaves us with a catalog of 69 BBH mergers observerd oveer a period of about 2 years, from which we want to infer its population properties. 
+We start by looking towards the mass distribution.
+
+\subsection{BBH Mass Distibution} \label{sec:mass_dist}
+
+%PLPeak: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_99percentile]}$}
+%PLSpline: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_99percentile]}$}
+%MSpline: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_99percentile]}$}
+
+We apply our newly constructed models to the BBH analysis that was done in the astrophysical population companion paper to GWTC-3. 
+Figure \ref{fig:mass_distribution} shows how the MSpline model (red) found consistent features in the mass disribution with 
+what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \cite{Talbot_2019,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
+In particular our MSpline model finds a peak in merger rate density at both 10 and 35 soloar masses, agreeing with those reported using the same dataset in \citet{o3b_astro_dist}. 
+We also find a significantly less declining mass distribution that has considerably larger support for higher mass mergers when 
+compared to the other power-law based models. Another interesting consequence of this is that we no longer find an confidently
+evolving merger rate with redshift, as inferred with power-law based models. There is a strong correlation between the primary mass 
+power law index, $\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- the inferred 
+rate must drastically increase with resdshift to explain the highest mass events in the catalog. However, when one infers a 
+flatter distribution like, as the MSPline did in figure \ref{fig:mass_distribution}, the higher mass mergers are consistent with 
+the local merger rate denstiy as a function of mass. With the more flexible mass population model, we find that the merger rate 
+is consistent with being unifom with co-moving volume with $\lambda_z = $\resut{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared 
+to $\lambda_z = $\resut{$\CIPlusMinus{\macros[PLPeak][lamb]}$} found with the \textsc{PowerlawPeak} model.
+
+We also find a mass ratio distribution with more support for unequal mass ratios, with power law index 
+$\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} 
+found with the \textsc{PowerlawPeak} model. This can also be in part related with the harder mass distribution 
+as mentioned above. More support for higher mass primaries  -- since total mass is measured better -- increases support for more unequal 
+mass ratio binaries.
 
@@
 
-\subsection{Discussion}
-
 \begin{figure}
@@
 \end{figure}
-
-\bruce{Here we discuss the astrophysical implications of work -- connect to wider literature}

### 2022-09-26 src/scripts/create_macros.py

@@ -6,7 +6,7 @@ import paths
 import numpy as np
 import deepdish as dd
 from scipy.integrate import cumtrapz
-from utils import load_iid_tilt_ppd, load_ind_tilt_ppd, save_param_cred_intervals, load_o3b_paper_run_masspdf, load_mass_ppd
+from utils import load_iid_tilt_ppd, load_ind_tilt_ppd, save_param_cred_intervals, load_o3b_paper_run_masspdf, load_mass_ppd, load_iid_posterior, load_ind_posterior, load_o3b_posterior
 
 
 def get_m1_m99(pdfs, ms):
@@ -65,7 +65,11 @@ def MSplineIIDSpinMacros():
     peak_tilts = np.array(peak_tilts)
     gamma_fracs = np.array(gamma_fracs)
     frac_neg_cts = np.array(frac_neg_cts)
-    return {'peakCosTilt': save_param_cred_intervals(peak_tilts), 
+    posts = load_iid_posterior()
+
+    return {'beta': save_param_cred_intervals(posts['beta']),
+            'lamb': save_param_cred_intervals(posts['lamb']),
+            'peakCosTilt': save_param_cred_intervals(peak_tilts), 
             'log10gammaFrac': save_param_cred_intervals(np.log10(gamma_fracs)), 
             'negFrac': save_param_cred_intervals(frac_neg_cts)}
 
@@ -98,8 +102,11 @@ def MSplineIndSpinMacros():
     gamma_fracs2 = np.array(gamma_fracs2)
     frac_neg_cts1 = np.array(frac_neg_cts1)
     frac_neg_cts2 = np.array(frac_neg_cts2)
+    posts = load_ind_posterior()
 
-    return {'peakCosTilt1': save_param_cred_intervals(peak_tilts1), 'peakCosTilt2': save_param_cred_intervals(peak_tilts2), 
+    return {'beta': save_param_cred_intervals(posts['beta']),
+            'lamb': save_param_cred_intervals(posts['lamb']),
+            'peakCosTilt1': save_param_cred_intervals(peak_tilts1), 'peakCosTilt2': save_param_cred_intervals(peak_tilts2), 
             'log10gammaFrac1': save_param_cred_intervals(np.log10(gamma_fracs1)), 'log10gammaFrac2': save_param_cred_intervals(np.log10(gamma_fracs2)), 
[…]

### 2022-09-26 src/scripts/utils.py

@@ -1,7 +1,7 @@
 import numpy as np
 import jax.numpy as jnp
 import paths
-import json
+from bilby.core.result import read_in_result
 import deepdish as dd
 
 
@@ -31,15 +31,6 @@ def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None
             ax.plot(xs, ar[idx], color=tracecolor, lw=0.025, alpha=0.02)  
     
     return ax
-
-
-def save_macro(subdict):
-    with open(paths.data / "macros.json", 'r') as f:
-        old_macro = json.load(f)
-    new_macro = old_macro.copy()
-    new_macro.update(subdict)
-    with open(paths.data / "macros.json", 'w') as f:
-        json.dump(new_macro, f)
 
 
 def powerlaw_pdf(xx, alpha, low, high):
@@ -485,6 +476,15 @@ def load_ind_mag_ppd():
     datadict = dd.io.load(paths.data / 'mspline_50m1_16ind_compspins_smoothprior_powerlaw_q_z_ppds.h5')
     return datadict['dRda1'], datadict['dRda2'], datadict['mags'], datadict['mags']
 
+
+def load_ind_posterior():
+    return dd.io.load(paths.data / 'mspline_50m1_16ind_compspins_smoothprior_powerlaw_q_z_ppds.h5')
+
+def load_iid_posterior():
+    return dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_ppds.h5')
+
+def load_o3b_posterior(filename):
+    return read_in_result(paths.data / filename).posterior
 
 def load_o3b_paper_run_masspdf(filename):
     """

### 2022-09-26 src/tex/macros.tex
fixtypo

--- 2022-09-25 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"MSplineIIDCompSpins": \{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "MSplineIndependentCompSpins": \{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}\}}\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\def\macros@out{??}\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@I@out\macros@III\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@I@out\macros@IV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@I@out\macros@V\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@VI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@VII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@III@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@III@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@III@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@III@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@III@out{1.00}\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IV@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IV@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IV@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IV@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IV@out{0.96}\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@V@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@V@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@V@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@V@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@V@out{0.47}\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{0.89}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{1.00}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{0.84}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.99}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.62}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.57}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XV\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XX\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXIV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.00}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.00}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.84}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{0.99}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.62}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.57}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{3.31}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{1.00}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{1.00}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.96}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.47}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXI@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXI@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXI@out\macros@XXX\else\def\macros@XXI@out{??}\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIX\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXV@out\macros@XLI\else\def\macros@XXV@out{??}\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@XLIII\else\def\macros@XXVI@out{??}\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@XLV\else\def\macros@XXVII@out{??}\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.03}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.49}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.05}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.05}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.44}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.07}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.05}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.47}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.05}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.12}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.50}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.07}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{6.32}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{5.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{6.90}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{44.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{38.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{55.46}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{6.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{5.82}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{6.59}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{80.10}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{11.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{12.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{67.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{91.26}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{5.83}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{1.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{1.47}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{4.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{6.81}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{43.20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{10.47}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{38.49}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{54.97}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLV@out}\makeatother

### 2022-09-26 src/tex/results.tex
fixtypo

@@
 the local merger rate denstiy as a function of mass. With the more flexible mass population model, we find that the merger rate 
-is consistent with being unifom with co-moving volume with $\lambda_z = $\resut{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared 
-to $\lambda_z = $\resut{$\CIPlusMinus{\macros[PLPeak][lamb]}$} found with the \textsc{PowerlawPeak} model.
+is consistent with being unifom with co-moving volume with $\lambda_z = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared 
+to $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} found with the \textsc{PowerlawPeak} model.
 

### 2022-09-26 src/scripts/utils.py

@@ -478,10 +478,10 @@ def load_ind_mag_ppd():
 
 
 def load_ind_posterior():
-    return dd.io.load(paths.data / 'mspline_50m1_16ind_compspins_smoothprior_powerlaw_q_z_ppds.h5')
+    return dd.io.load(paths.data / 'mspline_50m1_16ind_compspins_smoothprior_powerlaw_q_z_posterior_samples.h5')
 
 def load_iid_posterior():
-    return dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_ppds.h5')
+    return dd.io.load(paths.data / 'mspline_50m1_16iid_compspins_smoothprior_powerlaw_q_z_posterior_samples.h5')
 
 def load_o3b_posterior(filename):
     return read_in_result(paths.data / filename).posterior

### 2022-09-26 src/tex/results.tex
fix q

@@
 
-We also find a mass ratio distribution with more support for unequal mass ratios, with power law index 
-$\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} 
-found with the \textsc{PowerlawPeak} model. This can also be in part related with the harder mass distribution 
-as mentioned above. More support for higher mass primaries  -- since total mass is measured better -- increases support for more unequal 
-mass ratio binaries.
+We find a similar mass ratio distribution to what was found with the found with the \textsc{PowerlawPeak} model in \citet{o3b_astro_dist}. 
+With the MSpline model on primary mass the mass ratio power law index is $\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, 
+compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} for \textsc{PowerlawPeak}.
 

### 2022-09-26 src/tex/results.tex
move macros

@@
 
+MSpline IID:
+$\cos{\theta}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}
+$\gamma = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}
+$f_{<0} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}
+MSpline Independent:
+$\cos{\theta_1}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$} and $\cos{\theta_2}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}
+$\gamma_1 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and $\gamma_2 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$} 
+$f_{1,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}
+
 The spins distribution of merging combact binaries provides a very useful insight into the formation history of the binary. In particular the two main subcategories, 
@@
 
+Default: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$} 
+$f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} 
+$\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$}
+
+MSplineIID: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelowNeg0p3]}$}
+   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$} 
+   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$}
+
+MSplineIND: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$}
+   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$} 
+   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$}
+
+MSplineChiEff: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelowNeg0p3]}$}
+      $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$} 
+      $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}
+
 Present results fitting chi eff dist with MSpline I am making a change.

### 2022-09-26 src/tex/intro.tex
add more citations

@@
 understanding of the population properties CBCs, just 7 years after the first observation \cite{o1o2_pop,o3a_pop,o3b_astro_dist}. 
-In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration detectors \cite{aLIGO,aVIRGO, KAGRA}, with the increased sensitivities, 
+In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration detectors \citep{aLIGO,aVIRGO}, with the increased sensitivities, 
 there could be a detection as often as every day \cite{LVK_prospects}. This large influx of incoming data will drastically increase what we can learn by combining all observations
@@
 of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitation radiation emitted. The population distibutions 
-of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB}, 
-constrain modified gravitational wave propagation, constrain a running Planck mass, look for evidence of ultralight bosons through superradiance, 
-constrain stellar nuclear reaction rates \cite{Farmer_2020}, look for primordial black holes \cite{Ng_2021}, and constrain the neutron star equation of state \bruce{Cite all points}. 
+of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, 
+constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,Ng_BosonGWTC2_2021},
+constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, and constrain the neutron star equation of state \citep{Golomb_EOS}.
 Through a better understanding of the mass, spin, and redshift distributions of compact binaries that will come with the increased catalog size, 

### 2022-09-26 src/tex/intro.tex
fix citation

@@
 of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, 
-constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,Ng_BosonGWTC2_2021},
+constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng},
 constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, and constrain the neutron star equation of state \citep{Golomb_EOS}.
 Through a better understanding of the mass, spin, and redshift distributions of compact binaries that will come with the increased catalog size, 
-one can probe a wide range of different physical phenoma with even greater fidelity.
+one can probe a wide range of different physical phenoma with even greater fidelity. \bruce{Cite others??}
 

### 2022-09-26 src/tex/macros.tex
fix citation

--- 2022-09-25 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"MSplineIndependentCompSpins": \{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@III\else\def\macros@out{??}\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@I@out\macros@IV\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@I@out\macros@V\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XII\else\def\macros@II@out{??}\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@III@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@III@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@III@out\macros@XV\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@III@out\macros@XVI\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IV@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IV@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IV@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IV@out{0.89}\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@V@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@V@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@V@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@V@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@V@out{1.00}\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{0.84}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{0.99}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{0.62}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.57}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{1.00}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.96}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.47}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XIII@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XIII@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XIII@out\macros@XIX\else\def\macros@XIII@out{??}\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XIV@out\macros@XX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XIV@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XIV@out\macros@XXII\else\def\macros@XIV@out{??}\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XV@out\macros@XXV\else\def\macros@XV@out{??}\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XVI@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XVI@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XVI@out\macros@XXVIII\else\def\macros@XVI@out{??}\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.03}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{0.49}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.05}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.05}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.44}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.07}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.05}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{0.47}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.05}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.12}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.50}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.07}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XV\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XX\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXIV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.00}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.00}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.84}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{0.99}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.62}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.57}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{3.31}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{1.00}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{1.00}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.96}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.47}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXI@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXI@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXI@out\macros@XXX\else\def\macros@XXI@out{??}\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIX\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXV@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXV@out\macros@XLII\else\def\macros@XXV@out{??}\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@XLV\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@XLVIII\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.03}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.49}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.05}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.05}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.44}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.07}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.05}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.47}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.05}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.12}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.50}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.07}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{6.81}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{14.95}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{5.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{2.75}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{12.20}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{21.03}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{44.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{38.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{55.46}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{5.91}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{5.72}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{6.50}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{30.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{4.42}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{7.86}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{22.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{34.17}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{80.10}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{11.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{12.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{67.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{91.26}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{6.81}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{11.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{4.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{10.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{16.62}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{43.20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{10.47}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{38.49}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{54.97}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\makeatother

### 2022-09-26 src/scripts/create_macros.py

@@ -9,45 +9,39 @@ from scipy.integrate import cumtrapz
 from utils import load_iid_tilt_ppd, load_ind_tilt_ppd, save_param_cred_intervals, load_o3b_paper_run_masspdf, load_mass_ppd, load_iid_posterior, load_ind_posterior, load_o3b_posterior
 
 
-def get_m1_m99(pdfs, ms):
-    m99 = []
-    m1 = []
+def get_percentile(pdfs, xs, perc):
+    x = []
     for m in pdfs:                                                                                                                                                                        
         i = len(m)
-        cumulative_prob = cumtrapz(m, ms, initial = 0)
+        cumulative_prob = cumtrapz(m, xs, initial = 0)
         init_prob = cumulative_prob[-1]
         prob = init_prob
-        final_prob = init_prob*0.99                                                                                                                                              
+        final_prob = init_prob * perc / 100.0                                                                                                                                              
         while prob > (final_prob):
             i -= 1
             prob = cumulative_prob[i]                                                                                                                                                         
-        m99.append(ms[i])
-    m99 = np.array(m99)
-    for m in pdfs:
-        i = 0
-        cumulative_prob = cumtrapz(m, ms, initial = 0)
-        init_prob = cumulative_prob[-1]
-        prob = 0
-        final_prob = init_prob*0.01
-        while prob < (final_prob):
-            i += 1
-            prob = cumulative_prob[i]
-        m1.append(ms[i])
-    m1 = np.array(m1)
-    return m1, m99
+        x.append(xs[i])
+    return np.array(x)
 
 
 def MSplineMassMacros():
     print("Saving Mass Distribution Macros...")
     ms, m_pdfs, _, _ = load_mass_ppd()
-    m1s, m99s = get_m1_m99(m_pdfs, ms)
+    m1s = get_percentile(m_pdfs, ms, 1)
+    m99s = get_percentile(m_pdfs, ms, 99)
[…]

### 2022-09-26 src/tex/macros.tex
add tilt spin results text -- chieff only left

--- 2022-09-26 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"MSplineIndependentCompSpins": \{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@IV\else\def\macros@out{??}\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@I@out\macros@V\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@I@out\macros@IX\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@I@out\macros@X\else\def\macros@I@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XIII\else\def\macros@II@out{??}\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@III@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@III@out\macros@XV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@III@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@III@out\macros@XVII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"PLPeak": \{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@IV@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@IV@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@IV@out\macros@XX\else\def\macros@IV@out{??}\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@V@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@V@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@V@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@V@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@V@out{0.89}\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{1.00}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{0.84}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{0.99}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.62}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.57}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.00}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.96}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{0.47}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XIV@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XIV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XIV@out\macros@XXIII\else\def\macros@XIV@out{??}\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XV@out\macros@XXVI\else\def\macros@XV@out{??}\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XVI@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XVI@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XVI@out\macros@XXIX\else\def\macros@XVI@out{??}\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XVII@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XVII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XVII@out\macros@XXXII\else\def\macros@XVII@out{??}\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XVIII@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XVIII@out\macros@XXXIV\else\def\macros@XVIII@out{??}\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XIX@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XIX@out\macros@XXXVI\else\def\macros@XIX@out{??}\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XX@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XX@out\macros@XXXVIII\else\def\macros@XX@out{??}\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.03}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.49}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.05}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{0.05}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.44}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.07}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.05}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.47}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.05}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.12}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.50}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.07}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{6.32}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{5.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{6.90}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{44.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{38.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{55.46}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{6.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{5.82}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{6.59}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{80.10}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{11.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{12.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{67.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{91.26}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{5.83}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{1.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{1.47}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{4.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{6.81}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{43.20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{10.47}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{38.49}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{54.97}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "a1\_90percentile": \{"median": "0.75", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.58", "95th percentile": "0.89"\}, "a2\_90percentile": \{"median": "0.78", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.61", "95th percentile": "0.91"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "a\_90percentile": \{"median": "0.69", "error plus": "0.15", "error minus": "0.16", "5th percentile": "0.53", "95th percentile": "0.84"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "a1\_90percentile": \{"median": "0.75", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.58", "95th percentile": "0.89"\}, "a2\_90percentile": \{"median": "0.78", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.61", "95th percentile": "0.91"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "a\_90percentile": \{"median": "0.69", "error plus": "0.15", "error minus": "0.16", "5th percentile": "0.53", "95th percentile": "0.84"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXVII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXX\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.00}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.75", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.58", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.75}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.58}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.78", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.61", "95th percentile": "0.91"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.78}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.91}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.89}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.00}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.84}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.99}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.62}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.57}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{3.31}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": "0.69", "error plus": "0.15", "error minus": "0.16", "5th percentile": "0.53", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.69}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.53}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.84}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.00}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{1.00}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.96}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.47}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIII\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXVI\else\def\macros@XXV@out{??}\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XXXIX\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XL\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLII\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@XLV\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@XLVIII\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@L\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LI\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.03}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.49}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.05}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.05}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.44}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.07}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.05}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.47}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.05}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.12}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.50}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.07}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{6.81}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{14.95}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{5.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{2.75}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{12.20}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{21.03}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{44.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{38.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{55.46}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{5.91}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{5.72}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{6.50}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{30.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{4.42}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{7.86}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{22.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{34.17}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{80.10}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{11.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{12.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{67.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{91.26}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{6.81}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{11.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{4.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{10.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{16.62}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{43.20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{10.47}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{38.49}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{54.97}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\macros@LI@out}\makeatother

### 2022-09-26 src/tex/results.tex
move figs
add tilt spin results text -- chieff only left

@@
 
-%PLPeak: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_99percentile]}$}
-%PLSpline: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_99percentile]}$}
-%MSpline: $m_{1\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_1percentile]}$}, $m_{99\%} = $\result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_99percentile]}$}
-
 We apply our newly constructed models to the BBH analysis that was done in the astrophysical population companion paper to GWTC-3. 
@@
 We also find a significantly less declining mass distribution that has considerably larger support for higher mass mergers when 
-compared to the other power-law based models. Another interesting consequence of this is that we no longer find an confidently
-evolving merger rate with redshift, as inferred with power-law based models. There is a strong correlation between the primary mass 
-power law index, $\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- the inferred 
-rate must drastically increase with resdshift to explain the highest mass events in the catalog. However, when one infers a 
+compared to the other power-law based models, finding that 75\% percent of primary masses below \result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_75percentile]}$}, 
+at 90\% credibility, compared to \result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_75percentile]}$}, found with the similar \textsc{PowerlawSpline} model. 
+An interesting consequence of this is that we do not find a confidently evolving merger rate with redshift, as inferred with power-law based mass models in \citet{o3b_astro_dist}. 
+There is a strong correlation between the primary mass power law index, $\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- 
+the inferred rate must drastically increase with resdshift to explain the highest mass events in the catalog. However, when one infers a 
 flatter distribution like, as the MSPline did in figure \ref{fig:mass_distribution}, the higher mass mergers are consistent with 
-the local merger rate denstiy as a function of mass. With the more flexible mass population model, we find that the merger rate 
-is consistent with being unifom with co-moving volume with $\lambda_z = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared 
-to $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} found with the \textsc{PowerlawPeak} model.
+the local merger rate denstiy as a function of mass given the selection effects. With our more flexible mass model, we find that the merger rate 
+is consistent with being unifom with co-moving volume, with $\lambda_z = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared with 
+\citet{o3b_astro_dist}'s reported value -- $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} with the \textsc{PowerlawPeak} mass model.
 
@@
 With the MSpline model on primary mass the mass ratio power law index is $\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, 
-compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} for \textsc{PowerlawPeak}.
+compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} for \textsc{PowerlawPeak}. We find that BBH mergers favor more equal mass mergers
+as would be expected of both main formation channels due to binary mass transfer in isolated formation and three-body interactions that preferentially eject
+the lightest of the three compact objects, in dynamical formation \bruce{cite these}. We also find no evidence for a sharp fall off in merger rate following 
+the pileup at $\sim35\,\msun$, which is expected if such a pileup was due to pulsational pair instability supernovae (PPISNe). The lack of any high mass truncation 
+along with the peak at 35\msun, significantly lower than expected, may pose challenges for conventional stellar evolution theory and could be a sign of 
+the significant presence of sub-populations that may avoid PISN as the binary forms.
 
@@
 
-\subsubsection{Spin Magnitude}
-
-\subsubsection{Spin Orientation}
-
-MSpline IID:
-$\cos{\theta}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}
-$\gamma = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}
-$f_{<0} = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}
-MSpline Independent:
-$\cos{\theta_1}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$} and $\cos{\theta_2}_\mathrm{max} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}
-$\gamma_1 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and $\gamma_2 = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$} 
-$f_{1,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0} = $\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}
-
-The spins distribution of merging combact binaries provides a very useful insight into the formation history of the binary. In particular the two main subcategories, 
-the isolated and dynamical formation channels, would produce distinct signatures in the spin distribution when looking at a population of observations. Isolated formation
-is where the only interactions with the binary are between each other. As the binary evolves and mass transfer happens between the two components, we expect the orientation
-of each components spin vector to be preferentially aligned with the orbital angular mommentumof the system. Some misalignment is epected to occur due to the kicks from 
-each star exploding in supernovae leaving behind the compact objects. Conversely, the dynamical channel     
 \begin{figure}
@@
 \end{figure}
+
+\subsubsection{Spin Magnitude}
+
+The \textsc{Default} spin model models the spin magnitude of both components as identical and indendendently distributed (IID) non-singular Beta distributions. The
+Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 
+the Beta distribution non-singluar (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. While in reality, it is expected that 
+all physical bodies must have at least some non-zero angular mommentum, studies have proposed the existence of a distinct sub-population of non-spinning or 
+negliglby spinning black holes that can elude discovery with such a model.
+
+\begin{figure}
+    \script{plot_ind_spinmag.py}
+    \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
+    \caption{Caption.}
+    \label{fig:ind_spinmag_dist}
+\end{figure}
+
+We model the spin magnitude distibutions as IID MSpline distibutions as a flexible check
+to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the \textsc{MSpline} model, 
+compared with the \textsc{Default} model from \citet{o3b_astro_dist}. The MSpline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
+of BBH spins below \result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility. The regions of parameter space where they don't agree as well are the bounds. 
+The MSpline model has no enforcment for vanishing support at the extremal values like the Beta distribution, 
+allowing it to probe the zero-spin question. We find broad support, with large variance, for non-zero probabilities at $a_i=0$, but cannot confidently determine the presence of 
+a significant non-spinning subpopulation, corroborating the conclusions of \citet{BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}. 
+We now repeat the same analysis as above but with independent MSpline distibutions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
+we show the inferred primary (orange), and secondary (olive) spin magnitude distributions inferred when relaxing the IID assumption. We find both 
+distributions to be remarkably similar, showing no signs that each component spin magnitude are distributed differently from each other.
+
+\subsubsection{Spin Orientation}
+
+The \textsc{Default} spin model models the spin orientation of both components as identical and indendendently distributed (IID) mixture models over an
+aligned and an isotropic component. The aligned component is modeled with a truncated Gaussian distribution with mean at $\cos{\theta}=1$ and variance a free 
+hyper-parameter to be fit. This provides a simple 2-parameter model motivated by simple distributions expected from the two main formation scenario families, allowing 
+for a straightforward interpretation of results. One possible limitation however, is that by construction this distribution is forced to peak at perfecty aligned spins, 
+i.e. $\cos{\theta}=1$. While this may be a reasonable assumption recently \citet{spinitasyoulike} recently extended the model space of parameteric descriptions 
+used to model the spin orientation distribution and found considerably evidence that the distibution peaks away from $\cos{\theta}=1$. Again, this provides a clear 
+use-case where data-driven models can help in our understanding and possibly resolve disputes among differing parametric approaches.
 
@@
 
-Comment here are the inferences of iid model vs Default and then iid vs independent test pointing out possible reasons for why spin tilt 
-does not peak at cos theta = 1 i.e. salvo's paper
+We repeat the tests done above on the the spin magnitude distibutions now with the spin orientation distributions. Figure \ref{fig:iid_spintilt_dist} 
+shows the inferred spin magnitude distribution with the \textsc{MSpline} model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
+The MSpline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
+We find a distribution that instead of intrinsicly peaking at $\cos{\theta}=1$, is found to peak at: $\cos{\theta}=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}, at 
+90\% credibility. We find less, but still considerable, support for misaligned spins (i.e. $\cos{\theta}<0$) as the \textsc{Default} model. Specifically we 
+find that the fraction of misaligned systems is $f_{<0}=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}. This implies 
+the presence of an isotropic component as expected by dynamical formation channels, albeit less than with the \textsc{Default} model. To quantify the 
+amount of isotropy in the tilt distibution we calculate Y, the ratio defined in Eq. 4 of \citet{spinitasyoulike} which is 1 when the distribution is 
+purely isotropic, less than one when negative (anti-aligned) values are favored, and greater than one when positive (aligned) values are favored.
+We find a $\log_{10}Y=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}.
+
+Now we model each of the components' orientation distributions with independent \textsc{MSpline} models as done above, and show the inferred 
+distributions in figure \ref{fig:ind_spintilt_dist}. The primary and secondary orientation distibutions do not agree as well as the magnitude 
+distibutions did in figure \ref{fig:ind_spinmag_dist}, and the PPDs look to peak at different values, but the wide uncertainties still are 
+consistent with both each other and the \textsc{Default} model's PPD.
+We find the two distributions to peak at: $\cos{\theta_1}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$}
+and $\cos{\theta_2}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}, showing that the primary distribution peak is inferred further away 
+from the assumed $\cos{\theta}=1$ with the \textsc{Default} model. There is also significant (albeit uncertain) evidence of spin mis-alignments in each distribution, finding 
+the fraction of mis-aligned primary and secondary components as: $f_{1,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}.
+We again calculate the isotropy ratio, Y, for each and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
+$\log_{10}Y_2=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$}.
+
+\begin{figure}
+    \script{plot_ind_spintilt.py}
+        \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
+        \caption{Caption.}
+        \label{fig:ind_spintilt_dist}
+\end{figure}
 
 \subsection{The Effective Spin Dimension}
+
+\begin{figure}
+    \script{plot_chieff.py}
+    \includegraphics[width=0.45\textwidth]{figures/chi_eff.pdf}
+    \caption{Caption.}
+    \label{fig:chieff_dist}
+\end{figure}
 
@@
 Present results fitting chi eff dist with MSpline I am making a change.
-
-\begin{figure}
-    \script{plot_ind_spinmag.py}
-    \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
-    \caption{Caption.}
-    \label{fig:ind_spinmag_dist}
-\end{figure}
-
-\begin{figure}
-    \script{plot_ind_spintilt.py}
-        \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
-        \caption{Caption.}
-        \label{fig:ind_spintilt_dist}
-\end{figure}
-
-\begin{figure}
-    \script{plot_chieff.py}
-    \includegraphics[width=0.45\textwidth]{figures/chi_eff.pdf}
-    \caption{Caption.}
-    \label{fig:chieff_dist}
-\end{figure}

### 2022-09-26 src/scripts/create_macros.py

@@ -6,7 +6,7 @@ import paths
 import numpy as np
 import deepdish as dd
 from scipy.integrate import cumtrapz
-from utils import load_iid_tilt_ppd, load_ind_tilt_ppd, save_param_cred_intervals, load_o3b_paper_run_masspdf, load_mass_ppd, load_iid_posterior, load_ind_posterior, load_o3b_posterior
+from utils import load_iid_mag_ppd, load_iid_tilt_ppd, load_ind_mag_ppd, load_ind_tilt_ppd, save_param_cred_intervals, load_o3b_paper_run_masspdf, load_mass_ppd, load_iid_posterior, load_ind_posterior, load_o3b_posterior
 
 
 def get_percentile(pdfs, xs, perc):
@@ -60,8 +60,9 @@ def MSplineIIDSpinMacros():
     gamma_fracs = np.array(gamma_fracs)
     frac_neg_cts = np.array(frac_neg_cts)
     posts = load_iid_posterior()
-
+    mags, a_pdfs = load_iid_mag_ppd()
     return {'beta': save_param_cred_intervals(posts['beta']),
+            'a_90percentile': save_param_cred_intervals(get_percentile(a_pdfs, mags, 90)),
             'lamb': save_param_cred_intervals(posts['lamb']),
             'peakCosTilt': save_param_cred_intervals(peak_tilts), 
             'log10gammaFrac': save_param_cred_intervals(np.log10(gamma_fracs)), 
@@ -97,9 +98,11 @@ def MSplineIndSpinMacros():
     frac_neg_cts1 = np.array(frac_neg_cts1)
     frac_neg_cts2 = np.array(frac_neg_cts2)
     posts = load_ind_posterior()
-
+    a1_pdfs, a2_pdfs, mags, mags = load_ind_mag_ppd()
     return {'beta': save_param_cred_intervals(posts['beta']),
             'lamb': save_param_cred_intervals(posts['lamb']),
+            'a1_90percentile': save_param_cred_intervals(get_percentile(a1_pdfs, mags, 90)),
+            'a2_90percentile': save_param_cred_intervals(get_percentile(a2_pdfs, mags, 90)),
             'peakCosTilt1': save_param_cred_intervals(peak_tilts1), 'peakCosTilt2': save_param_cred_intervals(peak_tilts2), 
[…]

### 2022-09-26 src/tex/results.tex
add chieff results

@@
 
-\subsection{BBH Mass Distibution} \label{sec:mass_dist}
+\subsection{Binary Black Hole Masses} \label{sec:mass_dist}
 
@@
 
-\subsection{BBH Component Spin Distributions} \label{sec:spin_dist}
+\subsection{Binary Black Hole Spins} \label{sec:spin_dist}
 
@@
 Now we model each of the components' orientation distributions with independent \textsc{MSpline} models as done above, and show the inferred 
-distributions in figure \ref{fig:ind_spintilt_dist}. The primary and secondary orientation distibutions do not agree as well as the magnitude 
-distibutions did in figure \ref{fig:ind_spinmag_dist}, and the PPDs look to peak at different values, but the wide uncertainties still are 
+primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distibutions do not agree quite as well as 
+the magnitude distibutions did in figure \ref{fig:ind_spinmag_dist}, and the PPDs look to peak at different values, but the wide uncertainties still are 
 consistent with both each other and the \textsc{Default} model's PPD.
@@
 
-Transform comp spin results to effective dims to see how strong changes in mag/tilt dont significantly affect our best constrained/measured
-effective spins
-
-Default: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$} 
-    $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} 
-    $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$}
-
-MSplineIID: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelowNeg0p3]}$}
-   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$} 
-   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$}
-
-MSplineIND: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$}
-   $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$} 
-   $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$}
-
-MSplineChiEff: $f_{\chi_\mathrm{eff}<-0.3} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelowNeg0p3]}$}
-    $f_{\chi_\mathrm{eff}<0} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$} 
-    $\chi_\mathrm{eff, peak} = $\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}
-
-Present results fitting chi eff dist with MSpline I am making a change.
+While the component spin magnitude and tilts are more easily interpretable in context of the astrophysics, they are parameters that 
+are not measured well during individual event parameter estimation. The best measured spin parameter, that enters the waveform at XXPN, is 
+called the effective spin defined as: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$. As an alternative check 
+on the spin distributions we also try modeling an MSpline distribution of effective spins instead of component spin magnitude and tilts 
+as done above. Figure \ref{fig:chieff_dist} shows the inferred effective spin distribution with the MSpline model (red) along with the 
+inferred effective spin distribution transformed from the PPDs of the component spin models shown previously. We find considerable agreement 
+among the component spin distributions, highlighting that wildy different component spin distributions can imply very similar effective spin 
+distributions which is the better constrained parameter. When modeling the effective spin with the \textsc{MSpline} model we see very similar 
+shape, but with a slightly sharper peak centered at $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}, compared to 
+$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model. As for the misaligned spin question, 
+we can investigate the fraction of systems with effective spins that are mis-aligned (i.e. $\chi_\mathrm{eff}<0$) and find for the \textsc{MSpline} 
+model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}, compared to $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$}
+with the \textsc{Default} model.

### 2022-09-26 src/tex/ms.tex
move macros
update readme
add abstract

--- 2022-09-25 src/tex/ms.tex
@@
 
-\author{Jaxen Godfrey}
-\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
+%\author{Jaxen Godfrey}
+%\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
 
-\author{Alexis Vives}
-\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
+%\author{Alexis Vives}
+%\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
 
-\author{Jon Hornung}
-\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-\affiliation{Thurston High School, Springfield, OR 9747, USA}
+%\author{Jon Hornung}
+%\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
+%\affiliation{Thurston High School, Springfield, OR 9747, USA}
 
@@
 We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 
-binary black hole masses and spins using the 69 confident observations in GWTC-3. We find the same features previously recovered 
-with similarly flexible models in the mass distribution, namely the peaks in merger rates at \~10\msun and \~35\msun. 
-We apply our method to investigate whether the spin components are indendendenty distributed with a model agnositc way, where we find that 
-the spin magnitude distribution seems to be quite consistently IID, with XX\% of black hole spins below XX at XX\% credibility. We report 
-slight evidence of tilt distributions that do not peak at $\cos(\theta_i) = 1$ as previous models assumed, and slight evidence that 
-the components are distributed differently, in contrast to the spin magnitude distribution. While we do not find signs of a significant
-zero spinning sub population we do find that the data prefer not to force the support for exactly zero spinning black holes to 0 as 
-the non-singular Beta distribution and \textsc{Default} model assumes. \result{$\CIPlusMinus{\macros[MSPlineIIDCompSpins][peakCosTilt]}$}
-\result{$\CIPlusMinus{\macros[MSPlineIndependentCompSpins][peakCosTilt1]}$}, \result{$\CIPlusMinus{\macros[MSPlineIndependentCompSpins][peakCosTilt2]}$}
+binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3. We report the same features previously recovered 
+with similarly flexible models in the mass distribution, most notably the peaks in merger rates at \~10\msun and \~35\msun. 
+We then use our method as the first non-parametric model applied to the BBH spin distribution, corroborating the results of \citet{spinitasyoulike}, 
+showing that tilt distributions may not peak at $\cos(\theta_i) = 1$ as previous models assumed. We find broad agreement with the 
+accepted conlcusions of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
+and there is mild support for a non-spinning subpopulaton, but cannot resolve this with current catalog sizes. We also test components whether the data 
+prefers the spin distributions to be identical for each component, finding no strong sign of differening distibutions. When modeling the $\chi_\mathrm{eff}$ 
+distribution with basis splines we find similar conclusions as previously reported, consistent with a non-isotropic distribution 
+(peaks at $\chi_\mathrm{eff}$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}), showing considerable support 
+($\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
+We conclude by discussing how non-parametric methods in gravitatonal-wave population inference are poised to provide a useful complement to 
+the usual parametric approach going into the data rich catalog era of gravitational-wave astronomy.
 \end{abstract}

### 2022-09-26 src/tex/appendicies.tex
update readme
more refs

@@
 
-Spline functions have been shown to be sensitivite to the chosen number of knots, and their locations or spacing. 
+Spline functions have been shown to be sensitivite to the chosen number of knots, and their locations or spacing \citep{deBoor78}. 
 Adding more knots knots increases the a-priori variance in the spline function, while the space between knots can limit the 
@@
 To overcome this we resort to the frequentist penalized spline (P-Spline) in which one applies a penalty or regularization term 
-to the likelihood based on the difference of adjacent knot coeficients. The linear combination of spline basis components is 
-is flat when the basis coeficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as the differences between adjacent
-knot coeficients get larger, one gets a smoothing of the spline function inferences. Since we are using hierarchical Bayesian inferece as our 
-statistical framework, we formulate this penalized likelihood with its Bayesian analog. The difference penalty is equivalent to applying a stochastic 
-differnece prior among the knots, as described in \bruce{CITE THIS PAPER}. This is also sometimes referred to as a Gaussian random walk prior, since
-each coeficient is normally distributed about its neighboring coeficients. For a spline basis with $n$ degree's of freedom, 
-and a difference penalty of order of $r$ (see \bruce{cite P-splines paper}), our prior is defined as:
+to the likelihood based on the difference of adjacent knot coeficients \citep{eilers2021practical}. The linear combination of spline basis components 
+or the resulting spline function is flat when the basis coeficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as 
+the differences between adjacent knot coeficients get larger, one gets a smoothing of the spline function inferences \citep{eilers2021practical}. 
+Since we are using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog. 
+The difference penalty is equivalent to applying a stochastic differnece prior among the knots, as described in  \\citet{BayesianPSplines,Jullion2007RobustSO}. 
+This is also sometimes referred to as a Gaussian random walk prior, since each coeficient is normally distributed about its neighboring coeficients. 
+For a spline basis with $n$ degree's of freedom, and a difference penalty of order of $r$ (see \citet{eilers2021practical}), the smoothing prior is defined as:
 
@@
 of knots such that your domain is densly populated with basis coeficients, this allows the freedom for the model to find the smoothing 
-scale that the data prefers. One downside of this prior specification as noted by\ bruce{CITE BAYESIAN PSPLINES}, is a slight dependence on choice 
-of the b hyper-parameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \bruce{CITE BAYESIAN PSPLINES} 
+scale that the data prefers. One downside of this prior specification as noted in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}, is a slight dependence on choice 
+of the b hyper-parameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \citet{Jullion2007RobustSO}
 to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyper-parameters. 
@@
 must ensure that the spline function is in fact flat given all equal coeficients. Since one needs to define n+k knots to construct an order-k basis with 
-n degrees of freedom, people often will place knots on top of each other at hard parameter boundaries \bruce{cite msplines / o-splines}. 
+n degrees of freedom, people often will place knots on top of each other at hard parameter boundaries \cite{deBoor78,monotone_regression_splines}. 
 This may seemed motivated, especially if there is no reality in the parameter beyond the boundary, but this violates the above condition. 
-We follow the distinction from \bruce{CITE psplines} that the difference penalty or smooothing prior is only valid with ``proper'' spline bases. 
+We follow the distinction from \citet{eilers2021practical} that the difference penalty or smooothing prior is only valid with ``proper'' spline bases. 
 A proper basis is where all n+k knots are evenly spaced, see Figure \ref{fig:spline_basis}, as opposed to stacking them at the bounds.
@@
 samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
-NUTS hamiltonian monte carlo sampler in \textsc{numpyro} and \textsc{jax} to calculate likelihoods \bruce{FIND citations for these}.
+NUTS hamiltonian monte carlo sampler in \textsc{NumPyro} and \textsc{Jax} to calculate likelihoods \citep{jax,pyro,numpyro}.
 
@@
 
-%\section{Validation Studies} \label{sec:validation}
+\section{Validation Studies} \label{sec:validation}
+
+\bruce{Need to fill this section}

### 2022-09-26 src/tex/methods.tex
move plot

@@
 \section{Constructing A Basis} \label{sec:basis_splines}
+
+\begin{figure}[ht!]
+    \script{spline_basis_plot.py}
+        \includegraphics[width=0.45\textwidth]{figures/spline_basis_plot.pdf}
+        \caption{Plot showing a ``proper'' MSpline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
+        In black we show the resulting spline function with given equal weights and denote the location of the knots with grey x's.}
+        \label{fig:spline_basis}
+\end{figure}
 
@@
 
-\begin{figure}[ht!]
-    \script{spline_basis_plot.py}
-        \includegraphics[width=0.45\textwidth]{figures/spline_basis_plot.pdf}
-        \caption{Plot showing proper MSpline bases with 20 degrees of freedom and equal weights for each component.}
-        \label{fig:spline_basis}
-\end{figure}
-
 \noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper. 

### 2022-09-26 src/tex/results.tex
Add captions

@@
         \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
-        \caption{Plot showing the primary mass distribution inferred with the \textsc{MSpline} model with 40 knots for $m_1$. We show the results for the 
-        \textsc{PowerlawSpline} (blue) model from the LVK's GWTC-3 population analyses.}
+        \caption{Plot showing the primary mass distribution inferred with the \textsc{MSpline} model (red), with 50 knots spaced lineary in $\log m_1$, from the 
+        minimum observed value to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
+        the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawSpline} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:mass_distribution}
@@
     \includegraphics[width=0.45\textwidth]{figures/iid_spinmag.pdf}
-    \caption{Caption.}
+    \caption{Plot showing the spin magnitude distribution inferred with the \textsc{MSpline} model (red), with 16 knots spaced linearly from 0 to 1, and 
+    assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
     \label{fig:iid_spinmag_dist}
@@
     \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
-    \caption{Caption.}
+    \caption{Plot showing the primary (orange) and secondary (olive) spin magnitude distributions inferred with the \textsc{MSpline} model, 
+    with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
     \label{fig:ind_spinmag_dist}
@@
     \includegraphics[width=0.45\textwidth]{figures/iid_spintilt.pdf}
-    \caption{Caption.}
+    \caption{Plot showing the spin orientation distribution inferred with the \textsc{MSpline} model (red), with 16 knots spaced linearly from -1 to 1, and 
+    assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
     \label{fig:iid_spintilt_dist}
@@
         \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
-        \caption{Caption.}
+        \caption{Plot showing the primary (orange) and secondary (olive) spin orientation distributions inferred with the \textsc{MSpline} model, 
+        with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+        We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:ind_spintilt_dist}
@@
     \includegraphics[width=0.45\textwidth]{figures/chi_eff.pdf}
-    \caption{Caption.}
+    \caption{Plot showing the effective spin distribution inferred with the \textsc{MSpline} model (red), with 24 knots spaced linearly from -1 to 1. 
+    The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. We show the inferred $\chi_\mathrm{eff}$ 
+    PPD from the IID component spin \textsc{MSpline} model (green), the independent component spin \textsc{MSpline} model (purple), 
+    and the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
     \label{fig:chieff_dist}

### 2022-09-26 src/tex/results.tex
cleanup captions

--- 2022-09-26 src/tex/results.tex
@@
         \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
-        \caption{Plot showing the primary mass distribution inferred with the \textsc{MSpline} model with 40 knots for $m_1$. We show the results for the 
-        \textsc{PowerlawSpline} (blue) model from the LVK's GWTC-3 population analyses.}
+        \caption{The primary mass distribution inferred with the \textsc{MSpline} model (red), with 50 knots spaced lineary in $\log m_1$, from the 
+        minimum observed value to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
+        the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawSpline} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:mass_distribution}
@@
     \includegraphics[width=0.45\textwidth]{figures/iid_spinmag.pdf}
-    \caption{Caption.}
+    \caption{The spin magnitude distribution inferred with the \textsc{MSpline} model (red), with 16 knots spaced linearly from 0 to 1, and 
+    assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
     \label{fig:iid_spinmag_dist}
@@
     \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
-    \caption{Caption.}
+    \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the \textsc{MSpline} model, 
+    with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
     \label{fig:ind_spinmag_dist}
@@
     \includegraphics[width=0.45\textwidth]{figures/iid_spintilt.pdf}
-    \caption{Caption.}
+    \caption{The spin orientation distribution inferred with the \textsc{MSpline} model (red), with 16 knots spaced linearly from -1 to 1, and 
+    assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
     \label{fig:iid_spintilt_dist}
@@
         \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
-        \caption{Caption.}
+        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the \textsc{MSpline} model, 
+        with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+        We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:ind_spintilt_dist}
@@
     \includegraphics[width=0.45\textwidth]{figures/chi_eff.pdf}
-    \caption{Caption.}
+    \caption{The effective spin distribution inferred with the \textsc{MSpline} model (red), with 24 knots spaced linearly from -1 to 1. 
+    The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. We show the inferred $\chi_\mathrm{eff}$ 
+    PPD from the IID component spin \textsc{MSpline} model (green), the independent component spin \textsc{MSpline} model (purple), 
+    and the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
     \label{fig:chieff_dist}

### 2022-09-26 src/tex/conclusion.tex
more macros and mass results
start discussion on masss (need to cite still)

@@
 
-\bruce{Here we discuss the astrophysical implications of work -- connect to wider literature}
+The collective distibution of BBH source properties provides a useful probe of the complex and uncertain astrophysics that governs their 
+formation and evolution to eventually merge \bruce{cite}. Our analysis with the newly constructed \textsc{MSpline} models corroborates important 
+conclusions of recent work and provides a robust data-driven framework for future population studies \bruce{cite}.
+
+% mass dist
+The results presented in section \ref{sec:mass_dist} illustrate a much wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}. 
+While isolated formation is able to predict the $10\msun$ peak, cluster and dynamical formation scenarios struggle to predict a peak in the BH mass distribution less than 
+$15-20\msun$. Globular cluster formation is expected to produce more top-heavy mass distributions than isolated and recent studies have shown suppressed BBH merger rates 
+at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel. BBH's formed near active galactive nuclei (AGN) can preferentially produce higher 
+mass black holes. We additionally do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts 
+due to pair-instability supernovae (PISNe). The original motivation for the peak in the \textsc{PLPeak} model was to represent a possible ``pileup'' of masses just before such the 
+truncation, since massive stars just light enough to avoid PISN will shed large amounts of mass in a series of ``pulses'' before collapsing to BHs in a process called 
+pulsational pair-instability supernova (PPISN). While the predictions of the mass scale where pair-instability kicks in are uncertain and depend on not well understood physics, 
+like nuclear reaction rates of carbon and oxygen in the core of stars, models have a hard time predicting this peak to be lower than $m\sim40\msun$. The lack of a truncation could 
+point towards a higher prevalence of dynamical processes that can produce black holes in mass ranges stellar collapse cannot. These possibilities include hierarchical mergers of BHs, 
+very low metallictiy population III stars, or black hole accretion of BHs in gaseous environments such as AGNs.
+
+% component spins
+
+% effective spins
 

### 2022-09-26 src/tex/intro.tex
remove comment"
add more conc

@@
 Through a better understanding of the mass, spin, and redshift distributions of compact binaries that will come with the increased catalog size, 
-one can probe a wide range of different physical phenoma with even greater fidelity. \bruce{Cite others??}
+one can probe a wide range of different physical phenoma with even greater fidelity.
 
 Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 \citep{Tiwari_2021_b,Edelman_2022ApJ} found signs of structure 
-beyond the reported $m_1\sim35\,\msun$ feature by \citet{Talbot_2019, o3a_pop}. The has evidence for this structure, such as the peak at $m_1\sim10\,\msun$, has only increased
+beyond the reported $m_1\sim35\,\msun$ feature by \citet{Talbot_2018, o3a_pop}. The has evidence for this structure, such as the peak at $m_1\sim10\,\msun$, has only increased
 with GWTC-3 \cite{o3b_astro_dist,Tiwari_2022ApJ}. This substructure was first confidently found with mutliple different flexible or non-parametric models that aim 

### 2022-09-26 src/tex/results.tex
add more conc

@@
 model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$. 
-Where $\beta$ is the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \cite{Talbot_2019,o1o2_pop,o3a_pop}.
+Where $\beta$ is the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \cite{Talbot_2018,o1o2_pop,o3a_pop}.
 We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model \cite{Fishbach_2018redshift}, which is desribed by 
@@
 Figure \ref{fig:mass_distribution} shows how the MSpline model (red) found consistent features in the mass disribution with 
-what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \cite{Talbot_2019,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
+what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \cite{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
 In particular our MSpline model finds a peak in merger rate density at both 10 and 35 soloar masses, agreeing with those reported using the same dataset in \citet{o3b_astro_dist}. 

### 2022-09-26 src/tex/conclusion.tex
add more conc
more citations in astro impl

--- 2022-09-26 src/tex/conclusion.tex
@@
-\section{Discussion}\label{sec:astrodiscussion}
+\section{Astrophysical Implications}\label{sec:astrodiscussion}
 
-\bruce{Here we discuss the astrophysical implications of work -- connect to wider literature}
+The collective distibution of BBH source properties provides a useful probe of the complex and uncertain astrophysics that governs their 
+formation and evolution to eventually merge \citep{Zevin_2017}. Our analysis with the newly constructed \textsc{MSpline} models corroborates important 
+conclusions of recent work and provides a robust data-driven framework for future population studies.
+
+% mass dist
+The results presented in section \ref{sec:mass_dist} illustrate a much wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}. 
+While isolated formation is able to predict the $10\msun$ peak \bruce{cite}, cluster and dynamical formation scenarios struggle to predict a peak in the BH mass distribution less than 
+$15-20\msun$ \bruce{cite}. Globular cluster formation is expected to produce more top-heavy mass distributions than isolated and recent studies have shown suppressed BBH merger rates 
+at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \bruce{cite}. BBHs that form near active galactive nuclei (AGN) can preferentially produce higher 
+mass black holes \bruce{cite}. We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts 
+due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017}.
+The original motivation for the peak in the \textsc{PLPeak} model \citep{Talbot_2018} was to represent a possible ``pileup'' of
+masses just before such the truncation, since massive stars just light enough to avoid PISN will shed large amounts of mass in a series of ``pulses'' before collapsing to BHs in a process called 
+pulsational pair-instability supernova (PPISN) \citep{Woosley_2017,Woosley_2019,Farmer_2019}.
+While the predictions of the mass scale where pair-instability kicks in are uncertain and depend on not well understood physics,
+like nuclear reaction rates of carbon and oxygen in the core of stars, models have a hard time predicting this peak to be lower than $m\sim40\msun$ \citep{Belczynski_2016,Marchant_2019,Renzo_2020,Farmer_2019,Farmer_2020}.
+The lack of a truncation could
+point towards a higher prevalence of dynamical processes that can produce black holes in mass ranges stellar collapse cannot, such as hierarchical mergers of BHs \citep{Fishbach_2017,Doctor_2020,Kimball_genealogy,kimball2020evidence,doctor2021black,Fishbach_2022},
+very low metallictiy population III stars \citep{Belczynski_2020,Farrell_2020}, new beyond the standard model physics\cite{Croon_newphysics,Sakstein_2020}, or black hole accretion of BHs in gaseous environments such as AGNs \citep{Secunda_2020,McKernan_2020,cruzosorio2021gw190521}.
+
+% spin dist
+Section \ref{sec:spin_dist} focused on inferences of the spin distributions of black holes, observing evidence of spin mis-alignment, spin anti-alignment, and suppressed support 
+for exactly aligned systems. These point towards a significant contribution of the population being formed through dynamical formation processes, agreeing with 
+conclusions drawn about the mass distribution inference of section \ref{sec:mass_dist}. While field formation is expected to produce systems with preferentially 
+aligned spins due to tidal interactions, but observational evidence suggests that tides may not be able to re-align spins in all systems as some 
+isolated population models assume. Additionally because of uncertain knowledge of supernovae kicks, isolated formation can produce systems with negative but small effective spins. 
+We report an effective spin distribution that is not symmetric about zero, disfavoring a scenarior in wihch all BBHs are formed dynamically. Following the rules in \citet{Fishbach_2022}, 
+we place conservative upper bounds on the fraction of hierarhical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$. We find with 
+the \textsc{MSpline} model that $f_\mathrm{HM} \leq XX$ and $f_\mathrm{dyn} \leq XX$ at 90\% credibility.
 

### 2022-09-26 src/tex/conclusion.tex
update refs/concl/macros

@@
 We report an effective spin distribution that is not symmetric about zero, disfavoring a scenarior in wihch all BBHs are formed dynamically. Following the rules in \citet{Fishbach_2022}, 
-we place conservative upper bounds on the fraction of hierarhical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$. We find with 
-the \textsc{MSpline} model that $f_\mathrm{HM} \leq XX$ and $f_\mathrm{dyn} \leq XX$ at 90\% credibility.
+we place conservative upper bounds on the fraction of hierarhical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$ with 
+the \textsc{MSpline} $\chi_\mathrm{eff}$ model constraining $f_\mathrm{HM} < $\result{$\macros[ChiEffective][chieff][frac_hm][10th percentile]$} 
+and $f_\mathrm{dyn} < $\result{$\macros[ChiEffective][chieff][frac_dyn][10th percentile]$} at 90\% credibility.
 

### 2022-09-26 src/tex/macros.tex
update refs/concl/macros

--- 2022-09-26 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XV\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XX\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXIV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.00}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.00}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.84}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{0.99}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.62}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.57}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{3.31}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{1.00}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{1.00}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.96}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.47}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXI@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXI@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXI@out\macros@XXX\else\def\macros@XXI@out{??}\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIX\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"m\_1percentile": \{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXV@out\macros@XLI\else\def\macros@XXV@out{??}\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@XLIII\else\def\macros@XXVI@out{??}\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@XLV\else\def\macros@XXVII@out{??}\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.03}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.49}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.05}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.05}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.44}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.07}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.05}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.47}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.05}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.12}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.50}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.07}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": "6.32", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.24", "95th percentile": "6.90"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{6.32}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{5.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{6.90}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{44.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{38.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{55.46}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": "6.01", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.82", "95th percentile": "6.59"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{6.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{5.82}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{6.59}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{80.10}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{11.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{12.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{67.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{91.26}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": "5.83", "error plus": "1.03", "error minus": "1.47", "5th percentile": "4.35", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{5.83}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{1.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{1.47}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{4.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{6.81}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{43.20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{10.47}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{38.49}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{54.97}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLV@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}, "a1\_90percentile": \{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}, "peakCosTilt1": \{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}, "peakCosTilt2": \{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}, "log10gammaFrac1": \{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}, "log10gammaFrac2": \{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}, "negFrac1": \{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}, "a\_90percentile": \{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}, "peakCosTilt": \{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}, "negFrac": \{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.015, "error minus": 0.0092, "5th percentile": 0.0036, "95th percentile": 0.029, "10th percentile": 0.0048, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.15, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.3, "5th percentile": 0.56, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.08, "error plus": 0.094, "error minus": 0.058, "5th percentile": 0.023, "95th percentile": 0.18, "10th percentile": 0.03, "90th percentile": 0.15\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.025, "error minus": 0.015, "5th percentile": 0.0046, "95th percentile": 0.046, "10th percentile": 0.006, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.35, "error plus": 0.096, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.24, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.029, "error plus": 0.038, "error minus": 0.022, "5th percentile": 0.007, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.059\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.25, "5th percentile": 0.45, "95th percentile": 0.87, "10th percentile": 0.48, "90th percentile": 0.85\}, "frac\_hm": \{"median": 0.12, "error plus": 0.16, "error minus": 0.095, "5th percentile": 0.029, "95th percentile": 0.29, "10th percentile": 0.038, "90th percentile": 0.2\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.017, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.39, "error plus": 0.075, "error minus": 0.071, "5th percentile": 0.32, "95th percentile": 0.47, "10th percentile": 0.34, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.027, "error plus": 0.026, "error minus": 0.026, "5th percentile": 0.001, "95th percentile": 0.051, "10th percentile": 0.005, "90th percentile": 0.045\}, "frac\_dyn": \{"median": 0.79, "error plus": 0.15, "error minus": 0.14, "5th percentile": 0.65, "95th percentile": 0.95, "10th percentile": 0.68, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.089, "5th percentile": 0.11, "95th percentile": 0.31, "10th percentile": 0.14, "90th percentile": 0.27\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}, "a1\_90percentile": \{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}, "peakCosTilt1": \{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}, "peakCosTilt2": \{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}, "log10gammaFrac1": \{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}, "log10gammaFrac2": \{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}, "negFrac1": \{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}, "a\_90percentile": \{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}, "peakCosTilt": \{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}, "negFrac": \{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.015, "error minus": 0.0092, "5th percentile": 0.0036, "95th percentile": 0.029, "10th percentile": 0.0048, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.15, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.3, "5th percentile": 0.56, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.08, "error plus": 0.094, "error minus": 0.058, "5th percentile": 0.023, "95th percentile": 0.18, "10th percentile": 0.03, "90th percentile": 0.15\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.025, "error minus": 0.015, "5th percentile": 0.0046, "95th percentile": 0.046, "10th percentile": 0.006, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.35, "error plus": 0.096, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.24, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.029, "error plus": 0.038, "error minus": 0.022, "5th percentile": 0.007, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.059\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.25, "5th percentile": 0.45, "95th percentile": 0.87, "10th percentile": 0.48, "90th percentile": 0.85\}, "frac\_hm": \{"median": 0.12, "error plus": 0.16, "error minus": 0.095, "5th percentile": 0.029, "95th percentile": 0.29, "10th percentile": 0.038, "90th percentile": 0.2\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.017, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.39, "error plus": 0.075, "error minus": 0.071, "5th percentile": 0.32, "95th percentile": 0.47, "10th percentile": 0.34, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.027, "error plus": 0.026, "error minus": 0.026, "5th percentile": 0.001, "95th percentile": 0.051, "10th percentile": 0.005, "90th percentile": 0.045\}, "frac\_dyn": \{"median": 0.79, "error plus": 0.15, "error minus": 0.14, "5th percentile": 0.65, "95th percentile": 0.95, "10th percentile": 0.68, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.089, "5th percentile": 0.11, "95th percentile": 0.31, "10th percentile": 0.14, "90th percentile": 0.27\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXVII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXX\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{0.61}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{2.9}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}1.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.68}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.75}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.58}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.62}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.86}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.78}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.91}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.88}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.71}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.36}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.98}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{0.68}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.83}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.28}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.58}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.53}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{1.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{3.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.62}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{2.9}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.69}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.53}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.57}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.8}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{1.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{1.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}1.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.69}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.88}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.96}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.8}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.44}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.015, "error minus": 0.0092, "5th percentile": 0.0036, "95th percentile": 0.029, "10th percentile": 0.0048, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.15, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.3, "5th percentile": 0.56, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.08, "error plus": 0.094, "error minus": 0.058, "5th percentile": 0.023, "95th percentile": 0.18, "10th percentile": 0.03, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XXXV\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.025, "error minus": 0.015, "5th percentile": 0.0046, "95th percentile": 0.046, "10th percentile": 0.006, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.35, "error plus": 0.096, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.24, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.029, "error plus": 0.038, "error minus": 0.022, "5th percentile": 0.007, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.059\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.25, "5th percentile": 0.45, "95th percentile": 0.87, "10th percentile": 0.48, "90th percentile": 0.85\}, "frac\_hm": \{"median": 0.12, "error plus": 0.16, "error minus": 0.095, "5th percentile": 0.029, "95th percentile": 0.29, "10th percentile": 0.038, "90th percentile": 0.2\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XL\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.017, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.39, "error plus": 0.075, "error minus": 0.071, "5th percentile": 0.32, "95th percentile": 0.47, "10th percentile": 0.34, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.027, "error plus": 0.026, "error minus": 0.026, "5th percentile": 0.001, "95th percentile": 0.051, "10th percentile": 0.005, "90th percentile": 0.045\}, "frac\_dyn": \{"median": 0.79, "error plus": 0.15, "error minus": 0.14, "5th percentile": 0.65, "95th percentile": 0.95, "10th percentile": 0.68, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.089, "5th percentile": 0.11, "95th percentile": 0.31, "10th percentile": 0.14, "90th percentile": 0.27\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLV\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@L\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LIII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LVI\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LVII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LIX\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.013, "error plus": 0.015, "error minus": 0.0092, "5th percentile": 0.0036, "95th percentile": 0.029, "10th percentile": 0.0048, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.015}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.0092}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.0036}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.029}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.0048}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.024}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.43, "error plus": 0.078, "error minus": 0.15, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.078}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.32}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.48}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.017, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.043}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.86, "error plus": 0.16, "error minus": 0.3, "5th percentile": 0.56, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.56}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.64}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.97}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.08, "error plus": 0.094, "error minus": 0.058, "5th percentile": 0.023, "95th percentile": 0.18, "10th percentile": 0.03, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.094}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.058}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.18}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.03}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.15}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.02, "error plus": 0.025, "error minus": 0.015, "5th percentile": 0.0046, "95th percentile": 0.046, "10th percentile": 0.006, "90th percentile": 0.033\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.025}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.0046}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.046}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.006}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.033}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.35, "error plus": 0.096, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.24, "90th percentile": 0.43\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.096}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.44}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.43}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.029, "error plus": 0.038, "error minus": 0.022, "5th percentile": 0.007, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.059\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.029}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.038}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.007}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.071}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.059}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.7, "error plus": 0.19, "error minus": 0.25, "5th percentile": 0.45, "95th percentile": 0.87, "10th percentile": 0.48, "90th percentile": 0.85\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.25}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.45}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.48}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.85}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.12, "error plus": 0.16, "error minus": 0.095, "5th percentile": 0.029, "95th percentile": 0.29, "10th percentile": 0.038, "90th percentile": 0.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.095}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.29}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.038}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.2}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.032, "error plus": 0.017, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.032}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.017}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.014}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.05}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.043}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.39, "error plus": 0.075, "error minus": 0.071, "5th percentile": 0.32, "95th percentile": 0.47, "10th percentile": 0.34, "90th percentile": 0.45\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.075}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.071}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.34}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.45}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.027, "error plus": 0.026, "error minus": 0.026, "5th percentile": 0.001, "95th percentile": 0.051, "10th percentile": 0.005, "90th percentile": 0.045\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.027}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.026}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.026}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.001}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.051}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.005}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.045}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.79, "error plus": 0.15, "error minus": 0.14, "5th percentile": 0.65, "95th percentile": 0.95, "10th percentile": 0.68, "90th percentile": 0.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.79}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.95}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.68}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.9}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.2, "error plus": 0.11, "error minus": 0.089, "5th percentile": 0.11, "95th percentile": 0.31, "10th percentile": 0.14, "90th percentile": 0.27\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.27}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.071}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.047}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.034}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.036}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.042}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.1}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.31}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.48}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.035}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.044}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.0088}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.063}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.21}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.63}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.95}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.75}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.65}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{6.7}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{19}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{52}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{5.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{5.7}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{6.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{5.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{6.3}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{30}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{4.4}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{7.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{34}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{24}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{33}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{80}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{68}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{91}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{70}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{89}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{6.7}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{15}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{52}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\makeatother

### 2022-09-26 src/scripts/create_macros.py

@@ -133,6 +133,8 @@ def chi_eff():
         v['FracBelowNeg0p3'] = save_param_cred_intervals(np.array(below_m0p3[k]))
         v['FracBelow0'] = save_param_cred_intervals(np.array(below_0[k]))
         v['PeakChiEff'] = save_param_cred_intervals(np.array(maxchis[k]))
+        v['frac_dyn'] = save_param_cred_intervals(2.0*np.array(below_0[k]))
+        v['frac_hm'] = save_param_cred_intervals(6.25*np.array(below_m0p3[k]))
     return macdict
 
 

### 2022-09-26 src/scripts/utils.py

@@ -5,12 +5,22 @@ from bilby.core.result import read_in_result
 import deepdish as dd
 
 
+def round_sig(f, sig=2):
+    max10exp = np.floor(np.log10(abs(f))) + 1
+    if max10exp < float(sig):
+        return float(('%.' + str(sig) + 'g') % f)
+    else:
+        return int(float(('%.' + str(sig) + 'g') % f))
+
+
 def save_param_cred_intervals(param_data):
-    return  {'median': "{:.2f}".format(np.median(param_data)), 
-             'error plus': "{:.2f}".format(np.percentile(param_data, 95)-np.mean(param_data)), 
-             'error minus': "{:.2f}".format(np.median(param_data)-np.percentile(param_data, 5)),
-             '5th percentile': "{:.2f}".format(np.percentile(param_data, 5)), 
-             '95th percentile': "{:.2f}".format(np.percentile(param_data, 95))}
+    return  {'median': round_sig(np.median(param_data)), 
+             'error plus':round_sig(np.percentile(param_data, 95)-np.mean(param_data)), 
+             'error minus': round_sig(np.median(param_data)-np.percentile(param_data, 5)),
+             '5th percentile': round_sig(np.percentile(param_data, 5)), 
+             '95th percentile': round_sig(np.percentile(param_data, 95)), 
+             '10th percentile': round_sig(np.percentile(param_data, 10)),
+             '90th percentile': round_sig(np.percentile(param_data, 90))}
 
 
 def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None, tracecolor='k'):

### 2022-09-27 src/tex/conclusion.tex
start conclusion

@@
 
-\bruce{main points for conclusion are to sum up conclusions with one last call to literature for most important parts, 
-followed by short discussion of the outlook going into O4 and how this method will be especially useful as we rapidly approach
-GW's data rich era}
+Non-parametric and data-driven statistical modeling methods have been put to use with great success across the ever-growing field of gravitational 
+waves \citep{B_Farr_etal_2014,Littenberg_2015,MaMandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
+We presented a case study exploring how basis splines make for an especially powerful and efficient model-agnostic probe of the binary black hole population observed 
+with gravitational waves. With the coming influx of new data with the LVK's next observing run, and the wide range of questions in astro/physics that a better 
+understanding of the black hole population will uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
+sense of the data.

### 2022-09-27 src/tex/intro.tex
start conclusion

@@
 in order to studying the compact object population. The history of these dense objects is imprinted on the properties of the population 
-of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitation radiation emitted. The population distibutions 
+of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitation radiation emitted \citep{Zevin_2017}. The population distibutions 
 of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, 

### 2022-09-27 src/tex/conclusion.tex
super basic conclusion....

@@
 Non-parametric and data-driven statistical modeling methods have been put to use with great success across the ever-growing field of gravitational 
-waves \citep{B_Farr_etal_2014,Littenberg_2015,MaMandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
+waves \citep{B_Farr_etal_2014,Littenberg_2015,Mandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
 We presented a case study exploring how basis splines make for an especially powerful and efficient model-agnostic probe of the binary black hole population observed 

### 2022-09-27 src/tex/appendicies.tex
Update readme with current tasks / progress

@@
 Since we are using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog. 
-The difference penalty is equivalent to applying a stochastic differnece prior among the knots, as described in  \\citet{BayesianPSplines,Jullion2007RobustSO}. 
+The difference penalty is equivalent to applying a stochastic differnece prior among the knots, as described in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}. 
 This is also sometimes referred to as a Gaussian random walk prior, since each coeficient is normally distributed about its neighboring coeficients. 
@@
 
-\section{Validation Studies} \label{sec:validation}
+%\section{Validation Studies} \label{sec:validation}
 
-\bruce{Need to fill this section}
+%bruce{Need to fill this section}

### 2022-09-27 src/tex/ms.tex
more refs
Update readme with current tasks / progress
try using caption package -- doesnt work
fix figure icon buttons overlapping fig captions
remove unused latex packages
rework macros and fix some abs things

@@
-\documentclass[twocolumn, linenumber]{aastex63}
+\documentclass[twocolumn, linenumbers]{aastex631}
 
@@
 \usepackage{showyourwork}
-\usepackage[perpage]{footmisc}
-\usepackage{colortbl}
-\usepackage{lineno}
+%\usepackage[perpage]{footmisc}
+%\usepackage{colortbl}
+%\usepackage{lineno}
+%\linenumbers
 \usepackage{bm}
@@
 \usepackage{appendix}
+%\usepackage[margin=10pt]{caption}
 \input{macros}
 
-\definecolor{Gray}{gray}{0.9}
-\linenumbers
+%\definecolor{Gray}{gray}{0.9}
 
@@
 distribution with basis splines we find similar conclusions as previously reported, consistent with a non-isotropic distribution 
-(peaks at $\chi_\mathrm{eff}$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}), showing considerable support 
-($\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
+(peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}), showing considerable support 
+($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
 We conclude by discussing how non-parametric methods in gravitatonal-wave population inference are poised to provide a useful complement to 
@@
 (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
+The authors are grateful for computational resources provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.  
 This work benefited from access to the University of Oregon high performance computer, Talapas. This material is based upon work supported 
@@
 \textsc{Matplotlib}~\citep{Hunter:2007},
-\textsc{jax},
-\textsc{numpyro},
-\bruce{CITE ALL ABOVE}
+\textsc{Jax}~\citep{jax},
+\textsc{NumPyro}~\citep{pyro,numpyro},
+\textsc{GWPopulation}~\citep{Talbot_2019},
+\textsc{Bilby}~\citep{Ashton_2019,bilby_gwtc1},
+\textsc{Dynesty}~\citep{Speagle_2020}
 }

### 2022-09-27 src/scripts/create_macros.py

@@ -8,7 +8,6 @@ import deepdish as dd
 from scipy.integrate import cumtrapz
 from utils import load_iid_mag_ppd, load_iid_tilt_ppd, load_ind_mag_ppd, load_ind_tilt_ppd, save_param_cred_intervals, load_o3b_paper_run_masspdf, load_mass_ppd, load_iid_posterior, load_ind_posterior, load_o3b_posterior
 
-
 def get_percentile(pdfs, xs, perc):
     x = []
     for m in pdfs:                                                                                                                                                                        
@@ -22,7 +21,6 @@ def get_percentile(pdfs, xs, perc):
             prob = cumulative_prob[i]                                                                                                                                                         
         x.append(xs[i])
     return np.array(x)
-
 
 def MSplineMassMacros():
     print("Saving Mass Distribution Macros...")
@@ -41,7 +39,6 @@ def MSplineMassMacros():
     return {'PLPeak': {'m_1percentile': save_param_cred_intervals(plpeak_m1s), 'm_75percentile': save_param_cred_intervals(plpeak_m75s), 'm_99percentile': save_param_cred_intervals(plpeak_m99s)}, 
             'MSpline': {'m_1percentile': save_param_cred_intervals(m1s), 'm_75percentile': save_param_cred_intervals(m75s), 'm_99percentile': save_param_cred_intervals(m99s)}, 
             'PLSpline': {'m_1percentile': save_param_cred_intervals(ps_m1s), 'm_75percentile': save_param_cred_intervals(ps_m75s), 'm_99percentile': save_param_cred_intervals(ps_m99s)}}
-
 
 def MSplineIIDSpinMacros():
     print("Saving MSpline IID Component Spin macros...")
@@ -67,7 +64,6 @@ def MSplineIIDSpinMacros():
             'peakCosTilt': save_param_cred_intervals(peak_tilts), 
             'log10gammaFrac': save_param_cred_intervals(np.log10(gamma_fracs)), 
             'negFrac': save_param_cred_intervals(frac_neg_cts)}
-
 
 def MSplineIndSpinMacros():
     print("Saving MSpline Independent Component Spin macros...")
@@ -107,7 +103,6 @@ def MSplineIndSpinMacros():
[…]

### 2022-09-27 src/scripts/utils.py

@@ -5,7 +5,7 @@ from bilby.core.result import read_in_result
 import deepdish as dd
 
 
-def round_sig(f, sig=2):
+def round_sig(f, sig=3):
     max10exp = np.floor(np.log10(abs(f))) + 1
     if max10exp < float(sig):
         return float(('%.' + str(sig) + 'g') % f)

### 2022-09-28 src/tex/intro.tex
Add comments and update abs/into/methods -- add o3b gaussian chieff to plot

--- 2022-09-26 src/tex/intro.tex
@@
 
-Observations of gravitational waves (GWs) from compact binary coalescences (CBCs) is becoming a regular occurrence, 
-recently producing catalogs of 90 such detection \cite{GWTC1,gwtc2,GWTC3}. With this growing catalog size, we are steadily approaching a more complete  
-understanding of the population properties CBCs, just 7 years after the first observation \cite{o1o2_pop,o3a_pop,o3b_astro_dist}. 
-In the coming fourth observing run of the LIGO-Virgo-KAGRA collaboration detectors \citep{aLIGO,aVIRGO}, with the increased sensitivities, 
-there could be a detection as often as every day \cite{LVK_prospects}. This large influx of incoming data will drastically increase what we can learn by combining all observations
-in order to studying the compact object population. The history of these dense objects is imprinted on the properties of the population 
-of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitation radiation emitted. The population distibutions 
-of merging compact objects inferred from gravitational-wave observations has been shown to be parituclar useful in order to, measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, 
-constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng},
-constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, and constrain the neutron star equation of state \citep{Golomb_EOS}.
-Through a better understanding of the mass, spin, and redshift distributions of compact binaries that will come with the increased catalog size, 
-one can probe a wide range of different physical phenoma with even greater fidelity.
+Observations of gravitational waves (GWs) from compact binary coalescences (CBCs) are becoming a regular occurrence, 
+recently producing catalogs of 90 such detections \citep{GWTC1,gwtc2,GWTC3}. With this growing catalog size, we are steadily approaching a more complete  
+understanding of the population properties of CBCs, just 7 years after the first observation \citep{o1o2_pop,o3a_pop,o3b_astro_dist}. 
+In the coming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration detectors \citep{aLIGO,aVIRGO}, with the increased sensitivities, 
+there could be a detection as often as every day \citep{LVK_prospects}. This large influx of incoming data will drastically increase what we can 
+learn by combining all observations in order to study the compact object population. The history of these dense objects is imprinted on the properties 
+of the population  of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitational radiation emitted \citep{Zevin_2017}. 
+The population distributions of merging compact objects inferred from gravitational-wave observations have been shown to be particularly useful in order to
+measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, 
+constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng}, 
+constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, 
+and constrain the neutron star equation of state \citep{Golomb_EOS}. Through a better understanding of the mass, spin, and redshift distributions of 
+compact binaries that will come with the increased catalog size, one can probe a wide range of different physical phenomena with even greater fidelity.
 
-Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 \citep{Tiwari_2021_b,Edelman_2022ApJ} found signs of structure 
-beyond the reported $m_1\sim35\,\msun$ feature by \citet{Talbot_2018, o3a_pop}. The has evidence for this structure, such as the peak at $m_1\sim10\,\msun$, has only increased
-with GWTC-3 \cite{o3b_astro_dist,Tiwari_2022ApJ}. This substructure was first confidently found with mutliple different flexible or non-parametric models that aim 
-to be data-oriented with little bias on the functional form. Conversely the other canonical approach is to use simple parametric models that aim to describe the data
-in the simplest way, building in astrophyscially motivated priors, followed by sequentially adding complexities only as the data demands it. While in the current environment 
-this simple approach is clearly more powerful, as we go forward into the data-rich catalog era flexible models can be a useful complement.
-Non-parametric or semi-parametric methods are particularly useful at looking for unexpected features in the data, or finding where 
-our simpler parametric models may be missing features in the data. Development and robust teting of these types of methods in the short term will provide
-knock dowm effects later down the line as the size of our catalogs increase and we enter a data-dominated regime rather than prior/model dominated.
+Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 found signs of structure 
+beyond the first reported feature found at $m_1\sim35\,\msun$ \citep{Talbot_2018,o3a_pop,Tiwari_2021_b,Edelman_2022ApJ}. The evidence for this structure, 
+such as the peak at $m_1\sim10\,\msun$, has only increased after analyzing the following catalog, GWTC-3 \citep{o3b_astro_dist,Tiwari_2022ApJ}. 
+This substructure was first confidently found with multiple different flexible or non-parametric models that are data-driven with little 
+bias on the functional form. Conversely, the other canonical approach is to use simple parametric models that aim to describe the data
+in the simplest way, building in astrophysically motivated priors, followed by sequentially adding complexities only as the data demands it. While in data-scarce, prior dominated
+environments, this simple approach is more powerful. However, as we go forward into the data-rich catalog era, flexible models will be necessary to discover new features that may be in
+the data, which quickly becomes unwieldy with the sequential approach. Non-parametric or semi-parametric methods are particularly useful in looking for unexpected features in the data, finding where 
+our simpler parametric models may be failing to capture meaningful features in the data. Development and robust testing of such methods in the short term will provide
+knock on effects as the size of our catalogs increase, and GW astronomy enters its data-dominated era.
 
-The spin distributions of binary black holes (BBHs) have particular interest since the two main formation scenarios of BBHs produce 
-distinctly different spin distrubitons \bruce{cite}. Isolated or field formation scenarios predict spins that are preferentially, although some small misalignment can occur 
-depending on the nature of the supernovae kicks as each star collapses to a compact object \bruce{cite}. Dynamical formation scenarios occur in dense environments where 
-many-body interactions between a large number compact objects occur before producing a binary that will merger within a Hubble time. Thus the dynamical channel produces 
-an isotropic spin orientation distribution \bruce{cite}. It has also been of controversial interest in the literature recently, with different parameteric approaches finding 
-different conclusions on the distribution of spins of BBHs. Recent studies have disagreed on the possible existence of a significant zero-spinning subpopulation, along with the 
-presence of significant mis-alignment ($\cos{\theta_i} < 0.0$) \cite{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}. A recent study 
-has shown the spin orientation distribution infernce is senitive to modeling choices and may not peak at perfectly aligned spins, as is commonly assumed \cite{spinitasyoulike}. 
-Other approaches to building better models for BBH spins again, as with the mass models, focus on iterating through different simple parameteric descriptions with 
-increasing complexities \cite{BuildBetterSpinModels,Callister_NoEvidence,spinitasyoulike}. The spin distributions offer a nice use case for flexible data-driven models, both 
-to help alleivate the current disputes in the literature and because there has been little work on flexible model development for the spin distribution of BBHs thus far.
+The spin distributions of BBHs are particularly interesting since the two main formation scenarios produce distinctly different spin distributions \bruce{cite}. 
+Isolated or field formation scenarios predict component spins that are preferentially aligned with the binaries orbital angular momentum, although some small 
+misalignment can occur depending on the nature of the supernova kicks as each star collapses to a compact object \bruce{cite}. Dynamical formation scenarios may 
+occur in dense environments where many-body interactions between a large number compact objects occur during the binary formation hardening the binary so that it 
+will merge within a Hubble time. Thus, the dynamical channel produces an isotropic spin tilt distribution \bruce{cite}. BBH spins have also been of controversial 
+interest recently, with different parametric approaches to modeling the spin distribution coming to different conclusions. The studies have disagreed on the possible existence 
+of a significant zero-spinning subpopulation, along with the presence of significant spin misalignment (i.e.
+$\cos{\theta_i} < 0.0$) \citep{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}.
+Another study recently showed that the spin tilt distribution inference is sensitive to modeling choices and may not peak at perfectly aligned spins, as is often assumed \citep{spinitasyoulike}. 
+Other approaches to building improved models for BBH spins again, as with the mass models, focus on iterating through different simple parametric descriptions with 
+increasing complexities \citep{BuildBetterSpinModels,Callister_NoEvidence,spinitasyoulike}. The spin distributions offer a nice use case for flexible data-driven models, as 
+we present in this manuscript, both to help alleviate the current disputes in the literature and because there has been little work on flexible model development for the 
+spin distribution of BBHs beyond assuming aligned spins thus far \citep{Tiwari_2021_a,Tiwari_2021_b}.
 
 Polynomial splines have been applied to success across different areas of gravitational-wave astronomy. They have been used to model the gravitational-wave data noise spectrum, 
-detector calibration uncertainties, coherent gravitational waveform deviations, and modulations to a power law mass distribution \cite{Littenberg_2015,Edwards_2018,B_Farr_etal_2014,Edelman_2021,Edelman_2022ApJ}
+detector calibration uncertainties, coherent gravitational waveform deviations, and modulations to a power law mass distribution \citep{Littenberg_2015,Edwards_2018,B_Farr_etal_2014,Edelman_2021,Edelman_2022ApJ}
 In this paper we highlight how the use of basis-splines can provide a powerful non-parametric modeling approach to the astrophysical distributions of compact 
-binaries. We illustrate how one can efficiently model the mass and spin distributions of compact binaries in GWTC-3 with basis splines to infer population properties using 
-hierarchical Bayesian inference.
-We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower dimensional parametric models.
-This data-drien approach will be capable of finding more subtle features, that may not be expected, should they appear in future catalogs. 
-In Section \ref{sec:basis_splines} we go over the background of basis splines, in Section \ref{sec:results} we present results using our basis 
-spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context Section \ref{sec:astrodiscussion} 
-and concluding in Section \ref{sec:conclusion}.
+binaries. We illustrate how one can efficiently model both the mass and spin distributions of merging compact binaries in GWTC-3 with basis splines to infer CBC population properties using 
+hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower 
+dimensional parametric models in the short run, and will become necessary with future catalogs. This data-driven approach will provide checks of our understanding by finding more 
+subtle features, that may not be expected, should they appear in with more observations. The rest of this manuscript is structured by first going over the background of basis splines in 
+section \ref{sec:basis_splines}, followed by presenting the results of our extensive data-driven study of the mass and spin distributions of BBHs in GWTC-3 section \ref{sec:results}. We 
+discuss our results and their astrophysical implications in section \ref{sec:astrodiscussion}, finishing with our conclusions in section \ref{sec:conclusion}.

### 2022-09-28 src/tex/macros.tex
Add comments and update abs/into/methods -- add o3b gaussian chieff to plot

--- 2022-09-26 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XV\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XX\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXIV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.00}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.00}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.84}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{0.99}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.62}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.57}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{3.31}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{1.00}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{1.00}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.96}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.47}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXI@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXI@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXI@out\macros@XXX\else\def\macros@XXI@out{??}\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIX\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXV@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXV@out\macros@XLII\else\def\macros@XXV@out{??}\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@XLV\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@XLVIII\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.03}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.49}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.05}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.05}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.44}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.07}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.05}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.47}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.05}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.12}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.50}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.07}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{6.81}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{14.95}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{5.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{2.75}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{12.20}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{21.03}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{44.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{38.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{55.46}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{5.91}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{5.72}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{6.50}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{30.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{4.42}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{7.86}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{22.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{34.17}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{80.10}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{11.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{12.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{67.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{91.26}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{6.81}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{11.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{4.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{10.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{16.62}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{43.20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{10.47}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{38.49}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{54.97}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}, "lamb": \{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}, "lamb": \{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}, "a1\_90percentile": \{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}, "peakCosTilt1": \{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}, "peakCosTilt2": \{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}, "log10gammaFrac1": \{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}, "log10gammaFrac2": \{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}, "negFrac1": \{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}, "negFrac2": \{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}, "a\_90percentile": \{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}, "lamb": \{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}, "peakCosTilt": \{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}, "negFrac": \{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}, "lamb": \{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}, "lamb": \{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}, "a1\_90percentile": \{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}, "peakCosTilt1": \{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}, "peakCosTilt2": \{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}, "log10gammaFrac1": \{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}, "log10gammaFrac2": \{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}, "negFrac1": \{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}, "negFrac2": \{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}, "a\_90percentile": \{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}, "lamb": \{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}, "peakCosTilt": \{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}, "negFrac": \{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXVII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXX\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.246}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.0162}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.39}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.856}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.15}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.279}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{0.605}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{2.94}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.537}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.996}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}1.75}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.685}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.751}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.141}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.167}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.584}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.886}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.623}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.86}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.777}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.138}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.607}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.907}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.645}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.885}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.193}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.726}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.731}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.538}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.379}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.708}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.395}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.636}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.664}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.363}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.984}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.133}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.708}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.699}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.565}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.845}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.407}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{0.685}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.276}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.716}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.741}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.465}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.986}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.292}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.828}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.427}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.189}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.178}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.249}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.618}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.283}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.577}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.373}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.188}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.161}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.212}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.568}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.244}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.526}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{3.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.624}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{2.92}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.692}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.148}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.158}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.534}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.836}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.567}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.805}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.997}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}1.76}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.687}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.367}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.641}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.503}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{{-}0.135}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.878}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.658}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.659}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.349}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.965}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.803}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.344}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.124}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.116}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.228}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{0.252}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.442}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XXXV\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XL\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLV\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@L\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LIII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LVI\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LVII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LIX\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.0137}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.0158}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.0107}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.00302}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.0303}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.00431}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.0259}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.433}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.0759}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.158}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.275}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.309}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.484}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.00501}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.0531}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.043}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.866}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.152}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.316}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.55}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.618}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.968}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.0859}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.0986}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.067}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.0188}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.189}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.027}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.162}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.0198}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.0153}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.0154}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.00444}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.0355}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.00599}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.0322}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.351}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.0966}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.119}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.232}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.438}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.248}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.429}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.031}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.026}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.00501}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.0671}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.0551}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.702}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.193}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.238}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.463}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.876}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.496}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.858}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.124}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.0957}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.0961}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.0278}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.222}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.0374}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.201}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.0321}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.0183}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.0144}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.0177}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.0505}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.0215}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.0434}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.399}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.0722}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.0682}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.331}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.473}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.348}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.449}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.023}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.0257}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.001}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.00501}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.041}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.799}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.144}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.136}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.662}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.946}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.696}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.897}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.114}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.0899}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.111}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.316}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.134}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.271}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.0705}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.0475}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.0345}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.0361}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.0421}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.104}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.398}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.101}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.104}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.294}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.499}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.313}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.475}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.0351}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.044}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.0731}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.00881}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.0631}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.797}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.202}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.208}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.588}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.997}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.626}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.95}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.441}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.297}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.215}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.225}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.751}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.263}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.65}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.643}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{6.81}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{5.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{6.71}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{14.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{5.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{2.75}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{12.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{21.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{12.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{19.1}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{44.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{38.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{55.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{39.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{52.4}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{5.91}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.509}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.194}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{5.72}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{6.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{5.72}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{6.3}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{30.5}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{4.42}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{7.86}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{22.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{34.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{24.5}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{33.5}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{80.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{11.4}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{12.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{67.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{91.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{70.2}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{89.3}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.643}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{6.81}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{5.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{6.71}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{11.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{4.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.589}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{10.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{16.6}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{10.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{15.0}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{43.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{10.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{38.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{55.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{39.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{52.2}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\makeatother

### 2022-09-28 src/tex/methods.tex
move again...
Update methods.tex
change fig widths
fix latex figs
Add comments and update abs/into/methods -- add o3b gaussian chieff to plot

--- 2022-09-26 src/tex/methods.tex
@@
 
-A common non-parametric method in used in many statistical applications is basis splines. A spline function of order $k$, 
+A common non-parametric method used in many statistical applications is basis splines. A spline function of order $k$, 
 is a piece-wise polynomial of order $k$ polynomials stitched together from defined ``knot'' locations across the domain. 
 They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
-Basis splines of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
-Given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
-every possible spline function with knots, $\mathbf{t}$. One can construct the B-Splines basis components for a given knot vector 
-using the Cox-de Boor recursion formula \cite{deBoor78}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:
+\it{Basis splines} (or ``B-Splines'') of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
+Therefore, given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
+every possible spline function interpolated by knots, $\mathbf{t}$. The basis components for a given knot vector are constructed  
+using the Cox-de Boor recursion formula \citep{deBoor78}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/spline_basis_plot.pdf}
+        \caption{Plot showing a ``proper'' (see appendix \ref{sec:psplines}) M-Spline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
+        In black, we show the resulting spline function with given equal weights and denote the location of the knots with gray x's.}
+        \label{fig:spline_basis}
+    \end{centering}
+    \script{spline_basis_plot.py}
+\end{figure}
 
@@
 
-\noindent where $\omega_{i,k}$ is defined as:
+\noindent where above $\omega_{i,k}$ is defined as:
 
@@
 
-\noindent allowing one to build a basis of $i$ components that spans the vector space of order-$k$ spline functions interpolated 
-from this knot vector. This is known as the ``B-Spline'' basis after it's inventor de Boor \cite{deBoor78}. The power of basis splines
-comes from the fact that you only have to do the, somewhat expensive, interpolation once for each set of points you want to evaluate your
-spline functions at. This allows for much quicker speeds since each evaluation of the spline function becomes a simpler operation that is just
-a dot product of 2d matrix and 1d vector. This straightforward operation is also ideal for optimizations from the use GPU accelerators, 
-enabling expensive markov chain monte carlo (MCMC) based analyses with hundreds of parameters. Basis splines can easily be generalized to 
-their two-dimensional analog, producing tensor product basis splines that, with this computational advantange, allow for high fidelity
-modeling of two-dimensional spline functions.
+\noindent This is known as the ``B-Spline'' basis after it's inventor de Boor \citep{deBoor78}. The power of basis splines
+comes from the fact that one only has to do the somewhat-expensive interpolation once for each set of points at which the spline is evaluated. 
+This provides a considerable computational speedup since each evaluation of the spline function becomes a simpler operation that is just
+a dot product of a matrix and a vector. This straightforward operation is also ideal for optimizations from the use GPU accelerators, 
+enabling expensive Markov chain Monte Carlo (MCMC) based analyses with hundreds of parameters \bruce{citation?}. 
+Basis splines can easily be generalized to their two-dimensional analog, producing tensor product basis splines that, 
+with this computational advantage, allow for high fidelity modeling of two-dimensional spline functions.
 
 A similar basis, the M-Spline basis \citep{monotone_regression_splines}, has desirable properties when looking to model a probability density function, 
-which is the goal of population inference. Namely, $M_i \geq 0$ within $(t_i, t_i+k)$, zero elsewhere, and normalized to unity, $\int M_i(x)dx = 1$. We now have
-a useful basis that can represent all spline functions that are probability density functions given our array of knots. The M-Spline basis differs 
-from B-Splines by the normalization factor:
+which is the goal of population inference. Each basis component is scaled such that it is normalized over the domain, $\int M_i(x)dx = 1$. This ensures 
+that given a vector of basis coefficients, if they sum to unity, the resulting spline function is normalized across the interpolation domain. 
+The M-Spline basis differs from B-Splines by the scaling factor that normalizes each component:
 
@@
 
-\begin{figure}[ht!]
-    \script{spline_basis_plot.py}
-        \includegraphics[width=0.45\textwidth]{figures/spline_basis_plot.pdf}
-        \caption{Plot showing proper MSpline bases with 20 degrees of freedom and equal weights for each component.}
-        \label{fig:spline_basis}
-\end{figure}
-
-\noindent We use this definition of the M-Spline basis for the models presented and applied in the later sections of this paper. 
-Figure \ref{fig:spline_basis} shows an example of a 3rd order M-Spline basis with 20 degrees of freedom and knots linearly spaced from 0 to 1.
-Another important feature of basis splines is that under appropiate prior conditions, one can alleviate sensitivities to arbitrarily 
-chosen prior specifications that splines commonly struggle with. We look to the use of penalized splines or P-Splines \cite{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
-that adds a smoothing penalty (or prior) based on the difference of basis spline coeficients. This allows one to much more denseley populate
-the domain with knots without the worry of extra variance in the inferred spline functions. We discuss the smoothing prior in more detail 
-in Appendix \ref{sec:psplines}, along with our specific prior and basis choices for each model in Appendix \ref{sec:modelpriors}.
+\noindent We use this definition of the M-Spline basis for all the basis spline models used in this manuscript. Figure \ref{fig:spline_basis} 
+shows an example of a cubic (3rd order) M-Spline basis with 20 degrees of freedom and knots linearly spaced from 0 to 1.
+Another important feature of basis splines is that under appropriate prior conditions, one can alleviate sensitivities to arbitrarily 
+chosen prior specifications that splines commonly struggle with. We look to the use of penalized splines (or P-Splines) \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
+where one adds a smoothing prior based on the difference of basis spline coefficients. This allows one to populate the domain with more dense knots 
+without the worry of extra variance in the inferred spline functions. We discuss the details of our smoothing prior implementation 
+in more detail in Appendix \ref{sec:psplines}, along with our specific prior and basis choices for each model in Appendix \ref{sec:modelpriors}.

### 2022-09-28 src/tex/ms.tex
Add comments and update abs/into/methods -- add o3b gaussian chieff to plot

@@
 \begin{abstract}                 
-We introduce a non-parametric model built from basis splines, and apply it to infer the astrophysical distribution of 
-binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3. We report the same features previously recovered 
-with similarly flexible models in the mass distribution, most notably the peaks in merger rates at \~10\msun and \~35\msun. 
-We then use our method as the first non-parametric model applied to the BBH spin distribution, corroborating the results of \citet{spinitasyoulike}, 
-showing that tilt distributions may not peak at $\cos(\theta_i) = 1$ as previous models assumed. We find broad agreement with the 
-accepted conlcusions of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
-and there is mild support for a non-spinning subpopulaton, but cannot resolve this with current catalog sizes. We also test components whether the data 
-prefers the spin distributions to be identical for each component, finding no strong sign of differening distibutions. When modeling the $\chi_\mathrm{eff}$ 
-distribution with basis splines we find similar conclusions as previously reported, consistent with a non-isotropic distribution 
-(peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}), showing considerable support 
-($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
-We conclude by discussing how non-parametric methods in gravitatonal-wave population inference are poised to provide a useful complement to 
-the usual parametric approach going into the data rich catalog era of gravitational-wave astronomy.
+We introduce a non-parametric model built from basis splines, and use it to infer the astrophysical distribution of 
+binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3, in the most comprehensive data-driven
+investigation of the compact object population. We report the same features previously recovered 
+with similarly flexible models focusing solely on the mass distribution, most notably the peaks in merger rates at $\sim10\msun$ and $\sim35\msun$. 
+Our study provides the first non-parametric investigation into BBH spin distribution, while simultaneously modeling the mass distribution in the same way, 
+showing signs that the spin tilt distributions may not peak at $\cos(\theta_i) = 1$ as previous models assumed. We find broad agreement with the 
+accepted conclusions of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
+and there is mild support for a non-spinning subpopulation, which may become resolvable with larger catalogs. 
+We also perform a data-driven test of whether the data prefers the spin distributions to be identical for both the more and less massive binary components, 
+finding no strong sign of differing distributions. When modeling the $\chi_\mathrm{eff}$ distribution with our model we find similar 
+conclusions as previously reported, the distribution is consistent with a non-isotropic distribution (that peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}),
+showing considerable support ($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
+We conclude by discussing how non-parametric methods in gravitational-wave population inference are poised to provide a useful complement to 
+the parametric approach going into the data-rich catalog era of gravitational-wave astronomy.
 \end{abstract}
@@
 This work benefited from access to the University of Oregon high performance computer, Talapas. This material is based upon work supported 
-in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF’s LIGO Laboratory which is a major facility 
+in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF's LIGO Laboratory which is a major facility 
 fully funded by the National Science Foundation.

### 2022-09-28 src/tex/methods.tex
update methods

@@
 They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
-\it{Basis splines} (or ``B-Splines'') of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
-Therefore, given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of B-Splines for 
-every possible spline function interpolated by knots, $\mathbf{t}$. The basis components for a given knot vector are constructed  
+Basis splines of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
+Therefore, given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of basis splines 
+for every possible spline function interpolated from knots, $\mathbf{t}$. The basis components for a given knot vector are constructed  
 using the Cox-de Boor recursion formula \citep{deBoor78}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:

### 2022-09-28 src/tex/results.tex
Update results.tex
Attempt to fix figs
change fig widths
more fig changes
fix latex figs
fix typos in results.tex

@@
 \begin{figure*}[ht!]
-    \script{mass_distribution_plot.py}
     \begin{centering}
-        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
-        \caption{The primary mass distribution inferred with the \textsc{MSpline} model (red), with 50 knots spaced lineary in $\log m_1$, from the 
+        \includegraphics[width=\linewidth]{figures/mass_distribution_plot.pdf}
+        \caption{The primary mass distribution inferred with the \textsc{M-Spline} model (red), with 50 knots spaced linearly in $\log m_1$, from the 
         minimum observed value to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
@@
     \end{centering}
+    \script{mass_distribution_plot.py}
 \end{figure*}
 
-We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneosly infer the astrophysical mass, spin and redshift distributions of 
+We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin and redshift distributions of 
 a binary black holes (BBHs) given a catalog of gravitational wave observations. We parameterize the binaries' masses with the primary (defined as the more massive component) mass 
-and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. We model 4 of the 6 total 
+and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. Furthermore, we model 4 of the 6 total 
 spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
-$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular mommentum vector. 
+$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular momentum vector. 
 We additionally will fit a population model on the redshift or luminosity distance distribution of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology using the 
 parameters from the Planck 2015 results \cite{Planck2015}, which defines an analytical mapping between each event's inferred
-luminosity distance and it's redshift. While we choose to use MSpline distibutions to model the primary mass and spin distributions, we 
+luminosity distance, and it's redshift. While we choose to use M-Spline distributions to model the primary mass and spin distributions, we 
 model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$. 
 Where $\beta$ is the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \cite{Talbot_2018,o1o2_pop,o3a_pop}.
-We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model \cite{Fishbach_2018redshift}, which is desribed by 
-$p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$. We describe our specific prior choices on the hyper-parameters and each model 
+We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model \cite{Fishbach_2018redshift}, which is described by 
+$p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$. We describe our specific prior choices on the hyperparameters and each model 
 in more detail in Appendix \ref{sec:modelpriors}. We use the same cut on the recent GWTC-3 catalog as was done in the LVK's accompanying population analysis, 
@@
 GW190814 \cite{190814disc}, as it was concluded to be an outlier of the rest of the BBH population in both GWTC-2 and GWTC-3 \cite{o3a_pop,o3b_astro_dist,Essick_2022}. 
-This leaves us with a catalog of 69 BBH mergers observerd oveer a period of about 2 years, from which we want to infer its population properties. 
+This leaves us with a catalog of 69 BBH mergers observed over a period of about 2 years, from which we want to infer its population properties. 
 We start by looking towards the mass distribution.
@@
 We apply our newly constructed models to the BBH analysis that was done in the astrophysical population companion paper to GWTC-3. 
-Figure \ref{fig:mass_distribution} shows how the MSpline model (red) found consistent features in the mass disribution with 
+Figure \ref{fig:mass_distribution} shows how the M-Spline model (red) found consistent features in the mass distribution with 
 what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \cite{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
-In particular our MSpline model finds a peak in merger rate density at both 10 and 35 soloar masses, agreeing with those reported using the same dataset in \citet{o3b_astro_dist}. 
+In particular our M-Spline model finds a peak in merger rate density at both 10 and 35 solar masses, agreeing with those reported using the same dataset in \citet{o3b_astro_dist}. 
 We also find a significantly less declining mass distribution that has considerably larger support for higher mass mergers when 
@@
 There is a strong correlation between the primary mass power law index, $\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- 
-the inferred rate must drastically increase with resdshift to explain the highest mass events in the catalog. However, when one infers a 
-flatter distribution like, as the MSPline did in figure \ref{fig:mass_distribution}, the higher mass mergers are consistent with 
-the local merger rate denstiy as a function of mass given the selection effects. With our more flexible mass model, we find that the merger rate 
-is consistent with being unifom with co-moving volume, with $\lambda_z = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared with 
+the inferred rate must drastically increase with redshift to explain the highest mass events in the catalog. However, when one infers a 
+flatter distribution like, as the M-Spline did in figure \ref{fig:mass_distribution}, the higher mass mergers are consistent with 
+the local merger rate density as a function of mass given the selection effects. With our more flexible mass model, we find that the merger rate 
+is consistent with being uniform with co-moving volume, with $\lambda_z = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared with 
 \citet{o3b_astro_dist}'s reported value -- $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} with the \textsc{PowerlawPeak} mass model.
@@
 We find a similar mass ratio distribution to what was found with the found with the \textsc{PowerlawPeak} model in \citet{o3b_astro_dist}. 
-With the MSpline model on primary mass the mass ratio power law index is $\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, 
+With the M-Spline model on primary mass the mass ratio power law index is $\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, 
 compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} for \textsc{PowerlawPeak}. We find that BBH mergers favor more equal mass mergers
@@
 along with the peak at 35\msun, significantly lower than expected, may pose challenges for conventional stellar evolution theory and could be a sign of 
-the significant presence of sub-populations that may avoid PISN as the binary forms.
+the significant presence of subpopulations that may avoid PISN as the binary forms.
 
@@
 \begin{figure}
-    \script{plot_iid_spinmag.py}
-    \includegraphics[width=0.45\textwidth]{figures/iid_spinmag.pdf}
-    \caption{The spin magnitude distribution inferred with the \textsc{MSpline} model (red), with 16 knots spaced linearly from 0 to 1, and 
+    \begin{centering}    
+        \includegraphics[width=\linewidth]{figures/iid_spinmag.pdf}
+        \caption{The spin magnitude distribution inferred with the \textsc{M-Spline} model (red), with 16 knots spaced linearly from 0 to 1, and 
         assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
         \label{fig:iid_spinmag_dist}
+    \end{centering}
+    \script{plot_iid_spinmag.py}
 \end{figure}
@@
 
-The \textsc{Default} spin model models the spin magnitude of both components as identical and indendendently distributed (IID) non-singular Beta distributions. The
+The \textsc{Default} spin model assumes the spin magnitude of both components are identical and independently distributed (IID) non-singular Beta distributions. The
 Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 
-the Beta distribution non-singluar (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. While in reality, it is expected that 
-all physical bodies must have at least some non-zero angular mommentum, studies have proposed the existence of a distinct sub-population of non-spinning or 
-negliglby spinning black holes that can elude discovery with such a model.
+the Beta distribution non-singular (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. While in reality, it is expected that 
+all physical bodies must have at least some non-zero angular momentum, studies have proposed the existence of a distinct subpopulation of non-spinning or 
+negligibly spinning black holes that can elude discovery with such a model.
 
 \begin{figure} 
-    \script{plot_ind_spinmag.py}
-    \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
-    \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the \textsc{MSpline} model, 
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
+        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the \textsc{M-Spline} model, 
         with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
         \label{fig:ind_spinmag_dist}
+    \end{centering}
+    \script{plot_ind_spinmag.py}
 \end{figure}
 
-We model the spin magnitude distibutions as IID MSpline distibutions as a flexible check
-to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the \textsc{MSpline} model, 
-compared with the \textsc{Default} model from \citet{o3b_astro_dist}. The MSpline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
+We model the spin magnitude distributions as IID M-Spline distributions as a flexible check
+to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the \textsc{M-Spline} model, 
+compared with the \textsc{Default} model from \citet{o3b_astro_dist}. The M-Spline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
 of BBH spins below \result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility. The regions of parameter space where they don't agree as well are the bounds. 
-The MSpline model has no enforcment for vanishing support at the extremal values like the Beta distribution, 
+The M-Spline model has no enforcement for vanishing support at the extremal values like the Beta distribution, 
 allowing it to probe the zero-spin question. We find broad support, with large variance, for non-zero probabilities at $a_i=0$, but cannot confidently determine the presence of 
 a significant non-spinning subpopulation, corroborating the conclusions of \citet{BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}. 
-We now repeat the same analysis as above but with independent MSpline distibutions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
+We now repeat the same analysis as above but with independent M-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
 we show the inferred primary (orange), and secondary (olive) spin magnitude distributions inferred when relaxing the IID assumption. We find both 
@@
 
-The \textsc{Default} spin model models the spin orientation of both components as identical and indendendently distributed (IID) mixture models over an
+The \textsc{Default} spin model assumes the spin orientation of both components are identical and independently distributed (IID) mixture models over an
 aligned and an isotropic component. The aligned component is modeled with a truncated Gaussian distribution with mean at $\cos{\theta}=1$ and variance a free 
-hyper-parameter to be fit. This provides a simple 2-parameter model motivated by simple distributions expected from the two main formation scenario families, allowing 
-for a straightforward interpretation of results. One possible limitation however, is that by construction this distribution is forced to peak at perfecty aligned spins, 
-i.e. $\cos{\theta}=1$. While this may be a reasonable assumption recently \citet{spinitasyoulike} recently extended the model space of parameteric descriptions 
-used to model the spin orientation distribution and found considerably evidence that the distibution peaks away from $\cos{\theta}=1$. Again, this provides a clear 
+hyperparameter to be fit. This provides a simple 2-parameter model motivated by simple distributions expected from the two main formation scenario families, allowing 
+for a straightforward interpretation of results. One possible limitation however, is that by construction this distribution is forced to peak at perfectly aligned spins, 
+i.e. $\cos{\theta}=1$. While this may be a reasonable assumption recently \citet{spinitasyoulike} recently extended the model space of parametric descriptions 
+used to model the spin orientation distribution and found considerably evidence that the distribution peaks away from $\cos{\theta}=1$. Again, this provides a clear 
 use-case where data-driven models can help in our understanding and possibly resolve disputes among differing parametric approaches.
@@
 \begin{figure}
-    \script{plot_iid_spintilt.py}
-    \includegraphics[width=0.45\textwidth]{figures/iid_spintilt.pdf}
-    \caption{The spin orientation distribution inferred with the \textsc{MSpline} model (red), with 16 knots spaced linearly from -1 to 1, and 
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/iid_spintilt.pdf}
+        \caption{The spin orientation distribution inferred with the \textsc{M-Spline} model (red), with 16 knots spaced linearly from -1 to 1, and 
         assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
         \label{fig:iid_spintilt_dist}
+    \end{centering}
+    \script{plot_iid_spintilt.py}
 \end{figure}
 
-We repeat the tests done above on the the spin magnitude distibutions now with the spin orientation distributions. Figure \ref{fig:iid_spintilt_dist} 
-shows the inferred spin magnitude distribution with the \textsc{MSpline} model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
-The MSpline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
-We find a distribution that instead of intrinsicly peaking at $\cos{\theta}=1$, is found to peak at: $\cos{\theta}=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}, at 
+We repeat the tests done above on the spin magnitude distributions now with the spin orientation distributions. Figure \ref{fig:iid_spintilt_dist} 
+shows the inferred spin magnitude distribution with the \textsc{M-Spline} model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
+The M-Spline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
+We find a distribution that instead of intrinsically peaking at $\cos{\theta}=1$, is found to peak at: $\cos{\theta}=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}, at 
 90\% credibility. We find less, but still considerable, support for misaligned spins (i.e. $\cos{\theta}<0$) as the \textsc{Default} model. Specifically we 
@@
 the presence of an isotropic component as expected by dynamical formation channels, albeit less than with the \textsc{Default} model. To quantify the 
-amount of isotropy in the tilt distibution we calculate Y, the ratio defined in Eq. 4 of \citet{spinitasyoulike} which is 1 when the distribution is 
+amount of isotropy in the tilt distribution we calculate Y, the ratio defined in equation 4 of \citet{spinitasyoulike} which is 1 when the distribution is 
 purely isotropic, less than one when negative (anti-aligned) values are favored, and greater than one when positive (aligned) values are favored.
@@
 
-Now we model each of the components' orientation distributions with independent \textsc{MSpline} models as done above, and show the inferred 
-primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distibutions do not agree quite as well as 
-the magnitude distibutions did in figure \ref{fig:ind_spinmag_dist}, and the PPDs look to peak at different values, but the wide uncertainties still are 
+Now we model each of the components' orientation distributions with independent \textsc{M-Spline} models as done above, and show the inferred 
+primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distributions do not agree quite as well as 
+the magnitude distributions did in figure \ref{fig:ind_spinmag_dist}, and the PPDs look to peak at different values, but the wide uncertainties still are 
 consistent with both each other and the \textsc{Default} model's PPD.
@@
 and $\cos{\theta_2}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}, showing that the primary distribution peak is inferred further away 
-from the assumed $\cos{\theta}=1$ with the \textsc{Default} model. There is also significant (albeit uncertain) evidence of spin mis-alignments in each distribution, finding 
-the fraction of mis-aligned primary and secondary components as: $f_{1,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} andand $f_{2,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}.
+from the assumed $\cos{\theta}=1$ with the \textsc{Default} model. There is also significant (albeit uncertain) evidence of spin misalignment in each distribution, finding 
+the fraction of misaligned primary and secondary components as: $f_{1,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} and $f_{2,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}.
 We again calculate the isotropy ratio, Y, for each and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
@@
 \begin{figure}
-    \script{plot_ind_spintilt.py}
-        \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
-        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the \textsc{MSpline} model, 
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
+        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the \textsc{M-Spline} model, 
         with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
         \label{fig:ind_spintilt_dist}
+    \end{centering}
+    \script{plot_ind_spintilt.py}
 \end{figure}
@@
 \begin{figure} 
-    \script{plot_chieff.py}
-    \includegraphics[width=0.45\textwidth]{figures/chi_eff.pdf}
-    \caption{The effective spin distribution inferred with the \textsc{MSpline} model (red), with 24 knots spaced linearly from -1 to 1. 
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/chi_eff.pdf}
+        \caption{The effective spin distribution inferred with the \textsc{M-Spline} model (red), with 24 knots spaced linearly from -1 to 1. 
         The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. We show the inferred $\chi_\mathrm{eff}$ 
-    PPD from the IID component spin \textsc{MSpline} model (green), the independent component spin \textsc{MSpline} model (purple), 
+        PPD from the IID component spin \textsc{M-Spline} model (green), the independent component spin \textsc{M-Spline} model (purple), 
         and the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:chieff_dist}
+    \end{centering}
+    \script{plot_chieff.py}
 \end{figure}
@@
 called the effective spin defined as: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$. As an alternative check 
-on the spin distributions we also try modeling an MSpline distribution of effective spins instead of component spin magnitude and tilts 
-as done above. Figure \ref{fig:chieff_dist} shows the inferred effective spin distribution with the MSpline model (red) along with the 
+on the spin distributions we also try modeling an M-Spline distribution of effective spins instead of component spin magnitude and tilts 
+as done above. Figure \ref{fig:chieff_dist} shows the inferred effective spin distribution with the M-Spline model (red) along with the 
 inferred effective spin distribution transformed from the PPDs of the component spin models shown previously. We find considerable agreement 
-among the component spin distributions, highlighting that wildy different component spin distributions can imply very similar effective spin 
-distributions which is the better constrained parameter. When modeling the effective spin with the \textsc{MSpline} model we see very similar 
+among the component spin distributions, highlighting that different component spin distributions can imply very similar effective spin 
+distributions which is the better constrained parameter. When modeling the effective spin with the \textsc{M-Spline} model we see very similar 
 shape, but with a slightly sharper peak centered at $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}, compared to 
 $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model. As for the misaligned spin question, 
-we can investigate the fraction of systems with effective spins that are mis-aligned (i.e. $\chi_\mathrm{eff}<0$) and find for the \textsc{MSpline} 
-model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}, compared to $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$}
-with the \textsc{Default} model.
+we can investigate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and find for the \textsc{M-Spline} 
+model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}, compared to 
+$f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} with the \textsc{Default} model.

### 2022-09-28 src/tex/results.tex
update results with edits

@@
         \includegraphics[width=\linewidth]{figures/mass_distribution_plot.pdf}
-        \caption{The primary mass distribution inferred with the \textsc{M-Spline} model (red), with 50 knots spaced linearly in $\log m_1$, from the 
+        \caption{The primary mass distribution inferred with the M-Spline model (red), with 50 knots spaced linearly in $\log m_1$, from the 
         minimum observed value to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
@@
 $\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular momentum vector. 
-We additionally will fit a population model on the redshift or luminosity distance distribution of BBHs. We assume a $\Lambda\mathrm{CDM}$ cosmology using the 
-parameters from the Planck 2015 results \cite{Planck2015}, which defines an analytical mapping between each event's inferred
-luminosity distance, and it's redshift. While we choose to use M-Spline distributions to model the primary mass and spin distributions, we 
+We assume the polar spin angles are uniformly distributed in the orbital plane. While we choose to use M-Spline distributions to model the primary mass and spin distributions, we 
 model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$. 
-Where $\beta$ is the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \cite{Talbot_2018,o1o2_pop,o3a_pop}.
-We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model \cite{Fishbach_2018redshift}, which is described by 
-$p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$. We describe our specific prior choices on the hyperparameters and each model 
-in more detail in Appendix \ref{sec:modelpriors}. We use the same cut on the recent GWTC-3 catalog as was done in the LVK's accompanying population analysis, 
-keeping all 70 possibly BBH mergers with false alarm rates less than 1 per year \cite{GWTC3,o3b_astro_dist}. We choose to emit the currently not well understood event, 
-GW190814 \cite{190814disc}, as it was concluded to be an outlier of the rest of the BBH population in both GWTC-2 and GWTC-3 \cite{o3a_pop,o3b_astro_dist,Essick_2022}. 
-This leaves us with a catalog of 69 BBH mergers observed over a period of about 2 years, from which we want to infer its population properties. 
-We start by looking towards the mass distribution.
+Where $\beta$ is the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \citep{Talbot_2018,o1o2_pop,o3a_pop}.
+Additionally, we fit a population model on the redshift or luminosity distance distribution of BBHs, assuming a $\Lambda\mathrm{CDM}$ cosmology defined by the parameters 
+from the Planck 2015 results \citep{Planck2015}. This defines an analytical mapping between each event's inferred luminosity distance, and it's redshift, which we now use interchangeably. 
+We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model, described by $p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$ \citep{Fishbach_2018redshift}.
+We describe our specific prior choices on the hyperparameters and each model in more detail in Appendix \ref{sec:modelpriors}. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
+accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist}. Since it was concluded to be an outlier of the rest of 
+the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
+a catalog of 69 confident BBH mergers observed over a period of about 2 years, from which we want to infer its population properties. Our study provides the first comprehensive 
+data-driven investigation of the BBH mass and spin distributions, uncovering new insights and corroborating those found with other methods. 
+We start by looking towards our model's inferences of the mass distribution.
 
@@
 Figure \ref{fig:mass_distribution} shows how the M-Spline model (red) found consistent features in the mass distribution with 
-what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \cite{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
-In particular our M-Spline model finds a peak in merger rate density at both 10 and 35 solar masses, agreeing with those reported using the same dataset in \citet{o3b_astro_dist}. 
-We also find a significantly less declining mass distribution that has considerably larger support for higher mass mergers when 
-compared to the other power-law based models, finding that 75\% percent of primary masses below \result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_75percentile]}$}, 
-at 90\% credibility, compared to \result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_75percentile]}$}, found with the similar \textsc{PowerlawSpline} model. 
+what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
+In particular our M-Spline model finds a peak in merger rate density as a function of primary mass, at both $\sim10\msun$ and $\sim35\msun$ agreeing with those 
+reported using the same dataset in \citet{o3b_astro_dist}. We also find a shallow mass distribution that has considerably larger support for higher mass mergers when 
+compared to power-law based models. The M-Spline model finds that 75\% percent of primary masses are below \result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_75percentile]}$}, 
+compared to \result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_75percentile]}$}, found with the similar \textsc{PowerlawSpline} model. 
 An interesting consequence of this is that we do not find a confidently evolving merger rate with redshift, as inferred with power-law based mass models in \citet{o3b_astro_dist}. 
@@
 
-We find a similar mass ratio distribution to what was found with the found with the \textsc{PowerlawPeak} model in \citet{o3b_astro_dist}. 
+We find a similar mass ratio distribution to what was found with the \textsc{PowerlawPeak} model in \citet{o3b_astro_dist}. 
 With the M-Spline model on primary mass the mass ratio power law index is $\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, 
@@
         \includegraphics[width=\linewidth]{figures/iid_spinmag.pdf}
-        \caption{The spin magnitude distribution inferred with the \textsc{M-Spline} model (red), with 16 knots spaced linearly from 0 to 1, and 
+        \caption{The spin magnitude distribution inferred with the M-Spline model (red), with 16 knots spaced linearly from 0 to 1, and 
         assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
         \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
-        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the \textsc{M-Spline} model, 
+        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the M-Spline model, 
         with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
 We model the spin magnitude distributions as IID M-Spline distributions as a flexible check
-to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the \textsc{M-Spline} model, 
+to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the M-Spline model, 
 compared with the \textsc{Default} model from \citet{o3b_astro_dist}. The M-Spline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
@@
         \includegraphics[width=\linewidth]{figures/iid_spintilt.pdf}
-        \caption{The spin orientation distribution inferred with the \textsc{M-Spline} model (red), with 16 knots spaced linearly from -1 to 1, and 
+        \caption{The spin orientation distribution inferred with the M-Spline model (red), with 16 knots spaced linearly from -1 to 1, and 
         assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
 We repeat the tests done above on the spin magnitude distributions now with the spin orientation distributions. Figure \ref{fig:iid_spintilt_dist} 
-shows the inferred spin magnitude distribution with the \textsc{M-Spline} model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
+shows the inferred spin magnitude distribution with the M-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
 The M-Spline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
@@
 90\% credibility. We find less, but still considerable, support for misaligned spins (i.e. $\cos{\theta}<0$) as the \textsc{Default} model. Specifically we 
-find that the fraction of misaligned systems is $f_{<0}=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}. This implies 
+find that the fraction of misaligned systems is $f_{\cos{\theta}<0}=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}. This implies 
 the presence of an isotropic component as expected by dynamical formation channels, albeit less than with the \textsc{Default} model. To quantify the 
@@
 
-Now we model each of the components' orientation distributions with independent \textsc{M-Spline} models as done above, and show the inferred 
+Now we model each of the components' orientation distributions with independent M-Spline models as done above, and show the inferred 
 primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distributions do not agree quite as well as 
@@
 from the assumed $\cos{\theta}=1$ with the \textsc{Default} model. There is also significant (albeit uncertain) evidence of spin misalignment in each distribution, finding 
-the fraction of misaligned primary and secondary components as: $f_{1,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} and $f_{2,<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}.
-We again calculate the isotropy ratio, Y, for each and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
+the fraction of misaligned primary and secondary components as: $f_{\cos{\theta_1}<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} and 
+$f_{\cos{\theta_2}<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}. We again calculate the isotropy ratio, Y, 
+for each and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
 $\log_{10}Y_2=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$}.
@@
         \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
-        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the \textsc{M-Spline} model, 
+        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the M-Spline model, 
         with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
         \includegraphics[width=\linewidth]{figures/chi_eff.pdf}
-        \caption{The effective spin distribution inferred with the \textsc{M-Spline} model (red), with 24 knots spaced linearly from -1 to 1. 
+        \caption{The effective spin distribution inferred with the M-Spline model (red), with 24 knots spaced linearly from -1 to 1. 
         The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. We show the inferred $\chi_\mathrm{eff}$ 
-        PPD from the IID component spin \textsc{M-Spline} model (green), the independent component spin \textsc{M-Spline} model (purple), 
+        PPD from the IID component spin M-Spline model (green), the independent component spin M-Spline model (purple), 
         and the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
@@
 among the component spin distributions, highlighting that different component spin distributions can imply very similar effective spin 
-distributions which is the better constrained parameter. When modeling the effective spin with the \textsc{M-Spline} model we see very similar 
+distributions which is the better constrained parameter. When modeling the effective spin with the M-Spline model we see very similar 
 shape, but with a slightly sharper peak centered at $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}, compared to 
 $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model. As for the misaligned spin question, 
-we can investigate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and find for the \textsc{M-Spline} 
+we can investigate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and find for the M-Spline 
 model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}, compared to 

### 2022-09-28 src/tex/results.tex
update results and macros with o3b gaussian chieff results

@@
         PPD from the IID component spin M-Spline model (green), the independent component spin M-Spline model (purple), 
-        and the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        and both the \textsc{Default} (blue) model and the Gaussian $\chi_\mathrm{eff}$ (olive) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:chieff_dist}
@@
 shape, but with a slightly sharper peak centered at $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}, compared to 
-$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model. As for the misaligned spin question, 
-we can investigate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and find for the M-Spline 
-model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}, compared to 
-$f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} with the \textsc{Default} model.
+$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model and 
+$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$} with the Gaussian $\chi_\mathrm{eff}$ model. 
+As for the misaligned spin question, we calculate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and 
+find for the M-Spline model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}, compared to 
+$f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} with the \textsc{Default} model and 
+$f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelow0]}$} with the Gaussian $\chi_\mathrm{eff}$ model.

### 2022-09-28 src/scripts/create_macros.py

@@ -110,9 +110,15 @@ def chi_eff():
     msplind = ppds["MSplineInd"]
     mspliid = ppds['MSplineIID']
     msplchieff = dd.io.load(paths.data / "mspline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5")
-    below_0 = {'default': [], 'iid': [], 'ind': [], 'chieff': []}
-    below_m0p3 = {'default': [], 'iid': [], 'ind': [], 'chieff': []}
-    maxchis = {'default': [], 'iid': [], 'ind': [], 'chieff': []}
+    below_0 = {'default': [], 'iid': [], 'ind': [], 'chieff': [], 'gaussian': []}
+    below_m0p3 = {'default': [], 'iid': [], 'ind': [], 'chieff': [], 'gaussian': []}
+    maxchis = {'default': [], 'iid': [], 'ind': [], 'chieff': [], 'gaussian': []}
+    with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json",'r') as jf:
+        gaussian_data = json.load(jf)
+    for k in range(500):
+        below_m0p3['gaussian'].append(np.trapz(gaussian_data['chi_eff_pdfs'][k,gaussian_data['chi_eff_grid']<-0.3], x=gaussian_data['chi_eff_grid'][gaussian_data['chi_eff_grid']<-0.3]))
+        below_0['gaussian'].append(np.trapz(gaussian_data['chi_eff_pdfs'][k,gaussian_data['chi_eff_grid']<0.0], x=gaussian_data['chi_eff_grid'][gaussian_data['chi_eff_grid']<0.0]))
+        maxchis['gaussian'].append(gaussian_data['chi_eff_grid'][np.argmax(gaussian_data['chi_eff_pdfs'][k])])
     for i in range(1500):
         norm = np.trapz(msplchieff['dRdchieff'][i, :], x=msplchieff['chieffs'])
         below_m0p3['chieff'].append(np.trapz(1./norm*msplchieff['dRdchieff'][i, msplchieff['chieffs']<-0.3], x=msplchieff['chieffs'][msplchieff['chieffs']<-0.3]))

### 2022-09-28 src/tex/macros.tex
update more results with edits

--- 2022-09-26 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "a1\_90percentile": \{"median": "0.75", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.58", "95th percentile": "0.89"\}, "a2\_90percentile": \{"median": "0.78", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.61", "95th percentile": "0.91"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "a\_90percentile": \{"median": "0.69", "error plus": "0.15", "error minus": "0.16", "5th percentile": "0.53", "95th percentile": "0.84"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}, "lamb": \{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}, "a1\_90percentile": \{"median": "0.75", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.58", "95th percentile": "0.89"\}, "a2\_90percentile": \{"median": "0.78", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.61", "95th percentile": "0.91"\}, "peakCosTilt1": \{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}, "peakCosTilt2": \{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}, "log10gammaFrac1": \{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}, "log10gammaFrac2": \{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}, "negFrac1": \{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}, "negFrac2": \{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}, "a\_90percentile": \{"median": "0.69", "error plus": "0.15", "error minus": "0.16", "5th percentile": "0.53", "95th percentile": "0.84"\}, "lamb": \{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}, "peakCosTilt": \{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}, "log10gammaFrac": \{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}, "negFrac": \{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}, "iid": \{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}, "ind": \{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXVII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}, "MSpline": \{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}, "PLSpline": \{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXX\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": "1.08", "error plus": "1.69", "error minus": "1.32", "5th percentile": "{-}0.25", "95th percentile": "2.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": "2.73", "error plus": "1.82", "error minus": "1.87", "5th percentile": "0.86", "95th percentile": "4.54"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": "1.71", "error plus": "1.61", "error minus": "1.43", "5th percentile": "0.28", "95th percentile": "3.35"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": "{-}0.54", "error plus": "1.53", "error minus": "1.56", "5th percentile": "{-}2.10", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.00}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": "0.75", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.58", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.75}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.58}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": "0.78", "error plus": "0.14", "error minus": "0.17", "5th percentile": "0.61", "95th percentile": "0.91"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.78}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.91}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": "0.19", "error plus": "0.73", "error minus": "0.73", "5th percentile": "{-}0.54", "95th percentile": "0.89"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.89}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": "0.40", "error plus": "0.64", "error minus": "1.06", "5th percentile": "{-}0.66", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.00}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": "0.13", "error plus": "0.71", "error minus": "0.70", "5th percentile": "{-}0.57", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.70}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.84}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": "0.28", "error plus": "0.72", "error minus": "0.74", "5th percentile": "{-}0.46", "95th percentile": "0.99"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.99}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": "0.43", "error plus": "0.19", "error minus": "0.18", "5th percentile": "0.25", "95th percentile": "0.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.62}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": "0.37", "error plus": "0.19", "error minus": "0.16", "5th percentile": "0.21", "95th percentile": "0.57"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.57}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": "1.68", "error plus": "1.58", "error minus": "1.36", "5th percentile": "0.32", "95th percentile": "3.31"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{3.31}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": "0.69", "error plus": "0.15", "error minus": "0.16", "5th percentile": "0.53", "95th percentile": "0.84"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.69}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.53}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.84}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": "{-}0.54", "error plus": "1.55", "error minus": "1.58", "5th percentile": "{-}2.12", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.00}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": "0.37", "error plus": "0.64", "error minus": "0.50", "5th percentile": "{-}0.14", "95th percentile": "1.00"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.50}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{1.00}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": "0.31", "error plus": "0.66", "error minus": "0.66", "5th percentile": "{-}0.35", "95th percentile": "0.96"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.96}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": "0.34", "error plus": "0.12", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.47}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}, "FracBelow0": \{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}, "PeakChiEff": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIII\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXVI\else\def\macros@XXV@out{??}\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}, "FracBelow0": \{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}, "PeakChiEff": \{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XXXIX\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}, "FracBelow0": \{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}, "PeakChiEff": \{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XL\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLII\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}, "m\_99percentile": \{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@XLV\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}, "m\_75percentile": \{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}, "m\_99percentile": \{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@XLVIII\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}, "m\_75percentile": \{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}, "m\_99percentile": \{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@L\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LI\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": "0.01", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.00", "95th percentile": "0.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.01}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.03}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": "0.43", "error plus": "0.08", "error minus": "0.15", "5th percentile": "0.28", "95th percentile": "0.49"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.49}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "{-}0.01", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.05}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": "0.02", "error plus": "0.03", "error minus": "0.02", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.05}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": "0.35", "error plus": "0.10", "error minus": "0.12", "5th percentile": "0.23", "95th percentile": "0.44"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.44}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": "0.03", "error plus": "0.04", "error minus": "0.02", "5th percentile": "0.01", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.02}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.07}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": "0.03", "error plus": "0.02", "error minus": "0.01", "5th percentile": "0.02", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.05}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": "0.39", "error plus": "0.08", "error minus": "0.07", "5th percentile": "0.32", "95th percentile": "0.47"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.08}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.07}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.47}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": "0.03", "error plus": "0.03", "error minus": "0.03", "5th percentile": "0.00", "95th percentile": "0.05"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.05}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": "0.07", "error plus": "0.05", "error minus": "0.03", "5th percentile": "0.04", "95th percentile": "0.12"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.05}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.04}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.12}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": "0.40", "error plus": "0.10", "error minus": "0.10", "5th percentile": "0.29", "95th percentile": "0.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.40}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.10}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.50}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": "0.04", "error plus": "0.04", "error minus": "0.04", "5th percentile": "{-}0.00", "95th percentile": "0.07"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.04}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{{-}0.00}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.07}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{6.81}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": "14.95", "error plus": "5.51", "error minus": "2.75", "5th percentile": "12.20", "95th percentile": "21.03"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{14.95}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{5.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{2.75}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{12.20}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{21.03}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": "44.77", "error plus": "9.94", "error minus": "6.18", "5th percentile": "38.59", "95th percentile": "55.46"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{44.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{38.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{55.46}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": "5.91", "error plus": "0.51", "error minus": "0.19", "5th percentile": "5.72", "95th percentile": "6.50"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{5.91}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{5.72}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{6.50}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": "30.48", "error plus": "4.42", "error minus": "7.86", "5th percentile": "22.61", "95th percentile": "34.17"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{30.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{4.42}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{7.86}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{22.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{34.17}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": "80.10", "error plus": "11.37", "error minus": "12.53", "5th percentile": "67.57", "95th percentile": "91.26"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{80.10}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{11.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{12.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{67.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{91.26}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": "6.22", "error plus": "0.64", "error minus": "1.08", "5th percentile": "5.14", "95th percentile": "6.81"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{6.81}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": "11.22", "error plus": "4.64", "error minus": "0.59", "5th percentile": "10.63", "95th percentile": "16.62"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{11.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{4.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{10.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{16.62}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": "43.20", "error plus": "10.47", "error minus": "4.71", "5th percentile": "38.49", "95th percentile": "54.97"\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{43.20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{10.47}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{38.49}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{54.97}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\macros@LI@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}, "lamb": \{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}, "lamb": \{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}, "a1\_90percentile": \{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}, "peakCosTilt1": \{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}, "peakCosTilt2": \{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}, "log10gammaFrac1": \{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}, "log10gammaFrac2": \{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}, "negFrac1": \{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}, "negFrac2": \{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}, "a\_90percentile": \{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}, "lamb": \{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}, "peakCosTilt": \{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}, "negFrac": \{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.000245, "error plus": 0.00671, "error minus": 0.000245, "5th percentile": 1.11e{-}07, "95th percentile": 0.00835, "10th percentile": 9.17e{-}07, "90th percentile": 0.00386\}, "FracBelow0": \{"median": 0.276, "error plus": 0.145, "error minus": 0.128, "5th percentile": 0.148, "95th percentile": 0.425, "10th percentile": 0.176, "90th percentile": 0.391\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.0311, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.0319, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.551, "error plus": 0.289, "error minus": 0.256, "5th percentile": 0.296, "95th percentile": 0.849, "10th percentile": 0.351, "90th percentile": 0.782\}, "frac\_hm": \{"median": 0.00153, "error plus": 0.0419, "error minus": 0.00153, "5th percentile": 6.94e{-}07, "95th percentile": 0.0522, "10th percentile": 5.73e{-}06, "90th percentile": 0.0241\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}, "lamb": \{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}, "lamb": \{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}, "a1\_90percentile": \{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}, "peakCosTilt1": \{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}, "peakCosTilt2": \{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}, "log10gammaFrac1": \{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}, "log10gammaFrac2": \{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}, "negFrac1": \{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}, "negFrac2": \{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}, "a\_90percentile": \{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}, "lamb": \{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}, "peakCosTilt": \{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}, "negFrac": \{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.000245, "error plus": 0.00671, "error minus": 0.000245, "5th percentile": 1.11e{-}07, "95th percentile": 0.00835, "10th percentile": 9.17e{-}07, "90th percentile": 0.00386\}, "FracBelow0": \{"median": 0.276, "error plus": 0.145, "error minus": 0.128, "5th percentile": 0.148, "95th percentile": 0.425, "10th percentile": 0.176, "90th percentile": 0.391\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.0311, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.0319, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.551, "error plus": 0.289, "error minus": 0.256, "5th percentile": 0.296, "95th percentile": 0.849, "10th percentile": 0.351, "90th percentile": 0.782\}, "frac\_hm": \{"median": 0.00153, "error plus": 0.0419, "error minus": 0.00153, "5th percentile": 6.94e{-}07, "95th percentile": 0.0522, "10th percentile": 5.73e{-}06, "90th percentile": 0.0241\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXVIII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXXI\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.246}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.0162}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.39}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.856}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.15}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.279}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{0.605}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{2.94}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.537}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.996}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}1.75}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.685}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.751}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.141}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.167}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.584}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.886}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.623}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.86}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.777}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.138}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.607}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.907}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.645}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.885}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.193}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.726}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.731}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.538}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.379}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.708}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.395}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.636}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.664}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.363}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.984}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.133}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.708}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.699}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.565}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.845}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.407}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{0.685}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.276}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.716}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.741}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.465}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.986}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.292}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.828}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.427}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.189}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.178}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.249}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.618}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.283}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.577}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.373}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.188}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.161}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.212}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.568}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.244}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.526}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{3.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.624}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{2.92}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.692}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.148}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.158}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.534}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.836}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.567}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.805}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.997}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}1.76}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.687}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.367}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.641}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.503}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{{-}0.135}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.878}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.658}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.659}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.349}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.965}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.803}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.344}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.124}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.116}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.228}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{0.252}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.442}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XXXVI\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XLI\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLVI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@LI\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.000245, "error plus": 0.00671, "error minus": 0.000245, "5th percentile": 1.11e{-}07, "95th percentile": 0.00835, "10th percentile": 9.17e{-}07, "90th percentile": 0.00386\}, "FracBelow0": \{"median": 0.276, "error plus": 0.145, "error minus": 0.128, "5th percentile": 0.148, "95th percentile": 0.425, "10th percentile": 0.176, "90th percentile": 0.391\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.0311, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.0319, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.551, "error plus": 0.289, "error minus": 0.256, "5th percentile": 0.296, "95th percentile": 0.849, "10th percentile": 0.351, "90th percentile": 0.782\}, "frac\_hm": \{"median": 0.00153, "error plus": 0.0419, "error minus": 0.00153, "5th percentile": 6.94e{-}07, "95th percentile": 0.0522, "10th percentile": 5.73e{-}06, "90th percentile": 0.0241\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVIII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVIII@out\macros@LVI\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LVII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LIX\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LXII\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXXI@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXXI@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXXI@out\macros@LXV\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.0137}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.0158}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.0107}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.00302}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.0303}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.00431}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.0259}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.433}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.0759}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.158}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.275}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.309}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.484}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.00501}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.0531}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.043}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.866}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.152}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.316}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.55}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.618}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.968}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.0859}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.0986}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.067}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.0188}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.189}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.027}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.162}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.0198}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.0153}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.0154}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.00444}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.0355}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.00599}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.0322}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.351}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.0966}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.119}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.232}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.438}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.248}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.429}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.026}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.00501}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.0671}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.0551}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.702}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.193}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.238}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.463}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.876}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.496}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.858}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.124}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.0957}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.0961}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.0278}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.222}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.0374}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.201}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.0321}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.0183}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.0144}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.0177}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.0505}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.0215}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.0434}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.399}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.0722}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.0682}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.331}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.473}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.348}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.449}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.023}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.0257}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.001}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.00501}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.041}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.799}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.144}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.136}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.662}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.946}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.696}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.897}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.114}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.0899}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.111}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.316}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.134}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.271}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.0705}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.0475}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.0345}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.0361}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.0421}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.104}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.398}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.101}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.104}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.294}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.499}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.313}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.475}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.0351}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.044}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.0731}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.00881}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.0631}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.797}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.202}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.208}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.588}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.997}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.626}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.95}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.441}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.297}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.215}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.225}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.751}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.263}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.65}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.000245, "error plus": 0.00671, "error minus": 0.000245, "5th percentile": 1.11e{-}07, "95th percentile": 0.00835, "10th percentile": 9.17e{-}07, "90th percentile": 0.00386\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.000245}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.00671}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.000245}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{1.11e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.00835}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{9.17e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.00386}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.276, "error plus": 0.145, "error minus": 0.128, "5th percentile": 0.148, "95th percentile": 0.425, "10th percentile": 0.176, "90th percentile": 0.391\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.276}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.145}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.128}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.148}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.425}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.176}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.391}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.06, "error plus": 0.0311, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.0319, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.0311}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.0319}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.082}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.551, "error plus": 0.289, "error minus": 0.256, "5th percentile": 0.296, "95th percentile": 0.849, "10th percentile": 0.351, "90th percentile": 0.782\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.551}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.289}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.256}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{0.296}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.849}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{0.351}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.782}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.00153, "error plus": 0.0419, "error minus": 0.00153, "5th percentile": 6.94e{-}07, "95th percentile": 0.0522, "10th percentile": 5.73e{-}06, "90th percentile": 0.0241\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.00153}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.0419}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.00153}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{6.94e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{0.0522}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{5.73e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.0241}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.643}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{6.81}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{5.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{6.71}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{14.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{5.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{2.75}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{12.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{21.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{12.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{19.1}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{44.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{38.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{55.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{39.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{52.4}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{5.91}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.509}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.194}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{5.72}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{6.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{5.72}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{6.3}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{30.5}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{4.42}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{7.86}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{22.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{34.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{24.5}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{33.5}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{80.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{11.4}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{12.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{67.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{91.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{70.2}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{89.3}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.643}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.81}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.71}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{11.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{4.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{0.589}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{10.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{16.6}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{10.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{15.0}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{43.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{10.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{38.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{39.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52.2}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\makeatother

### 2022-09-28 src/tex/results.tex
update more results with edits

@@
         minimum observed value to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
-        the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawSpline} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models 
+        from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
         \label{fig:mass_distribution}
@@
 compared to power-law based models. The M-Spline model finds that 75\% percent of primary masses are below \result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_75percentile]}$}, 
-compared to \result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_75percentile]}$}, found with the similar \textsc{PowerlawSpline} model. 
+compared to \result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_75percentile]}$} and \result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_75percentile]}$}, found with 
+the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} models respectively.
 An interesting consequence of this is that we do not find a confidently evolving merger rate with redshift, as inferred with power-law based mass models in \citet{o3b_astro_dist}.
-There is a strong correlation between the primary mass power law index, $\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- 
+There is a strong correlation measured between the primary mass power law index, $\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- 
 the inferred rate must drastically increase with redshift to explain the highest mass events in the catalog. However, when one infers a 
-flatter distribution like, as the M-Spline did in figure \ref{fig:mass_distribution}, the higher mass mergers are consistent with 
+flatter distribution like, as the M-Spline does in figure \ref{fig:mass_distribution}, the higher-mass mergers are consistent with 
 the local merger rate density as a function of mass given the selection effects. With our more flexible mass model, we find that the merger rate 
 is consistent with being uniform with co-moving volume, with $\lambda_z = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared with 
-\citet{o3b_astro_dist}'s reported value -- $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} with the \textsc{PowerlawPeak} mass model.
+\citet{o3b_astro_dist}'s reported value of $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} with the \textsc{PowerlawPeak} mass model.
 
@@
 compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} for \textsc{PowerlawPeak}. We find that BBH mergers favor more equal mass mergers
-as would be expected of both main formation channels due to binary mass transfer in isolated formation and three-body interactions that preferentially eject
-the lightest of the three compact objects, in dynamical formation \bruce{cite these}. We also find no evidence for a sharp fall off in merger rate following 
-the pileup at $\sim35\,\msun$, which is expected if such a pileup was due to pulsational pair instability supernovae (PPISNe). The lack of any high mass truncation 
-along with the peak at 35\msun, significantly lower than expected, may pose challenges for conventional stellar evolution theory and could be a sign of 
-the significant presence of subpopulations that may avoid PISN as the binary forms.
+as would be expected of both main formation channels due to binary mass transfer in isolated formation \bruce{double check this statement with pop synth lit} 
+and three-body interactions that preferentially eject the lightest of the three compact objects, in dynamical formation \bruce{cite these}. 
+We also find no evidence for a sharp fall off in merger rate following the pileup at $\sim35\,\msun$, which is expected if such a pileup was due 
+to pulsational pair instability supernovae (PPISNe). The lack of any high mass truncation along with the peak at 35\msun, significantly lower 
+than expected, may pose challenges for conventional stellar evolution theory and could be a sign of the significant 
+presence of subpopulations that may avoid PISN as the binary forms.
 
@@
 
-The \textsc{Default} spin model assumes the spin magnitude of both components are identical and independently distributed (IID) non-singular Beta distributions. The
-Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 
-the Beta distribution non-singular (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. While in reality, it is expected that 
+The \textsc{Default} spin model describes the spin magnitude of both components are identical and independently distributed (IID) non-singular Beta distributions. \bruce{cite Wysocki/Talbot}
+The Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 
+the Beta distribution non-singular (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. In reality, it is expected that 
 all physical bodies must have at least some non-zero angular momentum, studies have proposed the existence of a distinct subpopulation of non-spinning or 
-negligibly spinning black holes that can elude discovery with such a model.
+negligibly spinning black holes that can elude discovery with such a model \citep{FullerMa2019,RouletGWTC2Pop,BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}.
 
@@
 to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the M-Spline model, 
-compared with the \textsc{Default} model from \citet{o3b_astro_dist}. The M-Spline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
-of BBH spins below \result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility. The regions of parameter space where they don't agree as well are the bounds. 
-The M-Spline model has no enforcement for vanishing support at the extremal values like the Beta distribution, 
+compared with the \textsc{Default} model. The M-Spline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
+of BBH spins below \result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility. The regions of parameter space where they don't agree as well are at 
+the boundaries. The M-Spline model has no enforcement for vanishing support at the extremal values like the Beta distribution, 
 allowing it to probe the zero-spin question. We find broad support, with large variance, for non-zero probabilities at $a_i=0$, but cannot confidently determine the presence of 
-a significant non-spinning subpopulation, corroborating the conclusions of \citet{BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}. 
+a significant non-spinning subpopulation, corroborating similar recent conclusions \citep{BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}. 
 We now repeat the same analysis as above but with independent M-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
@@
 for a straightforward interpretation of results. One possible limitation however, is that by construction this distribution is forced to peak at perfectly aligned spins, 
-i.e. $\cos{\theta}=1$. While this may be a reasonable assumption recently \citet{spinitasyoulike} recently extended the model space of parametric descriptions 
-used to model the spin orientation distribution and found considerably evidence that the distribution peaks away from $\cos{\theta}=1$. Again, this provides a clear 
+i.e. $\cos{\theta}=1$. While this may be a reasonable assumption, \citet{spinitasyoulike} recently extended the model space of parametric descriptions 
+used to model the spin orientation distribution and found considerable evidence that the distribution peaks away from $\cos{\theta}=1$. Again, this provides a clear 
 use-case where data-driven models can help in our understanding and possibly resolve disputes among differing parametric approaches.
@@
 the presence of an isotropic component as expected by dynamical formation channels, albeit less than with the \textsc{Default} model. To quantify the 
-amount of isotropy in the tilt distribution we calculate Y, the ratio defined in equation 4 of \citet{spinitasyoulike} which is 1 when the distribution is 
-purely isotropic, less than one when negative (anti-aligned) values are favored, and greater than one when positive (aligned) values are favored.
-We find a $\log_{10}Y=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}.
+amount of isotropy in the tilt distribution we calculate $\log_{10}Y$, where $Y$ is the ratio of nearly aligned tilts to nearly anti-aligned, 
+introduced in \citet{spinitasyoulike} and defined as:
+
+\begin{equation}
+    Y \equiv \frac{\int_{0.9}^{1.0} d\cos{\theta} p(\cos{\theta})}{\int_{-1.0}^{-0.9} d\cos{\theta} p(\cos{\theta})}
+\end{equation}
+
+\noindent Now the log this quantity, $\log_{10}Y$, is 0 for tilt distribution that is purely isotropic, negative when anti-aligned values are favored, 
+and positive when aligned tilts are favored. We find a $\log_{10}Y=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}, exhibiting a 
+slight preference for aligned tilts.
 
@@
 the fraction of misaligned primary and secondary components as: $f_{\cos{\theta_1}<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} and 
-$f_{\cos{\theta_2}<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}. We again calculate the isotropy ratio, Y, 
-for each and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
+$f_{\cos{\theta_2}<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}. We again calculate $\log_{10}Y$  
+for each component distribution and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
 $\log_{10}Y_2=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$}.
@@
 distributions which is the better constrained parameter. When modeling the effective spin with the M-Spline model we see very similar 
-shape, but with a slightly sharper peak centered at $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}, compared to 
+shape, but with a sharper peak centered at $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}, compared to 
 $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model and 

### 2022-09-28 src/scripts/create_macros.py

@@ -115,17 +115,14 @@ def chi_eff():
     maxchis = {'default': [], 'iid': [], 'ind': [], 'chieff': [], 'gaussian': []}
     with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json",'r') as jf:
         gaussian_data = json.load(jf)
-    for k in range(500):
-        below_m0p3['gaussian'].append(np.trapz(gaussian_data['chi_eff_pdfs'][k,gaussian_data['chi_eff_grid']<-0.3], x=gaussian_data['chi_eff_grid'][gaussian_data['chi_eff_grid']<-0.3]))
-        below_0['gaussian'].append(np.trapz(gaussian_data['chi_eff_pdfs'][k,gaussian_data['chi_eff_grid']<0.0], x=gaussian_data['chi_eff_grid'][gaussian_data['chi_eff_grid']<0.0]))
-        maxchis['gaussian'].append(gaussian_data['chi_eff_grid'][np.argmax(gaussian_data['chi_eff_pdfs'][k])])
+        gauschieff = {'pchieff': np.array(gaussian_data['chi_eff_pdfs']), 'chieffs': np.array(gaussian_data['chi_eff_grid'])}
     for i in range(1500):
         norm = np.trapz(msplchieff['dRdchieff'][i, :], x=msplchieff['chieffs'])
         below_m0p3['chieff'].append(np.trapz(1./norm*msplchieff['dRdchieff'][i, msplchieff['chieffs']<-0.3], x=msplchieff['chieffs'][msplchieff['chieffs']<-0.3]))
         below_0['chieff'].append(np.trapz(1./norm*msplchieff['dRdchieff'][i, msplchieff['chieffs']<0.0], x=msplchieff['chieffs'][msplchieff['chieffs']<0.0]))
         maxchis['chieff'].append(msplchieff['chieffs'][np.argmax(msplchieff['dRdchieff'][i])])
     for j in range(500):
-        for k,v in zip(['default', 'ind', 'iid'], [default, msplind, mspliid]):
+        for k,v in zip(['default', 'ind', 'iid', 'gaussian'], [default, msplind, mspliid, gauschieff]):
             below_m0p3[k].append(np.trapz(v['pchieff'][j,v['chieffs']<-0.3], x=v['chieffs'][v['chieffs']<-0.3]))
[…]

### 2022-09-28 src/tex/macros.tex
update macros

--- 2022-09-26 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}, "a1\_90percentile": \{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}, "peakCosTilt1": \{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}, "peakCosTilt2": \{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}, "log10gammaFrac1": \{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}, "log10gammaFrac2": \{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}, "negFrac1": \{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}, "a\_90percentile": \{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}, "peakCosTilt": \{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}, "negFrac": \{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.015, "error minus": 0.0092, "5th percentile": 0.0036, "95th percentile": 0.029, "10th percentile": 0.0048, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.15, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.3, "5th percentile": 0.56, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.08, "error plus": 0.094, "error minus": 0.058, "5th percentile": 0.023, "95th percentile": 0.18, "10th percentile": 0.03, "90th percentile": 0.15\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.025, "error minus": 0.015, "5th percentile": 0.0046, "95th percentile": 0.046, "10th percentile": 0.006, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.35, "error plus": 0.096, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.24, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.029, "error plus": 0.038, "error minus": 0.022, "5th percentile": 0.007, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.059\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.25, "5th percentile": 0.45, "95th percentile": 0.87, "10th percentile": 0.48, "90th percentile": 0.85\}, "frac\_hm": \{"median": 0.12, "error plus": 0.16, "error minus": 0.095, "5th percentile": 0.029, "95th percentile": 0.29, "10th percentile": 0.038, "90th percentile": 0.2\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.017, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.39, "error plus": 0.075, "error minus": 0.071, "5th percentile": 0.32, "95th percentile": 0.47, "10th percentile": 0.34, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.027, "error plus": 0.026, "error minus": 0.026, "5th percentile": 0.001, "95th percentile": 0.051, "10th percentile": 0.005, "90th percentile": 0.045\}, "frac\_dyn": \{"median": 0.79, "error plus": 0.15, "error minus": 0.14, "5th percentile": 0.65, "95th percentile": 0.95, "10th percentile": 0.68, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.089, "5th percentile": 0.11, "95th percentile": 0.31, "10th percentile": 0.14, "90th percentile": 0.27\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}, "a1\_90percentile": \{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}, "peakCosTilt1": \{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}, "peakCosTilt2": \{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}, "log10gammaFrac1": \{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}, "log10gammaFrac2": \{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}, "negFrac1": \{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}, "a\_90percentile": \{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}, "peakCosTilt": \{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}, "negFrac": \{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.015, "error minus": 0.0092, "5th percentile": 0.0036, "95th percentile": 0.029, "10th percentile": 0.0048, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.15, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.3, "5th percentile": 0.56, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.08, "error plus": 0.094, "error minus": 0.058, "5th percentile": 0.023, "95th percentile": 0.18, "10th percentile": 0.03, "90th percentile": 0.15\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.025, "error minus": 0.015, "5th percentile": 0.0046, "95th percentile": 0.046, "10th percentile": 0.006, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.35, "error plus": 0.096, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.24, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.029, "error plus": 0.038, "error minus": 0.022, "5th percentile": 0.007, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.059\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.25, "5th percentile": 0.45, "95th percentile": 0.87, "10th percentile": 0.48, "90th percentile": 0.85\}, "frac\_hm": \{"median": 0.12, "error plus": 0.16, "error minus": 0.095, "5th percentile": 0.029, "95th percentile": 0.29, "10th percentile": 0.038, "90th percentile": 0.2\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.017, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.39, "error plus": 0.075, "error minus": 0.071, "5th percentile": 0.32, "95th percentile": 0.47, "10th percentile": 0.34, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.027, "error plus": 0.026, "error minus": 0.026, "5th percentile": 0.001, "95th percentile": 0.051, "10th percentile": 0.005, "90th percentile": 0.045\}, "frac\_dyn": \{"median": 0.79, "error plus": 0.15, "error minus": 0.14, "5th percentile": 0.65, "95th percentile": 0.95, "10th percentile": 0.68, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.089, "5th percentile": 0.11, "95th percentile": 0.31, "10th percentile": 0.14, "90th percentile": 0.27\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXVII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXX\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{0.61}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{2.9}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}1.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.68}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.75}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.58}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.62}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.86}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.78}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.91}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.88}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.71}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.36}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.98}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{0.68}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.83}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.28}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.58}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.53}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{1.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{3.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.62}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{2.9}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.69}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.53}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.57}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.8}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{1.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{1.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}1.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.69}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.88}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.96}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.8}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.44}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.015, "error minus": 0.0092, "5th percentile": 0.0036, "95th percentile": 0.029, "10th percentile": 0.0048, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.15, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.3, "5th percentile": 0.56, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.08, "error plus": 0.094, "error minus": 0.058, "5th percentile": 0.023, "95th percentile": 0.18, "10th percentile": 0.03, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XXXV\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.025, "error minus": 0.015, "5th percentile": 0.0046, "95th percentile": 0.046, "10th percentile": 0.006, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.35, "error plus": 0.096, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.24, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.029, "error plus": 0.038, "error minus": 0.022, "5th percentile": 0.007, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.059\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.25, "5th percentile": 0.45, "95th percentile": 0.87, "10th percentile": 0.48, "90th percentile": 0.85\}, "frac\_hm": \{"median": 0.12, "error plus": 0.16, "error minus": 0.095, "5th percentile": 0.029, "95th percentile": 0.29, "10th percentile": 0.038, "90th percentile": 0.2\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XL\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.017, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.39, "error plus": 0.075, "error minus": 0.071, "5th percentile": 0.32, "95th percentile": 0.47, "10th percentile": 0.34, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.027, "error plus": 0.026, "error minus": 0.026, "5th percentile": 0.001, "95th percentile": 0.051, "10th percentile": 0.005, "90th percentile": 0.045\}, "frac\_dyn": \{"median": 0.79, "error plus": 0.15, "error minus": 0.14, "5th percentile": 0.65, "95th percentile": 0.95, "10th percentile": 0.68, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.089, "5th percentile": 0.11, "95th percentile": 0.31, "10th percentile": 0.14, "90th percentile": 0.27\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLV\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@L\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LIII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LVI\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LVII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LIX\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.013, "error plus": 0.015, "error minus": 0.0092, "5th percentile": 0.0036, "95th percentile": 0.029, "10th percentile": 0.0048, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.015}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.0092}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.0036}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.029}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.0048}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.024}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.43, "error plus": 0.078, "error minus": 0.15, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.078}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.32}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.48}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.017, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.043}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.86, "error plus": 0.16, "error minus": 0.3, "5th percentile": 0.56, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.56}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.64}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.97}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.08, "error plus": 0.094, "error minus": 0.058, "5th percentile": 0.023, "95th percentile": 0.18, "10th percentile": 0.03, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.094}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.058}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.18}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.03}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.15}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.02, "error plus": 0.025, "error minus": 0.015, "5th percentile": 0.0046, "95th percentile": 0.046, "10th percentile": 0.006, "90th percentile": 0.033\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.025}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.0046}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.046}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.006}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.033}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.35, "error plus": 0.096, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.24, "90th percentile": 0.43\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.096}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.44}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.43}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.029, "error plus": 0.038, "error minus": 0.022, "5th percentile": 0.007, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.059\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.029}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.038}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.007}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.071}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.059}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.7, "error plus": 0.19, "error minus": 0.25, "5th percentile": 0.45, "95th percentile": 0.87, "10th percentile": 0.48, "90th percentile": 0.85\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.25}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.45}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.48}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.85}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.12, "error plus": 0.16, "error minus": 0.095, "5th percentile": 0.029, "95th percentile": 0.29, "10th percentile": 0.038, "90th percentile": 0.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.095}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.29}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.038}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.2}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.032, "error plus": 0.017, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.032}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.017}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.014}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.05}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.043}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.39, "error plus": 0.075, "error minus": 0.071, "5th percentile": 0.32, "95th percentile": 0.47, "10th percentile": 0.34, "90th percentile": 0.45\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.075}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.071}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.34}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.45}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.027, "error plus": 0.026, "error minus": 0.026, "5th percentile": 0.001, "95th percentile": 0.051, "10th percentile": 0.005, "90th percentile": 0.045\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.027}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.026}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.026}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.001}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.051}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.005}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.045}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.79, "error plus": 0.15, "error minus": 0.14, "5th percentile": 0.65, "95th percentile": 0.95, "10th percentile": 0.68, "90th percentile": 0.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.79}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.95}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.68}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.9}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.2, "error plus": 0.11, "error minus": 0.089, "5th percentile": 0.11, "95th percentile": 0.31, "10th percentile": 0.14, "90th percentile": 0.27\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.27}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.071}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.047}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.034}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.036}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.042}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.1}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.31}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.48}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.035}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.044}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.0088}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.063}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.21}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.63}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.95}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.75}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.65}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{6.7}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{19}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{52}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{5.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{5.7}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{6.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{5.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{6.3}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{30}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{4.4}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{7.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{34}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{24}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{33}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{80}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{68}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{91}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{70}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{89}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{6.7}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{15}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{52}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}, "a1\_90percentile": \{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}, "peakCosTilt1": \{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}, "peakCosTilt2": \{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}, "log10gammaFrac1": \{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}, "log10gammaFrac2": \{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}, "negFrac1": \{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}, "a\_90percentile": \{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}, "peakCosTilt": \{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}, "negFrac": \{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.014, "error plus": 0.016, "error minus": 0.011, "5th percentile": 0.003, "95th percentile": 0.03, "10th percentile": 0.0043, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.16, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.053, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.32, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.62, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.086, "error plus": 0.099, "error minus": 0.067, "5th percentile": 0.019, "95th percentile": 0.19, "10th percentile": 0.027, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.015, "error minus": 0.015, "5th percentile": 0.0044, "95th percentile": 0.036, "10th percentile": 0.006, "90th percentile": 0.032\}, "FracBelow0": \{"median": 0.35, "error plus": 0.097, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.25, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.005, "95th percentile": 0.067, "10th percentile": 0.017, "90th percentile": 0.055\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.24, "5th percentile": 0.46, "95th percentile": 0.88, "10th percentile": 0.5, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.096, "error minus": 0.096, "5th percentile": 0.028, "95th percentile": 0.22, "10th percentile": 0.037, "90th percentile": 0.2\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.018, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.4, "error plus": 0.072, "error minus": 0.068, "5th percentile": 0.33, "95th percentile": 0.47, "10th percentile": 0.35, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.026, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.005, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.14, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.95, "10th percentile": 0.7, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.09, "5th percentile": 0.11, "95th percentile": 0.32, "10th percentile": 0.13, "90th percentile": 0.27\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}, "a1\_90percentile": \{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}, "peakCosTilt1": \{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}, "peakCosTilt2": \{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}, "log10gammaFrac1": \{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}, "log10gammaFrac2": \{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}, "negFrac1": \{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}, "a\_90percentile": \{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}, "lamb": \{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}, "peakCosTilt": \{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}, "negFrac": \{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.014, "error plus": 0.016, "error minus": 0.011, "5th percentile": 0.003, "95th percentile": 0.03, "10th percentile": 0.0043, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.16, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.053, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.32, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.62, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.086, "error plus": 0.099, "error minus": 0.067, "5th percentile": 0.019, "95th percentile": 0.19, "10th percentile": 0.027, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.015, "error minus": 0.015, "5th percentile": 0.0044, "95th percentile": 0.036, "10th percentile": 0.006, "90th percentile": 0.032\}, "FracBelow0": \{"median": 0.35, "error plus": 0.097, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.25, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.005, "95th percentile": 0.067, "10th percentile": 0.017, "90th percentile": 0.055\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.24, "5th percentile": 0.46, "95th percentile": 0.88, "10th percentile": 0.5, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.096, "error minus": 0.096, "5th percentile": 0.028, "95th percentile": 0.22, "10th percentile": 0.037, "90th percentile": 0.2\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.018, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.4, "error plus": 0.072, "error minus": 0.068, "5th percentile": 0.33, "95th percentile": 0.47, "10th percentile": 0.35, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.026, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.005, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.14, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.95, "10th percentile": 0.7, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.09, "5th percentile": 0.11, "95th percentile": 0.32, "10th percentile": 0.13, "90th percentile": 0.27\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXVIII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXXI\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.28, "95th percentile": 3.4, "10th percentile": 0.61, "90th percentile": 2.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{0.61}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{2.9}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.68\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}1.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.68}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.75, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.58, "95th percentile": 0.89, "10th percentile": 0.62, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.75}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.58}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.62}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.86}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.78, "error plus": 0.14, "error minus": 0.17, "5th percentile": 0.61, "95th percentile": 0.91, "10th percentile": 0.64, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.78}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.91}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.64}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.88}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.19, "error plus": 0.73, "error minus": 0.73, "5th percentile": {-}0.54, "95th percentile": 0.89, "10th percentile": {-}0.38, "90th percentile": 0.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.73}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.71}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.4, "error plus": 0.64, "error minus": 1.1, "5th percentile": {-}0.66, "95th percentile": 1.0, "10th percentile": {-}0.36, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.36}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.98}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.13, "error plus": 0.71, "error minus": 0.7, "5th percentile": {-}0.57, "95th percentile": 0.84, "10th percentile": {-}0.41, "90th percentile": 0.68\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.71}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.57}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{0.68}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.28, "error plus": 0.72, "error minus": 0.74, "5th percentile": {-}0.46, "95th percentile": 0.99, "10th percentile": {-}0.29, "90th percentile": 0.83\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.72}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.83}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.43, "error plus": 0.19, "error minus": 0.18, "5th percentile": 0.25, "95th percentile": 0.62, "10th percentile": 0.28, "90th percentile": 0.58\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.28}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.58}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.37, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.21, "95th percentile": 0.57, "10th percentile": 0.24, "90th percentile": 0.53\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.53}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 1.7, "error plus": 1.6, "error minus": 1.4, "5th percentile": 0.32, "95th percentile": 3.3, "10th percentile": 0.62, "90th percentile": 2.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{1.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{3.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.62}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{2.9}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.69, "error plus": 0.15, "error minus": 0.16, "5th percentile": 0.53, "95th percentile": 0.84, "10th percentile": 0.57, "90th percentile": 0.8\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.69}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.53}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.57}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.8}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": {-}0.54, "error plus": 1.5, "error minus": 1.6, "5th percentile": {-}2.1, "95th percentile": 1.0, "10th percentile": {-}1.8, "90th percentile": 0.69\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{1.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{1.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}1.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.69}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.37, "error plus": 0.64, "error minus": 0.5, "5th percentile": {-}0.14, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{{-}0.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.88}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.31, "error plus": 0.66, "error minus": 0.66, "5th percentile": {-}0.35, "95th percentile": 0.96, "10th percentile": {-}0.19, "90th percentile": 0.8\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.96}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.8}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.34, "error plus": 0.12, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.47, "10th percentile": 0.25, "90th percentile": 0.44\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.44}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.014, "error plus": 0.016, "error minus": 0.011, "5th percentile": 0.003, "95th percentile": 0.03, "10th percentile": 0.0043, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.16, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.053, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.32, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.62, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.086, "error plus": 0.099, "error minus": 0.067, "5th percentile": 0.019, "95th percentile": 0.19, "10th percentile": 0.027, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XXXVI\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.02, "error plus": 0.015, "error minus": 0.015, "5th percentile": 0.0044, "95th percentile": 0.036, "10th percentile": 0.006, "90th percentile": 0.032\}, "FracBelow0": \{"median": 0.35, "error plus": 0.097, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.25, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.005, "95th percentile": 0.067, "10th percentile": 0.017, "90th percentile": 0.055\}, "frac\_dyn": \{"median": 0.7, "error plus": 0.19, "error minus": 0.24, "5th percentile": 0.46, "95th percentile": 0.88, "10th percentile": 0.5, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.096, "error minus": 0.096, "5th percentile": 0.028, "95th percentile": 0.22, "10th percentile": 0.037, "90th percentile": 0.2\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XLI\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.032, "error plus": 0.018, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}, "FracBelow0": \{"median": 0.4, "error plus": 0.072, "error minus": 0.068, "5th percentile": 0.33, "95th percentile": 0.47, "10th percentile": 0.35, "90th percentile": 0.45\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.026, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.005, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.14, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.95, "10th percentile": 0.7, "90th percentile": 0.9\}, "frac\_hm": \{"median": 0.2, "error plus": 0.11, "error minus": 0.09, "5th percentile": 0.11, "95th percentile": 0.32, "10th percentile": 0.13, "90th percentile": 0.27\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLVI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}, "FracBelow0": \{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@LI\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVIII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVIII@out\macros@LVI\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LVII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LIX\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}, "m\_99percentile": \{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LXII\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXXI@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXXI@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXXI@out\macros@LXV\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.014, "error plus": 0.016, "error minus": 0.011, "5th percentile": 0.003, "95th percentile": 0.03, "10th percentile": 0.0043, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.014}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.011}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.0043}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.026}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.43, "error plus": 0.076, "error minus": 0.16, "5th percentile": 0.28, "95th percentile": 0.49, "10th percentile": 0.31, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.076}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.31}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.48}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.053, "10th percentile": {-}0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.053}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.043}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.87, "error plus": 0.15, "error minus": 0.32, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.62, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.87}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.55}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.62}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.97}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.086, "error plus": 0.099, "error minus": 0.067, "5th percentile": 0.019, "95th percentile": 0.19, "10th percentile": 0.027, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.086}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.099}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.067}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.019}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.027}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.16}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.02, "error plus": 0.015, "error minus": 0.015, "5th percentile": 0.0044, "95th percentile": 0.036, "10th percentile": 0.006, "90th percentile": 0.032\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.015}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.0044}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.036}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.006}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.032}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.35, "error plus": 0.097, "error minus": 0.12, "5th percentile": 0.23, "95th percentile": 0.44, "10th percentile": 0.25, "90th percentile": 0.43\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.097}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.43}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.005, "95th percentile": 0.067, "10th percentile": 0.017, "90th percentile": 0.055\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.026}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.067}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.055}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.7, "error plus": 0.19, "error minus": 0.24, "5th percentile": 0.46, "95th percentile": 0.88, "10th percentile": 0.5, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.24}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.88}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.5}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.86}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.12, "error plus": 0.096, "error minus": 0.096, "5th percentile": 0.028, "95th percentile": 0.22, "10th percentile": 0.037, "90th percentile": 0.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.096}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.096}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.028}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.22}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.2}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.032, "error plus": 0.018, "error minus": 0.014, "5th percentile": 0.018, "95th percentile": 0.05, "10th percentile": 0.022, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.032}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.018}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.014}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.05}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.043}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.4, "error plus": 0.072, "error minus": 0.068, "5th percentile": 0.33, "95th percentile": 0.47, "10th percentile": 0.35, "90th percentile": 0.45\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.072}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.068}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.45}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.023, "error plus": 0.026, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.005, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.023}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.026}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.001}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.005}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.041}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.8, "error plus": 0.14, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.95, "10th percentile": 0.7, "90th percentile": 0.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.95}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.9}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.2, "error plus": 0.11, "error minus": 0.09, "5th percentile": 0.11, "95th percentile": 0.32, "10th percentile": 0.13, "90th percentile": 0.27\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.09}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.27}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.071, "error plus": 0.047, "error minus": 0.034, "5th percentile": 0.036, "95th percentile": 0.12, "10th percentile": 0.042, "90th percentile": 0.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.071}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.047}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.034}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.036}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.042}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.1}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.4, "error plus": 0.1, "error minus": 0.1, "5th percentile": 0.29, "95th percentile": 0.5, "10th percentile": 0.31, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.31}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.48}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.041, "error plus": 0.035, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.073, "10th percentile": 0.0088, "90th percentile": 0.063\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.035}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.044}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.0088}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.063}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.8, "error plus": 0.2, "error minus": 0.21, "5th percentile": 0.59, "95th percentile": 1.0, "10th percentile": 0.63, "90th percentile": 0.95\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.21}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.63}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.95}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.44, "error plus": 0.3, "error minus": 0.22, "5th percentile": 0.23, "95th percentile": 0.75, "10th percentile": 0.26, "90th percentile": 0.65\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.75}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.65}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.0039}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.39}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.082}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.78}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.024}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{6.7}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{19}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{52}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 5.9, "error plus": 0.51, "error minus": 0.19, "5th percentile": 5.7, "95th percentile": 6.5, "10th percentile": 5.7, "90th percentile": 6.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{5.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{5.7}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{6.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{5.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{6.3}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 30, "error plus": 4.4, "error minus": 7.9, "5th percentile": 23, "95th percentile": 34, "10th percentile": 24, "90th percentile": 33\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{30}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{4.4}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{7.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{34}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{24}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{33}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 80, "error plus": 11, "error minus": 13, "5th percentile": 68, "95th percentile": 91, "10th percentile": 70, "90th percentile": 89\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{80}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{68}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{91}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{70}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{89}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.7}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{15}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\makeatother

### 2022-09-28 src/scripts/create_macros.py

@@ -6,7 +6,23 @@ import paths
 import numpy as np
 import deepdish as dd
 from scipy.integrate import cumtrapz
-from utils import load_iid_mag_ppd, load_iid_tilt_ppd, load_ind_mag_ppd, load_ind_tilt_ppd, save_param_cred_intervals, load_o3b_paper_run_masspdf, load_mass_ppd, load_iid_posterior, load_ind_posterior, load_o3b_posterior
+from utils import load_iid_mag_ppd, load_iid_tilt_ppd, load_ind_mag_ppd, load_ind_tilt_ppd, load_o3b_paper_run_masspdf, load_mass_ppd, load_iid_posterior, load_ind_posterior, load_o3b_posterior
+
+def round_sig(f, sig=2):
+    max10exp = np.floor(np.log10(abs(f))) + 1
+    if max10exp < float(sig):
+        return float(('%.' + str(sig) + 'g') % f)
+    else:
+        return int(float(('%.' + str(sig) + 'g') % f))
+
+def save_param_cred_intervals(param_data):
+    return  {'median': round_sig(np.median(param_data)), 
+             'error plus':round_sig(np.percentile(param_data, 95)-np.mean(param_data)), 
+             'error minus': round_sig(np.median(param_data)-np.percentile(param_data, 5)),
+             '5th percentile': round_sig(np.percentile(param_data, 5)), 
+             '95th percentile': round_sig(np.percentile(param_data, 95)), 
+             '10th percentile': round_sig(np.percentile(param_data, 10)),
+             '90th percentile': round_sig(np.percentile(param_data, 90))}
 
 def get_percentile(pdfs, xs, perc):
     x = []

### 2022-09-28 src/scripts/utils.py

@@ -5,24 +5,6 @@ from bilby.core.result import read_in_result
 import deepdish as dd
 
 
-def round_sig(f, sig=3):
-    max10exp = np.floor(np.log10(abs(f))) + 1
-    if max10exp < float(sig):
-        return float(('%.' + str(sig) + 'g') % f)
-    else:
-        return int(float(('%.' + str(sig) + 'g') % f))
-
-
-def save_param_cred_intervals(param_data):
-    return  {'median': round_sig(np.median(param_data)), 
-             'error plus':round_sig(np.percentile(param_data, 95)-np.mean(param_data)), 
-             'error minus': round_sig(np.median(param_data)-np.percentile(param_data, 5)),
-             '5th percentile': round_sig(np.percentile(param_data, 5)), 
-             '95th percentile': round_sig(np.percentile(param_data, 95)), 
-             '10th percentile': round_sig(np.percentile(param_data, 10)),
-             '90th percentile': round_sig(np.percentile(param_data, 90))}
-
-
 def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None, tracecolor='k'):
 
     mean = np.mean(ar, axis=0)

### 2022-09-28 src/tex/conclusion.tex
fix typos in conclusion

@@
 
-The collective distibution of BBH source properties provides a useful probe of the complex and uncertain astrophysics that governs their 
-formation and evolution to eventually merge \citep{Zevin_2017}. Our analysis with the newly constructed \textsc{MSpline} models corroborates important 
+The collective distribution of BBH source properties provides a useful probe of the complex and uncertain astrophysics that governs their 
+formation and evolution to eventually merge \citep{Zevin_2017}. Our analysis with the newly constructed M-Spline models corroborates important 
 conclusions of recent work and provides a robust data-driven framework for future population studies.
@@
 $15-20\msun$ \bruce{cite}. Globular cluster formation is expected to produce more top-heavy mass distributions than isolated and recent studies have shown suppressed BBH merger rates 
-at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \bruce{cite}. BBHs that form near active galactive nuclei (AGN) can preferentially produce higher 
+at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \bruce{cite}. BBHs that form near active galactic nuclei (AGN) can preferentially produce higher 
 mass black holes \bruce{cite}. We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts 
 due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017}.
-The original motivation for the peak in the \textsc{PLPeak} model \citep{Talbot_2018} was to represent a possible ``pileup'' of
+The original motivation for the peak in the \textsc{PowerlawPeak} model \citep{Talbot_2018} was to represent a possible ``pileup'' of
 masses just before such the truncation, since massive stars just light enough to avoid PISN will shed large amounts of mass in a series of ``pulses'' before collapsing to BHs in a process called 
@@
 point towards a higher prevalence of dynamical processes that can produce black holes in mass ranges stellar collapse cannot, such as hierarchical mergers of BHs \citep{Fishbach_2017,Doctor_2020,Kimball_genealogy,kimball2020evidence,doctor2021black,Fishbach_2022},
-very low metallictiy population III stars \citep{Belczynski_2020,Farrell_2020}, new beyond the standard model physics\cite{Croon_newphysics,Sakstein_2020}, or black hole accretion of BHs in gaseous environments such as AGNs \citep{Secunda_2020,McKernan_2020,cruzosorio2021gw190521}.
+very low metallicity population III stars \citep{Belczynski_2020,Farrell_2020}, new beyond the standard model physics\citep{Croon_newphysics,Sakstein_2020}, or black hole accretion of BHs in gaseous environments such as AGNs \citep{Secunda_2020,McKernan_2020,cruzosorio2021gw190521}.
 
 % spin dist
-Section \ref{sec:spin_dist} focused on inferences of the spin distributions of black holes, observing evidence of spin mis-alignment, spin anti-alignment, and suppressed support 
+Section \ref{sec:spin_dist} focused on inferences of the spin distributions of black holes, observing evidence of spin misalignment, spin anti-alignment, and suppressed support 
 for exactly aligned systems. These point towards a significant contribution of the population being formed through dynamical formation processes, agreeing with 
@@
 aligned spins due to tidal interactions, but observational evidence suggests that tides may not be able to re-align spins in all systems as some 
-isolated population models assume. Additionally because of uncertain knowledge of supernovae kicks, isolated formation can produce systems with negative but small effective spins. 
-We report an effective spin distribution that is not symmetric about zero, disfavoring a scenarior in wihch all BBHs are formed dynamically. Following the rules in \citet{Fishbach_2022}, 
-we place conservative upper bounds on the fraction of hierarhical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$ with 
-the \textsc{MSpline} $\chi_\mathrm{eff}$ model constraining $f_\mathrm{HM} < $\result{$\macros[ChiEffective][chieff][frac_hm][10th percentile]$} 
+isolated population models assume. Additionally, because of uncertain knowledge of supernovae kicks, isolated formation can produce systems with negative but small effective spins. 
+We report an effective spin distribution that is not symmetric about zero, disfavoring a scenario in which all BBHs are formed dynamically. Following the rules in \citet{Fishbach_2022}, 
+we place conservative upper bounds on the fraction of hierarchical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$ with 
+the M-Spline $\chi_\mathrm{eff}$ model constraining $f_\mathrm{HM} < $\result{$\macros[ChiEffective][chieff][frac_hm][10th percentile]$} 
 and $f_\mathrm{dyn} < $\result{$\macros[ChiEffective][chieff][frac_dyn][10th percentile]$} at 90\% credibility.
@@
 We presented a case study exploring how basis splines make for an especially powerful and efficient model-agnostic probe of the binary black hole population observed 
-with gravitational waves. With the coming influx of new data with the LVK's next observing run, and the wide range of questions in astro/physics that a better 
+with gravitational waves. With the coming influx of new data with the LVK's next observing run, and the wide range of questions in astrophysics and cosmology that a better 
 understanding of the black hole population will uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make

### 2022-09-28 src/tex/appendicies.tex
fix appendix typos -- add inj citation

@@
 
-Spline functions have been shown to be sensitivite to the chosen number of knots, and their locations or spacing \citep{deBoor78}. 
-Adding more knots knots increases the a-priori variance in the spline function, while the space between knots can limit the 
+Spline functions have been shown to be sensitive to the chosen number of knots, and their locations or spacing \citep{deBoor78}. 
+Adding more knots increases the a priori variance in the spline function, while the space between knots can limit the 
 resolution of features in the data the spline is capable of resolving. To ensure your spline based model is flexible enough 
-one would want to add as many knots as densely as possible, but this comes with the inherit larger variance as mentioned above. 
-To overcome this we resort to the frequentist penalized spline (P-Spline) in which one applies a penalty or regularization term 
-to the likelihood based on the difference of adjacent knot coeficients \citep{eilers2021practical}. The linear combination of spline basis components 
-or the resulting spline function is flat when the basis coeficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as 
-the differences between adjacent knot coeficients get larger, one gets a smoothing of the spline function inferences \citep{eilers2021practical}. 
-Since we are using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog. 
-The difference penalty is equivalent to applying a stochastic differnece prior among the knots, as described in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}. 
-This is also sometimes referred to as a Gaussian random walk prior, since each coeficient is normally distributed about its neighboring coeficients. 
+one would want to add as many knots as densely as possible, but this comes with unwanted side effect of larger variance as mentioned above. 
+To overcome this we resort to the frequentest penalized spline (P-Spline) in which one applies a penalty or regularization term 
+to the likelihood based on the difference of adjacent knot coefficients \citep{eilers2021practical}. The linear combination of spline basis components 
+or the resulting spline function is flat when the basis coefficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as 
+the differences between adjacent knot coefficients get larger, one gets a smoothing of the spline function inferences \citep{eilers2021practical}. 
+Since we are using hierarchical Bayesian inference as our statistical framework, we formulate this penalized likelihood with its Bayesian analog. 
+The difference penalty is equivalent to applying a stochastic difference prior among the knots, as described in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}. 
+This is also sometimes referred to as a Gaussian random walk prior, since each coefficient is normally distributed about its neighboring coefficients. 
 For a spline basis with $n$ degree's of freedom, and a difference penalty of order of $r$ (see \citet{eilers2021practical}), the smoothing prior is defined as:
@@
 \noindent Above $\bm{D}_r$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $\Gamma(a,b)$ the Gamma distribution with shape parameters, $a$ and $b$. 
-This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. By adding in a very large number 
-of knots such that your domain is densly populated with basis coeficients, this allows the freedom for the model to find the smoothing 
+This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. The $\tau_\lambda$ controls the ``strength'' of 
+smoothing, or the inverse variance of the Gaussian priors on knot differences. By adding in a very large number 
+of knots such that your domain is densely populated with basis coefficients, this allows the freedom for the model to find the smoothing 
 scale that the data prefers. One downside of this prior specification as noted in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}, is a slight dependence on choice 
-of the b hyper-parameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \citet{Jullion2007RobustSO}
-to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyper-parameters. 
+of the b hyperparameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \citet{Jullion2007RobustSO}
+to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyperparameters. 
 We now replace the prior on $\tau_\lambda$ with:
@@
 
-This prior is imparting a natural attraction of the coeficients closer to each other in order to smooth the spline function, so one 
-must ensure that the spline function is in fact flat given all equal coeficients. Since one needs to define n+k knots to construct an order-k basis with 
-n degrees of freedom, people often will place knots on top of each other at hard parameter boundaries \cite{deBoor78,monotone_regression_splines}. 
-This may seemed motivated, especially if there is no reality in the parameter beyond the boundary, but this violates the above condition. 
-We follow the distinction from \citet{eilers2021practical} that the difference penalty or smooothing prior is only valid with ``proper'' spline bases. 
+Since the prior is imparting a natural attraction of the coefficients closer to each other in order to smooth the spline function, so one 
+must ensure that the spline function is in fact flat given all equal coefficients. Since one needs to define n+k knots to construct an order-k basis with 
+n degrees of freedom, sometimes studies place knots on top of each other at hard parameter boundaries \cite{deBoor78,monotone_regression_splines}. 
+This may seem motivated, especially when is no reality in the parameter beyond the boundary, but this violates the above condition. 
+We follow the distinction from \citet{eilers2021practical} that such a smoothing prior is only valid with ``proper'' spline bases. 
 A proper basis is where all n+k knots are evenly spaced, see Figure \ref{fig:spline_basis}, as opposed to stacking them at the bounds.
@@
 in the universe and how this can change with their masses, spins, etc. Often times it is useful to formulate the question in terms of the 
-merger rates which is the number of mergers per $Gpc^{3}$ co-moving volume per year. For a set of hyper-parameters, $\Lambda$, $\lambda$, and local ($z=0$) 
+merger rates which is the number of mergers per $Gpc^{3}$ co-moving volume per year. For a set of hyperparameters, $\Lambda$, $\lambda$, and local ($z=0$) 
 merger rate density, $\mathcal{R}_0$, we write the overall number density of BBH mergers in the universe as:
@@
 Where up above, we denote the co-moving volume element as $dV_c$ \citep{hogg_cosmo}, and $T_\mathrm{obs}$ as the observing time period that produced the 
-catalog with the related factor of $1+z$ converting this detector-frame time to source-frame. We assume a LambdaCDM cosmology using 
+catalog with the related factor of $1+z$ converting this detector-frame time to source-frame. We assume a Lambda CDM cosmology using 
 the cosmological parameters from \citet{Planck2015}. We model the merger rate evolving with redshift following a power law distribution: 
@@
 and out to some maximum redshift, $z_\mathrm{max}$, we get the total number of CBCs in the universe out to that redshift. We follow previous notations, \
-letting $\{d_i\}$ represent the set of data from $N_\mathrm{obs}$ CBCs observed with gravitational waves. The merger rate is then described as an inhomogenous 
-Poisson process and after imposing the usual log-uniform prior on the merger rate, we marginalize out merger rate and arrive at the posterior
-distribution of our hyper-parameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.
+letting $\{d_i\}$ represent the set of data from $N_\mathrm{obs}$ CBCs observed with gravitational waves. The merger rate is then described as an inhomogeneous 
+Poisson process and after imposing the usual log-uniform prior on the merger rate, we marginalize over the local merger rate, $\mathcal{R}_0$, and arrive at the posterior
+distribution of our hyperparameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.
 
@@
 \noindent
-where, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples. Above, $j$
+Where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples. Above, $j$
 indexes the $K_i$ posterior samples from each event and $\pi(\theta, z)$ is the default prior used by parameter estimations that 
@@
 component spins and Euclidean volume or the posterior samples were re-weighted to such a prior before using them in our analysis. 
-The corresponding prior evaluated in the parameters we hierarchicaly model, i.e. source frame primary mass, mass ratio, component spins and redshift is:
+The corresponding prior evaluated in the parameters we hierarchically model, i.e. source frame primary mass, mass ratio, component spins and redshift is:
 
@@
 
-\noindent where $D_L$ is the luminosity distance. To carefully incorporate selection effects to our model we need to quantify the detection efficiency,
+\noindent Above, $D_L$ is the luminosity distance. To carefully incorporate selection effects to our model we need to quantify the detection efficiency,
 $\xi(\Lambda, \lambda)$, of the search pipelines that were used to create GWTC-3, at a given population distribution described by $\Lambda$ and $\lambda$.
@@
 To estimate this integral we use a software injection campaign where gravitational waveforms from a large population of simulated sources. 
-These simulated waevforms are put into real detector data, and then this data is evaluated with the same search pipelines that were used to 
+These simulated waveforms are put into real detector data, and then this data is evaluated with the same search pipelines that were used to 
 produce the catalog we are analyzing. With these search results in hand, we use importance sampling and evaluate the integral 
-with the monte carlo sum estimate $\mu$, and its corresponding variance and effective number of samples:
+with the Monte Carlo sum estimate $\mu$, and its corresponding variance and effective number of samples:
 
@@
 \noindent
-Where the sums indexes only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, 
-and $p_\mathrm{inj}(\theta, z)$ is the reference distribution from which the injections were drawn. Additionally, we follow the procedure 
+Where the sum is only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, 
+and $p_\mathrm{inj}(\theta, z)$ is the reference distribution from which the injections were drawn. We use the LVK released injection sets that describe the 
+detector sensitivities over the first, second and third observing runs \citep{o1o2o3_injection_sets}. Additionally, we follow the procedure 
 outlined in \citet{Farr_2019} to marginalize the uncertainty in our estimate of $\xi(\Lambda, \lambda)$, in which we verify that $N_\mathrm{eff}$ is 
 sufficiently high after re-weighting the injections to a given population (i.e. $N_\mathrm{eff} > 4N_\mathrm{obs}$). 
-The total hyper-posterior marginalized over the merger rate and the uncertainty in the monte carlo integral calculating $\xi(\Lambda, \lambda)$ \citep{Farr_2019}, as:
+The total hyper-posterior marginalized over the merger rate and the uncertainty in the Monte Carlo integral calculating $\xi(\Lambda, \lambda)$ \citep{Farr_2019}, as:
 
@@
 We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
-their respective hyper-parameters and prior distributions in the next section. To calculate draw 
-samples of the hyper parameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
-NUTS hamiltonian monte carlo sampler in \textsc{NumPyro} and \textsc{Jax} to calculate likelihoods \citep{jax,pyro,numpyro}.
+their respective hyperparameters and prior distributions in the next section. To calculate draw 
+samples of the hyperparameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
+NUTS Hamiltonian Monte Carlo sampler in \textsc{NumPyro} and \textsc{Jax} to calculate likelihoods \citep{jax,pyro,numpyro}.
 
@@
 
-\bruce{Need to fill this section in and put tables with specific hyper-parameter/prior settings made}
+\bruce{Need to fill this section in and put tables with specific hyperparameter/prior settings made}
 

### 2022-09-28 src/tex/intro.tex
add landry/read NS citation

@@
 constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, 
-and constrain the neutron star equation of state \citep{Golomb_EOS}. Through a better understanding of the mass, spin, and redshift distributions of 
+and to constrain physics of neutron stars \citep{Golomb_EOS,LandryRead_NS_Masses2021}. Through a better understanding of the mass, spin, and redshift distributions of 
 compact binaries that will come with the increased catalog size, one can probe a wide range of different physical phenomena with even greater fidelity.
@@
 we present in this manuscript, both to help alleviate the current disputes in the literature and because there has been little work on flexible model development for the 
-spin distribution of BBHs beyond assuming aligned spins thus far \citep{Tiwari_2021_a,Tiwari_2021_b}.
+spin distribution of BBHs beyond the aligned spin dimension thus far \citep{Tiwari_2021_a,Tiwari_2021_b}.
 

### 2022-09-29 src/tex/appendicies.tex
start table work on ppcs/prior dists

@@
 
+\begin{table*}[ht!]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    \textbf{Model} & \textbf{Parameter} & \textbf{Description} & \textbf{Prior} \\ \hline \hline
+    \multicolumn{4}{|c|}{\textbf{Primary Mass Model Parameters}} \\ \hline
+    \textsc{M-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+     & $\tau_\lambda$ & Smoothing Prior Scale & $\sum_i^m p_i \Gamma(1, b_i)$ \\ \cline{2-4}
+     & $\bm{p}$ & Hyper-Parameter weights on smoothing scale mixture prior & $\sim \mathcal{D}(m)$ \\ \cline{2-4}
+     & $b_m$ & array of different concentration parameters for $\Gamma$ distribution & equal in $[10^{-9},10^{-1}]$ \\ \cline{2-4} 
+     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 50 \\ \cline{2-4} 
+     & $m$ & number of mixture components for prior on $\tau_\lambda$ & 24  \\ \hline \hline
+    \multicolumn{4}{|c|}{\textbf{Mass Ratio Model Parameters}} \\ \hline
+    \textsc{PowerLaw Mass Ratio} & $\beta$ & slope of the mass ratio power law & $\sim \mathcal{N}(0,2)$ \\ \cline{2-4} 
+    & $m_\mathrm{min}$ & minimum BH mass & 3\msun  \\ \hline \hline    
+    \multicolumn{4}{|c|}{\textbf{Redshift Evolution Model Parameters}} \\ \hline
+    \textsc{PowerLaw Redshift} & $\lambda$ & slope of redshift evolution power law $(1+z)^\lambda$ &  $\sim \mathcal{N}(0,2)$ \\ \hline \hline
+    \multicolumn{4}{|c|}{\textbf{Spin Distribution Model Parameters}} \\ \hline
+    \textsc{M-Spline Magnitude} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
+    & $\tau_\lambda$ & Smoothing Prior Scale & $\sum_i^m p_i \Gamma(1, 10^{-3})$ \\ \cline{2-4}
+    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 16 \\ \hline
+    \textsc{M-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
+    & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \Gamma(1, 10^{-3})$ \\ \cline{2-4}
+    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 16 \\ \hline
+    \textsc{M-Spline Effective} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
+    & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \Gamma(1, 10^{-3})$ \\ \cline{2-4}
+    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 24 \\ \hline
+    \end{tabular}
+\end{table*}
+
 \bruce{Need to fill this section in and put tables with specific hyperparameter/prior settings made}

### 2022-09-29 src/scripts/analysis_scripts/common.py

@@ -23,6 +23,7 @@ def load_base_parser():
     parser.add_argument('--samples', type=int, default=2000)
     parser.add_argument('--warmup', type=int, default=250)
     parser.add_argument('--dirichlet', action='store_true', default=False)
+    parser.add_argument('--sample-prior', action='store_true', default=False)
     parser.add_argument('--chieff-knots', type=int, default=24)
     parser.add_argument('--chip-knots', type=int, default=12)
     return parser
@@ -40,16 +41,14 @@ def setup_mass_MSpline_model(injdata, pedata, pmap, nknots, mmax=100.0, k=4):
     knots = 10**(logknots)
     model = MSplinePrimaryPowerlawRatio(nknots, pedata[pmap['mass_1']],injdata[pmap['mass_1']],
                                        knots=knots)
-    return {'model': model, 'pe': {'mass_1': pedata[pmap['mass_1']], 'mass_ratio': pedata[pmap['mass_ratio']]}, 
-            'inj': {'mass_1': injdata[pmap['mass_1']], 'mass_ratio': injdata[pmap['mass_ratio']]}}, mmin
-    return model
+    return model, mmin
 
 
 def setup_redshift_model(injdata, pedata, pmap):
     z_pe = pedata[pmap['redshift']]
     z_inj = injdata[pmap['redshift']]
     model = PowerlawRedshiftModel(z_pe, z_inj)
-    return {'pe': z_pe, 'inj': z_inj, 'model': model}
+    return model
 
 
 def calculate_penalty(coefs, inv_var, Lambda=None, degree=1):

### 2022-09-29 src/scripts/analysis_scripts/run_mspline_chieff.py

@@ -30,7 +30,7 @@ def setup_effspin_MSpline_model(injdata, pedata, pmap, nknots, k=4):
     dx = interior_knots[1] - interior_knots[0]
     knots = np.concatenate([xmin-dx*np.arange(1,k)[::-1], interior_knots, xmax+dx*np.arange(1,k)])
     model = MSplineChiEffective(nknots, pedata[pmap['chi_eff']], injdata[pmap['chi_eff']], knots=knots)#HARDCODED_KNOTS)
-    return {'model': model}
+    return model
 
 
 def setup(args):
@@ -48,37 +48,29 @@ def setup(args):
     total_inj = injections["total_generated"]
     obs_time = injections["analysis_time"]
     
-    mass_dict, min_m1_interp = setup_mass_MSpline_model(injdata, pedata, param_map, args.mass_knots, mmax=args.mmax)
-    z_dict = setup_redshift_model(injdata, pedata, param_map)
+    mass_model, min_m1_interp = setup_mass_MSpline_model(injdata, pedata, param_map, args.mass_knots, mmax=args.mmax)
+    z_model = setup_redshift_model(injdata, pedata, param_map)
+    spin_model = setup_effspin_MSpline_model(injdata, pedata, param_map, args.chieff_knots)
     
-    prior_dict = {'pe': pedata[param_map['prior']], 'inj': injdata[param_map['prior']]}
-    spin_dict = setup_effspin_MSpline_model(injdata, pedata, param_map, args.chieff_knots)    
-    print(f"{len(z_dict['inj'])} found injections out of {total_inj} total")
-    print(f"Observed {nObs} events, each with {z_dict['pe'].shape[1]} samples, over an observing time of {obs_time} yrs")    
-    return mass_dict, spin_dict, z_dict, prior_dict, total_inj, nObs, obs_time, min_m1_interp
+    inj_dict = {k: injdata[param_map[k]] for k in param_names}
+    pe_dict = {k: pedata[param_map[k]] for k in param_names}
+     
+    print(f"{len(inj_dict['redshift'])} found injections out of {total_inj} total")
[…]

### 2022-09-29 src/scripts/analysis_scripts/run_mspline_iid_componentspins.py

@@ -34,7 +34,7 @@ def setup_spin_MSpline_model(injdata, pedata, pmap, nknots, k=4):
                                         injdata[pmap['a_1']], injdata[pmap['a_2']], knots=magknots)
     tiltmodel = MSplineIIDSpinTilts(nknots, pedata[pmap['cos_tilt_1']], pedata[pmap['cos_tilt_2']], 
                                     injdata[pmap['cos_tilt_1']], injdata[pmap['cos_tilt_2']], knots=tiltknots)
-    return {'models': {'mag': magmodel, 'tilt': tiltmodel}}
+    return {'mag': magmodel, 'tilt': tiltmodel}
 
 
 def setup(args):
@@ -47,77 +47,83 @@ def setup(args):
     nObs = pedata.shape[1]
     total_inj = injections["total_generated"]
     obs_time = injections["analysis_time"]
-    mass_dict, min_m1_interp = setup_mass_MSpline_model(injdata, pedata, param_map, args.mass_knots, mmax=args.mmax)    
-    z_dict = setup_redshift_model(injdata, pedata, param_map)
-    prior_dict = {'pe': pedata[param_map['prior']], 'inj': injdata[param_map['prior']]}
-    spin_dict = setup_spin_MSpline_model(injdata, pedata, param_map, args.spin_knots)
-    print(f"{len(z_dict['inj'])} found injections out of {total_inj} total")
-    print(f"Observed {nObs} events, each with {z_dict['pe'].shape[1]} samples, over an observing time of {obs_time} yrs")    
-    return mass_dict, spin_dict, z_dict, prior_dict, total_inj, nObs, obs_time, min_m1_interp
+    
+    mass_model, min_m1_interp = setup_mass_MSpline_model(injdata, pedata, param_map, args.mass_knots, mmax=args.mmax)    
+    z_model = setup_redshift_model(injdata, pedata, param_map)
+    spin_models = setup_spin_MSpline_model(injdata, pedata, param_map, args.spin_knots)
+    inj_dict = {k: injdata[param_map[k]] for k in param_names}
+    pe_dict = {k: pedata[param_map[k]] for k in param_names}
+     
+    print(f"{len(inj_dict['redshift'])} found injections out of {total_inj} total")
[…]

### 2022-09-29 src/scripts/analysis_scripts/run_mspline_ind_componentspins.py

@@ -12,10 +12,8 @@ from gwheiro.data_collection import load_injections, load_posterior_samples
 from gwheiro.analysis_utils import heirarchical_likelihood
 import matplotlib.pyplot as plt
 import arviz as az
-import os
 from common import *
 az.style.use("arviz-darkgrid")
-#plt.rcParams['plot.max_subplots'] = 35
 
 
 def setup_parser():
@@ -36,7 +34,7 @@ def setup_spin_MSpline_model(injdata, pedata, pmap, nknots, k=4):
                                         injdata[pmap['a_1']], injdata[pmap['a_2']], knots1=magknots, knots2=magknots)
     tiltmodel = MSplineIndependentSpinTilts(nknots, nknots, pedata[pmap['cos_tilt_1']], pedata[pmap['cos_tilt_2']], 
                                     injdata[pmap['cos_tilt_1']], injdata[pmap['cos_tilt_2']], knots1=tiltknots, knots2=tiltknots)
-    return {'models': {'mag': magmodel, 'tilt': tiltmodel}}
+    return {'mag': magmodel, 'tilt': tiltmodel}
 
 
 def setup(args):
@@ -49,101 +47,96 @@ def setup(args):
     nObs = pedata.shape[1]
     total_inj = injections["total_generated"]
     obs_time = injections["analysis_time"]
-    mass_dict, min_m1_interp = setup_mass_MSpline_model(injdata, pedata, param_map, args.mass_knots, mmax=args.mmax)    
-    z_dict = setup_redshift_model(injdata, pedata, param_map)
-    prior_dict = {'pe': pedata[param_map['prior']], 'inj': injdata[param_map['prior']]}
-    spin_dict = setup_spin_MSpline_model(injdata, pedata, param_map, args.spin_knots)
-    print(f"{len(z_dict['inj'])} found injections out of {total_inj} total")
-    print(f"Observed {nObs} events, each with {z_dict['pe'].shape[1]} samples, over an observing time of {obs_time} yrs")    
-    return mass_dict, spin_dict, z_dict, prior_dict, total_inj, nObs, obs_time, min_m1_interp
+    
+    mass_model, min_m1_interp = setup_mass_MSpline_model(injdata, pedata, param_map, args.mass_knots, mmax=args.mmax)    
[…]

### 2022-09-29 src/scripts/posterior_pred_checks.py

@@ -1,0 +1,95 @@
+import numpy as np
+import jax.numpy as jnp
+from scipy.stats import gaussian_kde
+from gwpopulation.cupy_utils import trapz
+from gwpopulation.conversions import convert_to_beta_parameters
+from gwpopulation.models.mass import SinglePeakSmoothedMassDistribution
+from gwpopulation.models.spin import iid_spin_orientation_gaussian_isotropic, iid_spin_magnitude_beta
+from gwpopulation.models.redshift import PowerLawRedshift
+from gwpopulation.hyperpe import HyperparameterLikelihood
+from gwpopulation.vt import ResamplingVT
+from bilby.core.result import read_in_result
+from bilby.hyper.model import Model
+from jax import jit
+from utils import MSplineIndependentSpinTilts, MSplineIndependentSpinMagnitudes, MSplinePrimaryPowerlawRatio, MSplineIIDSpinMagnitudes, MSplineIIDSpinTilts
+import deepdish as dd
+from tqdm import trange
+import paths
+import warnings
+warnings.filterwarnings('ignore')
+
+
+
+
+
+def resample_posteriors(likelihood, result, injdata, save=True):
+    
+    original_samples = {key: to_numpy(likelihood.data[key]) for key in likelihood.data}
+    original_samples["prior"] = to_numpy(likelihood.sampling_prior)
+    reweighted_samples, weights = likelihood.posterior_predictive_resample(
+        result.posterior, return_weights=True
+    )
+    original_samples["weights"] = to_numpy(weights)
+    reweighted_samples = {
+        key: to_numpy(reweighted_samples[key]) for key in reweighted_samples
+    }
+    predicted_samples = generate_posterior_predictive_from_injections(
+        likelihood, result, injdata
+    )
+    if save:
+        dd.io.save(
+            os.path.join(result.outdir, f"{result.label}_samples.hdf5"),
+            dict(
+                original=original_samples,
+                reweighted=reweighted_samples,
+                predicted=predicted_samples,
+                names=result.meta_data["event_ids"],
+                label=result.label,
+            ),
+        )
+    else:
+        return original_samples, reweighted_samples
+
+
+def generate_posterior_predictive_from_injections(likelihood, result, injdata):
+    weights = xp.zeros(len(injdata["prior"]))
+    for idx in trange(len(result.posterior)):
+        sample = result.posterior.iloc[idx]
+        likelihood.parameters.update(sample.copy())
+        likelihood.parameters, added_keys = likelihood.conversion_function(
[…]

### 2022-10-04 src/tex/conclusion.tex
more comments fixing up text/wording/grammar

@@
 The original motivation for the peak in the \textsc{PowerlawPeak} model \citep{Talbot_2018} was to represent a possible ``pileup'' of
-masses just before such the truncation, since massive stars just light enough to avoid PISN will shed large amounts of mass in a series of ``pulses'' before collapsing to BHs in a process called 
+masses just before such truncation, since massive stars just light enough to avoid PISN will shed large amounts of mass in a series of ``pulses'' before collapsing to BHs in a process called 
 pulsational pair-instability supernova (PPISN) \citep{Woosley_2017,Woosley_2019,Farmer_2019}.
-While the predictions of the mass scale where pair-instability kicks in are uncertain and depend on not well understood physics,
+While the predictions of the mass scale where pair-instability kicks in are uncertain and depend on poorly understood physics,
 like nuclear reaction rates of carbon and oxygen in the core of stars, models have a hard time predicting this peak to be lower than $m\sim40\msun$ \citep{Belczynski_2016,Marchant_2019,Renzo_2020,Farmer_2019,Farmer_2020}.
@@
 conclusions drawn about the mass distribution inference of section \ref{sec:mass_dist}. While field formation is expected to produce systems with preferentially 
-aligned spins due to tidal interactions, but observational evidence suggests that tides may not be able to re-align spins in all systems as some 
+aligned spins due to tidal interactions, observational evidence suggests that tides may not be able to re-align spins in all systems as some 
 isolated population models assume. Additionally, because of uncertain knowledge of supernovae kicks, isolated formation can produce systems with negative but small effective spins. 

### 2022-10-04 src/tex/intro.tex
more comments fixing up text/wording/grammar

@@
 understanding of the population properties of CBCs, just 7 years after the first observation \citep{o1o2_pop,o3a_pop,o3b_astro_dist}. 
-In the coming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration detectors \citep{aLIGO,aVIRGO}, with the increased sensitivities, 
-there could be a detection as often as every day \citep{LVK_prospects}. This large influx of incoming data will drastically increase what we can 
-learn by combining all observations in order to study the compact object population. The history of these dense objects is imprinted on the properties 
-of the population  of CBCs, allowing us to learn about their formation and evolution by the last few seconds of gravitational radiation emitted \citep{Zevin_2017}. 
+Due to their increased sensitivity, detections could occur as often as every day in the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration 
+detectors \citep{aLIGO,aVIRGO,LVK_prospects}. This large influx of data will drastically improve our ability to study the population of observed CBCs by 
+combining the insights from the entire catalog. The history of these dense objects is imprinted on the properties 
+of the population  of CBCs, allowing us to learn about their formation and evolution from the last few seconds of gravitational radiation emitted \citep{Zevin_2017}. 
 The population distributions of merging compact objects inferred from gravitational-wave observations have been shown to be particularly useful in order to
@@
 
-Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 found signs of structure 
-beyond the first reported feature found at $m_1\sim35\,\msun$ \citep{Talbot_2018,o3a_pop,Tiwari_2021_b,Edelman_2022ApJ}. The evidence for this structure, 
-such as the peak at $m_1\sim10\,\msun$, has only increased after analyzing the following catalog, GWTC-3 \citep{o3b_astro_dist,Tiwari_2022ApJ}. 
-This substructure was first confidently found with multiple different flexible or non-parametric models that are data-driven with little 
-bias on the functional form. Conversely, the other canonical approach is to use simple parametric models that aim to describe the data
-in the simplest way, building in astrophysically motivated priors, followed by sequentially adding complexities only as the data demands it. While in data-scarce, prior dominated
-environments, this simple approach is more powerful. However, as we go forward into the data-rich catalog era, flexible models will be necessary to discover new features that may be in
-the data, which quickly becomes unwieldy with the sequential approach. Non-parametric or semi-parametric methods are particularly useful in looking for unexpected features in the data, finding where 
-our simpler parametric models may be failing to capture meaningful features in the data. Development and robust testing of such methods in the short term will provide
-knock on effects as the size of our catalogs increase, and GW astronomy enters its data-dominated era.
+Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 found signs of structure beyond the first reported feature found at 
+$m_1\sim35\,\msun$ \citep{Talbot_2018,o3a_pop,Tiwari_2021_b,Edelman_2022ApJ}. The evidence for this structure, 
+such as the peak at $m_1\sim10\,\msun$, only grew after analyzing the latest catalog, GWTC-3, with the same models \citep{o3b_astro_dist,Tiwari_2022ApJ}, illustrating  
+the usefulness of data-driven methods even with the relatively small current catalog size. Canonically, the approach to constructing population models has been 
+to use simple parametric models that aim to describe the data in the simplest way, build in astrophysically motivated priors, then sequentially add in 
+complexities only as the data demands. This simple approach is powerful in data-scarce, prior dominated environments; however, as we go forward into 
+the data-rich catalog era, flexible methods such as non-parametric modeling will be necessary to discover new features in the data that can quickly 
+become unwieldy to incorporate into the parametric approach. As opposed to parametric models, flexible and non-parametric models are data-driven and 
+contribute little bias to functional form. Non-parametric or semi-parametric methods are particularly useful to search for unexpected features in the 
+data, such as meaningful features that parametric models may fail to capture. Development and robust testing of such flexible methods in the short 
+term will only provide knock on effects when the time comes to analyze the next catalog of CBC detections.
 
@@
 Isolated or field formation scenarios predict component spins that are preferentially aligned with the binaries orbital angular momentum, although some small 
-misalignment can occur depending on the nature of the supernova kicks as each star collapses to a compact object \bruce{cite}. Dynamical formation scenarios may 
-occur in dense environments where many-body interactions between a large number compact objects occur during the binary formation hardening the binary so that it 
-will merge within a Hubble time. Thus, the dynamical channel produces an isotropic spin tilt distribution \bruce{cite}. BBH spins have also been of controversial 
-interest recently, with different parametric approaches to modeling the spin distribution coming to different conclusions. The studies have disagreed on the possible existence 
-of a significant zero-spinning subpopulation, along with the presence of significant spin misalignment (i.e.
-$\cos{\theta_i} < 0.0$) \citep{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}.
+misalignment can occur depending on the nature of the supernova kicks as each star collapses to a compact object \bruce{cite}. Dynamical formation scenarios may occur in 
+dense environments where many-body interactions between many compact objects cause a binary to harden so that it will merge within a Hubble time. Thus, the dynamical 
+channel produces an isotropic spin tilt distribution \bruce{cite}. BBH spins have also been of controversial interest recently, with different parametric approaches to modeling 
+the spin distribution coming to different conclusions. The studies have disagreed on the possible existence of a significant zero-spinning subpopulation, along with the presence of 
+significant spin misalignment (i.e. $\cos{\theta_i} < 0.0$) \citep{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}. 
 Another study recently showed that the spin tilt distribution inference is sensitive to modeling choices and may not peak at perfectly aligned spins, as is often assumed \citep{spinitasyoulike}. 
@@
 hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower 
-dimensional parametric models in the short run, and will become necessary with future catalogs. This data-driven approach will provide checks of our understanding by finding more 
-subtle features, that may not be expected, should they appear in with more observations. The rest of this manuscript is structured by first going over the background of basis splines in 
-section \ref{sec:basis_splines}, followed by presenting the results of our extensive data-driven study of the mass and spin distributions of BBHs in GWTC-3 section \ref{sec:results}. We 
-discuss our results and their astrophysical implications in section \ref{sec:astrodiscussion}, finishing with our conclusions in section \ref{sec:conclusion}.
+dimensional parametric models in the short run, and will become necessary with future catalogs. Should they appear with more observations, this data-driven approach will provide checks of 
+our understanding by uncovering more subtle -- potentially unexpected -- features. The rest of this manuscript is structured as follows: a description of the background of 
+basis splines in section \ref{sec:basis_splines}, followed by a presentation of the results of our extensive, data-driven study of the mass and spin distributions of BBHs in GWTC-3 in section 
+\ref{sec:results}. We then discuss these results and their astrophysical implications in section \ref{sec:astrodiscussion} and finish with our conclusions in section \ref{sec:conclusion}.

### 2022-10-04 src/tex/methods.tex
more comments fixing up text/wording/grammar

@@
 comes from the fact that one only has to do the somewhat-expensive interpolation once for each set of points at which the spline is evaluated. 
-This provides a considerable computational speedup since each evaluation of the spline function becomes a simpler operation that is just
-a dot product of a matrix and a vector. This straightforward operation is also ideal for optimizations from the use GPU accelerators, 
+This provides a considerable computational speedup as each evaluation of the spline function becomes a simpler operation: a dot product of a 
+matrix and a vector. This straightforward operation is also ideal for optimizations from the use of GPU accelerators, 
 enabling expensive Markov chain Monte Carlo (MCMC) based analyses with hundreds of parameters \bruce{citation?}. 

### 2022-10-04 src/tex/ms.tex
Possible slight title change? highlighting first comprehensive data driven study
new title?
more comments fixing up text/wording/grammar

@@
 \usepackage{showyourwork}
-%\usepackage[perpage]{footmisc}
-%\usepackage{colortbl}
-%\usepackage{lineno}
-%\linenumbers
 \usepackage{bm}
@@
 \usepackage{appendix}
-%\usepackage[margin=10pt]{caption}
 \input{macros}
-
-%\definecolor{Gray}{gray}{0.9}
 
@@
 
-\title{Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population}
+\title{Covering Basis: Comprehensive Model Agnostic Probes of the Binary Black Hole Population}
 
@@
 \affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-
 \author{Ben Farr}
 \affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-
 \author{Zoheyr Doctor}
@@
 University, Evanston, IL 60201, USA}
-
 %\author{Jaxen Godfrey}
 %\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-
 %\author{Alexis Vives}
 %\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-
 %\author{Jon Hornung}
@@
 \begin{abstract}                 
-We introduce a non-parametric model built from basis splines, and use it to infer the astrophysical distribution of 
-binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3, in the most comprehensive data-driven
-investigation of the compact object population. We report the same features previously recovered 
+We introduce a non-parametric model built from basis splines and use it to infer the astrophysical distribution of 
+binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3, which marks this work as 
+the most comprehensive data-driven investigation of the BBH population to date. We report the same features previously recovered 
 with similarly flexible models focusing solely on the mass distribution, most notably the peaks in merger rates at $\sim10\msun$ and $\sim35\msun$. 
@@
 and there is mild support for a non-spinning subpopulation, which may become resolvable with larger catalogs. 
-We also perform a data-driven test of whether the data prefers the spin distributions to be identical for both the more and less massive binary components, 
-finding no strong sign of differing distributions. When modeling the $\chi_\mathrm{eff}$ distribution with our model we find similar 
-conclusions as previously reported, the distribution is consistent with a non-isotropic distribution (that peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}),
+We perform a data-driven test to determine if the data prefers differing spin distributions for each binary component, and 
+find no strong sign that the distributions differ. When modeling the $\chi_\mathrm{eff}$ distribution with our model we find similar 
+conclusions as previously reported: the distribution is consistent with a non-isotropic distribution (that peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}),
 showing considerable support ($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
-We conclude by discussing how non-parametric methods in gravitational-wave population inference are poised to provide a useful complement to 
-the parametric approach going into the data-rich catalog era of gravitational-wave astronomy.
+We conclude with a discussion of how non-parametric methods in gravitational-wave population inference are uniquely poised to complement to 
+the parametric approach as we enter the data-rich era of gravitational-wave astronomy.
 \end{abstract}
@@
 \section{Acknowledgements}\label{sec:acknowledments}
-We thank Will Farr, Tom Callister, Amanda Farah and Maya Fishbach for useful discussions during the preparation this manuscript, 
-along with helpful comments on an early draft by Tom Callister.
+We thank Will Farr, Tom Callister, and Maya Fishbach for useful discussions during the preparation of this manuscript, 
+along with helpful comments on an early draft by Tom Callister and Jaxen Godfrey.
 This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 

### 2022-10-04 src/tex/results.tex
more comments fixing up text/wording/grammar

@@
 We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin and redshift distributions of 
-a binary black holes (BBHs) given a catalog of gravitational wave observations. We parameterize the binaries' masses with the primary (defined as the more massive component) mass 
+binary black holes (BBHs) given a catalog of gravitational wave observations. We parameterize the binaries' masses with the primary (defined as the more massive component) mass 
 and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. Furthermore, we model 4 of the 6 total 
@@
 We assume the polar spin angles are uniformly distributed in the orbital plane. While we choose to use M-Spline distributions to model the primary mass and spin distributions, we 
-model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$. 
-Where $\beta$ is the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \citep{Talbot_2018,o1o2_pop,o3a_pop}.
+model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$, where $\beta$ is 
+the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \citep{Talbot_2018,o1o2_pop,o3a_pop}.
 Additionally, we fit a population model on the redshift or luminosity distance distribution of BBHs, assuming a $\Lambda\mathrm{CDM}$ cosmology defined by the parameters 
@@
 compared to \result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_75percentile]}$} and \result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_75percentile]}$}, found with 
-the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} models respectively.
-An interesting consequence of this is that we do not find a confidently evolving merger rate with redshift, as inferred with power-law based mass models in \citet{o3b_astro_dist}.
-There is a strong correlation measured between the primary mass power law index, $\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution -- 
+the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} models respectively. An interesting consequence of this is that we do not find a confidently evolving merger rate with redshift, 
+as inferred with power-law based mass models in \citet{o3b_astro_dist}. There is a strong correlation measured between the primary mass power law index, 
+$\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution, 
 the inferred rate must drastically increase with redshift to explain the highest mass events in the catalog. However, when one infers a 
-flatter distribution like, as the M-Spline does in figure \ref{fig:mass_distribution}, the higher-mass mergers are consistent with 
+flatter distribution, as the M-Spline does in figure \ref{fig:mass_distribution}, the higher-mass mergers are consistent with 
 the local merger rate density as a function of mass given the selection effects. With our more flexible mass model, we find that the merger rate 
@@
 
-The \textsc{Default} spin model describes the spin magnitude of both components are identical and independently distributed (IID) non-singular Beta distributions. \bruce{cite Wysocki/Talbot}
+The \textsc{Default} spin model describes the spin magnitude of both components as identical and independently distributed (IID) non-singular Beta distributions. \bruce{cite Wysocki/Talbot}
 The Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 

### 2022-10-09 src/tex/appendicies.tex
Move some stuff around in prep for new results -- dont ever mention mspline

@@
 \appendix
-\section{Penalized Splines and Smoothing}\label{sec:psplines}
+\section{Basis Splines} \label{sec:basis_splines}
+
+A common non-parametric method used in many statistical applications is basis splines. A spline function of order $k$, 
+is a piece-wise polynomial of order $k$ polynomials stitched together from defined ``knot'' locations across the domain. 
+They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
+Basis splines of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
+Therefore, given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of basis splines 
+for every possible spline function interpolated from knots, $\mathbf{t}$. The basis components for a given knot vector can be constructed  
+using the Cox-de Boor recursion formula \citep{deBoor78,monotone_regression_splines}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ 
+the base case and recursion relation that generates this particular basis are defined as:
+
+\begin{equation}
+    B_{i,1}(x | \mathbf{t}) = 
+    \begin{cases}
+        1, & \text{if } t_i \leq x < t_{i+1} \\
+        0, & \text{otherwise}
+    \end{cases}
+\end{equation}
+
+\begin{equation}
+    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x | \mathbf{t})B_{i,k}(x | \mathbf{t}) + \big[1-\omega_{i+1,k}(x | \mathbf{t})\big] B_{i+1,k}(x | \mathbf{t})
+\end{equation}
+
+\begin{equation}
+    \omega_{i,k}(x | \mathbf{t}) =
+    \begin{cases}
+        \frac{x-t_i}{t_{i+k}-t_i}, & t_{i+k} \neq t_i \\
+        0, & \text{otherwise}
+    \end{cases}
+\end{equation}
+
+\noindent This is known as the ``B-Spline'' basis after it's inventor de Boor \citep{deBoor78}. The power of basis splines
+comes from the fact that one only has to do the somewhat-expensive interpolation once for each set of points at which the spline is evaluated. 
+This provides a considerable computational speedup as each evaluation of the spline function becomes a simpler operation: a dot product of a 
+matrix and a vector. This straightforward operation is also ideal for optimizations from the use of GPU accelerators, 
+enabling our Markov chain Monte Carlo (MCMC) based analyses, often with hundreds of parameters, to converge in an hour or less. 
+Basis splines can easily be generalized to their two-dimensional analog, producing tensor product basis splines that, 
+with this computational advantage, allow for high fidelity modeling of two-dimensional spline functions.
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/spline_basis_plot.pdf}
+        \caption{Plot showing a ``proper'' (see appendix \ref{sec:psplines}) normalized B-Spline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
+        In black, we show the resulting spline function given equal weights and denote the location of the knots with gray x's.}
+        \label{fig:spline_basis}
+    \end{centering}
+    \script{spline_basis_plot.py}
+\end{figure}
+
+Another important feature of basis splines is that under appropriate prior conditions, one can alleviate sensitivities to arbitrarily 
+chosen prior specifications that splines commonly struggle with. Previous studies using splines had to perform multiple analyses, varying the 
+number of spline knots, then either marginalized over the models or used model comparisons to motivate the best choice \citep{Edelman_2022ApJ}. 
+We can avoid this step with the use of penalized splines (or P-Splines) \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
+where one adds a smoothing prior comprised of Gaussian distributions on the differences between neighboring basis spline coefficients. 
+This prior allows one to populate the domain more densely with knots without the worry of extra variance in the inferred spline functions. When also fitting the scale 
+of the smoothing prior (i.e. the width of the Gaussian distributions on the differences), this allows the data to inform the scale of smoothing required. 
+We discuss the details of our smoothing prior implementation in more detail in the next section, Appendix \ref{sec:psplines}, 
+along with our specific prior and basis choices for each model following that in Appendix \ref{sec:modelpriors}.
+
+\section{Penalized Splines and Smoothing Priors}\label{sec:psplines}
 
@@
 resolution of features in the data the spline is capable of resolving. To ensure your spline based model is flexible enough 
-one would want to add as many knots as densely as possible, but this comes with unwanted side effect of larger variance as mentioned above. 
-To overcome this we resort to the frequentest penalized spline (P-Spline) in which one applies a penalty or regularization term 
+one would want to add as many knots as densely as possible, but this comes with unwanted side effect of larger variance imposed by your model. 
+This can be fixed with the use of penalized splines (P-Spline) in which one applies a prior or regularization term 
 to the likelihood based on the difference of adjacent knot coefficients \citep{eilers2021practical}. The linear combination of spline basis components 
 or the resulting spline function is flat when the basis coefficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as 
-the differences between adjacent knot coefficients get larger, one gets a smoothing of the spline function inferences \citep{eilers2021practical}. 
-Since we are using hierarchical Bayesian inference as our statistical framework, we formulate this penalized likelihood with its Bayesian analog. 
-The difference penalty is equivalent to applying a stochastic difference prior among the knots, as described in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}. 
-This is also sometimes referred to as a Gaussian random walk prior, since each coefficient is normally distributed about its neighboring coefficients. 
-For a spline basis with $n$ degree's of freedom, and a difference penalty of order of $r$ (see \citet{eilers2021practical}), the smoothing prior is defined as:
+the differences between adjacent knot coefficients get larger, one gets a smoothing effect on the spline function \citep{eilers2021practical}. 
+With hierarchical Bayesian inference as our statistical framework, we formulate the penalized likelihood of \citet{eilers2021practical}'s P-Splines with 
+their Bayesian analog \citep{BayesianPSplines}. The Bayesian P-Spline prior places Gaussian distributions over the $r$-th order differences of the 
+coefficients \citep{BayesianPSplines,Jullion2007RobustSO}. This is also sometimes referred to as a Gaussian random walk prior. 
+For a spline basis with $n$ degree's of freedom, and a difference penalty of order of $r$ (see \citet{eilers2021practical}), 
+the smoothing prior is defined as:
 
@@
 This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. The $\tau_\lambda$ controls the ``strength'' of 
-smoothing, or the inverse variance of the Gaussian priors on knot differences. By adding in a very large number 
-of knots such that your domain is densely populated with basis coefficients, this allows the freedom for the model to find the smoothing 
-scale that the data prefers. One downside of this prior specification as noted in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}, is a slight dependence on choice 
-of the b hyperparameter for Gamma distribution prior on $\tau_\lambda$. We reduce this affect by following the method introduced in \citet{Jullion2007RobustSO}
-to alleviate this. This is done by modeling $\tau_\lambda$ with a mixture model on gamma distributions with varying b hyperparameters. 
-We now replace the prior on $\tau_\lambda$ with:
+smoothing, or the inverse variance of the Gaussian priors on knot differences. When there are a very large number of knots, 
+such that your domain is densely populated with basis coefficients, this allows the freedom for the model to find the smoothing 
+scale that the data prefers. One downside of this prior specification as noted in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}, is the dependence on 
+one's choice of value for the $b$ hyperparameter in the Gamma distribution for $\tau_\lambda$. The models introduced in \citet{Jullion2007RobustSO} show how 
+to alleviate this. W model $\tau_\lambda$ with a mixture model composed of multiple Gamma distributions each with varying values for $b$. 
+With this we now have the full prior on $\tau_\lambda$ as:
 
@@
 
-\noindent Where above $\mathcal{D}(m)$ is a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
+\noindent Above $\mathcal{D}(m)$, denotes a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
 and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.
@@
 
-Since the prior is imparting a natural attraction of the coefficients closer to each other in order to smooth the spline function, so one 
-must ensure that the spline function is in fact flat given all equal coefficients. Since one needs to define n+k knots to construct an order-k basis with 
-n degrees of freedom, sometimes studies place knots on top of each other at hard parameter boundaries \cite{deBoor78,monotone_regression_splines}. 
-This may seem motivated, especially when is no reality in the parameter beyond the boundary, but this violates the above condition. 
-We follow the distinction from \citet{eilers2021practical} that such a smoothing prior is only valid with ``proper'' spline bases. 
-A proper basis is where all n+k knots are evenly spaced, see Figure \ref{fig:spline_basis}, as opposed to stacking them at the bounds.
+This prior is imparting a natural attraction of the coefficients closer to each other in order to smooth the spline function, so one 
+must ensure that the spline function is in fact flat given all equal coefficients. There needs to be $n+k$ knots to construct an order-k 
+basis with n degrees of freedom. Some studies place knots on top of each other at hard parameter boundaries \citep{deBoor78,monotone_regression_splines}, 
+which may seem motivated, but this violates the above condition necessary for the P-Spline prior. We follow the distinction in \citet{eilers2021practical} 
+that such a smoothing prior is only valid with ``proper'' spline bases. A proper basis is where all $n+k$ knots are evenly and equally spaced, 
+see Figure \ref{fig:spline_basis}, as opposed to stacking them at the bounds.
 

### 2022-10-09 src/tex/intro.tex
Move some stuff around in prep for new results -- dont ever mention mspline

@@
 contribute little bias to functional form. Non-parametric or semi-parametric methods are particularly useful to search for unexpected features in the 
-data, such as meaningful features that parametric models may fail to capture. Development and robust testing of such flexible methods in the short 
+data, providing meaningful insight of these features that parametric models may fail to capture. Development and robust testing of such flexible methods in the short 
 term will only provide knock on effects when the time comes to analyze the next catalog of CBC detections.

### 2022-10-09 src/tex/methods.tex
Move some stuff around in prep for new results -- dont ever mention mspline

@@
-\section{Constructing A Basis} \label{sec:basis_splines}
+\section{Building the Model} \label{sec:methods}
 
-A common non-parametric method used in many statistical applications is basis splines. A spline function of order $k$, 
-is a piece-wise polynomial of order $k$ polynomials stitched together from defined ``knot'' locations across the domain. 
-They provide a useful and cheap way to interpolate generically smooth functions from a finite sampling of ``knot'' heights. 
-Basis splines of order $k$ are a set of order $k$ polynomials that form a complete basis for any spline function of order $k$. 
-Therefore, given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of basis splines 
-for every possible spline function interpolated from knots, $\mathbf{t}$. The basis components for a given knot vector are constructed  
-using the Cox-de Boor recursion formula \citep{deBoor78}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ we start with the base case as:
-
-\begin{figure}[ht!]
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/spline_basis_plot.pdf}
-        \caption{Plot showing a ``proper'' (see appendix \ref{sec:psplines}) M-Spline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
-        In black, we show the resulting spline function with given equal weights and denote the location of the knots with gray x's.}
-        \label{fig:spline_basis}
-    \end{centering}
-    \script{spline_basis_plot.py}
-\end{figure}
-
-\begin{equation}
-    B_{i,1}(x | \mathbf{t}) = 
-    \begin{cases}
-        1, & \text{if } t_i \leq x < t_{i+1} \\
-        0, & \text{otherwise}
-    \end{cases}
-\end{equation}
-
-\noindent combined with the recursion relation:
-
-\begin{multline*}
-    B_{i,k+1}(x | \mathbf{t}) = \omega_{i,k}(x | \mathbf{t})B_{i,k}(x | \mathbf{t})\\
-                                + \big[1-\omega_{i+1,k}(x | \mathbf{t})\big] B_{i+1,k}(x | \mathbf{t})
-\end{multline*}
-
-\noindent where above $\omega_{i,k}$ is defined as:
-
-\begin{equation}
-\omega_{i,k}(x | \mathbf{t}) =
-\begin{cases}
-    \frac{x-t_i}{t_{i+k}-t_i}, & t_{i+k} \neq t_i \\
-    0, & \text{otherwise}
-\end{cases}
-\end{equation}
-
-\noindent This is known as the ``B-Spline'' basis after it's inventor de Boor \citep{deBoor78}. The power of basis splines
-comes from the fact that one only has to do the somewhat-expensive interpolation once for each set of points at which the spline is evaluated. 
-This provides a considerable computational speedup as each evaluation of the spline function becomes a simpler operation: a dot product of a 
-matrix and a vector. This straightforward operation is also ideal for optimizations from the use of GPU accelerators, 
-enabling expensive Markov chain Monte Carlo (MCMC) based analyses with hundreds of parameters \bruce{citation?}. 
-Basis splines can easily be generalized to their two-dimensional analog, producing tensor product basis splines that, 
-with this computational advantage, allow for high fidelity modeling of two-dimensional spline functions.
-
-A similar basis, the M-Spline basis \citep{monotone_regression_splines}, has desirable properties when looking to model a probability density function, 
-which is the goal of population inference. Each basis component is scaled such that it is normalized over the domain, $\int M_i(x)dx = 1$. This ensures 
-that given a vector of basis coefficients, if they sum to unity, the resulting spline function is normalized across the interpolation domain. 
-The M-Spline basis differs from B-Splines by the scaling factor that normalizes each component:
-
-\begin{equation}\label{eq:MB_SplineRelation}
-M_{i,k} = \frac{k}{t_{i+k} - t_i} B_{i,k}
-\end{equation}
-
-\noindent We use this definition of the M-Spline basis for all the basis spline models used in this manuscript. Figure \ref{fig:spline_basis} 
-shows an example of a cubic (3rd order) M-Spline basis with 20 degrees of freedom and knots linearly spaced from 0 to 1.
-Another important feature of basis splines is that under appropriate prior conditions, one can alleviate sensitivities to arbitrarily 
-chosen prior specifications that splines commonly struggle with. We look to the use of penalized splines (or P-Splines) \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}, 
-where one adds a smoothing prior based on the difference of basis spline coefficients. This allows one to populate the domain with more dense knots 
-without the worry of extra variance in the inferred spline functions. We discuss the details of our smoothing prior implementation 
-in more detail in Appendix \ref{sec:psplines}, along with our specific prior and basis choices for each model in Appendix \ref{sec:modelpriors}.
+We parameterize the binaries' masses with the primary (defined as the more massive component) mass 
+and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. Furthermore, we model 4 of the 6 total 
+spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
+$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular momentum vector. 
+We assume the polar spin angles are uniformly distributed in the orbital plane. While we choose to use M-Spline distributions to model the primary mass and spin distributions, we 
+model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$, where $\beta$ is 
+the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \citep{Talbot_2018,o1o2_pop,o3a_pop}.
+Additionally, we fit a population model on the redshift or luminosity distance distribution of BBHs, assuming a $\Lambda\mathrm{CDM}$ cosmology defined by the parameters 
+from the Planck 2015 results \citep{Planck2015}. This defines an analytical mapping between each event's inferred luminosity distance, and it's redshift, which we now use interchangeably. 
+We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model, described by $p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$ \citep{Fishbach_2018redshift}.
+We describe our specific prior choices on the hyperparameters and each model in more detail in Appendix \ref{sec:modelpriors}.

### 2022-10-09 src/tex/results.tex
Move some stuff around in prep for new results -- dont ever mention mspline

@@
 \section{Binary Black Hole Population Inference with GWTC-3} \label{sec:results}
+
+We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin and redshift distributions of 
+binary black holes (BBHs) given a catalog of gravitational wave observations. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
+accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist}. Since it was concluded to be an outlier of the rest of 
+the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
+a catalog of 69 confident BBH mergers observed over a period of about 2 years, from which we want to infer its population properties. Our study provides the first comprehensive 
+data-driven investigation of the BBH mass and spin distributions, uncovering new insights and corroborating those found with other methods. 
+We start by looking towards our model's inferences of the mass distribution.
 
@@
 \end{figure*}
-
-We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin and redshift distributions of 
-binary black holes (BBHs) given a catalog of gravitational wave observations. We parameterize the binaries' masses with the primary (defined as the more massive component) mass 
-and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. Furthermore, we model 4 of the 6 total 
-spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
-$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular momentum vector. 
-We assume the polar spin angles are uniformly distributed in the orbital plane. While we choose to use M-Spline distributions to model the primary mass and spin distributions, we 
-model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$, where $\beta$ is 
-the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \citep{Talbot_2018,o1o2_pop,o3a_pop}.
-Additionally, we fit a population model on the redshift or luminosity distance distribution of BBHs, assuming a $\Lambda\mathrm{CDM}$ cosmology defined by the parameters 
-from the Planck 2015 results \citep{Planck2015}. This defines an analytical mapping between each event's inferred luminosity distance, and it's redshift, which we now use interchangeably. 
-We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model, described by $p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$ \citep{Fishbach_2018redshift}.
-We describe our specific prior choices on the hyperparameters and each model in more detail in Appendix \ref{sec:modelpriors}. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
-accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist}. Since it was concluded to be an outlier of the rest of 
-the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
-a catalog of 69 confident BBH mergers observed over a period of about 2 years, from which we want to infer its population properties. Our study provides the first comprehensive 
-data-driven investigation of the BBH mass and spin distributions, uncovering new insights and corroborating those found with other methods. 
-We start by looking towards our model's inferences of the mass distribution.
 

### 2022-10-09 src/scripts/mass_distribution_plot.py

@@ -5,6 +5,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 from utils import plot_mean_and_90CI, load_mass_ppd, load_o3b_paper_run_masspdf
 from matplotlib.ticker import ScalarFormatter
+import deepdish as dd
 
 
 def plot_o3b_res(ax, fi, m1=True, col='tab:blue', lab='PP', bounds=False):
@@ -16,7 +17,7 @@ def plot_o3b_res(ax, fi, m1=True, col='tab:blue', lab='PP', bounds=False):
     return ax
 
 
-mmin = 6.5
+mmin = 6
 mmax = 100
 ms, m_pdfs, qs, q_pdfs = load_mass_ppd()
 for jj in range(len(m_pdfs)):
@@ -26,20 +27,29 @@ for jj in range(len(m_pdfs)):
 figx, figy = 14, 5
 fig, axs = plt.subplots(nrows=1, ncols=1, figsize=(figx,figy))
 
+def load_plsplinemass_ppd():
+    datadict = dd.io.load(paths.data / 'plbspline_38n_mspline_12n_iid_compsins_8chains_ppds.h5')
+    return datadict['m1s'], datadict['dRdm1'], datadict['qs'], datadict['dRdq']
+
+plspl_ms, plspl_mpdfs, plspl_qs, plspl_qpdfs = load_plsplinemass_ppd()
+
 for ax, xs, ps, lab in zip([axs], [ms], [m_pdfs], ['m1']):
-    ax = plot_o3b_res(ax,'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5', lab='PLPeak', col='tab:blue')
-    ax = plot_o3b_res(ax,'spline_20n_mass_m_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5', lab='PLSpline', col='tab:green')
-    ax = plot_mean_and_90CI(ax, xs, ps, color='tab:red', label='MSpline')
+    ax = plot_o3b_res(ax,'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5', lab='PLPeak', col='tab:blue', bounds=True)
+    ax = plot_o3b_res(ax,'spline_20n_mass_m_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5', lab='PLSpline', col='tab:green', bounds=True)
[…]

### 2022-10-09 src/scripts/spline_basis_plot.py

@@ -12,7 +12,7 @@ xmax = 1
 xlab = 'x'
 
 cmap = 'magma'
-figx, figy = 7, 5
+figx, figy = 14, 5
 fig, axs = plt.subplots(nrows=1, ncols=1, sharey='all', figsize=(figx,figy))
 
 nadd = k - 1
@@ -56,12 +56,12 @@ leg_item = ndof + 2
 max_col = 6
 ncol = max([leg_item // max_col, 3])
 axs.legend(loc='upper center', fancybox=True, shadow=True, ncol=ncol, fontsize=16)
-axs.set_xlim(0,1)
+axs.set_xlim(0-1./(2*ndof),1+1./(2*ndof))
 axs.set_ylim(0, 1.45)
 axs.set_xlabel(xlab, fontsize=18)
 axs.grid(True, which="major", ls=":")
 axs.set_ylabel(f'p({xlab})', fontsize=18)
 axs.tick_params(labelsize=14)
-plt.title(f'MSpline Basis: k={k-1}, n={ndof}', fontsize=16)
+plt.title(f'Normalized B-Spline Basis: k={k-1}, n={ndof}', fontsize=16)
 fig.tight_layout()
 plt.savefig(paths.figures / 'spline_basis_plot.pdf', dpi=300)

### 2022-10-09 src/scripts/utils.py

@@ -5,7 +5,7 @@ from bilby.core.result import read_in_result
 import deepdish as dd
 
 
-def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None, tracecolor='k'):
+def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None, tracecolor='k', fill_alpha=0.08):
 
     mean = np.mean(ar, axis=0)
     ax.plot(xs, mean, color=color, label=label, lw=5, alpha=0.75)
@@ -15,7 +15,7 @@ def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None
         high = np.percentile(ar, 100-(100-CI)/2., axis=0)
         #ax.plot(xs, low, color='k', lw=0.05, alpha=0.05)
         #ax.plot(xs, high, color='k', lw=0.05, alpha=0.05)
-        ax.fill_between(xs, low, high, color=color, alpha=0.08)
+        ax.fill_between(xs, low, high, color=color, alpha=fill_alpha)
     
     if traces is not None:
         for _ in range(traces):

### 2022-10-10 src/tex/macros.tex
update with new data so paper builds

--- 2022-09-28 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}, "lamb": \{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}\}, "MSplineIndependentCompSpins": \{"beta": \{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}, "lamb": \{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}, "a1\_90percentile": \{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}, "peakCosTilt1": \{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}, "peakCosTilt2": \{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}, "log10gammaFrac1": \{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}, "log10gammaFrac2": \{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}, "negFrac1": \{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}, "negFrac2": \{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}\}, "MSplineIIDCompSpins": \{"beta": \{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}, "a\_90percentile": \{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}, "lamb": \{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}, "peakCosTilt": \{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}, "negFrac": \{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}, "lamb": \{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"beta": \{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}, "lamb": \{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}, "a1\_90percentile": \{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}, "peakCosTilt1": \{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}, "peakCosTilt2": \{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}, "log10gammaFrac1": \{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}, "log10gammaFrac2": \{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}, "negFrac1": \{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}, "negFrac2": \{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"beta": \{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}, "a\_90percentile": \{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}, "lamb": \{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}, "peakCosTilt": \{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}, "log10gammaFrac": \{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}, "negFrac": \{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}, "chieff": \{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{chieff}=0\let\macros@IV@out\macros@XXVII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}, "MSpline": \{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVIII\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXX\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.08, "error plus": 1.69, "error minus": 1.32, "5th percentile": {-}0.246, "95th percentile": 2.84, "10th percentile": 0.0162, "90th percentile": 2.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.08}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.69}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.32}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.246}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.0162}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.39}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.73, "error plus": 1.82, "error minus": 1.87, "5th percentile": 0.856, "95th percentile": 4.54, "10th percentile": 1.26, "90th percentile": 4.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.73}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.87}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.856}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.54}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.15}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 1.71, "error plus": 1.61, "error minus": 1.43, "5th percentile": 0.279, "95th percentile": 3.35, "10th percentile": 0.605, "90th percentile": 2.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{1.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.61}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.43}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.279}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{3.35}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{0.605}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{2.94}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": {-}0.537, "error plus": 1.53, "error minus": 1.56, "5th percentile": {-}2.1, "95th percentile": 0.996, "10th percentile": {-}1.75, "90th percentile": 0.685\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{{-}0.537}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.56}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}2.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.996}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}1.75}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.685}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.751, "error plus": 0.141, "error minus": 0.167, "5th percentile": 0.584, "95th percentile": 0.886, "10th percentile": 0.623, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.751}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.141}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.167}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.584}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.886}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.623}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.86}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.777, "error plus": 0.138, "error minus": 0.17, "5th percentile": 0.607, "95th percentile": 0.907, "10th percentile": 0.645, "90th percentile": 0.885\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.777}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.138}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.607}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.907}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.645}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.885}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.193, "error plus": 0.726, "error minus": 0.731, "5th percentile": {-}0.538, "95th percentile": 0.89, "10th percentile": {-}0.379, "90th percentile": 0.708\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.193}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.726}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.731}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}0.538}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.89}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.379}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.708}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.395, "error plus": 0.636, "error minus": 1.06, "5th percentile": {-}0.664, "95th percentile": 1.0, "10th percentile": {-}0.363, "90th percentile": 0.984\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.395}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.636}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{1.06}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.664}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.363}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.984}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.133, "error plus": 0.708, "error minus": 0.699, "5th percentile": {-}0.565, "95th percentile": 0.845, "10th percentile": {-}0.407, "90th percentile": 0.685\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.133}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.708}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.699}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.565}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{0.845}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.407}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{0.685}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.276, "error plus": 0.716, "error minus": 0.741, "5th percentile": {-}0.465, "95th percentile": 0.986, "10th percentile": {-}0.292, "90th percentile": 0.828\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.276}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.716}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.741}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.465}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.986}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.292}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.828}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.427, "error plus": 0.189, "error minus": 0.178, "5th percentile": 0.249, "95th percentile": 0.618, "10th percentile": 0.283, "90th percentile": 0.577\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.427}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.189}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.178}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.249}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.618}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.283}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.577}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.373, "error plus": 0.188, "error minus": 0.161, "5th percentile": 0.212, "95th percentile": 0.568, "10th percentile": 0.244, "90th percentile": 0.526\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.373}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.188}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.161}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.212}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.568}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.244}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.526}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 1.68, "error plus": 1.58, "error minus": 1.36, "5th percentile": 0.32, "95th percentile": 3.31, "10th percentile": 0.624, "90th percentile": 2.92\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{1.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{1.58}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{1.36}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{3.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.624}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{2.92}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.692, "error plus": 0.148, "error minus": 0.158, "5th percentile": 0.534, "95th percentile": 0.836, "10th percentile": 0.567, "90th percentile": 0.805\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.692}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.148}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.158}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.534}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.836}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.567}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.805}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": {-}0.54, "error plus": 1.55, "error minus": 1.58, "5th percentile": {-}2.12, "95th percentile": 0.997, "10th percentile": {-}1.76, "90th percentile": 0.687\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{{-}0.54}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{1.55}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{1.58}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}2.12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.997}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}1.76}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.687}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.367, "error plus": 0.641, "error minus": 0.503, "5th percentile": {-}0.135, "95th percentile": 1.0, "10th percentile": {-}0.003, "90th percentile": 0.878\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.367}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.641}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.503}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{{-}0.135}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.878}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.31, "error plus": 0.658, "error minus": 0.659, "5th percentile": {-}0.349, "95th percentile": 0.965, "10th percentile": {-}0.19, "90th percentile": 0.803\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.658}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.659}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.349}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.965}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.803}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.344, "error plus": 0.124, "error minus": 0.116, "5th percentile": 0.228, "95th percentile": 0.47, "10th percentile": 0.252, "90th percentile": 0.442\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.344}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.124}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.116}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{0.228}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{0.252}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.442}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}, "FracBelow0": \{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}, "frac\_hm": \{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XXXV\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}, "FracBelow0": \{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}, "PeakChiEff": \{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}, "frac\_dyn": \{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}, "frac\_hm": \{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XL\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}, "FracBelow0": \{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}, "frac\_hm": \{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLV\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}, "FracBelow0": \{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}, "frac\_dyn": \{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@L\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}, "m\_99percentile": \{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LIII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}, "m\_75percentile": \{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}, "m\_99percentile": \{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LVI\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}, "m\_75percentile": \{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}, "m\_99percentile": \{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LVII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LIX\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.0137, "error plus": 0.0158, "error minus": 0.0107, "5th percentile": 0.00302, "95th percentile": 0.0303, "10th percentile": 0.00431, "90th percentile": 0.0259\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.0137}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.0158}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.0107}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{0.00302}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.0303}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.00431}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.0259}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.433, "error plus": 0.0759, "error minus": 0.158, "5th percentile": 0.275, "95th percentile": 0.49, "10th percentile": 0.309, "90th percentile": 0.484\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.433}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.0759}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.158}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.275}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.309}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.484}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.00501, "95th percentile": 0.0531, "10th percentile": {-}0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.00501}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.0531}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.043}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.866, "error plus": 0.152, "error minus": 0.316, "5th percentile": 0.55, "95th percentile": 0.98, "10th percentile": 0.618, "90th percentile": 0.968\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.866}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.152}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.316}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.55}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.618}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.968}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.0859, "error plus": 0.0986, "error minus": 0.067, "5th percentile": 0.0188, "95th percentile": 0.189, "10th percentile": 0.027, "90th percentile": 0.162\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.0859}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.0986}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.067}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.0188}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.189}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.027}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.162}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.0198, "error plus": 0.0153, "error minus": 0.0154, "5th percentile": 0.00444, "95th percentile": 0.0355, "10th percentile": 0.00599, "90th percentile": 0.0322\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.0198}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.0153}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.0154}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.00444}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.0355}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.00599}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.0322}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.351, "error plus": 0.0966, "error minus": 0.119, "5th percentile": 0.232, "95th percentile": 0.438, "10th percentile": 0.248, "90th percentile": 0.429\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.351}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.0966}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.119}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.232}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.438}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.248}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.429}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.031, "error plus": 0.034, "error minus": 0.026, "5th percentile": 0.00501, "95th percentile": 0.0671, "10th percentile": 0.017, "90th percentile": 0.0551\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.031}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.026}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.00501}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.0671}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.0551}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.702, "error plus": 0.193, "error minus": 0.238, "5th percentile": 0.463, "95th percentile": 0.876, "10th percentile": 0.496, "90th percentile": 0.858\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.702}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.193}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.238}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.463}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.876}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.496}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.858}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.124, "error plus": 0.0957, "error minus": 0.0961, "5th percentile": 0.0278, "95th percentile": 0.222, "10th percentile": 0.0374, "90th percentile": 0.201\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.124}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.0957}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.0961}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.0278}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.222}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.0374}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.201}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.0321, "error plus": 0.0183, "error minus": 0.0144, "5th percentile": 0.0177, "95th percentile": 0.0505, "10th percentile": 0.0215, "90th percentile": 0.0434\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.0321}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.0183}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.0144}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.0177}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.0505}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.0215}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.0434}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.399, "error plus": 0.0722, "error minus": 0.0682, "5th percentile": 0.331, "95th percentile": 0.473, "10th percentile": 0.348, "90th percentile": 0.449\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.399}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.0722}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.0682}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.331}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.473}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.348}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.449}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.023, "error plus": 0.0257, "error minus": 0.022, "5th percentile": 0.001, "95th percentile": 0.049, "10th percentile": 0.00501, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.023}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.0257}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.001}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.00501}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.041}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.799, "error plus": 0.144, "error minus": 0.136, "5th percentile": 0.662, "95th percentile": 0.946, "10th percentile": 0.696, "90th percentile": 0.897\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.799}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.144}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.136}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.662}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.946}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.696}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.897}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.2, "error plus": 0.114, "error minus": 0.0899, "5th percentile": 0.111, "95th percentile": 0.316, "10th percentile": 0.134, "90th percentile": 0.271\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.114}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.0899}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.111}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.316}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.134}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.271}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.0705, "error plus": 0.0475, "error minus": 0.0345, "5th percentile": 0.0361, "95th percentile": 0.12, "10th percentile": 0.0421, "90th percentile": 0.104\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.0705}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.0475}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.0345}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.0361}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.0421}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.104}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.398, "error plus": 0.101, "error minus": 0.104, "5th percentile": 0.294, "95th percentile": 0.499, "10th percentile": 0.313, "90th percentile": 0.475\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.398}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.101}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.104}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.294}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.499}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.313}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.475}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.041, "error plus": 0.0351, "error minus": 0.044, "5th percentile": {-}0.003, "95th percentile": 0.0731, "10th percentile": 0.00881, "90th percentile": 0.0631\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.0351}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.044}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.0731}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.00881}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.0631}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.797, "error plus": 0.202, "error minus": 0.208, "5th percentile": 0.588, "95th percentile": 0.997, "10th percentile": 0.626, "90th percentile": 0.95\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.797}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.202}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.208}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.588}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.997}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.626}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.95}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.441, "error plus": 0.297, "error minus": 0.215, "5th percentile": 0.225, "95th percentile": 0.751, "10th percentile": 0.263, "90th percentile": 0.65\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.441}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.297}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.215}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.225}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.751}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.263}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.65}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.643}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{6.81}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{5.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{6.71}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 14.9, "error plus": 5.51, "error minus": 2.75, "5th percentile": 12.2, "95th percentile": 21.0, "10th percentile": 12.7, "90th percentile": 19.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{14.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{5.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{2.75}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{12.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{21.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{12.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{19.1}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 44.8, "error plus": 9.94, "error minus": 6.18, "5th percentile": 38.6, "95th percentile": 55.5, "10th percentile": 39.7, "90th percentile": 52.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{44.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{9.94}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{6.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{38.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{55.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{39.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{52.4}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 5.91, "error plus": 0.509, "error minus": 0.194, "5th percentile": 5.72, "95th percentile": 6.5, "10th percentile": 5.72, "90th percentile": 6.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{5.91}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.509}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.194}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{5.72}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{6.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{5.72}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{6.3}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 30.5, "error plus": 4.42, "error minus": 7.86, "5th percentile": 22.6, "95th percentile": 34.2, "10th percentile": 24.5, "90th percentile": 33.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{30.5}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{4.42}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{7.86}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{22.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{34.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{24.5}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{33.5}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 80.1, "error plus": 11.4, "error minus": 12.5, "5th percentile": 67.6, "95th percentile": 91.3, "10th percentile": 70.2, "90th percentile": 89.3\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{80.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{11.4}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{12.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{67.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{91.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{70.2}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{89.3}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 6.22, "error plus": 0.643, "error minus": 1.08, "5th percentile": 5.14, "95th percentile": 6.81, "10th percentile": 5.43, "90th percentile": 6.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{6.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.643}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{1.08}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{5.14}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{6.81}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{5.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{6.71}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 11.2, "error plus": 4.64, "error minus": 0.589, "5th percentile": 10.6, "95th percentile": 16.6, "10th percentile": 10.7, "90th percentile": 15.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{11.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{4.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.589}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{10.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{16.6}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{10.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{15.0}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 43.2, "error plus": 10.5, "error minus": 4.71, "5th percentile": 38.5, "95th percentile": 55.0, "10th percentile": 39.3, "90th percentile": 52.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{43.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{10.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{4.71}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{38.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{55.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{39.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{52.2}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "MSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0094, "5th percentile": 0.0032, "95th percentile": 0.03, "10th percentile": 0.0048, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.13, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.0012, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.099, "error minus": 0.059, "5th percentile": 0.02, "95th percentile": 0.19, "10th percentile": 0.03, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.011, "error minus": 0.0054, "5th percentile": 0.002, "95th percentile": 0.02, "10th percentile": 0.0026, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.18, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.051, "error plus": 0.034, "error minus": 0.034, "5th percentile": 0.017, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.53, "error plus": 0.24, "error minus": 0.18, "5th percentile": 0.35, "95th percentile": 0.79, "10th percentile": 0.38, "90th percentile": 0.73\}, "frac\_hm": \{"median": 0.046, "error plus": 0.069, "error minus": 0.033, "5th percentile": 0.012, "95th percentile": 0.13, "10th percentile": 0.016, "90th percentile": 0.1\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.019, "error minus": 0.0083, "5th percentile": 0.0027, "95th percentile": 0.031, "10th percentile": 0.0038, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.31, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.83, "10th percentile": 0.43, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.068, "error plus": 0.12, "error minus": 0.052, "5th percentile": 0.017, "95th percentile": 0.2, "10th percentile": 0.024, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXI\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0094, "5th percentile": 0.0032, "95th percentile": 0.03, "10th percentile": 0.0048, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.13, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.0012, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.099, "error minus": 0.059, "5th percentile": 0.02, "95th percentile": 0.19, "10th percentile": 0.03, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.011, "error minus": 0.0054, "5th percentile": 0.002, "95th percentile": 0.02, "10th percentile": 0.0026, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.18, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.051, "error plus": 0.034, "error minus": 0.034, "5th percentile": 0.017, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.53, "error plus": 0.24, "error minus": 0.18, "5th percentile": 0.35, "95th percentile": 0.79, "10th percentile": 0.38, "90th percentile": 0.73\}, "frac\_hm": \{"median": 0.046, "error plus": 0.069, "error minus": 0.033, "5th percentile": 0.012, "95th percentile": 0.13, "10th percentile": 0.016, "90th percentile": 0.1\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.019, "error minus": 0.0083, "5th percentile": 0.0027, "95th percentile": 0.031, "10th percentile": 0.0038, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.31, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.83, "10th percentile": 0.43, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.068, "error plus": 0.12, "error minus": 0.052, "5th percentile": 0.017, "95th percentile": 0.2, "10th percentile": 0.024, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVIII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.7}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.79}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.82}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.86}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{1.0}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{1.1}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.51}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.74}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.7}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{4.7}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{1.0}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.98}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.37}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0094, "5th percentile": 0.0032, "95th percentile": 0.03, "10th percentile": 0.0048, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.13, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.0012, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.099, "error minus": 0.059, "5th percentile": 0.02, "95th percentile": 0.19, "10th percentile": 0.03, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.011, "error minus": 0.0054, "5th percentile": 0.002, "95th percentile": 0.02, "10th percentile": 0.0026, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.18, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.051, "error plus": 0.034, "error minus": 0.034, "5th percentile": 0.017, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.53, "error plus": 0.24, "error minus": 0.18, "5th percentile": 0.35, "95th percentile": 0.79, "10th percentile": 0.38, "90th percentile": 0.73\}, "frac\_hm": \{"median": 0.046, "error plus": 0.069, "error minus": 0.033, "5th percentile": 0.012, "95th percentile": 0.13, "10th percentile": 0.016, "90th percentile": 0.1\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIII@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIII@out\macros@XXXVIII\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.019, "error minus": 0.0083, "5th percentile": 0.0027, "95th percentile": 0.031, "10th percentile": 0.0038, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.31, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.83, "10th percentile": 0.43, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.068, "error plus": 0.12, "error minus": 0.052, "5th percentile": 0.017, "95th percentile": 0.2, "10th percentile": 0.024, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XLIII\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XLVIII\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVI@out\macros@L\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@LI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@LIV\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LVII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.013, "error plus": 0.016, "error minus": 0.0094, "5th percentile": 0.0032, "95th percentile": 0.03, "10th percentile": 0.0048, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.0094}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.0032}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.0048}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.026}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.43, "error plus": 0.078, "error minus": 0.13, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.078}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.32}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.49}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.0012, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.032}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.007}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.051}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{{-}0.0012}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.041}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.86, "error plus": 0.16, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.64}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.97}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.079, "error plus": 0.099, "error minus": 0.059, "5th percentile": 0.02, "95th percentile": 0.19, "10th percentile": 0.03, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.079}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.099}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.059}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.16}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.0073, "error plus": 0.011, "error minus": 0.0054, "5th percentile": 0.002, "95th percentile": 0.02, "10th percentile": 0.0026, "90th percentile": 0.016\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.0073}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.011}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.0054}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.002}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.0026}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.016}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.18, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.18}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.37}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.051, "error plus": 0.034, "error minus": 0.034, "5th percentile": 0.017, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.051}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.034}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.085}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.079}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.53, "error plus": 0.24, "error minus": 0.18, "5th percentile": 0.35, "95th percentile": 0.79, "10th percentile": 0.38, "90th percentile": 0.73\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.79}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.73}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.046, "error plus": 0.069, "error minus": 0.033, "5th percentile": 0.012, "95th percentile": 0.13, "10th percentile": 0.016, "90th percentile": 0.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.046}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.069}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.033}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.012}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.1}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.011, "error plus": 0.019, "error minus": 0.0083, "5th percentile": 0.0027, "95th percentile": 0.031, "10th percentile": 0.0038, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.019}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.0083}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.0027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.0038}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.024}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.31, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.19}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.22}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.39}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.033}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.065}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.61, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.83, "10th percentile": 0.43, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.83}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.78}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.068, "error plus": 0.12, "error minus": 0.052, "5th percentile": 0.017, "95th percentile": 0.2, "10th percentile": 0.024, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.068}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.052}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.15}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.0039}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.39}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.082}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.78}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.024}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{6.7}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{19}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{52}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{9.2}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{21}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{54}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{6.7}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{15}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{52}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\makeatother

### 2022-10-10 src/scripts/create_chieff_from_compspin.py

@@ -143,9 +143,9 @@ def main():
     DefaultSpinTiltModel = Model([iid_spin_orientation_gaussian_isotropic])
     DefaultSpinMagModel = Model([iid_spin_magnitude_beta])
     MassModel = Model([SinglePeakSmoothedMassDistribution(mmin=2.0, mmax=100.0)])
-    mspl_post = dd.io.load(paths.data / "bsplines_64m1_18q_ind16mag_ind12tilt_pl16z_posterior_samples.h5")
+    mspl_post = dd.io.load(paths.data / "bsplines_64m1_18q_ind16mag_ind14tilt_pl16z_posterior_samples.h5")
     chi_effs_mspl = draw_chieff_samples(mspl_post, MSplinePrimaryMSplineRatio, MSplineIndependentSpinMagnitudes, MSplineIndependentSpinTilts, 
-                                        64, 18, 16, 12)
+                                        64, 18, 16, 14)
     pchieffs, chieffs = chi_eff_kde_ppd(chi_effs_mspl)
     mspl_post_iid = dd.io.load(paths.data / "bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_posterior_samples.h5")
     chi_effs_mspl_iid = draw_chieff_samples(mspl_post_iid, MSplinePrimaryMSplineRatio, MSplineIIDSpinMagnitudes, MSplineIIDSpinTilts, 

### 2022-10-10 src/scripts/create_macros.py

@@ -74,8 +74,7 @@ def MSplineIIDSpinMacros():
     frac_neg_cts = np.array(frac_neg_cts)
     posts = load_iid_posterior()
     mags, a_pdfs = load_iid_mag_ppd()
-    return {'beta': save_param_cred_intervals(posts['beta']),
-            'a_90percentile': save_param_cred_intervals(get_percentile(a_pdfs, mags, 90)),
+    return {'a_90percentile': save_param_cred_intervals(get_percentile(a_pdfs, mags, 90)),
             'lamb': save_param_cred_intervals(posts['lamb']),
             'peakCosTilt': save_param_cred_intervals(peak_tilts), 
             'log10gammaFrac': save_param_cred_intervals(np.log10(gamma_fracs)), 
@@ -111,8 +110,7 @@ def MSplineIndSpinMacros():
     frac_neg_cts2 = np.array(frac_neg_cts2)
     posts = load_ind_posterior()
     a1_pdfs, a2_pdfs, mags, mags = load_ind_mag_ppd()
-    return {'beta': save_param_cred_intervals(posts['beta']),
-            'lamb': save_param_cred_intervals(posts['lamb']),
+    return {'lamb': save_param_cred_intervals(posts['lamb']),
             'a1_90percentile': save_param_cred_intervals(get_percentile(a1_pdfs, mags, 90)),
             'a2_90percentile': save_param_cred_intervals(get_percentile(a2_pdfs, mags, 90)),
             'peakCosTilt1': save_param_cred_intervals(peak_tilts1), 'peakCosTilt2': save_param_cred_intervals(peak_tilts2), 
@@ -125,18 +123,18 @@ def chi_eff():
     default = ppds["Default"]
     msplind = ppds["MSplineInd"]
     mspliid = ppds['MSplineIID']
-    msplchieff = dd.io.load(paths.data / "mspline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5")
-    below_0 = {'default': [], 'iid': [], 'ind': [], 'chieff': [], 'gaussian': []}
-    below_m0p3 = {'default': [], 'iid': [], 'ind': [], 'chieff': [], 'gaussian': []}
-    maxchis = {'default': [], 'iid': [], 'ind': [], 'chieff': [], 'gaussian': []}
[…]

### 2022-10-10 src/scripts/plot_chieff.py

@@ -12,27 +12,27 @@ mspl = ppds["MSplineInd"]
 mspl2 = ppds['MSplineIID']
 ax = plot_mean_and_90CI(ax, default["chieffs"], default["pchieff"], color='tab:blue', label='Default', bounds=False)
 ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:purple', label='MSpline-Ind Spin', bounds=False)
-ax = plot_mean_and_90CI(ax, mspl2["chieffs"], mspl2["pchieff"], color='tab:green', label='MSpline-IID Spin', bounds=False)
+ax = plot_mean_and_90CI(ax, mspl2["chieffs"], mspl2["pchieff"], color='tab:red', label='MSpline-IID Spin', bounds=True, fill_alpha=0.125)
 
-handpicked_ppds = dd.io.load(
-    paths.data / "mspline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5"
-)
-xs = handpicked_ppds["chieffs"]
-pchiefss = handpicked_ppds["dRdchieff"]
-for i in range(1500):
-    norm = np.trapz(pchiefss[i, :], x=xs)
-    pchiefss[i, :] /= norm
-ax = plot_mean_and_90CI(ax, xs, pchiefss, color='tab:red', label='MSpline Chi Eff')
+#handpicked_ppds = dd.io.load(
+#    paths.data / "mspline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5"
+#)
+#xs = handpicked_ppds["chieffs"]
+#pchiefss = handpicked_ppds["dRdchieff"]
+#for i in range(1500):
+#    norm = np.trapz(pchiefss[i, :], x=xs)
+#    pchiefss[i, :] /= norm
+#ax = plot_mean_and_90CI(ax, xs, pchiefss, color='tab:red', label='MSpline Chi Eff')
 
 with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json", 'r') as jf:
     o3b_gaussian_data = json.load(jf)
     o3b_gaussian_chi_eff_grid = np.array(o3b_gaussian_data['chi_eff_grid'])
     o3b_gaussian_chi_eff_data = np.array(o3b_gaussian_data['chi_eff_pdfs'])
[…]

### 2022-10-10 src/scripts/utils.py

@@ -45,8 +45,8 @@ def load_iid_tilt_ppd():
     return xs, dRdct
 
 def load_ind_tilt_ppd():
-    datadict = dd.io.load(paths.data / 'bsplines_64m1_18q_ind16mag_ind12tilt_pl16z_ppds.h5')
-    return datadict['tilts'], datadict['dRdct'], datadict['dRdct']
+    datadict = dd.io.load(paths.data / 'bsplines_64m1_18q_ind16mag_ind14tilt_pl16z_ppds.h5')
+    return datadict['tilts'], datadict['dRdct1'], datadict['dRdct2']
 
 def plot_o3b_spintilt(ax, fi,ct1=False, col='tab:blue', lab='PP'):
     xs = np.linspace(-1, 1, 1000)
@@ -81,12 +81,12 @@ def plot_o3b_spinmag(ax, fi, a1=True, col='tab:blue', lab='PP'):
     return ax
 
 def load_ind_mag_ppd():
-    datadict = dd.io.load(paths.data / 'bsplines_64m1_18q_ind16mag_ind12tilt_pl16z_ppds.h5')
-    return datadict['dRda'], datadict['dRda'], datadict['mags'], datadict['mags']
+    datadict = dd.io.load(paths.data / 'bsplines_64m1_18q_ind16mag_ind14tilt_pl16z_ppds.h5')
+    return datadict['dRda1'], datadict['dRda2'], datadict['mags'], datadict['mags']
 
 
 def load_ind_posterior():
-    return dd.io.load(paths.data / 'bsplines_64m1_18q_ind16mag_ind12tilt_pl16z_posterior_samples.h5')
+    return dd.io.load(paths.data / 'bsplines_64m1_18q_ind16mag_ind14tilt_pl16z_posterior_samples.h5')
 
 def load_iid_posterior():
     return dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_posterior_samples.h5')

### 2022-10-10 src/tex/ms.tex
Move some stuff around in prep for new results -- dont ever mention mspline
title?
fix bug

@@
 
-\title{Covering Basis: Comprehensive Model Agnostic Probes of the Binary Black Hole Population}
+\title{Cover Your Basis: Comprehensive Model Agnostic Probes of the Binary Black Hole Population}
 
@@
 University, Evanston, IL 60201, USA}
-%\author{Jaxen Godfrey}
-%\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-%\author{Alexis Vives}
-%\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-%\author{Jon Hornung}
-%\affiliation{Institute  for  Fundamental  Science, Department of Physics, University of Oregon, Eugene, OR 97403, USA}
-%\affiliation{Thurston High School, Springfield, OR 9747, USA}
 
@@
 We perform a data-driven test to determine if the data prefers differing spin distributions for each binary component, and 
-find no strong sign that the distributions differ. When modeling the $\chi_\mathrm{eff}$ distribution with our model we find similar 
-conclusions as previously reported: the distribution is consistent with a non-isotropic distribution (that peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}),
-showing considerable support ($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
-We conclude with a discussion of how non-parametric methods in gravitational-wave population inference are uniquely poised to complement to 
-the parametric approach as we enter the data-rich era of gravitational-wave astronomy.
+find no strong sign that the distributions differ. We conclude with a discussion of how non-parametric methods in 
+gravitational-wave population inference are uniquely poised to complement to the parametric approach as we enter the 
+data-rich era of gravitational-wave astronomy.
+
+%When modeling the $\chi_\mathrm{eff}$ distribution with our model we find similar 
+%conclusions as previously reported: the distribution is consistent with a non-isotropic distribution (that peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}),
+%showing considerable support ($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
 \end{abstract}
@@
 \software{
-\textsc{Astropy}~\citep{2018AJ....156..123A},
+\textsc{Matplotlib}~\citep{Hunter:2007},
 \textsc{NumPy}~\citep{harris2020array},
-\textsc{Matplotlib}~\citep{Hunter:2007},
+\textsc{SciPy}~\citep{2020SciPy-NMeth}
+\textsc{AstroPy}~\citep{2018AJ....156..123A},
 \textsc{Jax}~\citep{jax},
 \textsc{NumPyro}~\citep{pyro,numpyro},
-\textsc{GWPopulation}~\citep{Talbot_2019},
-\textsc{Bilby}~\citep{Ashton_2019,bilby_gwtc1},
-\textsc{Dynesty}~\citep{Speagle_2020}
 }

### 2022-10-10 src/scripts/spline_basis_plot.py

@@ -23,7 +23,7 @@ knots = np.concatenate([xmin-np.arange(1,k)[::-1]*dx, interior_knots, xmax+dx*np
 
 coef = np.array([1./ndof]*ndof)
 grid = np.linspace(xmin, xmax, 2500)
-basis = MSpline(ndof, k=k, knots=knots)(grid)
+basis = MSpline(ndof, k=k, knots=knots).bases(grid)
 
 color_cycle = iter(plt.cm.get_cmap(cmap)(np.linspace(0.3, .9,ndof)[::-1]))
 total_color = iter(plt.cm.get_cmap(cmap)([0.05]))

### 2022-10-10 src/scripts/spline_basis_plot.py
fix bug

@@ -23,7 +23,7 @@ knots = np.concatenate([xmin-np.arange(1,k)[::-1]*dx, interior_knots, xmax+dx*np
 
 coef = np.array([1./ndof]*ndof)
 grid = np.linspace(xmin, xmax, 2500)
-basis = MSpline(ndof, k=k, knots=knots).bases(grid)
+basis = np.array(MSpline(ndof, k=k, knots=knots).bases(grid))
 
 color_cycle = iter(plt.cm.get_cmap(cmap)(np.linspace(0.3, .9,ndof)[::-1]))
 total_color = iter(plt.cm.get_cmap(cmap)([0.05]))

### 2022-10-11 src/tex/macros.tex
update title and abstract

@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "MSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0094, "5th percentile": 0.0032, "95th percentile": 0.03, "10th percentile": 0.0048, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.13, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.0012, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.099, "error minus": 0.059, "5th percentile": 0.02, "95th percentile": 0.19, "10th percentile": 0.03, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.011, "error minus": 0.0054, "5th percentile": 0.002, "95th percentile": 0.02, "10th percentile": 0.0026, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.18, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.051, "error plus": 0.034, "error minus": 0.034, "5th percentile": 0.017, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.53, "error plus": 0.24, "error minus": 0.18, "5th percentile": 0.35, "95th percentile": 0.79, "10th percentile": 0.38, "90th percentile": 0.73\}, "frac\_hm": \{"median": 0.046, "error plus": 0.069, "error minus": 0.033, "5th percentile": 0.012, "95th percentile": 0.13, "10th percentile": 0.016, "90th percentile": 0.1\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.019, "error minus": 0.0083, "5th percentile": 0.0027, "95th percentile": 0.031, "10th percentile": 0.0038, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.31, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.83, "10th percentile": 0.43, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.068, "error plus": 0.12, "error minus": 0.052, "5th percentile": 0.017, "95th percentile": 0.2, "10th percentile": 0.024, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXI\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0094, "5th percentile": 0.0032, "95th percentile": 0.03, "10th percentile": 0.0048, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.13, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.0012, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.099, "error minus": 0.059, "5th percentile": 0.02, "95th percentile": 0.19, "10th percentile": 0.03, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.011, "error minus": 0.0054, "5th percentile": 0.002, "95th percentile": 0.02, "10th percentile": 0.0026, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.18, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.051, "error plus": 0.034, "error minus": 0.034, "5th percentile": 0.017, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.53, "error plus": 0.24, "error minus": 0.18, "5th percentile": 0.35, "95th percentile": 0.79, "10th percentile": 0.38, "90th percentile": 0.73\}, "frac\_hm": \{"median": 0.046, "error plus": 0.069, "error minus": 0.033, "5th percentile": 0.012, "95th percentile": 0.13, "10th percentile": 0.016, "90th percentile": 0.1\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.019, "error minus": 0.0083, "5th percentile": 0.0027, "95th percentile": 0.031, "10th percentile": 0.0038, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.31, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.83, "10th percentile": 0.43, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.068, "error plus": 0.12, "error minus": 0.052, "5th percentile": 0.017, "95th percentile": 0.2, "10th percentile": 0.024, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVIII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.7}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.79}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.82}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.86}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{1.0}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{1.1}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.51}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.74}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.7}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{4.7}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{1.0}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.98}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.37}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0094, "5th percentile": 0.0032, "95th percentile": 0.03, "10th percentile": 0.0048, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.078, "error minus": 0.13, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.0012, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.16, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.099, "error minus": 0.059, "5th percentile": 0.02, "95th percentile": 0.19, "10th percentile": 0.03, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.011, "error minus": 0.0054, "5th percentile": 0.002, "95th percentile": 0.02, "10th percentile": 0.0026, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.18, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.051, "error plus": 0.034, "error minus": 0.034, "5th percentile": 0.017, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.53, "error plus": 0.24, "error minus": 0.18, "5th percentile": 0.35, "95th percentile": 0.79, "10th percentile": 0.38, "90th percentile": 0.73\}, "frac\_hm": \{"median": 0.046, "error plus": 0.069, "error minus": 0.033, "5th percentile": 0.012, "95th percentile": 0.13, "10th percentile": 0.016, "90th percentile": 0.1\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIII@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIII@out\macros@XXXVIII\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.019, "error minus": 0.0083, "5th percentile": 0.0027, "95th percentile": 0.031, "10th percentile": 0.0038, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.31, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.83, "10th percentile": 0.43, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.068, "error plus": 0.12, "error minus": 0.052, "5th percentile": 0.017, "95th percentile": 0.2, "10th percentile": 0.024, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XLIII\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XLVIII\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVI@out\macros@L\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@LI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@LIV\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LVII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.013, "error plus": 0.016, "error minus": 0.0094, "5th percentile": 0.0032, "95th percentile": 0.03, "10th percentile": 0.0048, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.0094}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.0032}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.0048}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.026}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.43, "error plus": 0.078, "error minus": 0.13, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.078}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.32}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.49}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.0012, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.032}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.007}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.051}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{{-}0.0012}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.041}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.86, "error plus": 0.16, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.99, "10th percentile": 0.64, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.64}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.97}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.079, "error plus": 0.099, "error minus": 0.059, "5th percentile": 0.02, "95th percentile": 0.19, "10th percentile": 0.03, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.079}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.099}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.059}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.16}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.0073, "error plus": 0.011, "error minus": 0.0054, "5th percentile": 0.002, "95th percentile": 0.02, "10th percentile": 0.0026, "90th percentile": 0.016\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.0073}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.011}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.0054}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.002}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.02}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.0026}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.016}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.18, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.18}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.37}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.051, "error plus": 0.034, "error minus": 0.034, "5th percentile": 0.017, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.051}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.034}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.085}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.079}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.53, "error plus": 0.24, "error minus": 0.18, "5th percentile": 0.35, "95th percentile": 0.79, "10th percentile": 0.38, "90th percentile": 0.73\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.79}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.73}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.046, "error plus": 0.069, "error minus": 0.033, "5th percentile": 0.012, "95th percentile": 0.13, "10th percentile": 0.016, "90th percentile": 0.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.046}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.069}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.033}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.012}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.1}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.011, "error plus": 0.019, "error minus": 0.0083, "5th percentile": 0.0027, "95th percentile": 0.031, "10th percentile": 0.0038, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.019}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.0083}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.0027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.0038}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.024}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.31, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.19}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.22}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.39}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.033}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.065}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.61, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.83, "10th percentile": 0.43, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.83}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.78}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.068, "error plus": 0.12, "error minus": 0.052, "5th percentile": 0.017, "95th percentile": 0.2, "10th percentile": 0.024, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.068}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.052}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.15}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.0039}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.39}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.082}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.78}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.024}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{6.7}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{19}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{52}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{9.2}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{21}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{54}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{6.7}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{15}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{52}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "MSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXI\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVIII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.7}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.79}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.82}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.86}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{1.0}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{1.1}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.51}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.74}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.7}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{4.7}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{1.0}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.98}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.37}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIII@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIII@out\macros@XXXVIII\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XLIII\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XLVIII\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVI@out\macros@L\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@LI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@LIV\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LVII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.012}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.017}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.0089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.0034}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.0049}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.027}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.075}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.48}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.041}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.96}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.077}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.056}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.021}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.17}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.0072}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.0092}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.0057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.0015}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.018}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.0022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.016}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.097}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.35}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.055}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.019}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.027}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.081}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.77}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.7}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.045}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.0094}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.014}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.099}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.022}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.008}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.0026}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.035}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.0037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.024}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.19}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.21}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.39}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.071}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.065}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.23}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.83}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.42}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.78}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.066}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.05}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.22}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.023}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.15}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.0039}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.39}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.082}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.78}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.024}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{6.7}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{19}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{52}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{9.2}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{21}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{54}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{6.7}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{15}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{52}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\makeatother

### 2022-10-11 src/tex/ms.tex
update title
update title and abstract

@@
 
-\title{Cover Your Basis: Comprehensive Model Agnostic Probes of the Binary Black Hole Population}
+\title{Cover Your Basis: Comprehensive Data-Driven Characterization of the Binary Black Hole Population}
 
@@
 \begin{abstract}                 
-We introduce a non-parametric model built from basis splines and use it to infer the astrophysical distribution of 
-binary black hole (BBH) masses and spins using the 69 confident observations in GWTC-3, which marks this work as 
-the most comprehensive data-driven investigation of the BBH population to date. We report the same features previously recovered 
-with similarly flexible models focusing solely on the mass distribution, most notably the peaks in merger rates at $\sim10\msun$ and $\sim35\msun$. 
-Our study provides the first non-parametric investigation into BBH spin distribution, while simultaneously modeling the mass distribution in the same way, 
-showing signs that the spin tilt distributions may not peak at $\cos(\theta_i) = 1$ as previous models assumed. We find broad agreement with the 
-accepted conclusions of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
-and there is mild support for a non-spinning subpopulation, which may become resolvable with larger catalogs. 
-We perform a data-driven test to determine if the data prefers differing spin distributions for each binary component, and 
-find no strong sign that the distributions differ. We conclude with a discussion of how non-parametric methods in 
+We introduce the first complete non-parametric models for the astrophysical distribution of the binary black hole (BBH) population.
+Using the 69 confident observations in GWTC-3, we present the most comprehensive data-driven investigation of the BBH population to date, including BBH mass ratio, spin magnitudes and misalignments, and redshift.
+We report the same features previously recovered
+with similarly flexible models of the mass distribution, most notably the peaks in merger rates at primary masses of ${\sim}10\msun$ and ${\sim}35\msun$.
+We infer a distribution for primary spin misalignments that peaks away from alignment, supporting recent work that used a variety of parameterized models to come to the same conclusion.
+We find broad agreement with the
+previous inferences of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
+and there is mild support for a non-spinning subpopulation, which may be resolved with larger catalogs. 
+Using our non-parametric models, we explore whether the data support spin distributions unique for each binary component, and 
+find no strong evidence that the distributions differ. We conclude with a discussion of how non-parametric methods in 
 gravitational-wave population inference are uniquely poised to complement to the parametric approach as we enter the 

### 2022-10-11 src/tex/macros.tex
add more plots results etc

@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "MSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXI\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVIII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.7}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.79}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.82}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.86}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{1.0}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{1.1}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.51}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.74}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.7}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{4.7}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{1.0}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.98}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.37}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIII@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIII@out\macros@XXXVIII\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XLIII\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XLVIII\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVI@out\macros@L\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@LI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@LIV\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LVII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.012}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.017}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.0089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.0034}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.0049}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.027}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.075}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.48}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.041}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.96}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.077}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.056}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.021}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.17}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.0072}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.0092}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.0057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.0015}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.018}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.0022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.016}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.097}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.35}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.055}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.019}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.027}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.081}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.77}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.7}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.045}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.0094}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.014}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.099}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.022}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.008}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.0026}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.035}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.0037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.024}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.19}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.21}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.39}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.071}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.065}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.23}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.83}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.42}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.78}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.066}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.05}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.22}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.023}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.15}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.0039}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.39}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.082}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.78}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.024}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{6.7}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{19}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{52}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{9.2}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{21}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{54}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{6.7}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{15}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{52}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.016, "error minus": 0.0092, "5th percentile": 0.0033, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.12, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.85, "error plus": 0.15, "error minus": 0.25, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.078, "error plus": 0.1, "error minus": 0.057, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0069, "error plus": 0.011, "error minus": 0.0051, "5th percentile": 0.0018, "95th percentile": 0.02, "10th percentile": 0.0024, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.033, "error minus": 0.038, "5th percentile": 0.015, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.25, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.78, "10th percentile": 0.37, "90th percentile": 0.72\}, "frac\_hm": \{"median": 0.043, "error plus": 0.07, "error minus": 0.032, "5th percentile": 0.011, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.096\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0079, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0036, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.4, "10th percentile": 0.21, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.013, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.067\}, "frac\_dyn": \{"median": 0.6, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.8, "10th percentile": 0.43, "90th percentile": 0.76\}, "frac\_hm": \{"median": 0.066, "error plus": 0.1, "error minus": 0.049, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.022, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VIII\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVIII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIV\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.016, "error minus": 0.0092, "5th percentile": 0.0033, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.12, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.85, "error plus": 0.15, "error minus": 0.25, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.078, "error plus": 0.1, "error minus": 0.057, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0069, "error plus": 0.011, "error minus": 0.0051, "5th percentile": 0.0018, "95th percentile": 0.02, "10th percentile": 0.0024, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.033, "error minus": 0.038, "5th percentile": 0.015, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.25, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.78, "10th percentile": 0.37, "90th percentile": 0.72\}, "frac\_hm": \{"median": 0.043, "error plus": 0.07, "error minus": 0.032, "5th percentile": 0.011, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.096\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0079, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0036, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.4, "10th percentile": 0.21, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.013, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.067\}, "frac\_dyn": \{"median": 0.6, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.8, "10th percentile": 0.43, "90th percentile": 0.76\}, "frac\_hm": \{"median": 0.066, "error plus": 0.1, "error minus": 0.049, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.022, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXVIII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@V@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXXI\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{25}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.1}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.7}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{45}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{5.9}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{52}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.79}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.82}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.86}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{1.1}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{1.0}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.51}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{0.74}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.7}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{4.7}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{70}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{5.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{51}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{1.0}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.98}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.37}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.016, "error minus": 0.0092, "5th percentile": 0.0033, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.12, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.85, "error plus": 0.15, "error minus": 0.25, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.078, "error plus": 0.1, "error minus": 0.057, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XXXVI\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.0069, "error plus": 0.011, "error minus": 0.0051, "5th percentile": 0.0018, "95th percentile": 0.02, "10th percentile": 0.0024, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.033, "error minus": 0.038, "5th percentile": 0.015, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.25, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.78, "10th percentile": 0.37, "90th percentile": 0.72\}, "frac\_hm": \{"median": 0.043, "error plus": 0.07, "error minus": 0.032, "5th percentile": 0.011, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.096\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0079, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0036, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.4, "10th percentile": 0.21, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.013, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.067\}, "frac\_dyn": \{"median": 0.6, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.8, "10th percentile": 0.43, "90th percentile": 0.76\}, "frac\_hm": \{"median": 0.066, "error plus": 0.1, "error minus": 0.049, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.022, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@XLVI\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVIII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVIII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVIII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVIII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVIII@out\macros@LI\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LIV\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LVII\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXXI@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXXI@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXXI@out\macros@LX\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.012, "error plus": 0.016, "error minus": 0.0092, "5th percentile": 0.0033, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.025\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.012}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.0092}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.0033}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.0049}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.025}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.43, "error plus": 0.074, "error minus": 0.12, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.074}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.48}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.028}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.047}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.041}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.85, "error plus": 0.15, "error minus": 0.25, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.85}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.25}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.65}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.97}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.078, "error plus": 0.1, "error minus": 0.057, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.078}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.021}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.16}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.0069, "error plus": 0.011, "error minus": 0.0051, "5th percentile": 0.0018, "95th percentile": 0.02, "10th percentile": 0.0024, "90th percentile": 0.015\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.0069}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.011}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.0051}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.0018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.0024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.015}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.17}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.36}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.053, "error plus": 0.033, "error minus": 0.038, "5th percentile": 0.015, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.053}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.033}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.038}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.015}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.085}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.079}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.51, "error plus": 0.25, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.78, "10th percentile": 0.37, "90th percentile": 0.72\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.25}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.78}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.37}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.72}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.043, "error plus": 0.07, "error minus": 0.032, "5th percentile": 0.011, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.096\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.043}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.07}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.032}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.015}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.096}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.011, "error plus": 0.016, "error minus": 0.0079, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0036, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.0079}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.0027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.029}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.0036}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.024}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.4, "10th percentile": 0.21, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.21}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.38}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.041, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.013, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.067\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.067}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.6, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.8, "10th percentile": 0.43, "90th percentile": 0.76\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.6}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.76}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.066, "error plus": 0.1, "error minus": 0.049, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.022, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.066}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.049}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.15}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.0039}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.39}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.082}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.78}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.024}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{6.7}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{19}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{52}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{9.2}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{21}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{54}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{6.7}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{15}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{52}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\makeatother

### 2022-10-11 src/tex/methods.tex
add more plots results etc

@@
 
-We parameterize the binaries' masses with the primary (defined as the more massive component) mass 
-and the mass ratio -- defined as $q=\frac{m_2}{m_1}$, bounded in the range from 0 to 1. Furthermore, we model 4 of the 6 total 
+For the method of our data-driven model, we look to the use of basis splines, or B-Splines \citep{deBoor78}. B-Splines of order $k$, are a set of order $k-1$ polynomials that 
+span the space of possible spline functions interpolated from a given set of knot locations. The basis representation of the splines allows for the computational 
+expensive interpolation to be just a single preprocessing step -- amortizing the cost of model evaluation during inference. To mitigate the unwanted side effects of 
+adding extra knots and to avoid running a model grid of differing numbers of knots (as in \citet{Edelman_2022ApJ}), we use the smoothing prior for Bayesian P-Splines, 
+allowing the data to pick the optimal scale needed to fit the present features \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}. We discuss basis splines, the smoothing prior 
+and our specific prior choices on hyperparameters in Appendix \ref{sec:basis_splines}, \ref{sec:psplines} and \ref{sec:modelpriors}.
+
+We parameterize each binaries' masses with the primary (more massive component) mass 
+and the mass ratio ($q=\frac{m_2}{m_1}$), bounded in the range from 0 to 1. Furthermore, we model 4 of the 6 total 
 spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
 $\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular momentum vector. 
-We assume the polar spin angles are uniformly distributed in the orbital plane. While we choose to use M-Spline distributions to model the primary mass and spin distributions, we 
-model the mass ratio distribution with a power law, i.e. $p(q | m_1, m_\mathrm{min}, \beta) \propto q^{\beta} \Theta(qm_1 - m_\mathrm{min}) \Theta(m_1 - qm_1)$, where $\beta$ is 
-the power law index and $\Theta$ is the Heaviside step function which ensures $m_2$ is within the allowed range, [$m_\mathrm{min}$, $m_1$] \citep{Talbot_2018,o1o2_pop,o3a_pop}.
-Additionally, we fit a population model on the redshift or luminosity distance distribution of BBHs, assuming a $\Lambda\mathrm{CDM}$ cosmology defined by the parameters 
+We assume the polar spin angles are uniformly distributed in the orbital plane. For the primary mass distribution, we model the log probability with a B-Spline interpolated over 
+knots linearly spaced in $\log(m_1)$ in the range of support given our observations ($[6.5\msun -- 100\msun]$), such that $\log(p(m_1 | \bm{c})) \propto B_{k}(\log(m_1) | \bm{c})$. 
+We follow the same procedure for the models in mass ratio and spin distributions with knots spaced linearly across each domain, so that we have $\log(p(\theta | \bm{c}_\theta)) \propto B_{k}(\theta | \bm{c}_\theta)$,
+where $\theta$ can be $q$, $a_1$, $a_2$, $\cos{\theta_1}$ or $\cos{\theta_2}$. For the spin magnitude and tilt distributions we construct two versions of the model: first, we model  
+each component's distribution is independently and identically distribution (IID), where we have a single B-Spline model and parameters (coefficients) for each binary spin. 
+Secondly, we model each component's distribution to be unique, fitting separate sets of coefficients for the B-Spline models of the primary and secondary spin distributions. 
+Lastly, we fit a population model on the redshift or luminosity distance distribution of BBHs, assuming a $\Lambda\mathrm{CDM}$ cosmology defined by the parameters 
 from the Planck 2015 results \citep{Planck2015}. This defines an analytical mapping between each event's inferred luminosity distance, and it's redshift, which we now use interchangeably. 
-We model the evolution of the merger rate with redshift with the \textsc{PowerlawRedshift} model, described by $p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$ \citep{Fishbach_2018redshift}.
-We describe our specific prior choices on the hyperparameters and each model in more detail in Appendix \ref{sec:modelpriors}.
+We take a semi-parametric approach to model the evolution of the merger rate with redshift, following \citet{Edelman_2022ApJ}, that parameterizes modulations to an underlying model 
+with splines (in our case basis Splines). We use the \textsc{PowerlawRedshift} model as the underlying distribution to modulate, which has a single hyperparameter, $\lambda_z$, and 
+probability density defined as: $p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$ \citep{Fishbach_2018redshift}. For more detailed descriptions of each model and 
+specific prior choices used for the hyperparameters fit in Appendix \ref{sec:modelpriors}. Now that we have our comprehensive data-driven population model over 
+each of the 7 modeled parameters built, we now apply it using the usual hierarchical Bayesian inference framework (see appendix \ref{sec:hierarchical_inference} for a review) in order to characterize the population of
+BBHs in the most recent catalog of GW observations, GWTC-3 \citep{GWTC3,o3b_astro_dist}.

### 2022-10-11 src/tex/results.tex
add more plots results etc

@@
 the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
-a catalog of 69 confident BBH mergers observed over a period of about 2 years, from which we want to infer its population properties. Our study provides the first comprehensive 
-data-driven investigation of the BBH mass and spin distributions, uncovering new insights and corroborating those found with other methods. 
+a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer its population properties. Our study provides the first comprehensive 
+data-driven investigation of the BBH mass, spin and redshift distributions, uncovering new insights and corroborating those found with other methods. 
 We start by looking towards our model's inferences of the mass distribution.
@@
         \includegraphics[width=\linewidth]{figures/mass_distribution_plot.pdf}
-        \caption{The primary mass distribution inferred with the M-Spline model (red), with 50 knots spaced linearly in $\log m_1$, from the 
-        minimum observed value to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
+        \caption{The marginal primary mass distribution inferred with the B-Spline model (red), with 64 knots spaced linearly in $\log m_1$, from 6.5\msun 
+        to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
         the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models 
@@
 
-We apply our newly constructed models to the BBH analysis that was done in the astrophysical population companion paper to GWTC-3. 
-Figure \ref{fig:mass_distribution} shows how the M-Spline model (red) found consistent features in the mass distribution with 
-what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
-In particular our M-Spline model finds a peak in merger rate density as a function of primary mass, at both $\sim10\msun$ and $\sim35\msun$ agreeing with those 
-reported using the same dataset in \citet{o3b_astro_dist}. We also find a shallow mass distribution that has considerably larger support for higher mass mergers when 
-compared to power-law based models. The M-Spline model finds that 75\% percent of primary masses are below \result{$\CIPlusMinus{\macros[MassDistribution][MSpline][m_75percentile]}$}, 
-compared to \result{$\CIPlusMinus{\macros[MassDistribution][PLPeak][m_75percentile]}$} and \result{$\CIPlusMinus{\macros[MassDistribution][PLSpline][m_75percentile]}$}, found with 
-the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} models respectively. An interesting consequence of this is that we do not find a confidently evolving merger rate with redshift, 
-as inferred with power-law based mass models in \citet{o3b_astro_dist}. There is a strong correlation measured between the primary mass power law index, 
-$\alpha$, and the redshift power-law index, $\lambda_z$. When one infers a steeper mass distribution, 
-the inferred rate must drastically increase with redshift to explain the highest mass events in the catalog. However, when one infers a 
-flatter distribution, as the M-Spline does in figure \ref{fig:mass_distribution}, the higher-mass mergers are consistent with 
-the local merger rate density as a function of mass given the selection effects. With our more flexible mass model, we find that the merger rate 
-is consistent with being uniform with co-moving volume, with $\lambda_z = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][lamb]}$}, compared with 
-\citet{o3b_astro_dist}'s reported value of $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} with the \textsc{PowerlawPeak} mass model.
+Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see that it recovered consistent 
+features with what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
+In particular our B-Spline model finds a peak in merger rate density as a function of primary mass, at both $\sim10\msun$ and $\sim35\msun$ agreeing with those 
+reported using the same dataset in \citet{o3b_astro_dist}. The B-Spline model finds the same feature at $\sim18\msun$ as the \textsc{PowerlawSpline} model, but also 
+agreeing with the \textsc{PowerlawSpline} model, the mass distribution is more uncertain and less constrained in this region than other two confident peaks found.
+Additionally, there is some disagreement at low masses where the models based on power laws show a much higher rate below $\sim8--9\msun$. This is partly due to  
+the minimum mass hyperparameter, which is where the power law ``begins'' in those models. They enforce this hyperparameter as the minimum allowable primary and secondary 
+masses of the catalog. This leads to inferences of $m_\mathrm{min}$ below the minimum observed primary mass in the catalog, $\sim 6.4\msun$, to account for secondary BBH masses 
+that can possibly get to as low as $\sim 3\msun$. Since non-parametric models cannot provide meaningful insights where there is no data - we enforce the minimum primary mass of 
+our B-Spline model to be $6.5\msun$, while secondary BBH masses are enforced to be greater than $3\msun$. The lack of observations in the low primary mass region could 
+point towards signs of a decrease in merger rate from a purported ``lower mass gap'' between neutron star and BH masses, or could be a feature of selection effects which make it 
+more unlikely to observe BBHs in that region of parameter space due to small sensitive volumes probed. We also find no evidence for a sharp fall off in merger rate either following 
+the pileup at $\sim35\,\msun$, which is expected if such a pileup was due to pulsational pair instability supernovae (PPISNe), or where the maximum mass truncation of the power law models 
+is inferred. The lack of any high mass truncation along with the most significant peak found to be at $\sim35\msun$, significantly lower than expected, may pose challenges for conventional stellar 
+evolution theory. This could be a sign of the significant presence of subpopulations that may avoid PISN as the binary forms, but the confirmation of their existence cannot be determined 
+with current catalog sizes.
 
-We find a similar mass ratio distribution to what was found with the \textsc{PowerlawPeak} model in \citet{o3b_astro_dist}. 
-With the M-Spline model on primary mass the mass ratio power law index is $\beta = $\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][beta]}$}, 
-compared to $\beta = $\result{$\CIPlusMinus{\macros[PLPeak][beta]}$} for \textsc{PowerlawPeak}. We find that BBH mergers favor more equal mass mergers
-as would be expected of both main formation channels due to binary mass transfer in isolated formation \bruce{double check this statement with pop synth lit} 
-and three-body interactions that preferentially eject the lightest of the three compact objects, in dynamical formation \bruce{cite these}. 
-We also find no evidence for a sharp fall off in merger rate following the pileup at $\sim35\,\msun$, which is expected if such a pileup was due 
-to pulsational pair instability supernovae (PPISNe). The lack of any high mass truncation along with the peak at 35\msun, significantly lower 
-than expected, may pose challenges for conventional stellar evolution theory and could be a sign of the significant 
-presence of subpopulations that may avoid PISN as the binary forms.
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{figures/q_distribution_plot.pdf}
+    \caption{The marginal mass ratio distribution inferred with the B-Spline model (red), with 18 knots spaced linearly in $q$, from 0.03 to 1. 
+    The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
+    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's 
+    GWTC-3 population analyses \citep{o3b_astro_dist}.}
+    \label{fig:q_distribution}
+    \script{q_distribution_plot.py}
+\end{figure}
+
+We report the B-Spline model's inferred marginal mass ratio distribution in figure \ref{fig:q_distribution}, where we can begin to see some departure from a simple 
+power law. Specifically there looks to be a small decrease or flattening of the merger rate near equal mass ratios. Then we see a small decline to flat plateau from 
+$q\sim0.3$ to $q\sim0.7$. The last step down in rate below $q\sim0.3$ is due to the minimum mass ratio truncation defined by: $q_\mathrm{min}=\frac{m_\mathrm{min}}{m_1}$. 
+When marginalizing over the primary mass distribution with a strong peak at $10\msun$, we get a strong truncation at $q\sim0.3$ which is the minimum secondary mass, $3\msun$, 
+over the most common primary mass, $10\msun$.
 
@@
         \includegraphics[width=\linewidth]{figures/iid_spinmag.pdf}
-        \caption{The spin magnitude distribution inferred with the M-Spline model (red), with 16 knots spaced linearly from 0 to 1, and 
+        \caption{The spin magnitude distribution inferred with the B-Spline model (red), with 16 knots spaced linearly from 0 to 1, and 
         assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
         \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
-        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the M-Spline model, 
+        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model, 
         with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
 
-We model the spin magnitude distributions as IID M-Spline distributions as a flexible check
-to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the M-Spline model, 
-compared with the \textsc{Default} model. The M-Spline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
-of BBH spins below \result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility. The regions of parameter space where they don't agree as well are at 
-the boundaries. The M-Spline model has no enforcement for vanishing support at the extremal values like the Beta distribution, 
+We model the spin magnitude distributions as IID B-Spline distributions as a flexible check
+to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the B-Spline model, 
+compared with the \textsc{Default} model. The B-Spline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
+of BBH spins below \result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility. The regions of parameter space where they don't agree as well are at 
+the boundaries. The B-Spline model has no enforcement for vanishing support at the extremal values like the Beta distribution, 
 allowing it to probe the zero-spin question. We find broad support, with large variance, for non-zero probabilities at $a_i=0$, but cannot confidently determine the presence of 
 a significant non-spinning subpopulation, corroborating similar recent conclusions \citep{BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}. 
-We now repeat the same analysis as above but with independent M-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
+We now repeat the same analysis as above but with independent B-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
 we show the inferred primary (orange), and secondary (olive) spin magnitude distributions inferred when relaxing the IID assumption. We find both 
@@
         \includegraphics[width=\linewidth]{figures/iid_spintilt.pdf}
-        \caption{The spin orientation distribution inferred with the M-Spline model (red), with 16 knots spaced linearly from -1 to 1, and 
+        \caption{The spin orientation distribution inferred with the B-Spline model (red), with 16 knots spaced linearly from -1 to 1, and 
         assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
 We repeat the tests done above on the spin magnitude distributions now with the spin orientation distributions. Figure \ref{fig:iid_spintilt_dist} 
-shows the inferred spin magnitude distribution with the M-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
-The M-Spline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
-We find a distribution that instead of intrinsically peaking at $\cos{\theta}=1$, is found to peak at: $\cos{\theta}=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][peakCosTilt]}$}, at 
+shows the inferred spin magnitude distribution with the B-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
+The B-Spline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
+We find a distribution that instead of intrinsically peaking at $\cos{\theta}=1$, is found to peak at: $\cos{\theta}=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][peakCosTilt]}$}, at 
 90\% credibility. We find less, but still considerable, support for misaligned spins (i.e. $\cos{\theta}<0$) as the \textsc{Default} model. Specifically we 
-find that the fraction of misaligned systems is $f_{\cos{\theta}<0}=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][negFrac]}$}. This implies 
+find that the fraction of misaligned systems is $f_{\cos{\theta}<0}=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][negFrac]}$}. This implies 
 the presence of an isotropic component as expected by dynamical formation channels, albeit less than with the \textsc{Default} model. To quantify the 
@@
 \noindent Now the log this quantity, $\log_{10}Y$, is 0 for tilt distribution that is purely isotropic, negative when anti-aligned values are favored, 
-and positive when aligned tilts are favored. We find a $\log_{10}Y=$\result{$\CIPlusMinus{\macros[MSplineIIDCompSpins][log10gammaFrac]}$}, exhibiting a 
+and positive when aligned tilts are favored. We find a $\log_{10}Y=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][log10gammaFrac]}$}, exhibiting a 
 slight preference for aligned tilts.
 
-Now we model each of the components' orientation distributions with independent M-Spline models as done above, and show the inferred 
+Now we model each of the components' orientation distributions with independent B-Spline models as done above, and show the inferred 
 primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distributions do not agree quite as well as 
@@
 consistent with both each other and the \textsc{Default} model's PPD.
-We find the two distributions to peak at: $\cos{\theta_1}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt1]}$}
-and $\cos{\theta_2}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][peakCosTilt2]}$}, showing that the primary distribution peak is inferred further away 
+We find the two distributions to peak at: $\cos{\theta_1}=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt1]}$}
+and $\cos{\theta_2}=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt2]}$}, showing that the primary distribution peak is inferred further away 
 from the assumed $\cos{\theta}=1$ with the \textsc{Default} model. There is also significant (albeit uncertain) evidence of spin misalignment in each distribution, finding 
-the fraction of misaligned primary and secondary components as: $f_{\cos{\theta_1}<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac1]}$} and 
-$f_{\cos{\theta_2}<0}=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][negFrac2]}$}. We again calculate $\log_{10}Y$  
-for each component distribution and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac1]}$} and 
-$\log_{10}Y_2=$\result{$\CIPlusMinus{\macros[MSplineIndependentCompSpins][log10gammaFrac2]}$}.
+the fraction of misaligned primary and secondary components as: $f_{\cos{\theta_1}<0}=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][negFrac1]}$} and 
+$f_{\cos{\theta_2}<0}=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][negFrac2]}$}. We again calculate $\log_{10}Y$  
+for each component distribution and find: $\log_{10}Y_1=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][log10gammaFrac1]}$} and 
+$\log_{10}Y_2=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][log10gammaFrac2]}$}.
 
@@
         \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
-        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the M-Spline model, 
+        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model, 
         with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
@@
         \includegraphics[width=\linewidth]{figures/chi_eff.pdf}
-        \caption{The effective spin distribution inferred with the M-Spline model (red), with 24 knots spaced linearly from -1 to 1. 
-        The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. We show the inferred $\chi_\mathrm{eff}$ 
-        PPD from the IID component spin M-Spline model (green), the independent component spin M-Spline model (purple), 
-        and both the \textsc{Default} (blue) model and the Gaussian $\chi_\mathrm{eff}$ (olive) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        \caption{The effective spin distribution inferred with the B-Spline IID spin model (red). The solid line shows the population predictive 
+        distribution (PPD) and the shaded region, the 90\% credible interval. We show the inferred $\chi_\mathrm{eff}$ 
+        PPD from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the 
+        Gaussian $\chi_\mathrm{eff}$ (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:chieff_dist}
@@
 called the effective spin defined as: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$. As an alternative check 
-on the spin distributions we also try modeling an M-Spline distribution of effective spins instead of component spin magnitude and tilts 
-as done above. Figure \ref{fig:chieff_dist} shows the inferred effective spin distribution with the M-Spline model (red) along with the 
-inferred effective spin distribution transformed from the PPDs of the component spin models shown previously. We find considerable agreement 
-among the component spin distributions, highlighting that different component spin distributions can imply very similar effective spin 
-distributions which is the better constrained parameter. When modeling the effective spin with the M-Spline model we see very similar 
-shape, but with a sharper peak centered at $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}, compared to 
+on the spin distributions we also try modeling an B-Spline distribution of effective spins instead of component spin magnitude and tilts 
+as done above. Figure \ref{fig:chieff_dist} shows the inferred effective spin distribution with the B-Spline models (red and purple) 
+along with results on the \textsc{Default} and \textsc{Gaussian} models. We find considerable agreement 
+among the effective spin distributions, but the more flexible B-Spline models in component spins, more closely resemble the \textsc{Gaussian} 
+that directly models $\chi_\mathrm{eff}$, than the \textsc{Default} model. This could be signs that the population fit is driven by $\chi_\mathrm{eff}$ 
+more than the component spin dimensions. The B-Spline model finds very similar shapes to the other models, with a peak centered at 
+$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$}, compared to 
 $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model and 
-$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$} with the Gaussian $\chi_\mathrm{eff}$ model. 
+$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$} with the \textsc{Gaussian} $\chi_\mathrm{eff}$ model. 
 As for the misaligned spin question, we calculate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and 
-find for the M-Spline model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}, compared to 
+find for the B-Spline model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$}, compared to 
 $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} with the \textsc{Default} model and 
 $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelow0]}$} with the Gaussian $\chi_\mathrm{eff}$ model.
+
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{figures/rate_vs_z_plot.pdf}
+    \caption{The BBH merger rate as a function of redshift. We show the B-Spline model (red), with 16 knots spaced linearly in $\log(z)$, 
+    from the minimum to the maximum observed redshifts. The solid line shows the population predictive distribution (PPD) and the shaded region, 
+    the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawRedshift} (blue) model from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
+    \label{fig:rofz}
+    \script{rate_vs_z_plot.py}
+\end{figure}
+
+\subsection{Binary Black Hole Merger Rates}
+
+Recent analysis of the GWTC-3 BBH population has shown confident evidence for an increasing merger rate with redshift, nearly ruling out a merger rate that is 
+constant with co-moving volume \citep{Fishbach_2018redshift,o3b_astro_dist}. When extending the power law form of the previously used model to have a modulation 
+that we model with B-Splines, the merger rate as a function of redshift in figure \ref{fig:rofz}, shows mild support for features departing from the underlying power law. 
+In particular, we see a small increase in merger rate from $z\sim0.09$ to $z\sim0.2$ (where we best constrain the rate), followed by a plateau in the rate increase from $z\sim0.2$ to $z\sim0.4$. 
+At larger redshifts, where we begin to have sparse observations, we see no sign of departure from the power-law as the rate continues to increase with redshift. 
+The underlying power-law slope of our modulated B-Spline model is very similar to the GWTC-3 results with the underlying model by itself: the \textsc{PowerlawRedshift} model 
+found $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} when inferred with the \textsc{PowerlawPeak} mass, and \textsc{Default} spin models. Our more 
+flexible model infers a power law slope of $\lambda_z = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][lamb]}$}. We show the basis spline modulations or departure 
+from the power law in \ref{fig:z_modulation} compared to the prior -- showing where we can constrain deviations from the simpler parametric model. 
+The extra freedom of our model does inflate the rate estimates, especially at $z\sim0$ where we don't have any observations. We find a local ($z=0$) merger rate 
+of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}$} for the B-Spline modulation model which compares to 
+$\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}$} for the GWTC-3 result.
+
+\begin{figure}[h]
+    \includegraphics[width=\linewidth]{figures/z_modulation_plot.pdf}
+    \caption{The B-Spline modulation to the underlying power law in redshift, (red). The solid line shows the population predictive distribution (PPD) 
+    and the shaded region, the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines.}
+    \label{fig:z_modulation}
+    \script{z_modulation_plot.py}
+\end{figure}

### 2022-10-11 src/scripts/create_chieff_from_compspin.py

@@ -154,8 +154,8 @@ def main():
     o3b_default_spin_result = read_in_result(paths.data / "o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_result.json")
     chi_effs_o3b_default = draw_chieff_samples_gwpop(o3b_default_spin_result, DefaultSpinMagModel, DefaultSpinTiltModel, MassModel)
     pchieffs_def, chieffs_def = chi_eff_kde_ppd(chi_effs_o3b_default)
-    datadict = {'MSplineInd': {'pchieff': pchieffs, 'chieffs': chieffs}, 
-                'MSplineIID': {'pchieff': pchieffs_iid, 'chieffs': chieffs_iid}, 
+    datadict = {'BSplineInd': {'pchieff': pchieffs, 'chieffs': chieffs}, 
+                'BSplineIID': {'pchieff': pchieffs_iid, 'chieffs': chieffs_iid}, 
                 'Default': {'pchieff':pchieffs_def, 'chieffs':chieffs_def}}
     dd.io.save(paths.data / "chi_eff_ppds.h5", datadict)
 

### 2022-10-11 src/scripts/create_macros.py

@@ -38,7 +38,7 @@ def get_percentile(pdfs, xs, perc):
         x.append(xs[i])
     return np.array(x)
 
-def MSplineMassMacros():
+def BSplineMassMacros():
     print("Saving Mass Distribution Macros...")
     ms, m_pdfs, _, _ = load_mass_ppd()
     m1s = get_percentile(m_pdfs, ms, 1)
@@ -53,11 +53,11 @@ def MSplineMassMacros():
     ps_m99s = get_percentile(ps_mpdfs, ps_ms, 99)
     ps_m75s = get_percentile(ps_mpdfs, ps_ms, 75)  
     return {'PLPeak': {'m_1percentile': save_param_cred_intervals(plpeak_m1s), 'm_75percentile': save_param_cred_intervals(plpeak_m75s), 'm_99percentile': save_param_cred_intervals(plpeak_m99s)}, 
-            'MSpline': {'m_1percentile': save_param_cred_intervals(m1s), 'm_75percentile': save_param_cred_intervals(m75s), 'm_99percentile': save_param_cred_intervals(m99s)}, 
+            'BSpline': {'m_1percentile': save_param_cred_intervals(m1s), 'm_75percentile': save_param_cred_intervals(m75s), 'm_99percentile': save_param_cred_intervals(m99s)}, 
             'PLSpline': {'m_1percentile': save_param_cred_intervals(ps_m1s), 'm_75percentile': save_param_cred_intervals(ps_m75s), 'm_99percentile': save_param_cred_intervals(ps_m99s)}}
 
-def MSplineIIDSpinMacros():
-    print("Saving MSpline IID Component Spin macros...")
+def BSplineIIDSpinMacros():
+    print("Saving BSpline IID Component Spin macros...")
     xs, ct_pdfs = load_iid_tilt_ppd()
     peak_tilts = []
     gamma_fracs = []
@@ -76,12 +76,13 @@ def MSplineIIDSpinMacros():
     mags, a_pdfs = load_iid_mag_ppd()
     return {'a_90percentile': save_param_cred_intervals(get_percentile(a_pdfs, mags, 90)),
             'lamb': save_param_cred_intervals(posts['lamb']),
+            'local_rate': save_param_cred_intervals(posts['rate']),
             'peakCosTilt': save_param_cred_intervals(peak_tilts), 
[…]

### 2022-10-11 src/scripts/mass_distribution_plot.py

@@ -35,18 +35,18 @@ def load_bsplinemass_ppd():
     datadict = dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_ppds.h5')
     return datadict['m1s'], datadict['dRdm1'], datadict['qs'], datadict['dRdq']
 
-plspl_ms, plspl_mpdfs, plspl_qs, plspl_qpdfs = load_plsplinemass_ppd()
+#plspl_ms, plspl_mpdfs, plspl_qs, plspl_qpdfs = load_plsplinemass_ppd()
 bspl_ms, bspl_mpdfs, bspl_qs, bspl_qpdfs = load_bsplinemass_ppd()
 
 for ax, xs, ps, lab in zip([axs], [ms], [m_pdfs], ['m1']):
     ax = plot_o3b_res(ax,'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5', lab='PL+Peak', col='tab:blue', bounds=False)#, fill_alpha=0.15)
     ax = plot_o3b_res(ax,'spline_20n_mass_m_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5', lab='PL+Spline', col='tab:green', bounds=False)#, fill_alpha=0.15)
     #ax = plot_mean_and_90CI(ax, xs, ps, color='tab:red', label='MSpline', fill_alpha=0.125)
-    ax = plot_mean_and_90CI(ax, plspl_ms, plspl_mpdfs, color='tab:purple', label='PL+BSpline', bounds=False)#, fill_alpha=0.125)
-    ax = plot_mean_and_90CI(ax, bspl_ms, bspl_mpdfs, color='tab:red', label='LogLogBSpline', bounds=True)
+    #ax = plot_mean_and_90CI(ax, plspl_ms, plspl_mpdfs, color='tab:purple', label='PL+BSpline', bounds=False)#, fill_alpha=0.125)
+    ax = plot_mean_and_90CI(ax, bspl_ms, bspl_mpdfs, color='tab:red', label='BSpline', bounds=True)
     ax.legend(frameon=False, fontsize=14);
     ax.set_xlabel(r'$m_1 \,\,[M_\odot]$', fontsize=18)
-    ax.set_ylabel(r'$p_{MS}(m_1) \,\,[M_\odot^{-1}]$', fontsize=18)
[…]

### 2022-10-11 src/scripts/plot_chieff.py

@@ -8,21 +8,21 @@ from utils import plot_mean_and_90CI
 fig, ax = plt.subplots(1,1,figsize=(7,5))
 ppds = dd.io.load(paths.data / "chi_eff_ppds.h5")
 default = ppds["Default"]
-mspl = ppds["MSplineInd"]
-mspl2 = ppds['MSplineIID']
+mspl = ppds["BSplineInd"]
+mspl2 = ppds['BSplineIID']
 ax = plot_mean_and_90CI(ax, default["chieffs"], default["pchieff"], color='tab:blue', label='Default', bounds=False)
-ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:purple', label='MSpline-Ind Spin', bounds=False)
-ax = plot_mean_and_90CI(ax, mspl2["chieffs"], mspl2["pchieff"], color='tab:red', label='MSpline-IID Spin', bounds=True, fill_alpha=0.125)
+ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:purple', label='BSpline-Ind Spin', bounds=False)
+ax = plot_mean_and_90CI(ax, mspl2["chieffs"], mspl2["pchieff"], color='tab:red', label='BSpline-IID Spin', bounds=True, fill_alpha=0.125)
 
 #handpicked_ppds = dd.io.load(
-#    paths.data / "mspline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5"
+#    paths.data / "BSpline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5"
 #)
 #xs = handpicked_ppds["chieffs"]
 #pchiefss = handpicked_ppds["dRdchieff"]
 #for i in range(1500):
 #    norm = np.trapz(pchiefss[i, :], x=xs)
 #    pchiefss[i, :] /= norm
-#ax = plot_mean_and_90CI(ax, xs, pchiefss, color='tab:red', label='MSpline Chi Eff')
+#ax = plot_mean_and_90CI(ax, xs, pchiefss, color='tab:red', label='BSpline Chi Eff')
 
 with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json", 'r') as jf:
     o3b_gaussian_data = json.load(jf)

### 2022-10-11 src/scripts/posterior_pred_checks.py

@@ -1,95 +1,0 @@
-import numpy as np
-import jax.numpy as jnp
-from scipy.stats import gaussian_kde
-from gwpopulation.cupy_utils import trapz
-from gwpopulation.conversions import convert_to_beta_parameters
-from gwpopulation.models.mass import SinglePeakSmoothedMassDistribution
-from gwpopulation.models.spin import iid_spin_orientation_gaussian_isotropic, iid_spin_magnitude_beta
-from gwpopulation.models.redshift import PowerLawRedshift
-from gwpopulation.hyperpe import HyperparameterLikelihood
-from gwpopulation.vt import ResamplingVT
-from bilby.core.result import read_in_result
-from bilby.hyper.model import Model
-from jax import jit
-from utils import MSplineIndependentSpinTilts, MSplineIndependentSpinMagnitudes, MSplinePrimaryPowerlawRatio, MSplineIIDSpinMagnitudes, MSplineIIDSpinTilts
-import deepdish as dd
-from tqdm import trange
-import paths
-import warnings
-warnings.filterwarnings('ignore')
-
-
-
-
-
-def resample_posteriors(likelihood, result, injdata, save=True):
-    
-    original_samples = {key: to_numpy(likelihood.data[key]) for key in likelihood.data}
-    original_samples["prior"] = to_numpy(likelihood.sampling_prior)
-    reweighted_samples, weights = likelihood.posterior_predictive_resample(
-        result.posterior, return_weights=True
-    )
-    original_samples["weights"] = to_numpy(weights)
-    reweighted_samples = {
-        key: to_numpy(reweighted_samples[key]) for key in reweighted_samples
-    }
-    predicted_samples = generate_posterior_predictive_from_injections(
-        likelihood, result, injdata
-    )
-    if save:
-        dd.io.save(
-            os.path.join(result.outdir, f"{result.label}_samples.hdf5"),
-            dict(
-                original=original_samples,
-                reweighted=reweighted_samples,
-                predicted=predicted_samples,
-                names=result.meta_data["event_ids"],
-                label=result.label,
-            ),
-        )
-    else:
-        return original_samples, reweighted_samples
-
-
-def generate_posterior_predictive_from_injections(likelihood, result, injdata):
-    weights = xp.zeros(len(injdata["prior"]))
-    for idx in trange(len(result.posterior)):
-        sample = result.posterior.iloc[idx]
-        likelihood.parameters.update(sample.copy())
-        likelihood.parameters, added_keys = likelihood.conversion_function(
[…]

### 2022-10-11 src/scripts/utils.py

@@ -5,18 +5,20 @@ from bilby.core.result import read_in_result
 import deepdish as dd
 
 
-def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None, tracecolor='k', fill_alpha=0.08):
+def plot_mean_and_90CI(ax, xs, ar, color, label, bounds=True, CI=90, traces=None, tracecolor='k', fill_alpha=0.08, median=False, mean=True):
 
-    mean = np.mean(ar, axis=0)
-    ax.plot(xs, mean, color=color, label=label, lw=5, alpha=0.75)
-    
+    if mean:
+        mean = np.mean(ar, axis=0)    
+        ax.plot(xs, mean, color=color, label=label, lw=5, alpha=0.75)
+    elif median:
+        mean = np.median(ar,axis=0)
+        ax.plot(xs, mean, color=color, label=label, lw=5, alpha=0.75)
     if bounds:
         low = np.percentile(ar, (100-CI)/2., axis=0)
         high = np.percentile(ar, 100-(100-CI)/2., axis=0)
         #ax.plot(xs, low, color='k', lw=0.05, alpha=0.05)
         #ax.plot(xs, high, color='k', lw=0.05, alpha=0.05)
         ax.fill_between(xs, low, high, color=color, alpha=fill_alpha)
-    
     if traces is not None:
         for _ in range(traces):
             idx = np.random.choice(ar.shape[0])

### 2022-10-11 src/scripts/q_distribution_plot.py
plotting scripts v1

@@ -1,0 +1,48 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+from utils import plot_mean_and_90CI, load_mass_ppd, load_o3b_paper_run_masspdf
+import deepdish as dd
+
+
+def plot_o3b_res(ax, fi, m1=True, col='tab:blue', lab='PP', bounds=False, fill_alpha=0.08):
+    plpeak_mpdfs, plpeak_qpdfs, plpeak_ms, plpeak_qs = load_o3b_paper_run_masspdf(paths.data / fi)
+    if m1:
+        plot_mean_and_90CI(ax, plpeak_ms, plpeak_mpdfs, color=col, label=lab, bounds=bounds, fill_alpha=fill_alpha)
+    else:
+        plot_mean_and_90CI(ax, plpeak_qs, plpeak_qpdfs, color=col, label=lab, bounds=bounds, fill_alpha=fill_alpha)
+    return ax
+
+
+mmin = 6
+mmax = 100
+ms, m_pdfs, qs, q_pdfs = load_mass_ppd()
+for jj in range(len(m_pdfs)):
+    m_pdfs[jj,:] /= np.trapz(m_pdfs[jj,:], ms)
+    q_pdfs[jj,:] /= np.trapz(q_pdfs[jj,:], qs)
+
+figx, figy = 7, 5
+fig, axs = plt.subplots(nrows=1, ncols=1, figsize=(figx,figy))
+
+
+for ax, xs, ps, lab in zip([axs], [qs], [q_pdfs], ['q']):
+    ax = plot_o3b_res(ax,'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5', m1=False, lab='PL+Peak', col='tab:blue', bounds=False)#, fill_alpha=0.15)
+    ax = plot_o3b_res(ax,'spline_20n_mass_m_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5', m1=False, lab='PL+Spline', col='tab:green', bounds=False)#, fill_alpha=0.15)
+    ax = plot_mean_and_90CI(ax, qs, q_pdfs, color='tab:red', label='BSpline', bounds=True)
+    ax.legend(frameon=False, fontsize=14);
+    ax.set_xlabel(r'$q$', fontsize=18)
+    ax.set_ylabel(r'$p(q)$', fontsize=18)
[…]

### 2022-10-11 src/scripts/rate_vs_z_plot.py

@@ -1,0 +1,39 @@
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+from utils import plot_mean_and_90CI, read_in_result
+import deepdish as dd
+
+def load_plbspline_ppd():
+    datadict = dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_ppds.h5')
+    return datadict['zs'], datadict['Rofz']
+
+def load_o3b_rofz(zs):
+    result = read_in_result(paths.data / 'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_result.json')
+    lamb = result.posterior['lamb']
+    rate = result.posterior['rate']
+    dRdzs = [rate[i]*(1+zs)**lamb[i] for i in range(len(lamb))]
+    return zs, np.array(dRdzs)
+
+zs, dR = load_plbspline_ppd()
+pl_zs, pl_dR = load_o3b_rofz(zs)
+
+def plot_rofz(dRdz, zs, pl_dRdz, pl_zs):
+    fig, ax = plt.subplots(nrows=1, ncols=1, figsize=(7, 4))
+    me = np.median(dRdz, axis=0)
+    ax = plot_mean_and_90CI(ax, zs, dRdz, color='tab:red', bounds=True, label='PL+BSpline', median=True, mean=False)
+    ax = plot_mean_and_90CI(ax, pl_zs, pl_dRdz, color='tab:blue', bounds=True, fill_alpha=0.2, label='PL', median=False, mean=False)
+    ax.plot(zs, me[0] * (1.0 + zs) ** 2.7, lw=5, alpha=0.15, color="k", label="SFR")
+    
+    ax.set_xlabel(r"$z$", fontsize=16)
+    ax.set_ylabel(r"$\mathcal{R}(z)$", fontsize=16)
+    ax.set_yscale("log")
+    ax.set_ylim(1,1e3)
+    ax.set_xlim(zs[0], 1.5)
+    ax.legend()
+    return fig
+
+fig = plot_rofz(dR, zs, pl_dR, pl_zs)
+plt.title(r'GWTC-3: $\mathcal{R}(z)$', fontsize=18);
+fig.tight_layout()
+plt.savefig(paths.figures / 'rate_vs_z_plot.pdf', dpi=300);

### 2022-10-11 src/scripts/z_modulation_plot.py

@@ -1,0 +1,47 @@
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+from utils import plot_mean_and_90CI
+import deepdish as dd
+
+def load_plbspline_ppd():
+    datadict = dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_ppds.h5')
+    prior_datadict = dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_prior_ppds.h5')
+    posterior = dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_posterior_samples.h5')
+    prior = dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_prior_samples.h5')
+    return datadict['zs'], datadict['Rofz'], prior_datadict['zs'], prior_datadict['Rofz'], posterior['lamb'], prior['lamb'], posterior['rate']
+
+def get_modulation(R,z,L,rate=None):
+    N = len(L)
+    mod = np.zeros_like(R)
+    for i in range(N):
+        if rate is not None:
+            rate_of_z = R[i,:] / rate[i]
+        else:
+            rate_of_z = R[i,:]
+        mod[i,:] = np.log(rate_of_z / (1+z)**(L[i]-1))
+    return mod
+
+zs, Rofz, pr_zs, pr_Rofz, lamb, pr_lamb, rate = load_plbspline_ppd()
+modulation = get_modulation(Rofz, zs, lamb, rate=rate)
+prior_modulation = get_modulation(pr_Rofz, pr_zs, pr_lamb)
+
+def plot_zmod(mod,priormod,zs):
+    fig, ax = plt.subplots(nrows=1, ncols=1, figsize=(7, 4))
+    ax = plot_mean_and_90CI(ax, zs, mod, color='tab:red', bounds=True, label='PL+BSpline', median=True, mean=False)
+
+    ax.plot(zs, np.percentile(priormod,5,axis=0), lw=3, ls='--', color="k", label="Prior")
+    ax.plot(zs, np.percentile(priormod,95,axis=0), lw=3, ls='--', color="k")
+
+    ax.set_xlabel(r"$z$", fontsize=16)
+    ax.set_ylabel(r"$B(z)$", fontsize=16)
+    ax.set_xscale('log')
+    ax.set_ylim(-2,2)
[…]

### 2022-10-11 src/tex/conclusion.tex
fix macro

@@
 we place conservative upper bounds on the fraction of hierarchical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$ with 
-the M-Spline $\chi_\mathrm{eff}$ model constraining $f_\mathrm{HM} < $\result{$\macros[ChiEffective][chieff][frac_hm][10th percentile]$} 
-and $f_\mathrm{dyn} < $\result{$\macros[ChiEffective][chieff][frac_dyn][10th percentile]$} at 90\% credibility.
+the M-Spline $\chi_\mathrm{eff}$ model constraining $f_\mathrm{HM} < $\result{$\macros[ChiEffective][iid][frac_hm][10th percentile]$} 
+and $f_\mathrm{dyn} < $\result{$\macros[ChiEffective][iid][frac_dyn][10th percentile]$} at 90\% credibility.
 

### 2022-10-11 src/tex/methods.tex
fix up some results/methods a bit

@@
 
-For the method of our data-driven model, we look to the use of basis splines, or B-Splines \citep{deBoor78}. B-Splines of order $k$, are a set of order $k-1$ polynomials that 
+We construct our data-driven model with the application of basis splines, or B-Splines \citep{deBoor78}. B-Splines of order $k$, are a set of order $k-1$ polynomials that 
 span the space of possible spline functions interpolated from a given set of knot locations. The basis representation of the splines allows for the computational 
-expensive interpolation to be just a single preprocessing step -- amortizing the cost of model evaluation during inference. To mitigate the unwanted side effects of 
+expensive interpolation to be done in a single preprocessing step -- amortizing the cost of model evaluation during inference. To mitigate the unwanted side effects of 
 adding extra knots and to avoid running a model grid of differing numbers of knots (as in \citet{Edelman_2022ApJ}), we use the smoothing prior for Bayesian P-Splines, 
@@
 We assume the polar spin angles are uniformly distributed in the orbital plane. For the primary mass distribution, we model the log probability with a B-Spline interpolated over 
-knots linearly spaced in $\log(m_1)$ in the range of support given our observations ($[6.5\msun -- 100\msun]$), such that $\log(p(m_1 | \bm{c})) \propto B_{k}(\log(m_1) | \bm{c})$. 
-We follow the same procedure for the models in mass ratio and spin distributions with knots spaced linearly across each domain, so that we have $\log(p(\theta | \bm{c}_\theta)) \propto B_{k}(\theta | \bm{c}_\theta)$,
-where $\theta$ can be $q$, $a_1$, $a_2$, $\cos{\theta_1}$ or $\cos{\theta_2}$. For the spin magnitude and tilt distributions we construct two versions of the model: first, we model  
+knots linearly spaced in $\log(m_1)$ in the range of support given our observations ($[6.5\msun-100\msun]$), such that $\log(p(m_1 | \bm{c})) \propto B_{k}(\log(m_1) | \bm{c})$, where $B_{k}$ is the 
+$k$-th order B-Spline function with basis coefficients, $\bm{c}$. We follow the same procedure for the models in mass ratio and spin distributions with knots spaced linearly across each domain, 
+so that we have $\log(p(\theta | \bm{c}_\theta)) \propto B_{k}(\theta | \bm{c}_\theta)$, where $\theta$ can be $q$, $a_1$, $a_2$, $\cos{\theta_1}$ or $\cos{\theta_2}$. 
+For the spin magnitude and tilt distributions we construct two versions of the model: first, we model  
 each component's distribution is independently and identically distribution (IID), where we have a single B-Spline model and parameters (coefficients) for each binary spin. 
@@
 specific prior choices used for the hyperparameters fit in Appendix \ref{sec:modelpriors}. Now that we have our comprehensive data-driven population model over 
-each of the 7 modeled parameters built, we now apply it using the usual hierarchical Bayesian inference framework (see appendix \ref{sec:hierarchical_inference} for a review) in order to characterize the population of
-BBHs in the most recent catalog of GW observations, GWTC-3 \citep{GWTC3,o3b_astro_dist}.
+each of the 7 modeled parameters built, we fit our model using the usual hierarchical Bayesian inference framework (see appendix \ref{sec:hierarchical_inference} for a review) in order to characterize
+the population of BBHs in the most recent catalog of GW observations, GWTC-3 \citep{GWTC3,o3b_astro_dist}.

### 2022-10-11 src/tex/results.tex
fix up some results/methods a bit

@@
 masses of the catalog. This leads to inferences of $m_\mathrm{min}$ below the minimum observed primary mass in the catalog, $\sim 6.4\msun$, to account for secondary BBH masses 
-that can possibly get to as low as $\sim 3\msun$. Since non-parametric models cannot provide meaningful insights where there is no data - we enforce the minimum primary mass of 
+that can possibly get to as low as $\sim 3\msun$. Since non-parametric models do not provide meaningful insights where there is no data - we enforce the minimum primary mass of 
 our B-Spline model to be $6.5\msun$, while secondary BBH masses are enforced to be greater than $3\msun$. The lack of observations in the low primary mass region could 
@@
 is inferred. The lack of any high mass truncation along with the most significant peak found to be at $\sim35\msun$, significantly lower than expected, may pose challenges for conventional stellar 
-evolution theory. This could be a sign of the significant presence of subpopulations that may avoid PISN as the binary forms, but the confirmation of their existence cannot be determined 
-with current catalog sizes.
+evolution theory. This could be hinting at the significant presence of subpopulations that avoid PISN during binary formation, but the confirmation of the existence of such subpopulations 
+cannot be determined with current catalog sizes.
 
@@
 
-We report the B-Spline model's inferred marginal mass ratio distribution in figure \ref{fig:q_distribution}, where we can begin to see some departure from a simple 
-power law. Specifically there looks to be a small decrease or flattening of the merger rate near equal mass ratios. Then we see a small decline to flat plateau from 
-$q\sim0.3$ to $q\sim0.7$. The last step down in rate below $q\sim0.3$ is due to the minimum mass ratio truncation defined by: $q_\mathrm{min}=\frac{m_\mathrm{min}}{m_1}$. 
-When marginalizing over the primary mass distribution with a strong peak at $10\msun$, we get a strong truncation at $q\sim0.3$ which is the minimum secondary mass, $3\msun$, 
-over the most common primary mass, $10\msun$.
+We report the B-Spline model's inferred marginal mass ratio distribution in figure \ref{fig:q_distribution}, where we can begin to see departure from a simple 
+power law. Specifically there looks to be a small decrease or flattening of the merger rate near equal mass ratios, as well as a fatter tail towards unequal mass ratios 
+than the power law based models find. Then we see a small decline to flat plateau from $q\sim0.3$ to $q\sim0.7$. The sharp decrease in rate just below 
+$q\sim0.3$ is due to the minimum mass ratio truncation defined by: $q_\mathrm{min}=\frac{m_\mathrm{min}}{m_1}$. When marginalizing over the primary mass 
+distribution with a strong peak at $10\msun$, the mass ratio distribution truncates at $q\sim0.3$: the minimum secondary mass, $3\msun$, 
+divided by the most common primary mass, $\sim10\msun$.
 
@@
 
-The \textsc{Default} spin model describes the spin magnitude of both components as identical and independently distributed (IID) non-singular Beta distributions. \bruce{cite Wysocki/Talbot}
+The \textsc{Default} spin model describes the spin magnitude of both components as identical and independently distributed (IID) non-singular Beta distributions \citep{Talbot_2017,Wysocki_2019}.
 The Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 
-the Beta distribution non-singular (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. In reality, it is expected that 
-all physical bodies must have at least some non-zero angular momentum, studies have proposed the existence of a distinct subpopulation of non-spinning or 
-negligibly spinning black holes that can elude discovery with such a model \citep{FullerMa2019,RouletGWTC2Pop,BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}.
+the Beta distribution non-singular (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. Recent studies have proposed the possible existence of a 
+distinct subpopulation of non-spinning or negligibly spinning black holes that can elude discovery with such a model \citep{FullerMa2019,RouletGWTC2Pop,BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}.
 
@@
 
-We model the spin magnitude distributions as IID B-Spline distributions as a flexible check
-to the assumptions of the \textsc{Default} model. Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the B-Spline model, 
-compared with the \textsc{Default} model. The B-Spline model finds broad agreement with the beta distribution, both peaking near ~0.2, with 90\% 
-of BBH spins below \result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility. The regions of parameter space where they don't agree as well are at 
-the boundaries. The B-Spline model has no enforcement for vanishing support at the extremal values like the Beta distribution, 
+We model the spin magnitude distributions as IID B-Spline distributions as a flexible check to the assumptions of the \textsc{Default} model. 
+Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the B-Spline model, compared with the \textsc{Default} model. 
+The B-Spline model finds consistent agreement with the beta distribution, peaking near $a\sim0.2$, with 90\% of BBH spins below 
+\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility.
+The B-Spline model has no enforcement for vanishing support at the extremal values like the Beta distribution,
 allowing it to probe the zero-spin question. We find broad support, with large variance, for non-zero probabilities at $a_i=0$, but cannot confidently determine the presence of 
@@
 We now repeat the same analysis as above but with independent B-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
-we show the inferred primary (orange), and secondary (olive) spin magnitude distributions inferred when relaxing the IID assumption. We find both 
-distributions to be remarkably similar, showing no signs that each component spin magnitude are distributed differently from each other.
+we show the inferred primary (orange), and secondary (olive) spin magnitude distributions inferred when relaxing the IID assumption. We find that the primary spin magnitude distribution 
+peaking slightly higher at $a\sim0.25$ than the IID B-Spline model, but with similar support at near vanishing spins. The secondary spin magnitude distribution is more uncertain due to the 
+higher measurement uncertainty in inferring the secondary spins of BBH systems. The secondary distribution also peaks at smaller spin magnitudes of $a\sim0.15$, showing considerably larger 
+PPD and confidence band at $a\sim0$ than the primary distribution or B-Spline IID spin magnitude distribution in figure \ref{fig:iid_spinmag_dist}. While the distributions are still broadly 
+consistent with each other this could also be signs pointing towards component spin magnitude distributions uniquely distributed.
 
@@
 
-The \textsc{Default} spin model assumes the spin orientation of both components are identical and independently distributed (IID) mixture models over an
+The \textsc{Default} spin model also assumes the spin orientation of both components are identical and independently distributed (IID), with a mixture model over an
 aligned and an isotropic component. The aligned component is modeled with a truncated Gaussian distribution with mean at $\cos{\theta}=1$ and variance a free 
-hyperparameter to be fit. This provides a simple 2-parameter model motivated by simple distributions expected from the two main formation scenario families, allowing 
+hyperparameter to be fit \citep{Talbot_2017,Wysocki_2019,o3a_pop,o3b_astro_dist}.
+This provides a simple 2-parameter model motivated by simple distributions expected from the two main formation scenario families, allowing
 for a straightforward interpretation of results. One possible limitation however, is that by construction this distribution is forced to peak at perfectly aligned spins, 
@@
 used to model the spin orientation distribution and found considerable evidence that the distribution peaks away from $\cos{\theta}=1$. Again, this provides a clear 
-use-case where data-driven models can help in our understanding and possibly resolve disputes among differing parametric approaches.
+use-case where data-driven models can help in our understanding of and possibly resolve disputes among differing parametric approaches to modeling the spin orientation distribution.
 
@@
 
-We repeat the tests done above on the spin magnitude distributions now with the spin orientation distributions. Figure \ref{fig:iid_spintilt_dist} 
-shows the inferred spin magnitude distribution with the B-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
+Figure \ref{fig:iid_spintilt_dist} shows the inferred spin magnitude distribution with the IID spin B-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
 The B-Spline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
@@
 Now we model each of the components' orientation distributions with independent B-Spline models as done above, and show the inferred 
-primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distributions do not agree quite as well as 
-the magnitude distributions did in figure \ref{fig:ind_spinmag_dist}, and the PPDs look to peak at different values, but the wide uncertainties still are 
-consistent with both each other and the \textsc{Default} model's PPD.
+primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distributions do not match perfectly, but both are broadly
+are consistent with each other and the \textsc{Default} model's PPD given the wide credible intervals.
 We find the two distributions to peak at: $\cos{\theta_1}=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt1]}$}
@@
     from the minimum to the maximum observed redshifts. The solid line shows the population predictive distribution (PPD) and the shaded region, 
-    the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawRedshift} (blue) model from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
+    the 90\% credible interval. We show the inferred 90\% credible interval from the \textsc{PowerlawRedshift} model 
+    from the LVK's GWTC-3 population analyses in blue and a power law with exponent of 2.7 in gray, representing the expected star formation rate 
+    \citep{Madau_2014, o3b_astro_dist}.}
     \label{fig:rofz}

### 2022-10-11 src/tex/intro.tex
changes to absract and intro

@@
 
-Observations of gravitational waves (GWs) from compact binary coalescences (CBCs) are becoming a regular occurrence, 
-recently producing catalogs of 90 such detections \citep{GWTC1,gwtc2,GWTC3}. With this growing catalog size, we are steadily approaching a more complete  
-understanding of the population properties of CBCs, just 7 years after the first observation \citep{o1o2_pop,o3a_pop,o3b_astro_dist}. 
-Due to their increased sensitivity, detections could occur as often as every day in the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration 
-detectors \citep{aLIGO,aVIRGO,LVK_prospects}. This large influx of data will drastically improve our ability to study the population of observed CBCs by 
-combining the insights from the entire catalog. The history of these dense objects is imprinted on the properties 
-of the population  of CBCs, allowing us to learn about their formation and evolution from the last few seconds of gravitational radiation emitted \citep{Zevin_2017}. 
-The population distributions of merging compact objects inferred from gravitational-wave observations have been shown to be particularly useful in order to
-measure cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2}, 
-constrain a running Planck mass \citep{Lagos_runningPlanckMass}, look for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng}, 
+Observations of gravitational waves (GWs) from compact binary mergers are becoming a regular occurrence, 
+producing a catalog of events that recently surpassed 90 such detections \citep{GWTC1,gwtc2,GWTC3}.
+As the catalog continues to grow, so does our understanding of the underlying astrophysical population of compact binaries \citep{o1o2_pop,o3a_pop,o3b_astro_dist}.
+Following numerous improvements to the detectors since the last observing run, the anticipated sensitivities for the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration suggest detection rates as high as once per \emph{day} \citep{aLIGO,aVIRGO,LVK_prospects}.
+With the formation history of these dense objects encoded in the details of their distribution \citep{Zevin_2017}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics.
+Beyond formation physics, population-level inference of the compact binary catalog has also been shown to provide novel measurements of cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2},
+constrain a running Planck mass \citep{Lagos_runningPlanckMass}, search for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng}, 
 constrain stellar nuclear reaction rates \citep{Farmer_2019,Farmer_2020}, look for primordial black holes \citep{Ng_2021,KenNgPBH2022}, 
@@
 such as the peak at $m_1\sim10\,\msun$, only grew after analyzing the latest catalog, GWTC-3, with the same models \citep{o3b_astro_dist,Tiwari_2022ApJ}, illustrating  
-the usefulness of data-driven methods even with the relatively small current catalog size. Canonically, the approach to constructing population models has been 
-to use simple parametric models that aim to describe the data in the simplest way, build in astrophysically motivated priors, then sequentially add in 
-complexities only as the data demands. This simple approach is powerful in data-scarce, prior dominated environments; however, as we go forward into 
-the data-rich catalog era, flexible methods such as non-parametric modeling will be necessary to discover new features in the data that can quickly 
-become unwieldy to incorporate into the parametric approach. As opposed to parametric models, flexible and non-parametric models are data-driven and 
+the usefulness of data-driven methods even with the current catalog size. The cannonical approach to constructing population models has been 
+to use simple parametric descriptions (e.g., power laws, beta distributions) that aim to describe the data in the simplest way, employ astrophysically motivated priors where appropriate, then sequentially add
+complexities (e.g., gaussian peaks) as the data demands.
+This simple approach was necessary when data was scarce, but as we move into the data-rich catalog era, this approach is already failing to scale.
+More flexible and scalable methods, such as non-parametric modeling techniques, will be necessary to continue to extract the full information contained in the compact binary catalog.
+In contrast to parametric models, flexible and non-parametric models are data-driven and
 contribute little bias to functional form. Non-parametric or semi-parametric methods are particularly useful to search for unexpected features in the 
-data, providing meaningful insight of these features that parametric models may fail to capture. Development and robust testing of such flexible methods in the short 
-term will only provide knock on effects when the time comes to analyze the next catalog of CBC detections.
+data, providing meaningful insight of these features that parametric models may fail to capture.
 
-The spin distributions of BBHs are particularly interesting since the two main formation scenarios produce distinctly different spin distributions \bruce{cite}. 
-Isolated or field formation scenarios predict component spins that are preferentially aligned with the binaries orbital angular momentum, although some small 
-misalignment can occur depending on the nature of the supernova kicks as each star collapses to a compact object \bruce{cite}. Dynamical formation scenarios may occur in 
-dense environments where many-body interactions between many compact objects cause a binary to harden so that it will merge within a Hubble time. Thus, the dynamical 
-channel produces an isotropic spin tilt distribution \bruce{cite}. BBH spins have also been of controversial interest recently, with different parametric approaches to modeling 
-the spin distribution coming to different conclusions. The studies have disagreed on the possible existence of a significant zero-spinning subpopulation, along with the presence of 
+While we eventually hope to uncover hints of binary formation mechanisms in the mass spectrum of BBHs, the distribution of spin properties have been of particular interest.
+While the measurement of spin properties of individual binaries often have large uncertainties, theorized formation channels are expected produce distinctly different spin distributions \bruce{cite}.
+Isolated (or field) formation scenarios predict component spins that are preferentially aligned with the binary's orbital angular momentum, although some small 
+misalignment can occur depending on the nature of the supernova kicks as each star collapses to a compact object \bruce{cite}. Alternatively, dynamical formation in 
+dense environments where many-body interactions between compact objects can result in binary formation and hardening (shrinking of binary orbits) should produce binaries with components' spins distributed isotropically \bruce{cite}.
+BBH spins have also been of controversial interest recently, with different parametric approaches to modeling
+the spin distribution coming to different conclusions. Studies have disagreed on the possible existence of a significant zero-spinning subpopulation, as well as the presence of 
 significant spin misalignment (i.e. $\cos{\theta_i} < 0.0$) \citep{o3b_astro_dist,RouletGWTC2Pop,BuildBetterSpinModels,GWTC3MonashSpin,Callister_NoEvidence}. 
-Another study recently showed that the spin tilt distribution inference is sensitive to modeling choices and may not peak at perfectly aligned spins, as is often assumed \citep{spinitasyoulike}. 
-Other approaches to building improved models for BBH spins again, as with the mass models, focus on iterating through different simple parametric descriptions with 
-increasing complexities \citep{BuildBetterSpinModels,Callister_NoEvidence,spinitasyoulike}. The spin distributions offer a nice use case for flexible data-driven models, as 
-we present in this manuscript, both to help alleviate the current disputes in the literature and because there has been little work on flexible model development for the 
-spin distribution of BBHs beyond the aligned spin dimension thus far \citep{Tiwari_2021_a,Tiwari_2021_b}.
+Another study recently showed that inferences of spin misalignment (or tilts) are sensitive to modeling choices and may not peak at perfectly aligned spins, as is often assumed \citep{spinitasyoulike}.
+While enlightening,
+these recent efforts to improve BBH spin models continue to build sequentially on previous parametric descriptions \citep{BuildBetterSpinModels,Callister_NoEvidence,spinitasyoulike}.
+To ensure we are extracting the full detail the catalog has to offer, we extend our previous non-parametric modeling techniques to include spin magnitudes and tilts, as well as the binary mass ratio and redshift.
+%We present in this manuscript, both to help alleviate the current disputes in the literature and because there has been little work on flexible model development for the 
+%spin distribution of BBHs beyond the aligned spin dimension thus far \citep{Tiwari_2021_a,Tiwari_2021_b}.
 
@@
 In this paper we highlight how the use of basis-splines can provide a powerful non-parametric modeling approach to the astrophysical distributions of compact 
-binaries. We illustrate how one can efficiently model both the mass and spin distributions of merging compact binaries in GWTC-3 with basis splines to infer CBC population properties using 
+binaries. We illustrate how one can efficiently model both the mass and spin distributions of merging compact binaries in GWTC-3 with basis splines to infer compact binary population properties using 
 hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower 

### 2022-10-11 src/tex/macros.tex
changes to absract and intro

--- 2022-10-11 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "MSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXI\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVIII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.7}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.79}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.82}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.86}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{1.0}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{1.1}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.51}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.74}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.7}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{4.7}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{1.0}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.98}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.37}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIII@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIII@out\macros@XXXVIII\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XLIII\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XLVIII\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVI@out\macros@L\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@LI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@LIV\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LVII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.012}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.017}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.0089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.0034}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.0049}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.027}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.075}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.48}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.041}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.96}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.077}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.056}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.021}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.17}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.0072}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.0092}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.0057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.0015}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.018}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.0022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.016}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.097}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.35}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.055}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.019}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.027}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.081}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.77}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.7}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.045}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.0094}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.014}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.099}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.022}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.008}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.0026}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.035}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.0037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.024}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.19}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.21}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.39}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.071}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.065}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.23}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.83}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.42}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.78}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.066}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.05}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.22}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.023}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.15}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.0039}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.39}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.082}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.78}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.024}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{6.7}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{19}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{52}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{9.2}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{21}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{54}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{6.7}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{15}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{52}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0091, "5th percentile": 0.0039, "95th percentile": 0.03, "10th percentile": 0.0052, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.073, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.031, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.6, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.057, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.032, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0068, "error plus": 0.01, "error minus": 0.0053, "5th percentile": 0.0015, "95th percentile": 0.019, "10th percentile": 0.0023, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.25, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.16, "95th percentile": 0.38, "10th percentile": 0.18, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.031, "error minus": 0.036, "5th percentile": 0.017, "95th percentile": 0.083, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.23, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.76, "10th percentile": 0.36, "90th percentile": 0.71\}, "frac\_hm": \{"median": 0.043, "error plus": 0.065, "error minus": 0.033, "5th percentile": 0.0093, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.094\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0085, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0039, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.032, "error minus": 0.03, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.21, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.82, "10th percentile": 0.43, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.07, "error plus": 0.1, "error minus": 0.053, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VIII\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVIII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIV\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0091, "5th percentile": 0.0039, "95th percentile": 0.03, "10th percentile": 0.0052, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.073, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.031, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.6, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.057, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.032, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0068, "error plus": 0.01, "error minus": 0.0053, "5th percentile": 0.0015, "95th percentile": 0.019, "10th percentile": 0.0023, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.25, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.16, "95th percentile": 0.38, "10th percentile": 0.18, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.031, "error minus": 0.036, "5th percentile": 0.017, "95th percentile": 0.083, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.23, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.76, "10th percentile": 0.36, "90th percentile": 0.71\}, "frac\_hm": \{"median": 0.043, "error plus": 0.065, "error minus": 0.033, "5th percentile": 0.0093, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.094\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0085, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0039, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.032, "error minus": 0.03, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.21, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.82, "10th percentile": 0.43, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.07, "error plus": 0.1, "error minus": 0.053, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXVIII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@V@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXXI\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{25}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.1}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.7}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{45}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{5.9}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{52}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.79}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.82}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.86}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{1.1}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{1.0}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.51}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{0.74}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.7}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{4.7}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{70}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{5.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{51}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{1.0}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.98}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.37}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0091, "5th percentile": 0.0039, "95th percentile": 0.03, "10th percentile": 0.0052, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.073, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.031, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.6, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.057, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.032, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XXXVI\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.0068, "error plus": 0.01, "error minus": 0.0053, "5th percentile": 0.0015, "95th percentile": 0.019, "10th percentile": 0.0023, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.25, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.16, "95th percentile": 0.38, "10th percentile": 0.18, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.031, "error minus": 0.036, "5th percentile": 0.017, "95th percentile": 0.083, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.23, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.76, "10th percentile": 0.36, "90th percentile": 0.71\}, "frac\_hm": \{"median": 0.043, "error plus": 0.065, "error minus": 0.033, "5th percentile": 0.0093, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.094\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0085, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0039, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.032, "error minus": 0.03, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.21, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.82, "10th percentile": 0.43, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.07, "error plus": 0.1, "error minus": 0.053, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@XLVI\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVIII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVIII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVIII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVIII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVIII@out\macros@LI\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LIV\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LVII\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXXI@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXXI@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXXI@out\macros@LX\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.013, "error plus": 0.016, "error minus": 0.0091, "5th percentile": 0.0039, "95th percentile": 0.03, "10th percentile": 0.0052, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.0091}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.0039}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.0052}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.026}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.43, "error plus": 0.073, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.073}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.48}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.017, "error plus": 0.031, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.041}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.87, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.6, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.87}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.97}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.081, "error plus": 0.098, "error minus": 0.057, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.032, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.081}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.098}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.024}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.16}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.0068, "error plus": 0.01, "error minus": 0.0053, "5th percentile": 0.0015, "95th percentile": 0.019, "10th percentile": 0.0023, "90th percentile": 0.015\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.0068}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.0053}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.019}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.0023}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.015}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.25, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.16, "95th percentile": 0.38, "10th percentile": 0.18, "90th percentile": 0.36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.25}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.38}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.36}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.053, "error plus": 0.031, "error minus": 0.036, "5th percentile": 0.017, "95th percentile": 0.083, "10th percentile": 0.025, "90th percentile": 0.079\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.053}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.079}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.76, "10th percentile": 0.36, "90th percentile": 0.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.36}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.71}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.043, "error plus": 0.065, "error minus": 0.033, "5th percentile": 0.0093, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.094\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.043}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.065}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.033}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.0093}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.015}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.094}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.011, "error plus": 0.016, "error minus": 0.0085, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0039, "90th percentile": 0.025\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.0085}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.0027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.029}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.0039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.025}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.22}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.38}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.041, "error plus": 0.032, "error minus": 0.03, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.032}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.065}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.61, "error plus": 0.21, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.82, "10th percentile": 0.43, "90th percentile": 0.77\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.21}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.82}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.77}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.07, "error plus": 0.1, "error minus": 0.053, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.053}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.15}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.0039}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.39}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.082}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.78}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.024}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{6.7}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{19}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{52}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{9.2}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{21}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{54}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{6.7}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{15}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{52}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\makeatother

### 2022-10-11 src/tex/ms.tex
changes to absract and intro

@@
 \begin{abstract}                 
-We introduce the first complete non-parametric models for the astrophysical distribution of the binary black hole (BBH) population.
-Using the 69 confident observations in GWTC-3, we present the most comprehensive data-driven investigation of the BBH population to date, including BBH mass ratio, spin magnitudes and misalignments, and redshift.
-We report the same features previously recovered
+We introduce the first complete non-parametric model for the astrophysical distribution of the binary black hole (BBH) population.
+Constructed from basis splines, we use these models to conduct the most comprehensive data-driven investigation of the BBH population to date, including non-parametric modeling of BBH mass ratio, spin magnitudes and misalignments, and redshift distributions for the first time.
+Using the 69 confident BBHs in GWTC-3, we report the same features previously recovered
 with similarly flexible models of the mass distribution, most notably the peaks in merger rates at primary masses of ${\sim}10\msun$ and ${\sim}35\msun$.

### 2022-10-11 src/scripts/plot_ind_spintilt.py
update plot scripts

@@ -8,7 +8,7 @@ from utils import plot_mean_and_90CI, plot_o3b_spintilt, load_ind_tilt_ppd
 figx, figy = 7,5
 fig, ax = plt.subplots(nrows=1, ncols=1, sharey='row', sharex='row', figsize=(figx,figy))
 lab='cos_tilt_1'
-ax = plot_o3b_spintilt(ax,'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_orientation_data.h5', ct1=lab=='cos_tilt_1', lab='Default', col='tab:blue')
+ax = plot_o3b_spintilt(ax,'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_orientation_data.h5', ct1=lab=='cos_tilt_1', lab='Abbott et. al. 2021b', col='tab:blue')
 
 xmin, xmax = -1, 1
 xs, ct1_pdfs, ct2_pdfs = load_ind_tilt_ppd()
@@ -18,7 +18,11 @@ for i in range(len(ct1_pdfs)):
 xmin=-1
 maxy=0
 for ps, lab, c in zip([ct1_pdfs, ct2_pdfs], ['cos_tilt_1', 'cos_tilt_2'],  ['tab:orange', 'tab:olive']):
-    ax = plot_mean_and_90CI(ax, xs, ps, color=c, label=f'MSpline-{lab}')
+    if lab == 'cos_tilt_1':
+        label=r'This Work ($p(\cos{\theta_1})$)'
+    else:
+        label=r'This Work ($p(\cos{\theta_2})$)'
+    ax = plot_mean_and_90CI(ax, xs, ps, color=c,label=label)
     high = np.percentile(ps, 95, axis=0)
     if max(high) > maxy:
         maxy = max(high)
@@ -28,11 +32,11 @@ ax.set_ylabel(r'$p(\cos{\theta})$', fontsize=18)
 
 ax.set_xlim(xmin, xmax)
 
-ax.set_ylim(0, maxy)
-ax.legend(frameon=False, fontsize=14);
+ax.set_ylim(0, 2)
+ax.legend(frameon=False, fontsize=14, loc='upper left');
 ax.grid(True, which="major", ls=":")
 ax.tick_params(labelsize=14)
     
-plt.title(f'GWTC-3: MSpline Spin Tilt Distribution', fontsize=18);
[…]

### 2022-10-11 src/tex/appendicies.tex
fix up appendix and model/prior table

@@
 \begin{eqnarray}
-\tau_\lambda \sim \Gamma(a, b) \\
-p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D}_{r}^{\mathrm{T}} \bm{D}_r \bm{c}  \big] e^{-n\bm{c}}
+\bm{c} \sim \mathcal{N}(0, \sigma) \\
+p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D}_{r}^{\mathrm{T}} \bm{D}_r \bm{c}  \big] 
 \end{eqnarray}
 
-\noindent Above $\bm{D}_r$ is the order-$r$ difference matrix, of shape $(n-r \times n)$ and $\Gamma(a,b)$ the Gamma distribution with shape parameters, $a$ and $b$. 
-This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. The $\tau_\lambda$ controls the ``strength'' of 
-smoothing, or the inverse variance of the Gaussian priors on knot differences. When there are a very large number of knots, 
-such that your domain is densely populated with basis coefficients, this allows the freedom for the model to find the smoothing 
-scale that the data prefers. One downside of this prior specification as noted in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}, is the dependence on 
-one's choice of value for the $b$ hyperparameter in the Gamma distribution for $\tau_\lambda$. The models introduced in \citet{Jullion2007RobustSO} show how 
-to alleviate this. W model $\tau_\lambda$ with a mixture model composed of multiple Gamma distributions each with varying values for $b$. 
-With this we now have the full prior on $\tau_\lambda$ as:
+\noindent Above $\bm{D}_r$ is the order-$r$ difference matrix, of shape $(n-r \times n)$, and $\mathcal{N}(0,\sigma)$ a Gaussian distribution with zero mean 
+and standard deviation, $\sigma$. This smoothing prior removes the strong dependence on number and location of knots that arises with using splines. 
+The $\tau_\lambda$ controls the ``strength'' of the smoothing, or the inverse variance of the Gaussian priors on knot differences. We 
+place uniform priors on $\tau_\lambda$ marginalize over this smoothing scale hyperparameter to let the data inform the optimal scale needed.
+When there are a very large number of knots, such that your domain is densely populated with basis coefficients, this allows the freedom for the model to find the smoothing 
+scale that the data prefers.
 
-\begin{align}
-    \bm{p} \sim \mathcal{D}(m) \\
-    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_i)
-\end{align}
+%One downside of this prior specification as noted in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}, is the dependence on 
+%one's choice of value for the $b$ hyperparameter in the Gamma distribution for $\tau_\lambda$. The models introduced in \citet{Jullion2007RobustSO} show how 
+%to alleviate this. W model $\tau_\lambda$ with a mixture model composed of multiple Gamma distributions each with varying values for $b$. 
+%With this we now have the full prior on $\tau_\lambda$ as:
 
-\noindent Above $\mathcal{D}(m)$, denotes a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
-and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.
+%\begin{align}
+%    \bm{p} \sim \mathcal{D}(m) \\
+%    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_i)
+%\end{align}
+
+%\noindent Above $\mathcal{D}(m)$, denotes a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
+%and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.
 
@@
 
+\begin{table*}[hb!]
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+    \hline
+    \textbf{Model} & \textbf{Parameter} & \textbf{Description} & \textbf{Prior} \\ \hline \hline
+    \multicolumn{4}{|c|}{\textbf{Primary Mass Model Parameters}} \\ \hline
+    \textsc{B-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,100) \\ \cline{2-4}
+     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 64 \\ \cline{2-4} 
+    \multicolumn{4}{|c|}{\textbf{Mass Ratio Model Parameters}} \\ \hline
+    \textsc{B-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
+     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 18 \\ \cline{2-4}  
+    \multicolumn{4}{|c|}{\textbf{Redshift Evolution Model Parameters}} \\ \hline
+    \textsc{PowerLaw+B-Spline} & $\lambda$ & slope of redshift evolution power law $(1+z)^\lambda$ &  $\sim \mathcal{N}(0,3)$ \\ \cline{2-4}
+    & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
+     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 16 \\ \cline{2-4} 
+    \multicolumn{4}{|c|}{\textbf{Spin Distribution Model Parameters}} \\ \hline
+    \textsc{B-Spline Magnitude} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
+    & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
+    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 18 \\ \cline{2-4} 
+    \textsc{B-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
+    & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
+    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 16 \\ \cline{2-4} 
+    \end{tabular}
+    \caption{All hyperparameter prior choices for each of the newly introduced basis spline models from this manuscript. See appendix 
+    \ref{sec:basis_splines} and \ref{sec:psplines} for more detailed description of basis spline or smoothing prior parameters.}
+    \label{tab:model_priors}
+\end{table*}
+
 We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
@@
 
-\begin{table*}[ht!]
-    \centering
-    \begin{tabular}{|l|l|l|l|}
-    \hline
-    \textbf{Model} & \textbf{Parameter} & \textbf{Description} & \textbf{Prior} \\ \hline \hline
-    \multicolumn{4}{|c|}{\textbf{Primary Mass Model Parameters}} \\ \hline
-    \textsc{M-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
-     & $\tau_\lambda$ & Smoothing Prior Scale & $\sum_i^m p_i \Gamma(1, b_i)$ \\ \cline{2-4}
-     & $\bm{p}$ & Hyper-Parameter weights on smoothing scale mixture prior & $\sim \mathcal{D}(m)$ \\ \cline{2-4}
-     & $b_m$ & array of different concentration parameters for $\Gamma$ distribution & equal in $[10^{-9},10^{-1}]$ \\ \cline{2-4} 
-     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-     & $n$ & number of knots in the basis spline & 50 \\ \cline{2-4} 
-     & $m$ & number of mixture components for prior on $\tau_\lambda$ & 24  \\ \hline \hline
-    \multicolumn{4}{|c|}{\textbf{Mass Ratio Model Parameters}} \\ \hline
-    \textsc{PowerLaw Mass Ratio} & $\beta$ & slope of the mass ratio power law & $\sim \mathcal{N}(0,2)$ \\ \cline{2-4} 
-    & $m_\mathrm{min}$ & minimum BH mass & 3\msun  \\ \hline \hline    
-    \multicolumn{4}{|c|}{\textbf{Redshift Evolution Model Parameters}} \\ \hline
-    \textsc{PowerLaw Redshift} & $\lambda$ & slope of redshift evolution power law $(1+z)^\lambda$ &  $\sim \mathcal{N}(0,2)$ \\ \hline \hline
-    \multicolumn{4}{|c|}{\textbf{Spin Distribution Model Parameters}} \\ \hline
-    \textsc{M-Spline Magnitude} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
-    & $\tau_\lambda$ & Smoothing Prior Scale & $\sum_i^m p_i \Gamma(1, 10^{-3})$ \\ \cline{2-4}
-    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-    & $n$ & number of knots in the basis spline & 16 \\ \hline
-    \textsc{M-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
-    & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \Gamma(1, 10^{-3})$ \\ \cline{2-4}
-    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-    & $n$ & number of knots in the basis spline & 16 \\ \hline
-    \textsc{M-Spline Effective} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
-    & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \Gamma(1, 10^{-3})$ \\ \cline{2-4}
-    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-    & $n$ & number of knots in the basis spline & 24 \\ \hline
-    \end{tabular}
-\end{table*}
-
-\bruce{Need to fill this section in and put tables with specific hyperparameter/prior settings made}
-
-%\section{Validation Studies} \label{sec:validation}
-
-%bruce{Need to fill this section}
+For each of the distributions with basis spline distributions, we have 2 fixed hyperparameters to specify. The number of degrees of freedom, $n$, and the difference 
+penalty order for the smoothing prior, $r$. Additionally, one must choose a prior distribution on the smoothing prior scale hyperparameter, $\tau_\lambda$, which we take to be Uniform. 
+For the primary mass distribution we model the log probability with a B-Spline interpolated in $\log(m_1)$ space. We follow a similar scheme for the models in mass ratio and spin, but since 
+these parameters have natural hard boundaries we model the log probability with B-Splines interpolated in $q$, $a_i$ or $\cos{\theta_i}$ space. The 
+redshift distribution is also lacking of a natural upper boundary, which we mitigate by using a semi parametric approach where B-Splines model modulations to the 
+simpler underlying \textsc{PowerlawRedshift} model. We both these B-Spline modulations in log probability interpolated in $\log z$ space. We enumerate each of our specific model hyperparameter 
+and prior choices in table \ref{tab:model_priors}.

### 2022-10-11 src/tex/methods.tex
fix up appendix and model/prior table

@@
 For the spin magnitude and tilt distributions we construct two versions of the model: first, we model  
-each component's distribution is independently and identically distribution (IID), where we have a single B-Spline model and parameters (coefficients) for each binary spin. 
+each component's distribution as independently and identically distribution (IID), where we have a single B-Spline model and parameters (coefficients) for each binary spin. 
 Secondly, we model each component's distribution to be unique, fitting separate sets of coefficients for the B-Spline models of the primary and secondary spin distributions. 

### 2022-10-11 src/tex/appendicies.tex
Fix Table

@@
     \multicolumn{4}{|c|}{\textbf{Primary Mass Model Parameters}} \\ \hline
-    \textsc{B-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+    \textsc{B-Spline Primary} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
      & $\tau_\lambda$ & Smoothing Prior Scale & U(1,100) \\ \cline{2-4}
      & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-     & $n$ & number of knots in the basis spline & 64 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 64 \\ \hline \hline 
     \multicolumn{4}{|c|}{\textbf{Mass Ratio Model Parameters}} \\ \hline
-    \textsc{B-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+    \textsc{B-Spline Ratio} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
      & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
      & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-     & $n$ & number of knots in the basis spline & 18 \\ \cline{2-4}  
+     & $n$ & number of knots in the basis spline & 18 \\ \hline \hline
     \multicolumn{4}{|c|}{\textbf{Redshift Evolution Model Parameters}} \\ \hline
@@
      & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-     & $n$ & number of knots in the basis spline & 16 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 16 \\ \hline \hline 
     \multicolumn{4}{|c|}{\textbf{Spin Distribution Model Parameters}} \\ \hline
@@
     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-    & $n$ & number of knots in the basis spline & 18 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 18 \\ \hline \hline 
     \textsc{B-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
@@
     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-    & $n$ & number of knots in the basis spline & 16 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 16 \\ \hline \hline
     \end{tabular}

### 2022-10-11 src/tex/conclusion.tex
add more citations -- remove \bruce{} flags

@@
 The results presented in section \ref{sec:mass_dist} illustrate a much wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}. 
-While isolated formation is able to predict the $10\msun$ peak \bruce{cite}, cluster and dynamical formation scenarios struggle to predict a peak in the BH mass distribution less than 
-$15-20\msun$ \bruce{cite}. Globular cluster formation is expected to produce more top-heavy mass distributions than isolated and recent studies have shown suppressed BBH merger rates 
-at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \bruce{cite}. BBHs that form near active galactic nuclei (AGN) can preferentially produce higher 
-mass black holes \bruce{cite}. We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts 
+While isolated formation is able to predict the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict a peak in the BH mass distribution less than 
+$15-20\msun$ \citep{Hong_2018, Rodriguez_2019}.
+Globular cluster formation is expected to produce more top-heavy mass distributions than isolated and recent studies have shown suppressed BBH merger rates
+at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \citep{Rodriguez_2015, Rodriguez_2019, BaveraMassTransfer,Belczynski_2016}.
+BBHs that form near active galactic nuclei (AGN) can preferentially produce higher
+mass black holes \citep{FordAGN, Tagawa_2021, Yang_2019}.
+We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts
 due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017}.

### 2022-10-11 src/tex/intro.tex
add more citations -- remove \bruce{} flags

@@
 such as the peak at $m_1\sim10\,\msun$, only grew after analyzing the latest catalog, GWTC-3, with the same models \citep{o3b_astro_dist,Tiwari_2022ApJ}, illustrating  
-the usefulness of data-driven methods even with the current catalog size. The cannonical approach to constructing population models has been 
+the usefulness of data-driven methods even with the current catalog size. The canonical approach to constructing population models has been 
 to use simple parametric descriptions (e.g., power laws, beta distributions) that aim to describe the data in the simplest way, employ astrophysically motivated priors where appropriate, then sequentially add
-complexities (e.g., gaussian peaks) as the data demands.
+complexities (e.g., Gaussian peaks) as the data demands.
 This simple approach was necessary when data was scarce, but as we move into the data-rich catalog era, this approach is already failing to scale.
@@
 While we eventually hope to uncover hints of binary formation mechanisms in the mass spectrum of BBHs, the distribution of spin properties have been of particular interest.  
-While the measurement of spin properties of individual binaries often have large uncertainties, theorized formation channels are expected produce distinctly different spin distributions \bruce{cite}.
+The measurement of spin properties of individual binaries often have large uncertainties, but the theorized formation channels are expected to produce distinctly 
+different spin distributions \citep{Farr_BinnedSpin, Farr2017Nature, Zevin_2017}.
 Isolated (or field) formation scenarios predict component spins that are preferentially aligned with the binary's orbital angular momentum, although some small
-misalignment can occur depending on the nature of the supernova kicks as each star collapses to a compact object \bruce{cite}. Alternatively, dynamical formation in 
-dense environments where many-body interactions between compact objects can result in binary formation and hardening (shrinking of binary orbits) should produce binaries with components' spins distributed isotropically \bruce{cite}.
+misalignment can occur depending on the nature of the supernova kicks as each star collapses to a compact object \citep{Zevin_2022, BaveraBBHSpin, BaveraMassTransfer}.
+Alternatively, dynamical formation in
+dense environments where many-body interactions between compact objects can result in binary formation and hardening (shrinking of binary orbits) should produce binaries with components' spins distributed isotropically \citep{Rodriguez_2016, Rodriguez_2019}.
 BBH spins have also been of controversial interest recently, with different parametric approaches to modeling

### 2022-10-11 src/tex/methods.tex
update some methods and results

@@
 
-We construct our data-driven model with the application of basis splines, or B-Splines \citep{deBoor78}. B-Splines of order $k$, are a set of order $k-1$ polynomials that 
-span the space of possible spline functions interpolated from a given set of knot locations. The basis representation of the splines allows for the computational 
+We construct our data-driven model with the application of basis splines, or B-Splines \citep{deBoor78}. B-Splines of order $k$ are a set of order $k-1$ polynomials that 
+span the space of possible spline functions interpolated from a given set of knot locations. The basis representation of the splines allows for the computationally
 expensive interpolation to be done in a single preprocessing step -- amortizing the cost of model evaluation during inference. To mitigate the unwanted side effects of 
-adding extra knots and to avoid running a model grid of differing numbers of knots (as in \citet{Edelman_2022ApJ}), we use the smoothing prior for Bayesian P-Splines, 
-allowing the data to pick the optimal scale needed to fit the present features \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO}. We discuss basis splines, the smoothing prior 
-and our specific prior choices on hyperparameters in Appendix \ref{sec:basis_splines}, \ref{sec:psplines} and \ref{sec:modelpriors}.
+adding extra knots and to avoid running a model grid of differing numbers of knots (as in \citet{Edelman_2022ApJ}), we use the smoothing prior for Bayesian P-Splines \citep{eilers2021practical,BayesianPSplines,Jullion2007RobustSO},
+allowing the data to pick the optimal scale needed to fit the present features.
+We discuss basis splines, the smoothing prior, and our specific prior choices on hyperparameters in Appendix \ref{sec:basis_splines}, \ref{sec:psplines} and \ref{sec:modelpriors}.
 
-We parameterize each binaries' masses with the primary (more massive component) mass 
-and the mass ratio ($q=\frac{m_2}{m_1}$), bounded in the range from 0 to 1. Furthermore, we model 4 of the 6 total 
-spin degrees of freedom of a binary merger with each component spin magnitude $a_1$ and $a_2$, along with the cosine of the tilt angle of each component, 
-$\cos{\theta_1}$ and $\cos{\theta_2}$. The tilt angle is defined as the angle between each components' spin vector and the binaries orbital angular momentum vector. 
+We parameterize each binaries' masses with the primary (more massive component) mass ($m_1$) 
+and the mass ratio ($q=m_2/m_1$) with support from 0 to 1. Furthermore, we model 4 of the 6 total 
+spin degrees of freedom of a binary merger: component spin magnitudes $a_1$ and $a_2$, and (cosine of) the tilt angles of each component, $\cos{\theta_1}$ and $\cos{\theta_2}$.
+The tilt angle is defined as the angle between each components' spin vector and the binary's orbital angular momentum vector.
 We assume the polar spin angles are uniformly distributed in the orbital plane. For the primary mass distribution, we model the log probability with a B-Spline interpolated over 
 knots linearly spaced in $\log(m_1)$ in the range of support given our observations ($[6.5\msun-100\msun]$), such that $\log(p(m_1 | \bm{c})) \propto B_{k}(\log(m_1) | \bm{c})$, where $B_{k}$ is the 
-$k$-th order B-Spline function with basis coefficients, $\bm{c}$. We follow the same procedure for the models in mass ratio and spin distributions with knots spaced linearly across each domain, 
+$k$-th order B-Spline function with basis coefficients $\bm{c}$. We follow the same procedure for the models in mass ratio and spin distributions with knots spaced linearly across each domain 
 so that we have $\log(p(\theta | \bm{c}_\theta)) \propto B_{k}(\theta | \bm{c}_\theta)$, where $\theta$ can be $q$, $a_1$, $a_2$, $\cos{\theta_1}$ or $\cos{\theta_2}$. 
@@
 Lastly, we fit a population model on the redshift or luminosity distance distribution of BBHs, assuming a $\Lambda\mathrm{CDM}$ cosmology defined by the parameters 
-from the Planck 2015 results \citep{Planck2015}. This defines an analytical mapping between each event's inferred luminosity distance, and it's redshift, which we now use interchangeably. 
+from the Planck 2015 results \citep{Planck2015}. This defines an analytical mapping between each event's inferred luminosity distance, and its redshift, which we now use interchangeably. 
 We take a semi-parametric approach to model the evolution of the merger rate with redshift, following \citet{Edelman_2022ApJ}, that parameterizes modulations to an underlying model 
-with splines (in our case basis Splines). We use the \textsc{PowerlawRedshift} model as the underlying distribution to modulate, which has a single hyperparameter, $\lambda_z$, and 
+with splines (in our case basis splines). We use the \textsc{PowerlawRedshift} model as the underlying distribution to modulate, which has a single hyperparameter, $\lambda_z$, and 
 probability density defined as: $p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$ \citep{Fishbach_2018redshift}. For more detailed descriptions of each model and 
-specific prior choices used for the hyperparameters fit in Appendix \ref{sec:modelpriors}. Now that we have our comprehensive data-driven population model over 
+specific prior choices used for the hyperparameters see Appendix \ref{sec:modelpriors}. Now that we have our comprehensive data-driven population model over 
 each of the 7 modeled parameters built, we fit our model using the usual hierarchical Bayesian inference framework (see appendix \ref{sec:hierarchical_inference} for a review) in order to characterize

### 2022-10-11 src/tex/results.tex
fix dash range
update some methods and results

@@
 
-We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin and redshift distributions of 
+We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin, and redshift distributions of 
 binary black holes (BBHs) given a catalog of gravitational wave observations. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
@@
 the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
-a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer its population properties. Our study provides the first comprehensive 
-data-driven investigation of the BBH mass, spin and redshift distributions, uncovering new insights and corroborating those found with other methods. 
-We start by looking towards our model's inferences of the mass distribution.
+a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer population properties. Our study provides the first comprehensive 
+data-driven investigation of the BBH mass, spin, and redshift distributions, uncovering new insights and corroborating those found with other methods. 
+We start with our inference of the mass distribution.
 
@@
         \caption{The marginal primary mass distribution inferred with the B-Spline model (red), with 64 knots spaced linearly in $\log m_1$, from 6.5\msun 
-        to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
+        to 100\msun. The solid line shows the population predictive distribution (PPD), and the shaded region 
         the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models 
@@
 
-Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see that it recovered consistent 
-features with what was inferred with the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}. 
-In particular our B-Spline model finds a peak in merger rate density as a function of primary mass, at both $\sim10\msun$ and $\sim35\msun$ agreeing with those 
-reported using the same dataset in \citet{o3b_astro_dist}. The B-Spline model finds the same feature at $\sim18\msun$ as the \textsc{PowerlawSpline} model, but also 
-agreeing with the \textsc{PowerlawSpline} model, the mass distribution is more uncertain and less constrained in this region than other two confident peaks found.
-Additionally, there is some disagreement at low masses where the models based on power laws show a much higher rate below $\sim8--9\msun$. This is partly due to  
-the minimum mass hyperparameter, which is where the power law ``begins'' in those models. They enforce this hyperparameter as the minimum allowable primary and secondary 
-masses of the catalog. This leads to inferences of $m_\mathrm{min}$ below the minimum observed primary mass in the catalog, $\sim 6.4\msun$, to account for secondary BBH masses 
-that can possibly get to as low as $\sim 3\msun$. Since non-parametric models do not provide meaningful insights where there is no data - we enforce the minimum primary mass of 
-our B-Spline model to be $6.5\msun$, while secondary BBH masses are enforced to be greater than $3\msun$. The lack of observations in the low primary mass region could 
-point towards signs of a decrease in merger rate from a purported ``lower mass gap'' between neutron star and BH masses, or could be a feature of selection effects which make it 
-more unlikely to observe BBHs in that region of parameter space due to small sensitive volumes probed. We also find no evidence for a sharp fall off in merger rate either following 
-the pileup at $\sim35\,\msun$, which is expected if such a pileup was due to pulsational pair instability supernovae (PPISNe), or where the maximum mass truncation of the power law models 
-is inferred. The lack of any high mass truncation along with the most significant peak found to be at $\sim35\msun$, significantly lower than expected, may pose challenges for conventional stellar 
-evolution theory. This could be hinting at the significant presence of subpopulations that avoid PISN during binary formation, but the confirmation of the existence of such subpopulations 
-cannot be determined with current catalog sizes.
+Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see features consistant with those inferred by the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}.
+In particular our B-Spline model finds peaks in merger rate density as a function of primary mass at both $\sim10\msun$ and $\sim35\msun$, agreeing with those 
+reported using the same dataset in \citet{o3b_astro_dist}.
+The B-Spline model finds the same feature at $\sim18\msun$ as the \textsc{PowerlawSpline} model, but remains consistent with the \textsc{PowerlawSpline} model; the mass distribution is more uncertain in this region.
+We find the largest disagreement at low masses, where the power-law-based models show a higher rate below ${\sim}8-9\msun$.
+This is partly due to the minimum mass hyperparameter (where the power law ``begins'') serving as the minimum allowable primary and secondary masses of the catalog.
+This leads to inferences of $m_\mathrm{min}$ below the minimum observed primary mass in the catalog, $\sim 6.4\msun$, to account for secondary BBH masses
+that can possibly get as low as $\sim 3\msun$. We choose a minimum primary mass for 
+the B-Spline model to be $6.5\msun$, while secondary masses are enforced to be greater than $3\msun$.
+The lack of observations of binaries with low primary mass make rate estimates in this region strongly model and prior dependent.
+We could be seeing signs of a decrease in merger rate from a ``lower mass gap'' between neutron star and BH masses, or we could be seeing fluctuations due to low-number statistics.
+Either way we explect this to be resolved with future catalog updates.
+We also find no evidence for a sharp fall off in merger rate either following
+the pileup at $\sim35\,\msun$ -- expected if such a pileup was due to pulsational pair instability supernovae (PPISNe) -- or where the maximum mass truncation of the power law models 
+are inferred. The lack of any high mass truncation, along with the peak at $\sim35\msun$ (significantly lower than expected from PPISNe) may pose challenges for conventional stellar 
+evolution theory. This could be hinting at the presence of subpopulations that avoid pair instability supernovae during binary formation, but the confirmation of the existence of such subpopulations 
+cannot be determined with the current catalog.
 

### 2022-10-11 src/tex/conclusion.tex

@@
 waves \citep{B_Farr_etal_2014,Littenberg_2015,Mandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
-We presented a case study exploring how basis splines make for an especially powerful and efficient model-agnostic probe of the binary black hole population observed 
-with gravitational waves. With the coming influx of new data with the LVK's next observing run, and the wide range of questions in astrophysics and cosmology that a better 
-understanding of the black hole population will uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
+We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 
+with gravitational waves. Our study paved the way as the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
+modeled population distributions. A complete understanding of the population properties of compact objects will help to advance poorly understood areas of stellar and 
+nuclear astrophysics and provide a novel independent cosmological probe. With the coming influx of new data with the LVK's next observing run and the wide 
+range of research avenues the compact object population will help to uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
 sense of the data.

### 2022-10-11 src/tex/results.tex
fix spelling/typos

@@
 
-Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see features consistant with those inferred by the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}.
+Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see features consistent with those inferred by the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}.
 In particular our B-Spline model finds peaks in merger rate density as a function of primary mass at both $\sim10\msun$ and $\sim35\msun$, agreeing with those 
@@
 We could be seeing signs of a decrease in merger rate from a ``lower mass gap'' between neutron star and BH masses, or we could be seeing fluctuations due to low-number statistics.
-Either way we explect this to be resolved with future catalog updates.
+Either way we expect this to be resolved with future catalog updates.
 We also find no evidence for a sharp fall off in merger rate either following

### 2022-10-11 src/tex/results.tex
remove sentance about fitting chieff with splines

@@
 PPD and confidence band at $a\sim0$ than the primary distribution or B-Spline IID spin magnitude distribution in figure \ref{fig:iid_spinmag_dist}. While the distributions are still broadly 
-consistent with each other this could also be signs pointing towards component spin magnitude distributions uniquely distributed.
+consistent with each other this could also be signs pointing towards component spin magnitude distributions being uniquely distributed.
 
@@
 are not measured well during individual event parameter estimation. The best measured spin parameter, that enters the waveform at XXPN, is 
-called the effective spin defined as: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$. As an alternative check 
-on the spin distributions we also try modeling an B-Spline distribution of effective spins instead of component spin magnitude and tilts 
-as done above. Figure \ref{fig:chieff_dist} shows the inferred effective spin distribution with the B-Spline models (red and purple) 
-along with results on the \textsc{Default} and \textsc{Gaussian} models. We find considerable agreement 
+called the effective spin defined as: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$. Figure \ref{fig:chieff_dist} 
+shows the inferred effective spin distribution with the two versions of our B-Spline models (red and purple), 
+along with results on the \textsc{Default} and \textsc{Gaussian} models from \citet{o3b_astro_dist}. We find considerable agreement 
 among the effective spin distributions, but the more flexible B-Spline models in component spins, more closely resemble the \textsc{Gaussian} 

### 2022-10-11 src/tex/results.tex
update spin magnitude results text

--- 2022-10-11 src/tex/results.tex
@@
 We also find no evidence for a sharp fall off in merger rate either following
-the pileup at $\sim35\,\msun$ -- expected if such a pileup was due to pulsational pair instability supernovae (PPISNe) -- or where the maximum mass truncation of the power law models 
+the pileup at ${\sim}35\,\msun$ -- expected if such a pileup was due to pulsational pair instability supernovae (PPISNe) -- or where the maximum mass truncation of the power law models 
 are inferred. The lack of any high mass truncation, along with the peak at $\sim35\msun$ (significantly lower than expected from PPISNe) may pose challenges for conventional stellar 
@@
     \caption{The marginal mass ratio distribution inferred with the B-Spline model (red), with 18 knots spaced linearly in $q$, from 0.03 to 1.
-    The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
-    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's 
-    GWTC-3 population analyses \citep{o3b_astro_dist}.}
+The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
+    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
     \label{fig:q_distribution}
@@
 
-We report the B-Spline model's inferred marginal mass ratio distribution in figure \ref{fig:q_distribution}, where we can begin to see departure from a simple 
-power law. Specifically there looks to be a small decrease or flattening of the merger rate near equal mass ratios, as well as a fatter tail towards unequal mass ratios 
-than the power law based models find. Then we see a small decline to flat plateau from $q\sim0.3$ to $q\sim0.7$. The sharp decrease in rate just below 
-$q\sim0.3$ is due to the minimum mass ratio truncation defined by: $q_\mathrm{min}=\frac{m_\mathrm{min}}{m_1}$. When marginalizing over the primary mass 
+The marginal mass ratio distribution inferred by the B-spline model is shown in figure \ref{fig:q_distribution}.
+These results suggest we may be seeing the first signs of departure from a simple power law behavior.
+We find a potential plateau or decrease in the merger rate near equal mass ratios, as well as a broader tail towards unequal mass ratios
+than the power law based models find. Our results also suggest a shallower slope from $q\sim0.3$ to $q\sim0.7$, though uncertainty is larger in this region. The sharp decrease in rate just below 
+$q\sim0.3$ is due to the minimum mass ratio truncation defined by $q_\mathrm{min}=\frac{m_\mathrm{min}}{m_1}$. When marginalizing over the primary mass 
 distribution with a strong peak at $10\msun$, the mass ratio distribution truncates at $q\sim0.3$: the minimum secondary mass, $3\msun$, 
-divided by the most common primary mass, $\sim10\msun$.
+divided by the most common primary mass, ${\sim}10\msun$.
 
@@
         \includegraphics[width=\linewidth]{figures/iid_spinmag.pdf}
-        \caption{The spin magnitude distribution inferred with the B-Spline model (red), with 16 knots spaced linearly from 0 to 1, and 
-        assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
-        We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        \caption{The spin magnitude distribution inferred with the B-Spline model (red) with 16 knots spaced linearly from 0 to 1, assuming the components are IID.
+The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
+        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:iid_spinmag_dist}
@@
 
-The \textsc{Default} spin model describes the spin magnitude of both components as identical and independently distributed (IID) non-singular Beta distributions \citep{Talbot_2017,Wysocki_2019}.
+The \textsc{Default} spin model (used by \citet{o3b_astro_dist}) describes the spin magnitude of both components as identical and independently distributed (IID) non-singular Beta distributions \citep{Talbot_2017,Wysocki_2019}.
 The Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 
@@
         \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
-        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model, 
-        with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
-        We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model
+        with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
+        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:ind_spinmag_dist}
@@
 
-We model the spin magnitude distributions as IID B-Spline distributions as a flexible check to the assumptions of the \textsc{Default} model. 
+We model the spin magnitude distributions as IID B-Spline distributions as a check to the assumptions of the \textsc{Default} model. 
 Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the B-Spline model, compared with the \textsc{Default} model. 
-The B-Spline model finds consistent agreement with the beta distribution, peaking near $a\sim0.2$, with 90\% of BBH spins below 
-\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility.
-The B-Spline model has no enforcement for vanishing support at the extremal values like the Beta distribution,
+The B-Spline model results are consistent with those using the Beta distribution, peaking near $a\sim0.2$, with 90\% of BBH spins below 
+\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][a_90percentile]}$} at 90\% credibility. The B-Spline model does not impose vanishing support at the extremal values like the Beta distribution, 
 allowing it to probe the zero-spin question. We find broad support, with large variance, for non-zero probabilities at $a_i=0$, but cannot confidently determine the presence of 
 a significant non-spinning subpopulation, corroborating similar recent conclusions \citep{BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}. 
-We now repeat the same analysis as above but with independent B-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
+We repeat the same analysis with independent B-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
 we show the inferred primary (orange), and secondary (olive) spin magnitude distributions inferred when relaxing the IID assumption. We find that the primary spin magnitude distribution 
-peaking slightly higher at $a\sim0.25$ than the IID B-Spline model, but with similar support at near vanishing spins. The secondary spin magnitude distribution is more uncertain due to the 
-higher measurement uncertainty in inferring the secondary spins of BBH systems. The secondary distribution also peaks at smaller spin magnitudes of $a\sim0.15$, showing considerably larger 
-PPD and confidence band at $a\sim0$ than the primary distribution or B-Spline IID spin magnitude distribution in figure \ref{fig:iid_spinmag_dist}. While the distributions are still broadly 
-consistent with each other this could also be signs pointing towards component spin magnitude distributions uniquely distributed.
+peaks slightly higher, at $a\sim0.25$, than the IID B-Spline model, but with similar support at near vanishing spins. The secondary spin magnitude distribution is more uncertain due to the 
+higher measurement uncertainty when inferring the secondary spins of BBH systems.
+The secondary distribution also peaks at smaller spin magnitudes of $a\sim0.15$, showing potentially rates at $a\sim0$ than the primary distribution or B-Spline IID spin magnitude distribution in figure \ref{fig:iid_spinmag_dist}, though uncertainties are large.
+While the distributions are broadly consistent, we could be seeing the first signs that component spin magnitude distributions are uniquely distributed.
 

### 2022-10-11 src/tex/results.tex
changes to spin orientation results

@@
 
-The \textsc{Default} spin model also assumes the spin orientation of both components are identical and independently distributed (IID), with a mixture model over an
+The \textsc{Default} spin model (used by \citet{o3b_astro_dist}) also assumes the spin orientation of both components are identical and independently distributed (IID), with a mixture model over an
 aligned and an isotropic component. The aligned component is modeled with a truncated Gaussian distribution with mean at $\cos{\theta}=1$ and variance a free 
@@
 used to model the spin orientation distribution and found considerable evidence that the distribution peaks away from $\cos{\theta}=1$. Again, this provides a clear 
-use-case where data-driven models can help in our understanding of and possibly resolve disputes among differing parametric approaches to modeling the spin orientation distribution.
+use-case where data-driven models can help us understand the population.
 
@@
         \includegraphics[width=\linewidth]{figures/iid_spintilt.pdf}
-        \caption{The spin orientation distribution inferred with the B-Spline model (red), with 16 knots spaced linearly from -1 to 1, and 
-        assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
-        We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        \caption{The spin orientation distribution inferred with the B-Spline model (red) with 16 knots spaced linearly from -1 to 1, and assuming the components are IID.
+The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:iid_spintilt_dist}
@@
 We find a distribution that instead of intrinsically peaking at $\cos{\theta}=1$, is found to peak at: $\cos{\theta}=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][peakCosTilt]}$}, at 
-90\% credibility. We find less, but still considerable, support for misaligned spins (i.e. $\cos{\theta}<0$) as the \textsc{Default} model. Specifically we 
+90\% credibility. We find less, but still considerable support for misaligned spins (i.e. $\cos{\theta}<0$), compared to the \textsc{Default} model. Specifically we 
 find that the fraction of misaligned systems is $f_{\cos{\theta}<0}=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][negFrac]}$}. This implies 
@@
 introduced in \citet{spinitasyoulike} and defined as:
+\begin{equation}
+    Y \equiv \frac{\int_{0.9}^{1.0} d\cos{\theta} p(\cos{\theta})}{\int_{-1.0}^{-0.9} d\cos{\theta} p(\cos{\theta})}.
+\end{equation}
+The log this quantity, $\log_{10}Y$, is 0 for tilt distribution that is purely isotropic, negative when anti-aligned values are favored, 
+and positive when aligned tilts are favored. We find a $\log_{10}Y=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][log10gammaFrac]}$}, exhibiting a slight preference for aligned tilts.
 
-\begin{equation}
-    Y \equiv \frac{\int_{0.9}^{1.0} d\cos{\theta} p(\cos{\theta})}{\int_{-1.0}^{-0.9} d\cos{\theta} p(\cos{\theta})}
-\end{equation}
-
-\noindent Now the log this quantity, $\log_{10}Y$, is 0 for tilt distribution that is purely isotropic, negative when anti-aligned values are favored, 
-and positive when aligned tilts are favored. We find a $\log_{10}Y=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][log10gammaFrac]}$}, exhibiting a 
-slight preference for aligned tilts.
-
-Now we model each of the components' orientation distributions with independent B-Spline models as done above, and show the inferred 
-primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distributions do not match perfectly, but both are broadly
-are consistent with each other and the \textsc{Default} model's PPD given the wide credible intervals.
+We also model each component's orientation distribution with an independent B-Spline model as done above, and show the inferred 
+primary (orange), and secondary (olive) distributions in figure \ref{fig:ind_spintilt_dist}. The orientation distributions are broadly
+consistent with each other and the \textsc{Default} model's PPD given the wide credible intervals.
 We find the two distributions to peak at: $\cos{\theta_1}=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt1]}$}
@@
         \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
-        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model, 
-        with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
-        We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model with 16 knots spaced linearly from -1 to 1.
+The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
+        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:ind_spintilt_dist}

### 2022-10-11 src/tex/conclusion.tex
add link/ref GWInferno

@@
 
-The collective distribution of BBH source properties provides a useful probe of the complex and uncertain astrophysics that governs their 
-formation and evolution to eventually merge \citep{Zevin_2017}. Our analysis with the newly constructed M-Spline models corroborates important 
-conclusions of recent work and provides a robust data-driven framework for future population studies.
+The collective distribution of BBH source properties provides a useful probe of the complex and uncertain astrophysics that govern their 
+formation and evolution until merger \citep{Zevin_2017}.
+Our analyses with the newly constructed B-spline models uncover hints new features in the population (e.g., in mass ratio and redshift) and corroborates important
+conclusions of recent work, and provides a robust data-driven framework for future population studies.
 
@@
 The results presented in section \ref{sec:mass_dist} illustrate a much wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}. 
-While isolated formation is able to predict the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict a peak in the BH mass distribution less than 
+While isolated formation could explain the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict a peak in the BH mass distribution less than 
 $15-20\msun$ \citep{Hong_2018, Rodriguez_2019}.
-Globular cluster formation is expected to produce more top-heavy mass distributions than isolated and recent studies have shown suppressed BBH merger rates
+Globular cluster formation is expected to produce more top-heavy mass distributions than isolated channels, and recent studies have shown suppressed BBH merger rates
 at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \citep{Rodriguez_2015, Rodriguez_2019, BaveraMassTransfer,Belczynski_2016}.
@@
 mass black holes \citep{FordAGN, Tagawa_2021, Yang_2019}.
-We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts
+We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, which stellar evolution theory predicts
 due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017}.
@@
 pulsational pair-instability supernova (PPISN) \citep{Woosley_2017,Woosley_2019,Farmer_2019}.
-While the predictions of the mass scale where pair-instability kicks in are uncertain and depend on poorly understood physics,
-like nuclear reaction rates of carbon and oxygen in the core of stars, models have a hard time predicting this peak to be lower than $m\sim40\msun$ \citep{Belczynski_2016,Marchant_2019,Renzo_2020,Farmer_2019,Farmer_2020}.
+While the predictions of the mass scale where pair-instability kicks in are uncertain and depend on poorly understood physics
+like nuclear reaction rates of carbon and oxygen in the core of stars, models have a hard time producing this peak lower than $m\sim40\msun$ \citep{Belczynski_2016,Marchant_2019,Renzo_2020,Farmer_2019,Farmer_2020}.
 The lack of a truncation could
 point towards a higher prevalence of dynamical processes that can produce black holes in mass ranges stellar collapse cannot, such as hierarchical mergers of BHs \citep{Fishbach_2017,Doctor_2020,Kimball_genealogy,kimball2020evidence,doctor2021black,Fishbach_2022},
-very low metallicity population III stars \citep{Belczynski_2020,Farrell_2020}, new beyond the standard model physics\citep{Croon_newphysics,Sakstein_2020}, or black hole accretion of BHs in gaseous environments such as AGNs \citep{Secunda_2020,McKernan_2020,cruzosorio2021gw190521}.
+very low metallicity population III stars \citep{Belczynski_2020,Farrell_2020}, new beyond-standard-model physics\citep{Croon_newphysics,Sakstein_2020}, or black hole accretion of BHs in gaseous environments such as AGNs \citep{Secunda_2020,McKernan_2020,cruzosorio2021gw190521}.
+
+Our constraints on the mass ratio distribution are not yet precise enough to claim definitive departures from power law behavior, but do suggest possible plateaus in the rate at several mass ratios, including equal mass.
+These features should sharpen (or resolve) with future updates to the catalog.
 
@@
 Section \ref{sec:spin_dist} focused on inferences of the spin distributions of black holes, observing evidence of spin misalignment, spin anti-alignment, and suppressed support 
-for exactly aligned systems. These point towards a significant contribution of the population being formed through dynamical formation processes, agreeing with 
+for exactly aligned systems. These point towards a significant contribution to the population from dynamical formation processes, agreeing with 
 conclusions drawn about the mass distribution inference of section \ref{sec:mass_dist}. While field formation is expected to produce systems with preferentially 
@@
 we place conservative upper bounds on the fraction of hierarchical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$ with 
-the M-Spline $\chi_\mathrm{eff}$ model constraining $f_\mathrm{HM} < $\result{$\macros[ChiEffective][iid][frac_hm][10th percentile]$} 
+the B-spline $\chi_\mathrm{eff}$ model constraining $f_\mathrm{HM} < $\result{$\macros[ChiEffective][iid][frac_hm][10th percentile]$} 
 and $f_\mathrm{dyn} < $\result{$\macros[ChiEffective][iid][frac_dyn][10th percentile]$} at 90\% credibility.
+
+Finally, section \ref{sec:redshift} shows potentially interesting evolution of the BBH merger rate with redshift.
+Though uncertainties are still large, we may be seeing the first signs of departure from following the star formation rate.
+Again, we expect these features to be resolved with future catalogs.
 
@@
 We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 
-with gravitational waves. Our study paved the way as the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
+with gravitational waves, along with the associated open source software \textsc{GWInferno} (\href[]{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models 
+described in this paper and performs hierarchical Bayesian inference with \textsc{NumPyro} and \textsc{Jax} \citep{pyro,numpyro,jax}. 
+Our study paved the way as the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
 modeled population distributions. A complete understanding of the population properties of compact objects will help to advance poorly understood areas of stellar and 

### 2022-10-11 src/tex/conclusion.tex
fix href

@@
 We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 
-with gravitational waves, along with the associated open source software \textsc{GWInferno} (\href[]{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models 
+with gravitational waves, along with the associated open source software \textsc{GWInferno} (\href[git.ligo.org/bruce.edelman/gwinferno]{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models
 described in this paper and performs hierarchical Bayesian inference with \textsc{NumPyro} and \textsc{Jax} \citep{pyro,numpyro,jax}. 

### 2022-10-11 src/tex/conclusion.tex
few changes

--- 2022-10-11 src/tex/conclusion.tex
@@
 We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 
-with gravitational waves, along with the associated open source software \textsc{GWInferno} (\href[]{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models 
+with gravitational waves, along with the associated open source software \textsc{GWInferno} (\url{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models 
 described in this paper and performs hierarchical Bayesian inference with \textsc{NumPyro} and \textsc{Jax} \citep{pyro,numpyro,jax}. 

### 2022-10-11 src/tex/results.tex
few changes

@@
         \includegraphics[width=\linewidth]{figures/chi_eff.pdf}
-        \caption{The effective spin distribution inferred with the B-Spline IID spin model (red). The solid line shows the population predictive 
-        distribution (PPD) and the shaded region, the 90\% credible interval. We show the inferred $\chi_\mathrm{eff}$ 
+        \caption{The effective spin distribution inferred with the B-Spline IID spin model (red).
+The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
+We show the inferred $\chi_\mathrm{eff}$
         PPD from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the 
@@
 
-While the component spin magnitude and tilts are more easily interpretable in context of the astrophysics, they are parameters that 
-are not measured well during individual event parameter estimation. The best measured spin parameter, that enters the waveform at XXPN, is 
-called the effective spin defined as: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$. Figure \ref{fig:chieff_dist} 
+While the component spin magnitudes and tilts are more directly tied to formation physics, they are typically poorly measured.
+The best-measured spin quantity, which enters at the highest post-Newtownian order, is the effective spin: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$.
+Figure \ref{fig:chieff_dist}
 shows the inferred effective spin distribution with the two versions of our B-Spline models (red and purple), 
 along with results on the \textsc{Default} and \textsc{Gaussian} models from \citet{o3b_astro_dist}. We find considerable agreement 
-among the effective spin distributions, but the more flexible B-Spline models in component spins, more closely resemble the \textsc{Gaussian} 
-that directly models $\chi_\mathrm{eff}$, than the \textsc{Default} model. This could be signs that the population fit is driven by $\chi_\mathrm{eff}$ 
+among the effective spin distributions, but the more flexible B-Spline models in component spins more closely resemble results form the \textsc{Gaussian} model that directly models $\chi_\mathrm{eff}$, than the \textsc{Default} model.
+This could indicate that the population fit is driven by $\chi_\mathrm{eff}$
 more than the component spin dimensions. The B-Spline model finds very similar shapes to the other models, with a peak centered at 
@@
 $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$} with the \textsc{Gaussian} $\chi_\mathrm{eff}$ model. 
-As for the misaligned spin question, we calculate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and 
+As for spin misalignment, we calculate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and 
 find for the B-Spline model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$}, compared to 
@@
     \includegraphics[width=\linewidth]{figures/rate_vs_z_plot.pdf}
-    \caption{The BBH merger rate as a function of redshift. We show the B-Spline model (red), with 16 knots spaced linearly in $\log(z)$, 
-    from the minimum to the maximum observed redshifts. The solid line shows the population predictive distribution (PPD) and the shaded region, 
+    \caption{The BBH merger rate as a function of redshift. We show the B-Spline model (red) with 16 knots spaced linearly in $\log(z)$, 
+    from the minimum to the maximum observed redshifts. The solid line shows the population predictive distribution (PPD), and the shaded region 
     the 90\% credible interval. We show the inferred 90\% credible interval from the \textsc{PowerlawRedshift} model 
@@
 
-\subsection{Binary Black Hole Merger Rates}
+\subsection{Merger Rate Evolution with Redshift} \label{sec:redshift}
 
-Recent analysis of the GWTC-3 BBH population has shown confident evidence for an increasing merger rate with redshift, nearly ruling out a merger rate that is 
+Recent analysis of the GWTC-3 BBH population has shown evidence for an increasing merger rate with redshift, nearly ruling out a merger rate that is 
 constant with co-moving volume \citep{Fishbach_2018redshift,o3b_astro_dist}. When extending the power law form of the previously used model to have a modulation 
-that we model with B-Splines, the merger rate as a function of redshift in figure \ref{fig:rofz}, shows mild support for features departing from the underlying power law. 
-In particular, we see a small increase in merger rate from $z\sim0.09$ to $z\sim0.2$ (where we best constrain the rate), followed by a plateau in the rate increase from $z\sim0.2$ to $z\sim0.4$. 
+that we model with B-Splines, the merger rate as a function of redshift in figure \ref{fig:rofz} shows mild support for features departing from the underlying power law. 
+In particular, we see a small increase in merger rate from $z\sim0.09$ to $z\sim0.2$ (where we best constrain the rate), followed by a plateau in the rate from $z\sim0.2$ to $z\sim0.4$. 
 At larger redshifts, where we begin to have sparse observations, we see no sign of departure from the power-law as the rate continues to increase with redshift. 
-The underlying power-law slope of our modulated B-Spline model is very similar to the GWTC-3 results with the underlying model by itself: the \textsc{PowerlawRedshift} model 
+The underlying power-law slope of our B-spline modulated model is consistent with the GWTC-3 results with the underlying model by itself: the \textsc{PowerlawRedshift} model 
 found $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} when inferred with the \textsc{PowerlawPeak} mass, and \textsc{Default} spin models. Our more 
 flexible model infers a power law slope of $\lambda_z = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][lamb]}$}. We show the basis spline modulations or departure 
-from the power law in \ref{fig:z_modulation} compared to the prior -- showing where we can constrain deviations from the simpler parametric model. 
-The extra freedom of our model does inflate the rate estimates, especially at $z\sim0$ where we don't have any observations. We find a local ($z=0$) merger rate 
-of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}$} for the B-Spline modulation model which compares to 
-$\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}$} for the GWTC-3 result.
+from the power law in \ref{fig:z_modulation} compared to the prior -- showing where we cannot constrain any significant deviations from the simpler parametric power law model. 
+The extra freedom of our model does inflate the uncertainty in its rate estimates, especially at $z\sim0$ where there are not any observations in the catalog. 
+We find a local ($z=0$) merger rate of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}$} using the B-Spline modulation model 
+which compares to $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}$} for the GWTC-3 result.
 
@@
     \includegraphics[width=\linewidth]{figures/z_modulation_plot.pdf}
-    \caption{The B-Spline modulation to the underlying power law in redshift, (red). The solid line shows the population predictive distribution (PPD) 
-    and the shaded region, the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines.}
+    \caption{The B-spline modulation to the underlying power law in redshift, (red). The solid line shows the population predictive distribution (PPD),
+    and the shaded region the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines.}
     \label{fig:z_modulation}

### 2022-10-11 src/tex/results.tex
changes to redshift results

--- 2022-10-11 src/tex/results.tex
@@
 
-\subsection{Merger Rate Evolution with Redshift} \label{sec:redshift}
+\subsection{Binary Black Hole Merger Rates}
 
@@
 found $\lambda_z = $\result{$\CIPlusMinus{\macros[PLPeak][lamb]}$} when inferred with the \textsc{PowerlawPeak} mass, and \textsc{Default} spin models. Our more 
-flexible model infers a power law slope of $\lambda_z = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][lamb]}$}. We show the basis spline modulations or departure 
-from the power law in \ref{fig:z_modulation} compared to the prior -- showing where we cannot constrain any significant deviations from the simpler parametric power law model. 
-The extra freedom of our model does inflate the uncertainty in its rate estimates, especially at $z\sim0$ where there are not any observations in the catalog. 
-We find a local ($z=0$) merger rate of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}$} using the B-Spline modulation model 
-which compares to $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}$} for the GWTC-3 result.
+flexible model infers a power law slope of $\lambda_z = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][lamb]}$}. We show the basis spline modulations (i.e., departure 
+from the power law) in \ref{fig:z_modulation} compared to the prior -- showing where we can constrain deviations from the simpler parametric model. 
+The extra freedom of our model does inflate the rate estimates, especially at $z\sim0$ where we don't have any observations. We find a local ($z=0$) merger rate 
+of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}$} for the B-spline modulation model which compares to 
+$\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}$} for the GWTC-3 result.
 

### 2022-10-11 src/tex/conclusion.tex
change sentence in conclus

@@
 % mass dist
-The results presented in section \ref{sec:mass_dist} illustrate a much wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}. 
-While isolated formation could explain the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict a peak in the BH mass distribution less than 
-$15-20\msun$ \citep{Hong_2018, Rodriguez_2019}.
-Globular cluster formation is expected to produce more top-heavy mass distributions than isolated channels, and recent studies have shown suppressed BBH merger rates
-at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \citep{Rodriguez_2015, Rodriguez_2019, BaveraMassTransfer,Belczynski_2016}.
-BBHs that form near active galactic nuclei (AGN) can preferentially produce higher
-mass black holes \citep{FordAGN, Tagawa_2021, Yang_2019}.
-We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, which stellar evolution theory predicts
-due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017}.
+
+The results presented in section \ref{sec:mass_dist} illustrate a wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}, and a suppressed merger rate 
+at low primary masses (i.e. $\leq8\msun$). While isolated formation is able to predict the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict 
+a peak in the BH mass distribution less than $15-20\msun$ \citep{Hong_2018, Rodriguez_2019}. Globular cluster formation is expected to produce more top-heavy mass distributions than isolated 
+and recent studies have shown suppressed BBH merger rates at lower ($m\leq15\msun$) masses when compared to predictions from the isolated channel \citep{Rodriguez_2015, Rodriguez_2019, BaveraMassTransfer,Belczynski_2016}.
+BBHs that form near active galactic nuclei (AGN) can preferentially produce higher mass black holes \citep{FordAGN, Tagawa_2021, Yang_2019}. 
+We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017}.
 The original motivation for the peak in the \textsc{PowerlawPeak} model \citep{Talbot_2018} was to represent a possible ``pileup'' of

### 2022-10-11 src/tex/conclusion.tex
changes to conclusions

--- 2022-10-11 src/tex/conclusion.tex
@@
 
-Our constraints on the mass ratio distribution are not yet precise enough to claim definitive departures from power law behavior, but do suggest possible plateaus in the rate at several mass ratios, including equal mass.
+Our constraints on the mass ratio distribution are not yet precise enough to claim diffinitive departures from power law behaviour, but do suggest possible plateaus in the rate at several mass ratios, including equal mass.
 These features should sharpen (or resolve) with future updates to the catalog.
@@
 We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 
-with gravitational waves, along with the associated open source software \textsc{GWInferno} (\url{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models 
-described in this paper and performs hierarchical Bayesian inference with \textsc{NumPyro} and \textsc{Jax} \citep{pyro,numpyro,jax}. 
-Our study paved the way as the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
+with gravitational waves. Our study is the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
 modeled population distributions. A complete understanding of the population properties of compact objects will help to advance poorly understood areas of stellar and 

### 2022-10-15 src/scripts/plot_ppcs.py
add ppc plot script

@@ -1,0 +1,113 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+
+params = [
+    "mass_1",
+    "mass_ratio",
+    "redshift",
+    "a",
+    "cos_tilt",
+]
+
+nplot = len(params)
+figx, figy = 20, 4
+fig, axs = plt.subplots(nrows=1, ncols=nplot, sharey='row', figsize=(figx,figy))
+
+Nobs = 69
+po = dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid16tilt_pl16z_posterior_samples.h5')
+
+for ax, param in zip(axs, params):
+    if param == 'a' or param == 'cos_tilt':
+        observed1 = np.array([po[f"{param}_1_obs_event_{i}"] for i in range(Nobs)])
+        synthetic1 = np.array([po[f"{param}_1_pred_event_{i}"] for i in range(Nobs)])
+        observed2 = np.array([po[f"{param}_2_obs_event_{i}"] for i in range(Nobs)])
+        synthetic2 = np.array([po[f"{param}_2_pred_event_{i}"] for i in range(Nobs)])
+        observed = np.concatenate([observed1, observed2]).reshape((2*observed1.shape[0],Nobs))
+        synthetic = np.concatenate([synthetic1, synthetic2]).reshape((2*synthetic1.shape[0],Nobs))
+    else:    
+        observed = np.array([po[f"{param}_obs_event_{i}"] for i in range(Nobs)])
+        synthetic = np.array([po[f"{param}_pred_event_{i}"] for i in range(Nobs)])
+    if param == ['redshift']:
+        zmax = max([max(observed), max(synthetic)])
+        
+    ax.fill_betweenx(
+        y=np.linspace(0, 1, len(observed[:, 0])),
+        x1=np.quantile(np.sort(observed, axis=0), 0.05, axis=1),
+        x2=np.quantile(np.sort(observed, axis=0), 0.95, axis=1),
+        color="tab:blue",
+        alpha=0.8,
+        label="Observed",
+    )
+    ax.plot(
+        np.quantile(np.sort(observed, axis=0), 0.05, axis=1),
+        np.linspace(0, 1, len(observed[:, 0])),
+        color="k",
+        alpha=0.25,
+        lw=0.15,
+    )
+    ax.plot(
[…]

### 2022-10-15 src/tex/appendicies.tex
add ppc plot and some tables to try and make results presentation cleaner and more complete

--- 2022-10-11 src/tex/appendicies.tex
@@
     \multicolumn{4}{|c|}{\textbf{Primary Mass Model Parameters}} \\ \hline
-    \textsc{B-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+    \textsc{B-Spline Primary} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
      & $\tau_\lambda$ & Smoothing Prior Scale & U(1,100) \\ \cline{2-4}
-     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-     & $n$ & number of knots in the basis spline & 64 \\ \cline{2-4} 
+     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
+     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 6 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 64 \\ \hline \hline 
     \multicolumn{4}{|c|}{\textbf{Mass Ratio Model Parameters}} \\ \hline
-    \textsc{B-Spline} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+    \textsc{B-Spline Ratio} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
      & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
-     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-     & $n$ & number of knots in the basis spline & 18 \\ \cline{2-4}  
+     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
+     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 3 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 18 \\ \hline \hline
     \multicolumn{4}{|c|}{\textbf{Redshift Evolution Model Parameters}} \\ \hline
     \textsc{PowerLaw+B-Spline} & $\lambda$ & slope of redshift evolution power law $(1+z)^\lambda$ &  $\sim \mathcal{N}(0,3)$ \\ \cline{2-4}
-    & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$ \\ \cline{2-4} 
+    & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
      & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
-     & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-     & $n$ & number of knots in the basis spline & 16 \\ \cline{2-4} 
+     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
+     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
+     & $n$ & number of knots in the basis spline & 16 \\ \hline \hline 
     \multicolumn{4}{|c|}{\textbf{Spin Distribution Model Parameters}} \\ \hline
-    \textsc{B-Spline Magnitude} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
+    \textsc{B-Spline Magnitude} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$  \\ \cline{2-4} 
     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
-    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-    & $n$ & number of knots in the basis spline & 18 \\ \cline{2-4} 
-    \textsc{B-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, r, n)$  \\ \cline{2-4} 
+    & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
+    & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 18 \\ \hline \hline 
+    \textsc{B-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$  \\ \cline{2-4} 
     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
-    & $r$ & order of the difference matrix for smoothing prior & 2 \\ \cline{2-4} 
-    & $n$ & number of knots in the basis spline & 16 \\ \cline{2-4} 
+    & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
+    & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
+    & $n$ & number of knots in the basis spline & 16 \\ \hline \hline
     \end{tabular}

### 2022-10-15 src/tex/macros.tex
add ppc plot and some tables to try and make results presentation cleaner and more complete

--- 2022-10-11 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "MSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "MSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{MSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{MSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VII\else\def\macros@I@out{??}\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXI\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "MSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{MSpline}=0\let\macros@V@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXVIII\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{4.1}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.7}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{0.79}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.82}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.86}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{1.0}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{1.1}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.51}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.74}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.7}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{4.7}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{1.0}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.98}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.37}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXII@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXII@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXII@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXII@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXII@out\macros@XXXIII\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"FracBelowNeg0p3": \{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}, "PeakChiEff": \{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}, "frac\_dyn": \{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}, "frac\_hm": \{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIII@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIII@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIII@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIII@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIII@out\macros@XXXVIII\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXIV@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXIV@out\macros@XL\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXIV@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXIV@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXIV@out\macros@XLIII\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XLVIII\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVI@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVI@out\macros@L\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVI@out\macros@LI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVII@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVII@out\macros@LIV\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXVIII@out\macros@LVII\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.012, "error plus": 0.017, "error minus": 0.0089, "5th percentile": 0.0034, "95th percentile": 0.031, "10th percentile": 0.0049, "90th percentile": 0.027\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.012}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.017}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.0089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.0034}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.0049}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.027}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.43, "error plus": 0.075, "error minus": 0.14, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.075}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.48}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 0.019, "error plus": 0.029, "error minus": 0.022, "5th percentile": {-}0.003, "95th percentile": 0.049, "10th percentile": 0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{0.041}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.96\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.66}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.96}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.077, "error plus": 0.1, "error minus": 0.056, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.17\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.077}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.056}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.021}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.17}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.0072, "error plus": 0.0092, "error minus": 0.0057, "5th percentile": 0.0015, "95th percentile": 0.018, "10th percentile": 0.0022, "90th percentile": 0.016\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.0072}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.0092}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.0057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{0.0015}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.018}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{0.0022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.016}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.26, "error plus": 0.12, "error minus": 0.097, "5th percentile": 0.16, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.35\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.097}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.35}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.055, "error plus": 0.029, "error minus": 0.036, "5th percentile": 0.019, "95th percentile": 0.083, "10th percentile": 0.027, "90th percentile": 0.081\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.055}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.019}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.027}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.081}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.52, "error plus": 0.24, "error minus": 0.19, "5th percentile": 0.33, "95th percentile": 0.77, "10th percentile": 0.37, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.77}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.7}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.045, "error plus": 0.057, "error minus": 0.036, "5th percentile": 0.0094, "95th percentile": 0.11, "10th percentile": 0.014, "90th percentile": 0.099\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.045}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.0094}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.014}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.099}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.011, "error plus": 0.022, "error minus": 0.008, "5th percentile": 0.0026, "95th percentile": 0.035, "10th percentile": 0.0037, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.022}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.008}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.0026}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.035}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.0037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.024}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.3, "error plus": 0.11, "error minus": 0.12, "5th percentile": 0.19, "95th percentile": 0.41, "10th percentile": 0.21, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.19}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.21}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.39}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.039, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.071, "10th percentile": 0.017, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.071}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.065}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.61, "error plus": 0.22, "error minus": 0.23, "5th percentile": 0.38, "95th percentile": 0.83, "10th percentile": 0.42, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.23}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.83}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.42}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.78}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.066, "error plus": 0.14, "error minus": 0.05, "5th percentile": 0.016, "95th percentile": 0.22, "10th percentile": 0.023, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.066}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.05}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.22}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.023}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.15}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.0039}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.39}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.082}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.78}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.024}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{6.7}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{19}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{52}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{9.2}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{21}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{54}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{6.7}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{15}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{52}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "Default": \{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peak\_a1": \{"median": 0.24, "error plus": 0.16, "error minus": 0.24, "5th percentile": 0.0, "95th percentile": 0.38, "10th percentile": 0.052, "90th percentile": 0.34\}, "peak\_a2": \{"median": 0.11, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.0, "95th percentile": 0.26, "10th percentile": 0.0, "90th percentile": 0.22\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "peak\_a": \{"median": 0.2, "error plus": 0.083, "error minus": 0.18, "5th percentile": 0.017, "95th percentile": 0.27, "10th percentile": 0.087, "90th percentile": 0.26\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.018, "error minus": 0.0091, "5th percentile": 0.0042, "95th percentile": 0.033, "10th percentile": 0.0053, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.072, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.03, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.14, "error minus": 0.26, "5th percentile": 0.6, "95th percentile": 0.98, "10th percentile": 0.68, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.083, "error plus": 0.11, "error minus": 0.057, "5th percentile": 0.026, "95th percentile": 0.21, "10th percentile": 0.033, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.012, "error minus": 0.0057, "5th percentile": 0.0016, "95th percentile": 0.021, "10th percentile": 0.0024, "90th percentile": 0.017\}, "FracBelow0": \{"median": 0.27, "error plus": 0.12, "error minus": 0.1, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.18, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.034, "error minus": 0.04, "5th percentile": 0.013, "95th percentile": 0.085, "10th percentile": 0.023, "90th percentile": 0.075\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.24, "error minus": 0.21, "5th percentile": 0.34, "95th percentile": 0.79, "10th percentile": 0.37, "90th percentile": 0.74\}, "frac\_hm": \{"median": 0.046, "error plus": 0.077, "error minus": 0.036, "5th percentile": 0.01, "95th percentile": 0.13, "10th percentile": 0.015, "90th percentile": 0.11\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.015, "error minus": 0.0077, "5th percentile": 0.0029, "95th percentile": 0.028, "10th percentile": 0.004, "90th percentile": 0.023\}, "FracBelow0": \{"median": 0.31, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.81, "10th percentile": 0.44, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.066, "error plus": 0.096, "error minus": 0.048, "5th percentile": 0.018, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.14\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{Default}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@V\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@VI\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peak\_a1": \{"median": 0.24, "error plus": 0.16, "error minus": 0.24, "5th percentile": 0.0, "95th percentile": 0.38, "10th percentile": 0.052, "90th percentile": 0.34\}, "peak\_a2": \{"median": 0.11, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.0, "95th percentile": 0.26, "10th percentile": 0.0, "90th percentile": 0.22\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peak_a1}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peak_a2}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@III@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@III@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@III@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@III@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@III@out\macros@XXVIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "peak\_a": \{"median": 0.2, "error plus": 0.083, "error minus": 0.18, "5th percentile": 0.017, "95th percentile": 0.27, "10th percentile": 0.087, "90th percentile": 0.26\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@IV@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@IV@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@IV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@IV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@IV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@IV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@IV@out\macros@XXXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.018, "error minus": 0.0091, "5th percentile": 0.0042, "95th percentile": 0.033, "10th percentile": 0.0053, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.072, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.03, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.14, "error minus": 0.26, "5th percentile": 0.6, "95th percentile": 0.98, "10th percentile": 0.68, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.083, "error plus": 0.11, "error minus": 0.057, "5th percentile": 0.026, "95th percentile": 0.21, "10th percentile": 0.033, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.012, "error minus": 0.0057, "5th percentile": 0.0016, "95th percentile": 0.021, "10th percentile": 0.0024, "90th percentile": 0.017\}, "FracBelow0": \{"median": 0.27, "error plus": 0.12, "error minus": 0.1, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.18, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.034, "error minus": 0.04, "5th percentile": 0.013, "95th percentile": 0.085, "10th percentile": 0.023, "90th percentile": 0.075\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.24, "error minus": 0.21, "5th percentile": 0.34, "95th percentile": 0.79, "10th percentile": 0.37, "90th percentile": 0.74\}, "frac\_hm": \{"median": 0.046, "error plus": 0.077, "error minus": 0.036, "5th percentile": 0.01, "95th percentile": 0.13, "10th percentile": 0.015, "90th percentile": 0.11\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.015, "error minus": 0.0077, "5th percentile": 0.0029, "95th percentile": 0.028, "10th percentile": 0.004, "90th percentile": 0.023\}, "FracBelow0": \{"median": 0.31, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.81, "10th percentile": 0.44, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.066, "error plus": 0.096, "error minus": 0.048, "5th percentile": 0.018, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.14\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@V@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@V@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@V@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@V@out\macros@XXXIX\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@VI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@VI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@VI@out\macros@XLII\else\def\macros@VI@out{??}\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{2.4}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{25}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.1}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.094}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.073}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.63}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.47}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.6}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.03}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.25}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{4.1}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{25}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.36}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.5}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.064}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.49}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{4.7}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{45}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{5.9}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{52}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.79}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.82}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.24, "error plus": 0.16, "error minus": 0.24, "5th percentile": 0.0, "95th percentile": 0.38, "10th percentile": 0.052, "90th percentile": 0.34\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.38}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.052}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.34}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.11, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.0, "95th percentile": 0.26, "10th percentile": 0.0, "90th percentile": 0.22\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.26}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.22}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.86}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{1.0}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXV@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXV@out{1.1}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVI@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVI@out{1.0}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVII@out{0.51}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVIII@out{0.74}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.7}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.2, "error plus": 0.083, "error minus": 0.18, "5th percentile": 0.017, "95th percentile": 0.27, "10th percentile": 0.087, "90th percentile": 0.26\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.083}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.087}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.26}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{4.7}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{70}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{5.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{51}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{1.0}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.98}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.37}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.018, "error minus": 0.0091, "5th percentile": 0.0042, "95th percentile": 0.033, "10th percentile": 0.0053, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.072, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.03, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.14, "error minus": 0.26, "5th percentile": 0.6, "95th percentile": 0.98, "10th percentile": 0.68, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.083, "error plus": 0.11, "error minus": 0.057, "5th percentile": 0.026, "95th percentile": 0.21, "10th percentile": 0.033, "90th percentile": 0.17\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVI@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVI@out\macros@XLVII\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.012, "error minus": 0.0057, "5th percentile": 0.0016, "95th percentile": 0.021, "10th percentile": 0.0024, "90th percentile": 0.017\}, "FracBelow0": \{"median": 0.27, "error plus": 0.12, "error minus": 0.1, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.18, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.034, "error minus": 0.04, "5th percentile": 0.013, "95th percentile": 0.085, "10th percentile": 0.023, "90th percentile": 0.075\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.24, "error minus": 0.21, "5th percentile": 0.34, "95th percentile": 0.79, "10th percentile": 0.37, "90th percentile": 0.74\}, "frac\_hm": \{"median": 0.046, "error plus": 0.077, "error minus": 0.036, "5th percentile": 0.01, "95th percentile": 0.13, "10th percentile": 0.015, "90th percentile": 0.11\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVII@out\macros@LII\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.015, "error minus": 0.0077, "5th percentile": 0.0029, "95th percentile": 0.028, "10th percentile": 0.004, "90th percentile": 0.023\}, "FracBelow0": \{"median": 0.31, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.81, "10th percentile": 0.44, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.066, "error plus": 0.096, "error minus": 0.048, "5th percentile": 0.018, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.14\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVIII@out\macros@LVII\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXIX@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXIX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXIX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXIX@out\macros@LXII\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XL@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XL@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XL@out\macros@LXV\else\def\macros@XL@out{??}\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLI@out\macros@LXVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLI@out\macros@LXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLI@out\macros@LXVIII\else\def\macros@XLI@out{??}\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLII@out\macros@LXIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLII@out\macros@LXX\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLII@out\macros@LXXI\else\def\macros@XLII@out{??}\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.013, "error plus": 0.018, "error minus": 0.0091, "5th percentile": 0.0042, "95th percentile": 0.033, "10th percentile": 0.0053, "90th percentile": 0.027\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.018}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.0091}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.0042}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.033}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.0053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.027}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.43, "error plus": 0.072, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.072}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.34}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.48}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.017, "error plus": 0.03, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.043}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.86, "error plus": 0.14, "error minus": 0.26, "5th percentile": 0.6, "95th percentile": 0.98, "10th percentile": 0.68, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.68}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.97}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.083, "error plus": 0.11, "error minus": 0.057, "5th percentile": 0.026, "95th percentile": 0.21, "10th percentile": 0.033, "90th percentile": 0.17\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.083}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.026}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.033}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.17}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.0073, "error plus": 0.012, "error minus": 0.0057, "5th percentile": 0.0016, "95th percentile": 0.021, "10th percentile": 0.0024, "90th percentile": 0.017\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.0073}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.012}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.0057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.0016}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.021}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.0024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.017}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.27, "error plus": 0.12, "error minus": 0.1, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.17}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.37}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.053, "error plus": 0.034, "error minus": 0.04, "5th percentile": 0.013, "95th percentile": 0.085, "10th percentile": 0.023, "90th percentile": 0.075\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.053}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.085}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.023}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.075}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.55, "error plus": 0.24, "error minus": 0.21, "5th percentile": 0.34, "95th percentile": 0.79, "10th percentile": 0.37, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.21}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.34}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.79}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.37}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.74}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.046, "error plus": 0.077, "error minus": 0.036, "5th percentile": 0.01, "95th percentile": 0.13, "10th percentile": 0.015, "90th percentile": 0.11\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.046}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.077}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.13}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{0.015}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.11}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.011, "error plus": 0.015, "error minus": 0.0077, "5th percentile": 0.0029, "95th percentile": 0.028, "10th percentile": 0.004, "90th percentile": 0.023\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.015}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.0077}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.0029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.028}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.004}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.023}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.31, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.22}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.39}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.063\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.033}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.063}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.61, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.81, "10th percentile": 0.44, "90th percentile": 0.77\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{0.39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{0.81}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.77}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 0.066, "error plus": 0.096, "error minus": 0.048, "5th percentile": 0.018, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.14\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{0.066}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.096}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{0.048}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{0.018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{0.18}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{0.14}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{0.0039}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{0.39}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{0.082}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{0.78}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{0.024}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.7}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{19}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\newcommand\macros@LXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVI@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVI@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVI@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVI@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVI@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVI@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVI@out{9.2}\else\def\macros@LXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVI@out}\newcommand\macros@LXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVII@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVII@out{21}\else\def\macros@LXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVII@out}\newcommand\macros@LXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVIII@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVIII@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVIII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVIII@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVIII@out{54}\else\def\macros@LXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVIII@out}\newcommand\macros@LXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIX@out{6.7}\else\def\macros@LXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIX@out}\newcommand\macros@LXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXX@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXX@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXX@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXX@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXX@out{15}\else\def\macros@LXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXX@out}\newcommand\macros@LXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXI@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXI@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXI@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXI@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXI@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXI@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXI@out{52}\else\def\macros@LXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXI@out}\makeatother

### 2022-10-15 src/tex/results.tex
changes to conclusions
fix few redshift sentences
add ppc plot script
add ppc plot and some tables to try and make results presentation cleaner and more complete

--- 2022-10-11 src/tex/results.tex
@@
 The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:iid_spinmag_dist}
@@
         with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
-        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:ind_spinmag_dist}
@@
 \end{figure}
+
+\begin{table*}[ht!]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|l|}
+        \hline
+        Model & $a_\mathrm{peak}$ & $a_\mathrm{90\%}$ & $\cos{\theta_\mathrm{peak}}$ & $f_{\cos{\theta}<0}$ & $\log_{10}Y$ \\ \hline \hline
+        B-Spline IID & $\CIPlusMinus{\macros[BSplineIIDCompSpins][peak_a]}$ & $\CIPlusMinus{\macros[BSplineIIDCompSpins][a_90percentile]}$ & $\CIPlusMinus{\macros[BSplineIIDCompSpins][peakCosTilt]}$ & $\CIPlusMinus{\macros[BSplineIIDCompSpins][negFrac]}$ & $\CIPlusMinus{\macros[BSplineIIDCompSpins][log10gammaFrac]}$ \\ \hline
+        B-Spline Ind(primary) & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peak_a1]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][a1_90percentile]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt1]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][negFrac1]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][log10gammaFrac1]}$ \\ \hline
+        B-Spline Ind(secondary) & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peak_a2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][a2_90percentile]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][negFrac2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][log10gammaFrac2]}$  \\ \hline
+        \textsc{Default} & $\CIPlusMinus{\macros[Default][peak_a]}$ & $\CIPlusMinus{\macros[Default][a_90percentile]}$ & $\CIPlusMinus{\macros[Default][peakCosTilt]}$ & $\CIPlusMinus{\macros[Default][negFrac]}$ & $\CIPlusMinus{\macros[Default][log10gammaFrac]}$ \\ \hline
+    \end{tabular}
+    \caption{Summary of Component Spin distributions inferred both the independent and IID component spin B-Spline models and the \textsc{Default} spin model from \citet{o3b_astro_dist}.}
+    \label{tab:compspins}
+\end{table*}
 
@@
 The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-        For comparison we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
         \label{fig:ind_spintilt_dist}
@@
 \subsection{The Effective Spin Dimension}
+
+\begin{table*}[ht!]
+    \centering
+    \begin{tabular}{|l|l|l|l|l|l|}
+        \hline
+        Model & $\chi_\mathrm{eff,peak}$ & $f_{\chi_\mathrm{eff}<0}$ & $f_{\chi_\mathrm{eff}<-0.3}$ & $f_\mathrm{dyn}$ & $f_\mathrm{HM}$ \\ \hline \hline
+        B-Spline IID & $\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][iid][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][iid][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][iid][frac_hm]}$ \\ \hline
+        B-Spline Ind & $\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][frac_hm]}$ \\ \hline
+        \textsc{Default} & $\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][default][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][default][frac_hm]}$ \\ \hline
+        \textsc{Gaussian} & $\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][frac_hm]}$ \\ \hline
+    \end{tabular}
+    \caption{Summary of the effective spin distributions inferred with the B-Spline model variations, along with the \textsc{Default} and \textsc{Gaussian} models from \citet{o3b_astro_dist}.}
+    \label{tab:chieff}
+\end{table*}
 
@@
 \end{figure}
+
+\subsection{Posterior Predictive Checks} \label{sec:ppcs}
+
+\begin{figure*}[ht!]
+    \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
+    \caption{Posterior Predictive Check}
+    \label{fig:ppc}
+    \script{plot_ppcs.py}
+\end{figure*}
+
+Here we describe our posterior predictive checking procedure and results shown in figure \ref{fig:ppc}.

### 2022-10-15 src/scripts/create_macros.py

@@ -74,12 +74,64 @@ def BSplineIIDSpinMacros():
     frac_neg_cts = np.array(frac_neg_cts)
     posts = load_iid_posterior()
     mags, a_pdfs = load_iid_mag_ppd()
+    peak_mags = []
+    for jj in range(len(a_pdfs)):
+        peak_mags.append(mags[np.argmax(a_pdfs[jj,:])])
+    peak_mags = np.array(peak_mags)
     return {'a_90percentile': save_param_cred_intervals(get_percentile(a_pdfs, mags, 90)),
+            'peak_a': save_param_cred_intervals(peak_mags),
             'lamb': save_param_cred_intervals(posts['lamb']),
             'local_rate': save_param_cred_intervals(posts['rate']),
             'peakCosTilt': save_param_cred_intervals(peak_tilts), 
             'log10gammaFrac': save_param_cred_intervals(np.log10(gamma_fracs)), 
             'negFrac': save_param_cred_intervals(frac_neg_cts)}
+    
+    
+def DefaultSpinMacros():
+    print("Saving Default Component Spin macros...")
+    xs = np.linspace(-1, 1, 1000)
+    tilt_data = dd.io.load(paths.data / 'o1o2o3_mass_c_iid_mag_iid_tilt_powerlaw_redshift_orientation_data.h5')
+    lines = dict()
+    for key in tilt_data["lines"].keys():
+        lines[key] = tilt_data["lines"][key][()]
+        for ii in range(len(lines[key])):
+            lines[key][ii] /= np.trapz(lines[key][ii], xs)
+    ct_pdfs = lines['cos_tilt_1']
+    peak_tilts = []
+    gamma_fracs = []
+    frac_neg_cts = []
+    for jj in range(len(ct_pdfs)):
+        ct_pdfs[jj,:] /= np.trapz(ct_pdfs[jj,:], xs)
+        peak_tilts.append(xs[np.argmax(ct_pdfs[jj,:])])
+        gam = ct_pdfs[jj,xs>=0.9] / ct_pdfs[jj, xs<=-0.9]
+        gamma_fracs.append(gam)
+        neg = xs <= 0
+        frac_neg_cts.append(np.trapz(ct_pdfs[jj,neg], x=xs[neg]))
+    peak_tilts = np.array(peak_tilts)
+    gamma_fracs = np.array(gamma_fracs)
+    frac_neg_cts = np.array(frac_neg_cts)
+    mags = np.linspace(0, 1, 1000)
[…]

### 2022-10-15 src/scripts/plot_ind_spinmag.py

@@ -20,9 +20,9 @@ for i in range(len(a1_pdfs)):
 
 for ps, lab, c in zip([a1_pdfs, a2_pdfs], ['a1', 'a2'], ['tab:orange', 'tab:olive']):
     if lab == 'a1':
-        label=r'This Work ($p(a_1))$)'
+        label=r'This Work ($p(a_1)$)'
     else:
-        label=r'This Work ($p(a_2))$)'
+        label=r'This Work ($p(a_2)$)'
     ax = plot_mean_and_90CI(ax, a1s, ps, color=c,label=label)    
     high = np.percentile(ps, 95, axis=0)
     if max(high) > maxy:

### 2022-10-15 src/scripts/plot_ppcs.py

@@ -14,8 +14,16 @@ params = [
     "cos_tilt",
 ]
 
+param_latex = {
+    "mass_1": r'$m_1$',
+    "mass_ratio": r'$q$',
+    "redshift": r'$z$',
+    "a": r'$a$',
+    "cos_tilt": r'$\cos{\theta}$',
+}
+
 nplot = len(params)
-figx, figy = 20, 4
+figx, figy = 16,4
 fig, axs = plt.subplots(nrows=1, ncols=nplot, sharey='row', figsize=(figx,figy))
 
 Nobs = 69
@@ -27,87 +35,97 @@ for ax, param in zip(axs, params):
         synthetic1 = np.array([po[f"{param}_1_pred_event_{i}"] for i in range(Nobs)])
         observed2 = np.array([po[f"{param}_2_obs_event_{i}"] for i in range(Nobs)])
         synthetic2 = np.array([po[f"{param}_2_pred_event_{i}"] for i in range(Nobs)])
-        observed = np.concatenate([observed1, observed2]).reshape((2*observed1.shape[0],Nobs))
-        synthetic = np.concatenate([synthetic1, synthetic2]).reshape((2*synthetic1.shape[0],Nobs))
+        observed = np.concatenate([observed1, observed2]).reshape((Nobs,2*observed1.shape[1]))
+        synthetic = np.concatenate([synthetic1, synthetic2]).reshape((Nobs,2*synthetic1.shape[1]))
     else:    
         observed = np.array([po[f"{param}_obs_event_{i}"] for i in range(Nobs)])
         synthetic = np.array([po[f"{param}_pred_event_{i}"] for i in range(Nobs)])
     if param == 'redshift':
-        zmax = max([max(observed), max(synthetic)])
+        zmax = max([np.max(observed) , np.max(synthetic)])
+        zmin = min([np.min(observed) , np.min(synthetic)])
+
         
     ax.fill_betweenx(
         y=np.linspace(0, 1, len(observed[:, 0])),
         x1=np.quantile(np.sort(observed, axis=0), 0.05, axis=1),
         x2=np.quantile(np.sort(observed, axis=0), 0.95, axis=1),
-        color="tab:blue",
-        alpha=0.8,
+        color="k",
+        alpha=0.25,
         label="Observed",
     )
-    ax.plot(
[…]

### 2022-10-15 src/tex/appendicies.tex
rewrite weird sentence

@@
 where one adds a smoothing prior comprised of Gaussian distributions on the differences between neighboring basis spline coefficients. 
-This prior allows one to populate the domain more densely with knots without the worry of extra variance in the inferred spline functions. When also fitting the scale 
-of the smoothing prior (i.e. the width of the Gaussian distributions on the differences), this allows the data to inform the scale of smoothing required. 
-We discuss the details of our smoothing prior implementation in more detail in the next section, Appendix \ref{sec:psplines}, 
-along with our specific prior and basis choices for each model following that in Appendix \ref{sec:modelpriors}.
+This allows for knots to be densely populated across the domain without the worry of extra variance in the inferred spline functions. 
+When also fitting the scale of the smoothing prior (i.e. the width of the Gaussian distributions on the differences), the data will inform the model 
+of the preferred the scale of smoothing required. We discuss the details of our smoothing prior implementation in more detail in the next section, 
+Appendix \ref{sec:psplines}, following with our specific prior and basis choices for each model in Appendix \ref{sec:modelpriors}.
 

### 2022-10-15 src/tex/appendicies.tex
fix table width

@@
      & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
-     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 6 \\ \cline{2-4} 
+     & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 6 \\ \cline{2-4} 
      & $n$ & number of knots in the basis spline & 64 \\ \hline \hline 
@@
      & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
-     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 3 \\ \cline{2-4} 
+     & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 3 \\ \cline{2-4} 
      & $n$ & number of knots in the basis spline & 18 \\ \hline \hline
@@
      & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
-     & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
+     & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 1 \\ \cline{2-4} 
      & $n$ & number of knots in the basis spline & 16 \\ \hline \hline 
@@
     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
-    & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
+    & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 1 \\ \cline{2-4} 
     & $n$ & number of knots in the basis spline & 18 \\ \hline \hline 
@@
     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
-    & $\sigma$ & standard deviation for Gaussian priors on coefficients in the smoothing prior & 1 \\ \cline{2-4} 
+    & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 1 \\ \cline{2-4} 
     & $n$ & number of knots in the basis spline & 16 \\ \hline \hline

### 2022-10-16 src/tex/intro.tex
add where are ligo/virgo big black holes citation

@@
 
-Studies using flexible methods to analyze the binary black hole (BBH) mass distribution with GWTC-2 found signs of structure beyond the first reported feature found at 
-$m_1\sim35\,\msun$ \citep{Talbot_2018,o3a_pop,Tiwari_2021_b,Edelman_2022ApJ}. The evidence for this structure, 
-such as the peak at $m_1\sim10\,\msun$, only grew after analyzing the latest catalog, GWTC-3, with the same models \citep{o3b_astro_dist,Tiwari_2022ApJ}, illustrating  
-the usefulness of data-driven methods even with the current catalog size. The canonical approach to constructing population models has been 
+The binary black hole (BBH) mass distribution was first found to have structure beyond a smooth power law exhibiting a possible high mass truncation and either a break or a peak at $m_1\sim35-40\,\msun$ with simpler parametric models \citep{Fishbach_2017,Talbot_2018,o1o2_pop,o3a_pop}.
+Starting with moderately sized catalog, GWTC-2, more flexible models found signs of additional structure \citep{Tiwari_2021_b,Edelman_2022ApJ}.
+The evidence supporting these features,
+such as the peak at $m_1\sim10\,\msun$, has only grown after analyzing the latest catalog, GWTC-3, with the same models \citep{o3b_astro_dist,Tiwari_2022ApJ}. 
+While this shows the usefulness of data-driven methods with the current relatively small catalog size, they will become more powerful with more observations.
+The canonical approach to constructing population models has been
 to use simple parametric descriptions (e.g., power laws, beta distributions) that aim to describe the data in the simplest way, employ astrophysically motivated priors where appropriate, then sequentially add

### 2022-10-16 src/tex/intro.tex
go back to syw version==0.3.0 instead to fix clickable icons

@@
 
-The binary black hole (BBH) mass distribution was first found to have structure beyond a smooth power law exhibiting a possible high mass truncation and either a break or a peak at $m_1\sim35-40\,\msun$ with simpler parametric models \citep{Fishbach_2017,Talbot_2018,o1o2_pop,o3a_pop}.
+The binary black hole (BBH) mass distribution was first found to have structure beyond a smooth power law with simpler parametric models, exhibiting a possible high mass truncation and either a break or a peak at $m_1\sim35-40\,\msun$ \citep{Fishbach_2017,Talbot_2018,o1o2_pop,o3a_pop}.
 Starting with moderately sized catalog, GWTC-2, more flexible models found signs of additional structure \citep{Tiwari_2021_b,Edelman_2022ApJ}.

### 2022-10-17 src/tex/appendicies.tex
fix model appendix

@@
 
-\begin{table*}[hb!]
+We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
+their respective hyperparameters and prior distributions in the next section. To calculate draw 
+samples of the hyperparameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
+NUTS Hamiltonian Monte Carlo sampler in \textsc{NumPyro} and \textsc{Jax} to calculate likelihoods \citep{jax,pyro,numpyro}.
+
+\begin{table*}[b!]
     \centering
@@
     \textsc{B-Spline Primary} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
-     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,100) \\ \cline{2-4}
+     & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \mathrm{U}(2,1000)$ \\ \cline{2-4}
      & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
@@
     \textsc{B-Spline Ratio} & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
-     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
+     & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \mathrm{U}(1,100)$ \\ \cline{2-4}
      & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
-     & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 3 \\ \cline{2-4} 
+     & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 4 \\ \cline{2-4} 
      & $n$ & number of knots in the basis spline & 18 \\ \hline \hline
@@
     & $\bm{c}$ & Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$ \\ \cline{2-4} 
-     & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
+     & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \mathrm{U}(1,10)$ \\ \cline{2-4}
      & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
      & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 1 \\ \cline{2-4} 
-     & $n$ & number of knots in the basis spline & 16 \\ \hline \hline 
+     & $n$ & number of knots in the basis spline & 18 \\ \hline \hline 
     \multicolumn{4}{|c|}{\textbf{Spin Distribution Model Parameters}} \\ \hline
     \textsc{B-Spline Magnitude} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$  \\ \cline{2-4} 
-    & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
+    & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \mathrm{U}(1,10)$ \\ \cline{2-4}
     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
@@
     \textsc{B-Spline Tilt} & $\bm{c}$ &  Basis coefficients & $\sim \mathrm{Smooth}(\tau_\lambda, \sigma, r, n)$  \\ \cline{2-4} 
-    & $\tau_\lambda$ & Smoothing Prior Scale & U(1,10) \\ \cline{2-4}
+    & $\tau_\lambda$ & Smoothing Prior Scale & $\sim \mathrm{U}(1,10)$ \\ \cline{2-4}
     & $r$ & order of the difference matrix for the smoothing prior & 2 \\ \cline{2-4} 
     & $\sigma$ & width of Gaussian priors on coefficients in smoothing prior & 1 \\ \cline{2-4} 
-    & $n$ & number of knots in the basis spline & 16 \\ \hline \hline
+    & $n$ & number of knots in the basis spline & 18 \\ \hline \hline
     \end{tabular}
@@
 
-We explicitly enumerate each of the models used in this work for $p(\theta|\Lambda)$, along with 
-their respective hyperparameters and prior distributions in the next section. To calculate draw 
-samples of the hyperparameters from the hierarchical posterior distribution shown in equation \ref{importance-posterior}, we use the 
-NUTS Hamiltonian Monte Carlo sampler in \textsc{NumPyro} and \textsc{Jax} to calculate likelihoods \citep{jax,pyro,numpyro}.
-
 \section{Model specification} \label{sec:modelpriors}
 
-For each of the distributions with basis spline distributions, we have 2 fixed hyperparameters to specify. The number of degrees of freedom, $n$, and the difference 
-penalty order for the smoothing prior, $r$. Additionally, one must choose a prior distribution on the smoothing prior scale hyperparameter, $\tau_\lambda$, which we take to be Uniform. 
-For the primary mass distribution we model the log probability with a B-Spline interpolated in $\log(m_1)$ space. We follow a similar scheme for the models in mass ratio and spin, but since 
-these parameters have natural hard boundaries we model the log probability with B-Splines interpolated in $q$, $a_i$ or $\cos{\theta_i}$ space. The 
-redshift distribution is also lacking of a natural upper boundary, which we mitigate by using a semi parametric approach where B-Splines model modulations to the 
-simpler underlying \textsc{PowerlawRedshift} model. We both these B-Spline modulations in log probability interpolated in $\log z$ space. We enumerate each of our specific model hyperparameter 
+For each of the distributions with basis spline distributions, we have 2 fixed hyperparameters to specify. 
+The number of degrees of freedom, $n$, and the difference 
+penalty order for the smoothing prior, $r$. Additionally, one must choose a prior distribution on the smoothing prior scale hyperparameter, 
+$\tau_\lambda$, which we take to be Uniform. For the primary mass distribution we model the log probability with a B-Spline interpolated 
+in $\log(m_1)$ space. We follow a similar scheme for the models in mass ratio and spin, except we model the log probability with 
+B-Splines that are interpolated in $q$, $a_i$ or $\cos{\theta_i}$ space. We adopt a minimum black hole mass of $5\msun$, 
+and maximum of $100\msun$ with the equally spaced in this range. The knots for the mass ratio B-Spline are equally spaced 
+from $\frac{m_\mathrm{min}}{m_\mathrm{max}}=0.05$ to $1$. There is motivation for the evolution of the merger rate with redshift 
+to follow a power law form since it should be related to the star formation rate \citep{Madau_2014}, 
+motivating our adoption of a semi-parametric approach where we use B-Splines to model modulations to the 
+simpler underlying \textsc{PowerlawRedshift} model \citep{Fishbach_2018redshift,Edelman_2022ApJ}. 
+We model modulations to the underlying probability density with the multiplicative factor, $e^{B(\log z)}$, 
+where $B(\log z)$ is the B-Spline interpolated from knots spaced linearly in $\log z$ space. 
+We enumerate each of our specific model hyperparameter 
 and prior choices in table \ref{tab:model_priors}.

### 2022-10-17 src/tex/methods.tex
remove text stating dif min bH masses -- all min mass =5

@@
 We assume the polar spin angles are uniformly distributed in the orbital plane. For the primary mass distribution, we model the log probability with a B-Spline interpolated over 
-knots linearly spaced in $\log(m_1)$ in the range of support given our observations ($[6.5\msun-100\msun]$), such that $\log(p(m_1 | \bm{c})) \propto B_{k}(\log(m_1) | \bm{c})$, where $B_{k}$ is the 
-$k$-th order B-Spline function with basis coefficients $\bm{c}$. We follow the same procedure for the models in mass ratio and spin distributions with knots spaced linearly across each domain 
-so that we have $\log(p(\theta | \bm{c}_\theta)) \propto B_{k}(\theta | \bm{c}_\theta)$, where $\theta$ can be $q$, $a_1$, $a_2$, $\cos{\theta_1}$ or $\cos{\theta_2}$. 
+knots linearly spaced in $\log(m_1)$ from a minimum black hole mass, which we fix to $5\msun$, and a maximum mass 
+that we set to $100\msun$. We then have the hyper-prior on primary mass with log probability density 
+$\log(p(m_1 | \bm{c})) \propto B_{k}(\log(m_1) | \bm{c})$, where $B_{k}$ is the 
+$k$-th order B-Spline function with basis coefficients $\bm{c}$. We follow the same procedure 
+for the models in mass ratio and spin distributions with knots spaced linearly across each domain 
+so that we have $\log(p(\theta | \bm{c}_\theta)) \propto B_{k}(\theta | \bm{c}_\theta)$, 
+where $\theta$ can be $q$, $a_1$, $a_2$, $\cos{\theta_1}$ or $\cos{\theta_2}$. 
 For the spin magnitude and tilt distributions we construct two versions of the model: first, we model  
-each component's distribution as independently and identically distribution (IID), where we have a single B-Spline model and parameters (coefficients) for each binary spin. 
+each component's distribution as independently and identically distribution (IID), 
+where we have a single B-Spline model and parameters (coefficients) for each binary spin. 
 Secondly, we model each component's distribution to be unique, fitting separate sets of coefficients for the B-Spline models of the primary and secondary spin distributions. 

### 2022-10-17 src/tex/results.tex
remove text stating dif min bH masses -- all min mass =5

@@
         \includegraphics[width=\linewidth]{figures/mass_distribution_plot.pdf}
-        \caption{The marginal primary mass distribution inferred with the B-Spline model (red), with 64 knots spaced linearly in $\log m_1$, from 6.5\msun 
+        \caption{The marginal primary mass distribution inferred with the B-Spline model (red), with 64 knots spaced linearly in $\log m_1$, from 5\msun 
         to 100\msun. The solid line shows the population predictive distribution (PPD), and the shaded region 
@@
 This is partly due to the minimum mass hyperparameter (where the power law ``begins'') serving as the minimum allowable primary and secondary masses of the catalog.
-This leads to inferences of $m_\mathrm{min}$ below the minimum observed primary mass in the catalog, $\sim 6.4\msun$, to account for secondary BBH masses
-that can possibly get as low as $\sim 3\msun$. We choose a minimum primary mass for 
-the B-Spline model to be $6.5\msun$, while secondary masses are enforced to be greater than $3\msun$.
+This leads to inferences of $m_\mathrm{min}$ below the minimum observed primary mass in the catalog, which is $\sim 6.4\msun$, to account for secondary BBH masses lower than that.
+We choose to fix the minimum black hole mass for both primary and secondaries to $5\msun$,
+similar to the inferred minimum mass in \citet{o3b_astro_dist}.
 The lack of observations of binaries with low primary mass make rate estimates in this region strongly model and prior dependent.
@@
     \includegraphics[width=\linewidth]{figures/q_distribution_plot.pdf}
-    \caption{The marginal mass ratio distribution inferred with the B-Spline model (red), with 18 knots spaced linearly in $q$, from 0.03 to 1.
+    \caption{The marginal mass ratio distribution inferred with the B-Spline model (red), with 18 knots spaced linearly in $q$, from 0.05 to 1.
 The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
@@
 than the power law based models find. Our results also suggest a shallower slope from $q\sim0.3$ to $q\sim0.7$, though uncertainty is larger in this region. The sharp decrease in rate just below 
-$q\sim0.3$ is due to the minimum mass ratio truncation defined by $q_\mathrm{min}=\frac{m_\mathrm{min}}{m_1}$. When marginalizing over the primary mass 
-distribution with a strong peak at $10\msun$, the mass ratio distribution truncates at $q\sim0.3$: the minimum secondary mass, $3\msun$, 
+$q\sim0.5$ is due to the minimum mass ratio truncation defined by $q_\mathrm{min}=\frac{m_\mathrm{min}}{m_1}$. When marginalizing over the primary mass 
+distribution with a strong peak at $10\msun$, the mass ratio distribution truncates at $q\sim0.5$: the minimum mass, $5\msun$, 
 divided by the most common primary mass, ${\sim}10\msun$.

### 2022-10-17 src/tex/macros.tex
fix plots

--- 2022-10-11 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.016, "error minus": 0.0092, "5th percentile": 0.0033, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.12, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.85, "error plus": 0.15, "error minus": 0.25, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.078, "error plus": 0.1, "error minus": 0.057, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0069, "error plus": 0.011, "error minus": 0.0051, "5th percentile": 0.0018, "95th percentile": 0.02, "10th percentile": 0.0024, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.033, "error minus": 0.038, "5th percentile": 0.015, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.25, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.78, "10th percentile": 0.37, "90th percentile": 0.72\}, "frac\_hm": \{"median": 0.043, "error plus": 0.07, "error minus": 0.032, "5th percentile": 0.011, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.096\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0079, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0036, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.4, "10th percentile": 0.21, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.013, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.067\}, "frac\_dyn": \{"median": 0.6, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.8, "10th percentile": 0.43, "90th percentile": 0.76\}, "frac\_hm": \{"median": 0.066, "error plus": 0.1, "error minus": 0.049, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.022, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VIII\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVIII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIV\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.016, "error minus": 0.0092, "5th percentile": 0.0033, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.12, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.85, "error plus": 0.15, "error minus": 0.25, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.078, "error plus": 0.1, "error minus": 0.057, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0069, "error plus": 0.011, "error minus": 0.0051, "5th percentile": 0.0018, "95th percentile": 0.02, "10th percentile": 0.0024, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.033, "error minus": 0.038, "5th percentile": 0.015, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.25, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.78, "10th percentile": 0.37, "90th percentile": 0.72\}, "frac\_hm": \{"median": 0.043, "error plus": 0.07, "error minus": 0.032, "5th percentile": 0.011, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.096\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0079, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0036, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.4, "10th percentile": 0.21, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.013, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.067\}, "frac\_dyn": \{"median": 0.6, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.8, "10th percentile": 0.43, "90th percentile": 0.76\}, "frac\_hm": \{"median": 0.066, "error plus": 0.1, "error minus": 0.049, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.022, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXVIII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@V@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXXI\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{25}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.1}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.7}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{45}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{5.9}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{52}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.79}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.82}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.86}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{1.1}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{1.0}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.51}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{0.74}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.7}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{4.7}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{70}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{5.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{51}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{1.0}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.98}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.37}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.012, "error plus": 0.016, "error minus": 0.0092, "5th percentile": 0.0033, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.12, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.85, "error plus": 0.15, "error minus": 0.25, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.078, "error plus": 0.1, "error minus": 0.057, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XXXVI\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.0069, "error plus": 0.011, "error minus": 0.0051, "5th percentile": 0.0018, "95th percentile": 0.02, "10th percentile": 0.0024, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.033, "error minus": 0.038, "5th percentile": 0.015, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.25, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.78, "10th percentile": 0.37, "90th percentile": 0.72\}, "frac\_hm": \{"median": 0.043, "error plus": 0.07, "error minus": 0.032, "5th percentile": 0.011, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.096\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0079, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0036, "90th percentile": 0.024\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.4, "10th percentile": 0.21, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.013, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.067\}, "frac\_dyn": \{"median": 0.6, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.8, "10th percentile": 0.43, "90th percentile": 0.76\}, "frac\_hm": \{"median": 0.066, "error plus": 0.1, "error minus": 0.049, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.022, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@XLVI\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVIII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVIII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVIII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVIII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVIII@out\macros@LI\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LIV\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LVII\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXXI@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXXI@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXXI@out\macros@LX\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.012, "error plus": 0.016, "error minus": 0.0092, "5th percentile": 0.0033, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.025\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.012}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.0092}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.0033}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.0049}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.025}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.43, "error plus": 0.074, "error minus": 0.12, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.074}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.48}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.028}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.047}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.041}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.85, "error plus": 0.15, "error minus": 0.25, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.85}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.25}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.65}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.97}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.078, "error plus": 0.1, "error minus": 0.057, "5th percentile": 0.021, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.078}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.021}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.16}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.0069, "error plus": 0.011, "error minus": 0.0051, "5th percentile": 0.0018, "95th percentile": 0.02, "10th percentile": 0.0024, "90th percentile": 0.015\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.0069}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.011}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.0051}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.0018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.02}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.0024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.015}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.26, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.19, "90th percentile": 0.36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.17}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.36}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.053, "error plus": 0.033, "error minus": 0.038, "5th percentile": 0.015, "95th percentile": 0.085, "10th percentile": 0.025, "90th percentile": 0.079\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.053}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.033}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.038}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.015}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.085}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.079}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.51, "error plus": 0.25, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.78, "10th percentile": 0.37, "90th percentile": 0.72\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.25}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.78}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.37}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.72}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.043, "error plus": 0.07, "error minus": 0.032, "5th percentile": 0.011, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.096\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.043}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.07}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.032}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.015}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.096}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.011, "error plus": 0.016, "error minus": 0.0079, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0036, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.0079}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.0027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.029}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.0036}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.024}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.19, "95th percentile": 0.4, "10th percentile": 0.21, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.19}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.21}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.38}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.041, "error plus": 0.031, "error minus": 0.028, "5th percentile": 0.013, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.067\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.067}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.6, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.8, "10th percentile": 0.43, "90th percentile": 0.76\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.6}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.76}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.066, "error plus": 0.1, "error minus": 0.049, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.022, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.066}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.049}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.15}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.0039}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.39}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.082}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.78}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.024}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{6.7}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{19}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{52}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{9.2}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{21}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{54}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{6.7}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{15}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{52}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "Default": \{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0088, "5th percentile": 0.0038, "95th percentile": 0.03, "10th percentile": 0.005, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.039\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.1, "error minus": 0.055, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.011, "5th percentile": 0.0083, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.035\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.032, "error minus": 0.032, "5th percentile": 0.005, "95th percentile": 0.069, "10th percentile": 0.011, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.68, "error plus": 0.22, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.91, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.066, "5th percentile": 0.052, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.22\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.034, "error plus": 0.025, "error minus": 0.016, "5th percentile": 0.018, "95th percentile": 0.061, "10th percentile": 0.022, "90th percentile": 0.052\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.09, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.47\}, "PeakChiEff": \{"median": 0.024, "error plus": 0.033, "error minus": 0.031, "5th percentile": {-}0.007, "95th percentile": 0.057, "10th percentile": {-}0.001, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.98, "10th percentile": 0.67, "90th percentile": 0.94\}, "frac\_hm": \{"median": 0.21, "error plus": 0.16, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.38, "10th percentile": 0.14, "90th percentile": 0.33\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{Default}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@V\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@VI\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"lamb": \{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peak_a1}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peak_a2}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@III@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@III@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@III@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@III@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@III@out\macros@XXVIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@IV@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@IV@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@IV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@IV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@IV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@IV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@IV@out\macros@XXXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0088, "5th percentile": 0.0038, "95th percentile": 0.03, "10th percentile": 0.005, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.039\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.1, "error minus": 0.055, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.011, "5th percentile": 0.0083, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.035\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.032, "error minus": 0.032, "5th percentile": 0.005, "95th percentile": 0.069, "10th percentile": 0.011, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.68, "error plus": 0.22, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.91, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.066, "5th percentile": 0.052, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.22\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.034, "error plus": 0.025, "error minus": 0.016, "5th percentile": 0.018, "95th percentile": 0.061, "10th percentile": 0.022, "90th percentile": 0.052\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.09, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.47\}, "PeakChiEff": \{"median": 0.024, "error plus": 0.033, "error minus": 0.031, "5th percentile": {-}0.007, "95th percentile": 0.057, "10th percentile": {-}0.001, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.98, "10th percentile": 0.67, "90th percentile": 0.94\}, "frac\_hm": \{"median": 0.21, "error plus": 0.16, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.38, "10th percentile": 0.14, "90th percentile": 0.33\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@V@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@V@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@V@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@V@out\macros@XXXIX\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@VI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@VI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@VI@out\macros@XLII\else\def\macros@VI@out{??}\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{2.4}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{25}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.1}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.094}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.073}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.63}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.47}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.6}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.03}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.25}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{4.1}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{25}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.36}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.5}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.064}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.49}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}0.027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{4.6}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{4.1}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{7.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{44}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{9.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{36}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.88}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.86}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.9}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.69}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.88}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.38}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.39}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.67}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.79}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.65}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.94}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXV@out{0.51}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.54}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVI@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVI@out{0.6}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.27}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVII@out{0.58}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVIII@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVIII@out{0.52}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.56}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.6}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.81}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.072}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.27}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{2.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{2.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{4.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.17}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{3.9}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{25}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{8.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{48}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{10}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{41}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.084}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.87}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.24}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.7}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.59}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.44}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0088, "5th percentile": 0.0038, "95th percentile": 0.03, "10th percentile": 0.005, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.039\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.1, "error minus": 0.055, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVI@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVI@out\macros@XLVII\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.011, "5th percentile": 0.0083, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.035\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.032, "error minus": 0.032, "5th percentile": 0.005, "95th percentile": 0.069, "10th percentile": 0.011, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.68, "error plus": 0.22, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.91, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.066, "5th percentile": 0.052, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.22\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVII@out\macros@LII\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.034, "error plus": 0.025, "error minus": 0.016, "5th percentile": 0.018, "95th percentile": 0.061, "10th percentile": 0.022, "90th percentile": 0.052\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.09, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.47\}, "PeakChiEff": \{"median": 0.024, "error plus": 0.033, "error minus": 0.031, "5th percentile": {-}0.007, "95th percentile": 0.057, "10th percentile": {-}0.001, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.98, "10th percentile": 0.67, "90th percentile": 0.94\}, "frac\_hm": \{"median": 0.21, "error plus": 0.16, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.38, "10th percentile": 0.14, "90th percentile": 0.33\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVIII@out\macros@LVII\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXIX@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXIX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXIX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXIX@out\macros@LXII\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XL@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XL@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XL@out\macros@LXV\else\def\macros@XL@out{??}\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLI@out\macros@LXVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLI@out\macros@LXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLI@out\macros@LXVIII\else\def\macros@XLI@out{??}\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLII@out\macros@LXIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLII@out\macros@LXX\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLII@out\macros@LXXI\else\def\macros@XLII@out{??}\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.013, "error plus": 0.016, "error minus": 0.0088, "5th percentile": 0.0038, "95th percentile": 0.03, "10th percentile": 0.005, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.0088}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.0038}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.005}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.026}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.43, "error plus": 0.076, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.076}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.32}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.48}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.028}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.047}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.039}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.65}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.97}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.079, "error plus": 0.1, "error minus": 0.055, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.079}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.055}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.024}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.16}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.019, "error plus": 0.02, "error minus": 0.011, "5th percentile": 0.0083, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.035\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.011}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.041}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.035}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.34, "error plus": 0.11, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.098}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.43}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.037, "error plus": 0.032, "error minus": 0.032, "5th percentile": 0.005, "95th percentile": 0.069, "10th percentile": 0.011, "90th percentile": 0.063\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.037}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.032}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.032}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.069}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.011}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.063}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.68, "error plus": 0.22, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.91, "10th percentile": 0.52, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.48}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.91}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.86}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.12, "error plus": 0.12, "error minus": 0.066, "5th percentile": 0.052, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.22\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.066}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{0.052}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.25}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{0.064}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.22}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.034, "error plus": 0.025, "error minus": 0.016, "5th percentile": 0.018, "95th percentile": 0.061, "10th percentile": 0.022, "90th percentile": 0.052\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.034}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.025}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.061}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.052}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.41, "error plus": 0.083, "error minus": 0.09, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.47\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.083}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.09}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.34}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.47}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.024, "error plus": 0.033, "error minus": 0.031, "5th percentile": {-}0.007, "95th percentile": 0.057, "10th percentile": {-}0.001, "90th percentile": 0.049\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.033}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.031}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{{-}0.007}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.057}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.049}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.98, "10th percentile": 0.67, "90th percentile": 0.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.82}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.17}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.94}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 0.21, "error plus": 0.16, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.38, "10th percentile": 0.14, "90th percentile": 0.33\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{0.33}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{0.0039}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{0.39}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{0.082}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{0.78}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{0.024}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.7}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{19}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\newcommand\macros@LXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVI@out{\{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVI@out{8.5}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVI@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVI@out{7.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVI@out{9.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVI@out{7.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVI@out{9.0}\else\def\macros@LXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVI@out}\newcommand\macros@LXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVII@out{\{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVII@out{1.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVII@out{21}\else\def\macros@LXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVII@out}\newcommand\macros@LXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVIII@out{\{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVIII@out{46}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVIII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVIII@out{6.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVIII@out{59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVIII@out{55}\else\def\macros@LXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVIII@out}\newcommand\macros@LXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIX@out{6.7}\else\def\macros@LXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIX@out}\newcommand\macros@LXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXX@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXX@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXX@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXX@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXX@out{15}\else\def\macros@LXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXX@out}\newcommand\macros@LXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXI@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXI@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXI@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXI@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXI@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXI@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXI@out{52}\else\def\macros@LXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXI@out}\makeatother

### 2022-10-17 src/scripts/plot_chieff.py

@@ -12,7 +12,6 @@ mspl = ppds["BSplineInd"]
 mspl2 = ppds['BSplineIID']
 ax = plot_mean_and_90CI(ax, default["chieffs"], default["pchieff"], color='tab:blue', label='Default \n(Abbott et. al. 2021b)', bounds=False)
 ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:purple', label='This Work (Ind Spin)', bounds=False)
-ax = plot_mean_and_90CI(ax, mspl2["chieffs"], mspl2["pchieff"], color='tab:red', label='This Work (IID Spin)', bounds=True, fill_alpha=0.125)
 
 #handpicked_ppds = dd.io.load(
 #    paths.data / "BSpline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5"
@@ -29,9 +28,9 @@ with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json", 'r') as jf:
     o3b_gaussian_chi_eff_grid = np.array(o3b_gaussian_data['chi_eff_grid'])
     o3b_gaussian_chi_eff_data = np.array(o3b_gaussian_data['chi_eff_pdfs'])
 ax = plot_mean_and_90CI(ax, o3b_gaussian_chi_eff_grid, o3b_gaussian_chi_eff_data, color='tab:green', label='Gaussian \n(Abbott et. al. 2021b)', bounds=False)
-
+ax = plot_mean_and_90CI(ax, mspl2["chieffs"], mspl2["pchieff"], color='tab:red', label='This Work (IID Spin)', bounds=True, fill_alpha=0.125)
 plt.xlim(-0.65, 0.5)
-plt.ylim(0, 6)
+plt.ylim(0, 5.25)
 plt.legend(frameon=False, fontsize=14, loc='upper left')
 ax.grid(True, which="major", ls=":")
 ax.tick_params(labelsize=14)

### 2022-10-17 src/scripts/plot_iid_spinmag.py

@@ -22,7 +22,7 @@ ax.set_xlabel(r'$a$', fontsize=18)
 ax.set_ylabel(r'$p(a)$', fontsize=18)
 
 ax.set_xlim(xmin, xmax)
-ax.set_ylim(0, 6)
+ax.set_ylim(0, 4.25)
 ax.legend(frameon=False, fontsize=14);
 ax.grid(True, which="major", ls=":")
 ax.tick_params(labelsize=14)

### 2022-10-17 src/scripts/plot_iid_spintilt.py

@@ -24,7 +24,7 @@ ax.set_xlim(xmin, xmax)
 ax.legend(frameon=False, fontsize=14, loc='upper left');
 ax.grid(True, which="major", ls=":")
 ax.tick_params(labelsize=14)
-ax.set_ylim(0, 2.)
+ax.set_ylim(0, 1.6)
 
 plt.title(f'GWTC-3: Spin Tilt Distribution', fontsize=18);
 fig.tight_layout()

### 2022-10-17 src/scripts/plot_ind_spinmag.py

@@ -34,7 +34,7 @@ ax.set_xlabel(r'$a$', fontsize=18)
 ax.set_ylabel(r'$p(a)$', fontsize=18)
 ax.set_xlim(xmin, xmax)
 
-ax.set_ylim(0, 6)
+ax.set_ylim(0, 4.25)
 ax.legend(frameon=False, fontsize=14);
 ax.grid(True, which="major", ls=":")
 ax.tick_params(labelsize=14)

### 2022-10-17 src/scripts/plot_ind_spintilt.py

@@ -32,7 +32,7 @@ ax.set_ylabel(r'$p(\cos{\theta})$', fontsize=18)
 
 ax.set_xlim(xmin, xmax)
 
-ax.set_ylim(0, 2)
+ax.set_ylim(0, 1.6)
 ax.legend(frameon=False, fontsize=14, loc='upper left');
 ax.grid(True, which="major", ls=":")
 ax.tick_params(labelsize=14)

### 2022-10-17 src/scripts/z_modulation_plot.py

@@ -36,7 +36,7 @@ ax.axhline(0, color="k", lw=2)
 ax.set_xlabel(r"$z$", fontsize=18)
 ax.set_ylabel(r"$B(z)$", fontsize=18)
 ax.set_xscale('log')
-ax.set_ylim(-2,2)
+ax.set_ylim(-1.2,1.2)
 ax.set_xlim(zs[0], zs[-1])
 ax.grid(True, which="major", ls=":")
 plt.title(r'GWTC-3: Redshift Modulation', fontsize=18);

### 2022-10-18 src/tex/appendicies.tex
again
address most all of toms pnp comments

@@
 Therefore, given an array of knot locations, $\mathbf{t}$ or knot vector, there exists a single unique linear combination of basis splines 
-for every possible spline function interpolated from knots, $\mathbf{t}$. The basis components for a given knot vector can be constructed  
-using the Cox-de Boor recursion formula \citep{deBoor78,monotone_regression_splines}. Given knots $t_0$, $t_1$,...,$t_{i+k}$ 
-the base case and recursion relation that generates this particular basis are defined as:
+for every possible spline function interpolated from $\mathbf{t}$. To construct a basis of $n$ components and knots, $t_0$, $t_1$,...,$t_{i+k}$, 
+we use the Cox-de Boor recursion formula \citep{deBoor78,monotone_regression_splines}. The recursion starts with the $k=0$ (constant) case and recursively constructs 
+the basis components of higher orders. The base case and recursion relation that generates this particular basis are defined as:
 
 \begin{equation}
-    B_{i,1}(x | \mathbf{t}) = 
+    B_{i,0}(x | \mathbf{t}) = 
     \begin{cases}
@@
 their Bayesian analog \citep{BayesianPSplines}. The Bayesian P-Spline prior places Gaussian distributions over the $r$-th order differences of the 
-coefficients \citep{BayesianPSplines,Jullion2007RobustSO}. This is also sometimes referred to as a Gaussian random walk prior. 
+coefficients \citep{BayesianPSplines,Jullion2007RobustSO}.
+This is also sometimes referred to as a Gaussian random walk prior, and is similar in spirit to a Gaussian process prior used to regularize or smooth histogram bin heights as done in other non-parametric population studies \citep{Mandel_2016,o3b_astro_dist}.
 For a spline basis with $n$ degree's of freedom, and a difference penalty of order of $r$ (see \citet{eilers2021practical}), 
-the smoothing prior is defined as:
+the smoothing prior on our basis spline coefficients, $\bm{c}$ is defined as:
 
@@
 This prior is imparting a natural attraction of the coefficients closer to each other in order to smooth the spline function, so one 
-must ensure that the spline function is in fact flat given all equal coefficients. There needs to be $n+k$ knots to construct an order-k 
+must ensure that the spline function is in fact flat given all equal coefficients. There needs to be $n+k+1$ knots to construct an order-k 
 basis with n degrees of freedom. Some studies place knots on top of each other at hard parameter boundaries \citep{deBoor78,monotone_regression_splines}, 
 which may seem motivated, but this violates the above condition necessary for the P-Spline prior. We follow the distinction in \citet{eilers2021practical} 
-that such a smoothing prior is only valid with ``proper'' spline bases. A proper basis is where all $n+k$ knots are evenly and equally spaced, 
+that such a smoothing prior is only valid with ``proper'' spline bases. A proper basis is where all $n+k+1$ knots are evenly and equally spaced, 
 see Figure \ref{fig:spline_basis}, as opposed to stacking them at the bounds.
@@
 % This appendix goes over in detail the hierarchical bayeisan inference framework
-We use hierarchical Bayesian inference to infer the population properties of CBCs. We want to infer the number density of merging CBCs 
+We use hierarchical Bayesian inference to infer the population properties of CBCs. We want to infer the number density of merging compact binaries  
 in the universe and how this can change with their masses, spins, etc. Often times it is useful to formulate the question in terms of the 
-merger rates which is the number of mergers per $Gpc^{3}$ co-moving volume per year. For a set of hyperparameters, $\Lambda$, $\lambda$, and local ($z=0$) 
-merger rate density, $\mathcal{R}_0$, we write the overall number density of BBH mergers in the universe as:
+merger rates which is the number of mergers per $Gpc^{3}$ co-moving volume per year. For a set of hyperparameters, $\Lambda$, $\lambda$, and overall 
+merger rate, $\mathcal{R}$, we write the overall number density of BBH mergers in the universe as:
 
 \begin{equation} \label{number_density}
-     \frac{dN(\theta, z | \mathcal{R}_0, \Lambda, \lambda)}{d\theta dz} = \frac{dV_c}{dz}\bigg(\frac{T_\mathrm{obs}}{1+z}\bigg) \frac{d\mathcal{R}(\theta, z | \mathcal{R}_0, \Lambda, \lambda)}{d\theta} = \mathcal{R}_0 p(\theta | \Lambda) p(z | \lambda)
+     \frac{dN(\theta, z | \mathcal{R}, \Lambda, \lambda)}{d\theta dz} = \frac{dV_c}{dz}\bigg(\frac{T_\mathrm{obs}}{1+z}\bigg) \frac{d\mathcal{R}(\theta, z | \mathcal{R}_0, \Lambda, \lambda)}{d\theta} = \mathcal{R} p(\theta | \Lambda) p(z | \lambda)
 \end{equation}
@@
 \noindent
-Where up above, we denote the co-moving volume element as $dV_c$ \citep{hogg_cosmo}, and $T_\mathrm{obs}$ as the observing time period that produced the 
+where up above, we denote the co-moving volume element as $dV_c$ \citep{hogg_cosmo}, and $T_\mathrm{obs}$ as the observing time period that produced the 
 catalog with the related factor of $1+z$ converting this detector-frame time to source-frame. We assume a Lambda CDM cosmology using 
 the cosmological parameters from \citet{Planck2015}. We model the merger rate evolving with redshift following a power law distribution: 
-$p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$ \cite{Fishbach_2018redshift}. When integrating equation \ref{number_density} across all $\theta$
+$p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$ \citep{Fishbach_2018redshift}. When integrating equation \ref{number_density} across all $\theta$
 and out to some maximum redshift, $z_\mathrm{max}$, we get the total number of CBCs in the universe out to that redshift. We follow previous notations, \
 letting $\{d_i\}$ represent the set of data from $N_\mathrm{obs}$ CBCs observed with gravitational waves. The merger rate is then described as an inhomogeneous 
-Poisson process and after imposing the usual log-uniform prior on the merger rate, we marginalize over the local merger rate, $\mathcal{R}_0$, and arrive at the posterior
+Poisson process and after imposing the usual log-uniform prior on the merger rate, we marginalize over the merger rate, $\mathcal{R}$, and arrive at the posterior
 distribution of our hyperparameters, $\Lambda$ \citep{Mandel_2019, Vitale_2021}.
@@
 \noindent
-Where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples. Above, $j$
+where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples. Above, $j$
 indexes the $K_i$ posterior samples from each event and $\pi(\theta, z)$ is the default prior used by parameter estimations that 
@@
 \noindent
-Where the sum is only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, 
+where the sum is only over the $N_\mathrm{found}$ injections that were successfully detected out of $N_\mathrm{inj}$ total injections, 
 and $p_\mathrm{inj}(\theta, z)$ is the reference distribution from which the injections were drawn. We use the LVK released injection sets that describe the 
@@
 
-\section{Model specification} \label{sec:modelpriors}
+\section{Model and Prior Specification} \label{sec:modelpriors}
 

### 2022-10-18 src/tex/conclusion.tex
address most all of toms pnp comments

--- 2022-10-11 src/tex/conclusion.tex
@@
 The collective distribution of BBH source properties provides a useful probe of the complex and uncertain astrophysics that govern their 
-formation and evolution until merger \citep{Zevin_2017}.
+formation and evolution until merger \citep{Rodriguez_2016,Farr2017Nature,Zevin_2017}.
 Our analyses with the newly constructed B-spline models uncover hints new features in the population (e.g., in mass ratio and redshift) and corroborates important
@@
 isolated population models assume. Additionally, because of uncertain knowledge of supernovae kicks, isolated formation can produce systems with negative but small effective spins. 
-We report an effective spin distribution that is not symmetric about zero, disfavoring a scenario in which all BBHs are formed dynamically. Following the rules in \citet{Fishbach_2022}, 
+Consistent with recent studies we report an effective spin distribution that is not symmetric about zero, disfavoring a scenario in which all BBHs are formed dynamically \citep{o3a_pop,o3b_astro_dist,Callister_NoEvidence}.
+Following the rules in \citet{Fishbach_2022}, 
 we place conservative upper bounds on the fraction of hierarchical mergers $f_\mathrm{HM}$ and fraction of dynamically formed BBHs, $f_\mathrm{dyn}$ with 
@@
 and $f_\mathrm{dyn} < $\result{$\macros[ChiEffective][iid][frac_dyn][10th percentile]$} at 90\% credibility.
+This is consistent with the 90\% credible interval found from the GWTC-2 analysis, $0.25\leq f_\mathrm{dyn} \leq 0.93$ \citep{o3a_pop}.
 
 Finally, section \ref{sec:redshift} shows potentially interesting evolution of the BBH merger rate with redshift.
-Though uncertainties are still large, we may be seeing the first signs of departure from following the star formation rate.
+Though uncertainties are still large, we may be seeing the first signs of departure from following the star formation rate, which could help in distinguishing different subpopulations should they exist \citep{van_Son_2022}.
 Again, we expect these features to be resolved with future catalogs.

### 2022-10-18 src/tex/intro.tex
address most all of toms pnp comments

@@
 With the formation history of these dense objects encoded in the details of their distribution \citep{Zevin_2017}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics.
-Beyond formation physics, population-level inference of the compact binary catalog has also been shown to provide novel measurements of cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo}, constrain modified gravitational wave propagation \citep{ModGWProp,ModGWProp2},
+Beyond formation physics, population-level inference of the compact binary catalog has also been shown to provide novel measurements of cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo,JoseSpectralSirens}, constrain modified gravitational wave propagation \citep{OkounkovaBirefringence,ModGWProp,ModGWProp2},
 constrain a running Planck mass \citep{Lagos_runningPlanckMass}, search for evidence of ultralight bosons through superradiance \citep{Ng_Boson2021,GWTC2_superradiance_Ng}, 
@@
 The measurement of spin properties of individual binaries often have large uncertainties, but the theorized formation channels are expected to produce distinctly 
-different spin distributions \citep{Farr_BinnedSpin, Farr2017Nature, Zevin_2017}.
+different spin distributions \citep{Rodriguez_2016,Gerosa2018, Farr_BinnedSpin, Farr2017Nature, Zevin_2017}.
 Isolated (or field) formation scenarios predict component spins that are preferentially aligned with the binary's orbital angular momentum, although some small

### 2022-10-18 src/tex/methods.tex
address most all of toms pnp comments

@@
 
-We construct our data-driven model with the application of basis splines, or B-Splines \citep{deBoor78}. B-Splines of order $k$ are a set of order $k-1$ polynomials that 
-span the space of possible spline functions interpolated from a given set of knot locations. The basis representation of the splines allows for the computationally
+We construct our data-driven model with the application of basis splines, or B-Splines \citep{deBoor78}. B-Splines of order $k$ are a set of order $k$ polynomials that 
+span the space of possible spline functions interpolated from a given set of knot locations.
+For all B-Splines used in our model we use a third order basis which consists of individual cubic polynomials.
+The basis representation of the splines allows for the computationally
 expensive interpolation to be done in a single preprocessing step -- amortizing the cost of model evaluation during inference. To mitigate the unwanted side effects of 
@@
 that we set to $100\msun$. We then have the hyper-prior on primary mass with log probability density 
-$\log(p(m_1 | \bm{c})) \propto B_{k}(\log(m_1) | \bm{c})$, where $B_{k}$ is the 
-$k$-th order B-Spline function with basis coefficients $\bm{c}$. We follow the same procedure 
+$\log(p(m_1 | \bm{c})) \propto B_{k=3}(\log(m_1) | \bm{c})$, where $B_{k=3}$ is the 
+cubic B-Spline function with a vector of basis coefficients $\bm{c}$. We follow the same procedure 
 for the models in mass ratio and spin distributions with knots spaced linearly across each domain 
-so that we have $\log(p(\theta | \bm{c}_\theta)) \propto B_{k}(\theta | \bm{c}_\theta)$, 
+so that we have $\log(p(\theta | \bm{c}_\theta)) \propto B_{k=3}(\theta | \bm{c}_\theta)$, 
 where $\theta$ can be $q$, $a_1$, $a_2$, $\cos{\theta_1}$ or $\cos{\theta_2}$. 
@@
 probability density defined as: $p(z|\lambda_z)\propto \frac{dV_c}{dz}(1+z)^{\lambda_z-1}$ \citep{Fishbach_2018redshift}. For more detailed descriptions of each model and 
-specific prior choices used for the hyperparameters see Appendix \ref{sec:modelpriors}. Now that we have our comprehensive data-driven population model over 
-each of the 7 modeled parameters built, we fit our model using the usual hierarchical Bayesian inference framework (see appendix \ref{sec:hierarchical_inference} for a review) in order to characterize
-the population of BBHs in the most recent catalog of GW observations, GWTC-3 \citep{GWTC3,o3b_astro_dist}.
+specific prior choices used for the hyperparameters see Appendix \ref{sec:modelpriors}.
+Now that we have our comprehensive data-driven population model built, we simultaneously fit the basis spline models on the BBH masses, spins and redshift.
+We use the usual hierarchical Bayesian inference framework (see appendix \ref{sec:hierarchical_inference} for a review; \citet{o1o2_pop,o3a_pop,o3b_astro_dist}), to perform the most
+extensive characterization of the population of BBHs to date using the most recent catalog of GW observations, GWTC-3 \citep{GWTC3}.

### 2022-10-18 src/tex/results.tex
address most all of toms pnp comments

@@
 reported using the same dataset in \citet{o3b_astro_dist}.
-The B-Spline model finds the same feature at $\sim18\msun$ as the \textsc{PowerlawSpline} model, but remains consistent with the \textsc{PowerlawSpline} model; the mass distribution is more uncertain in this region.
+The B-Spline model finds the same feature at $\sim18\msun$ as the \textsc{PowerlawSpline} model, but remains consistent with the \textsc{PowerlawPeak} model; the mass distribution is more uncertain in this region.
 We find the largest disagreement at low masses, where the power-law-based models show a higher rate below ${\sim}8-9\msun$.
@@
 allowing it to probe the zero-spin question. We find broad support, with large variance, for non-zero probabilities at $a_i=0$, but cannot confidently determine the presence of 
-a significant non-spinning subpopulation, corroborating similar recent conclusions \citep{BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}. 
+a significant non-spinning subpopulation, corroborating similar recent conclusions \citep{BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin,Mould2022}. 
 We repeat the same analysis with independent B-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
@@
 The secondary distribution also peaks at smaller spin magnitudes of $a\sim0.15$, showing potentially rates at $a\sim0$ than the primary distribution or B-Spline IID spin magnitude distribution in figure \ref{fig:iid_spinmag_dist}, though uncertainties are large.
-While the distributions are broadly consistent, we could be seeing the first signs that component spin magnitude distributions are uniquely distributed.
+While the distributions are broadly consistent, we could be seeing signs that component spin magnitude distributions are uniquely distributed, which can be produced through mass-ratio reversal in isolated binary evolution \citep{Mould2022}.
 
@@
 We find a distribution that instead of intrinsically peaking at $\cos{\theta}=1$, is found to peak at: $\cos{\theta}=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][peakCosTilt]}$}, at 
-90\% credibility. We find less, but still considerable support for misaligned spins (i.e. $\cos{\theta}<0$), compared to the \textsc{Default} model. Specifically we 
-find that the fraction of misaligned systems is $f_{\cos{\theta}<0}=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][negFrac]}$}. This implies 
+90\% credibility.
+We find less, but still considerable support for misaligned spins (i.e.
+$\cos{\theta}<0$), consistent with other recent studies \citep{o3a_pop,o3b_astro_dist,Callister_NoEvidence}.
+Specifically we
+find that the fraction of misaligned systems is $f_{\cos{\theta}<0}=$\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][negFrac]}$}, compared to 
+$f_{\cos{\theta}<0}=$\result{$\CIPlusMinus{\macros[Default][negFrac]}$} with the \textsc{Default} model from \citet{o3b_astro_dist}. This implies 
 the presence of an isotropic component as expected by dynamical formation channels, albeit less than with the \textsc{Default} model. To quantify the 
@@
 shows the inferred effective spin distribution with the two versions of our B-Spline models (red and purple), 
-along with results on the \textsc{Default} and \textsc{Gaussian} models from \citet{o3b_astro_dist}. We find considerable agreement 
-among the effective spin distributions, but the more flexible B-Spline models in component spins more closely resemble results form the \textsc{Gaussian} model that directly models $\chi_\mathrm{eff}$, than the \textsc{Default} model.
+along with results on the \textsc{Default} \citep{Talbot_2017} and \textsc{Gaussian} \citep{Miller2020} models from \citet{o3b_astro_dist}. We find considerable agreement 
+among the effective spin distributions, but the more flexible B-Spline models in component spins more closely resemble results from the \textsc{Gaussian} model that directly models $\chi_\mathrm{eff}$, than the \textsc{Default} model.
 This could indicate that the population fit is driven by $\chi_\mathrm{eff}$
@@
 $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$} with the \textsc{Gaussian} $\chi_\mathrm{eff}$ model. 
-As for spin misalignment, we calculate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and 
-find for the B-Spline model $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$}, compared to 
-$f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} with the \textsc{Default} model and 
-$f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelow0]}$} with the Gaussian $\chi_\mathrm{eff}$ model.
+As for spin misalignment, we calculate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and find similar 
+agreement with previous work \citep{o3a_pop,o3b_astro_dist,Callister_NoEvidence}. We find for the B-Spline model 
+$f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][iid][FracBelow0]}$}, compared to 
+$f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$} and $f_{\chi_\mathrm{eff}<0}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelow0]}$} 
+with the \textsc{Default} and \textsc{Gaussian} models from \citet{o3b_astro_dist}.
 
@@
 The extra freedom of our model does inflate the uncertainty in its rate estimates, especially at $z\sim0$ where there are not any observations in the catalog. 
-We find a local ($z=0$) merger rate of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}$} using the B-Spline modulation model 
-which compares to $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}$} for the GWTC-3 result.
+We find a local ($z=0$) merger rate of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}\,Gpc^{-3}yr^{-1}$} using the B-Spline modulation model 
+which compares to $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}\,Gpc^{-3}yr^{-1}$} for the GWTC-3 result.
 

### 2022-10-18 src/tex/intro.tex
finish toms comments

@@
 As the catalog continues to grow, so does our understanding of the underlying astrophysical population of compact binaries \citep{o1o2_pop,o3a_pop,o3b_astro_dist}.
-Following numerous improvements to the detectors since the last observing run, the anticipated sensitivities for the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration suggest detection rates as high as once per \emph{day} \citep{aLIGO,aVIRGO,LVK_prospects}.
+Following numerous improvements to the detectors since the last observing run, the anticipated sensitivities for the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration suggest detection rates as high as once per \emph{day} \citep{aLIGO,aVIRGO,LVK_prospects,KAGRAProg}.
 With the formation history of these dense objects encoded in the details of their distribution \citep{Zevin_2017}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics.

### 2022-10-18 src/scripts/plot_chieff.py

@@ -11,7 +11,14 @@ default = ppds["Default"]
 mspl = ppds["BSplineInd"]
 mspl2 = ppds['BSplineIID']
 ax = plot_mean_and_90CI(ax, default["chieffs"], default["pchieff"], color='tab:blue', label='Default \n(Abbott et. al. 2021b)', bounds=False)
-ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:purple', label='This Work (Ind Spin)', bounds=False)
+
+with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json", 'r') as jf:
+    o3b_gaussian_data = json.load(jf)
+    o3b_gaussian_chi_eff_grid = np.array(o3b_gaussian_data['chi_eff_grid'])
+    o3b_gaussian_chi_eff_data = np.array(o3b_gaussian_data['chi_eff_pdfs'])
+
+ax = plot_mean_and_90CI(ax, o3b_gaussian_chi_eff_grid, o3b_gaussian_chi_eff_data, color='k', label='Gaussian \n(Abbott et. al. 2021b)', bounds=False)
+ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:orange', label='This Work (Ind Spin)', bounds=False)
 
 #handpicked_ppds = dd.io.load(
 #    paths.data / "BSpline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5"
@@ -23,11 +30,6 @@ ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:purple'
 #    pchiefss[i, :] /= norm
 #ax = plot_mean_and_90CI(ax, xs, pchiefss, color='tab:red', label='BSpline Chi Eff')
 
-with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json", 'r') as jf:
-    o3b_gaussian_data = json.load(jf)
-    o3b_gaussian_chi_eff_grid = np.array(o3b_gaussian_data['chi_eff_grid'])
-    o3b_gaussian_chi_eff_data = np.array(o3b_gaussian_data['chi_eff_pdfs'])
[…]

### 2022-10-18 src/scripts/rate_vs_z_plot.py

@@ -25,7 +25,7 @@ ax = plot_mean_and_90CI(ax, pl_zs, pl_dR, color='tab:blue', bounds=True, fill_al
 ax.plot(zs, me[0] * (1.0 + zs) ** 2.7, lw=5, alpha=0.25, color="k", label=r"SFR: $\lambda_z=2.7$")
 
 ax.set_xlabel(r"$z$", fontsize=18)
-ax.set_ylabel(r"$\mathcal{R}(z)$", fontsize=18)
+ax.set_ylabel(r"$\mathcal{R}(z)\,\mathrm{Gpc}^{-3}\mathrm{yr}^{-1}$", fontsize=18)
 ax.set_yscale("log")
 ax.set_xscale("log")
 ax.set_ylim(5,1e3)

### 2022-10-18 src/tex/appendicies.tex
move PPC to appendix

@@
 and prior choices in table \ref{tab:model_priors}.
+
+\section{Posterior Predictive Checks} \label{sec:ppcs}
+
+\begin{figure*}[ht!]
+    \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
+    \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model.
+The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.
+    \label{fig:ppc}
+    \script{plot_ppcs.py}
+\end{figure*}
+
+We follow the posterior predictive checking procedure done in recent population studies to validate our models inferences \citep{o3a_pop,Edelman_2022ApJ}. 
+For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in \ref{fig:ppc}.
+When the observed region stays encompassed within the predicted region the model is performing well, which we see across each of the fit parameters.

### 2022-10-18 src/tex/appendicies.tex
fix bug
add ffig

@@
 
-\begin{figure*}[ht!]
+\begin{figure}
     \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
     \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model.
-The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.
+The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.}
     \label{fig:ppc}
     \script{plot_ppcs.py}
-\end{figure*}
+\end{figure}
 
 We follow the posterior predictive checking procedure done in recent population studies to validate our models inferences \citep{o3a_pop,Edelman_2022ApJ}. 
-For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in \ref{fig:ppc}.
+For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in figure \ref{fig:ppc}.
 When the observed region stays encompassed within the predicted region the model is performing well, which we see across each of the fit parameters.

### 2022-10-18 src/tex/appendicies.tex
add data citations

@@
 % This appendix goes over in detail the hierarchical bayeisan inference framework
-We use hierarchical Bayesian inference to infer the population properties of CBCs. We want to infer the number density of merging compact binaries  
+We use hierarchical Bayesian inference to infer the population properties of compact binaries. We want to infer the number density of merging compact binaries  
 in the universe and how this can change with their masses, spins, etc. Often times it is useful to formulate the question in terms of the 
@@
 $p(z|\lambda) \propto \frac{dV_c}{dz}\frac{1}{1+z}(1+z)^\lambda$ \citep{Fishbach_2018redshift}. When integrating equation \ref{number_density} across all $\theta$
-and out to some maximum redshift, $z_\mathrm{max}$, we get the total number of CBCs in the universe out to that redshift. We follow previous notations, \
-letting $\{d_i\}$ represent the set of data from $N_\mathrm{obs}$ CBCs observed with gravitational waves. The merger rate is then described as an inhomogeneous 
+and out to some maximum redshift, $z_\mathrm{max}$, we get the total number of compact binaries in the universe out to that redshift. We follow previous notations, \
+letting $\{d_i\}$ represent the set of data from $N_\mathrm{obs}$ compact binaries observed with gravitational waves. The merger rate is then described as an inhomogeneous 
 Poisson process and after imposing the usual log-uniform prior on the merger rate, we marginalize over the merger rate, $\mathcal{R}$, and arrive at the posterior
@@
 \noindent
-where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples. Above, $j$
+where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples \citep{gwtc3DATA}. Above, $j$
 indexes the $K_i$ posterior samples from each event and $\pi(\theta, z)$ is the default prior used by parameter estimations that 

### 2022-10-18 src/tex/results.tex
move PPC to appendix
add data citations

@@
 binary black holes (BBHs) given a catalog of gravitational wave observations. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
-accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist}. Since it was concluded to be an outlier of the rest of 
+accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist,gwtc3DATA}.
+Since it was concluded to be an outlier of the rest of
 the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
@@
 
-Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see features consistent with those inferred by the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist}.
+Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see features consistent with those inferred by the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist,gwtc3_POPDATA}.
 In particular our B-Spline model finds peaks in merger rate density as a function of primary mass at both $\sim10\msun$ and $\sim35\msun$, agreeing with those 
@@
 \end{figure}
-
-\subsection{Posterior Predictive Checks} \label{sec:ppcs}
-
-\begin{figure*}[ht!]
-    \includegraphics[width=\linewidth]{figures/ppc_plot.pdf}
-    \caption{Posterior Predictive Check}
-    \label{fig:ppc}
-    \script{plot_ppcs.py}
-\end{figure*}
-
-Here we describe our posterior predictive checking procedure and results shown in figure \ref{fig:ppc}.

### 2022-10-21 src/tex/conclusion.tex
update for arxiv

@@
 described in this paper and performs hierarchical Bayesian inference with \textsc{NumPyro} and \textsc{Jax} \citep{pyro,numpyro,jax}. 
-Our study paved the way as the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
+Our study paves the way as the first completely non-parametric compact object population study, employing data driven models for each of the hierarchically 
 modeled population distributions. A complete understanding of the population properties of compact objects will help to advance poorly understood areas of stellar and 
-nuclear astrophysics and provide a novel independent cosmological probe. With the coming influx of new data with the LVK's next observing run and the wide 
-range of research avenues the compact object population will help to uncover, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
-sense of the data.
+nuclear astrophysics and provide a novel independent cosmological probe.
+With the coming influx of new data with the LVK's next observing run, development of model-agnostic methods, such as the one we proposed here, will become necessary to efficiently make
+sense of the vast amounts of data and to extract as much information as possible from the population.

### 2022-10-21 src/tex/intro.tex
update for arxiv

@@
 Following numerous improvements to the detectors since the last observing run, the anticipated sensitivities for the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration suggest detection rates as high as once per \emph{day} \citep{aLIGO,aVIRGO,LVK_prospects,KAGRAProg}.
-With the formation history of these dense objects encoded in the details of their distribution \citep{Zevin_2017}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics.
+With the formation history of these dense objects encoded in the details of their distribution \citep{Rodriguez_2016,Farr2017Nature,Zevin_2017,Farr_BinnedSpin}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics.
 Beyond formation physics, population-level inference of the compact binary catalog has also been shown to provide novel measurements of cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo,JoseSpectralSirens}, constrain modified gravitational wave propagation \citep{OkounkovaBirefringence,ModGWProp,ModGWProp2},
@@
 The binary black hole (BBH) mass distribution was first found to have structure beyond a smooth power law with simpler parametric models, exhibiting a possible high mass truncation and either a break or a peak at $m_1\sim35-40\,\msun$ \citep{Fishbach_2017,Talbot_2018,o1o2_pop,o3a_pop}.
-Starting with moderately sized catalog, GWTC-2, more flexible models found signs of additional structure \citep{Tiwari_2021_b,Edelman_2022ApJ}.
+Starting with the moderately sized catalog, GWTC-2, more flexible models found signs of additional structure \citep{Tiwari_2021_b,Edelman_2022ApJ}.
 The evidence supporting these features,
@@
 This simple approach was necessary when data was scarce, but as we move into the data-rich catalog era, this approach is already failing to scale.
-More flexible and scalable methods, such as non-parametric modeling techniques, will be necessary to continue to extract the full information contained in the compact binary catalog.
-In contrast to parametric models, flexible and non-parametric models are data-driven and
-contribute little bias to functional form. Non-parametric or semi-parametric methods are particularly useful to search for unexpected features in the 
-data, providing meaningful insight of these features that parametric models may fail to capture.
+More flexible and scalable methods, such as the non-parametric modeling techniques presented in this manuscript, will be necessary to continue to extract the full information contained in the compact binary catalog.
+In contrast to parametric models, flexible and non-parametric models are data-driven and contribute little bias to functional form.
+They additionally are particularly useful to search for unexpected features in the
+data, providing meaningful insight into features that parametric models may fail to capture.
 
@@
 To ensure we are extracting the full detail the catalog has to offer, we extend our previous non-parametric modeling techniques to include spin magnitudes and tilts, as well as the binary mass ratio and redshift.
-%We present in this manuscript, both to help alleviate the current disputes in the literature and because there has been little work on flexible model development for the 
-%spin distribution of BBHs beyond the aligned spin dimension thus far \citep{Tiwari_2021_a,Tiwari_2021_b}.
 

### 2022-10-21 src/tex/macros.tex
update for arxiv

--- 2022-10-11 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0091, "5th percentile": 0.0039, "95th percentile": 0.03, "10th percentile": 0.0052, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.073, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.031, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.6, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.057, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.032, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0068, "error plus": 0.01, "error minus": 0.0053, "5th percentile": 0.0015, "95th percentile": 0.019, "10th percentile": 0.0023, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.25, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.16, "95th percentile": 0.38, "10th percentile": 0.18, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.031, "error minus": 0.036, "5th percentile": 0.017, "95th percentile": 0.083, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.23, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.76, "10th percentile": 0.36, "90th percentile": 0.71\}, "frac\_hm": \{"median": 0.043, "error plus": 0.065, "error minus": 0.033, "5th percentile": 0.0093, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.094\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0085, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0039, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.032, "error minus": 0.03, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.21, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.82, "10th percentile": 0.43, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.07, "error plus": 0.1, "error minus": 0.053, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@V\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@VIII\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@IX\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@II@out\macros@XVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@II@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@II@out\macros@XVIII\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@III@out\macros@XXIV\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0091, "5th percentile": 0.0039, "95th percentile": 0.03, "10th percentile": 0.0052, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.073, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.031, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.6, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.057, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.032, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0068, "error plus": 0.01, "error minus": 0.0053, "5th percentile": 0.0015, "95th percentile": 0.019, "10th percentile": 0.0023, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.25, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.16, "95th percentile": 0.38, "10th percentile": 0.18, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.031, "error minus": 0.036, "5th percentile": 0.017, "95th percentile": 0.083, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.23, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.76, "10th percentile": 0.36, "90th percentile": 0.71\}, "frac\_hm": \{"median": 0.043, "error plus": 0.065, "error minus": 0.033, "5th percentile": 0.0093, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.094\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0085, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0039, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.032, "error minus": 0.03, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.21, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.82, "10th percentile": 0.43, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.07, "error plus": 0.1, "error minus": 0.053, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.15\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@IV@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@IV@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@IV@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@IV@out\macros@XXVIII\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@V@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@V@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@V@out\macros@XXXI\else\def\macros@V@out{??}\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VI@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VI@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VI@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VI@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VI@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VI@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VI@out{2.4}\else\def\macros@VI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{25}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{4.1}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.7}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{45}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{5.9}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{52}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.79}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{0.82}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{0.86}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{1.1}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{1.0}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{0.51}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{0.74}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.7}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{4.7}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{70}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{5.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{51}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{1.0}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.98}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.37}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0091, "5th percentile": 0.0039, "95th percentile": 0.03, "10th percentile": 0.0052, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.073, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.031, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.6, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.057, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.032, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXV@out\macros@XXXV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXV@out\macros@XXXVI\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"FracBelowNeg0p3": \{"median": 0.0068, "error plus": 0.01, "error minus": 0.0053, "5th percentile": 0.0015, "95th percentile": 0.019, "10th percentile": 0.0023, "90th percentile": 0.015\}, "FracBelow0": \{"median": 0.25, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.16, "95th percentile": 0.38, "10th percentile": 0.18, "90th percentile": 0.36\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.031, "error minus": 0.036, "5th percentile": 0.017, "95th percentile": 0.083, "10th percentile": 0.025, "90th percentile": 0.079\}, "frac\_dyn": \{"median": 0.51, "error plus": 0.23, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.76, "10th percentile": 0.36, "90th percentile": 0.71\}, "frac\_hm": \{"median": 0.043, "error plus": 0.065, "error minus": 0.033, "5th percentile": 0.0093, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.094\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVI@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVI@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVI@out\macros@XXXIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVI@out\macros@XLI\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.016, "error minus": 0.0085, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0039, "90th percentile": 0.025\}, "FracBelow0": \{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.38\}, "PeakChiEff": \{"median": 0.041, "error plus": 0.032, "error minus": 0.03, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.21, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.82, "10th percentile": 0.43, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.07, "error plus": 0.1, "error minus": 0.053, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.15\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVII@out\macros@XLII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVII@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVII@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVII@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVII@out\macros@XLVI\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXVIII@out\macros@XLVII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXVIII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXVIII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXVIII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXVIII@out\macros@LI\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXIX@out\macros@LII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXIX@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXIX@out\macros@LIV\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXX@out\macros@LV\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXX@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXX@out\macros@LVII\else\def\macros@XXX@out{??}\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XXXI@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XXXI@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XXXI@out\macros@LX\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 0.013, "error plus": 0.016, "error minus": 0.0091, "5th percentile": 0.0039, "95th percentile": 0.03, "10th percentile": 0.0052, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{0.0091}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{0.0039}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{0.0052}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{0.026}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.43, "error plus": 0.073, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.073}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.48}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.017, "error plus": 0.031, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.041}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.87, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.6, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.87}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.97}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"median": 0.081, "error plus": 0.098, "error minus": 0.057, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.032, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVI@out{0.081}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVI@out{0.098}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVI@out{0.057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVI@out{0.024}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVI@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVI@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVI@out{0.16}\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"median": 0.0068, "error plus": 0.01, "error minus": 0.0053, "5th percentile": 0.0015, "95th percentile": 0.019, "10th percentile": 0.0023, "90th percentile": 0.015\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVII@out{0.0068}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVII@out{0.01}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVII@out{0.0053}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVII@out{0.019}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVII@out{0.0023}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVII@out{0.015}\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"median": 0.25, "error plus": 0.12, "error minus": 0.089, "5th percentile": 0.16, "95th percentile": 0.38, "10th percentile": 0.18, "90th percentile": 0.36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXVIII@out{0.25}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXVIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXVIII@out{0.089}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXVIII@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXVIII@out{0.38}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXVIII@out{0.36}\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"median": 0.053, "error plus": 0.031, "error minus": 0.036, "5th percentile": 0.017, "95th percentile": 0.083, "10th percentile": 0.025, "90th percentile": 0.079\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIX@out{0.053}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIX@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIX@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIX@out{0.083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIX@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIX@out{0.079}\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.18, "5th percentile": 0.33, "95th percentile": 0.76, "10th percentile": 0.36, "90th percentile": 0.71\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XL@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XL@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XL@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XL@out{0.33}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XL@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XL@out{0.36}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XL@out{0.71}\else\def\macros@XL@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"median": 0.043, "error plus": 0.065, "error minus": 0.033, "5th percentile": 0.0093, "95th percentile": 0.12, "10th percentile": 0.015, "90th percentile": 0.094\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLI@out{0.043}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLI@out{0.065}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLI@out{0.033}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLI@out{0.0093}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLI@out{0.12}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLI@out{0.015}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLI@out{0.094}\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"median": 0.011, "error plus": 0.016, "error minus": 0.0085, "5th percentile": 0.0027, "95th percentile": 0.029, "10th percentile": 0.0039, "90th percentile": 0.025\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLII@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLII@out{0.0085}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLII@out{0.0027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLII@out{0.029}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLII@out{0.0039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLII@out{0.025}\else\def\macros@XLII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.3, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.22}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.38}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.041, "error plus": 0.032, "error minus": 0.03, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.041}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.032}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.03}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.065}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.61, "error plus": 0.21, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.82, "10th percentile": 0.43, "90th percentile": 0.77\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.21}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{0.39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.82}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{0.43}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.77}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.07, "error plus": 0.1, "error minus": 0.053, "5th percentile": 0.017, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.07}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.053}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.15}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.0039}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.39}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.082}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.78}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.024}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{6.7}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{19}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{52}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{9.2}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{21}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{54}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{6.7}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{15}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{52}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "Default": \{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.017, "error minus": 0.009, "5th percentile": 0.0037, "95th percentile": 0.032, "10th percentile": 0.0047, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.14, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.28, "5th percentile": 0.58, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.11, "error minus": 0.056, "5th percentile": 0.023, "95th percentile": 0.2, "10th percentile": 0.029, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.01, "5th percentile": 0.0085, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.34, "error plus": 0.12, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.037, "error minus": 0.032, "5th percentile": 0.0049, "95th percentile": 0.075, "10th percentile": 0.011, "90th percentile": 0.069\}, "frac\_dyn": \{"median": 0.67, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.92, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.063, "5th percentile": 0.053, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.21\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.033, "error plus": 0.024, "error minus": 0.016, "5th percentile": 0.017, "95th percentile": 0.06, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.09, "error minus": 0.1, "5th percentile": 0.31, "95th percentile": 0.5, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.021, "error plus": 0.031, "error minus": 0.032, "5th percentile": {-}0.011, "95th percentile": 0.053, "10th percentile": {-}0.003, "90th percentile": 0.047\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.18, "error minus": 0.21, "5th percentile": 0.62, "95th percentile": 1.0, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.21, "error plus": 0.15, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.37, "10th percentile": 0.12, "90th percentile": 0.34\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{Default}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@V\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@VI\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"lamb": \{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peak_a1}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peak_a2}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@III@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@III@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@III@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@III@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@III@out\macros@XXVIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@IV@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@IV@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@IV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@IV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@IV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@IV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@IV@out\macros@XXXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.017, "error minus": 0.009, "5th percentile": 0.0037, "95th percentile": 0.032, "10th percentile": 0.0047, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.14, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.28, "5th percentile": 0.58, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.11, "error minus": 0.056, "5th percentile": 0.023, "95th percentile": 0.2, "10th percentile": 0.029, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.01, "5th percentile": 0.0085, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.34, "error plus": 0.12, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.037, "error minus": 0.032, "5th percentile": 0.0049, "95th percentile": 0.075, "10th percentile": 0.011, "90th percentile": 0.069\}, "frac\_dyn": \{"median": 0.67, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.92, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.063, "5th percentile": 0.053, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.21\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.033, "error plus": 0.024, "error minus": 0.016, "5th percentile": 0.017, "95th percentile": 0.06, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.09, "error minus": 0.1, "5th percentile": 0.31, "95th percentile": 0.5, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.021, "error plus": 0.031, "error minus": 0.032, "5th percentile": {-}0.011, "95th percentile": 0.053, "10th percentile": {-}0.003, "90th percentile": 0.047\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.18, "error minus": 0.21, "5th percentile": 0.62, "95th percentile": 1.0, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.21, "error plus": 0.15, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.37, "10th percentile": 0.12, "90th percentile": 0.34\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@V@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@V@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@V@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@V@out\macros@XXXIX\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@VI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@VI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@VI@out\macros@XLII\else\def\macros@VI@out{??}\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{2.4}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{25}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.1}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.094}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.073}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.63}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.47}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.6}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.03}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.25}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{4.1}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{25}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.36}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.5}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.064}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.49}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}0.027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{4.6}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{4.1}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{7.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{44}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{9.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{36}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.88}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.86}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.9}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.69}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.88}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.38}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.39}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.67}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.79}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.65}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.94}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXV@out{0.51}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.54}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVI@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVI@out{0.6}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.27}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVII@out{0.58}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVIII@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVIII@out{0.52}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.56}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.6}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.81}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.072}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.27}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{2.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{2.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{4.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.17}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{3.9}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{25}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{8.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{48}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{10}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{41}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.084}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.87}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.24}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.7}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.59}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.44}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.017, "error minus": 0.009, "5th percentile": 0.0037, "95th percentile": 0.032, "10th percentile": 0.0047, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.14, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.041\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.28, "5th percentile": 0.58, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.11, "error minus": 0.056, "5th percentile": 0.023, "95th percentile": 0.2, "10th percentile": 0.029, "90th percentile": 0.17\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVI@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVI@out\macros@XLVII\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.01, "5th percentile": 0.0085, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.033\}, "FracBelow0": \{"median": 0.34, "error plus": 0.12, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.037, "error minus": 0.032, "5th percentile": 0.0049, "95th percentile": 0.075, "10th percentile": 0.011, "90th percentile": 0.069\}, "frac\_dyn": \{"median": 0.67, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.92, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.063, "5th percentile": 0.053, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.21\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVII@out\macros@LII\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.033, "error plus": 0.024, "error minus": 0.016, "5th percentile": 0.017, "95th percentile": 0.06, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.09, "error minus": 0.1, "5th percentile": 0.31, "95th percentile": 0.5, "10th percentile": 0.33, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.021, "error plus": 0.031, "error minus": 0.032, "5th percentile": {-}0.011, "95th percentile": 0.053, "10th percentile": {-}0.003, "90th percentile": 0.047\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.18, "error minus": 0.21, "5th percentile": 0.62, "95th percentile": 1.0, "10th percentile": 0.66, "90th percentile": 0.96\}, "frac\_hm": \{"median": 0.21, "error plus": 0.15, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.37, "10th percentile": 0.12, "90th percentile": 0.34\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVIII@out\macros@LVII\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXIX@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXIX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXIX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXIX@out\macros@LXII\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XL@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XL@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XL@out\macros@LXV\else\def\macros@XL@out{??}\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLI@out\macros@LXVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLI@out\macros@LXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLI@out\macros@LXVIII\else\ifnum\pdfstrcmp{#1}{peaks}=0\let\macros@XLI@out\macros@LXIX\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLII@out\macros@LXX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLII@out\macros@LXXI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLII@out\macros@LXXII\else\def\macros@XLII@out{??}\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.013, "error plus": 0.017, "error minus": 0.009, "5th percentile": 0.0037, "95th percentile": 0.032, "10th percentile": 0.0047, "90th percentile": 0.027\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.009}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.0037}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.032}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.0047}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.027}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.43, "error plus": 0.076, "error minus": 0.14, "5th percentile": 0.29, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.076}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.29}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.49}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.017, "error plus": 0.032, "error minus": 0.024, "5th percentile": {-}0.007, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.041\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.032}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{{-}0.007}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.051}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.041}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.86, "error plus": 0.15, "error minus": 0.28, "5th percentile": 0.58, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.28}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.58}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.66}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.97}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.079, "error plus": 0.11, "error minus": 0.056, "5th percentile": 0.023, "95th percentile": 0.2, "10th percentile": 0.029, "90th percentile": 0.17\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.079}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.056}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.029}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.17}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.019, "error plus": 0.02, "error minus": 0.01, "5th percentile": 0.0085, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.033\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.0085}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.041}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.033}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.34, "error plus": 0.12, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.43\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.098}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.43}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.037, "error plus": 0.037, "error minus": 0.032, "5th percentile": 0.0049, "95th percentile": 0.075, "10th percentile": 0.011, "90th percentile": 0.069\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.037}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.037}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.032}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.0049}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.075}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.011}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.069}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.67, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.92, "10th percentile": 0.52, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.67}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.48}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.92}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.86}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.12, "error plus": 0.12, "error minus": 0.063, "5th percentile": 0.053, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.063}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{0.053}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.25}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{0.064}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.21}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.033, "error plus": 0.024, "error minus": 0.016, "5th percentile": 0.017, "95th percentile": 0.06, "10th percentile": 0.02, "90th percentile": 0.054\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.033}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.024}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.06}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.054}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.41, "error plus": 0.09, "error minus": 0.1, "5th percentile": 0.31, "95th percentile": 0.5, "10th percentile": 0.33, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.09}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.31}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.48}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.021, "error plus": 0.031, "error minus": 0.032, "5th percentile": {-}0.011, "95th percentile": 0.053, "10th percentile": {-}0.003, "90th percentile": 0.047\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.021}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.032}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{{-}0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.053}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.047}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.82, "error plus": 0.18, "error minus": 0.21, "5th percentile": 0.62, "95th percentile": 1.0, "10th percentile": 0.66, "90th percentile": 0.96\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.82}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.21}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{0.62}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{0.66}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.96}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 0.21, "error plus": 0.15, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.37, "10th percentile": 0.12, "90th percentile": 0.34\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{0.37}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{0.34}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{0.0039}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{0.39}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{0.082}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{0.78}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{0.024}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.7}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{19}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\newcommand\macros@LXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVI@out{\{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVI@out{8.5}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVI@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVI@out{7.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVI@out{9.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVI@out{7.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVI@out{9.0}\else\def\macros@LXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVI@out}\newcommand\macros@LXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVII@out{\{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVII@out{1.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVII@out{21}\else\def\macros@LXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVII@out}\newcommand\macros@LXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVIII@out{\{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVIII@out{46}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVIII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVIII@out{6.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVIII@out{59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVIII@out{55}\else\def\macros@LXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVIII@out}\newcommand\macros@LXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIX@out{\{"10": \{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}}\else\ifnum\pdfstrcmp{#1}{10}=0\let\macros@LXIX@out\macros@LXXIII\else\ifnum\pdfstrcmp{#1}{18}=0\let\macros@LXIX@out\macros@LXXIV\else\ifnum\pdfstrcmp{#1}{35}=0\let\macros@LXIX@out\macros@LXXV\else\def\macros@LXIX@out{??}\fi\fi\fi\fi\macros@LXIX@out}\newcommand\macros@LXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXX@out{6.7}\else\def\macros@LXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXX@out}\newcommand\macros@LXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXI@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXI@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXI@out{15}\else\def\macros@LXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXI@out}\newcommand\macros@LXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXII@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXII@out{52}\else\def\macros@LXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXII@out}\newcommand\macros@LXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXIII@out{\{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXIII@out{9.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXIII@out{0.63}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXIII@out{9.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXIII@out{11}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXIII@out{10}\else\def\macros@LXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXIII@out}\newcommand\macros@LXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXIV@out{\{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXIV@out{19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXIV@out{3.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXIV@out{2.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXIV@out{16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXIV@out{22}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXIV@out{17}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXIV@out{21}\else\def\macros@LXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXIV@out}\newcommand\macros@LXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXV@out{\{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXV@out{33}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXV@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXV@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXV@out{30}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXV@out{35}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXV@out{31}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXV@out{35}\else\def\macros@LXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXV@out}\makeatother

### 2022-10-21 src/tex/ms.tex
add zo's acknowledgements
add more citations -- remove \bruce{} flags
add ppc plot and some tables to try and make results presentation cleaner and more complete
go back to syw version==0.3.0 instead to fix clickable icons
update for arxiv

@@
 \documentclass[twocolumn, linenumbers]{aastex631}
+
+\usepackage{showyourwork}
+\usepackage{bm}
+\usepackage{amsmath}
+\usepackage{appendix}
+
+\input{macros}
+\newcommand{\CIPlusMinus}[1]{{#1[median]^{+#1[error plus]}_{-#1[error minus]}}}
+\newcommand{\CIBoundsBracket}[1]{{[#1[5th percentile], #1[95th percentile]]}}
+\newcommand{\CIBoundsDash}[1]{{#1[5th percentile]\textendash#1[95th percentile]}}
 
@@
 
-\newcommand{\CIPlusMinus}[1]{{#1[median]^{+#1[error plus]}_{-#1[error minus]}}}
-\newcommand{\CIBoundsBracket}[1]{{[#1[5th percentile], #1[95th percentile]]}}
-\newcommand{\CIBoundsDash}[1]{{#1[5th percentile]\textendash#1[95th percentile]}}
-
 \graphicspath{{./}{figures/}}
-
-\usepackage{showyourwork}
-\usepackage{bm}
-\usepackage{amsmath}
-\usepackage{appendix}
-\input{macros}
 
@@
 We introduce the first complete non-parametric model for the astrophysical distribution of the binary black hole (BBH) population.
-Constructed from basis splines, we use these models to conduct the most comprehensive data-driven investigation of the BBH population to date, including non-parametric modeling of BBH mass ratio, spin magnitudes and misalignments, and redshift distributions for the first time.
+Constructed from basis splines, we use these models to conduct the most comprehensive data-driven investigation of the BBH population to date, simultaneously fitting non-parametric models for the BBH mass ratio, spin magnitude and misalignment, and redshift distributions for the first time.
 Using the 69 confident BBHs in GWTC-3, we report the same features previously recovered
 with similarly flexible models of the mass distribution, most notably the peaks in merger rates at primary masses of ${\sim}10\msun$ and ${\sim}35\msun$.
+Our model reports a suppressed merger rate at low primary masses and a mass ratio distribution consistent with a power law.
 We infer a distribution for primary spin misalignments that peaks away from alignment, supporting recent work that used a variety of parameterized models to come to the same conclusion.
@@
 Using our non-parametric models, we explore whether the data support spin distributions unique for each binary component, and 
-find no strong evidence that the distributions differ. We conclude with a discussion of how non-parametric methods in 
+find no strong evidence that the distributions differ. With a modulated power law describing the BBH merger rate's evolution in redshift, 
+we see hints of the rate evolution either flattening or decreasing at $z\sim0.2-0.5$, but the full distribution remains entirely consistent with a monotonically increasing power law.
+We conclude with a discussion of the astrophysical context of our new findings and how non-parametric methods in
 gravitational-wave population inference are uniquely poised to complement to the parametric approach as we enter the 
 data-rich era of gravitational-wave astronomy.
-
-%When modeling the $\chi_\mathrm{eff}$ distribution with our model we find similar 
-%conclusions as previously reported: the distribution is consistent with a non-isotropic distribution (that peaks at $\chi_\mathrm{eff}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][PeakChiEff]}$}),
-%showing considerable support ($f_{\chi_\mathrm{eff}<0}=\,$\result{$\CIPlusMinus{\macros[ChiEffective][chieff][FracBelow0]}$}) for negative effective spins or misaligned systems.
 \end{abstract}
@@
 \input{intro.tex}
+
 \input{methods.tex}
+
 \input{results.tex}
+
 \input{conclusion.tex}
@@
 along with helpful comments on an early draft by Tom Callister and Jaxen Godfrey.
-This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
+In the spirit of open source and reproducible science, this paper was written using the \textsc{showyourwork} package, published at \url{https://github.com/bruce-edelman/CoveringYourBasis} \citep{Luger2021}.
+Z.D.
+also acknowledges support from the CIERA Board
+of Visitors Research Professorship. This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
 (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
@@
 \software{
+\textsc{ShowYourWork}~\citep{Luger2021},
 \textsc{Matplotlib}~\citep{Hunter:2007},

### 2022-10-21 src/tex/results.tex
update for arxiv

@@
 The B-Spline model finds the same feature at $\sim18\msun$ as the \textsc{PowerlawSpline} model, but remains consistent with the \textsc{PowerlawPeak} model; the mass distribution is more uncertain in this region.
+For each of these features we find the local maximums occurring at primary masses of \result{$\CIPlusMinus{\macros[MassDistribution][BSpline][peaks][10]}\,\msun$},
+\result{$\CIPlusMinus{\macros[MassDistribution][BSpline][peaks][18]}\,\msun$}, and  
+\result{$\CIPlusMinus{\macros[MassDistribution][BSpline][peaks][35]}\,\msun$} all at 90\% credibility.
 We find the largest disagreement at low masses, where the power-law-based models show a higher rate below ${\sim}8-9\msun$.
@@
 similar to the inferred minimum mass in \citet{o3b_astro_dist}.
-The lack of observations of binaries with low primary mass make rate estimates in this region strongly model and prior dependent.
+The lack of observations of binaries with low primary mass make rate estimates in this region strongly model dependent, while our flexible model provides an informed upper limit on the rate in this region and given the selection effects and that there are no observations.
 We could be seeing signs of a decrease in merger rate from a ``lower mass gap'' between neutron star and BH masses, or we could be seeing fluctuations due to low-number statistics.
@@
         B-Spline Ind(secondary) & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peak_a2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][a2_90percentile]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][peakCosTilt2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][negFrac2]}$ & $\CIPlusMinus{\macros[BSplineIndependentCompSpins][log10gammaFrac2]}$  \\ \hline
-        \textsc{Default} & $\CIPlusMinus{\macros[Default][peak_a]}$ & $\CIPlusMinus{\macros[Default][a_90percentile]}$ & $\CIPlusMinus{\macros[Default][peakCosTilt]}$ & $\CIPlusMinus{\macros[Default][negFrac]}$ & $\CIPlusMinus{\macros[Default][log10gammaFrac]}$ \\ \hline
+        \textsc{Default} \citep{o3b_astro_dist} & $\CIPlusMinus{\macros[Default][peak_a]}$ & $\CIPlusMinus{\macros[Default][a_90percentile]}$ & $\CIPlusMinus{\macros[Default][peakCosTilt]}$ & $\CIPlusMinus{\macros[Default][negFrac]}$ & $\CIPlusMinus{\macros[Default][log10gammaFrac]}$ \\ \hline
     \end{tabular}
@@
 
-We model the spin magnitude distributions as IID B-Spline distributions as a check to the assumptions of the \textsc{Default} model. 
-Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the B-Spline model, compared with the \textsc{Default} model. 
+We model the spin magnitude distributions as IID B-Spline distributions. 
+Figure \ref{fig:iid_spinmag_dist} shows the inferred spin magnitude distribution with the B-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
 The B-Spline model results are consistent with those using the Beta distribution, peaking near $a\sim0.2$, with 90\% of BBH spins below 
@@
 
-The \textsc{Default} spin model (used by \citet{o3b_astro_dist}) also assumes the spin orientation of both components are identical and independently distributed (IID), with a mixture model over an
+The \textsc{Default} spin model (used in \citet{o3a_pop, o3b_astro_dist}) also assumes the spin orientation of both components are identical and independently distributed (IID), with a mixture model over an
 aligned and an isotropic component. The aligned component is modeled with a truncated Gaussian distribution with mean at $\cos{\theta}=1$ and variance a free 
@@
         B-Spline Ind & $\CIPlusMinus{\macros[ChiEffective][ind][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][ind][frac_hm]}$ \\ \hline
-        \textsc{Default} & $\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][default][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][default][frac_hm]}$ \\ \hline
-        \textsc{Gaussian} & $\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][frac_hm]}$ \\ \hline
+        \textsc{Default} \citep{o3b_astro_dist} & $\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][default][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][default][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][default][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][default][frac_hm]}$ \\ \hline
+        \textsc{Gaussian} \citep{o3b_astro_dist}  & $\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelow0]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][FracBelowNeg0p3]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][frac_dyn]}$ & $\CIPlusMinus{\macros[ChiEffective][gaussian][frac_hm]}$ \\ \hline
     \end{tabular}
@@
 along with results on the \textsc{Default} \citep{Talbot_2017} and \textsc{Gaussian} \citep{Miller2020} models from \citet{o3b_astro_dist}. We find considerable agreement 
-among the effective spin distributions, but the more flexible B-Spline models in component spins more closely resemble results from the \textsc{Gaussian} model that directly models $\chi_\mathrm{eff}$, than the \textsc{Default} model.
-This could indicate that the population fit is driven by $\chi_\mathrm{eff}$
-more than the component spin dimensions. The B-Spline model finds very similar shapes to the other models, with a peak centered at 
+among the effective spin distributions, but the more flexible B-Spline models in component spins more closely resemble results from the \textsc{Default} model, also using the component spins.
+The B-Spline model finds very similar shapes to the other models, with a single peak centered at
 $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][iid][PeakChiEff]}$}, compared to 
 $\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][default][PeakChiEff]}$} with the \textsc{Default} model and 
-$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$} with the \textsc{Gaussian} $\chi_\mathrm{eff}$ model. 
+$\chi_\mathrm{eff}=$\result{$\CIPlusMinus{\macros[ChiEffective][gaussian][PeakChiEff]}$} with the \textsc{Gaussian} $\chi_\mathrm{eff}$ models from \citet{o3b_astro_dist}. 
 As for spin misalignment, we calculate the fraction of systems with effective spins that are misaligned (i.e. $\chi_\mathrm{eff}<0$) and find similar 

### 2022-10-21 src/scripts/create_macros.py

@@ -38,6 +38,17 @@ def get_percentile(pdfs, xs, perc):
         x.append(xs[i])
     return np.array(x)
 
+def get_mass_peaks(ms, ps):
+    low_sel = ms < 15
+    mid_sel = (15 <= ms) & (ms < 25)
+    high_sel = (25 <= ms) & (ms < 45)
+    peaks = {'10': [], '18': [], '35': []}
+    for i in range(ps.shape[0]):
+        for sel,k in zip([low_sel, mid_sel, high_sel], ['10', '18', '35']):
+            idx = np.argmax(ps[i,sel])
+            peaks[k].append(ms[sel][idx])
+    return peaks
+    
 def BSplineMassMacros():
     print("Saving Mass Distribution Macros...")
     ms, m_pdfs, _, _ = load_mass_ppd()
@@ -51,10 +62,15 @@ def BSplineMassMacros():
     ps_mpdfs, _, ps_ms, _ = load_o3b_paper_run_masspdf(paths.data / 'spline_20n_mass_m_iid_mag_iid_tilt_powerlaw_redshift_mass_data.h5')
     ps_m1s = get_percentile(plpeak_mpdfs, plpeak_ms, 1) 
     ps_m99s = get_percentile(ps_mpdfs, ps_ms, 99)
-    ps_m75s = get_percentile(ps_mpdfs, ps_ms, 75)  
+    ps_m75s = get_percentile(ps_mpdfs, ps_ms, 75)
+    bspline_peaks = get_mass_peaks(ms, m_pdfs)
     return {'PLPeak': {'m_1percentile': save_param_cred_intervals(plpeak_m1s), 'm_75percentile': save_param_cred_intervals(plpeak_m75s), 'm_99percentile': save_param_cred_intervals(plpeak_m99s)}, 
-            'BSpline': {'m_1percentile': save_param_cred_intervals(m1s), 'm_75percentile': save_param_cred_intervals(m75s), 'm_99percentile': save_param_cred_intervals(m99s)}, 
+            'BSpline': {'m_1percentile': save_param_cred_intervals(m1s), 'm_75percentile': save_param_cred_intervals(m75s), 'm_99percentile': save_param_cred_intervals(m99s), 
+                        'peaks': {'10': save_param_cred_intervals(np.array(bspline_peaks['10'])), 
+                                  '18': save_param_cred_intervals(np.array(bspline_peaks['18'])), 
[…]

### 2022-10-21 src/tex/macros.tex
twocolumn

--- 2022-10-15 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "Default": \{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peak\_a1": \{"median": 0.24, "error plus": 0.16, "error minus": 0.24, "5th percentile": 0.0, "95th percentile": 0.38, "10th percentile": 0.052, "90th percentile": 0.34\}, "peak\_a2": \{"median": 0.11, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.0, "95th percentile": 0.26, "10th percentile": 0.0, "90th percentile": 0.22\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "peak\_a": \{"median": 0.2, "error plus": 0.083, "error minus": 0.18, "5th percentile": 0.017, "95th percentile": 0.27, "10th percentile": 0.087, "90th percentile": 0.26\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.018, "error minus": 0.0091, "5th percentile": 0.0042, "95th percentile": 0.033, "10th percentile": 0.0053, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.072, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.03, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.14, "error minus": 0.26, "5th percentile": 0.6, "95th percentile": 0.98, "10th percentile": 0.68, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.083, "error plus": 0.11, "error minus": 0.057, "5th percentile": 0.026, "95th percentile": 0.21, "10th percentile": 0.033, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.012, "error minus": 0.0057, "5th percentile": 0.0016, "95th percentile": 0.021, "10th percentile": 0.0024, "90th percentile": 0.017\}, "FracBelow0": \{"median": 0.27, "error plus": 0.12, "error minus": 0.1, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.18, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.034, "error minus": 0.04, "5th percentile": 0.013, "95th percentile": 0.085, "10th percentile": 0.023, "90th percentile": 0.075\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.24, "error minus": 0.21, "5th percentile": 0.34, "95th percentile": 0.79, "10th percentile": 0.37, "90th percentile": 0.74\}, "frac\_hm": \{"median": 0.046, "error plus": 0.077, "error minus": 0.036, "5th percentile": 0.01, "95th percentile": 0.13, "10th percentile": 0.015, "90th percentile": 0.11\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.015, "error minus": 0.0077, "5th percentile": 0.0029, "95th percentile": 0.028, "10th percentile": 0.004, "90th percentile": 0.023\}, "FracBelow0": \{"median": 0.31, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.81, "10th percentile": 0.44, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.066, "error plus": 0.096, "error minus": 0.048, "5th percentile": 0.018, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.14\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{Default}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@V\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@VI\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"lamb": \{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}, "local\_rate": \{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}, "a1\_90percentile": \{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}, "a2\_90percentile": \{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}, "peak\_a1": \{"median": 0.24, "error plus": 0.16, "error minus": 0.24, "5th percentile": 0.0, "95th percentile": 0.38, "10th percentile": 0.052, "90th percentile": 0.34\}, "peak\_a2": \{"median": 0.11, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.0, "95th percentile": 0.26, "10th percentile": 0.0, "90th percentile": 0.22\}, "peakCosTilt1": \{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}, "peakCosTilt2": \{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}, "log10gammaFrac1": \{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}, "log10gammaFrac2": \{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}, "negFrac1": \{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}, "negFrac2": \{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peak_a1}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peak_a2}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@III@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@III@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@III@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@III@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@III@out\macros@XXVIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"a\_90percentile": \{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}, "peak\_a": \{"median": 0.2, "error plus": 0.083, "error minus": 0.18, "5th percentile": 0.017, "95th percentile": 0.27, "10th percentile": 0.087, "90th percentile": 0.26\}, "lamb": \{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}, "local\_rate": \{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}, "negFrac": \{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@IV@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@IV@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@IV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@IV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@IV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@IV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@IV@out\macros@XXXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.018, "error minus": 0.0091, "5th percentile": 0.0042, "95th percentile": 0.033, "10th percentile": 0.0053, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.072, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.03, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.14, "error minus": 0.26, "5th percentile": 0.6, "95th percentile": 0.98, "10th percentile": 0.68, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.083, "error plus": 0.11, "error minus": 0.057, "5th percentile": 0.026, "95th percentile": 0.21, "10th percentile": 0.033, "90th percentile": 0.17\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.012, "error minus": 0.0057, "5th percentile": 0.0016, "95th percentile": 0.021, "10th percentile": 0.0024, "90th percentile": 0.017\}, "FracBelow0": \{"median": 0.27, "error plus": 0.12, "error minus": 0.1, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.18, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.034, "error minus": 0.04, "5th percentile": 0.013, "95th percentile": 0.085, "10th percentile": 0.023, "90th percentile": 0.075\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.24, "error minus": 0.21, "5th percentile": 0.34, "95th percentile": 0.79, "10th percentile": 0.37, "90th percentile": 0.74\}, "frac\_hm": \{"median": 0.046, "error plus": 0.077, "error minus": 0.036, "5th percentile": 0.01, "95th percentile": 0.13, "10th percentile": 0.015, "90th percentile": 0.11\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.015, "error minus": 0.0077, "5th percentile": 0.0029, "95th percentile": 0.028, "10th percentile": 0.004, "90th percentile": 0.023\}, "FracBelow0": \{"median": 0.31, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.81, "10th percentile": 0.44, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.066, "error plus": 0.096, "error minus": 0.048, "5th percentile": 0.018, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.14\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@V@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@V@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@V@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@V@out\macros@XXXIX\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@VI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@VI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@VI@out\macros@XLII\else\def\macros@VI@out{??}\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{2.4}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{25}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.1}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.094}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.073}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.63}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.47}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.6}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.03}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.25}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{4.1}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{25}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.36}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.5}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.064}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.49}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 2.3, "error plus": 2.9, "error minus": 3.0, "5th percentile": {-}0.63, "95th percentile": 5.2, "10th percentile": {-}0.024, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{2.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}0.63}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{5.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{{-}0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{4.7}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 18, "error plus": 45, "error minus": 14, "5th percentile": 4.2, "95th percentile": 71, "10th percentile": 5.9, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{45}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{5.9}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{52}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.59, "error plus": 0.24, "error minus": 0.17, "5th percentile": 0.42, "95th percentile": 0.85, "10th percentile": 0.45, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.45}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.79}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.59, "error plus": 0.29, "error minus": 0.3, "5th percentile": 0.3, "95th percentile": 0.87, "10th percentile": 0.35, "90th percentile": 0.82\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.87}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.82}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.24, "error plus": 0.16, "error minus": 0.24, "5th percentile": 0.0, "95th percentile": 0.38, "10th percentile": 0.052, "90th percentile": 0.34\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.38}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.052}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.34}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.11, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.0, "95th percentile": 0.26, "10th percentile": 0.0, "90th percentile": 0.22\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.26}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.22}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.48, "error plus": 0.59, "error minus": 0.74, "5th percentile": {-}0.26, "95th percentile": 1.0, "10th percentile": {-}0.11, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.26}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.86}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.39, "error plus": 0.82, "error minus": 1.4, "5th percentile": {-}1.0, "95th percentile": 1.0, "10th percentile": {-}0.87, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.39}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.82}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{{-}1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{{-}0.87}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{1.0}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": 0.47, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.37, "95th percentile": 1.3, "10th percentile": {-}0.19, "90th percentile": 1.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.47}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{{-}0.37}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXV@out{{-}0.19}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXV@out{1.1}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": 0.22, "error plus": 1.0, "error minus": 1.0, "5th percentile": {-}0.79, "95th percentile": 1.3, "10th percentile": {-}0.58, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{{-}0.79}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{1.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVI@out{{-}0.58}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVI@out{1.0}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": 0.26, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.09, "95th percentile": 0.58, "10th percentile": 0.11, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.09}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.58}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVII@out{0.51}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": 0.4, "error plus": 0.37, "error minus": 0.29, "5th percentile": 0.11, "95th percentile": 0.8, "10th percentile": 0.14, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.37}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.29}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVIII@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVIII@out{0.74}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.51, "error plus": 0.23, "error minus": 0.14, "5th percentile": 0.36, "95th percentile": 0.76, "10th percentile": 0.38, "90th percentile": 0.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.51}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.36}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.76}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.38}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.7}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.2, "error plus": 0.083, "error minus": 0.18, "5th percentile": 0.017, "95th percentile": 0.27, "10th percentile": 0.087, "90th percentile": 0.26\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.083}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.087}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.26}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 2.4, "error plus": 2.8, "error minus": 3.1, "5th percentile": {-}0.65, "95th percentile": 5.3, "10th percentile": 0.15, "90th percentile": 4.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{2.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{3.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{5.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.15}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{4.7}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 16, "error plus": 46, "error minus": 12, "5th percentile": 4.2, "95th percentile": 70, "10th percentile": 5.8, "90th percentile": 51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{4.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{70}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{5.8}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{51}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.44, "error plus": 0.51, "error minus": 0.44, "5th percentile": {-}0.0013, "95th percentile": 1.0, "10th percentile": 0.12, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.0013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{1.0}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.34, "error plus": 0.8, "error minus": 0.74, "5th percentile": {-}0.4, "95th percentile": 1.2, "10th percentile": {-}0.25, "90th percentile": 0.98\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.74}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.4}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{1.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.98}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.27, "error plus": 0.14, "error minus": 0.11, "5th percentile": 0.16, "95th percentile": 0.41, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.37}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.018, "error minus": 0.0091, "5th percentile": 0.0042, "95th percentile": 0.033, "10th percentile": 0.0053, "90th percentile": 0.027\}, "FracBelow0": \{"median": 0.43, "error plus": 0.072, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.03, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.14, "error minus": 0.26, "5th percentile": 0.6, "95th percentile": 0.98, "10th percentile": 0.68, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.083, "error plus": 0.11, "error minus": 0.057, "5th percentile": 0.026, "95th percentile": 0.21, "10th percentile": 0.033, "90th percentile": 0.17\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVI@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVI@out\macros@XLVII\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"FracBelowNeg0p3": \{"median": 0.0073, "error plus": 0.012, "error minus": 0.0057, "5th percentile": 0.0016, "95th percentile": 0.021, "10th percentile": 0.0024, "90th percentile": 0.017\}, "FracBelow0": \{"median": 0.27, "error plus": 0.12, "error minus": 0.1, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.18, "90th percentile": 0.37\}, "PeakChiEff": \{"median": 0.053, "error plus": 0.034, "error minus": 0.04, "5th percentile": 0.013, "95th percentile": 0.085, "10th percentile": 0.023, "90th percentile": 0.075\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.24, "error minus": 0.21, "5th percentile": 0.34, "95th percentile": 0.79, "10th percentile": 0.37, "90th percentile": 0.74\}, "frac\_hm": \{"median": 0.046, "error plus": 0.077, "error minus": 0.036, "5th percentile": 0.01, "95th percentile": 0.13, "10th percentile": 0.015, "90th percentile": 0.11\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVII@out\macros@LII\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.011, "error plus": 0.015, "error minus": 0.0077, "5th percentile": 0.0029, "95th percentile": 0.028, "10th percentile": 0.004, "90th percentile": 0.023\}, "FracBelow0": \{"median": 0.31, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.61, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.81, "10th percentile": 0.44, "90th percentile": 0.77\}, "frac\_hm": \{"median": 0.066, "error plus": 0.096, "error minus": 0.048, "5th percentile": 0.018, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.14\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVIII@out\macros@LVII\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXIX@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXIX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXIX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXIX@out\macros@LXII\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XL@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XL@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XL@out\macros@LXV\else\def\macros@XL@out{??}\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"m\_1percentile": \{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}, "m\_75percentile": \{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLI@out\macros@LXVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLI@out\macros@LXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLI@out\macros@LXVIII\else\def\macros@XLI@out{??}\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLII@out\macros@LXIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLII@out\macros@LXX\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLII@out\macros@LXXI\else\def\macros@XLII@out{??}\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.013, "error plus": 0.018, "error minus": 0.0091, "5th percentile": 0.0042, "95th percentile": 0.033, "10th percentile": 0.0053, "90th percentile": 0.027\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.018}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.0091}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.0042}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.033}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.0053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.027}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.43, "error plus": 0.072, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.072}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.34}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.48}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.017, "error plus": 0.03, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.049, "10th percentile": {-}0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.03}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.049}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.043}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.86, "error plus": 0.14, "error minus": 0.26, "5th percentile": 0.6, "95th percentile": 0.98, "10th percentile": 0.68, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.6}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.68}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.97}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.083, "error plus": 0.11, "error minus": 0.057, "5th percentile": 0.026, "95th percentile": 0.21, "10th percentile": 0.033, "90th percentile": 0.17\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.083}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.026}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.033}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.17}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.0073, "error plus": 0.012, "error minus": 0.0057, "5th percentile": 0.0016, "95th percentile": 0.021, "10th percentile": 0.0024, "90th percentile": 0.017\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.0073}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.012}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.0057}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.0016}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.021}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.0024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.017}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.27, "error plus": 0.12, "error minus": 0.1, "5th percentile": 0.17, "95th percentile": 0.39, "10th percentile": 0.18, "90th percentile": 0.37\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.27}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.17}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.37}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.053, "error plus": 0.034, "error minus": 0.04, "5th percentile": 0.013, "95th percentile": 0.085, "10th percentile": 0.023, "90th percentile": 0.075\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.053}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.04}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.013}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.085}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.023}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.075}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.55, "error plus": 0.24, "error minus": 0.21, "5th percentile": 0.34, "95th percentile": 0.79, "10th percentile": 0.37, "90th percentile": 0.74\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.21}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.34}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.79}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.37}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.74}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.046, "error plus": 0.077, "error minus": 0.036, "5th percentile": 0.01, "95th percentile": 0.13, "10th percentile": 0.015, "90th percentile": 0.11\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.046}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.077}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.036}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{0.01}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.13}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{0.015}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.11}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.011, "error plus": 0.015, "error minus": 0.0077, "5th percentile": 0.0029, "95th percentile": 0.028, "10th percentile": 0.004, "90th percentile": 0.023\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.011}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.015}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.0077}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.0029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.028}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.004}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.023}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.31, "error plus": 0.1, "error minus": 0.11, "5th percentile": 0.2, "95th percentile": 0.41, "10th percentile": 0.22, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.31}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.2}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.22}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.39}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.039, "error plus": 0.033, "error minus": 0.028, "5th percentile": 0.011, "95th percentile": 0.073, "10th percentile": 0.017, "90th percentile": 0.063\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.033}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.028}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{0.017}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.063}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.61, "error plus": 0.2, "error minus": 0.22, "5th percentile": 0.39, "95th percentile": 0.81, "10th percentile": 0.44, "90th percentile": 0.77\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.61}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{0.39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{0.81}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.77}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 0.066, "error plus": 0.096, "error minus": 0.048, "5th percentile": 0.018, "95th percentile": 0.18, "10th percentile": 0.025, "90th percentile": 0.14\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{0.066}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.096}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{0.048}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{0.018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{0.18}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{0.025}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{0.14}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{0.0039}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{0.39}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{0.082}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{0.78}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{0.024}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.7}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{19}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\newcommand\macros@LXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVI@out{\{"median": 8.7, "error plus": 0.64, "error minus": 0.94, "5th percentile": 7.8, "95th percentile": 9.3, "10th percentile": 8.1, "90th percentile": 9.2\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVI@out{8.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVI@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVI@out{0.94}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVI@out{7.8}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVI@out{9.3}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVI@out{8.1}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVI@out{9.2}\else\def\macros@LXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVI@out}\newcommand\macros@LXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVII@out{\{"median": 12, "error plus": 13, "error minus": 1.1, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVII@out{21}\else\def\macros@LXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVII@out}\newcommand\macros@LXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVIII@out{\{"median": 45, "error plus": 10, "error minus": 6.2, "5th percentile": 39, "95th percentile": 57, "10th percentile": 40, "90th percentile": 54\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVIII@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVIII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVIII@out{57}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVIII@out{54}\else\def\macros@LXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVIII@out}\newcommand\macros@LXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIX@out{6.7}\else\def\macros@LXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIX@out}\newcommand\macros@LXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXX@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXX@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXX@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXX@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXX@out{15}\else\def\macros@LXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXX@out}\newcommand\macros@LXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXI@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXI@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXI@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXI@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXI@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXI@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXI@out{52}\else\def\macros@LXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXI@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "Default": \{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0095, "5th percentile": 0.0035, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.26, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.059, "5th percentile": 0.022, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.019, "error minus": 0.012, "5th percentile": 0.0071, "95th percentile": 0.04, "10th percentile": 0.0093, "90th percentile": 0.034\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.23, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.035, "error minus": 0.038, "5th percentile": 0.001, "95th percentile": 0.073, "10th percentile": 0.011, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.69, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.47, "95th percentile": 0.9, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.074, "5th percentile": 0.045, "95th percentile": 0.25, "10th percentile": 0.058, "90th percentile": 0.21\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.035, "error plus": 0.026, "error minus": 0.018, "5th percentile": 0.017, "95th percentile": 0.062, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.085, "error minus": 0.088, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.034, "error minus": 0.034, "5th percentile": {-}0.011, "95th percentile": 0.057, "10th percentile": {-}0.003, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.22, "error plus": 0.16, "error minus": 0.11, "5th percentile": 0.11, "95th percentile": 0.39, "10th percentile": 0.12, "90th percentile": 0.34\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{Default}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@V\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@VI\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"lamb": \{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peak_a1}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peak_a2}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@III@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@III@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@III@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@III@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@III@out\macros@XXVIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@IV@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@IV@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@IV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@IV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@IV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@IV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@IV@out\macros@XXXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0095, "5th percentile": 0.0035, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.26, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.059, "5th percentile": 0.022, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.019, "error minus": 0.012, "5th percentile": 0.0071, "95th percentile": 0.04, "10th percentile": 0.0093, "90th percentile": 0.034\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.23, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.035, "error minus": 0.038, "5th percentile": 0.001, "95th percentile": 0.073, "10th percentile": 0.011, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.69, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.47, "95th percentile": 0.9, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.074, "5th percentile": 0.045, "95th percentile": 0.25, "10th percentile": 0.058, "90th percentile": 0.21\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.035, "error plus": 0.026, "error minus": 0.018, "5th percentile": 0.017, "95th percentile": 0.062, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.085, "error minus": 0.088, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.034, "error minus": 0.034, "5th percentile": {-}0.011, "95th percentile": 0.057, "10th percentile": {-}0.003, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.22, "error plus": 0.16, "error minus": 0.11, "5th percentile": 0.11, "95th percentile": 0.39, "10th percentile": 0.12, "90th percentile": 0.34\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@V@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@V@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@V@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@V@out\macros@XXXIX\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@VI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@VI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@VI@out\macros@XLII\else\def\macros@VI@out{??}\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{2.4}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{25}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.1}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.094}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.073}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.63}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.47}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.6}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.03}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.25}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{4.1}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{25}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.36}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.5}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.064}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.49}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}0.027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{4.6}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{4.1}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{7.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{44}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{9.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{36}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.88}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.86}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.9}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.69}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.88}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.38}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.39}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.67}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.79}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.65}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.94}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXV@out{0.51}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.54}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVI@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVI@out{0.6}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.27}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVII@out{0.58}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVIII@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVIII@out{0.52}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.56}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.6}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.81}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.072}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.27}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{2.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{2.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{4.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.17}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{3.9}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{25}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{8.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{48}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{10}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{41}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.084}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.87}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.24}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.7}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.59}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.44}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0095, "5th percentile": 0.0035, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.074, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.032, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.15, "error minus": 0.26, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.098, "error minus": 0.059, "5th percentile": 0.022, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVI@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVI@out\macros@XLVII\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.019, "error minus": 0.012, "5th percentile": 0.0071, "95th percentile": 0.04, "10th percentile": 0.0093, "90th percentile": 0.034\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.23, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.035, "error minus": 0.038, "5th percentile": 0.001, "95th percentile": 0.073, "10th percentile": 0.011, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.69, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.47, "95th percentile": 0.9, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.074, "5th percentile": 0.045, "95th percentile": 0.25, "10th percentile": 0.058, "90th percentile": 0.21\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVII@out\macros@LII\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.035, "error plus": 0.026, "error minus": 0.018, "5th percentile": 0.017, "95th percentile": 0.062, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.085, "error minus": 0.088, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.034, "error minus": 0.034, "5th percentile": {-}0.011, "95th percentile": 0.057, "10th percentile": {-}0.003, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.22, "error plus": 0.16, "error minus": 0.11, "5th percentile": 0.11, "95th percentile": 0.39, "10th percentile": 0.12, "90th percentile": 0.34\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVIII@out\macros@LVII\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXIX@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXIX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXIX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXIX@out\macros@LXII\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XL@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XL@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XL@out\macros@LXV\else\def\macros@XL@out{??}\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLI@out\macros@LXVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLI@out\macros@LXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLI@out\macros@LXVIII\else\ifnum\pdfstrcmp{#1}{peaks}=0\let\macros@XLI@out\macros@LXIX\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLII@out\macros@LXX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLII@out\macros@LXXI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLII@out\macros@LXXII\else\def\macros@XLII@out{??}\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.013, "error plus": 0.016, "error minus": 0.0095, "5th percentile": 0.0035, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.0095}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.0035}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.0049}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.026}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.43, "error plus": 0.074, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.074}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.49}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.017, "error plus": 0.032, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.032}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.051}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.043}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.87, "error plus": 0.15, "error minus": 0.26, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.87}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.66}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.97}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.081, "error plus": 0.098, "error minus": 0.059, "5th percentile": 0.022, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.081}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.098}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.059}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.16}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.019, "error plus": 0.019, "error minus": 0.012, "5th percentile": 0.0071, "95th percentile": 0.04, "10th percentile": 0.0093, "90th percentile": 0.034\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.019}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.012}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.0071}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.0093}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.034}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.34, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.23, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.43}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.039, "error plus": 0.035, "error minus": 0.038, "5th percentile": 0.001, "95th percentile": 0.073, "10th percentile": 0.011, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.035}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.038}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.001}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.011}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.065}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.69, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.47, "95th percentile": 0.9, "10th percentile": 0.52, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.69}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.47}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.9}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.86}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.12, "error plus": 0.12, "error minus": 0.074, "5th percentile": 0.045, "95th percentile": 0.25, "10th percentile": 0.058, "90th percentile": 0.21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.074}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{0.045}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.25}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{0.058}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.21}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.035, "error plus": 0.026, "error minus": 0.018, "5th percentile": 0.017, "95th percentile": 0.062, "10th percentile": 0.02, "90th percentile": 0.054\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.035}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.026}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.018}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.062}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.054}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.41, "error plus": 0.085, "error minus": 0.088, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.085}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.088}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.34}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.48}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.023, "error plus": 0.034, "error minus": 0.034, "5th percentile": {-}0.011, "95th percentile": 0.057, "10th percentile": {-}0.003, "90th percentile": 0.049\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.023}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.034}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{{-}0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.057}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.049}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.95\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.82}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.17}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.95}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 0.22, "error plus": 0.16, "error minus": 0.11, "5th percentile": 0.11, "95th percentile": 0.39, "10th percentile": 0.12, "90th percentile": 0.34\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{0.34}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{0.0039}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{0.39}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{0.082}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{0.78}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{0.024}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.7}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{19}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\newcommand\macros@LXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVI@out{\{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVI@out{8.5}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVI@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVI@out{7.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVI@out{9.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVI@out{7.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVI@out{9.0}\else\def\macros@LXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVI@out}\newcommand\macros@LXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVII@out{\{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVII@out{1.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVII@out{21}\else\def\macros@LXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVII@out}\newcommand\macros@LXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVIII@out{\{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVIII@out{46}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVIII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVIII@out{6.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVIII@out{59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVIII@out{55}\else\def\macros@LXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVIII@out}\newcommand\macros@LXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIX@out{\{"10": \{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}}\else\ifnum\pdfstrcmp{#1}{10}=0\let\macros@LXIX@out\macros@LXXIII\else\ifnum\pdfstrcmp{#1}{18}=0\let\macros@LXIX@out\macros@LXXIV\else\ifnum\pdfstrcmp{#1}{35}=0\let\macros@LXIX@out\macros@LXXV\else\def\macros@LXIX@out{??}\fi\fi\fi\fi\macros@LXIX@out}\newcommand\macros@LXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXX@out{6.7}\else\def\macros@LXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXX@out}\newcommand\macros@LXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXI@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXI@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXI@out{15}\else\def\macros@LXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXI@out}\newcommand\macros@LXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXII@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXII@out{52}\else\def\macros@LXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXII@out}\newcommand\macros@LXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXIII@out{\{"median": 9.9, "error plus": 0.63, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXIII@out{9.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXIII@out{0.63}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXIII@out{9.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXIII@out{11}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXIII@out{10}\else\def\macros@LXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXIII@out}\newcommand\macros@LXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXIV@out{\{"median": 19, "error plus": 3.0, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXIV@out{19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXIV@out{3.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXIV@out{2.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXIV@out{16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXIV@out{22}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXIV@out{17}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXIV@out{21}\else\def\macros@LXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXIV@out}\newcommand\macros@LXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXV@out{\{"median": 33, "error plus": 2.3, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXV@out{33}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXV@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXV@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXV@out{30}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXV@out{35}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXV@out{31}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXV@out{35}\else\def\macros@LXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXV@out}\makeatother

### 2022-10-21 src/tex/appendicies.tex
fix cite calls

@@
 and $p_\mathrm{inj}(\theta, z)$ is the reference distribution from which the injections were drawn. We use the LVK released injection sets that describe the 
-detector sensitivities over the first, second and third observing runs \citep{o1o2o3_injection_sets}. Additionally, we follow the procedure 
+detector sensitivities over the first, second and third observing runs \citep{O1O2O3InjectionSets}. Additionally, we follow the procedure 
 outlined in \citet{Farr_2019} to marginalize the uncertainty in our estimate of $\xi(\Lambda, \lambda)$, in which we verify that $N_\mathrm{eff}$ is 

### 2022-10-21 src/tex/results.tex
fix cite calls

@@
 binary black holes (BBHs) given a catalog of gravitational wave observations. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
-accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist,gwtc3DATA}.
+accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist,GWTC3DATA}.
 Since it was concluded to be an outlier of the rest of
@@
 
-Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see features consistent with those inferred by the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist,gwtc3_POPDATA}.
+Figure \ref{fig:mass_distribution} shows the primary mass distribution inferred with our B-Spline model (red), where we see features consistent with those inferred by the \textsc{PowerlawPeak} and \textsc{PowerlawSpline} mass models \citep{Talbot_2018,o3a_pop,Edelman_2022ApJ,o3b_astro_dist,GWTC3POPDATA}.
 In particular our B-Spline model finds peaks in merger rate density as a function of primary mass at both $\sim10\msun$ and $\sim35\msun$, agreeing with those 

### 2022-10-23 src/tex/ms.tex
remove doc options
twocolumn
remove result color highlighting
update
fix jax cite
try to fix latex for submission
small

@@
-\documentclass[twocolumn, linenumbers]{aastex631}
+\documentclass[twocolumn]{aastex631}
 
@@
 
-\input{macros}
+\input{macros.tex}
 \newcommand{\CIPlusMinus}[1]{{#1[median]^{+#1[error plus]}_{-#1[error minus]}}}
@@
 \newcommand{\msun}{\ensuremath{{\rm M}_\odot}}
-\newcommand{\result}[1]{\textcolor{red}{#1}}
+\newcommand{\result}[1]{#1}
 \newcommand{\bruce}[1]{\textcolor{blue}{BE: #1}}
@@
 
-\graphicspath{{./}{figures/}}
+\graphicspath{{./}{./figures/}}
 
@@
 along with helpful comments on an early draft by Tom Callister and Jaxen Godfrey.
-In the spirit of open source and reproducible science, this paper was written using the \textsc{showyourwork} package, published at \url{https://github.com/bruce-edelman/CoveringYourBasis} \citep{Luger2021}.
+In the spirit of open source and reproducible science, this paper was written using the \textsc{showyourwork} package, published at \GitHubURL \citep{Luger2021}.
 Z.D.
@@
 fully funded by the National Science Foundation.
+
 \software{
@@
 \textsc{NumPy}~\citep{harris2020array},
-\textsc{SciPy}~\citep{2020SciPy-NMeth}
+\textsc{SciPy}~\citep{2020SciPy-NMeth},
 \textsc{AstroPy}~\citep{2018AJ....156..123A},
@@
 }
+
 \bibliography{bib}{}

### 2022-10-23 src/tex/conclusion.tex
try to fix link problem?

@@
 We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 
-with gravitational waves, along with the associated open source software \textsc{GWInferno} (\url{https://git.ligo.org/bruce.edelman/gwinferno}) that implements the models 
+with gravitational waves, along with the associated open source software \href{https://git.ligo.org/bruce.edelman/gwinferno}{GWInferno}, that implements the models 
 described in this paper and performs hierarchical Bayesian inference with \textsc{NumPyro} and \textsc{Jax} \citep{pyro,numpyro,jax}. 

### 2022-10-23 src/tex/ms.tex
try to fix link problem?

@@
 along with helpful comments on an early draft by Tom Callister and Jaxen Godfrey.
-In the spirit of open source and reproducible science, this paper was written using the \textsc{showyourwork} package, published at \GitHubURL \citep{Luger2021}.
+In the spirit of open source and reproducible science, this paper was written using the \textsc{showyourwork} package \citep{Luger2021}, and can be found in this \href{https://github.com/bruce-edelman/CoveringYourBasis}{repository}.
 Z.D.

### 2022-10-27 src/tex/conclusion.tex
update with last references

@@
 Non-parametric and data-driven statistical modeling methods have been put to use with great success across the ever-growing field of gravitational 
-waves \citep{B_Farr_etal_2014,Littenberg_2015,Mandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ}. 
+waves \citep{B_Farr_etal_2014,Littenberg_2015,Mandel_2016,Edwards_2018,Doctor_GPR,Edelman_2021,Vitale_2021,Tiwari_2021_a,Tiwari_2021_b,Edelman_2022ApJ,Tiwari_2022ApJ,ModelExploration_MaxPopLike}. 
 We presented a case study exploring how basis splines make for an especially powerful and efficient data driven method of characterizing the binary black hole population observed 

### 2022-10-27 src/tex/results.tex
try to fix latex for submission
table placements
fig ordering
small
update with last references

@@
 \section{Binary Black Hole Population Inference with GWTC-3} \label{sec:results}
-
-We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin, and redshift distributions of 
-binary black holes (BBHs) given a catalog of gravitational wave observations. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
-accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist,GWTC3DATA}.
-Since it was concluded to be an outlier of the rest of
-the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
-a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer population properties. Our study provides the first comprehensive 
-data-driven investigation of the BBH mass, spin, and redshift distributions, uncovering new insights and corroborating those found with other methods. 
-We start with our inference of the mass distribution.
 
@@
 
+We use hierarchical Bayesian inference (see Appendix \ref{sec:hierarchical_inference}) to simultaneously infer the astrophysical mass, spin, and redshift distributions of 
+binary black holes (BBHs) given a catalog of gravitational wave observations. Following the same cut on the recent GWTC-3 catalog done in the LVK's 
+accompanying BBH population analysis, we have 70 possible BBH mergers with false alarm rates less than 1 per year \citep{GWTC3,o3b_astro_dist,GWTC3DATA}.
+Since it was concluded to be an outlier of the rest of
+the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
+a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer population properties. Our study provides the first comprehensive 
+data-driven investigation of the BBH mass, spin, and redshift distributions, uncovering new insights and corroborating those found with other methods. 
+We start with our inference of the mass distribution.
+
 \subsection{Binary Black Hole Masses} \label{sec:mass_dist}
+
+\begin{figure}[ht!]
+    \includegraphics[width=\linewidth]{figures/q_distribution_plot.pdf}
+    \caption{The marginal mass ratio distribution inferred with the B-Spline model (red), with 18 knots spaced linearly in $q$, from 0.05 to 1.
+The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
+    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
+    \label{fig:q_distribution}
+    \script{q_distribution_plot.py}
+\end{figure}
 
@@
 The lack of observations of binaries with low primary mass make rate estimates in this region strongly model dependent, while our flexible model provides an informed upper limit on the rate in this region and given the selection effects and that there are no observations.
-We could be seeing signs of a decrease in merger rate from a ``lower mass gap'' between neutron star and BH masses, or we could be seeing fluctuations due to low-number statistics.
+We could be seeing signs of a decrease in merger rate from a ``lower mass gap'' between neutron star and BH masses, or we could be seeing fluctuations due to low-number statistics \citep{NoPeaksWithoutValleys}.
 Either way we expect this to be resolved with future catalog updates.
@@
 cannot be determined with the current catalog.
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{figures/q_distribution_plot.pdf}
-    \caption{The marginal mass ratio distribution inferred with the B-Spline model (red), with 18 knots spaced linearly in $q$, from 0.05 to 1.
-The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
-    \label{fig:q_distribution}
-    \script{q_distribution_plot.py}
-\end{figure}
 
@@
 
-\subsection{Binary Black Hole Spins} \label{sec:spin_dist}
-
-\begin{figure}
+\begin{figure}[ht!]
     \begin{centering}    
@@
 
-\subsubsection{Spin Magnitude}
-
-The \textsc{Default} spin model (used by \citet{o3b_astro_dist}) describes the spin magnitude of both components as identical and independently distributed (IID) non-singular Beta distributions \citep{Talbot_2017,Wysocki_2019}.
-The Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 
-the Beta distribution non-singular (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. Recent studies have proposed the possible existence of a 
-distinct subpopulation of non-spinning or negligibly spinning black holes that can elude discovery with such a model \citep{FullerMa2019,RouletGWTC2Pop,BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}.
-
-\begin{figure} 
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
-        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model
-        with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
-        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
-        \label{fig:ind_spinmag_dist}
-    \end{centering}
-    \script{plot_ind_spinmag.py}
-\end{figure}
+\subsection{Binary Black Hole Spins} \label{sec:spin_dist}
 
@@
 \end{table*}
+
+\subsubsection{Spin Magnitude}
+
+The \textsc{Default} spin model (used by \citet{o3b_astro_dist}) describes the spin magnitude of both components as identical and independently distributed (IID) non-singular Beta distributions \citep{Talbot_2017,Wysocki_2019}.
+The Beta distribution provides a simple 2-parameter model that can produce a wide range of functional forms on the unit interval. However, the constraint that keeps 
+the Beta distribution non-singular (i.e. $\alpha>1$ and $\beta>1$) enforces a spin magnitude that always has $p(a_i=0) = 0$. Recent studies have proposed the possible existence of a 
+distinct subpopulation of non-spinning or negligibly spinning black holes that can elude discovery with such a model \citep{FullerMa2019,RouletGWTC2Pop,BuildBetterSpinModels,Callister_NoEvidence,GWTC3MonashSpin}.
+
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/ind_spinmag.pdf}
+        \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the B-Spline model
+        with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        \label{fig:ind_spinmag_dist}
+    \end{centering}
+    \script{plot_ind_spinmag.py}
+\end{figure}
 
@@
 
-\begin{figure}
+\begin{figure}[ht!]
     \begin{centering}
@@
 
+\begin{figure}[ht!]
+    \begin{centering}
+        \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
+        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model with 16 knots spaced linearly from -1 to 1.
+The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        \label{fig:ind_spintilt_dist}
+    \end{centering}
+    \script{plot_ind_spintilt.py}
+\end{figure}
+
 We also model each component's orientation distribution with an independent B-Spline model as done above, and show the inferred 
@@
 $\log_{10}Y_2=$\result{$\CIPlusMinus{\macros[BSplineIndependentCompSpins][log10gammaFrac2]}$}.
-
-\begin{figure}
-    \begin{centering}
-        \includegraphics[width=\linewidth]{figures/ind_spintilt.pdf}
-        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the B-Spline model with 16 knots spaced linearly from -1 to 1.
-The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
-        \label{fig:ind_spintilt_dist}
-    \end{centering}
-    \script{plot_ind_spintilt.py}
-\end{figure}
-
-\subsection{The Effective Spin Dimension}
 
@@
 
-\begin{figure} 
+\subsection{The Effective Spin Dimension}
+
+\begin{figure}[ht!]
     \begin{centering}
@@
 
-\begin{figure}[h]
+\begin{figure}[ht!]
     \includegraphics[width=\linewidth]{figures/rate_vs_z_plot.pdf}
@@
 \subsection{Merger Rate Evolution with Redshift} \label{sec:redshift}
+
+\begin{figure}[ht!]
+    \includegraphics[width=\linewidth]{figures/z_modulation_plot.pdf}
+    \caption{The B-spline modulation to the underlying power law in redshift, (red). The solid line shows the population predictive distribution (PPD),
+    and the shaded region the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines.}
+    \label{fig:z_modulation}
+    \script{z_modulation_plot.py}
+\end{figure}
 
@@
 which compares to $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}\,Gpc^{-3}yr^{-1}$} for the GWTC-3 result.
-
-\begin{figure}[h]
-    \includegraphics[width=\linewidth]{figures/z_modulation_plot.pdf}
-    \caption{The B-spline modulation to the underlying power law in redshift, (red). The solid line shows the population predictive distribution (PPD),
-    and the shaded region the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines.}
-    \label{fig:z_modulation}
-    \script{z_modulation_plot.py}
-\end{figure}

### 2022-10-27 src/tex/ms.tex
update with last references
shorten abstract

@@
 \usepackage{appendix}
-
 \input{macros.tex}
@@
 We introduce the first complete non-parametric model for the astrophysical distribution of the binary black hole (BBH) population.
-Constructed from basis splines, we use these models to conduct the most comprehensive data-driven investigation of the BBH population to date, simultaneously fitting non-parametric models for the BBH mass ratio, spin magnitude and misalignment, and redshift distributions for the first time.
-Using the 69 confident BBHs in GWTC-3, we report the same features previously recovered
-with similarly flexible models of the mass distribution, most notably the peaks in merger rates at primary masses of ${\sim}10\msun$ and ${\sim}35\msun$.
+Constructed from basis splines, we use these models to conduct the most comprehensive data-driven investigation of the BBH population to date, simultaneously fitting non-parametric models for the BBH mass ratio, spin magnitude and misalignment, and redshift distributions.
+With GWTC-3, we report the same features previously recovered with similarly flexible models of the mass distribution, most notably the peaks in merger rates at primary masses of ${\sim}10\msun$ and ${\sim}35\msun$.
 Our model reports a suppressed merger rate at low primary masses and a mass ratio distribution consistent with a power law.
-We infer a distribution for primary spin misalignments that peaks away from alignment, supporting recent work that used a variety of parameterized models to come to the same conclusion.
-We find broad agreement with the
-previous inferences of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, 
-and there is mild support for a non-spinning subpopulation, which may be resolved with larger catalogs. 
-Using our non-parametric models, we explore whether the data support spin distributions unique for each binary component, and 
-find no strong evidence that the distributions differ. With a modulated power law describing the BBH merger rate's evolution in redshift, 
-we see hints of the rate evolution either flattening or decreasing at $z\sim0.2-0.5$, but the full distribution remains entirely consistent with a monotonically increasing power law.
-We conclude with a discussion of the astrophysical context of our new findings and how non-parametric methods in
-gravitational-wave population inference are uniquely poised to complement to the parametric approach as we enter the 
-data-rich era of gravitational-wave astronomy.
+We infer a distribution for primary spin misalignments that peaks away from alignment, supporting conclusions of recent work.
+We find broad agreement with the previous inferences of the spin magnitude distribution: the majority of BBH spins are small ($a<0.5$), the distribution peaks at $a\sim0.2$, and there is mild support for a non-spinning subpopulation, which may be resolved with larger catalogs.
+With a modulated power law describing the BBH merger rate's evolution in redshift, we see hints of the rate evolution either flattening or decreasing at $z\sim0.2-0.5$, but the full distribution remains entirely consistent with a monotonically increasing power law.
+We conclude with a discussion of the astrophysical context of our new findings and how non-parametric methods in gravitational-wave population inference are uniquely poised to complement to the parametric approach as we enter the data-rich era of gravitational-wave astronomy.
 \end{abstract}

### 2022-12-04 src/tex/results.tex
add chip plot/etc

@@
 
-\begin{figure}[ht!]
+\begin{figure*}[ht!]
     \begin{centering}
-        \includegraphics[width=\linewidth]{figures/chi_eff.pdf}
-        \caption{The effective spin distribution inferred with the B-Spline IID spin model (red).
+        \includegraphics[width=\linewidth]{figures/effspin.pdf}
+        \caption{The effective (left) and precessing (right) spin distributions inferred with the B-Spline IID spin model (red).
 The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-We show the inferred $\chi_\mathrm{eff}$
-        PPD from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the 
-        Gaussian $\chi_\mathrm{eff}$ (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
-        \label{fig:chieff_dist}
+We show the inferred PPDs from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the
+        Gaussian (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        \label{fig:eff_dist}
     \end{centering}
-    \script{plot_chieff.py}
-\end{figure}
+    \script{plot_effspin.py}
+\end{figure*}
+
+%\begin{figure}[ht!]
+%    \begin{centering}
+   %     \includegraphics[width=\linewidth]{figures/chi_p.pdf}
+   %     \caption{The effective precessing spin distribution inferred with the B-Spline IID spin model (red).
+The solid line shows the population predictive %distribution (PPD), and the shaded region the 90\% credible interval.
+We show the inferred $\chi_\mathrm{p}$
+   %     PPD from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the 
+   %     Gaussian $\chi_\mathrm{p}$ (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+   %     \label{fig:chip_dist}
+   % \end{centering}
+   % \script{plot_chip.py}
+% \end{figure}
 
@@
 The best-measured spin quantity, which enters at the highest post-Newtownian order, is the effective spin: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$.
-Figure \ref{fig:chieff_dist}
-shows the inferred effective spin distribution with the two versions of our B-Spline models (red and purple), 
+Figure \ref{fig:eff_dist}
+shows the inferred effective spin and precessing spin distributions with the two versions of our B-Spline models (red and purple), 
 along with results on the \textsc{Default} \citep{Talbot_2017} and \textsc{Gaussian} \citep{Miller2020} models from \citet{o3b_astro_dist}. We find considerable agreement 

### 2022-12-04 src/scripts/create_chieff_from_compspin.py

@@ -1,163 +1,0 @@
-import numpy as np
-import jax.numpy as jnp
-from scipy.stats import gaussian_kde
-from gwpopulation.cupy_utils import trapz
-from gwpopulation.conversions import convert_to_beta_parameters
-from gwpopulation.models.mass import SinglePeakSmoothedMassDistribution
-from gwpopulation.models.spin import iid_spin_orientation_gaussian_isotropic, iid_spin_magnitude_beta
-from bilby.core.result import read_in_result
-from bilby.hyper.model import Model
-from jax import jit
-from utils import LogXLogYBSpline, LogYBSpline, MSplineIndependentSpinTilts, MSplineIndependentSpinMagnitudes, MSplinePrimaryMSplineRatio, MSplineIIDSpinMagnitudes, MSplineIIDSpinTilts
-import deepdish as dd
-from tqdm import trange
-import paths
-import warnings
-warnings.filterwarnings('ignore')
-
-
-def draw_chieff_samples_gwpop(result, magmodel, tiltmodel, massmodel, ndraws=500, nsamples=2000):
-    mags = np.linspace(0,1,1500)
-    a1s, a2s = np.meshgrid(mags, mags)
-    m1s = np.linspace(2,100,2000)
-    qs = np.linspace(0.05, 1, 1000)
-    mms, qqs = np.meshgrid(m1s, qs)
-    ctilts = np.linspace(-1,1,1500)
-    ct1s, ct2s = np.meshgrid(ctilts, ctilts)
-    
-    magdata = {'a_1': a1s, 'a_2': a2s}
-    tiltdata = {'cos_tilt_1': ct1s, 'cos_tilt_2': ct2s}
-    massdata = {'mass_1': mms, 'mass_ratio': qqs}
-    
-    samples = {'a_1': np.empty((ndraws, nsamples)), 'a_2': np.empty((ndraws, nsamples)), 'cos_tilt_1': np.empty((ndraws, nsamples)),
-               'cos_tilt_2': np.empty((ndraws, nsamples)), 'mass_1': np.empty((ndraws, nsamples)), 'mass_ratio': np.empty((ndraws, nsamples))}
-    
-    idxs = np.random.choice(len(result.posterior), size=ndraws, replace=False)
-
-    for i in trange(ndraws):
-        samp  = result.posterior.iloc[idxs[i]]
[…]

### 2022-12-04 src/scripts/plot_chieff.py

@@ -6,7 +6,7 @@ import json
 from utils import plot_mean_and_90CI
 
 fig, ax = plt.subplots(1,1,figsize=(7,5))
-ppds = dd.io.load(paths.data / "chi_eff_ppds.h5")
+ppds = dd.io.load(paths.data / "chi_eff_chi_p_ppds.h5")
 default = ppds["Default"]
 mspl = ppds["BSplineInd"]
 mspl2 = ppds['BSplineIID']

### 2022-12-04 response.md
chip plots

# Referee Report

## Reviewer

This article reanalyses the binary black hole population and uses non-parametric
models to infer the underlying properties of black holes in the universe.
I enjoyed reading this article and I applaud the authors on a very well written
and clear manuscript. I only have a few comments, which I encourage the authors
to address:

- The authors do not reference the paper by Golomb and Talbot
    (https://arxiv.org/abs/2210.12287), which also use non-parametric models
    (flexible cubic splines) to fit the binary black hole population. I encourage
    the authors to discuss this work in the introduction and include their results
    in relevant plots. In light of this work, I also think the authors should
    change the statement "We introduce the first complete non-parametric model for
    the astrophysical distribution of the binary black hole (BBH) population." in
    the abstract.

- As far as I am aware, the LVK released posterior samples for two waveform
    models, SEOBNRv4PHM and IMRPhenomXPHM. I would like the authors to explicitly
    state which posterior samples were used in their hierarchical Bayesian
    inference and discuss whether waveform model systematics could influence their
    results.

- I am confused why the probability distribution shown in Figure 1 has units
    of inverse solar mass. Is this a typo or am I missing something?

- I believe there is a typo on line 411: Figure 5 shows the inferred spin
    orientation distribution not the inferred spin magnitude distribution.

- Since the effective spin distribution is shown in Figure 7, I would also be
    interested in seeing the inferred effective precession distribution (chi_p).
    This would allow the reader to easily interpret how the inferred tilt angle
    maps to the observed precession in the signal.

- I would be interested in seeing a study that investigates the effect of
    prior assumptions on the inferred results. For instance, how would the results
    change if a normal distribution was used for the smoothing prior scale
    hyperparameter compared to a uniform distribution?

## Data Editor's review:

- One of our data editors has reviewed your initial manuscript submission and has the following suggestion(s) to help improve the data, software citation and/or overall content. Please treat this as you would a reviewer's comments and respond accordingly in your report to the science editor. Questions can be sent directly to the data editors at data-editors@aas.org.

- The figures all have at least one icon links associated with them. These can be a Zenodo sandbox link, a Zenodo url, and a github link. There is no text for the reader to indicate what these icon links take you to. It would be best to add some text as not everybody is familiar with the "Show our work" philosophy.

- In addition, the Zenodo sandbox links are not permanent and can be removed at any time. These should be replace with true Zenodo repositories. Lastly, the authors should use the Zenodo DOI rather than the url for long term stability and discovery.

### 2022-12-04 src/scripts/create_effspin_from_compspin.py

@@ -1,0 +1,184 @@
+import numpy as np
+import jax.numpy as jnp
+from gwpopulation.cupy_utils import trapz
+from gwpopulation.conversions import convert_to_beta_parameters
+from gwpopulation.models.mass import SinglePeakSmoothedMassDistribution
+from gwpopulation.models.spin import iid_spin_orientation_gaussian_isotropic, iid_spin_magnitude_beta
+from bilby.core.result import read_in_result
+from bilby.hyper.model import Model
+from jax import jit
+from utils import LogXLogYBSpline, LogYBSpline, MSplineIndependentSpinTilts, MSplineIndependentSpinMagnitudes, MSplinePrimaryMSplineRatio, MSplineIIDSpinMagnitudes, MSplineIIDSpinTilts, ReflectionBoundedKDE
+import deepdish as dd
+from tqdm import trange
+import paths
+import warnings
+warnings.filterwarnings('ignore')
+
+
+def draw_chieff_chip_samples_gwpop(result, magmodel, tiltmodel, massmodel, ndraws=500, nsamples=2000):
+    mags = np.linspace(0,1,1500)
+    a1s, a2s = np.meshgrid(mags, mags)
+    m1s = np.linspace(2,100,2000)
+    qs = np.linspace(0.05, 1, 1000)
+    mms, qqs = np.meshgrid(m1s, qs)
+    ctilts = np.linspace(-1,1,1500)
+    ct1s, ct2s = np.meshgrid(ctilts, ctilts)
+    
+    magdata = {'a_1': a1s, 'a_2': a2s}
+    tiltdata = {'cos_tilt_1': ct1s, 'cos_tilt_2': ct2s}
+    massdata = {'mass_1': mms, 'mass_ratio': qqs}
+    
+    samples = {'a_1': np.empty((ndraws, nsamples)), 'a_2': np.empty((ndraws, nsamples)), 'cos_tilt_1': np.empty((ndraws, nsamples)),
+               'cos_tilt_2': np.empty((ndraws, nsamples)), 'mass_1': np.empty((ndraws, nsamples)), 'mass_ratio': np.empty((ndraws, nsamples))}
+    
+    idxs = np.random.choice(len(result.posterior), size=ndraws, replace=False)
+
+    for i in trange(ndraws):
+        samp  = result.posterior.iloc[idxs[i]]
+        if 'mu_chi' in samp:
[…]

### 2022-12-04 src/scripts/plot_chip.py

@@ -1,0 +1,43 @@
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+import json
+from utils import plot_mean_and_90CI
+
+fig, ax = plt.subplots(1,1,figsize=(7,5))
+ppds = dd.io.load(paths.data / "chi_eff_chi_p_ppds.h5")
+default = ppds["Default"]
+mspl = ppds["BSplineInd"]
+mspl2 = ppds['BSplineIID']
+ax = plot_mean_and_90CI(ax, default["chips"], default["pchip"], color='tab:blue', label='Default \n(Abbott et. al. 2021b)', bounds=False)
+
+with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json", 'r') as jf:
+    o3b_gaussian_data = json.load(jf)
+    o3b_gaussian_chi_eff_grid = np.array(o3b_gaussian_data['chi_p_grid'])
+    o3b_gaussian_chi_eff_data = np.array(o3b_gaussian_data['chi_p_pdfs'])
+
+ax = plot_mean_and_90CI(ax, o3b_gaussian_chi_eff_grid, o3b_gaussian_chi_eff_data, color='k', label='Gaussian \n(Abbott et. al. 2021b)', bounds=False)
+ax = plot_mean_and_90CI(ax, mspl["chips"], mspl["pchip"], color='tab:orange', label='This Work (Ind Spin)', bounds=False)
+
+#handpicked_ppds = dd.io.load(
+#    paths.data / "BSpline_50m1_24chieff_smoothprior_powerlaw_q_z_fitlamb_ppds.h5"
+#)
+#xs = handpicked_ppds["chieffs"]
+#pchiefss = handpicked_ppds["dRdchieff"]
+#for i in range(1500):
+#    norm = np.trapz(pchiefss[i, :], x=xs)
+#    pchiefss[i, :] /= norm
+#ax = plot_mean_and_90CI(ax, xs, pchiefss, color='tab:red', label='BSpline Chi Eff')
+
+ax = plot_mean_and_90CI(ax, mspl2["chips"], mspl2["pchip"], color='tab:red', label='This Work (IID Spin)', bounds=True, fill_alpha=0.125)
+plt.xlim(0, 1.0)
+plt.ylim(0)
+plt.legend(frameon=False, fontsize=14, loc='upper left')
[…]

### 2022-12-04 src/scripts/plot_effspin.py

@@ -1,0 +1,52 @@
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+import json
+from utils import plot_mean_and_90CI
+
+fig, axs = plt.subplots(nrows=1,ncols=2,figsize=(14,5))
+ppds = dd.io.load(paths.data / "chi_eff_chi_p_ppds.h5")
+default = ppds["Default"]
+mspl = ppds["BSplineInd"]
+mspl2 = ppds['BSplineIID']
+
+#Chi_Eff
+ax = axs[0]
+ax = plot_mean_and_90CI(ax, default["chieffs"], default["pchieff"], color='tab:blue', label='Default \n(Abbott et. al. 2021b)', bounds=False)
+with open(paths.data / "gaussian-spin-xeff-xp-ppd-data.json", 'r') as jf:
+    o3b_gaussian_data = json.load(jf)
+    o3b_gaussian_chi_eff_grid = np.array(o3b_gaussian_data['chi_eff_grid'])
+    o3b_gaussian_chi_eff_data = np.array(o3b_gaussian_data['chi_eff_pdfs'])
+ax = plot_mean_and_90CI(ax, o3b_gaussian_chi_eff_grid, o3b_gaussian_chi_eff_data, color='k', label='Gaussian \n(Abbott et. al. 2021b)', bounds=False)
+ax = plot_mean_and_90CI(ax, mspl["chieffs"], mspl["pchieff"], color='tab:orange', label='This Work (Ind Spin)', bounds=False)
+ax = plot_mean_and_90CI(ax, mspl2["chieffs"], mspl2["pchieff"], color='tab:red', label='This Work (IID Spin)', bounds=True, fill_alpha=0.125)
+ax.set_xlim(-0.65, 0.5)
+ax.set_ylim(0, 5.25)
+ax.legend(frameon=False, fontsize=14, loc='upper left')
+ax.grid(True, which="major", ls=":")
+ax.tick_params(labelsize=14)
+ax.set_xlabel(r"$\chi_\mathrm{eff}$", fontsize=18)
+ax.set_ylabel(r"$p(\chi_\mathrm{eff})$", fontsize=18)
+
+#Chi_P
+ax = axs[1]
+ax = plot_mean_and_90CI(ax, default["chips"], default["pchip"], color='tab:blue', label='Default \n(Abbott et. al. 2021b)', bounds=False)
[…]

### 2022-12-04 src/tex/ms.tex
acknowledgements

@@
 \section{Acknowledgements}\label{sec:acknowledments}
-We thank Will Farr, Tom Callister, and Maya Fishbach for useful discussions during the preparation of this manuscript, 
-along with helpful comments on an early draft by Tom Callister and Jaxen Godfrey.
-In the spirit of open source and reproducible science, this paper was written using the \textsc{showyourwork} package \citep{Luger2021}, and can be found in this \href{https://github.com/bruce-edelman/CoveringYourBasis}{repository}.
-Z.D.
-also acknowledges support from the CIERA Board
-of Visitors Research Professorship. This research has made use of data, software and/or web tools obtained from the Gravitational Wave Open Science Center 
-(\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the LIGO Scientific Collaboration and the Virgo Collaboration. 
-The authors are grateful for computational resources provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.  
-This work benefited from access to the University of Oregon high performance computer, Talapas. This material is based upon work supported 
-in part by the National Science Foundation under Grant PHY-1807046 and work supported by NSF's LIGO Laboratory which is a major facility 
-fully funded by the National Science Foundation.
+We thank Tom Callister, Will Farr, Maya Fishbach, Salvatore Vitale, and Jaxen Godfrey for useful discussions during the 
+preparation of this manuscript and/or helpful comments on early drafts. In the spirit of open source and 
+reproducible science, this paper was written using the \textsc{showyourwork} package \citep{Luger2021}, and can be 
+found in this \href{https://github.com/bruce-edelman/CoveringYourBasis}{repository}. Z.D. also acknowledges support from 
+the CIERA Board of Visitors Research Professorship.  This research has made use of data, software and/or web tools obtained 
+from the Gravitational Wave Open Science Center (\url{https://www.gw-openscience.org/}), a service of LIGO Laboratory, the 
+LIGO Scientific Collaboration and the Virgo Collaboration. The authors are grateful for computational resources 
+provided by the LIGO Laboratory and supported by National Science Foundation Grants PHY-0757058 and PHY-0823459.  
+This work was supported in part by the National Science Foundation under Grant PHY-2146528 and benefited from access 
+to the University of Oregon high performance computer, Talapas. This material is based upon work supported in part 
+by the National Science Foundation under Grant PHY-1807046 and work supported by NSF's LIGO Laboratory which is a major 
+facility fully funded by the National Science Foundation.
 

### 2022-12-04 src/scripts/analysis_scripts/run_iidspins.py

@@ -114,24 +114,24 @@ def model(mass_model, spin_models, z_model, pedict, injdict, total_inj, Nobs, To
     pen_deg = 2
     
     mass_cs = numpyro.sample('mass_cs', dist.Normal(0,6), sample_shape=(mass_knots,))
-    mass_tau = numpyro.sample("mass_tau", dist.Uniform(2,1000))
+    mass_tau = numpyro.sample("mass_tau", dist.TruncatedNormal(loc=1.0, scale=3*mass_knots, low=1.0)) #dist.Uniform(2,1000))
     numpyro.factor("mass_log_smoothing_prior", apply_difference_prior(mass_cs, mass_tau, degree=pen_deg))
 
     q_cs = numpyro.sample('q_cs', dist.Normal(0,4), sample_shape=(q_knots,))
-    q_tau = numpyro.sample("q_tau", dist.Uniform(1,100))
+    q_tau = numpyro.sample("q_tau", dist.TruncatedNormal(loc=1.0, scale=3*q_knots, low=1.0)) #dist.Uniform(1,100))
     numpyro.factor("q_log_smoothing_prior", apply_difference_prior(q_cs, q_tau, degree=pen_deg))
 
     mag_cs = numpyro.sample('mag_cs', dist.Normal(0,1), sample_shape=(mag_knots,))
-    mag_tau = numpyro.sample("mag_tau",dist.Uniform(1,10))
+    mag_tau = numpyro.sample("mag_tau",dist.TruncatedNormal(loc=1.0, scale=3*mag_knots, low=1.0)) #dist.Uniform(1,10))
     numpyro.factor("mag_log_smoothing_prior", apply_difference_prior(mag_cs, mag_tau, degree=pen_deg))
     tilt_cs = numpyro.sample('tilt_cs', dist.Normal(0,1), sample_shape=(tilt_knots,))
-    tilt_tau = numpyro.sample("tilt_tau", dist.Uniform(1,10))
+    tilt_tau = numpyro.sample("tilt_tau", dist.TruncatedNormal(loc=1.0, scale=3*tilt_knots, low=1.0)) #dist.Uniform(1,10))
     numpyro.factor("tilt_log_smoothing_prior", apply_difference_prior(tilt_cs, tilt_tau, degree=pen_deg))
 
     lamb = numpyro.sample("lamb", dist.Normal(0,3))
[…]

### 2022-12-04 src/scripts/analysis_scripts/run_indspins.py

@@ -112,17 +112,17 @@ def model(mass_model, spin_models, z_model, pedict, injdict, total_inj, Nobs, To
     pen_deg = 2
     
     mass_cs = numpyro.sample('mass_cs', dist.Normal(0,6), sample_shape=(mass_knots,))
-    mass_tau = numpyro.sample("mass_tau", dist.Uniform(2,1000))
+    mass_tau = numpyro.sample("mass_tau", dist.TruncatedNormal(loc=1.0, scale=3*mass_knots, low=1.0)) #dist.Uniform(2,1000))
     numpyro.factor("mass_log_smoothing_prior", apply_difference_prior(mass_cs, mass_tau, degree=pen_deg))
 
     q_cs = numpyro.sample('q_cs', dist.Normal(0,4), sample_shape=(q_knots,))
-    q_tau = numpyro.sample("q_tau", dist.Uniform(1,100))
+    q_tau = numpyro.sample("q_tau", dist.TruncatedNormal(loc=1.0, scale=3*q_knots, low=1.0)) #dist.Uniform(1,100))
     numpyro.factor("q_log_smoothing_prior", apply_difference_prior(q_cs, q_tau, degree=pen_deg))
 
     mag_cs = numpyro.sample('mag_cs', dist.Normal(0,1), sample_shape=(mag_knots,2))
-    mag_tau = numpyro.sample("mag_tau",dist.Uniform(1,10),sample_shape=(2,))
+    mag_tau = numpyro.sample("mag_tau",dist.TruncatedNormal(loc=1.0, scale=3*mag_knots, low=1.0),sample_shape=(2,))
     tilt_cs = numpyro.sample('tilt_cs', dist.Normal(0,1), sample_shape=(tilt_knots,2))
-    tilt_tau = numpyro.sample("tilt_tau", dist.Uniform(1,10),sample_shape=(2,))
+    tilt_tau = numpyro.sample("tilt_tau", dist.TruncatedNormal(loc=1.0, scale=3*tilt_knots, low=1.0),sample_shape=(2,))
     for i in range(2):
         numpyro.factor(f"mag{i}_log_smoothing_prior", apply_difference_prior(mag_cs[:,i], mag_tau[i], degree=pen_deg))
         numpyro.factor(f"tilt{i}_log_smoothing_prior", apply_difference_prior(tilt_cs[:,i], tilt_tau[i], degree=pen_deg))
[…]

### 2022-12-05 src/tex/intro.tex
update with salvos comments

@@
 Following numerous improvements to the detectors since the last observing run, the anticipated sensitivities for the upcoming fourth observing run of the LIGO-Virgo-KAGRA (LVK) collaboration suggest detection rates as high as once per \emph{day} \citep{aLIGO,aVIRGO,LVK_prospects,KAGRAProg}.
-With the formation history of these dense objects encoded in the details of their distribution \citep{Rodriguez_2016,Farr2017Nature,Zevin_2017,Farr_BinnedSpin}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics.
+With the formation history of these dense objects encoded in the details of their distribution \citep{1503.04307,Rodriguez_2016,Farr2017Nature,Zevin_2017,Farr_BinnedSpin}, the likely doubling in size of the catalog with the next observing run could provide another leap in our understanding of compact binary astrophysics.
 Beyond formation physics, population-level inference of the compact binary catalog has also been shown to provide novel measurements of cosmological parameters \citep{Farr_2019HUB,gwtc3_cosmo,JoseSpectralSirens}, constrain modified gravitational wave propagation \citep{OkounkovaBirefringence,ModGWProp,ModGWProp2},

### 2022-12-05 src/tex/results.tex
update with salvos comments

@@
 These results suggest we may be seeing the first signs of departure from a simple power law behavior.
-We find a potential plateau or decrease in the merger rate near equal mass ratios, as well as a broader tail towards unequal mass ratios
-than the power law based models find. Our results also suggest a shallower slope from $q\sim0.3$ to $q\sim0.7$, though uncertainty is larger in this region. The sharp decrease in rate just below 
+We find a potential signs of a plateau or decrease in the merger rate near equal mass ratios, as well as a broader tail towards unequal mass ratios
+than the power law based models find, although a smooth power law is still consistent with these results given the large uncertainties.
+Our results also suggest a shallower slope from $q\sim0.3$ to $q\sim0.7$, though uncertainty is larger in this region.
+The sharp decrease in rate just below
 $q\sim0.5$ is due to the minimum mass ratio truncation defined by $q_\mathrm{min}=\frac{m_\mathrm{min}}{m_1}$. When marginalizing over the primary mass 
@@
 We repeat the same analysis with independent B-Spline distributions for each spin magnitude component. In figure \ref{fig:ind_spinmag_dist} 
-we show the inferred primary (orange), and secondary (olive) spin magnitude distributions inferred when relaxing the IID assumption. We find that the primary spin magnitude distribution 
-peaks slightly higher, at $a\sim0.25$, than the IID B-Spline model, but with similar support at near vanishing spins. The secondary spin magnitude distribution is more uncertain due to the 
-higher measurement uncertainty when inferring the secondary spins of BBH systems.
+we show the inferred primary (orange), and secondary (olive) spin magnitude distributions inferred when relaxing the IID assumption.
+We find no signs that the spin magnitude distributions are not IID but that the primary spin magnitude distribution peaks slightly higher, at $a\sim0.25$, than the IID B-Spline model in figure \ref{fig:iid_spinmag_dist}, but with similar support at near vanishing spins.
+The secondary spin magnitude distribution is more uncertain due to the
+higher measurement uncertainty when inferring the secondary spins of BBH systems \citep{1403.0129,1611.01122}.
 The secondary distribution also peaks at smaller spin magnitudes of $a\sim0.15$, showing potentially rates at $a\sim0$ than the primary distribution or B-Spline IID spin magnitude distribution in figure \ref{fig:iid_spinmag_dist}, though uncertainties are large.
@@
 The extra freedom of our model does inflate the uncertainty in its rate estimates, especially at $z\sim0$ where there are not any observations in the catalog. 
-We find a local ($z=0$) merger rate of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}\,Gpc^{-3}yr^{-1}$} using the B-Spline modulation model 
-which compares to $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}\,Gpc^{-3}yr^{-1}$} for the GWTC-3 result.
+We find a local ($z=0$) merger rate of $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[BSplineIIDCompSpins][local_rate]}\,\mathrm{Gpc}^{-3}\mathrm{yr}^{-1}$} using the B-Spline modulation model 
+which compares to $\mathcal{R}_0 = $\result{$\CIPlusMinus{\macros[PLPeak][local_rate]}\,\mathrm{Gpc}^{-3}\mathrm{yr}^{-1}$} for the GWTC-3 result.

### 2022-12-05 src/tex/results.tex
results changes from referee

@@
 
-Figure \ref{fig:iid_spintilt_dist} shows the inferred spin magnitude distribution with the IID spin B-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
+Figure \ref{fig:iid_spintilt_dist} shows the inferred spin orientation distribution with the IID spin B-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
 The B-Spline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
@@
 The best-measured spin quantity, which enters at the highest post-Newtownian order, is the effective spin: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$.
-Figure \ref{fig:eff_dist}
-shows the inferred effective spin and precessing spin distributions with the two versions of our B-Spline models (red and purple), 
+There is additionally an effective precessing spin parameter, $\chi_\mathrm{p} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$, that quantifies the amount of spin precession given the systems mass ratio and component spin magnitudes and orientation.
+Figure \ref{fig:eff_dist} shows the inferred effective spin and precessing spin distributions with the two versions of our B-Spline models (red and purple), 
 along with results on the \textsc{Default} \citep{Talbot_2017} and \textsc{Gaussian} \citep{Miller2020} models from \citet{o3b_astro_dist}. We find considerable agreement 
@@
 with the \textsc{Default} and \textsc{Gaussian} models from \citet{o3b_astro_dist}.
+The precessing spin distributions inferred with the B-Spline models exhibit a similar shape to the \textsc{Default} model, but with a much fatter tail towards highly precessing systems, driven by the extra support for highly spinning components seen in figures \ref{fig:iid_spinmag_dist} and \ref{fig:iid_spinmag_dist}.
 

### 2022-12-05 src/tex/intro.tex
new changes for referee response

@@
 To ensure we are extracting the full detail the catalog has to offer, we extend our previous non-parametric modeling techniques to include spin magnitudes and tilts, as well as the binary mass ratio and redshift.
+\NewChange{\citet{2210.12287} was released concurrently with this work (based on our previous work \citet{Edelman_2022ApJ}), and find similar conclusions on the spin distribution when applying similar flexible models constructed with cubic splines.
+The work presented in this manuscript however, does not need to analyze a suite of different model configurations and includes flexible non-parametric models for each of the mass, spin and redshift distributions rather than spin alone.}
 

### 2022-12-05 src/tex/results.tex
new changes for referee response

--- 2022-12-05 src/tex/results.tex
@@
 
-Figure \ref{fig:iid_spintilt_dist} shows the inferred spin magnitude distribution with the IID spin B-Spline model, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
+\NewChange{Figure \ref{fig:iid_spintilt_dist} shows the inferred spin orientation distribution with the IID spin B-Spline model}, compared with the \textsc{Default} model from \citet{o3b_astro_dist}. 
 The B-Spline inferences have large uncertainties but start to show the same features as found and discussed in \citet{spinitasyoulike}. 
@@
 
-While the component spin magnitudes and tilts are more directly tied to formation physics, they are typically poorly measured.
+\NewChange{While the component spin magnitudes and tilts are more directly tied to formation physics, they are typically poorly measured.
 The best-measured spin quantity, which enters at the highest post-Newtownian order, is the effective spin: $\chi_\mathrm{eff} = \frac{a_1\cos{\theta_1} + qa_2\cos{\theta_2}}{1+q}$.
-Figure \ref{fig:eff_dist}
-shows the inferred effective spin and precessing spin distributions with the two versions of our B-Spline models (red and purple), 
+There is additionally an effective precessing spin parameter, $\chi_\mathrm{p} = \mathrm{max}\big[ a_1 \sin{\theta_1}, \frac{3+4q}{4+3q} q a_2 \sin{\theta_2} \big]$, that quantifies the amount of spin precession given the systems mass ratio and component spin magnitudes and orientation.}
+Figure \ref{fig:eff_dist} shows the inferred effective spin and precessing spin distributions with the two versions of our B-Spline models (red and purple), 
 along with results on the \textsc{Default} \citep{Talbot_2017} and \textsc{Gaussian} \citep{Miller2020} models from \citet{o3b_astro_dist}. We find considerable agreement 
@@
 with the \textsc{Default} and \textsc{Gaussian} models from \citet{o3b_astro_dist}.
+\NewChange{The precessing spin distributions inferred with the B-Spline models exhibit a similar shape to the \textsc{Default} model, but with a much fatter tail towards highly precessing systems, driven by the extra support for highly spinning components seen in figures \ref{fig:iid_spinmag_dist} and \ref{fig:iid_spinmag_dist}.}
 

### 2022-12-05 src/tex/results.tex
more referee responses done

@@
 the BBH population in both GWTC-2 and GWTC-3, we choose to omit the poorly understood event, GW190814 \citep{190814disc,o3a_pop,o3b_astro_dist,Essick_2022}. This leaves us with 
-a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer population properties. Our study provides the first comprehensive 
-data-driven investigation of the BBH mass, spin, and redshift distributions, uncovering new insights and corroborating those found with other methods. 
+a catalog of 69 confident BBH mergers, observed over a period of about 2 years, from which we want to infer population properties. 
+\NewChange{Following what was done in \citet{o3b_astro_dist}, for events included in GWTC-1 \citep{GWTC1}, we use the published samples that equally weight samples from analyses with the \textsc{IMRPhenomPv2} \citep{1308.3271} and \textsc{SEOBNRv3} \citep{1307.6232,1311.2544} waveforms.
+For the events from GWTC-2 \citep{gwtc2}, we use samples that equally weight all available analyses using higher-order mode waveforms (\textsc{PrecessingIMRPHM}).
+Finally, for new events reported in GWTC-2.1 and GWTC-3 \citep{2108.01045,GWTC3}, we use combined samples, equally weighted, from analyses with the \textsc{IMRPhenomXPHM} \citep{2004.06503} and the \textsc{SEOBNRv4PHM} \citep{2004.09442} waveform models.}
+Our study provides the first comprehensive 
+data-driven investigation, simultaneously inferring all the BBH population distributions (i.e. mass, spin, and redshift), uncovering new insights and corroborating those found with other methods. 
 We start with our inference of the mass distribution.

### 2022-12-05 response.md
fill in response.md some more

@@
 
+This work has now been referenced and discussed in the introduction and the new sentence was highlighted.
+Since both Golomb and Talbot and this paper appeared publically on arxiv on the same day and their paper had no impact on this work, I do not think it is necessary for us to include their results on our plots or discuss their results in any more detail, than mentioning their paper in the introduction.
+We also argue that the statement in the abstract is still fully correct in light of their paper as Golomb and Talbot only applied their flexible spline modeling to the spin distributions where we have applied our data-driven unbiased basis spline modeling to the primary mass, mass ratio, and redshift distributions **in addition** to the spin distributions.
+This is why we refer to our work as the first *complete* non-parametric model for the astrophysical distribution of the BBH population.
+To our understanding this work is the first study to do such an investigation simultaneously using data-driven models for each dimension.
+If this is still not clear we are open to other wordings we could rephrase this sentence as.
+A possible rewording could be:
+
+"We introduce the first entirely non-parametric model for the astrophysical distribution of the binary black hole (BBH) masses, spins and redshift."
+
 - As far as I am aware, the LVK released posterior samples for two waveform
@@
 
+We have added a few sentences to the beginning of the results section (highlighted) that explicitly states which waveform's samples were used in this work.
+We do not find any signs of waveform systematics which is consistent with what was investigated and discussed in Appendix C.4 of the LVK's population analysis of GWTC-3 (https://arxiv.org/abs/2111.03634).
+
 - I am confused why the probability distribution shown in Figure 1 has units
@@
 
+Thanks this has been fixed now.
+
 - I believe there is a typo on line 411: Figure 5 shows the inferred spin
     orientation distribution not the inferred spin magnitude distribution.
+
+Thanks this typo has been fixed.
 
@@
 
+Thanks for the suggestion, we have added the corresponding chi_p distribution for the models shown in Figure 7 and briefly discussed the results in the corresponding section.
+
 - I would be interested in seeing a study that investigates the effect of
@@
 
+Thanks for this suggestion and this is something we have looked into.
+We thoroughly investigated many different prior choices for the smoothing prior scale hyperparameter and found that the results were highly stable to these different choices.
+We wanted to have a prior that puts significant prior volume towards "strong smoothing" so that the model a-priori favors a smooth distribution.
+The two priors we decided on being the best to capture this is the uniform as presented in the paper and by placing a halfnormal prior on the inverse of the prior smoothing scale hyperparameter.
+While this prior does add even more a-priori preference for smooth distributions, and we do infer larger (smoother) posteriors on this parameter -- the distributions are nearly identical.
+We have attached some plots that show the distributions for the uniform prior (blue) and the HalfNormal inverse prior that more strongly favors smooth distributions.
+
 ## Data Editor's review:
 
-- One of our data editors has reviewed your initial manuscript submission and has the following suggestion(s) to help improve the data, software citation and/or overall content.
+One of our data editors has reviewed your initial manuscript submission and has the following suggestion(s) to help improve the data, software citation and/or overall content.
 Please treat this as you would a reviewer's comments and respond accordingly in your report to the science editor.
@@
 
+Thanks for this suggestion.
+I have added a short sentence that indicates where these icons/links lead to for each of the figures.
+If this is too much copied text into each caption, we are open to other possible suggestions that may also appropriately address this.
+
 - In addition, the Zenodo sandbox links are not permanent and can be removed at any time.
@@
 Lastly, the authors should use the Zenodo DOI rather than the url for long term stability and discovery.
+
+Thanks again for pointing this out, this was a mishap on our part, and we have now replaced all the zenodo links etc. to a permanent and stable zenodo repository.

### 2022-12-05 src/scripts/mass_distribution_plot.py
finish response

@@ -46,7 +46,7 @@ for ax, xs, ps, lab in zip([axs], [ms], [m_pdfs], ['m1']):
     ax = plot_mean_and_90CI(ax, bspl_ms, bspl_mpdfs, color='tab:red', label='This Work', bounds=True)
     ax.legend(frameon=False, fontsize=14);
     ax.set_xlabel(r'$m_1 \,\,[M_\odot]$', fontsize=18)
-    ax.set_ylabel(r'$p(m_1) \,\,[M_\odot^{-1}]$', fontsize=18)
+    ax.set_ylabel(r'$p(m_1)$', fontsize=18)
     ax.grid(True, which="major", ls=":")
     ax.tick_params(labelsize=14)
     

### 2022-12-05 src/scripts/plot_spin_ppcs.py

@@ -1,0 +1,119 @@
+#!/usr/bin/env python
+
+import paths
+import numpy as np
+import matplotlib.pyplot as plt
+import deepdish as dd
+
+
+params = [
+    "a",
+    "cos_tilt",
+    "chi_eff",
+    "chi_p",
+]
+
+param_latex = {
+    "a": r'$a$',
+    "cos_tilt": r'$\cos{\theta}$',
+    "chi_eff": r'$\chi_\mathrm{eff}$',
+    "chi_p": r'$\chi_\mathrm{p}$',
+}
+
+def chi_eff(q,a1,a2,ct1,ct2):
+    return (a1*ct1 + q*a2*ct2) / (1.0 + q)
+
+def chi_p(q,a1,a2,ct1,ct2):
+    st1 = np.sqrt(1.0 - ct1**2)
+    st2 = np.sqrt(1.0 - ct2**2)
+    return np.maximum(a1*st1, (3+4*q)/(4+3*q)*q*a2*st2)
+
+nplot = len(params)
+figx, figy = 16,5
+fig, axs = plt.subplots(nrows=1, ncols=nplot, sharey='row', figsize=(figx,figy))
+
+Nobs = 69
+po = dd.io.load(paths.data / 'bsplines_64m1_18q_iid18mag_iid18tilt_pl18z_posterior_samples.h5')
+
+obsdata = {'a1': np.array([po[f"a_1_obs_event_{i}"] for i in range(Nobs)]), 
+           'a2': np.array([po[f"a_2_obs_event_{i}"] for i in range(Nobs)]), 
+           'ct1': np.array([po[f"cos_tilt_1_obs_event_{i}"] for i in range(Nobs)]), 
+           'ct2': np.array([po[f"cos_tilt_2_obs_event_{i}"] for i in range(Nobs)]), 
+           'q': np.array([po[f"mass_ratio_obs_event_{i}"] for i in range(Nobs)])}
+synthdata = {'a1': np.array([po[f"a_1_pred_event_{i}"] for i in range(Nobs)]), 
+           'a2': np.array([po[f"a_2_pred_event_{i}"] for i in range(Nobs)]), 
+           'ct1': np.array([po[f"cos_tilt_1_pred_event_{i}"] for i in range(Nobs)]), 
+           'ct2': np.array([po[f"cos_tilt_2_pred_event_{i}"] for i in range(Nobs)]), 
[…]

### 2022-12-10 src/tex/ms.tex
finish response
linenumbers for resubmit
add zenodo

@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn,linenumbers]{aastex631}
 
@@
 \newcommand{\NewChange}[1]{\textcolor{green}{#1}}
+\newcommand{\LinkExplainer}{The icons link to the code used to generate this figure and to \href{https://zenodo.org}{zenodo} entries of any public data used.}
 
@@
 reproducible science, this paper was written using the \textsc{showyourwork} package \citep{Luger2021}, and can be 
-found in this \href{https://github.com/bruce-edelman/CoveringYourBasis}{repository}. Z.D. also acknowledges support from 
+found in this \href{https://github.com/bruce-edelman/CoveringYourBasis}{repository} and the accompanying data realease; \citet{edelman_bruce_2022_7422514}. Z.D. also acknowledges support from 
 the CIERA Board of Visitors Research Professorship.  This research has made use of data, software and/or web tools obtained 

### 2023-01-03 src/tex/macros.tex
finalize resubmit changes

--- 2022-10-17 src/tex/macros.tex
@@
-\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "Default": \{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0088, "5th percentile": 0.0038, "95th percentile": 0.03, "10th percentile": 0.005, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.039\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.1, "error minus": 0.055, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.011, "5th percentile": 0.0083, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.035\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.032, "error minus": 0.032, "5th percentile": 0.005, "95th percentile": 0.069, "10th percentile": 0.011, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.68, "error plus": 0.22, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.91, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.066, "5th percentile": 0.052, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.22\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.034, "error plus": 0.025, "error minus": 0.016, "5th percentile": 0.018, "95th percentile": 0.061, "10th percentile": 0.022, "90th percentile": 0.052\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.09, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.47\}, "PeakChiEff": \{"median": 0.024, "error plus": 0.033, "error minus": 0.031, "5th percentile": {-}0.007, "95th percentile": 0.057, "10th percentile": {-}0.001, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.98, "10th percentile": 0.67, "90th percentile": 0.94\}, "frac\_hm": \{"median": 0.21, "error plus": 0.16, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.38, "10th percentile": 0.14, "90th percentile": 0.33\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{Default}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@V\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@VI\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"a\_90percentile": \{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"lamb": \{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peak_a1}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peak_a2}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@III@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@III@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@III@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@III@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@III@out\macros@XXVIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@IV@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@IV@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@IV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@IV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@IV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@IV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@IV@out\macros@XXXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0088, "5th percentile": 0.0038, "95th percentile": 0.03, "10th percentile": 0.005, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.039\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.1, "error minus": 0.055, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.011, "5th percentile": 0.0083, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.035\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.032, "error minus": 0.032, "5th percentile": 0.005, "95th percentile": 0.069, "10th percentile": 0.011, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.68, "error plus": 0.22, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.91, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.066, "5th percentile": 0.052, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.22\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.034, "error plus": 0.025, "error minus": 0.016, "5th percentile": 0.018, "95th percentile": 0.061, "10th percentile": 0.022, "90th percentile": 0.052\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.09, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.47\}, "PeakChiEff": \{"median": 0.024, "error plus": 0.033, "error minus": 0.031, "5th percentile": {-}0.007, "95th percentile": 0.057, "10th percentile": {-}0.001, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.98, "10th percentile": 0.67, "90th percentile": 0.94\}, "frac\_hm": \{"median": 0.21, "error plus": 0.16, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.38, "10th percentile": 0.14, "90th percentile": 0.33\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@V@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@V@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@V@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@V@out\macros@XXXIX\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@VI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@VI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@VI@out\macros@XLII\else\def\macros@VI@out{??}\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 1.1, "error plus": 1.7, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.7}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{2.4}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{25}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.1}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.53, "error plus": 0.094, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.094}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.073}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.63}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.47}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.6}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.03}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.25}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{4.1}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 17, "error plus": 9.6, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{25}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.19, "error plus": 0.36, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.36}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.5}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.44, "error plus": 0.064, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.064}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.49}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 2.4, "error plus": 2.3, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}0.027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{4.6}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{4.1}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 18, "error plus": 23, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{23}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{7.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{44}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{9.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{36}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.88}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.86}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.8, "error plus": 0.11, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.9}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.69}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.88}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.38}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.17, "error plus": 0.26, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.26}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.39}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.67}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.79}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.38, "error plus": 0.65, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.65}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.94}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": 0.12, "error plus": 0.51, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.51}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXV@out{0.51}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.54}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVI@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVI@out{0.6}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": 0.43, "error plus": 0.18, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.27}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVII@out{0.58}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVIII@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVIII@out{0.52}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.56}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.6}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.81}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.19, "error plus": 0.13, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.072}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.27}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 2.1, "error plus": 2.3, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{2.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{2.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{2.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{4.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.17}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{3.9}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 20, "error plus": 25, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{25}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{8.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{48}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{10}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{41}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.084}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.87}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.24}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.7}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.59}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.44}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.016, "error minus": 0.0088, "5th percentile": 0.0038, "95th percentile": 0.03, "10th percentile": 0.005, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.076, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.039\}, "frac\_dyn": \{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.079, "error plus": 0.1, "error minus": 0.055, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVI@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVI@out\macros@XLVII\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.02, "error minus": 0.011, "5th percentile": 0.0083, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.035\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.037, "error plus": 0.032, "error minus": 0.032, "5th percentile": 0.005, "95th percentile": 0.069, "10th percentile": 0.011, "90th percentile": 0.063\}, "frac\_dyn": \{"median": 0.68, "error plus": 0.22, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.91, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.12, "error minus": 0.066, "5th percentile": 0.052, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.22\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVII@out\macros@LII\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.034, "error plus": 0.025, "error minus": 0.016, "5th percentile": 0.018, "95th percentile": 0.061, "10th percentile": 0.022, "90th percentile": 0.052\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.09, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.47\}, "PeakChiEff": \{"median": 0.024, "error plus": 0.033, "error minus": 0.031, "5th percentile": {-}0.007, "95th percentile": 0.057, "10th percentile": {-}0.001, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.98, "10th percentile": 0.67, "90th percentile": 0.94\}, "frac\_hm": \{"median": 0.21, "error plus": 0.16, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.38, "10th percentile": 0.14, "90th percentile": 0.33\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVIII@out\macros@LVII\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXIX@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXIX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXIX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXIX@out\macros@LXII\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XL@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XL@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XL@out\macros@LXV\else\def\macros@XL@out{??}\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"m\_1percentile": \{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLI@out\macros@LXVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLI@out\macros@LXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLI@out\macros@LXVIII\else\def\macros@XLI@out{??}\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLII@out\macros@LXIX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLII@out\macros@LXX\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLII@out\macros@LXXI\else\def\macros@XLII@out{??}\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.013, "error plus": 0.016, "error minus": 0.0088, "5th percentile": 0.0038, "95th percentile": 0.03, "10th percentile": 0.005, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.0088}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.0038}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.005}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.026}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.43, "error plus": 0.076, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.32, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.076}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.32}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.48}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.017, "error plus": 0.028, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.047, "10th percentile": {-}0.001, "90th percentile": 0.039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.028}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.047}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.039}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.86, "error plus": 0.15, "error minus": 0.27, "5th percentile": 0.59, "95th percentile": 0.98, "10th percentile": 0.65, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.86}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.27}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.59}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.65}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.97}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.079, "error plus": 0.1, "error minus": 0.055, "5th percentile": 0.024, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.079}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.055}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.024}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.16}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.019, "error plus": 0.02, "error minus": 0.011, "5th percentile": 0.0083, "95th percentile": 0.041, "10th percentile": 0.01, "90th percentile": 0.035\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.011}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.041}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.01}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.035}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.34, "error plus": 0.11, "error minus": 0.098, "5th percentile": 0.24, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.098}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.43}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.037, "error plus": 0.032, "error minus": 0.032, "5th percentile": 0.005, "95th percentile": 0.069, "10th percentile": 0.011, "90th percentile": 0.063\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.037}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.032}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.032}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.069}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.011}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.063}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.68, "error plus": 0.22, "error minus": 0.2, "5th percentile": 0.48, "95th percentile": 0.91, "10th percentile": 0.52, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.68}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.48}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.91}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.86}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.12, "error plus": 0.12, "error minus": 0.066, "5th percentile": 0.052, "95th percentile": 0.25, "10th percentile": 0.064, "90th percentile": 0.22\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.066}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{0.052}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.25}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{0.064}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.22}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.034, "error plus": 0.025, "error minus": 0.016, "5th percentile": 0.018, "95th percentile": 0.061, "10th percentile": 0.022, "90th percentile": 0.052\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.034}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.025}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.016}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.018}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.061}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.022}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.052}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.41, "error plus": 0.083, "error minus": 0.09, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.47\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.083}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.09}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.34}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.47}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.024, "error plus": 0.033, "error minus": 0.031, "5th percentile": {-}0.007, "95th percentile": 0.057, "10th percentile": {-}0.001, "90th percentile": 0.049\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.033}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.031}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{{-}0.007}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.057}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.049}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.98, "10th percentile": 0.67, "90th percentile": 0.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.82}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.17}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.94}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 0.21, "error plus": 0.16, "error minus": 0.1, "5th percentile": 0.11, "95th percentile": 0.38, "10th percentile": 0.14, "90th percentile": 0.33\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{0.21}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{0.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{0.38}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{0.14}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{0.33}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 0.00024, "error plus": 0.0067, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.0067}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{0.0039}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 0.28, "error plus": 0.14, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{0.39}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 0.06, "error plus": 0.031, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.031}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{0.082}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 0.55, "error plus": 0.29, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{0.78}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 0.0015, "error plus": 0.042, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{0.042}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{0.024}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.7}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 15, "error plus": 5.5, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{5.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{19}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 45, "error plus": 9.9, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{9.9}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\newcommand\macros@LXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVI@out{\{"median": 8.5, "error plus": 0.8, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVI@out{8.5}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVI@out{0.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVI@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVI@out{7.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVI@out{9.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVI@out{7.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVI@out{9.0}\else\def\macros@LXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVI@out}\newcommand\macros@LXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVII@out{\{"median": 12, "error plus": 12, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVII@out{1.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVII@out{21}\else\def\macros@LXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVII@out}\newcommand\macros@LXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVIII@out{\{"median": 46, "error plus": 12, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVIII@out{46}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVIII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVIII@out{6.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVIII@out{59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVIII@out{55}\else\def\macros@LXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVIII@out}\newcommand\macros@LXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIX@out{\{"median": 6.2, "error plus": 0.64, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIX@out{6.7}\else\def\macros@LXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIX@out}\newcommand\macros@LXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXX@out{\{"median": 11, "error plus": 4.6, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXX@out{4.6}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXX@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXX@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXX@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXX@out{15}\else\def\macros@LXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXX@out}\newcommand\macros@LXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXI@out{\{"median": 43, "error plus": 10, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXI@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXI@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXI@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXI@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXI@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXI@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXI@out{52}\else\def\macros@LXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXI@out}\makeatother
+\makeatletter\newcommand\macros[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@out{\{"PLPeak": \{"beta": \{"median": 1.1, "error plus": 1.8, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 10, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}, "Default": \{"a\_90percentile": \{"median": 0.53, "error plus": 0.098, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 10, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.4, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.052, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}, "BSplineIndependentCompSpins": \{"lamb": \{"median": 2.4, "error plus": 2.2, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 26, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.1, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.62, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.5, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}, "BSplineIIDCompSpins": \{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.12, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.2, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 29, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}, "ChiEffective": \{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.017, "error minus": 0.0095, "5th percentile": 0.0035, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.059, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.12, "error minus": 0.26, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.11, "error minus": 0.059, "5th percentile": 0.022, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.021, "error minus": 0.012, "5th percentile": 0.0071, "95th percentile": 0.04, "10th percentile": 0.0093, "90th percentile": 0.034\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.23, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.034, "error minus": 0.038, "5th percentile": 0.001, "95th percentile": 0.073, "10th percentile": 0.011, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.69, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.47, "95th percentile": 0.9, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.13, "error minus": 0.074, "5th percentile": 0.045, "95th percentile": 0.25, "10th percentile": 0.058, "90th percentile": 0.21\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.035, "error plus": 0.027, "error minus": 0.018, "5th percentile": 0.017, "95th percentile": 0.062, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.088, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.034, "error minus": 0.034, "5th percentile": {-}0.011, "95th percentile": 0.057, "10th percentile": {-}0.003, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.22, "error plus": 0.17, "error minus": 0.11, "5th percentile": 0.11, "95th percentile": 0.39, "10th percentile": 0.12, "90th percentile": 0.34\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0081, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.15, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.029, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.3, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.051, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}, "MassDistribution": \{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.59, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 6.1, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 11, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.67, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 15, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 13, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.67, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.2, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.1, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.59, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 5.4, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 12, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@out\macros@I\else\ifnum\pdfstrcmp{#1}{Default}=0\let\macros@out\macros@II\else\ifnum\pdfstrcmp{#1}{BSplineIndependentCompSpins}=0\let\macros@out\macros@III\else\ifnum\pdfstrcmp{#1}{BSplineIIDCompSpins}=0\let\macros@out\macros@IV\else\ifnum\pdfstrcmp{#1}{ChiEffective}=0\let\macros@out\macros@V\else\ifnum\pdfstrcmp{#1}{MassDistribution}=0\let\macros@out\macros@VI\else\def\macros@out{??}\fi\fi\fi\fi\fi\fi\fi\macros@out}\newcommand\macros@I[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@I@out{\{"beta": \{"median": 1.1, "error plus": 1.8, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}, "local\_rate": \{"median": 17, "error plus": 10, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}\}}\else\ifnum\pdfstrcmp{#1}{beta}=0\let\macros@I@out\macros@VII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@I@out\macros@VIII\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@I@out\macros@IX\else\def\macros@I@out{??}\fi\fi\fi\fi\macros@I@out}\newcommand\macros@II[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@II@out{\{"a\_90percentile": \{"median": 0.53, "error plus": 0.098, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}, "peak\_a": \{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}, "lamb": \{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}, "local\_rate": \{"median": 17, "error plus": 10, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}, "peakCosTilt": \{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}, "log10gammaFrac": \{"median": 0.19, "error plus": 0.4, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}, "negFrac": \{"median": 0.44, "error plus": 0.052, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@II@out\macros@X\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@II@out\macros@XI\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@II@out\macros@XII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@II@out\macros@XIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@II@out\macros@XIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@II@out\macros@XV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@II@out\macros@XVI\else\def\macros@II@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@II@out}\newcommand\macros@III[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@III@out{\{"lamb": \{"median": 2.4, "error plus": 2.2, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}, "local\_rate": \{"median": 18, "error plus": 26, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}, "a1\_90percentile": \{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}, "a2\_90percentile": \{"median": 0.8, "error plus": 0.1, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}, "peak\_a1": \{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}, "peak\_a2": \{"median": 0.17, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}, "peakCosTilt1": \{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}, "peakCosTilt2": \{"median": 0.38, "error plus": 0.62, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}, "log10gammaFrac1": \{"median": 0.12, "error plus": 0.5, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}, "log10gammaFrac2": \{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}, "negFrac1": \{"median": 0.43, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}, "negFrac2": \{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}\}}\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@III@out\macros@XVII\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@III@out\macros@XVIII\else\ifnum\pdfstrcmp{#1}{a1_90percentile}=0\let\macros@III@out\macros@XIX\else\ifnum\pdfstrcmp{#1}{a2_90percentile}=0\let\macros@III@out\macros@XX\else\ifnum\pdfstrcmp{#1}{peak_a1}=0\let\macros@III@out\macros@XXI\else\ifnum\pdfstrcmp{#1}{peak_a2}=0\let\macros@III@out\macros@XXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt1}=0\let\macros@III@out\macros@XXIII\else\ifnum\pdfstrcmp{#1}{peakCosTilt2}=0\let\macros@III@out\macros@XXIV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac1}=0\let\macros@III@out\macros@XXV\else\ifnum\pdfstrcmp{#1}{log10gammaFrac2}=0\let\macros@III@out\macros@XXVI\else\ifnum\pdfstrcmp{#1}{negFrac1}=0\let\macros@III@out\macros@XXVII\else\ifnum\pdfstrcmp{#1}{negFrac2}=0\let\macros@III@out\macros@XXVIII\else\def\macros@III@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\fi\macros@III@out}\newcommand\macros@IV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IV@out{\{"a\_90percentile": \{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}, "peak\_a": \{"median": 0.19, "error plus": 0.12, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}, "lamb": \{"median": 2.1, "error plus": 2.2, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}, "local\_rate": \{"median": 20, "error plus": 29, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}, "peakCosTilt": \{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}, "log10gammaFrac": \{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}, "negFrac": \{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}\}}\else\ifnum\pdfstrcmp{#1}{a_90percentile}=0\let\macros@IV@out\macros@XXIX\else\ifnum\pdfstrcmp{#1}{peak_a}=0\let\macros@IV@out\macros@XXX\else\ifnum\pdfstrcmp{#1}{lamb}=0\let\macros@IV@out\macros@XXXI\else\ifnum\pdfstrcmp{#1}{local_rate}=0\let\macros@IV@out\macros@XXXII\else\ifnum\pdfstrcmp{#1}{peakCosTilt}=0\let\macros@IV@out\macros@XXXIII\else\ifnum\pdfstrcmp{#1}{log10gammaFrac}=0\let\macros@IV@out\macros@XXXIV\else\ifnum\pdfstrcmp{#1}{negFrac}=0\let\macros@IV@out\macros@XXXV\else\def\macros@IV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IV@out}\newcommand\macros@V[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@V@out{\{"default": \{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.017, "error minus": 0.0095, "5th percentile": 0.0035, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.059, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.12, "error minus": 0.26, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.11, "error minus": 0.059, "5th percentile": 0.022, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}, "iid": \{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.021, "error minus": 0.012, "5th percentile": 0.0071, "95th percentile": 0.04, "10th percentile": 0.0093, "90th percentile": 0.034\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.23, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.034, "error minus": 0.038, "5th percentile": 0.001, "95th percentile": 0.073, "10th percentile": 0.011, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.69, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.47, "95th percentile": 0.9, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.13, "error minus": 0.074, "5th percentile": 0.045, "95th percentile": 0.25, "10th percentile": 0.058, "90th percentile": 0.21\}\}, "ind": \{"FracBelowNeg0p3": \{"median": 0.035, "error plus": 0.027, "error minus": 0.018, "5th percentile": 0.017, "95th percentile": 0.062, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.088, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.034, "error minus": 0.034, "5th percentile": {-}0.011, "95th percentile": 0.057, "10th percentile": {-}0.003, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.22, "error plus": 0.17, "error minus": 0.11, "5th percentile": 0.11, "95th percentile": 0.39, "10th percentile": 0.12, "90th percentile": 0.34\}\}, "gaussian": \{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0081, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.15, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.029, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.3, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.051, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}\}}\else\ifnum\pdfstrcmp{#1}{default}=0\let\macros@V@out\macros@XXXVI\else\ifnum\pdfstrcmp{#1}{iid}=0\let\macros@V@out\macros@XXXVII\else\ifnum\pdfstrcmp{#1}{ind}=0\let\macros@V@out\macros@XXXVIII\else\ifnum\pdfstrcmp{#1}{gaussian}=0\let\macros@V@out\macros@XXXIX\else\def\macros@V@out{??}\fi\fi\fi\fi\fi\macros@V@out}\newcommand\macros@VI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VI@out{\{"PLPeak": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.59, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 6.1, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 11, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}, "BSpline": \{"m\_1percentile": \{"median": 8.5, "error plus": 0.67, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 15, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 13, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.67, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.2, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.1, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}, "PLSpline": \{"m\_1percentile": \{"median": 6.2, "error plus": 0.59, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 5.4, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 12, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}\}}\else\ifnum\pdfstrcmp{#1}{PLPeak}=0\let\macros@VI@out\macros@XL\else\ifnum\pdfstrcmp{#1}{BSpline}=0\let\macros@VI@out\macros@XLI\else\ifnum\pdfstrcmp{#1}{PLSpline}=0\let\macros@VI@out\macros@XLII\else\def\macros@VI@out{??}\fi\fi\fi\fi\macros@VI@out}\newcommand\macros@VII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VII@out{\{"median": 1.1, "error plus": 1.8, "error minus": 1.3, "5th percentile": {-}0.25, "95th percentile": 2.8, "10th percentile": 0.016, "90th percentile": 2.4\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VII@out{1.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VII@out{1.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VII@out{{-}0.25}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VII@out{2.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VII@out{0.016}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VII@out{2.4}\else\def\macros@VII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VII@out}\newcommand\macros@VIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@VIII@out{\{"median": 17, "error plus": 10, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@VIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@VIII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@VIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@VIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@VIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@VIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@VIII@out{25}\else\def\macros@VIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@VIII@out}\newcommand\macros@IX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@IX@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@IX@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@IX@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@IX@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@IX@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@IX@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@IX@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@IX@out{4.1}\else\def\macros@IX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@IX@out}\newcommand\macros@X[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@X@out{\{"median": 0.53, "error plus": 0.098, "error minus": 0.073, "5th percentile": 0.46, "95th percentile": 0.63, "10th percentile": 0.47, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@X@out{0.53}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@X@out{0.098}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@X@out{0.073}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@X@out{0.46}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@X@out{0.63}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@X@out{0.47}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@X@out{0.6}\else\def\macros@X@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@X@out}\newcommand\macros@XI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XI@out{\{"median": 0.16, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.03, "95th percentile": 0.27, "10th percentile": 0.053, "90th percentile": 0.25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XI@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XI@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XI@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XI@out{0.03}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XI@out{0.27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XI@out{0.053}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XI@out{0.25}\else\def\macros@XI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XI@out}\newcommand\macros@XII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XII@out{\{"median": 2.7, "error plus": 1.8, "error minus": 1.9, "5th percentile": 0.86, "95th percentile": 4.5, "10th percentile": 1.3, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XII@out{2.7}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XII@out{1.8}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XII@out{1.9}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XII@out{0.86}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XII@out{4.5}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XII@out{1.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XII@out{4.1}\else\def\macros@XII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XII@out}\newcommand\macros@XIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIII@out{\{"median": 17, "error plus": 10, "error minus": 6.7, "5th percentile": 11, "95th percentile": 28, "10th percentile": 12, "90th percentile": 25\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIII@out{17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIII@out{10}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIII@out{6.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIII@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIII@out{28}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIII@out{12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIII@out{25}\else\def\macros@XIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIII@out}\newcommand\macros@XIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIV@out{\{"median": 1.0, "error plus": 0.0, "error minus": 0.0, "5th percentile": 1.0, "95th percentile": 1.0, "10th percentile": 1.0, "90th percentile": 1.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIV@out{0.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIV@out{1.0}\else\def\macros@XIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIV@out}\newcommand\macros@XV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XV@out{\{"median": 0.19, "error plus": 0.4, "error minus": 0.17, "5th percentile": 0.022, "95th percentile": 0.59, "10th percentile": 0.039, "90th percentile": 0.5\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XV@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XV@out{0.4}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XV@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XV@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XV@out{0.59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XV@out{0.039}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XV@out{0.5}\else\def\macros@XV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XV@out}\newcommand\macros@XVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVI@out{\{"median": 0.44, "error plus": 0.052, "error minus": 0.12, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.35, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVI@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVI@out{0.052}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVI@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVI@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVI@out{0.49}\else\def\macros@XVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVI@out}\newcommand\macros@XVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVII@out{\{"median": 2.4, "error plus": 2.2, "error minus": 2.4, "5th percentile": {-}0.027, "95th percentile": 4.6, "10th percentile": 0.52, "90th percentile": 4.1\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVII@out{2.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVII@out{2.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVII@out{{-}0.027}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVII@out{4.6}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVII@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVII@out{4.1}\else\def\macros@XVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVII@out}\newcommand\macros@XVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XVIII@out{\{"median": 18, "error plus": 26, "error minus": 11, "5th percentile": 7.5, "95th percentile": 44, "10th percentile": 9.0, "90th percentile": 36\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XVIII@out{18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XVIII@out{26}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XVIII@out{11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XVIII@out{7.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XVIII@out{44}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XVIII@out{9.0}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XVIII@out{36}\else\def\macros@XVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XVIII@out}\newcommand\macros@XIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XIX@out{\{"median": 0.77, "error plus": 0.11, "error minus": 0.13, "5th percentile": 0.64, "95th percentile": 0.88, "10th percentile": 0.67, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XIX@out{0.77}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XIX@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XIX@out{0.88}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XIX@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XIX@out{0.86}\else\def\macros@XIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XIX@out}\newcommand\macros@XX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XX@out{\{"median": 0.8, "error plus": 0.1, "error minus": 0.14, "5th percentile": 0.66, "95th percentile": 0.9, "10th percentile": 0.69, "90th percentile": 0.88\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XX@out{0.8}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XX@out{0.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XX@out{0.66}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XX@out{0.9}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XX@out{0.69}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XX@out{0.88}\else\def\macros@XX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XX@out}\newcommand\macros@XXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXI@out{\{"median": 0.2, "error plus": 0.24, "error minus": 0.2, "5th percentile": 0.0, "95th percentile": 0.45, "10th percentile": 0.037, "90th percentile": 0.38\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXI@out{0.24}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXI@out{0.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXI@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXI@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXI@out{0.037}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXI@out{0.38}\else\def\macros@XXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXI@out}\newcommand\macros@XXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXII@out{\{"median": 0.17, "error plus": 0.29, "error minus": 0.17, "5th percentile": 0.0, "95th percentile": 0.46, "10th percentile": 0.024, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXII@out{0.29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXII@out{0.17}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXII@out{0.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXII@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXII@out{0.024}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXII@out{0.39}\else\def\macros@XXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXII@out}\newcommand\macros@XXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIII@out{\{"median": 0.16, "error plus": 0.84, "error minus": 0.84, "5th percentile": {-}0.67, "95th percentile": 1.0, "10th percentile": {-}0.41, "90th percentile": 0.79\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIII@out{0.16}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIII@out{0.84}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIII@out{{-}0.67}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIII@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIII@out{0.79}\else\def\macros@XXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIII@out}\newcommand\macros@XXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIV@out{\{"median": 0.38, "error plus": 0.62, "error minus": 1.0, "5th percentile": {-}0.65, "95th percentile": 1.0, "10th percentile": {-}0.29, "90th percentile": 0.94\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIV@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIV@out{0.62}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIV@out{{-}0.65}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIV@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIV@out{0.94}\else\def\macros@XXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIV@out}\newcommand\macros@XXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXV@out{\{"median": 0.12, "error plus": 0.5, "error minus": 0.53, "5th percentile": {-}0.41, "95th percentile": 0.62, "10th percentile": {-}0.29, "90th percentile": 0.51\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXV@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXV@out{0.5}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXV@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXV@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXV@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXV@out{{-}0.29}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXV@out{0.51}\else\def\macros@XXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXV@out}\newcommand\macros@XXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVI@out{\{"median": 0.18, "error plus": 0.53, "error minus": 0.54, "5th percentile": {-}0.35, "95th percentile": 0.71, "10th percentile": {-}0.23, "90th percentile": 0.6\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVI@out{0.53}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVI@out{0.54}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVI@out{{-}0.35}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVI@out{0.71}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVI@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVI@out{0.6}\else\def\macros@XXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVI@out}\newcommand\macros@XXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVII@out{\{"median": 0.43, "error plus": 0.19, "error minus": 0.16, "5th percentile": 0.27, "95th percentile": 0.62, "10th percentile": 0.3, "90th percentile": 0.58\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVII@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVII@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVII@out{0.27}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVII@out{0.62}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVII@out{0.3}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVII@out{0.58}\else\def\macros@XXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVII@out}\newcommand\macros@XXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXVIII@out{\{"median": 0.38, "error plus": 0.18, "error minus": 0.15, "5th percentile": 0.23, "95th percentile": 0.56, "10th percentile": 0.26, "90th percentile": 0.52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXVIII@out{0.38}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXVIII@out{0.18}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXVIII@out{0.15}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXVIII@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXVIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXVIII@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXVIII@out{0.52}\else\def\macros@XXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXVIII@out}\newcommand\macros@XXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXIX@out{\{"median": 0.71, "error plus": 0.13, "error minus": 0.14, "5th percentile": 0.56, "95th percentile": 0.84, "10th percentile": 0.6, "90th percentile": 0.81\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXIX@out{0.71}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXIX@out{0.14}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXIX@out{0.56}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXIX@out{0.84}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXIX@out{0.6}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXIX@out{0.81}\else\def\macros@XXIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXIX@out}\newcommand\macros@XXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXX@out{\{"median": 0.19, "error plus": 0.12, "error minus": 0.16, "5th percentile": 0.029, "95th percentile": 0.31, "10th percentile": 0.072, "90th percentile": 0.27\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXX@out{0.19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXX@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXX@out{0.16}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXX@out{0.029}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXX@out{0.31}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXX@out{0.072}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXX@out{0.27}\else\def\macros@XXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXX@out}\newcommand\macros@XXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXI@out{\{"median": 2.1, "error plus": 2.2, "error minus": 2.5, "5th percentile": {-}0.41, "95th percentile": 4.4, "10th percentile": 0.17, "90th percentile": 3.9\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXI@out{2.1}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXI@out{2.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXI@out{2.5}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXI@out{{-}0.41}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXI@out{4.4}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXI@out{0.17}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXI@out{3.9}\else\def\macros@XXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXI@out}\newcommand\macros@XXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXII@out{\{"median": 20, "error plus": 29, "error minus": 12, "5th percentile": 8.0, "95th percentile": 48, "10th percentile": 10, "90th percentile": 41\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXII@out{20}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXII@out{29}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXII@out{12}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXII@out{8.0}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXII@out{48}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXII@out{10}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXII@out{41}\else\def\macros@XXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXII@out}\newcommand\macros@XXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIII@out{\{"median": 0.44, "error plus": 0.56, "error minus": 0.53, "5th percentile": {-}0.084, "95th percentile": 1.0, "10th percentile": 0.057, "90th percentile": 0.87\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIII@out{0.44}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIII@out{0.56}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIII@out{0.53}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIII@out{{-}0.084}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIII@out{1.0}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIII@out{0.057}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIII@out{0.87}\else\def\macros@XXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIII@out}\newcommand\macros@XXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIV@out{\{"median": 0.24, "error plus": 0.46, "error minus": 0.46, "5th percentile": {-}0.23, "95th percentile": 0.7, "10th percentile": {-}0.12, "90th percentile": 0.59\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXIV@out{0.24}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXIV@out{0.46}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXIV@out{{-}0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXIV@out{0.7}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXIV@out{{-}0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXIV@out{0.59}\else\def\macros@XXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXIV@out}\newcommand\macros@XXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXV@out{\{"median": 0.35, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.24, "95th percentile": 0.46, "10th percentile": 0.26, "90th percentile": 0.44\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XXXV@out{0.35}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XXXV@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XXXV@out{0.24}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XXXV@out{0.46}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XXXV@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XXXV@out{0.44}\else\def\macros@XXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XXXV@out}\newcommand\macros@XXXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVI@out{\{"FracBelowNeg0p3": \{"median": 0.013, "error plus": 0.017, "error minus": 0.0095, "5th percentile": 0.0035, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.026\}, "FracBelow0": \{"median": 0.43, "error plus": 0.059, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}, "PeakChiEff": \{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.043\}, "frac\_dyn": \{"median": 0.87, "error plus": 0.12, "error minus": 0.26, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}, "frac\_hm": \{"median": 0.081, "error plus": 0.11, "error minus": 0.059, "5th percentile": 0.022, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVI@out\macros@XLIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVI@out\macros@XLIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVI@out\macros@XLV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVI@out\macros@XLVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVI@out\macros@XLVII\else\def\macros@XXXVI@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVI@out}\newcommand\macros@XXXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVII@out{\{"FracBelowNeg0p3": \{"median": 0.019, "error plus": 0.021, "error minus": 0.012, "5th percentile": 0.0071, "95th percentile": 0.04, "10th percentile": 0.0093, "90th percentile": 0.034\}, "FracBelow0": \{"median": 0.34, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.23, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}, "PeakChiEff": \{"median": 0.039, "error plus": 0.034, "error minus": 0.038, "5th percentile": 0.001, "95th percentile": 0.073, "10th percentile": 0.011, "90th percentile": 0.065\}, "frac\_dyn": \{"median": 0.69, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.47, "95th percentile": 0.9, "10th percentile": 0.52, "90th percentile": 0.86\}, "frac\_hm": \{"median": 0.12, "error plus": 0.13, "error minus": 0.074, "5th percentile": 0.045, "95th percentile": 0.25, "10th percentile": 0.058, "90th percentile": 0.21\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVII@out\macros@XLVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVII@out\macros@XLIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVII@out\macros@L\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVII@out\macros@LI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVII@out\macros@LII\else\def\macros@XXXVII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVII@out}\newcommand\macros@XXXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXVIII@out{\{"FracBelowNeg0p3": \{"median": 0.035, "error plus": 0.027, "error minus": 0.018, "5th percentile": 0.017, "95th percentile": 0.062, "10th percentile": 0.02, "90th percentile": 0.054\}, "FracBelow0": \{"median": 0.41, "error plus": 0.083, "error minus": 0.088, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}, "PeakChiEff": \{"median": 0.023, "error plus": 0.034, "error minus": 0.034, "5th percentile": {-}0.011, "95th percentile": 0.057, "10th percentile": {-}0.003, "90th percentile": 0.049\}, "frac\_dyn": \{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.95\}, "frac\_hm": \{"median": 0.22, "error plus": 0.17, "error minus": 0.11, "5th percentile": 0.11, "95th percentile": 0.39, "10th percentile": 0.12, "90th percentile": 0.34\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXVIII@out\macros@LIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXVIII@out\macros@LIV\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXVIII@out\macros@LV\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXVIII@out\macros@LVI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXVIII@out\macros@LVII\else\def\macros@XXXVIII@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXVIII@out}\newcommand\macros@XXXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XXXIX@out{\{"FracBelowNeg0p3": \{"median": 0.00024, "error plus": 0.0081, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}, "FracBelow0": \{"median": 0.28, "error plus": 0.15, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}, "PeakChiEff": \{"median": 0.06, "error plus": 0.029, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}, "frac\_dyn": \{"median": 0.55, "error plus": 0.3, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}, "frac\_hm": \{"median": 0.0015, "error plus": 0.051, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}\}}\else\ifnum\pdfstrcmp{#1}{FracBelowNeg0p3}=0\let\macros@XXXIX@out\macros@LVIII\else\ifnum\pdfstrcmp{#1}{FracBelow0}=0\let\macros@XXXIX@out\macros@LIX\else\ifnum\pdfstrcmp{#1}{PeakChiEff}=0\let\macros@XXXIX@out\macros@LX\else\ifnum\pdfstrcmp{#1}{frac_dyn}=0\let\macros@XXXIX@out\macros@LXI\else\ifnum\pdfstrcmp{#1}{frac_hm}=0\let\macros@XXXIX@out\macros@LXII\else\def\macros@XXXIX@out{??}\fi\fi\fi\fi\fi\fi\macros@XXXIX@out}\newcommand\macros@XL[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XL@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.59, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 15, "error plus": 6.1, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}, "m\_99percentile": \{"median": 45, "error plus": 11, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XL@out\macros@LXIII\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XL@out\macros@LXIV\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XL@out\macros@LXV\else\def\macros@XL@out{??}\fi\fi\fi\fi\macros@XL@out}\newcommand\macros@XLI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLI@out{\{"m\_1percentile": \{"median": 8.5, "error plus": 0.67, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}, "m\_75percentile": \{"median": 12, "error plus": 15, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}, "m\_99percentile": \{"median": 46, "error plus": 13, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}, "peaks": \{"10": \{"median": 9.9, "error plus": 0.67, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.2, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.1, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLI@out\macros@LXVI\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLI@out\macros@LXVII\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLI@out\macros@LXVIII\else\ifnum\pdfstrcmp{#1}{peaks}=0\let\macros@XLI@out\macros@LXIX\else\def\macros@XLI@out{??}\fi\fi\fi\fi\fi\macros@XLI@out}\newcommand\macros@XLII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLII@out{\{"m\_1percentile": \{"median": 6.2, "error plus": 0.59, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}, "m\_75percentile": \{"median": 11, "error plus": 5.4, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}, "m\_99percentile": \{"median": 43, "error plus": 12, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}\}}\else\ifnum\pdfstrcmp{#1}{m_1percentile}=0\let\macros@XLII@out\macros@LXX\else\ifnum\pdfstrcmp{#1}{m_75percentile}=0\let\macros@XLII@out\macros@LXXI\else\ifnum\pdfstrcmp{#1}{m_99percentile}=0\let\macros@XLII@out\macros@LXXII\else\def\macros@XLII@out{??}\fi\fi\fi\fi\macros@XLII@out}\newcommand\macros@XLIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIII@out{\{"median": 0.013, "error plus": 0.017, "error minus": 0.0095, "5th percentile": 0.0035, "95th percentile": 0.03, "10th percentile": 0.0049, "90th percentile": 0.026\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIII@out{0.013}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIII@out{0.0095}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIII@out{0.0035}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIII@out{0.03}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIII@out{0.0049}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIII@out{0.026}\else\def\macros@XLIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIII@out}\newcommand\macros@XLIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIV@out{\{"median": 0.43, "error plus": 0.059, "error minus": 0.13, "5th percentile": 0.3, "95th percentile": 0.49, "10th percentile": 0.33, "90th percentile": 0.49\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIV@out{0.43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIV@out{0.059}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIV@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIV@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIV@out{0.33}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIV@out{0.49}\else\def\macros@XLIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIV@out}\newcommand\macros@XLV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLV@out{\{"median": 0.017, "error plus": 0.034, "error minus": 0.022, "5th percentile": {-}0.005, "95th percentile": 0.051, "10th percentile": {-}0.001, "90th percentile": 0.043\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLV@out{0.017}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLV@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLV@out{0.022}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLV@out{{-}0.005}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLV@out{0.051}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLV@out{{-}0.001}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLV@out{0.043}\else\def\macros@XLV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLV@out}\newcommand\macros@XLVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVI@out{\{"median": 0.87, "error plus": 0.12, "error minus": 0.26, "5th percentile": 0.61, "95th percentile": 0.98, "10th percentile": 0.66, "90th percentile": 0.97\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVI@out{0.87}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVI@out{0.12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVI@out{0.61}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVI@out{0.98}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVI@out{0.66}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVI@out{0.97}\else\def\macros@XLVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVI@out}\newcommand\macros@XLVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVII@out{\{"median": 0.081, "error plus": 0.11, "error minus": 0.059, "5th percentile": 0.022, "95th percentile": 0.19, "10th percentile": 0.031, "90th percentile": 0.16\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVII@out{0.081}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVII@out{0.059}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVII@out{0.022}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVII@out{0.19}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVII@out{0.031}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVII@out{0.16}\else\def\macros@XLVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVII@out}\newcommand\macros@XLVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLVIII@out{\{"median": 0.019, "error plus": 0.021, "error minus": 0.012, "5th percentile": 0.0071, "95th percentile": 0.04, "10th percentile": 0.0093, "90th percentile": 0.034\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLVIII@out{0.019}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLVIII@out{0.021}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLVIII@out{0.012}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLVIII@out{0.0071}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLVIII@out{0.04}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLVIII@out{0.0093}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLVIII@out{0.034}\else\def\macros@XLVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLVIII@out}\newcommand\macros@XLIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@XLIX@out{\{"median": 0.34, "error plus": 0.11, "error minus": 0.11, "5th percentile": 0.23, "95th percentile": 0.45, "10th percentile": 0.26, "90th percentile": 0.43\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@XLIX@out{0.34}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@XLIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@XLIX@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@XLIX@out{0.23}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@XLIX@out{0.45}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@XLIX@out{0.26}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@XLIX@out{0.43}\else\def\macros@XLIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@XLIX@out}\newcommand\macros@L[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@L@out{\{"median": 0.039, "error plus": 0.034, "error minus": 0.038, "5th percentile": 0.001, "95th percentile": 0.073, "10th percentile": 0.011, "90th percentile": 0.065\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@L@out{0.039}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@L@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@L@out{0.038}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@L@out{0.001}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@L@out{0.073}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@L@out{0.011}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@L@out{0.065}\else\def\macros@L@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@L@out}\newcommand\macros@LI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LI@out{\{"median": 0.69, "error plus": 0.22, "error minus": 0.22, "5th percentile": 0.47, "95th percentile": 0.9, "10th percentile": 0.52, "90th percentile": 0.86\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LI@out{0.69}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LI@out{0.22}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LI@out{0.22}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LI@out{0.47}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LI@out{0.9}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LI@out{0.52}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LI@out{0.86}\else\def\macros@LI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LI@out}\newcommand\macros@LII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LII@out{\{"median": 0.12, "error plus": 0.13, "error minus": 0.074, "5th percentile": 0.045, "95th percentile": 0.25, "10th percentile": 0.058, "90th percentile": 0.21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LII@out{0.12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LII@out{0.13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LII@out{0.074}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LII@out{0.045}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LII@out{0.25}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LII@out{0.058}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LII@out{0.21}\else\def\macros@LII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LII@out}\newcommand\macros@LIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIII@out{\{"median": 0.035, "error plus": 0.027, "error minus": 0.018, "5th percentile": 0.017, "95th percentile": 0.062, "10th percentile": 0.02, "90th percentile": 0.054\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIII@out{0.035}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIII@out{0.027}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIII@out{0.018}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIII@out{0.017}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIII@out{0.062}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIII@out{0.02}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIII@out{0.054}\else\def\macros@LIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIII@out}\newcommand\macros@LIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIV@out{\{"median": 0.41, "error plus": 0.083, "error minus": 0.088, "5th percentile": 0.32, "95th percentile": 0.49, "10th percentile": 0.34, "90th percentile": 0.48\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIV@out{0.41}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIV@out{0.083}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIV@out{0.088}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIV@out{0.32}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIV@out{0.49}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIV@out{0.34}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIV@out{0.48}\else\def\macros@LIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIV@out}\newcommand\macros@LV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LV@out{\{"median": 0.023, "error plus": 0.034, "error minus": 0.034, "5th percentile": {-}0.011, "95th percentile": 0.057, "10th percentile": {-}0.003, "90th percentile": 0.049\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LV@out{0.023}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LV@out{0.034}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LV@out{0.034}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LV@out{{-}0.011}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LV@out{0.057}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LV@out{{-}0.003}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LV@out{0.049}\else\def\macros@LV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LV@out}\newcommand\macros@LVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVI@out{\{"median": 0.82, "error plus": 0.17, "error minus": 0.18, "5th percentile": 0.64, "95th percentile": 0.99, "10th percentile": 0.67, "90th percentile": 0.95\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVI@out{0.82}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVI@out{0.17}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVI@out{0.18}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVI@out{0.64}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVI@out{0.99}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVI@out{0.67}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVI@out{0.95}\else\def\macros@LVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVI@out}\newcommand\macros@LVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVII@out{\{"median": 0.22, "error plus": 0.17, "error minus": 0.11, "5th percentile": 0.11, "95th percentile": 0.39, "10th percentile": 0.12, "90th percentile": 0.34\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVII@out{0.22}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVII@out{0.17}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVII@out{0.11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVII@out{0.39}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVII@out{0.12}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVII@out{0.34}\else\def\macros@LVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVII@out}\newcommand\macros@LVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LVIII@out{\{"median": 0.00024, "error plus": 0.0081, "error minus": 0.00024, "5th percentile": 1.1e{-}07, "95th percentile": 0.0083, "10th percentile": 9.2e{-}07, "90th percentile": 0.0039\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LVIII@out{0.0081}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LVIII@out{0.00024}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LVIII@out{1.1e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LVIII@out{0.0083}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LVIII@out{9.2e{-}07}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LVIII@out{0.0039}\else\def\macros@LVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LVIII@out}\newcommand\macros@LIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LIX@out{\{"median": 0.28, "error plus": 0.15, "error minus": 0.13, "5th percentile": 0.15, "95th percentile": 0.42, "10th percentile": 0.18, "90th percentile": 0.39\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LIX@out{0.28}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LIX@out{0.13}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LIX@out{0.15}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LIX@out{0.42}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LIX@out{0.18}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LIX@out{0.39}\else\def\macros@LIX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LIX@out}\newcommand\macros@LX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LX@out{\{"median": 0.06, "error plus": 0.029, "error minus": 0.037, "5th percentile": 0.023, "95th percentile": 0.089, "10th percentile": 0.032, "90th percentile": 0.082\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LX@out{0.06}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LX@out{0.029}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LX@out{0.037}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LX@out{0.023}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LX@out{0.089}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LX@out{0.032}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LX@out{0.082}\else\def\macros@LX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LX@out}\newcommand\macros@LXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXI@out{\{"median": 0.55, "error plus": 0.3, "error minus": 0.26, "5th percentile": 0.3, "95th percentile": 0.85, "10th percentile": 0.35, "90th percentile": 0.78\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXI@out{0.55}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXI@out{0.3}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXI@out{0.26}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXI@out{0.3}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXI@out{0.85}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXI@out{0.35}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXI@out{0.78}\else\def\macros@LXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXI@out}\newcommand\macros@LXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXII@out{\{"median": 0.0015, "error plus": 0.051, "error minus": 0.0015, "5th percentile": 6.9e{-}07, "95th percentile": 0.052, "10th percentile": 5.7e{-}06, "90th percentile": 0.024\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXII@out{0.051}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXII@out{0.0015}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXII@out{6.9e{-}07}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXII@out{0.052}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXII@out{5.7e{-}06}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXII@out{0.024}\else\def\macros@LXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXII@out}\newcommand\macros@LXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIII@out{\{"median": 6.2, "error plus": 0.59, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIII@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIII@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIII@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIII@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIII@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIII@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIII@out{6.7}\else\def\macros@LXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIII@out}\newcommand\macros@LXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIV@out{\{"median": 15, "error plus": 6.1, "error minus": 2.7, "5th percentile": 12, "95th percentile": 21, "10th percentile": 13, "90th percentile": 19\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXIV@out{15}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXIV@out{6.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXIV@out{2.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXIV@out{12}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXIV@out{21}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXIV@out{13}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXIV@out{19}\else\def\macros@LXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXIV@out}\newcommand\macros@LXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXV@out{\{"median": 45, "error plus": 11, "error minus": 6.2, "5th percentile": 39, "95th percentile": 55, "10th percentile": 40, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXV@out{45}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXV@out{11}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXV@out{6.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXV@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXV@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXV@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXV@out{52}\else\def\macros@LXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXV@out}\newcommand\macros@LXVI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVI@out{\{"median": 8.5, "error plus": 0.67, "error minus": 1.4, "5th percentile": 7.1, "95th percentile": 9.2, "10th percentile": 7.7, "90th percentile": 9.0\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVI@out{8.5}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVI@out{0.67}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVI@out{1.4}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVI@out{7.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVI@out{9.2}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVI@out{7.7}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVI@out{9.0}\else\def\macros@LXVI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVI@out}\newcommand\macros@LXVII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVII@out{\{"median": 12, "error plus": 15, "error minus": 1.2, "5th percentile": 10, "95th percentile": 27, "10th percentile": 11, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVII@out{12}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVII@out{15}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVII@out{1.2}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVII@out{10}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVII@out{27}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVII@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVII@out{21}\else\def\macros@LXVII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVII@out}\newcommand\macros@LXVIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXVIII@out{\{"median": 46, "error plus": 13, "error minus": 6.6, "5th percentile": 39, "95th percentile": 59, "10th percentile": 40, "90th percentile": 55\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXVIII@out{46}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXVIII@out{13}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXVIII@out{6.6}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXVIII@out{39}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXVIII@out{59}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXVIII@out{40}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXVIII@out{55}\else\def\macros@LXVIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXVIII@out}\newcommand\macros@LXIX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXIX@out{\{"10": \{"median": 9.9, "error plus": 0.67, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}, "18": \{"median": 19, "error plus": 3.2, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}, "35": \{"median": 33, "error plus": 2.1, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}\}}\else\ifnum\pdfstrcmp{#1}{10}=0\let\macros@LXIX@out\macros@LXXIII\else\ifnum\pdfstrcmp{#1}{18}=0\let\macros@LXIX@out\macros@LXXIV\else\ifnum\pdfstrcmp{#1}{35}=0\let\macros@LXIX@out\macros@LXXV\else\def\macros@LXIX@out{??}\fi\fi\fi\fi\macros@LXIX@out}\newcommand\macros@LXX[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXX@out{\{"median": 6.2, "error plus": 0.59, "error minus": 1.1, "5th percentile": 5.1, "95th percentile": 6.8, "10th percentile": 5.4, "90th percentile": 6.7\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXX@out{6.2}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXX@out{0.59}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXX@out{1.1}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXX@out{5.1}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXX@out{6.8}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXX@out{5.4}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXX@out{6.7}\else\def\macros@LXX@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXX@out}\newcommand\macros@LXXI[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXI@out{\{"median": 11, "error plus": 5.4, "error minus": 0.59, "5th percentile": 11, "95th percentile": 17, "10th percentile": 11, "90th percentile": 15\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXI@out{5.4}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXI@out{0.59}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXI@out{17}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXI@out{11}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXI@out{15}\else\def\macros@LXXI@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXI@out}\newcommand\macros@LXXII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXII@out{\{"median": 43, "error plus": 12, "error minus": 4.7, "5th percentile": 38, "95th percentile": 55, "10th percentile": 39, "90th percentile": 52\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXII@out{43}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXII@out{12}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXII@out{4.7}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXII@out{38}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXII@out{55}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXII@out{39}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXII@out{52}\else\def\macros@LXXII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXII@out}\newcommand\macros@LXXIII[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXIII@out{\{"median": 9.9, "error plus": 0.67, "error minus": 0.48, "5th percentile": 9.5, "95th percentile": 11, "10th percentile": 9.6, "90th percentile": 10\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXIII@out{9.9}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXIII@out{0.67}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXIII@out{0.48}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXIII@out{9.5}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXIII@out{11}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXIII@out{9.6}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXIII@out{10}\else\def\macros@LXXIII@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXIII@out}\newcommand\macros@LXXIV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXIV@out{\{"median": 19, "error plus": 3.2, "error minus": 2.3, "5th percentile": 16, "95th percentile": 22, "10th percentile": 17, "90th percentile": 21\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXIV@out{19}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXIV@out{3.2}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXIV@out{2.3}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXIV@out{16}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXIV@out{22}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXIV@out{17}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXIV@out{21}\else\def\macros@LXXIV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXIV@out}\newcommand\macros@LXXV[1][all]{\ifnum\pdfstrcmp{#1}{all}=0\def\macros@LXXV@out{\{"median": 33, "error plus": 2.1, "error minus": 3.0, "5th percentile": 30, "95th percentile": 35, "10th percentile": 31, "90th percentile": 35\}}\else\ifnum\pdfstrcmp{#1}{median}=0\def\macros@LXXV@out{33}\else\ifnum\pdfstrcmp{#1}{error plus}=0\def\macros@LXXV@out{2.1}\else\ifnum\pdfstrcmp{#1}{error minus}=0\def\macros@LXXV@out{3.0}\else\ifnum\pdfstrcmp{#1}{5th percentile}=0\def\macros@LXXV@out{30}\else\ifnum\pdfstrcmp{#1}{95th percentile}=0\def\macros@LXXV@out{35}\else\ifnum\pdfstrcmp{#1}{10th percentile}=0\def\macros@LXXV@out{31}\else\ifnum\pdfstrcmp{#1}{90th percentile}=0\def\macros@LXXV@out{35}\else\def\macros@LXXV@out{??}\fi\fi\fi\fi\fi\fi\fi\fi\macros@LXXV@out}\makeatother

### 2023-01-03 src/scripts/create_macros.py

@@ -17,7 +17,7 @@ def round_sig(f, sig=2):
 
 def save_param_cred_intervals(param_data):
     return  {'median': round_sig(np.median(param_data)), 
-             'error plus':round_sig(np.percentile(param_data, 95)-np.mean(param_data)), 
+             'error plus':round_sig(np.percentile(param_data, 95)-np.median(param_data)), 
              'error minus': round_sig(np.median(param_data)-np.percentile(param_data, 5)),
              '5th percentile': round_sig(np.percentile(param_data, 5)), 
              '95th percentile': round_sig(np.percentile(param_data, 95)), 

### 2023-01-03 src/tex/appendicies.tex
maybe final fix?

@@
         \caption{Plot showing a ``proper'' (see appendix \ref{sec:psplines}) normalized B-Spline basis of order 3 (cubic) with 20 degrees of freedom and equal weights for each component. 
-        In black, we show the resulting spline function given equal weights and denote the location of the knots with gray x's.}
+        In black, we show the resulting spline function given equal weights and denote the location of the knots with gray x's. \LinkExplainer}
         \label{fig:spline_basis}
@@
 
-%One downside of this prior specification as noted in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}, is the dependence on 
-%one's choice of value for the $b$ hyperparameter in the Gamma distribution for $\tau_\lambda$. The models introduced in \citet{Jullion2007RobustSO} show how 
-%to alleviate this. W model $\tau_\lambda$ with a mixture model composed of multiple Gamma distributions each with varying values for $b$. 
-%With this we now have the full prior on $\tau_\lambda$ as:
-
-%\begin{align}
-%    \bm{p} \sim \mathcal{D}(m) \\
-%    p(\tau_\lambda | \bm{p}) = \sum_i^m p_i \Gamma(1, b_i)
-%\end{align}
-
-%\noindent Above $\mathcal{D}(m)$, denotes a Dirichlet distribution with $m$ degrees of freedom and ones as the concentration parameters, 
-%and the $b_i$'s are $m$ different b shape parameters for the Gamma distribution.
-
-%Additionally one can implement a spatially adaptive smoothing prior which allows for a smoothing prior
-%that can smoothly evolve over the domain of your spline function. This is done in practice by having the $\tau_\lambda$ parameter evolve smoothly
-%across the knots. \bruce{CITE BAYESIAN PSPLINES}, formulates a spatially adaptive prior in this way by adding in $n-r-1$ additional parameters that
-%effectively modulate the $\tau_\lambda$ across each difference. We now replace our prior on the coeficients with:
-
-%\begin{eqnarray}
-%\bm{\lambda} \sim \mathcal{G}(\omega, \omega), \\
-%\bm{\Lambda} \equiv \mathrm{diag}\big(1, \lambda_0,...,\lambda_{n-r-1}\big), \\
-%p(\bm{c} | \tau_\lambda) \propto \exp \big[ -\frac{1}{2} \tau_\lambda \bm{c}^{\mathrm{T}} \bm{D_r}^{\mathrm{T}} \bm{\Lambda} \bm{D_r} \bm{c} \big] e^{-n\bm{c}}
-%\end{eqnarray}
-
-%Where above the matrix $\bm{\Lambda}$ a diagonal matrix of shape $(n-r \times n-r)$, and $\omega$ an arbitrarily small value such that the Gamma distribution 
-%prior on $\bm{\lambda}$ has a mean of 1 and an arbitrarily large variance. This enforces a smooth evolution of the smoothing penalty 
-%across the domain that is being analyzed. This type of prior is especiially important when modeling distributions that span large orders of magnitude like 
-%the power-law like mass distributions that are commonly used.
-
 This prior is imparting a natural attraction of the coefficients closer to each other in order to smooth the spline function, so one 
@@
 \noindent
-where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples \citep{gwtc3DATA}. Above, $j$
+where above, we replaced the integrals over each event's likelihood with ensemble averages over $K_i$ posterior samples \citep{GWTC3DATA}. Above, $j$
 indexes the $K_i$ posterior samples from each event and $\pi(\theta, z)$ is the default prior used by parameter estimations that 
@@
     \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model.
-The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.}
+The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.
+\LinkExplainer}
     \label{fig:ppc}
@@
 
+\begin{figure}
+    \includegraphics[width=\linewidth]{figures/spin_ppc_plot.pdf}
+    \caption{Posterior predictive checks showing the CDFs of the observed (black) and predicted (red) distributions of GWTC-3 sized catalogs for each posterior sample of the IID spin B-Spline model.
+The shaded regions show 90\% credible intervals and the solid red line is the median of the predicted distribution.
+\LinkExplainer}
+    \label{fig:spin_ppc}
+    \script{plot_spin_ppcs.py}
+\end{figure}
+
 We follow the posterior predictive checking procedure done in recent population studies to validate our models inferences \citep{o3a_pop,Edelman_2022ApJ}. 
-For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in figure \ref{fig:ppc}.
+For each posterior sample describing our model's inferred population we reweigh the observed event samples and the found injections to that population and draw a set 69 (size of GWTC-3 BBH catalog) samples to construct the observed and predicted distributions we show in figure \ref{fig:ppc} and figure \ref{fig:spin_ppc}.
 When the observed region stays encompassed within the predicted region the model is performing well, which we see across each of the fit parameters.

### 2023-01-03 src/tex/conclusion.tex
add more citations in conclusions

@@
 The results presented in section \ref{sec:mass_dist} illustrate a wider mass distribution than inferred with power-law based models in \citet{o3b_astro_dist}, and a suppressed merger rate 
-at low primary masses (i.e. $\leq8\msun$). While isolated formation is able to predict the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict 
+at low primary masses (i.e.
+$\leq8\msun$), showing possible signs of binary selection effects or the purported low mass gap between neutron stars and black holes \citep{Fishbach_2020_mm,Farah_2022,NoPeaksWithoutValleys}.
+While isolated formation is able to predict the $10\msun$ peak \citep{Antonini_2020}, cluster and dynamical formation scenarios struggle to predict
 a peak in the BH mass distribution less than $15-20\msun$ \citep{Hong_2018, Rodriguez_2019}. Globular cluster formation is expected to produce more top-heavy mass distributions than isolated 
@@
 BBHs that form near active galactic nuclei (AGN) can preferentially produce higher mass black holes \citep{FordAGN, Tagawa_2021, Yang_2019}. 
-We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017}.
+We do not find any evidence for a truncation or rapid decline in the merger rate as a function of mass, that stellar evolution theory predicts due to pair-instability supernovae (PISNe) \citep{Heger_2002,PISN_Woosley,Heger_2003,Spera_2017,Stevenson_2019}.
 The original motivation for the peak in the \textsc{PowerlawPeak} model \citep{Talbot_2018} was to represent a possible ``pileup'' of

### 2023-01-03 src/tex/results.tex

@@
         the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models 
-        from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
+        from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}. \LinkExplainer}
         \label{fig:mass_distribution}
@@
 The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}.}
+    We show the inferred PPD from the \textsc{PowerlawPeak} (blue) and \textsc{PowerlawSpline} (green) models from the LVK's GWTC-3 population analyses \citep{o3b_astro_dist}. \LinkExplainer}
     \label{fig:q_distribution}
@@
 The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
         \label{fig:iid_spinmag_dist}
@@
         with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval. 
-        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
         \label{fig:ind_spinmag_dist}
@@
 The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
         \label{fig:iid_spintilt_dist}
@@
 The solid line shows the population predictive distribution (PPD), and the shaded region the 90\% credible interval.
-        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        For comparison, we show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
         \label{fig:ind_spintilt_dist}
@@
 We show the inferred PPDs from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the
-        Gaussian (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
+        Gaussian (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses. \LinkExplainer}
         \label{fig:eff_dist}
@@
 \end{figure*}
-
-%\begin{figure}[ht!]
-%    \begin{centering}
-   %     \includegraphics[width=\linewidth]{figures/chi_p.pdf}
-   %     \caption{The effective precessing spin distribution inferred with the B-Spline IID spin model (red).
-The solid line shows the population predictive %distribution (PPD), and the shaded region the 90\% credible interval.
-We show the inferred $\chi_\mathrm{p}$
-   %     PPD from the independent component spin B-Spline model (purple), and both the \textsc{Default} (blue) model and the 
-   %     Gaussian $\chi_\mathrm{p}$ (green) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
-   %     \label{fig:chip_dist}
-   % \end{centering}
-   % \script{plot_chip.py}
-% \end{figure}
 
@@
     from the LVK's GWTC-3 population analyses in blue and a power law with exponent of 2.7 in gray, representing the expected star formation rate 
-    \citep{Madau_2014, o3b_astro_dist}.}
+    \citep{Madau_2014, o3b_astro_dist}. \LinkExplainer}
     \label{fig:rofz}
@@
     \caption{The B-spline modulation to the underlying power law in redshift, (red). The solid line shows the population predictive distribution (PPD),
-    and the shaded region the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines.}
+    and the shaded region the 90\% credible interval. We show the 90\% credible interval of the prior predictive distribution in dashed black lines. \LinkExplainer}
     \label{fig:z_modulation}

### 2023-01-24 src/tex/appendicies.tex
add reproducability appendix

@@
 When the observed region stays encompassed within the predicted region the model is performing well, which we see across each of the fit parameters.
+
+\section{Reproducibility}
+\label{sec:reproducibility}
+
+In the spirit of open source and reproducible science, this study was done using the reproducibility software \href{https://github.com/showyourwork/showyourwork}{\showyourwork} \citep{Luger2021}, which leverages continuous integration to programmatically download the data from \href{https://zenodo.org/}{zenodo.org}, create the figures, and compile the manuscript.
+Each figure caption contains two links that point towards the dataset (stored on zenodo) used in the corresponding figure, and to the script used to make the figure (at the commit corresponding to the current build of the manuscript).
+The git repository associated to this study is publicly available at \url{https://github.com/bruce-edelman/CoveringYourBasis}, which allows anyone to re-build the entire manuscript.
+The datasets and all analysis or figure generating scripts are all stored on \href{https://zenodo.org/}{zenodo.org} at \url{https://zenodo.org/record/7566301} \citep{edelman_bruce_2022_7422514}.

### 2023-01-24 src/tex/ms.tex
add reproducability appendix

@@
-\documentclass[twocolumn,linenumbers]{aastex631}
+\documentclass[twocolumn]{aastex631}
 
@@
 \newcommand{\bruce}[1]{\textcolor{blue}{BE: #1}}
-\newcommand{\NewChange}[1]{\textcolor{green}{#1}}
+%\newcommand{\NewChange}[1]{\textcolor{green}{#1}}
+\newcommand{\NewChange}[1]{#1}
 \newcommand{\LinkExplainer}{The icons link to the code used to generate this figure and to \href{https://zenodo.org}{zenodo} entries of any public data used.}
@@
 We thank Tom Callister, Will Farr, Maya Fishbach, Salvatore Vitale, and Jaxen Godfrey for useful discussions during the 
-preparation of this manuscript and/or helpful comments on early drafts. In the spirit of open source and 
-reproducible science, this paper was written using the \textsc{showyourwork} package \citep{Luger2021}, and can be 
-found in this \href{https://github.com/bruce-edelman/CoveringYourBasis}{repository} and the accompanying data realease; \citet{edelman_bruce_2022_7422514}. Z.D. also acknowledges support from 
+preparation of this manuscript and/or helpful comments on early drafts. Z.D. also acknowledges support from 
 the CIERA Board of Visitors Research Professorship.  This research has made use of data, software and/or web tools obtained 
